---
title: "Avenelles - test méthode"
output:
  html_document:
    toc: true
    toc_float: true
    number_sections: true
    code_folding: hide
date: "2025-06-06"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = F, warning = F, error = F, fig.align = "center", collapse = T,
                      cache = T)
```

```{r libraries, cache = F}
library(ggplot2)
library(ggpubr)

library(dplyr)
library(readxl)
library(lubridate)

library(nlme)

library(knitr)
library(kableExtra)
```

# Get data

https://bdoh.inrae.fr/SITE-ATELIER-ARDIERES-MORCILLE/ 

https://onlinelibrary.wiley.com/doi/10.1002/hyp.14384


```{r load-data-from-excel, message = F}

avenelles <- readxl::read_xlsx(path = "Data_Avenelles_DOC_DIC_Debit.xlsx", sheet = "Data_Avenelles_DOC_DIC_Debit", col_types = c("date","numeric", "text","numeric","text","numeric","text","text","numeric")) %>%  mutate(Site = NULL, bv_km2 = NULL) %>% unique()

```

```{r merge}

#avenelles$q_L.s <- imputeTS::na_interpolation(avenelles$q_L.s) # fill empty Q

avenelles$year <- year(avenelles$DateHeure)
avenelles$week <- week(avenelles$DateHeure)
avenelles$month <- month(avenelles$DateHeure)

avenelles$commondate <- as.Date(paste0("2000-", format(avenelles$DateHeure,"%j")), "%Y-%j")
avenelles$Date <- format(avenelles$DateHeure, "%Y-%m-%d") %>% as.Date()

avenelles$period <- with(avenelles, as.numeric(-(DateHeure - lead(DateHeure)))) # period is calculated in second, we get it in days
avenelles$periodj <- round(avenelles$period / 60 / 60 / 24, 0)

avenelles <- unique(avenelles)
  
strange_periods_dates <- avenelles %>% subset(periodj > 3) %>% pull(Date) 

bv <- 45
```

Une mesure de doc par jour en général.

```{r summary-data}
summary_avenelles <- merge(
avenelles %>% subset(!is.na(doc_mg.L)) %>% group_by(year) %>% summarise(nb_doc = n()),
avenelles %>% subset(!is.na(q_L.s)) %>% group_by(year) %>% summarise(nb_q = n()), by = "year", all = T) %>% 
  merge(avenelles %>% subset(!is.na(doc_mg.L) ) %>% group_by(year) %>% summarise(total_period_j_nona = length(unique(DateHeure))), by = "year", all = T)

knitr::kable(summary_avenelles) %>% kableExtra::kable_styling()

cat("mean Q", mean(avenelles$q_L.s, na.rm = T))
cat("range OC (0-25-50-75-100)", quantile(with(avenelles, doc_mg.L), na.rm = T))


avenelles %>% filter(!is.na(doc_mg.L)) %>% group_by(year) %>% summarise(nb_obs = n(), nb_unique_date = length(unique(Date))) %>% kable() %>% kable_styling()
```


# View data

```{r plot-by-year-doc, fig.dim = c(10,15)}

ggarrange(
ggplot(subset(avenelles, year %in% c(2007:2016)), aes(x = commondate))+
  geom_point(aes(y = q_L.s, col = "Débit, L/s"), alpha = 0.5)+
  scale_x_date(labels = function(x) format(x, "%d-%b"), date_minor_breaks = "1 month", name = "")+
  scale_color_manual(values = c("lightblue"), name = "")+
  facet_grid(rows = vars(year))+
  labs(y = "Débit, L/s", col = "")+
  theme_minimal(base_size = 15)+
  theme(legend.position = "none"),

ggplot(subset(avenelles, year %in% c(2007:2016)), aes(x = commondate))+
  geom_point(aes(y = doc_mg.L, col = "DOC, mg.L"), alpha = 0.5)+
  scale_x_date(labels = function(x) format(x, "%d-%b"), date_minor_breaks = "1 month", name = "")+
  scale_color_manual(values = c("palegreen4"), name = "")+
  facet_grid(rows = vars(year))+
  labs(y = "DOC, mg/L", col = "")+
  theme_minimal(base_size = 15)+
  theme(legend.position = "none")
)

```

# Relation DOC-Q

```{r doc-avenelles}
doc_avenelles <- avenelles %>% filter(!is.na(doc_mg.L))

'%notin%' <- function(x,y) !(x %in% y)

ggplot(doc_avenelles)+geom_point(aes(x = q_L.s, y = doc_mg.L))
ggplot(doc_avenelles)+geom_point(aes(x = log(q_L.s), y = doc_mg.L, col = as.character(year), shape = as.character(year)))+scale_color_viridis_d()

ggplot(filter(doc_avenelles, year == 2014))+geom_point(aes(x = log(q_L.s), y = doc_mg.L))
ggplot(filter(doc_avenelles, year %notin% c(2009,2014,2015)), aes(x = q_L.s, y = doc_mg.L))+geom_point()+
  geom_smooth()

lm(doc_mg.L~q_L.s, data = doc_avenelles) %>% summary()
```


# Annual and interannual flux 

Années choisies: années avec des observations plus de 1 jour sur 2 (nobs > 365/2)

On considère que l'erreur sur DOC vient de la mesure par analyse TOC.

```{r uncertainties}
complete_years <- c(2009,2011,2012,2013,2014,2015,2016,2021)
nyears <- length(complete_years)

avenelles_flux <- avenelles %>% filter(year %in% complete_years)


q_u <- 0.1

nobs <- dim(avenelles_flux)[1]
nrep <- 1000
```

## total flux

```{r compute-flux}
#doc matrix
doc_meas <- matrix(avenelles_flux$doc_mg.L, nrow = nrep, ncol = nobs, byrow = T) # repeats nrep lines with observations

doc_cv <- 3.2*doc_meas^(-0.2) # from quich check Claire, vaut pour TOC mais pas autres moyens de mesure
doc_random <- matrix(rnorm(nrep*nobs, mean = 0, sd = 1), nrow=nrep, ncol = nobs)
doc_noise <- doc_cv*doc_random
doc_mat <- doc_meas * (1 + doc_noise/100) # final value of doc, with noise in percent

# Q matrix
q_meas <- matrix(avenelles_flux$q_L.s, nrow = nrep, ncol = nobs, byrow = T) # repeats nrow_boot times the vector q_L.s
q_noise <- matrix(rnorm(nrep*nobs, mean = 0, sd = q_u), nrow = nrep, ncol = nobs) # creates a noise in percent (proportion), between 0 and 10%
q_mat <- q_meas * (1 + q_noise) # final value of q, with noise

period_mat <- matrix(avenelles_flux$period, nrow = nrep, ncol = nobs, byrow = T) # in seconds

# Flux per time step
flux_ton_mat <- doc_mat*1e-9*q_mat*period_mat # flux per period (period in seconds, so flux in ton/s is converted to flux per period). 
flux_ton.s_mat <- doc_mat*1e-9*q_mat # without period

index_years <- lapply(complete_years, function(y){which(avenelles_flux$year == y)}) # list of indices corresponding to each year

# Annual flux
annual_flux_ton.y <- sapply(index_years, function(idx){apply(flux_ton_mat[,idx], 1, sum, na.rm = T)}) # sum of fluxes per year, for each iteration of the bootstrap. Result is a matrix with nrow_boot rows and 19 columns (1 per year)
annual_flux_pi <- apply(annual_flux_ton.y, 2, quantile, probs = c(0.025, 0.5, 0.975), na.rm = T) # prediction interval for annual fluxes, per year. 3 lignes, 19 columns
annual_flux_mean <- colMeans(annual_flux_ton.y, na.rm = T) # mean annual flux per year. 1 vector
annual_flux_sd <- apply(annual_flux_ton.y, 2, sd, na.rm = T) # standard deviation of annual flux per year. Is just an estimate of goodness of mean, not as good as than the confidence interval. 

annual_flux_df <- data.frame(year = complete_years, 
                        annual_flux_mean = annual_flux_mean, 
                        annual_flux_variability = annual_flux_sd, 
                        annual_flux_pi_lower = annual_flux_pi[1,], 
                        annual_flux_pi_upper = annual_flux_pi[3,])

# Interannual flux 
interannual_flux_ton.y <- rowMeans(annual_flux_ton.y, na.rm = T) # mean interannual flux per iteration of the bootstrap
interannual_flux_pi <- quantile(interannual_flux_ton.y, probs = c(0.025, 0.5, 0.975), na.rm = T) # prediction interval
interannual_flux_mean <- mean(interannual_flux_ton.y, na.rm = T) # mean interannual flux
interannual_flux_variability <- sd(annual_flux_mean, na.rm = T) # standard deviation of interannual flux per year

interannual_flux_df <- data.frame(year = "interannual", annual_flux_mean = interannual_flux_mean, 
                                  annual_flux_variability = interannual_flux_variability,
                        annual_flux_pi_lower = interannual_flux_pi[1], 
                        annual_flux_pi_upper = interannual_flux_pi[3])

total_flux_df <- rbind(annual_flux_df, interannual_flux_df)
total_flux_df$group <- c(rep("annual", nyears), "interannual")

# Q df

annual_q <- sapply(index_years, function(idx){apply(q_mat[,idx], 1, sum, na.rm = T)}) # sum of fluxes per year, for each iteration of the bootstrap. Result is a matrix with nrow_boot rows and 19 columns (1 per year)
annual_q_pi <- apply(annual_q, 2, quantile, probs = c(0.025, 0.5, 0.975), na.rm = T) # prediction interval for annual fluxes, per year. 3 lignes, 19 columns
annual_q_mean <- colMeans(annual_q, na.rm = T) # mean annual flux per year. 1 vector
annual_q_sd <- apply(annual_q, 2, sd, na.rm = T) # standard deviation of annual flux per year. Is just an estimate of goodness of mean, not as good as than the confidence interval. 
interannual_q <- rowMeans(annual_q, na.rm = T) # mean interannual flux per iteration of the bootstrap
interannual_q_pi <- quantile(interannual_q, probs = c(0.025, 0.5, 0.975), na.rm = T) # prediction interval
interannual_q_mean <- mean(interannual_q, na.rm = T) # mean interannual flux
interannual_q_variability <- sd(annual_q_mean, na.rm = T) # standard deviation of interannual flux per year

q_df <- data.frame(year = c(complete_years, "interannual"), 
                        q_mean = c(annual_q_mean, interannual_q_mean),
                        q_variability = c(annual_flux_sd, interannual_q_variability), 
                        q_pi_lower = c(annual_q_pi[1,], interannual_q_pi[1]), 
                        q_pi_upper = c(annual_q_pi[3,], interannual_q_pi[3]),
                   group = c(rep("annual", nyears), "interannual"))

# Plot
ggplot()+
  geom_col(data = total_flux_df, aes(x=year, y = annual_flux_mean, fill = group))+
    geom_errorbar(data = total_flux_df, aes(x = year, ymin = annual_flux_pi_lower, ymax = annual_flux_pi_upper, col = "prediction interval"), width = 0.3, size = 0.8)+
  geom_errorbar(data = filter(total_flux_df, year == "interannual"), aes(x = year, ymin = annual_flux_mean - annual_flux_variability, ymax = annual_flux_mean + annual_flux_variability, col = "interannual variability"), width = 0.2, size = 0.8, linetype = 2)+
  scale_fill_manual(values = c("annual" = "lightblue", "interannual" = "indianred"))+
  scale_color_manual(values = c("prediction interval" = "darkblue", "interannual variability" = "darkred"), name = "")+
   labs(x = "Year", y = "Flux (ton/year)", fill = "")+
  theme_minimal(base_size = 15)+
  theme(axis.text.x = element_text(angle = 45, hjust = 1), legend.position = "bottom")

ggplot()+
  geom_col(data = q_df, aes(x=year, y = q_mean, fill = group))+
    geom_errorbar(data = q_df, aes(x = year, ymin = q_pi_lower, ymax = q_pi_upper, col = "prediction interval"), width = 0.3, size = 0.8)+
  geom_errorbar(data = filter(q_df, year == "interannual"), aes(x = year, ymin = q_mean - q_variability, ymax = q_mean + q_variability, col = "interannual variability"), width = 0.2, size = 0.8, linetype = 2)+
  scale_fill_manual(values = c("annual" = "lightblue", "interannual" = "indianred"))+
  scale_color_manual(values = c("prediction interval" = "darkblue", "interannual variability" = "darkred"), name = "")+
   labs(x = "Year", y = "Discharge (L/year)", fill = "")+
  theme_minimal(base_size = 15)+
  theme(axis.text.x = element_text(angle = 45, hjust = 1), legend.position = "bottom")

knitr::kable(total_flux_df, digits = 2, row.names = F) %>% kableExtra::kable_styling()

```

## Specific flux

```{r specific-flux}
sflux_ton_mat <- doc_mat*1e-9*q_mat*period_mat/bv # flux per period (period in seconds, so flux in ton/s is converted to flux per period). 
sflux_ton.s_mat <- doc_mat*1e-9*q_mat/bv # without period

annual_sflux_ton.y <- sapply(index_years, function(idx){apply(sflux_ton_mat[,idx], 1, sum, na.rm = T)}) # sum of fluxes per year, for each iteration of the bootstrap. Result is a matrix with nrow_boot rows and 19 columns (1 per year)
annual_sflux_pi <- apply(annual_sflux_ton.y, 2, quantile, probs = c(0.025, 0.5, 0.975), na.rm = T) # prediction interval for annual fluxes, per year. 3 lignes, 19 columns
annual_sflux_mean <- colMeans(annual_sflux_ton.y, na.rm = T) # mean annual flux per year. 1 vector
annual_sflux_sd <- apply(annual_sflux_ton.y, 2, sd, na.rm = T) # standard deviation of annual flux per year. Is just an estimate of goodness of mean, not as good as than the confidence interval. 

annual_sflux_df <- data.frame(year = complete_years, 
                        annual_flux_mean = annual_sflux_mean, 
                        annual_flux_variability = annual_sflux_sd, 
                        annual_flux_pi_lower = annual_sflux_pi[1,], 
                        annual_flux_pi_upper = annual_sflux_pi[3,])

# Interannual flux 
interannual_sflux_ton.y <- rowMeans(annual_sflux_ton.y, na.rm = T) # mean interannual flux per iteration of the bootstrap
interannual_sflux_pi <- quantile(interannual_sflux_ton.y, probs = c(0.025, 0.5, 0.975), na.rm = T) # prediction interval
interannual_sflux_mean <- mean(interannual_sflux_ton.y, na.rm = T) # mean interannual flux
interannual_sflux_variability <- sd(annual_sflux_mean, na.rm = T) # standard deviation of interannual flux per year

interannual_sflux_df <- data.frame(year = "interannual", annual_flux_mean = interannual_sflux_mean, 
                                  annual_flux_variability = interannual_sflux_variability,
                        annual_flux_pi_lower = interannual_sflux_pi[1], 
                        annual_flux_pi_upper = interannual_sflux_pi[3])

total_sflux_df <- rbind(annual_sflux_df, interannual_sflux_df)
total_sflux_df$group <- c(rep("annual", nyears), "interannual")

ggplot()+
  geom_col(data = total_sflux_df, aes(x=year, y = annual_flux_mean, fill = group))+
    geom_errorbar(data = total_sflux_df, aes(x = year, ymin = annual_flux_pi_lower, ymax = annual_flux_pi_upper, col = "prediction interval"), width = 0.3, size = 0.8)+
  geom_errorbar(data = filter(total_sflux_df, year == "interannual"), aes(x = year, ymin = annual_flux_mean - annual_flux_variability, ymax = annual_flux_mean + annual_flux_variability, col = "interannual variability"), width = 0.2, size = 0.8, linetype = 2)+
  scale_fill_manual(values = c("annual" = "lightblue", "interannual" = "indianred"))+
  scale_color_manual(values = c("prediction interval" = "darkblue", "interannual variability" = "darkred"), name = "")+
   labs(x = "Year", y = "Flux (tons/km2/year)", fill = "")+
  theme_minimal(base_size = 15)+
  theme(axis.text.x = element_text(angle = 45, hjust = 1), legend.position = "bottom")

```


# Time steps

```{r common-data-timestep}
avenelles_time <- avenelles_flux %>% select(c("DateHeure", "doc_mg.L","q_L.s"))
```


## 2 Days

```{r avenelles-day2, cache.lazy = F}
# prepare df
avenelles_group_day2 <- avenelles_time %>% mutate(day = as.numeric(as.Date(format(DateHeure, "%Y-%m-%d"))), month = month(DateHeure), day2 = floor((day - min(day)) / 2), year = year(DateHeure)) %>% group_by(day2, year) # group avenelles_time by day
nrow_day2 <- n_groups(avenelles_group_day2)


# creates matrix for DOC
avenelles_doc_day2 <- avenelles_group_day2 %>% select(c("DateHeure","day2", "doc_mg.L")) %>% summarize("DateHeure" = mean(DateHeure),"list_doc" = list(doc_mg.L)) %>% ungroup() # creates a list of doc for each day2
doc_random_day2 <- replicate(nrep, sapply(avenelles_doc_day2$list_doc, function(x) sample(x,1)))%>% t() # matrix of mes: one random sample per day2, replicated 1000 times

doc_cv_day2 <- 3.2*doc_random_day2^(-0.2)
rnorm_day2 <- matrix(rnorm(nrep*nrow_day2, mean = 0, sd = 1), nrow=nrep, ncol = nrow_day2)
doc_noise_day2 <- doc_cv_day2*rnorm_day2
doc_mat_day2 <- doc_random_day2 * (1 + doc_noise_day2/100) # final value of doc, with noise in percent

# matrix for q
q_day2 <- avenelles_group_day2 %>% select(c("day2", "q_L.s")) %>% summarize_all(list("q_mean" = mean, "q_sd" = sd)) %>% ungroup() # mean of Q for each day2

q_day2_mean <-  matrix(q_day2$q_mean, nrow = nrep, ncol = nrow_day2, byrow = T)
q_noise <- matrix(rnorm(nrep*nrow_day2, mean = 0, sd = q_u), nrow = nrep, ncol = nrow_day2) # creates a noise in percent (proportion), between 0 and 10%
q_mat_day2 <- q_day2_mean * (1 + q_noise) # final MC of q, with noise. SD NOT INCLUDED: will not always be available

# period matrix: too many missing 2-days
avenelles_doc_day2$period <- with(avenelles_doc_day2, as.numeric(-(DateHeure - lead(DateHeure)))) # period is calculated in hours
period_mat_day2 <- matrix(avenelles_doc_day2$period, nrow = nrep, ncol = nrow_day2, byrow = T) # in seconds

# compute flux
flux_ton_mat_day2 <- doc_mat_day2*1e-9*q_mat_day2*period_mat_day2*60*60*24 #doc in mg/L converted to ton; q_mat in L/s. Period : time between groups of days. Period is in days

# Get index for columns by year
index_years <- lapply(complete_years, function(y){which(avenelles_doc_day2$year == y)}) # list of indices corresponding to each year

# annual flux
annual_flux_ton.y_day2 <- lapply(index_years, function(idx){apply(flux_ton_mat_day2[,idx], 1, sum, na.rm = T)}) %>% do.call("cbind", .)# sum of fluxes per year, for each iteration of the bootstrap. 
annual_flux_day2_pi <- apply(annual_flux_ton.y_day2, 2, quantile, probs = c(0.025, 0.5, 0.975), na.rm = T) # confidence interval for annual fluxes, per year. 3 lignes, 19 columns
annual_flux_day2_mean <- colMeans(annual_flux_ton.y_day2, na.rm = T) # mean annual flux per year. 1 vector
annual_flux_day2_sd <- apply(annual_flux_ton.y_day2, 2, sd, na.rm = T) # standard deviation of annual flux per year. Is just an estimate of goodness of mean, not as good as than the confidence interval. 
 
annual_flux_day2_df <- data.frame(year = complete_years, 
                        annual_flux_mean = annual_flux_day2_mean, 
                        annual_flux_variability = annual_flux_day2_sd, 
                        annual_flux_pi_lower = annual_flux_day2_pi[1,], 
                        annual_flux_pi_upper = annual_flux_day2_pi[3,])

interannual_flux_ton.y_day2 <- rowMeans(annual_flux_ton.y_day2, na.rm = T) # mean interannual flux per iteration of the bootstrap
interannual_flux_pi_day2 <- quantile(interannual_flux_ton.y_day2, probs = c(0.025, 0.5, 0.975), na.rm = T) # prediction interval
interannual_flux_mean_day2 <- mean(interannual_flux_ton.y_day2, na.rm = T) # mean interannual flux
interannual_flux_variability_day2 <- sd(annual_flux_day2_mean, na.rm = T) # standard deviation of interannual flux per year

interannual_flux_day2_df <- data.frame(year = "interannual", annual_flux_mean = interannual_flux_mean_day2, 
                                  annual_flux_variability = interannual_flux_variability_day2,
                        annual_flux_pi_lower = interannual_flux_pi_day2[1], 
                        annual_flux_pi_upper = interannual_flux_pi_day2[3])

total_flux_day2_df <- rbind(annual_flux_day2_df, interannual_flux_day2_df)
total_flux_day2_df$group <- c(rep("annual", nyears), "interannual")

ggplot()+
  geom_col(data = total_flux_day2_df, aes(x=year, y = annual_flux_mean, fill = group))+
    geom_errorbar(data = total_flux_day2_df, aes(x = year, ymin = annual_flux_pi_lower, ymax = annual_flux_pi_upper, col = "prediction interval"), width = 0.3, size = 0.8)+
  geom_errorbar(data = filter(total_flux_day2_df, year == "interannual"), aes(x = year, ymin = annual_flux_mean - annual_flux_variability, ymax = annual_flux_mean + annual_flux_variability, col = "interannual variability"), width = 0.2, size = 0.8, linetype = 2)+
  scale_fill_manual(values = c("annual" = "lightblue", "interannual" = "indianred"))+
  scale_color_manual(values = c("prediction interval" = "darkblue", "interannual variability" = "darkred"), name = "")+
   labs(x = "Year", y = "Flux, from bi-dayly mean values (ton/year)", fill = "")+
  theme_minimal(base_size = 15)+
  theme(axis.text.x = element_text(angle = 45, hjust = 1), legend.position = "bottom")

knitr::kable(total_flux_day2_df, digits = 2, row.names = F) %>% kableExtra::kable_styling()
```

## 4 Days 

```{r avenelles-day4, cache.lazy = F}
# prepare df
avenelles_group_day4 <- avenelles_time %>% mutate(day = as.numeric(as.Date(format(DateHeure, "%Y-%m-%d"))), month = month(DateHeure), day4 = floor((day - min(day)) / 4), year = year(DateHeure)) %>% group_by(day4, year) # group avenelles_time by day
nrow_day4 <- n_groups(avenelles_group_day4)



# creates matrix for DOC
avenelles_doc_day4 <- avenelles_group_day4 %>% select(c("day4", "doc_mg.L")) %>% summarize("list_doc" = list(doc_mg.L)) %>% ungroup() # creates a list of mes for each day4
doc_random_day4 <- replicate(nrep, sapply(avenelles_doc_day4$list_doc, function(x) sample(x,1)))%>% t() # matrix of mes: one random sample per day4, replicated 1000 times
# doc_day4_noise <- matrix(rnorm(nrep*nrow_day4, mean = 0, sd = doc_u), nrow = nrep, ncol = nrow_day4) 
# doc_mat_day4 <- doc_day4_random * (1 + doc_day4_noise) # final value of mes, with noise
# 
# doc_mean <- colMeans(doc_mat_day4)

doc_cv_day4 <- 3.2*doc_random_day4^(-0.2)
rnorm_day4 <- matrix(rnorm(nrep*nrow_day4, mean = 0, sd = 1), nrow=nrep, ncol = nrow_day4)
doc_noise_day4 <- doc_cv_day4*rnorm_day4
doc_mat_day4 <- doc_random_day4 * (1 + doc_noise_day4/100) # final value of doc, with noise in percent



# matrix for q
q_day4 <- avenelles_group_day4 %>% select(c("day4", "q_L.s")) %>% summarize_all(list("q_mean" = mean, "q_sd" = sd)) %>% ungroup() # mean of Q for each day4

q_day4_mean <-  matrix(q_day4$q_mean, nrow = nrep, ncol = nrow_day4, byrow = T)
q_noise <- matrix(rnorm(nrep*nrow_day4, mean = 0, sd = q_u), nrow = nrep, ncol = nrow_day4) # creates a noise in percent (proportion), between 0 and 10%
q_mat_day4 <- q_day4_mean * (1 + q_noise) # final MC of q, with noise. SD NOT INCLUDED: will not always be available

# compute flux
flux_ton_mat_day4 <- doc_mat_day4*1e-9*q_mat_day4*60*60*24*4 #pred_day4 * mes_mat : poc in mg/L converted to ton; q_mat converted from m3/s to L/s. Period : nb of seconds in 1 day4. 

# Get index for columns by year
index_years <- lapply(complete_years, function(y){which(avenelles_doc_day4$year == y)}) # list of indices corresponding to each year

# annual flux
annual_flux_ton.y_day4 <- lapply(index_years, function(idx){apply(flux_ton_mat_day4[,idx], 1, sum, na.rm = T)}) %>% do.call("cbind", .)# sum of fluxes per year, for each iteration of the bootstrap. 
annual_flux_day4_pi <- apply(annual_flux_ton.y_day4, 2, quantile, probs = c(0.025, 0.5, 0.975), na.rm = T) # confidence interval for annual fluxes, per year. 3 lignes, 19 columns
annual_flux_day4_mean <- colMeans(annual_flux_ton.y_day4, na.rm = T) # mean annual flux per year. 1 vector
annual_flux_day4_sd <- apply(annual_flux_ton.y_day4, 2, sd, na.rm = T) # standard deviation of annual flux per year. Is just an estimate of goodness of mean, not as good as than the confidence interval. 
 
annual_flux_day4_df <- data.frame(year = complete_years, 
                        annual_flux_mean = annual_flux_day4_mean, 
                        annual_flux_variability = annual_flux_day4_sd, 
                        annual_flux_pi_lower = annual_flux_day4_pi[1,], 
                        annual_flux_pi_upper = annual_flux_day4_pi[3,])

interannual_flux_ton.y_day4 <- rowMeans(annual_flux_ton.y_day4, na.rm = T) # mean interannual flux per iteration of the bootstrap
interannual_flux_pi_day4 <- quantile(interannual_flux_ton.y_day4, probs = c(0.025, 0.5, 0.975), na.rm = T) # prediction interval
interannual_flux_mean_day4 <- mean(interannual_flux_ton.y_day4, na.rm = T) # mean interannual flux
interannual_flux_variability_day4 <- sd(annual_flux_day4_mean, na.rm = T) # standard deviation of interannual flux per year

interannual_flux_day4_df <- data.frame(year = "interannual", annual_flux_mean = interannual_flux_mean_day4, 
                                  annual_flux_variability = interannual_flux_variability_day4,
                        annual_flux_pi_lower = interannual_flux_pi_day4[1], 
                        annual_flux_pi_upper = interannual_flux_pi_day4[3])

total_flux_day4_df <- rbind(annual_flux_day4_df, interannual_flux_day4_df)
total_flux_day4_df$group <- c(rep("annual", nyears), "interannual")

ggplot()+
  geom_col(data = total_flux_day4_df, aes(x=year, y = annual_flux_mean, fill = group))+
    geom_errorbar(data = total_flux_day4_df, aes(x = year, ymin = annual_flux_pi_lower, ymax = annual_flux_pi_upper, col = "prediction interval"), width = 0.3, size = 0.8)+
  geom_errorbar(data = filter(total_flux_day4_df, year == "interannual"), aes(x = year, ymin = annual_flux_mean - annual_flux_variability, ymax = annual_flux_mean + annual_flux_variability, col = "interannual variability"), width = 0.2, size = 0.8, linetype = 2)+
  scale_fill_manual(values = c("annual" = "lightblue", "interannual" = "indianred"))+
  scale_color_manual(values = c("prediction interval" = "darkblue", "interannual variability" = "darkred"), name = "")+
   labs(x = "Year", y = "Flux, from bi-dayly mean values (ton/year)", fill = "")+
  theme_minimal(base_size = 15)+
  theme(axis.text.x = element_text(angle = 45, hjust = 1), legend.position = "bottom")

knitr::kable(total_flux_day4_df, digits = 2, row.names = F) %>% kableExtra::kable_styling()
```



## 1 week

```{r avenelles-week, cache.lazy = F}
# prepare df
avenelles_group_week <- avenelles_time %>% mutate("week" = week(DateHeure), year = year(DateHeure)) %>% group_by(week,year) # group isere_time by week
nrow_week <- n_groups(avenelles_group_week)


# creates matrix for DOC
avenelles_doc_week <- avenelles_group_week %>% select(c("week", "doc_mg.L")) %>% summarize("list_doc" = list(doc_mg.L)) %>% ungroup() # creates a list of mes for each week
doc_random_week <- replicate(nrep, sapply(avenelles_doc_week$list_doc, function(x) sample(x,1)))%>% t() # matrix of mes: one random sample per week, replicated 1000 times
# doc_week_noise <- matrix(rnorm(nrep*nrow_week, mean = 0, sd = doc_u), nrow = nrep, ncol = nrow_week) 
# doc_mat_week <- doc_week_random * (1 + doc_week_noise) # final value of mes, with noise
# doc_mean <- colMeans(doc_mat_week)

doc_cv_week <- 3.2*doc_random_week^(-0.2)
rnorm_week <- matrix(rnorm(nrep*nrow_week, mean = 0, sd = 1), nrow=nrep, ncol = nrow_week)
doc_noise_week <- doc_cv_week*rnorm_week
doc_mat_week <- doc_random_week * (1 + doc_noise_week/100) # final value of doc, with noise in percent


# matrix for q
q_week <- avenelles_group_week %>% select(c("week", "q_L.s")) %>% summarize_all(list("q_mean" = mean, "q_sd" = sd)) %>% ungroup() # mean of Q for each week

q_week_mean <-  matrix(q_week$q_mean, nrow = nrep, ncol = nrow_week, byrow = T)
q_noise <- matrix(rnorm(nrep*nrow_week, mean = 0, sd = q_u), nrow = nrep, ncol = nrow_week) # creates a noise in percent (proportion), between 0 and 10%
q_mat_week <- q_week_mean * (1 + q_noise) # final MC of q, with noise. SD NOT INCLUDED: will not always be available

# compute flux
flux_ton_mat_week <- doc_mat_week*1e-9*q_mat_week*60*60*24*7 #pred_week * mes_mat : poc in mg/L converted to ton; q_mat converted from m3/s to L/s. Period : nb of seconds in 1 week. 

# Get index for columns by year
index_years <- lapply(complete_years, function(y){which(avenelles_doc_week$year == y)}) # list of indices corresponding to each year

# annual flux
annual_flux_ton.y_week <- lapply(index_years, function(idx){apply(flux_ton_mat_week[,idx], 1, sum, na.rm = T)}) %>% do.call("cbind", .) # sum of fluxes per year, for each iteration of the bootstrap. 
annual_flux_week_pi <- apply(annual_flux_ton.y_week, 2, quantile, probs = c(0.025, 0.5, 0.975), na.rm = T) # confidence interval for annual fluxes, per year. 3 lignes, 19 columns
annual_flux_week_mean <- colMeans(annual_flux_ton.y_week, na.rm = T) # mean annual flux per year. 1 vector
annual_flux_week_sd <- apply(annual_flux_ton.y_week, 2, sd, na.rm = T) # standard deviation of annual flux per year. Is just an estimate of goodness of mean, not as good as than the confidence interval. 
 
annual_flux_week_df <- data.frame(year = complete_years, 
                        annual_flux_mean = annual_flux_week_mean, 
                        annual_flux_variability = annual_flux_week_sd, 
                        annual_flux_pi_lower = annual_flux_week_pi[1,], 
                        annual_flux_pi_upper = annual_flux_week_pi[3,])

interannual_flux_ton.y_week <- rowMeans(annual_flux_ton.y_week, na.rm = T) # mean interannual flux per iteration of the bootstrap
interannual_flux_pi_week <- quantile(interannual_flux_ton.y_week, probs = c(0.025, 0.5, 0.975), na.rm = T) # prediction interval
interannual_flux_mean_week <- mean(interannual_flux_ton.y_week, na.rm = T) # mean interannual flux
interannual_flux_variability_week <- sd(annual_flux_week_mean, na.rm = T) # standard deviation of interannual flux per year

interannual_flux_week_df <- data.frame(year = "interannual", annual_flux_mean = interannual_flux_mean_week, 
                                  annual_flux_variability = interannual_flux_variability_week,
                        annual_flux_pi_lower = interannual_flux_pi_week[1], 
                        annual_flux_pi_upper = interannual_flux_pi_week[3])

total_flux_week_df <- rbind(annual_flux_week_df, interannual_flux_week_df)
total_flux_week_df$group <- c(rep("annual", nyears), "interannual")

ggplot()+
  geom_col(data = total_flux_week_df, aes(x=year, y = annual_flux_mean, fill = group))+
    geom_errorbar(data = total_flux_week_df, aes(x = year, ymin = annual_flux_pi_lower, ymax = annual_flux_pi_upper, col = "prediction interval"), width = 0.3, size = 0.8)+
  geom_errorbar(data = filter(total_flux_week_df, year == "interannual"), aes(x = year, ymin = annual_flux_mean - annual_flux_variability, ymax = annual_flux_mean + annual_flux_variability, col = "interannual variability"), width = 0.2, size = 0.8, linetype = 2)+
  scale_fill_manual(values = c("annual" = "lightblue", "interannual" = "indianred"))+
  scale_color_manual(values = c("prediction interval" = "darkblue", "interannual variability" = "darkred"), name = "")+
   labs(x = "Year", y = "Flux, from bi-dayly mean values (ton/year)", fill = "")+
  theme_minimal(base_size = 15)+
  theme(axis.text.x = element_text(angle = 45, hjust = 1), legend.position = "bottom")
```
## 2 weeks

```{r avenelles-week2, cache.lazy = F}
# prepare df
avenelles_group_week2 <- avenelles_time %>% mutate(week = week(DateHeure), week2 =  floor(as.numeric(week - min(week)) / 2), year = year(DateHeure)) %>% group_by(week2,year) # group isere_time by week2
nrow_week2 <- n_groups(avenelles_group_week2)


# creates matrix for DOC
avenelles_doc_week2 <- avenelles_group_week2 %>% select(c("week2", "doc_mg.L")) %>% summarize("list_doc" = list(doc_mg.L)) %>% ungroup() # creates a list of mes for each week2
doc_random_week2 <- replicate(nrep, sapply(avenelles_doc_week2$list_doc, function(x) sample(x,1)))%>% t() # matrix of mes: one random sample per week2, replicated 1000 times
# doc_week2_noise <- matrix(rnorm(nrep*nrow_week2, mean = 0, sd = doc_u), nrow = nrep, ncol = nrow_week2) 
# doc_mat_week2 <- doc_week2_random * (1 + doc_week2_noise) # final value of mes, with noise
# doc_mean <- colMeans(doc_mat_week2)

doc_cv_week2 <- 3.2*doc_random_week2^(-0.2)
rnorm_week2 <- matrix(rnorm(nrep*nrow_week2, mean = 0, sd = 1), nrow=nrep, ncol = nrow_week2)
doc_noise_week2 <- doc_cv_week2*rnorm_week2
doc_mat_week2 <- doc_random_week2 * (1 + doc_noise_week2/100) # final value of doc, with noise in percent

# matrix for q
q_week2 <- avenelles_group_week2 %>% select(c("week2", "q_L.s")) %>% summarize_all(list("q_mean" = mean, "q_sd" = sd)) %>% ungroup() # mean of Q for each week2

q_week2_mean <-  matrix(q_week2$q_mean, nrow = nrep, ncol = nrow_week2, byrow = T)
q_noise <- matrix(rnorm(nrep*nrow_week2, mean = 0, sd = q_u), nrow = nrep, ncol = nrow_week2) # creates a noise in percent (proportion), between 0 and 10%
q_mat_week2 <- q_week2_mean * (1 + q_noise) # final MC of q, with noise. SD NOT INCLUDED: will not always be available

# compute flux
flux_ton_mat_week2 <- doc_mat_week2*1e-9*q_mat_week2*60*60*24*14 #Doc in mg/L converted to ton; q_mat converted from m3/s to L/s. Period : nb of seconds in 1 week2. 

# Get index for columns by year
index_years <- lapply(complete_years, function(y){which(avenelles_doc_week2$year == y)}) # list of indices corresponding to each year

# annual flux
annual_flux_ton.y_week2 <- lapply(index_years, function(idx){apply(flux_ton_mat_week2[,idx], 1, sum, na.rm = T)}) %>% do.call("cbind", .) # sum of fluxes per year, for each iteration of the bootstrap. 
annual_flux_week2_pi <- apply(annual_flux_ton.y_week2, 2, quantile, probs = c(0.025, 0.5, 0.975), na.rm = T) # confidence interval for annual fluxes, per year. 3 lignes, 19 columns
annual_flux_week2_mean <- colMeans(annual_flux_ton.y_week2, na.rm = T) # mean annual flux per year. 1 vector
annual_flux_week2_sd <- apply(annual_flux_ton.y_week2, 2, sd, na.rm = T) # standard deviation of annual flux per year. Is just an estimate of goodness of mean, not as good as than the confidence interval. 
 
annual_flux_week2_df <- data.frame(year = complete_years, 
                        annual_flux_mean = annual_flux_week2_mean, 
                        annual_flux_variability = annual_flux_week2_sd, 
                        annual_flux_pi_lower = annual_flux_week2_pi[1,], 
                        annual_flux_pi_upper = annual_flux_week2_pi[3,])

interannual_flux_ton.y_week2 <- rowMeans(annual_flux_ton.y_week2, na.rm = T) # mean interannual flux per iteration of the bootstrap
interannual_flux_pi_week2 <- quantile(interannual_flux_ton.y_week2, probs = c(0.025, 0.5, 0.975), na.rm = T) # prediction interval
interannual_flux_mean_week2 <- mean(interannual_flux_ton.y_week2, na.rm = T) # mean interannual flux
interannual_flux_variability_week2 <- sd(annual_flux_week2_mean, na.rm = T) # standard deviation of interannual flux per year

interannual_flux_week2_df <- data.frame(year = "interannual", annual_flux_mean = interannual_flux_mean_week2, 
                                  annual_flux_variability = interannual_flux_variability_week2,
                        annual_flux_pi_lower = interannual_flux_pi_week2[1], 
                        annual_flux_pi_upper = interannual_flux_pi_week2[3])

total_flux_week2_df <- rbind(annual_flux_week2_df, interannual_flux_week2_df)
total_flux_week2_df$group <- c(rep("annual", nyears), "interannual")

ggplot()+
  geom_col(data = total_flux_week2_df, aes(x=year, y = annual_flux_mean, fill = group))+
    geom_errorbar(data = total_flux_week2_df, aes(x = year, ymin = annual_flux_pi_lower, ymax = annual_flux_pi_upper, col = "prediction interval"), width = 0.3, size = 0.8)+
  geom_errorbar(data = filter(total_flux_week2_df, year == "interannual"), aes(x = year, ymin = annual_flux_mean - annual_flux_variability, ymax = annual_flux_mean + annual_flux_variability, col = "interannual variability"), width = 0.2, size = 0.8, linetype = 2)+
  scale_fill_manual(values = c("annual" = "lightblue", "interannual" = "indianred"))+
  scale_color_manual(values = c("prediction interval" = "darkblue", "interannual variability" = "darkred"), name = "")+
   labs(x = "Year", y = "Flux, from bi-dayly mean values (ton/year)", fill = "")+
  theme_minimal(base_size = 15)+
  theme(axis.text.x = element_text(angle = 45, hjust = 1), legend.position = "bottom")
```
## Month

```{r avenelles-month, cache.lazy = F}
# prepare df
avenelles_group_month <- avenelles_time %>% mutate(week = week(DateHeure), month =  floor(as.numeric(week - min(week)) / 2), year = year(DateHeure)) %>% group_by(month,year) # group isere_time by month
nrow_month <- n_groups(avenelles_group_month)


# creates matrix for DOC
avenelles_doc_month <- avenelles_group_month %>% select(c("month", "doc_mg.L")) %>% summarize("list_doc" = list(doc_mg.L)) %>% ungroup() # creates a list of mes for each month
doc_random_month <- replicate(nrep, sapply(avenelles_doc_month$list_doc, function(x) sample(x,1)))%>% t() # matrix of mes: one random sample per month, replicated 1000 times

# doc_month_noise <- matrix(rnorm(nrep*nrow_month, mean = 0, sd = doc_u), nrow = nrep, ncol = nrow_month) 
# doc_mat_month <- doc_month_random * (1 + doc_month_noise) # final value of mes, with noise
# doc_mean <- colMeans(doc_mat_month)

doc_cv_month <- 3.2*doc_random_month^(-0.2)
rnorm_month <- matrix(rnorm(nrep*nrow_month, mean = 0, sd = 1), nrow=nrep, ncol = nrow_month)
doc_noise_month <- doc_cv_month*rnorm_month
doc_mat_month <- doc_random_month * (1 + doc_noise_month/100) # final value of doc, with noise in percent



# matrix for q
q_month <- avenelles_group_month %>% select(c("month", "q_L.s")) %>% summarize_all(list("q_mean" = mean, "q_sd" = sd)) %>% ungroup() # mean of Q for each month

q_month_mean <-  matrix(q_month$q_mean, nrow = nrep, ncol = nrow_month, byrow = T)
q_noise <- matrix(rnorm(nrep*nrow_month, mean = 0, sd = q_u), nrow = nrep, ncol = nrow_month) # creates a noise in percent (proportion), between 0 and 10%
q_mat_month <- q_month_mean * (1 + q_noise) # final MC of q, with noise. SD NOT INCLUDED: will not always be available

# compute flux
flux_ton_mat_month <- doc_mat_month*1e-9*q_mat_month*60*60*24*14 #Doc in mg/L converted to ton; q_mat converted from m3/s to L/s. Period : nb of seconds in 1 month. 

# Get index for columns by year
index_years <- lapply(complete_years, function(y){which(avenelles_doc_month$year == y)}) # list of indices corresponding to each year

# annual flux
annual_flux_ton.y_month <- lapply(index_years, function(idx){apply(flux_ton_mat_month[,idx], 1, sum, na.rm = T)}) %>% do.call("cbind", .) # sum of fluxes per year, for each iteration of the bootstrap. 
annual_flux_month_pi <- apply(annual_flux_ton.y_month, 2, quantile, probs = c(0.025, 0.5, 0.975), na.rm = T) # confidence interval for annual fluxes, per year. 3 lignes, 19 columns
annual_flux_month_mean <- colMeans(annual_flux_ton.y_month, na.rm = T) # mean annual flux per year. 1 vector
annual_flux_month_sd <- apply(annual_flux_ton.y_month, 2, sd, na.rm = T) # standard deviation of annual flux per year. Is just an estimate of goodness of mean, not as good as than the confidence interval. 
 
annual_flux_month_df <- data.frame(year = complete_years, 
                        annual_flux_mean = annual_flux_month_mean, 
                        annual_flux_variability = annual_flux_month_sd, 
                        annual_flux_pi_lower = annual_flux_month_pi[1,], 
                        annual_flux_pi_upper = annual_flux_month_pi[3,])

interannual_flux_ton.y_month <- rowMeans(annual_flux_ton.y_month, na.rm = T) # mean interannual flux per iteration of the bootstrap
interannual_flux_pi_month <- quantile(interannual_flux_ton.y_month, probs = c(0.025, 0.5, 0.975), na.rm = T) # prediction interval
interannual_flux_mean_month <- mean(interannual_flux_ton.y_month, na.rm = T) # mean interannual flux
interannual_flux_variability_month <- sd(annual_flux_month_mean, na.rm = T) # standard deviation of interannual flux per year

interannual_flux_month_df <- data.frame(year = "interannual", annual_flux_mean = interannual_flux_mean_month, 
                                  annual_flux_variability = interannual_flux_variability_month,
                        annual_flux_pi_lower = interannual_flux_pi_month[1], 
                        annual_flux_pi_upper = interannual_flux_pi_month[3])

total_flux_month_df <- rbind(annual_flux_month_df, interannual_flux_month_df)
total_flux_month_df$group <- c(rep("annual", nyears), "interannual")

ggplot()+
  geom_col(data = total_flux_month_df, aes(x=year, y = annual_flux_mean, fill = group))+
    geom_errorbar(data = total_flux_month_df, aes(x = year, ymin = annual_flux_pi_lower, ymax = annual_flux_pi_upper, col = "prediction interval"), width = 0.3, size = 0.8)+
  geom_errorbar(data = filter(total_flux_month_df, year == "interannual"), aes(x = year, ymin = annual_flux_mean - annual_flux_variability, ymax = annual_flux_mean + annual_flux_variability, col = "interannual variability"), width = 0.2, size = 0.8, linetype = 2)+
  scale_fill_manual(values = c("annual" = "lightblue", "interannual" = "indianred"))+
  scale_color_manual(values = c("prediction interval" = "darkblue", "interannual variability" = "darkred"), name = "")+
   labs(x = "Year", y = "Flux, from bi-dayly mean values (ton/year)", fill = "")+
  theme_minimal(base_size = 15)+
  theme(axis.text.x = element_text(angle = 45, hjust = 1), legend.position = "bottom")
```

## Compare fluxes

```{r interannual-error-in-percent, cache = F}
# relative error by Monte-Carlo world
error_day2 <- (interannual_flux_ton.y_day2 - interannual_flux_ton.y)/interannual_flux_ton.y * 100
error_day2_pi <- quantile(error_day2, probs = c(0.025, 0.5, 0.975), na.rm = T) # confidence interval for annual fluxes, per year. 3 lignes, 19 columns
error_day2_mean <- mean(error_day2)

error_day4 <- (interannual_flux_ton.y_day4 - interannual_flux_ton.y)/interannual_flux_ton.y * 100
error_day4_pi <- quantile(error_day4, probs = c(0.025, 0.5, 0.975), na.rm = T) # confidence interval for annual fluxes, per year. 3 lignes, 19 columns
error_day4_mean <- mean(error_day4)

error_week <- (interannual_flux_ton.y_week - interannual_flux_ton.y)/interannual_flux_ton.y * 100
error_week_pi <- quantile(error_week, probs = c(0.025, 0.5, 0.975), na.rm = T) # confidence interval for annual fluxes, per year. 3 lignes, 19 columns
error_week_mean <- mean(error_week)

error_week2 <- (interannual_flux_ton.y_week2 - interannual_flux_ton.y)/interannual_flux_ton.y * 100
error_week2_pi <- quantile(error_week2, probs = c(0.025, 0.5, 0.975), na.rm = T) # confidence interval for annual fluxes, per year. 3 lignes, 19 columns
error_week2_mean <- mean(error_week2)

error_month <- (interannual_flux_ton.y_month - interannual_flux_ton.y)/interannual_flux_ton.y * 100
error_month_pi <- quantile(error_month, probs = c(0.025, 0.5, 0.975), na.rm = T) # confidence interval for annual fluxes, per year. 3 lignes, 19 columns
error_month_mean <- mean(error_month)

error <- data.frame(time_step = factor(c("2days","4days","week","2weeks","month"), levels = c("day","2days","4days","week","2weeks","month")),
                    error = c(error_day2_mean, error_day4_mean, error_week_mean, error_week2_mean, error_month_mean),
                    pi_upr = c(error_day2_pi[3], error_day4_pi[3], error_week_pi[3], error_week2_pi[3], error_month_pi[3]),
                    pi_lwr = c(error_day2_pi[1], error_day4_pi[1], error_week_pi[1], error_week2_pi[1], error_month_pi[1])) 

ggplot(data=error, aes(x = time_step))+
  geom_point(aes(y = error))+
  geom_errorbar(aes(ymin=pi_lwr, ymax=pi_upr))+
  theme_minimal(base_size = 15)

error %>% knitr::kable(digits = 2, row.names = F) %>% kableExtra::kable_styling()
```
Bond d'erreur entre 2 days et 4 days: peut-être parce que dans le prélèvement initial, on est plus proche de tous les 2 jours que de tous les jours ? 


# Missing data 2015

```{r common-data-weighted-2015}
avenelles_2015 <- avenelles_flux %>% filter(year == 2015)

n_ave_2015 <- nrow(avenelles_2015)

mes_u <- 0.05
q_u <- 0.05

set.seed(503)

unique_years <- unique(avenelles_2015$year)
nyears <- length(unique_years)

n_rep <- 100

index_2015 <- which(avenelles_flux$year == 2015) # list of indices corresponding to each year
flux_ton.s_mat_2015 <- flux_ton.s_mat[,index_2015]
flux_ton_mat_2015 <- flux_ton_mat[,index_2015]
q_mat_2015  <- q_mat[,index_2015]
mean_q_2015 <- apply(q_mat, 1, mean, na.rm = T)

# Completude?
cat("nb obs 2015:", dim(flux_ton_mat_2015)[2])
cat("Period in s in Avenelles = ", sum(avenelles_2015$period), "; nb of s in 1 year = ", 365*24*60*60)

```

## 10% missing

```{r percent10-2015}

waf_10_2015 <- list()

for(i in 1:n_rep){
  block_size <- floor(n_ave_2015*0.10)
  start_idx <- sample(1:n_ave_2015, 1) # choisit aléatoirement une colonne où faire commencer le bloc manquant
  # idx_block <- start_idx:(start_idx + block_size - 1) # idx des colonnes du bloc
  # 
  # Calculer les indices du bloc (avec retour au début si nécessaire)
  if(start_idx + block_size - 1 <= n_ave_2015){
    # Le bloc ne dépasse pas : bloc simple
    idx_block <- start_idx:(start_idx + block_size - 1)
  } else {
    # Le bloc dépasse : il se sépare en 2 parties
    # Partie 1 : de start_idx à la fin
    part1 <- start_idx:n_ave_2015
    # Partie 2 : du début jusqu'à compléter block_size
    remaining <- block_size - length(part1)
    part2 <- 1:remaining
    # Combiner les deux parties
    idx_block <- c(part1, part2)
  }
  
  ftsm_10_2015 <- flux_ton.s_mat_2015[,-idx_block]
  q_10_2015 <- q_mat_2015[, -idx_block]

  # Annual flux
  sum_instant_flux_ton.y_10 <- apply(ftsm_10_2015, 1, sum, na.rm = T)  # sum of fluxes per year, for each MC world computed previously. Result is a matrix with 1000 rows 
  sum_instant_q_10 <- apply(q_10_2015, 1, sum, na.rm = T) # same for Q
  mean_instant_q_10 <- apply(q_10_2015, 1, mean, na.rm = T) # same for mean Q: 1000 lines
  
  weighted_annual_flux_ton.y_10 <- sum_instant_flux_ton.y_10 / sum_instant_q_10 * mean_q_2015 * 60 * 60 * 24 *365 # 1000 lines and 3 columns of weignted annual fluxes
  
  waf_10_2015[[i]] <- weighted_annual_flux_ton.y_10 # stored in the big list
}

waf_10_mcmean <- lapply(waf_10_2015, mean) %>% unlist()# moyenne des simulations montecarlo pour chaque resampling 
waf_10_upr_2015 <- lapply(waf_10_2015, quantile, 0.975) %>% unlist()
waf_10_lwr_2015 <- lapply(waf_10_2015, quantile, 0.025) %>% unlist()

```


## 20% missing

```{r percent20-2015}


waf_20_2015 <- list()

for(i in 1:n_rep){
   block_size <- floor(n_ave_2015*0.20)
   start_idx <- sample(1:n_ave_2015, 1) # choisit aléatoirement une colonne où faire commencer le bloc manquant
  # idx_block <- start_idx:(start_idx + block_size - 1) # idx des colonnes du bloc
  # 
    # Calculer les indices du bloc (avec retour au début si nécessaire)
  if(start_idx + block_size - 1 <= n_ave_2015){
    # Le bloc ne dépasse pas : bloc simple
    idx_block <- start_idx:(start_idx + block_size - 1)
  } else {
    # Le bloc dépasse : il se sépare en 2 parties
    # Partie 1 : de start_idx à la fin
    part1 <- start_idx:n_ave_2015
    # Partie 2 : du début jusqu'à compléter block_size
    remaining <- block_size - length(part1)
    part2 <- 1:remaining
    # Combiner les deux parties
    idx_block <- c(part1, part2)
  }
  
  ftsm_20_2015 <- flux_ton.s_mat_2015[,-idx_block]
  q_20_2015 <- q_mat_2015[, -idx_block]

  # Annual flux
  sum_instant_flux_ton.y_20 <- apply(ftsm_20_2015, 1, sum, na.rm = T)  # sum of fluxes per year, for each MC world computed previously. Result is a matrix with 1000 rows and 3 columns  (1 per year)
  sum_instant_q_20 <- apply(q_20_2015, 1, sum, na.rm = T) # same for Q
  mean_instant_q_20 <- apply(q_20_2015, 1, mean, na.rm = T) # same for mean Q: 1000 lines, 3 columns
  
  weighted_annual_flux_ton.y_20 <- sum_instant_flux_ton.y_20 / sum_instant_q_20 * mean_q_2015 * 60 * 60 * 24 *365 # 1000 lines and 3 columns of weignted annual fluxes
  
  waf_20_2015[[i]] <- weighted_annual_flux_ton.y_20 # stored in the big list
}

waf_20_mcmean <- lapply(waf_20_2015, mean) %>% unlist()# moyenne des simulations montecarlo pour chaque resampling 
waf_20_upr_2015 <- lapply(waf_20_2015, quantile, 0.975) %>% unlist()
waf_20_lwr_2015 <- lapply(waf_20_2015, quantile, 0.025) %>% unlist()


```

## 30% missing

```{r percent30-2015}


waf_30_2015 <- list()

for(i in 1:n_rep){
 block_size <- floor(n_ave_2015*0.30)
 start_idx <- sample(1:n_ave_2015, 1) # choisit aléatoirement une colonne où faire commencer le bloc manquant
  # idx_block <- start_idx:(start_idx + block_size - 1) # idx des colonnes du bloc
  # 
    # Calculer les indices du bloc (avec retour au début si nécessaire)
  if(start_idx + block_size - 1 <= n_ave_2015){
    # Le bloc ne dépasse pas : bloc simple
    idx_block <- start_idx:(start_idx + block_size - 1)
  } else {
    # Le bloc dépasse : il se sépare en 2 parties
    # Partie 1 : de start_idx à la fin
    part1 <- start_idx:n_ave_2015
    # Partie 2 : du début jusqu'à compléter block_size
    remaining <- block_size - length(part1)
    part2 <- 1:remaining
    # Combiner les deux parties
    idx_block <- c(part1, part2)
  }
  
  ftsm_30_2015 <- flux_ton.s_mat_2015[,-idx_block]
  q_30_2015 <- q_mat_2015[, -idx_block]

  # Annual flux
  sum_instant_flux_ton.y_30 <- apply(ftsm_30_2015, 1, sum, na.rm = T)  # sum of fluxes per year, for each MC world computed previously. Result is a matrix with 1000 rows and 3 columns  (1 per year)
  sum_instant_q_30 <- apply(q_30_2015, 1, sum, na.rm = T) # same for Q
  mean_instant_q_30 <- apply(q_30_2015, 1, mean, na.rm = T) # same for mean Q: 1000 lines, 3 columns
  
  weighted_annual_flux_ton.y_30 <- sum_instant_flux_ton.y_30 / sum_instant_q_30 * mean_q_2015 * 60 * 60 * 24 *365 # 1000 lines and 3 columns of weignted annual fluxes
  
  waf_30_2015[[i]] <- weighted_annual_flux_ton.y_30 # stored in the big list
}

waf_30_mcmean <- lapply(waf_30_2015, mean) %>% unlist()# moyenne des simulations montecarlo pour chaque resampling 
waf_30_upr_2015 <- lapply(waf_30_2015, quantile, 0.975) %>% unlist()
waf_30_lwr_2015 <- lapply(waf_30_2015, quantile, 0.025) %>% unlist()


```

## 40% missing

```{r percent40-2015}


waf_40_2015 <- list()

for(i in 1:n_rep){
 block_size <- floor(n_ave_2015*0.40)
 start_idx <- sample(1:n_ave_2015, 1) # choisit aléatoirement une colonne où faire commencer le bloc manquant
  # idx_block <- start_idx:(start_idx + block_size - 1) # idx des colonnes du bloc
 
   # Calculer les indices du bloc (avec retour au début si nécessaire)
  if(start_idx + block_size - 1 <= n_ave_2015){
    # Le bloc ne dépasse pas : bloc simple
    idx_block <- start_idx:(start_idx + block_size - 1)
  } else {
    # Le bloc dépasse : il se sépare en 2 parties
    # Partie 1 : de start_idx à la fin
    part1 <- start_idx:n_ave_2015
    # Partie 2 : du début jusqu'à compléter block_size
    remaining <- block_size - length(part1)
    part2 <- 1:remaining
    # Combiner les deux parties
    idx_block <- c(part1, part2)
  }
  
  ftsm_40_2015 <- flux_ton.s_mat_2015[,-idx_block]
  q_40_2015 <- q_mat_2015[, -idx_block]

  # Annual flux
  sum_instant_flux_ton.y_40 <- apply(ftsm_40_2015, 1, sum, na.rm = T)  # sum of fluxes per year, for each MC world computed previously. Result is a matrix with 1000 rows and 3 columns  (1 per year)
  sum_instant_q_40 <- apply(q_40_2015, 1, sum, na.rm = T) # same for Q
  mean_instant_q_40 <- apply(q_40_2015, 1, mean, na.rm = T) # same for mean Q: 1000 lines, 3 columns
  
  weighted_annual_flux_ton.y_40 <- sum_instant_flux_ton.y_40 / sum_instant_q_40 * mean_q_2015 * 60 * 60 * 24 *365 # 1000 lines and 3 columns of weignted annual fluxes
  
  waf_40_2015[[i]] <- weighted_annual_flux_ton.y_40 # stored in the big list
}

waf_40_mcmean <- lapply(waf_40_2015, mean) %>% unlist() # moyenne des simulations montecarlo pour chaque resampling 
waf_40_upr_2015 <- lapply(waf_40_2015, quantile, 0.975) %>% unlist()
waf_40_lwr_2015 <- lapply(waf_40_2015, quantile, 0.025) %>% unlist()


```


## 50% missing

```{r percent50-2015}


waf_50_2015 <- list()

for(i in 1:n_rep){
 block_size <- floor(n_ave_2015*0.50)
 start_idx <- sample(1:n_ave_2015, 1) # choisit aléatoirement une colonne où faire commencer le bloc manquant
  # idx_block <- start_idx:(start_idx + block_size - 1) # idx des colonnes du bloc
 
   # Calculer les indices du bloc (avec retour au début si nécessaire)
  if(start_idx + block_size - 1 <= n_ave_2015){
    # Le bloc ne dépasse pas : bloc simple
    idx_block <- start_idx:(start_idx + block_size - 1)
  } else {
    # Le bloc dépasse : il se sépare en 2 parties
    # Partie 1 : de start_idx à la fin
    part1 <- start_idx:n_ave_2015
    # Partie 2 : du début jusqu'à compléter block_size
    remaining <- block_size - length(part1)
    part2 <- 1:remaining
    # Combiner les deux parties
    idx_block <- c(part1, part2)
  }
  
  ftsm_50_2015 <- flux_ton.s_mat_2015[,-idx_block]
  q_50_2015 <- q_mat_2015[, -idx_block]
  
  # Annual flux
  sum_instant_flux_ton.y_50 <- apply(ftsm_50_2015, 1, sum, na.rm = T)  # sum of fluxes per year, for each MC world computed previously. Result is a matrix with 1000 rows and 3 columns  (1 per year)
  sum_instant_q_50 <- apply(q_50_2015, 1, sum, na.rm = T) # same for Q
  mean_instant_q_50 <- apply(q_50_2015, 1, mean, na.rm = T) # same for mean Q: 1000 lines, 3 columns
  
  weighted_annual_flux_ton.y_50 <- sum_instant_flux_ton.y_50 / sum_instant_q_50 * mean_q_2015 * 60 * 60 * 24 *365 # 1000 lines and 3 columns of weignted annual fluxes
  
  waf_50_2015[[i]] <- weighted_annual_flux_ton.y_50 # stored in the big list
}

waf_50_mcmean <- lapply(waf_50_2015, mean) %>% unlist() # moyenne des simulations montecarlo pour chaque resampling 
waf_50_upr_2015 <- lapply(waf_50_2015, quantile, 0.975) %>% unlist()
waf_50_lwr_2015 <- lapply(waf_50_2015, quantile, 0.025) %>% unlist()


```

## 60% missing

from here we select a block instead of removing it

```{r percent60-2015}


waf_60_2015 <- list()

for(i in 1:n_rep){
  block_size <- floor(n_ave_2015*0.60)
   start_idx <- sample(1:n_ave_2015, 1) # choisit aléatoirement une colonne où faire commencer le bloc choisi
  # idx_block <- start_idx:(start_idx + block_size - 1) # idx des colonnes du bloc
  
    # Calculer les indices du bloc (avec retour au début si nécessaire)
  if(start_idx + block_size - 1 <= n_ave_2015){
    # Le bloc ne dépasse pas : bloc simple
    idx_block <- start_idx:(start_idx + block_size - 1)
  } else {
    # Le bloc dépasse : il se sépare en 2 parties
    # Partie 1 : de start_idx à la fin
    part1 <- start_idx:n_ave_2015
    # Partie 2 : du début jusqu'à compléter block_size
    remaining <- block_size - length(part1)
    part2 <- 1:remaining
    # Combiner les deux parties
    idx_block <- c(part1, part2)
  }
  
  ftsm_60_2015 <- flux_ton.s_mat_2015[,-idx_block]
  q_60_2015 <- q_mat_2015[, -idx_block]
  
  # Annual flux
  sum_instant_flux_ton.y_60 <- apply(ftsm_60_2015, 1, sum, na.rm = T)  # sum of fluxes per year, for each MC world computed previously. Result is a matrix with 1000 rows and 3 columns  (1 per year)
  sum_instant_q_60 <- apply(q_60_2015, 1, sum, na.rm = T) # same for Q
  mean_instant_q_60 <- apply(q_60_2015, 1, mean, na.rm = T) # same for mean Q: 1000 lines, 3 columns
  
  weighted_annual_flux_ton.y_60 <- sum_instant_flux_ton.y_60 / sum_instant_q_60 * mean_q_2015 * 60 * 60 * 24 *365 # 1000 lines and 3 columns of weignted annual fluxes
  
  waf_60_2015[[i]] <- weighted_annual_flux_ton.y_60 # stored in the big list
}

waf_60_mcmean <- lapply(waf_60_2015, mean) %>% unlist() # moyenne des simulations montecarlo pour chaque resampling 
waf_60_upr_2015 <- lapply(waf_60_2015, quantile, 0.975) %>% unlist()
waf_60_lwr_2015 <- lapply(waf_60_2015, quantile, 0.025) %>% unlist()


```

## 70% missing

```{r percent70-2015}


waf_70_2015 <- list()

for(i in 1:n_rep){
  block_size <- floor(n_ave_2015*0.70)
   start_idx <- sample(1:n_ave_2015, 1) # choisit aléatoirement une colonne où faire commencer le bloc choisi
  # idx_block <- start_idx:(start_idx + block_size - 1) # idx des colonnes du bloc
  # 
    # Calculer les indices du bloc (avec retour au début si nécessaire)
  if(start_idx + block_size - 1 <= n_ave_2015){
    # Le bloc ne dépasse pas : bloc simple
    idx_block <- start_idx:(start_idx + block_size - 1)
  } else {
    # Le bloc dépasse : il se sépare en 2 parties
    # Partie 1 : de start_idx à la fin
    part1 <- start_idx:n_ave_2015
    # Partie 2 : du début jusqu'à compléter block_size
    remaining <- block_size - length(part1)
    part2 <- 1:remaining
    # Combiner les deux parties
    idx_block <- c(part1, part2)
  }
  
  ftsm_70_2015 <- flux_ton.s_mat_2015[,-idx_block]
  q_70_2015 <- q_mat_2015[, -idx_block]
  
  # Annual flux
  sum_instant_flux_ton.y_70 <- apply(ftsm_70_2015, 1, sum, na.rm = T)  # sum of fluxes per year, for each MC world computed previously. Result is a matrix with 1000 rows and 3 columns  (1 per year)
  sum_instant_q_70 <- apply(q_70_2015, 1, sum, na.rm = T) # same for Q
  mean_instant_q_70 <- apply(q_70_2015, 1, mean, na.rm = T) # same for mean Q: 1000 lines, 3 columns
  
  weighted_annual_flux_ton.y_70 <- sum_instant_flux_ton.y_70 / sum_instant_q_70 * mean_q_2015 * 60 * 60 * 24 *365 # 1000 lines and 3 columns of weignted annual fluxes
  
  waf_70_2015[[i]] <- weighted_annual_flux_ton.y_70 # stored in the big list
}

waf_70_mcmean <- lapply(waf_70_2015, mean) %>% unlist()# moyenne des simulations montecarlo pour chaque resampling 
waf_70_upr_2015 <- lapply(waf_70_2015, quantile, 0.975) %>% unlist()
waf_70_lwr_2015 <- lapply(waf_70_2015, quantile, 0.025) %>% unlist()


```

## 80% missing

```{r percent80-2015}


waf_80_2015 <- list()

for(i in 1:n_rep){
 block_size <- floor(n_ave_2015*0.80)
   start_idx <- sample(1:n_ave_2015, 1) # choisit aléatoirement une colonne où faire commencer le bloc choisi
  # idx_block <- start_idx:(start_idx + block_size - 1) # idx des colonnes du bloc
 
   # Calculer les indices du bloc (avec retour au début si nécessaire)
  if(start_idx + block_size - 1 <= n_ave_2015){
    # Le bloc ne dépasse pas : bloc simple
    idx_block <- start_idx:(start_idx + block_size - 1)
  } else {
    # Le bloc dépasse : il se sépare en 2 parties
    # Partie 1 : de start_idx à la fin
    part1 <- start_idx:n_ave_2015
    # Partie 2 : du début jusqu'à compléter block_size
    remaining <- block_size - length(part1)
    part2 <- 1:remaining
    # Combiner les deux parties
    idx_block <- c(part1, part2)
  }
  # 
  ftsm_80_2015 <- flux_ton.s_mat_2015[,-idx_block]
  q_80_2015 <- q_mat_2015[, -idx_block]

  # Annual flux
  sum_instant_flux_ton.y_80 <- apply(ftsm_80_2015, 1, sum, na.rm = T)  # sum of fluxes per year, for each MC world computed previously. Result is a matrix with 1000 rows and 3 columns  (1 per year)
  sum_instant_q_80 <- apply(q_80_2015, 1, sum, na.rm = T) # same for Q
  mean_instant_q_80 <- apply(q_80_2015, 1, mean, na.rm = T) # same for mean Q: 1000 lines, 3 columns
  
  weighted_annual_flux_ton.y_80 <- sum_instant_flux_ton.y_80 / sum_instant_q_80 * mean_q_2015 * 60 * 60 * 24 *365 # 1000 lines and 3 columns of weignted annual fluxes
  
  waf_80_2015[[i]] <- weighted_annual_flux_ton.y_80 # stored in the big list
}

waf_80_mcmean <- lapply(waf_80_2015, mean) %>% unlist() # moyenne des simulations montecarlo pour chaque resampling 
waf_80_upr_2015 <- lapply(waf_80_2015, quantile, 0.975) %>% unlist()
waf_80_lwr_2015 <- lapply(waf_80_2015, quantile, 0.025) %>% unlist()


```

## 90% missing

```{r percent90-2015}


waf_90_2015 <- list()

for(i in 1:n_rep){
 block_size <- floor(n_ave_2015*0.90)
 start_idx <- sample(1:n_ave_2015, 1) # choisit aléatoirement une colonne où faire commencer le bloc choisi
  # idx_block <- start_idx:(start_idx + block_size - 1) # idx des colonnes du bloc
 
   # Calculer les indices du bloc (avec retour au début si nécessaire)
  if(start_idx + block_size - 1 <= n_ave_2015){
    # Le bloc ne dépasse pas : bloc simple
    idx_block <- start_idx:(start_idx + block_size - 1)
  } else {
    # Le bloc dépasse : il se sépare en 2 parties
    # Partie 1 : de start_idx à la fin
    part1 <- start_idx:n_ave_2015
    # Partie 2 : du début jusqu'à compléter block_size
    remaining <- block_size - length(part1)
    part2 <- 1:remaining
    # Combiner les deux parties
    idx_block <- c(part1, part2)
  }
  
  ftsm_90_2015 <- flux_ton.s_mat_2015[,-idx_block]
  q_90_2015 <- q_mat_2015[, -idx_block]

  # Annual flux
  sum_instant_flux_ton.y_90 <- apply(ftsm_90_2015, 1, sum, na.rm = T)  # sum of fluxes per year, for each MC world computed previously. Result is a matrix with 1000 rows and 3 columns  (1 per year)
  sum_instant_q_90 <- apply(q_90_2015, 1, sum, na.rm = T) # same for Q
  mean_instant_q_90 <- apply(q_90_2015, 1, mean, na.rm = T) # same for mean Q: 1000 lines, 3 columns
  
  weighted_annual_flux_ton.y_90 <- sum_instant_flux_ton.y_90 / sum_instant_q_90 * mean_q_2015 * 60 * 60 * 24 *365 # 1000 lines and 3 columns of weignted annual fluxes
  
  waf_90_2015[[i]] <- weighted_annual_flux_ton.y_90 # stored in the big list
}

waf_90_mcmean <- lapply(waf_90_2015, mean) %>% unlist() # moyenne des simulations montecarlo pour chaque resampling 
waf_90_upr_2015 <- lapply(waf_90_2015, quantile, 0.975) %>% unlist() # quantile superieur pour chaque resampling
waf_90_lwr_2015 <- lapply(waf_90_2015, quantile, 0.025) %>% unlist() # quantile inférieur pour chaque resampling


```

## No missing data

```{r percent100-2015}
# REF
flux_ref_2015 <- apply(flux_ton_mat_2015, 1, sum, na.rm = T)
flux_ref_2015_mean <- mean(flux_ref_2015)
flux_ref_2015_lwr <- quantile(flux_ref_2015, 0.025)
flux_ref_2015_upr <- quantile(flux_ref_2015, 0.975)

mean_q_2015 <- apply(q_mat, 1, mean, na.rm = T)
q_sum_2015<- apply(q_mat, 1, mean, na.rm = T)

# weighted
sum_instant_flux_ton.y_100 <- apply(flux_ton.s_mat_2015, 1, sum, na.rm = T)  # sum of fluxes per year, for each MC world computed previously. Result is a matrix with 1000 rows and 3 columns  (1 per year)
sum_instant_q_100 <- apply(q_mat_2015, 1, sum, na.rm = T) # same for Q

weighted_annual_flux_ton.y_100 <- sum_instant_flux_ton.y_100 / sum_instant_q_100 * mean_q_2015 * 60 * 60 * 24 *365 # 1000 lines and 3 columns of weignted annual fluxes

waf_100_mcmean <- mean(weighted_annual_flux_ton.y_100) # moyenne des simulations montecarlo 
waf_100_upr_2015 <- quantile(weighted_annual_flux_ton.y_100, 0.975) 
waf_100_lwr_2015 <- quantile(weighted_annual_flux_ton.y_100, 0.025) 


```

## Compare weighted fluxes

The "error" represents the range in which resampled interannual mean fall. Max value = 97.5% quantile of the 100 resampled means; minimum value = 2.5% quantile of the 100 resampled means; median value = median value of the 100 resampled means. 

```{r weighted-fluxes-compared-to-ref}

error_mwf2015 <- data.frame(percent_missing_data = c(10,20,30,40,50,60,70,80,90,0,"Ref"),
  mean_wflux = c(mean((waf_10_mcmean-flux_ref_2015)/flux_ref_2015*100), 
                 mean((waf_20_mcmean-flux_ref_2015)/flux_ref_2015*100), 
                 mean((waf_30_mcmean-flux_ref_2015)/flux_ref_2015*100), 
                 mean((waf_40_mcmean-flux_ref_2015)/flux_ref_2015*100), 
                 mean((waf_50_mcmean-flux_ref_2015)/flux_ref_2015*100), 
                 mean((waf_60_mcmean-flux_ref_2015)/flux_ref_2015*100),
                 mean((waf_70_mcmean-flux_ref_2015)/flux_ref_2015*100),
                 mean((waf_80_mcmean-flux_ref_2015)/flux_ref_2015*100), 
                 mean((waf_90_mcmean-flux_ref_2015)/flux_ref_2015*100), 
                 mean((waf_100_mcmean-flux_ref_2015)/flux_ref_2015*100), 
                 mean((flux_ref_2015-flux_ref_2015)/flux_ref_2015*100)),
  max_mean = c(max((waf_10_mcmean-flux_ref_2015)/flux_ref_2015*100),
               max((waf_20_mcmean-flux_ref_2015)/flux_ref_2015*100), 
               max((waf_30_mcmean-flux_ref_2015)/flux_ref_2015*100), 
               max((waf_40_mcmean-flux_ref_2015)/flux_ref_2015*100), 
               max((waf_50_mcmean-flux_ref_2015)/flux_ref_2015*100), 
               max((waf_60_mcmean-flux_ref_2015)/flux_ref_2015*100), 
               max((waf_70_mcmean-flux_ref_2015)/flux_ref_2015*100), 
               max((waf_80_mcmean-flux_ref_2015)/flux_ref_2015*100), 
               max((waf_90_mcmean-flux_ref_2015)/flux_ref_2015*100), 
               max((waf_100_mcmean-flux_ref_2015)/flux_ref_2015*100), 
               max((flux_ref_2015-flux_ref_2015)/flux_ref_2015*100)),
  min_mean = c(min((waf_10_mcmean-flux_ref_2015)/flux_ref_2015*100),
               min((waf_20_mcmean-flux_ref_2015)/flux_ref_2015*100), 
               min((waf_30_mcmean-flux_ref_2015)/flux_ref_2015*100), 
               min((waf_40_mcmean-flux_ref_2015)/flux_ref_2015*100), 
               min((waf_50_mcmean-flux_ref_2015)/flux_ref_2015*100), 
               min((waf_60_mcmean-flux_ref_2015)/flux_ref_2015*100), 
               min((waf_70_mcmean-flux_ref_2015)/flux_ref_2015*100), 
               min((waf_80_mcmean-flux_ref_2015)/flux_ref_2015*100), 
               min((waf_90_mcmean-flux_ref_2015)/flux_ref_2015*100), 
               min((waf_100_mcmean-flux_ref_2015)/flux_ref_2015*100), 
               min((flux_ref_2015-flux_ref_2015)/flux_ref_2015*100)))

error_mwf2015$percent_missing_data <- factor(error_mwf2015$percent_missing_data, levels = c("Ref",0,10,20,30,40,50,60,70,80,90))

ggplot(data = error_mwf2015, aes(x = percent_missing_data))+
  geom_point(aes(y = mean_wflux))+
  geom_errorbar(aes(ymin = min_mean, ymax = max_mean, col = "Prediction interval range"))+
  labs(title = "Mean, max and min error of resampled fluxes", y = "Error in %")+
  theme_minimal(base_size = 15)+
  theme(legend.position = "bottom", axis.text.x = element_text(angle = 45))

error_mwf2015 %>% knitr::kable(digits = 2, row.names = F) %>% kableExtra::kable_styling()

# boxplot
error_boxplot <- data.frame("M10" = (waf_10_mcmean-flux_ref_2015)/flux_ref_2015*100,
                            "M20" = (waf_20_mcmean-flux_ref_2015)/flux_ref_2015*100,
                            "M30" = (waf_30_mcmean-flux_ref_2015)/flux_ref_2015*100,
                            "M40" = (waf_40_mcmean-flux_ref_2015)/flux_ref_2015*100,
                            "M50" = (waf_50_mcmean-flux_ref_2015)/flux_ref_2015*100,
                            "M60" = (waf_60_mcmean-flux_ref_2015)/flux_ref_2015*100,
                            "M70" = (waf_70_mcmean-flux_ref_2015)/flux_ref_2015*100,
                            "M80" = (waf_80_mcmean-flux_ref_2015)/flux_ref_2015*100,
                            "M90" = (waf_90_mcmean-flux_ref_2015)/flux_ref_2015*100,
                            "M0" = (waf_100_mcmean-flux_ref_2015)/flux_ref_2015*100,
                            "Ref" = (flux_ref_2015-flux_ref_2015)/flux_ref_2015*100
                            )

error_boxplot_long <- tidyr::pivot_longer(data = error_boxplot, cols = 1:11, names_to = "percent_missing", values_to = "error_percent")
error_boxplot_long$percent_missing <- factor(error_boxplot_long$percent_missing, levels = c("Ref","M0","M10","M20","M30","M40","M50","M60","M70","M80","M90"))
error_boxplot_long$Site <- "Avenelles"
error_boxplot_long$OC <- "DOC"

write.csv(error_boxplot_long, "error_boxplot_long_avenelles.csv")

ggplot(error_boxplot_long)+
  geom_boxplot(aes(y=error_percent, x=percent_missing))+
  theme_minimal()
```




# Exit

```{r exit, cache = F}

knitr::knit_exit()
```





















# Archives

```{r most-complete-years-function}
compare_docfluxes <- function(data, frac){ #results = c(sum doc kg/year, sum doc kg/s, weighted doc kg/y, nb obs, relative difference between weighted and sum for the year)
    results <<- c()
    df <- sample_frac(data, frac)
    df$doc_flux_mg <- with(df, doc_mg.L * q_L.s * period) # Period is in second.
    results[1] <<- sum(df$doc_flux_mg, na.rm = T)*1e-6 #sum of all periods amounts. 
    results[2] <<- sum(with(df, doc_mg.L* q_L.s ), na.rm = T)*1e-6 #sum of daily amounts.
    results[3] <<- sum(with(df, doc_mg.L* q_L.s), na.rm = T)*1e-6 / with(df, sum(q_L.s, na.rm = T)) * with(df, mean(q_L.s, na.rm = T))  * 24 * 60 * 60 * 365
    results[4] <<- dim(df)[1]
    results[5] <<- results[3]/results[1]
    results[6] <<- sum(df$period, na.rm = T) / (24*60*60) # sum of period in days
    return(results)
    
}

compare_docfluxes_interpol <- function(data, frac){ #results = c(sum doc kg/year, sum doc kg/s, weighted doc kg/y, nb obs, relative difference between weighted and sum for the year)
    results <<- c()
    df <- sample_frac(data, frac)
    df$doc_flux_interpol <- with(df, doc_interpol * q_L.s * 24*60*60) # Period is in second.
    results[1] <<- sum(df$doc_flux_interpol, na.rm = T)*1e-6 #sum of all periods amounts. 
    results[2] <<- sum(with(df, doc_interpol* q_L.s ), na.rm = T)*1e-6 #sum of daily amounts.
    results[3] <<- sum(with(df, doc_interpol* q_L.s), na.rm = T)*1e-6 / with(df, sum(q_L.s, na.rm = T)) * with(df, mean(q_L.s, na.rm = T))  * 24 * 60 * 60 * 365
    results[4] <<- dim(df)[1]
    results[5] <<- results[3]/results[1]
    results[6] <<- sum(df$period, na.rm = T) / (24*60*60) # sum of period in days
    return(results)
    
}

```
## Year 2015

### Comparaison sum and weighted

```{r comparison-2015}
avenelles_2015 <- subset(avenelles, year == 2015)
avenelles_2015 <- avenelles_2015 %>% tidyr::complete(Date = seq(min(Date), max(Date), by = "1 day"))

doc_2015 <-  data.frame(compare_docfluxes(avenelles_2015, 1), 
                       compare_docfluxes(avenelles_2015, 0.1), 
                       compare_docfluxes(avenelles_2015, 0.25), 
                       compare_docfluxes(avenelles_2015, 0.5), 
                       compare_docfluxes(avenelles_2015, 0.75), 
                       compare_docfluxes(avenelles_2015, 0.9))

doc_2015 <- rbind(doc_2015, c(doc_2015[3,1]/doc_2015[1,1],
                              doc_2015[3,2]/doc_2015[1,1],
                              doc_2015[3,3]/doc_2015[1,1],
                              doc_2015[3,4]/doc_2015[1,1],
                              doc_2015[3,5]/doc_2015[1,1],
                              doc_2015[3,6]/doc_2015[1,1]))

rownames(doc_2015) <- c("Sum DOC kg/year", "Sum DOC kg/s", "Weighted DOC kg/year", "Number of observations", "W/S","sum of period","W/S1")

knitr::kable(doc_2015, digits = 2, col.names = c("Full year", "10%", "25%","50%","75%","90%"), 
             caption = "DOC fluxes 2015") %>% 
  kableExtra::kable_styling()

```

### complete year

Does not work because no discharge values in the extended dataset

```{r interpolation-na} 
avenelles_2015$doc_interpol <- imputeTS::na_interpolation(avenelles_2015$doc_mg.L, maxgap = 2*24*60*60) # débit toutes les 5 min, gap de 1 jour

doc_2015 <-  data.frame(compare_docfluxes_interpol(avenelles_2015, 1), 
                       compare_docfluxes_interpol(avenelles_2015, 0.1), 
                       compare_docfluxes_interpol(avenelles_2015, 0.25), 
                       compare_docfluxes_interpol(avenelles_2015, 0.5), 
                       compare_docfluxes_interpol(avenelles_2015, 0.75), 
                       compare_docfluxes_interpol(avenelles_2015, 0.9))

doc_2015 <- rbind(doc_2015, c(doc_2015[3,1]/doc_2015[1,1],
                              doc_2015[3,2]/doc_2015[1,1],
                              doc_2015[3,3]/doc_2015[1,1],
                              doc_2015[3,4]/doc_2015[1,1],
                              doc_2015[3,5]/doc_2015[1,1],
                              doc_2015[3,6]/doc_2015[1,1]))

rownames(doc_2015) <- c("Sum DOC kg/year", "Sum DOC kg/s", "Weighted DOC kg/year", "Number of observations", "W/S","sum of period","W/S1")

knitr::kable(doc_2015, digits = 2, col.names = c("Full year", "10%", "25%","50%","75%","90%"), 
             caption = "DOC fluxes 2015 interpol") %>% 
  kableExtra::kable_styling()


avenelles_2015$doc_flux_mg <- with(avenelles_2015, doc_mg.L * q_L.s * period)
avenelles_2015$doc_flux_interpol <- with(avenelles_2015, doc_interpol * q_L.s * period)

ggplot(avenelles_2015)+geom_point(aes(x = Date, y = cumsum(tidyr::replace_na(doc_flux_mg,0)), col = "measured"), size = 2)+
  geom_point(data = avenelles_2015, aes(x = Date, y = cumsum(tidyr::replace_na(doc_flux_interpol,0)), col = "interpol"), size = 1)+
  labs(y = "Somme cumulée du flux de DOC en mg", col = "Sampling frequency")+
  scale_x_date(labels = function(x) format(x, "%d-%b"), date_minor_breaks = "1 month")+
  theme_minimal(base_size = 15)+
  theme(legend.position = "bottom")

ggplot(avenelles_2015, aes(x=Date))+geom_point(aes(y=doc_mg.L, col = "measured"), size = 2)+
  geom_point(aes(y=doc_interpol, col = "predict"), size = 1)+
  theme_minimal(base_size = 15)

```



### Frequency

```{r frequency-2015}
avenelles_2015_day <- avenelles_2015 %>% group_by(Date) %>% summarize_all(mean, na.rm = T)
avenelles_2015_week <- avenelles_2015 %>% group_by(week) %>% summarize_all(mean, na.rm = T)
avenelles_2015_month <- avenelles_2015 %>% group_by(month) %>% summarize_all(mean, na.rm = T)

nb_days_doc_2015 <- avenelles_2015 %>% filter(!is.na(doc_mg.L)) %>% pull(Date) %>% unique() %>% length()


# DOC 

avenelles_2015_day$doc_flux_mg <- with(avenelles_2015_day, doc_mg.L * q_L.s * 24 * 3600) %>% tidyr::replace_na(0) # conversion q from m3/s to L/period. 
sum_doc_flux_avenelles_2015_day <- sum(avenelles_2015_day$doc_flux_mg, na.rm = T)*1e-6

avenelles_2015_week$doc_flux_mg <- with(avenelles_2015_week, doc_mg.L * q_L.s * 7 * 24 * 3600) %>% tidyr::replace_na(0) # conversion q from m3/s to L/period. Period is in hours.
sum_doc_flux_avenelles_2015_week <- sum(avenelles_2015_week$doc_flux_mg, na.rm = T)*1e-6

avenelles_2015_month$doc_flux_mg <- with(avenelles_2015_month, doc_mg.L * q_L.s * 30.42 * 24 * 3600) %>% tidyr::replace_na(0) # conversion q from m3/s to L/period. Period is in hours.
sum_doc_flux_avenelles_2015_month <- sum(avenelles_2015_month$doc_flux_mg, na.rm = T)*1e-6

ggplot()+geom_point(data = avenelles_2015_day, aes(x = Date, y = cumsum(doc_flux_mg), col = "per day"), size = 1)+
  geom_point(data = avenelles_2015_week, aes(x = Date, y = cumsum(doc_flux_mg), col = "per week"), size = 2)+
  geom_point(data = avenelles_2015_month, aes(x = Date, y = cumsum(doc_flux_mg), col = "per month"), size = 3)+
  labs(y = "Somme cumulée du flux de DOC en mg", col = "Sampling frequency")+
  scale_x_date(labels = function(x) format(x, "%d-%b"), date_minor_breaks = "1 month")+
  theme_minimal(base_size = 15)+
  theme(legend.position = "bottom")


knitr::kable(data.frame(
  "nb of days sampled doc" = nb_days_doc_2015,
  "doc flux" = c(sum_doc_flux_avenelles_2015_day, sum_doc_flux_avenelles_2015_week, sum_doc_flux_avenelles_2015_month),
  "% of daily doc value" = c(sum_doc_flux_avenelles_2015_day/sum_doc_flux_avenelles_2015_day*100, sum_doc_flux_avenelles_2015_week/sum_doc_flux_avenelles_2015_day*100, sum_doc_flux_avenelles_2015_month/sum_doc_flux_avenelles_2015_day*100),
  row.names = c("day","week","month")),
  digits = 2
) %>% kable_paper
```



## Year 2017

### Comparaison sum and weighted

```{r comparison-2017}
avenelles_2017 <- subset(avenelles, year == 2017)

doc_2017 <-  data.frame(compare_docfluxes(avenelles_2017, 1), 
                       compare_docfluxes(avenelles_2017, 0.1), 
                       compare_docfluxes(avenelles_2017, 0.25), 
                       compare_docfluxes(avenelles_2017, 0.5), 
                       compare_docfluxes(avenelles_2017, 0.75), 
                       compare_docfluxes(avenelles_2017, 0.9))

doc_2017 <- rbind(doc_2017, c(doc_2017[3,1]/doc_2017[1,1],
                              doc_2017[3,2]/doc_2017[1,1],
                              doc_2017[3,3]/doc_2017[1,1],
                              doc_2017[3,4]/doc_2017[1,1],
                              doc_2017[3,5]/doc_2017[1,1],
                              doc_2017[3,6]/doc_2017[1,1]))

rownames(doc_2017) <- c("Sum DOC kg/year", "Sum DOC kg/s", "Weighted DOC kg/year", "Number of observations", "W/S","sum of period","W/S1")

knitr::kable(doc_2017, digits = 2, col.names = c("Full year", "10%", "25%","50%","75%","90%"), 
             caption = "DOC fluxes 2017") %>% 
  kableExtra::kable_styling()

```

### Frequency

```{r frequency-2017}
avenelles_2017_day <- avenelles_2017 %>% group_by(Date) %>% summarize_all(mean, na.rm = T)
avenelles_2017_week <- avenelles_2017 %>% group_by(week) %>% summarize_all(mean, na.rm = T)
avenelles_2017_month <- avenelles_2017 %>% group_by(month) %>% summarize_all(mean, na.rm = T)

nb_days_doc_2017 <- avenelles_2017 %>% filter(!is.na(doc_mg.L)) %>% pull(Date) %>% unique() %>% length()


# DOC 

avenelles_2017_day$doc_flux_mg <- with(avenelles_2017_day, doc_mg.L * q_L.s * 24 * 3600) %>% tidyr::replace_na(0) # conversion q from m3/s to L/period. 
sum_doc_flux_avenelles_2017_day <- sum(avenelles_2017_day$doc_flux_mg, na.rm = T)*1e-6

avenelles_2017_week$doc_flux_mg <- with(avenelles_2017_week, doc_mg.L * q_L.s * 7 * 24 * 3600) %>% tidyr::replace_na(0) # conversion q from m3/s to L/period. Period is in hours.
sum_doc_flux_avenelles_2017_week <- sum(avenelles_2017_week$doc_flux_mg, na.rm = T)*1e-6

avenelles_2017_month$doc_flux_mg <- with(avenelles_2017_month, doc_mg.L * q_L.s * 30.42 * 24 * 3600) %>% tidyr::replace_na(0) # conversion q from m3/s to L/period. Period is in hours.
sum_doc_flux_avenelles_2017_month <- sum(avenelles_2017_month$doc_flux_mg, na.rm = T)*1e-6

ggplot()+geom_point(data = avenelles_2017_day, aes(x = Date, y = cumsum(doc_flux_mg), col = "per day"), size = 1)+
  geom_point(data = avenelles_2017_week, aes(x = Date, y = cumsum(doc_flux_mg), col = "per week"), size = 2)+
  geom_point(data = avenelles_2017_month, aes(x = Date, y = cumsum(doc_flux_mg), col = "per month"), size = 3)+
  labs(y = "Somme cumulée du flux de DOC en mg", col = "Sampling frequency")+
  scale_x_date(labels = function(x) format(x, "%d-%b"), date_minor_breaks = "1 month")+
  theme_minimal(base_size = 15)+
  theme(legend.position = "bottom")


knitr::kable(data.frame(
  "nb of days sampled doc" = nb_days_doc_2017,
  "doc flux" = c(sum_doc_flux_avenelles_2017_day, sum_doc_flux_avenelles_2017_week, sum_doc_flux_avenelles_2017_month),
  "% of daily doc value" = c(sum_doc_flux_avenelles_2017_day/sum_doc_flux_avenelles_2017_day*100, sum_doc_flux_avenelles_2017_week/sum_doc_flux_avenelles_2017_day*100, sum_doc_flux_avenelles_2017_month/sum_doc_flux_avenelles_2017_day*100),
  row.names = c("day","week","month")),
  digits = 2
) %>% kable_paper
```


## Missing data

```{r common-data-weighted}
avenelles_w <- avenelles_flux

n_ave <- nrow(avenelles_w)

mes_u <- 0.05
q_u <- 0.05

set.seed(503)

unique_years <- unique(avenelles_w$year)
nyears <- length(unique_years)

n_rep <- 100
```

## Random sampling in 2015 to compare sum of measurements

Sum of periods is 365 days, even though there are only 320 unique observations

```{r make-1000-datasets, cache = T}
weighted_fluxes <- data.frame("0.1" = NA, "0.2" = NA, "0.3" = NA, "0.4" = NA, "0.5" = NA, "0.6" = NA, "0.7" = NA, "0.8" = NA, "0.9" = NA)
avenelles_2015 <- avenelles_flux %>% filter(year == 2015)

for(i in 1:10000){
iflux <- vector("numeric",10)
for(n in 1:9){
  set.seed(i)
  df <- sample_frac(avenelles_2015, n/10)
  weighted_fluxn <- sum(with(df, doc_mg.L* q_L.s), na.rm = T)*1e-9 / with(df, sum(q_L.s, na.rm = T)) * with(df, mean(q_L.s, na.rm = T))  * 24 * 60 * 60 * 365
  iflux[n] <- weighted_fluxn
  #weighted_fluxes[i,paste("X",n,sep = "")] <<- weighted_fluxn
}
weighted_fluxes <- rbind(weighted_fluxes, iflux)
}

weighted_fluxes <- weighted_fluxes[-1,]

```

```{r annual-flux-ref}
annual_flux_ref <- with(avenelles_2015, doc_mg.L * q_L.s * 1e3 * period * 3600) %>% sum(na.rm = T)*1e-9 #DOC in mg/L, q converted from m3/s to L/s, so we get flux in mg/s, multiplied by the number of s in one period (in hour converted to second) then summed and converted to ton

```


```{r compare-with-ref-value}
ggplot(weighted_fluxes)+geom_boxplot(aes(x = "0.1", y = X0.1))+
  geom_boxplot(aes(x = "0.2", y = X0.2))+
  geom_boxplot(aes(x = "0.3", y = X0.3))+
  geom_boxplot(aes(x = "0.4", y = X0.4))+
  geom_boxplot(aes(x = "0.5", y = X0.5))+
  geom_boxplot(aes(x = "0.6", y = X0.6))+
  geom_boxplot(aes(x = "0.7", y = X0.7))+
  geom_boxplot(aes(x = "0.8", y = X0.8))+
  geom_boxplot(aes(x = "0.9", y = X0.9))+
  labs(x="Proportion of dataset", y = "Estimated annual flux, ton")+
  geom_abline(slope = 0, intercept = annual_flux_ref, col = 
  "pink")+
  theme_minimal(base_size = 15)
```

```{r incertitude-weighting-method}
summary_weighted_fluxes <- rbind(summarise_all(weighted_fluxes, mean),
                                 summarise_all(weighted_fluxes, sd))

knitr::kable(summary_weighted_fluxes)
```

## 10%



```{r percent10}


waf_10 <- list()

for(i in 1:n_rep){
  idx_10 <- sample(n_ave, n_ave*0.10)
  ftsm_10 <- flux_ton.s_mat[,idx_10]
  q_10 <- q_mat[, idx_10]

  # Get index for the columns corresponding to the same year
  index_years <- lapply(unique_years, function(y){which(avenelles_w$year[idx_10] == y)}) # list of indices corresponding to each year

  # Annual flux
  sum_instant_flux_ton.y_10 <- lapply(index_years, FUN = function(idx){apply(ftsm_10[,idx], 1, sum, na.rm = T)}) %>% do.call("cbind",.) # sum of fluxes per year, for each MC world computed previously. Result is a matrix with 1000 rows and 3 columns  (1 per year)
  sum_instant_q_10 <- sapply(index_years, function(idx){apply(q_10[,idx], 1, sum, na.rm = T)}) # same for Q
  mean_instant_q_10 <- sapply(index_years, function(idx){apply(q_10[,idx], 1, mean, na.rm = T)}) # same for mean Q: 1000 lines, 3 columns
  
  weighted_annual_flux_ton.y_10 <- sum_instant_flux_ton.y_10 / sum_instant_q_10 * mean_instant_q_10 * 60 * 60 * 24 *365 # 1000 lines and 3 columns of weignted annual fluxes
  
  waf_10[[i]] <- weighted_annual_flux_ton.y_10 # stored in the big list
}

```

```{r 10-percent-mean}
# waf_10_mean <- c()
# waf_10_upr <- c()
# waf_10_lwr <- c()
# 
# # calcul du flux annuel pour chaque resampling
# for(i in 1:nyears){
#   waf_10_mean[i] <- lapply(waf_10, function(x) x[,i]) %>% unlist() %>% mean() # mean of the 1000 MC worlds for each year: 1 line, 3 columns
#   waf_10_upr[i] <- lapply(waf_10, function(x) x[,i]) %>% unlist() %>% quantile(0.975)
#   waf_10_lwr[i] <- lapply(waf_10, function(x) x[,i]) %>% unlist() %>% quantile(0.025)
#   }

wiaf_10 <- lapply(waf_10, rowMeans) # 100 moyennes interannuelles resampled, avec 1000 simulations montecarlo 

wiaf_10_mean <- lapply(wiaf_10, mean) %>% unlist()
wiaf_10_sd <- lapply(wiaf_10, sd) %>% unlist()
wiaf_10_upr <- lapply(wiaf_10, quantile, 0.975) %>% unlist()
wiaf_10_lwr <- lapply(wiaf_10, quantile, 0.025) %>% unlist()


```

```{r visualisation-wiaf-10, eval = F}
# Merge in df
weighted_total_flux_df_10 <- data.frame(year = c(unique_years, "interannual"), 
                        annual_flux_mean = c(waf_10_mean, wiaf_10_mean), 
                        annual_flux_variability = c(rep(NA, nyears), wiaf_10_sd), 
                        annual_flux_pi_lower = c(waf_10_lwr, wiaf_10_lwr), 
                        annual_flux_pi_upper = c(waf_10_upr, wiaf_10_upr),
                        group = c(rep("annual",nyears),"interannual"))

ggplot()+
  geom_col(data = weighted_total_flux_df_10, aes(x=year, y = annual_flux_mean, fill = group))+
    geom_errorbar(data = weighted_total_flux_df_10, aes(x = year, ymin = annual_flux_pi_lower, ymax = annual_flux_pi_upper, col = "prediction interval"), width = 0.3, linewidth = 0.8)+
  geom_errorbar(data = filter(weighted_total_flux_df_10, year == "interannual"), aes(x = year, ymin = annual_flux_mean - annual_flux_variability, ymax = annual_flux_mean + annual_flux_variability, col = "interannual variability"), width = 0.2, linewidth = 0.8, linetype = 2)+
  scale_fill_manual(values = c("annual" = "lightblue", "interannual" = "indianred"))+
  scale_color_manual(values = c("prediction interval" = "darkblue", "interannual variability" = "darkred"), name = "")+
   labs(x = "Year", y = "Flux (ton/year)", fill = "")+
  theme_minimal(base_size = 15)+
  theme(axis.text.x = element_text(angle = 45, hjust = 1), legend.position = "bottom")

```



## 20%

```{r percent20}
waf_20 <- list()

for(i in 1:n_rep){
  idx_20 <- sample(n_ave, n_ave*0.20)
  ftsm_20 <- flux_ton.s_mat[,idx_20]
  q_20 <- q_mat[, idx_20]

  # Get index for the columns corresponding to the same year
  index_years <- lapply(unique_years, function(y){which(avenelles_w$year[idx_20] == y)}) # list of indices corresponding to each year

  # Annual flux
  sum_instant_flux_ton.y_20 <- lapply(index_years, FUN = function(idx){apply(ftsm_20[,idx], 1, sum, na.rm = T)}) %>% do.call("cbind",.) # sum of fluxes per year, for each iteration of the bootstrap. Result is a matrix with nrow_boot rows and  (1 column per year)
  sum_instant_q_20 <- sapply(index_years, function(idx){apply(q_20[,idx], 1, sum, na.rm = T)}) # sum of discharge per year, for each iteration of the bootstrap. Result is a matrix with nrow_boot rows and 1 columns per year
  mean_instant_q_20 <- sapply(index_years, function(idx){apply(q_20[,idx], 1, mean, na.rm = T)}) # mean discharge per year
  
  weighted_annual_flux_ton.y_20 <- sum_instant_flux_ton.y_20 / sum_instant_q_20 * mean_instant_q_20 * 60 * 60 * 24 *365 # period is a number of hours, converted to day
  
  waf_20[[i]] <- weighted_annual_flux_ton.y_20
}

```

```{r 20-percent-mean}
# waf_20_mean <- c()
# waf_20_upr <- c()
# waf_20_lwr <- c()
# 
# for(i in 1:nyears){
#   waf_20_mean[i] <- lapply(waf_20, function(x) x[,i]) %>% unlist() %>% mean()
#   waf_20_upr[i] <- lapply(waf_20, function(x) x[,i]) %>% unlist() %>% quantile(0.975)
#   waf_20_lwr[i] <- lapply(waf_20, function(x) x[,i]) %>% unlist() %>% quantile(0.025)
# }

wiaf_20 <- lapply(waf_20, rowMeans) # 100 moyennes interannuelles resampled, avec 1000 simulations montecarlo 

wiaf_20_mean <- lapply(wiaf_20, mean) %>% unlist()
wiaf_20_sd <- lapply(wiaf_20, sd) %>% unlist()
wiaf_20_upr <- lapply(wiaf_20, quantile, 0.975) %>% unlist()
wiaf_20_lwr <- lapply(wiaf_20, quantile, 0.025) %>% unlist()

```


```{r visualisation-wiaf-20, eval = F}
# Merge in df
weighted_total_flux_df_20 <- data.frame(year = c(unique_years, "interannual"), 
                        annual_flux_mean = c(waf_20_mean, wiaf_20_mean), 
                        annual_flux_variability = c(rep(NA, nyears), wiaf_20_sd), 
                        annual_flux_pi_lower = c(waf_20_lwr, wiaf_20_lwr), 
                        annual_flux_pi_upper = c(waf_20_upr, wiaf_20_upr),
                        group = c(rep("annual",nyears),"interannual"))

ggplot()+
  geom_col(data = weighted_total_flux_df_20, aes(x=year, y = annual_flux_mean, fill = group))+
    geom_errorbar(data = weighted_total_flux_df_20, aes(x = year, ymin = annual_flux_pi_lower, ymax = annual_flux_pi_upper, col = "prediction interval"), width = 0.3, linewidth = 0.8)+
  geom_errorbar(data = filter(weighted_total_flux_df_20, year == "interannual"), aes(x = year, ymin = annual_flux_mean - annual_flux_variability, ymax = annual_flux_mean + annual_flux_variability, col = "interannual variability"), width = 0.2, linewidth = 0.8, linetype = 2)+
  scale_fill_manual(values = c("annual" = "lightblue", "interannual" = "indianred"))+
  scale_color_manual(values = c("prediction interval" = "darkblue", "interannual variability" = "darkred"), name = "")+
   labs(x = "Year", y = "Flux (ton/year)", fill = "")+
  theme_minimal(base_size = 15)+
  theme(axis.text.x = element_text(angle = 45, hjust = 1), legend.position = "bottom")

```


## 30%

```{r percent30}
waf_30 <- list()

for(i in 1:n_rep){
  idx_30 <- sample(n_ave, n_ave*0.30)
  ftsm_30 <- flux_ton.s_mat[,idx_30]
  q_30 <- q_mat[, idx_30]

  # Get index for the columns corresponding to the same year
  index_years <- lapply(unique_years, function(y){which(avenelles_w$year[idx_30] == y)}) # list of indices corresponding to each year

  # Annual flux
  sum_instant_flux_ton.y_30 <- lapply(index_years, FUN = function(idx){apply(ftsm_30[,idx], 1, sum, na.rm = T)}) %>% do.call("cbind",.) # sum of fluxes per year, for each iteration of the bootstrap. Result is a matrix with nrow_boot rows and  (1 column per year)
  sum_instant_q_30 <- sapply(index_years, function(idx){apply(q_30[,idx], 1, sum, na.rm = T)}) # sum of discharge per year, for each iteration of the bootstrap. Result is a matrix with nrow_boot rows and 1 columns per year
  mean_instant_q_30 <- sapply(index_years, function(idx){apply(q_30[,idx], 1, mean, na.rm = T)}) # mean discharge per year
  
  weighted_annual_flux_ton.y_30 <- sum_instant_flux_ton.y_30 / sum_instant_q_30 * mean_instant_q_30 * 60 * 60 * 24 *365 # period is a number of hours, converted to day
  
  waf_30[[i]] <- weighted_annual_flux_ton.y_30
}

```

```{r 30-percent-mean}
# waf_30_mean <- c()
# waf_30_upr <- c()
# waf_30_lwr <- c()
# 
# for(i in 1:nyears){
#   waf_30_mean[i] <- lapply(waf_30, function(x) x[,i]) %>% unlist() %>% mean()
#   waf_30_upr[i] <- lapply(waf_30, function(x) x[,i]) %>% unlist() %>% quantile(0.975)
#   waf_30_lwr[i] <- lapply(waf_30, function(x) x[,i]) %>% unlist() %>% quantile(0.025)
#   }

wiaf_30 <- lapply(waf_30, rowMeans) # 100 moyennes interannuelles resampled, avec 1000 simulations montecarlo 

wiaf_30_mean <- lapply(wiaf_30, mean) %>% unlist()
wiaf_30_sd <- lapply(wiaf_30, sd) %>% unlist()
wiaf_30_upr <- lapply(wiaf_30, quantile, 0.975) %>% unlist()
wiaf_30_lwr <- lapply(wiaf_30, quantile, 0.025) %>% unlist()

```


```{r visualisation-wiaf-30, eval = F}
# Merge in df
weighted_total_flux_df_30 <- data.frame(year = c(unique_years, "interannual"), 
                        annual_flux_mean = c(waf_30_mean, wiaf_30_mean), 
                        annual_flux_variability = c(rep(NA, nyears), wiaf_30_sd), 
                        annual_flux_pi_lower = c(waf_30_lwr, wiaf_30_lwr), 
                        annual_flux_pi_upper = c(waf_30_upr, wiaf_30_upr),
                        group = c(rep("annual",nyears),"interannual"))

ggplot()+
  geom_col(data = weighted_total_flux_df_30, aes(x=year, y = annual_flux_mean, fill = group))+
    geom_errorbar(data = weighted_total_flux_df_30, aes(x = year, ymin = annual_flux_pi_lower, ymax = annual_flux_pi_upper, col = "prediction interval"), width = 0.3, linewidth = 0.8)+
  geom_errorbar(data = filter(weighted_total_flux_df_30, year == "interannual"), aes(x = year, ymin = annual_flux_mean - annual_flux_variability, ymax = annual_flux_mean + annual_flux_variability, col = "interannual variability"), width = 0.2, linewidth = 0.8, linetype = 2)+
  scale_fill_manual(values = c("annual" = "lightblue", "interannual" = "indianred"))+
  scale_color_manual(values = c("prediction interval" = "darkblue", "interannual variability" = "darkred"), name = "")+
   labs(x = "Year", y = "Flux (ton/year)", fill = "")+
  theme_minimal(base_size = 15)+
  theme(axis.text.x = element_text(angle = 45, hjust = 1), legend.position = "bottom")

```

## 40%

```{r percent40}
waf_40 <- list()

for(i in 1:n_rep){
  idx_40 <- sample(n_ave, n_ave*0.40)
  ftsm_40 <- flux_ton.s_mat[,idx_40]
  q_40 <- q_mat[, idx_40]

  # Get index for the columns corresponding to the same year
  index_years <- lapply(unique_years, function(y){which(avenelles_w$year[idx_40] == y)}) # list of indices corresponding to each year

  # Annual flux
  sum_instant_flux_ton.y_40 <- lapply(index_years, FUN = function(idx){apply(ftsm_40[,idx], 1, sum, na.rm = T)}) %>% do.call("cbind",.) # sum of fluxes per year, for each iteration of the bootstrap. Result is a matrix with nrow_boot rows and  (1 column per year)
  sum_instant_q_40 <- sapply(index_years, function(idx){apply(q_40[,idx], 1, sum, na.rm = T)}) # sum of discharge per year, for each iteration of the bootstrap. Result is a matrix with nrow_boot rows and 1 columns per year
  mean_instant_q_40 <- sapply(index_years, function(idx){apply(q_40[,idx], 1, mean, na.rm = T)}) # mean discharge per year
  
  weighted_annual_flux_ton.y_40 <- sum_instant_flux_ton.y_40 / sum_instant_q_40 * mean_instant_q_40 * 60 * 60 * 24 *365 # period is a number of hours, converted to day
  
  waf_40[[i]] <- weighted_annual_flux_ton.y_40
}

```

```{r 40-percent-mean}
# waf_40_mean <- c()
# waf_40_upr <- c()
# waf_40_lwr <- c()
# 
# for(i in 1:nyears){
#   waf_40_mean[i] <- lapply(waf_40, function(x) x[,i]) %>% unlist() %>% mean()
#   waf_40_upr[i] <- lapply(waf_40, function(x) x[,i]) %>% unlist() %>% quantile(0.975)
#   waf_40_lwr[i] <- lapply(waf_40, function(x) x[,i]) %>% unlist() %>% quantile(0.025)
#   }

wiaf_40 <- lapply(waf_40, rowMeans) # 100 moyennes interannuelles resampled, avec 1000 simulations montecarlo 

wiaf_40_mean <- lapply(wiaf_40, mean) %>% unlist()
wiaf_40_sd <- lapply(wiaf_40, sd) %>% unlist()
wiaf_40_upr <- lapply(wiaf_40, quantile, 0.975) %>% unlist()
wiaf_40_lwr <- lapply(wiaf_40, quantile, 0.025) %>% unlist()

```


```{r visualisation-wiaf-40, eval = F}
# Merge in df
weighted_total_flux_df_40 <- data.frame(year = c(unique_years, "interannual"), 
                        annual_flux_mean = c(waf_40_mean, wiaf_40_mean), 
                        annual_flux_variability = c(rep(NA, nyears), wiaf_40_sd), 
                        annual_flux_pi_lower = c(waf_40_lwr, wiaf_40_lwr), 
                        annual_flux_pi_upper = c(waf_40_upr, wiaf_40_upr),
                        group = c(rep("annual",nyears),"interannual"))

ggplot()+
  geom_col(data = weighted_total_flux_df_40, aes(x=year, y = annual_flux_mean, fill = group))+
    geom_errorbar(data = weighted_total_flux_df_40, aes(x = year, ymin = annual_flux_pi_lower, ymax = annual_flux_pi_upper, col = "prediction interval"), width = 0.3, linewidth = 0.8)+
  geom_errorbar(data = filter(weighted_total_flux_df_40, year == "interannual"), aes(x = year, ymin = annual_flux_mean - annual_flux_variability, ymax = annual_flux_mean + annual_flux_variability, col = "interannual variability"), width = 0.2, linewidth = 0.8, linetype = 2)+
  scale_fill_manual(values = c("annual" = "lightblue", "interannual" = "indianred"))+
  scale_color_manual(values = c("prediction interval" = "darkblue", "interannual variability" = "darkred"), name = "")+
   labs(x = "Year", y = "Flux (ton/year)", fill = "")+
  theme_minimal(base_size = 15)+
  theme(axis.text.x = element_text(angle = 45, hjust = 1), legend.position = "bottom")

```

## 50%

```{r percent50}
waf_50 <- list()

for(i in 1:n_rep){
  idx_50 <- sample(n_ave, n_ave*0.50)
  ftsm_50 <- flux_ton.s_mat[,idx_50]
  q_50 <- q_mat[, idx_50]

  # Get index for the columns corresponding to the same year
  index_years <- lapply(unique_years, function(y){which(avenelles_w$year[idx_50] == y)}) # list of indices corresponding to each year

  # Annual flux
  sum_instant_flux_ton.y_50 <- lapply(index_years, FUN = function(idx){apply(ftsm_50[,idx], 1, sum, na.rm = T)}) %>% do.call("cbind",.) # sum of fluxes per year, for each iteration of the bootstrap. Result is a matrix with nrow_boot rows and  (1 column per year)
  sum_instant_q_50 <- sapply(index_years, function(idx){apply(q_50[,idx], 1, sum, na.rm = T)}) # sum of discharge per year, for each iteration of the bootstrap. Result is a matrix with nrow_boot rows and 1 columns per year
  mean_instant_q_50 <- sapply(index_years, function(idx){apply(q_50[,idx], 1, mean, na.rm = T)}) # mean discharge per year
  
  weighted_annual_flux_ton.y_50 <- sum_instant_flux_ton.y_50 / sum_instant_q_50 * mean_instant_q_50 * 60 * 60 * 24 *365 # period is a number of hours, converted to day
  
  waf_50[[i]] <- weighted_annual_flux_ton.y_50
}

```

```{r 50-percent-mean}
# waf_50_mean <- c()
# waf_50_upr <- c()
# waf_50_lwr <- c()
# 
# for(i in 1:nyears){
#   waf_50_mean[i] <- lapply(waf_50, function(x) x[,i]) %>% unlist() %>% mean()
#   waf_50_upr[i] <- lapply(waf_50, function(x) x[,i]) %>% unlist() %>% quantile(0.975)
#   waf_50_lwr[i] <- lapply(waf_50, function(x) x[,i]) %>% unlist() %>% quantile(0.025)
#   }

wiaf_50 <- lapply(waf_50, rowMeans) # 100 moyennes interannuelles resampled, avec 1000 simulations montecarlo 

wiaf_50_mean <- lapply(wiaf_50, mean) %>% unlist()
wiaf_50_sd <- lapply(wiaf_50, sd) %>% unlist()
wiaf_50_upr <- lapply(wiaf_50, quantile, 0.975) %>% unlist()
wiaf_50_lwr <- lapply(wiaf_50, quantile, 0.025) %>% unlist()

```


```{r visualisation-wiaf-50, eval = F}
# Merge in df
weighted_total_flux_df_50 <- data.frame(year = c(unique_years, "interannual"), 
                        annual_flux_mean = c(waf_50_mean, wiaf_50_mean), 
                        annual_flux_variability = c(rep(NA, nyears), wiaf_50_sd), 
                        annual_flux_pi_lower = c(waf_50_lwr, wiaf_50_lwr), 
                        annual_flux_pi_upper = c(waf_50_upr, wiaf_50_upr),
                        group = c(rep("annual",nyears),"interannual"))

ggplot()+
  geom_col(data = weighted_total_flux_df_50, aes(x=year, y = annual_flux_mean, fill = group))+
    geom_errorbar(data = weighted_total_flux_df_50, aes(x = year, ymin = annual_flux_pi_lower, ymax = annual_flux_pi_upper, col = "prediction interval"), width = 0.3, linewidth = 0.8)+
  geom_errorbar(data = filter(weighted_total_flux_df_50, year == "interannual"), aes(x = year, ymin = annual_flux_mean - annual_flux_variability, ymax = annual_flux_mean + annual_flux_variability, col = "interannual variability"), width = 0.2, linewidth = 0.8, linetype = 2)+
  scale_fill_manual(values = c("annual" = "lightblue", "interannual" = "indianred"))+
  scale_color_manual(values = c("prediction interval" = "darkblue", "interannual variability" = "darkred"), name = "")+
   labs(x = "Year", y = "Flux (ton/year)", fill = "")+
  theme_minimal(base_size = 15)+
  theme(axis.text.x = element_text(angle = 45, hjust = 1), legend.position = "bottom")

```

## 60%

```{r percent60}
waf_60 <- list()

for(i in 1:n_rep){
  idx_60 <- sample(n_ave, n_ave*0.60)
  ftsm_60 <- flux_ton.s_mat[,idx_60]
  q_60 <- q_mat[, idx_60]

  # Get index for the columns corresponding to the same year
  index_years <- lapply(unique_years, function(y){which(avenelles_w$year[idx_60] == y)}) # list of indices corresponding to each year

  # Annual flux
  sum_instant_flux_ton.y_60 <- lapply(index_years, FUN = function(idx){apply(ftsm_60[,idx], 1, sum, na.rm = T)}) %>% do.call("cbind",.) # sum of fluxes per year, for each iteration of the bootstrap. Result is a matrix with nrow_boot rows and  (1 column per year)
  sum_instant_q_60 <- sapply(index_years, function(idx){apply(q_60[,idx], 1, sum, na.rm = T)}) # sum of discharge per year, for each iteration of the bootstrap. Result is a matrix with nrow_boot rows and 1 columns per year
  mean_instant_q_60 <- sapply(index_years, function(idx){apply(q_60[,idx], 1, mean, na.rm = T)}) # mean discharge per year
  
  weighted_annual_flux_ton.y_60 <- sum_instant_flux_ton.y_60 / sum_instant_q_60 * mean_instant_q_60 * 60 * 60 * 24 *365 # period is a number of hours, converted to day
  
  waf_60[[i]] <- weighted_annual_flux_ton.y_60
}

```

```{r 60-percent-mean}
# waf_60_mean <- c()
# waf_60_upr <- c()
# waf_60_lwr <- c()
# 
# for(i in 1:nyears){
#   waf_60_mean[i] <- lapply(waf_60, function(x) x[,i]) %>% unlist() %>% mean()
#   waf_60_upr[i] <- lapply(waf_60, function(x) x[,i]) %>% unlist() %>% quantile(0.975)
#   waf_60_lwr[i] <- lapply(waf_60, function(x) x[,i]) %>% unlist() %>% quantile(0.025)
#   }

wiaf_60 <- lapply(waf_60, rowMeans) # 100 moyennes interannuelles resampled, avec 1000 simulations montecarlo 

wiaf_60_mean <- lapply(wiaf_60, mean) %>% unlist()
wiaf_60_sd <- lapply(wiaf_60, sd) %>% unlist()
wiaf_60_upr <- lapply(wiaf_60, quantile, 0.975) %>% unlist()
wiaf_60_lwr <- lapply(wiaf_60, quantile, 0.025) %>% unlist()

```


```{r visualisation-wiaf-60, eval = F}
# Merge in df
weighted_total_flux_df_60 <- data.frame(year = c(unique_years, "interannual"), 
                        annual_flux_mean = c(waf_60_mean, wiaf_60_mean), 
                        annual_flux_variability = c(rep(NA, nyears), wiaf_60_sd), 
                        annual_flux_pi_lower = c(waf_60_lwr, wiaf_60_lwr), 
                        annual_flux_pi_upper = c(waf_60_upr, wiaf_60_upr),
                        group = c(rep("annual",nyears),"interannual"))

ggplot()+
  geom_col(data = weighted_total_flux_df_60, aes(x=year, y = annual_flux_mean, fill = group))+
    geom_errorbar(data = weighted_total_flux_df_60, aes(x = year, ymin = annual_flux_pi_lower, ymax = annual_flux_pi_upper, col = "prediction interval"), width = 0.3, linewidth = 0.8)+
  geom_errorbar(data = filter(weighted_total_flux_df_60, year == "interannual"), aes(x = year, ymin = annual_flux_mean - annual_flux_variability, ymax = annual_flux_mean + annual_flux_variability, col = "interannual variability"), width = 0.2, linewidth = 0.8, linetype = 2)+
  scale_fill_manual(values = c("annual" = "lightblue", "interannual" = "indianred"))+
  scale_color_manual(values = c("prediction interval" = "darkblue", "interannual variability" = "darkred"), name = "")+
   labs(x = "Year", y = "Flux (ton/year)", fill = "")+
  theme_minimal(base_size = 15)+
  theme(axis.text.x = element_text(angle = 45, hjust = 1), legend.position = "bottom")

```

## 70%

```{r percent70}
waf_70 <- list()

for(i in 1:n_rep){
  idx_70 <- sample(n_ave, n_ave*0.70)
  ftsm_70 <- flux_ton.s_mat[,idx_70]
  q_70 <- q_mat[, idx_70]

  # Get index for the columns corresponding to the same year
  index_years <- lapply(unique_years, function(y){which(avenelles_w$year[idx_70] == y)}) # list of indices corresponding to each year

  # Annual flux
  sum_instant_flux_ton.y_70 <- lapply(index_years, FUN = function(idx){apply(ftsm_70[,idx], 1, sum, na.rm = T)}) %>% do.call("cbind",.) # sum of fluxes per year, for each iteration of the bootstrap. Result is a matrix with nrow_boot rows and  (1 column per year)
  sum_instant_q_70 <- sapply(index_years, function(idx){apply(q_70[,idx], 1, sum, na.rm = T)}) # sum of discharge per year, for each iteration of the bootstrap. Result is a matrix with nrow_boot rows and 1 columns per year
  mean_instant_q_70 <- sapply(index_years, function(idx){apply(q_70[,idx], 1, mean, na.rm = T)}) # mean discharge per year
  
  weighted_annual_flux_ton.y_70 <- sum_instant_flux_ton.y_70 / sum_instant_q_70 * mean_instant_q_70 * 60 * 60 * 24 *365 # period is a number of hours, converted to day
  
  waf_70[[i]] <- weighted_annual_flux_ton.y_70
}

```

```{r 70-percent-mean}
# waf_70_mean <- c()
# waf_70_upr <- c()
# waf_70_lwr <- c()
# 
# for(i in 1:nyears){
#   waf_70_mean[i] <- lapply(waf_70, function(x) x[,i]) %>% unlist() %>% mean()
#   waf_70_upr[i] <- lapply(waf_70, function(x) x[,i]) %>% unlist() %>% quantile(0.975)
#   waf_70_lwr[i] <- lapply(waf_70, function(x) x[,i]) %>% unlist() %>% quantile(0.025)
# }

wiaf_70 <- lapply(waf_70, rowMeans) # 100 moyennes interannuelles resampled, avec 1000 simulations montecarlo 

wiaf_70_mean <- lapply(wiaf_70, mean) %>% unlist()
wiaf_70_sd <- lapply(wiaf_70, sd) %>% unlist()
wiaf_70_upr <- lapply(wiaf_70, quantile, 0.975) %>% unlist()
wiaf_70_lwr <- lapply(wiaf_70, quantile, 0.025) %>% unlist()

```


```{r visualisation-wiaf-70, eval = F}
# Merge in df
weighted_total_flux_df_70 <- data.frame(year = c(unique_years, "interannual"), 
                        annual_flux_mean = c(waf_70_mean, wiaf_70_mean), 
                        annual_flux_variability = c(rep(NA, nyears), wiaf_70_sd), 
                        annual_flux_pi_lower = c(waf_70_lwr, wiaf_70_lwr), 
                        annual_flux_pi_upper = c(waf_70_upr, wiaf_70_upr),
                        group = c(rep("annual",nyears),"interannual"))

ggplot()+
  geom_col(data = weighted_total_flux_df_70, aes(x=year, y = annual_flux_mean, fill = group))+
    geom_errorbar(data = weighted_total_flux_df_70, aes(x = year, ymin = annual_flux_pi_lower, ymax = annual_flux_pi_upper, col = "prediction interval"), width = 0.3, linewidth = 0.8)+
  geom_errorbar(data = filter(weighted_total_flux_df_70, year == "interannual"), aes(x = year, ymin = annual_flux_mean - annual_flux_variability, ymax = annual_flux_mean + annual_flux_variability, col = "interannual variability"), width = 0.2, linewidth = 0.8, linetype = 2)+
  scale_fill_manual(values = c("annual" = "lightblue", "interannual" = "indianred"))+
  scale_color_manual(values = c("prediction interval" = "darkblue", "interannual variability" = "darkred"), name = "")+
   labs(x = "Year", y = "Flux (ton/year)", fill = "")+
  theme_minimal(base_size = 15)+
  theme(axis.text.x = element_text(angle = 45, hjust = 1), legend.position = "bottom")

```

## 80%

```{r percent80}
waf_80 <- list()

for(i in 1:n_rep){
  idx_80 <- sample(n_ave, n_ave*0.80)
  ftsm_80 <- flux_ton.s_mat[,idx_80]
  q_80 <- q_mat[, idx_80]

  # Get index for the columns corresponding to the same year
  index_years <- lapply(unique_years, function(y){which(avenelles_w$year[idx_80] == y)}) # list of indices corresponding to each year

  # Annual flux
  sum_instant_flux_ton.y_80 <- lapply(index_years, FUN = function(idx){apply(ftsm_80[,idx], 1, sum, na.rm = T)}) %>% do.call("cbind",.) # sum of fluxes per year, for each iteration of the bootstrap. Result is a matrix with nrow_boot rows and  (1 column per year)
  sum_instant_q_80 <- sapply(index_years, function(idx){apply(q_80[,idx], 1, sum, na.rm = T)}) # sum of discharge per year, for each iteration of the bootstrap. Result is a matrix with nrow_boot rows and 1 columns per year
  mean_instant_q_80 <- sapply(index_years, function(idx){apply(q_80[,idx], 1, mean, na.rm = T)}) # mean discharge per year
  
  weighted_annual_flux_ton.y_80 <- sum_instant_flux_ton.y_80 / sum_instant_q_80 * mean_instant_q_80 * 60 * 60 * 24 *365 # period is a number of hours, converted to day
  
  waf_80[[i]] <- weighted_annual_flux_ton.y_80
}

```

```{r 80-percent-mean}
# waf_80_mean <- c()
# waf_80_upr <- c()
# waf_80_lwr <- c()
# 
# for(i in 1:nyears){
#   waf_80_mean[i] <- lapply(waf_80, function(x) x[,i]) %>% unlist() %>% mean()
#   waf_80_upr[i] <- lapply(waf_80, function(x) x[,i]) %>% unlist() %>% quantile(0.975)
#   waf_80_lwr[i] <- lapply(waf_80, function(x) x[,i]) %>% unlist() %>% quantile(0.025)
#   }

wiaf_80 <- lapply(waf_80, rowMeans) # 100 moyennes interannuelles resampled, avec 1000 simulations montecarlo 

wiaf_80_mean <- lapply(wiaf_80, mean) %>% unlist()
wiaf_80_sd <- lapply(wiaf_80, sd) %>% unlist()
wiaf_80_upr <- lapply(wiaf_80, quantile, 0.975) %>% unlist()
wiaf_80_lwr <- lapply(wiaf_80, quantile, 0.025) %>% unlist()

```


```{r visualisation-wiaf-80, eval = F}
# Merge in df
weighted_total_flux_df_80 <- data.frame(year = c(unique_years, "interannual"), 
                        annual_flux_mean = c(waf_80_mean, wiaf_80_mean), 
                        annual_flux_variability = c(rep(NA, nyears), wiaf_80_sd), 
                        annual_flux_pi_lower = c(waf_80_lwr, wiaf_80_lwr), 
                        annual_flux_pi_upper = c(waf_80_upr, wiaf_80_upr),
                        group = c(rep("annual",nyears),"interannual"))

ggplot()+
  geom_col(data = weighted_total_flux_df_80, aes(x=year, y = annual_flux_mean, fill = group))+
    geom_errorbar(data = weighted_total_flux_df_80, aes(x = year, ymin = annual_flux_pi_lower, ymax = annual_flux_pi_upper, col = "prediction interval"), width = 0.3, linewidth = 0.8)+
  geom_errorbar(data = filter(weighted_total_flux_df_80, year == "interannual"), aes(x = year, ymin = annual_flux_mean - annual_flux_variability, ymax = annual_flux_mean + annual_flux_variability, col = "interannual variability"), width = 0.2, linewidth = 0.8, linetype = 2)+
  scale_fill_manual(values = c("annual" = "lightblue", "interannual" = "indianred"))+
  scale_color_manual(values = c("prediction interval" = "darkblue", "interannual variability" = "darkred"), name = "")+
   labs(x = "Year", y = "Flux (ton/year)", fill = "")+
  theme_minimal(base_size = 15)+
  theme(axis.text.x = element_text(angle = 45, hjust = 1), legend.position = "bottom")

```

## 90%

```{r percent90}
waf_90 <- list()

for(i in 1:n_rep){
  idx_90 <- sample(n_ave, n_ave*0.90)
  ftsm_90 <- flux_ton.s_mat[,idx_90]
  q_90 <- q_mat[, idx_90]

  # Get index for the columns corresponding to the same year
  index_years <- lapply(unique_years, function(y){which(avenelles_w$year[idx_90] == y)}) # list of indices corresponding to each year

  # Annual flux
  sum_instant_flux_ton.y_90 <- lapply(index_years, FUN = function(idx){apply(ftsm_90[,idx], 1, sum, na.rm = T)}) %>% do.call("cbind",.) # sum of fluxes per year, for each iteration of the bootstrap. Result is a matrix with nrow_boot rows and  (1 column per year)
  sum_instant_q_90 <- sapply(index_years, function(idx){apply(q_90[,idx], 1, sum, na.rm = T)}) # sum of discharge per year, for each iteration of the bootstrap. Result is a matrix with nrow_boot rows and 1 columns per year
  mean_instant_q_90 <- sapply(index_years, function(idx){apply(q_90[,idx], 1, mean, na.rm = T)}) # mean discharge per year
  
  weighted_annual_flux_ton.y_90 <- sum_instant_flux_ton.y_90 / sum_instant_q_90 * mean_instant_q_90 * 60 * 60 * 24 *365 # period is a number of hours, converted to day
  
  waf_90[[i]] <- weighted_annual_flux_ton.y_90
}

```

```{r 90-percent-mean}
# waf_90_mean <- c()
# waf_90_upr <- c()
# waf_90_lwr <- c()
# 
# for(i in 1:nyears){
#   waf_90_mean[i] <- lapply(waf_90, function(x) x[,i]) %>% unlist() %>% mean()
#   waf_90_upr[i] <- lapply(waf_90, function(x) x[,i]) %>% unlist() %>% quantile(0.975)
#   waf_90_lwr[i] <- lapply(waf_90, function(x) x[,i]) %>% unlist() %>% quantile(0.025)
#   }

wiaf_90 <- lapply(waf_90, rowMeans) # 100 moyennes interannuelles resampled, avec 1000 simulations montecarlo 

wiaf_90_mean <- lapply(wiaf_90, mean) %>% unlist()
wiaf_90_sd <- lapply(wiaf_90, sd) %>% unlist()
wiaf_90_upr <- lapply(wiaf_90, quantile, 0.975) %>% unlist()
wiaf_90_lwr <- lapply(wiaf_90, quantile, 0.025) %>% unlist()

```


```{r visualisation-wiaf-90, eval = F}
# Merge in df
weighted_total_flux_df_90 <- data.frame(year = c(unique_years, "interannual"), 
                        annual_flux_mean = c(waf_90_mean, wiaf_90_mean), 
                        annual_flux_variability = c(rep(NA, nyears), wiaf_90_sd), 
                        annual_flux_pi_lower = c(waf_90_lwr, wiaf_90_lwr), 
                        annual_flux_pi_upper = c(waf_90_upr, wiaf_90_upr),
                        group = c(rep("annual",nyears),"interannual"))

ggplot()+
  geom_col(data = weighted_total_flux_df_90, aes(x=year, y = annual_flux_mean, fill = group))+
    geom_errorbar(data = weighted_total_flux_df_90, aes(x = year, ymin = annual_flux_pi_lower, ymax = annual_flux_pi_upper, col = "prediction interval"), width = 0.3, linewidth = 0.8)+
  geom_errorbar(data = filter(weighted_total_flux_df_90, year == "interannual"), aes(x = year, ymin = annual_flux_mean - annual_flux_variability, ymax = annual_flux_mean + annual_flux_variability, col = "interannual variability"), width = 0.2, linewidth = 0.8, linetype = 2)+
  scale_fill_manual(values = c("annual" = "lightblue", "interannual" = "indianred"))+
  scale_color_manual(values = c("prediction interval" = "darkblue", "interannual variability" = "darkred"), name = "")+
   labs(x = "Year", y = "Flux (ton/year)", fill = "")+
  theme_minimal(base_size = 15)+
  theme(axis.text.x = element_text(angle = 45, hjust = 1), legend.position = "bottom")

```

## 100%

```{r percent100}
waf_100 <- list()

for(i in 1:n_rep){
  idx_100 <- sample(n_ave, n_ave, replace = T)
  ftsm_100 <- flux_ton.s_mat[,idx_100]
  q_100 <- q_mat[, idx_100]

  # Get index for the columns corresponding to the same year
  index_years <- lapply(unique_years, function(y){which(avenelles_w$year[idx_100] == y)}) # list of indices corresponding to each year

  # Annual flux
  sum_instant_flux_ton.y_100 <- lapply(index_years, FUN = function(idx){apply(ftsm_100[,idx], 1, sum, na.rm = T)}) %>% do.call("cbind",.) # sum of fluxes per year, for each iteration of the bootstrap. Result is a matrix with nrow_boot rows and  (1 column per year)
  sum_instant_q_100 <- sapply(index_years, function(idx){apply(q_100[,idx], 1, sum, na.rm = T)}) # sum of discharge per year, for each iteration of the bootstrap. Result is a matrix with nrow_boot rows and 1 columns per year
  mean_instant_q_100 <- sapply(index_years, function(idx){apply(q_100[,idx], 1, mean, na.rm = T)}) # mean discharge per year
  
  weighted_annual_flux_ton.y_100 <- sum_instant_flux_ton.y_100 / sum_instant_q_100 * mean_instant_q_100 * 60 * 60 * 24 *365 # period is a number of hours, converted to day
  
  waf_100[[i]] <- weighted_annual_flux_ton.y_100
}

```

```{r 100-percent-mean}
wiaf_100 <- lapply(waf_100, rowMeans) # 100 moyennes interannuelles resampled, avec 1000 simulations montecarlo 

wiaf_100_mean <- lapply(wiaf_100, mean) %>% unlist()
wiaf_100_sd <- lapply(wiaf_100, sd) %>% unlist()
wiaf_100_upr <- lapply(wiaf_100, quantile, 0.975) %>% unlist()
wiaf_100_lwr <- lapply(wiaf_100, quantile, 0.025) %>% unlist()

```


## Compare weighted fluxes

The "error" represents the range in which resampled interannual mean fall. Max value = 97.5% quantile of the 100 resampled means; minimum value = 2.5% quantile of the 100 resampled means; median value = median value of the 100 resampled means. 

```{r compare-weighted-fluxes}
error_10_mean <- mean((wiaf_10_mean - interannual_flux_ton.y)/interannual_flux_ton.y * 100)
error_10_median <- median((wiaf_10_mean - interannual_flux_ton.y)/interannual_flux_ton.y * 100)
error_10_mean_min <- min((wiaf_10_mean - interannual_flux_ton.y)/interannual_flux_ton.y * 100)
error_10_mean_max <- max((wiaf_10_mean - interannual_flux_ton.y)/interannual_flux_ton.y * 100)
error_10_upr <- max((wiaf_10_upr - interannual_flux_pi[3])/interannual_flux_pi[3] * 100)
error_10_lwr <- min((wiaf_10_lwr - interannual_flux_pi[1])/interannual_flux_pi[1] * 100)

error_20_mean <- mean((wiaf_20_mean - interannual_flux_ton.y)/interannual_flux_ton.y * 100)
error_20_median <- median((wiaf_20_mean - interannual_flux_ton.y)/interannual_flux_ton.y * 100)
error_20_mean_min <- min((wiaf_20_mean - interannual_flux_ton.y)/interannual_flux_ton.y * 100)
error_20_mean_max <- max((wiaf_20_mean - interannual_flux_ton.y)/interannual_flux_ton.y * 100)
error_20_upr <- max((wiaf_20_upr - interannual_flux_pi[3])/interannual_flux_pi[3] * 100)
error_20_lwr <- min((wiaf_20_lwr - interannual_flux_pi[1])/interannual_flux_pi[1] * 100)


error_30_mean <- mean((wiaf_30_mean - interannual_flux_ton.y)/interannual_flux_ton.y * 100)
error_30_median <- median((wiaf_30_mean - interannual_flux_ton.y)/interannual_flux_ton.y * 100)
error_30_mean_min <- min((wiaf_30_mean - interannual_flux_ton.y)/interannual_flux_ton.y * 100)
error_30_mean_max <- max((wiaf_30_mean - interannual_flux_ton.y)/interannual_flux_ton.y * 100)
error_30_upr <- max((wiaf_30_upr - interannual_flux_pi[3])/interannual_flux_pi[3] * 100)
error_30_lwr <- min((wiaf_30_lwr - interannual_flux_pi[1])/interannual_flux_pi[1] * 100)

error_40_mean <- mean((wiaf_40_mean - interannual_flux_ton.y)/interannual_flux_ton.y * 100)
error_40_median <- median((wiaf_40_mean - interannual_flux_ton.y)/interannual_flux_ton.y * 100)
error_40_mean_min <- min((wiaf_40_mean - interannual_flux_ton.y)/interannual_flux_ton.y * 100)
error_40_mean_max <- max((wiaf_40_mean - interannual_flux_ton.y)/interannual_flux_ton.y * 100)
error_40_upr <- max((wiaf_40_upr - interannual_flux_pi[3])/interannual_flux_pi[3] * 100)
error_40_lwr <- min((wiaf_40_lwr - interannual_flux_pi[1])/interannual_flux_pi[1] * 100)

error_50_mean <- mean((wiaf_50_mean - interannual_flux_ton.y)/interannual_flux_ton.y * 100)
error_50_median <- median((wiaf_50_mean - interannual_flux_ton.y)/interannual_flux_ton.y * 100)
error_50_mean_min <- min((wiaf_50_mean - interannual_flux_ton.y)/interannual_flux_ton.y * 100)
error_50_mean_max <- max((wiaf_50_mean - interannual_flux_ton.y)/interannual_flux_ton.y * 100)
error_50_upr <- max((wiaf_50_upr - interannual_flux_pi[3])/interannual_flux_pi[3] * 100)
error_50_lwr <- min((wiaf_50_lwr - interannual_flux_pi[1])/interannual_flux_pi[1] * 100)

error_60_mean <- mean((wiaf_60_mean - interannual_flux_ton.y)/interannual_flux_ton.y * 100)
error_60_median <- median((wiaf_60_mean - interannual_flux_ton.y)/interannual_flux_ton.y * 100)
error_60_mean_min <- min((wiaf_60_mean - interannual_flux_ton.y)/interannual_flux_ton.y * 100)
error_60_mean_max <- max((wiaf_60_mean - interannual_flux_ton.y)/interannual_flux_ton.y * 100)
error_60_upr <- max((wiaf_60_upr - interannual_flux_pi[3])/interannual_flux_pi[3] * 100) 
error_60_lwr <- min((wiaf_60_lwr - interannual_flux_pi[1])/interannual_flux_pi[1] * 100)

error_70_mean <- mean((wiaf_70_mean - interannual_flux_ton.y)/interannual_flux_ton.y * 100)
error_70_median <- median((wiaf_70_mean - interannual_flux_ton.y)/interannual_flux_ton.y * 100)
error_70_mean_min <- min((wiaf_70_mean - interannual_flux_ton.y)/interannual_flux_ton.y * 100)
error_70_mean_max <- max((wiaf_70_mean - interannual_flux_ton.y)/interannual_flux_ton.y * 100)
error_70_upr <- max((wiaf_70_upr - interannual_flux_pi[3])/interannual_flux_pi[3] * 100)
error_70_lwr <- min((wiaf_70_lwr - interannual_flux_pi[1])/interannual_flux_pi[1] * 100)

error_80_mean <- mean((wiaf_80_mean - interannual_flux_ton.y)/interannual_flux_ton.y * 100)
error_80_median <- median((wiaf_80_mean - interannual_flux_ton.y)/interannual_flux_ton.y * 100)
error_80_mean_min <- min((wiaf_80_mean - interannual_flux_ton.y)/interannual_flux_ton.y * 100)
error_80_mean_max <- max((wiaf_80_mean - interannual_flux_ton.y)/interannual_flux_ton.y * 100)
error_80_upr <- max((wiaf_80_upr - interannual_flux_pi[3])/interannual_flux_pi[3] * 100)
error_80_lwr <- min((wiaf_80_lwr - interannual_flux_pi[1])/interannual_flux_pi[1] * 100)

error_90_mean <- mean((wiaf_90_mean - interannual_flux_ton.y)/interannual_flux_ton.y * 100)
error_90_median <- median((wiaf_90_mean - interannual_flux_ton.y)/interannual_flux_ton.y * 100)
error_90_mean_min <- min((wiaf_90_mean - interannual_flux_ton.y)/interannual_flux_ton.y * 100)
error_90_mean_max <- max((wiaf_90_mean - interannual_flux_ton.y)/interannual_flux_ton.y * 100)
error_90_upr <- max((wiaf_90_upr - interannual_flux_pi[3])/interannual_flux_pi[3] * 100)
error_90_lwr <- min((wiaf_90_lwr - interannual_flux_pi[1])/interannual_flux_pi[1] * 100)

error_100_mean <- mean((wiaf_100_mean - interannual_flux_ton.y)/interannual_flux_ton.y * 100)
error_100_median <- median((wiaf_100_mean - interannual_flux_ton.y)/interannual_flux_ton.y * 100)
error_100_mean_min <- min((wiaf_100_mean - interannual_flux_ton.y)/interannual_flux_ton.y * 100)
error_100_mean_max <- max((wiaf_100_mean - interannual_flux_ton.y)/interannual_flux_ton.y * 100)
error_100_upr <- max((wiaf_100_upr - interannual_flux_pi[3])/interannual_flux_pi[3] * 100)
error_100_lwr <- min((wiaf_100_lwr - interannual_flux_pi[1])/interannual_flux_pi[1] * 100)



weighted_error <- data.frame(percent_data = factor(c("10","20","30","40","50","60","70","80","90","100"),
                                          levels = c("10","20","30","40","50","60","70","80","90","100")),
                    error_mean = c(error_10_mean, error_20_mean, error_30_mean, error_40_mean, error_50_mean, error_60_mean, error_70_mean, error_80_mean, error_90_mean, error_100_mean),
                    error_median = c(error_10_median, error_20_median, error_30_median, error_40_median, error_50_median, error_60_median, error_70_median, error_80_median, error_90_median, error_100_median),
                    error_mean_min = c(error_10_mean_min, error_20_mean_min, error_30_mean_min, error_40_mean_min, error_50_mean_min, error_60_mean_min, error_70_mean_min, error_80_mean_min, error_90_mean_min, error_100_mean_min),
                    error_mean_max = c(error_10_mean_max, error_20_mean_max, error_30_mean_max, error_40_mean_max, error_50_mean_max, error_60_mean_max, error_70_mean_max, error_80_mean_max, error_90_mean_max, error_100_mean_max),
                    pi_upr = c(error_10_upr, error_20_upr, error_30_upr, error_40_upr, error_50_upr, error_60_upr, error_70_upr, error_80_upr, error_90_upr, error_100_upr),
                    pi_lwr = c(error_10_lwr, error_20_lwr, error_30_lwr, error_40_lwr, error_50_lwr, error_60_lwr, error_70_lwr, error_80_lwr, error_90_lwr, error_100_lwr)) %>%
  mutate(pi_range = pi_upr - pi_lwr)

ggplot(data= weighted_error, aes(x = percent_data))+
  geom_point(aes(y = error_mean))+
  geom_errorbar(aes(ymin = error_mean_min, ymax = error_mean_max, col = "mean range"))+
  labs(title = "Mean of resampled error and its standard deviation")+
  theme_minimal(base_size = 15)

ggplot(data= weighted_error, aes(x = percent_data))+
  geom_point(aes(y = error_median))+
 geom_errorbar(aes(ymin = pi_lwr, ymax = pi_upr, col = "Prediction interval range"))+
  labs(title = "Range of prediction intervals, median of resampled errors")+
  theme_minimal(base_size = 15)

ggplot(data= weighted_error, aes(x = percent_data))+
  geom_point(aes(y = error_mean))+
 geom_errorbar(aes(ymin = pi_lwr, ymax = pi_upr, col = "Prediction interval range"))+
  labs(title = "Range of prediction intervals, mean of resampled errors")+
  theme_minimal(base_size = 15)


weighted_error %>% knitr::kable(digits = 2, row.names = F) %>% kableExtra::kable_styling()
```


















