---
title: "Arles"
output:
  html_document:
    toc: true
    toc_float: true
    number_sections: true
    code_folding: hide
date: "2025-06-06"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = F, warning = F, error = F, fig.align = "center", collapse = T,
                      cache = T)
```

```{r libraries, cache = F}
library(ggplot2)
library(ggpubr)

library(dplyr)
library(readxl)
library(lubridate)

library(nlme)
```

# Load data

```{r prepare-data}
arles <- read_xlsx("arles.xlsx", sheet = "clean_data", col_types = c("date","text",rep("numeric",18))) 
arles$year <- year(arles$Date)
arles$month <- month(arles$Date)
arles$week <- week(arles$Date)

arles$Date <- as.Date(arles$Date)
arles$commondate <- as.Date(paste0("2000-", format(arles$Date,"%j")), "%Y-%j")
arles$period <- with(arles, end-start) # donne la périod en heure

arles$poc_mg.L <- with(arles, poc_umol.L*1e-3/12.011)
arles$poc_percent <- with(arles, poc_mg.L/mes_mg.L)
arles$doc_mg.L <- with(arles, doc_umol.L*1e-3/12.011)

bv <- 95590
```

```{r summary-data}
summary_arles <- merge(
arles %>% subset(!is.na(doc_mg.L)) %>% group_by(year) %>% summarise(nb_doc = n()),
arles %>% subset(!is.na(q_m3.s)) %>% group_by(year) %>% summarise(nb_q = n()), by = "year", all = T) %>% 
  merge(arles %>% subset(!is.na(period) & !is.na(q_m3.s) & !is.na(doc_mg.L)) %>% group_by(year) %>% summarise(total_period_j_nona = round(sum(period)/24)), by = "year", all = T)

knitr::kable(summary_arles) %>% kableExtra::kable_styling()

cat("mean Q", mean(arles$q_m3.s, na.rm = T))
cat("range OC (0-25-50-75-100)", quantile(with(arles, doc_mg.L), na.rm = T))
```



# View data

```{r plot-by-year-doc, fig.dim = c(15,15)}
n <- 100000

ggarrange(
ggplot(subset(arles, year %in% c(2007:2007)), aes(x = commondate))+
  geom_point(aes(y = q_m3.s, col = "Débit, m3/s"), alpha = 0.5)+
  scale_x_date(labels = function(x) format(x, "%d-%b"), date_minor_breaks = "1 month", name = "")+
  scale_color_manual(values = c("lightblue"), name = "")+
  facet_grid(rows = vars(year))+
  labs(y = "Débit, m3/s", col = "")+
  theme_minimal(base_size = 15)+
  theme(legend.position = "none"),

ggplot(subset(arles, year %in% c(2007:2007)), aes(x = commondate))+
  geom_point(aes(y = doc_mg.L, col = "DOC, mg.L"), alpha = 0.5)+
  scale_x_date(labels = function(x) format(x, "%d-%b"), date_minor_breaks = "1 month", name = "")+
  scale_color_manual(values = c("palegreen4"), name = "")+
  facet_grid(rows = vars(year))+
  labs(y = "DOC, mg/L", col = "")+
  theme_minimal(base_size = 15)+
  theme(legend.position = "none")
)
```

# Annual and interannual flux 

On considère que l'erreur sur DOC vient de la mesure par analyse TOC.

```{r constant-numbers}
complete_years <- c(2007,2008,2009)
nyears <- length(complete_years)

arles_flux <- arles %>% filter(year %in% complete_years)


q_u <- 0.1

nobs <- dim(arles_flux)[1]
nrep <- 1000
```

## Total flux 

```{r compute-flux}
#doc matrix
doc_meas <- matrix(arles_flux$doc_mg.L, nrow = nrep, ncol = nobs, byrow = T) # repeats nrep lines with observations

doc_cv <- 3.2*doc_meas^(-0.2) # from quich check Claire, vaut pour TOC mais pas autres moyens de mesure
doc_random <- matrix(rnorm(nrep*nobs, mean = 0, sd = 1), nrow=nrep, ncol = nobs)
doc_noise <- doc_cv*doc_random
doc_mat <- doc_meas * (1 + doc_noise/100) # final value of doc, with noise in percent

# Q matrix
q_meas <- matrix(arles_flux$q_m3.s, nrow = nrep, ncol = nobs, byrow = T) # repeats nrow_boot times the vector arles_for_gnls$q_m3.s
q_noise <- matrix(rnorm(nrep*nobs, mean = 0, sd = q_u), nrow = nrep, ncol = nobs) # creates a noise in percent (proportion), between 0 and 10%
q_mat <- q_meas * (1 + q_noise) # final value of q, with noise

# period mat
period_mat <- matrix(arles_flux$period, nrow = nrep, ncol = nobs, byrow = T) # in hours

# Flux per time step
flux_ton_mat <- doc_mat*1e-9*q_mat*1e3*period_mat*60*60 # flux per period (period in hours, so flux in ton/s is converted to flux per period. Period in days
flux_ton.s_mat <- doc_mat*1e-9*q_mat*1e3 # without period

index_years <- lapply(complete_years, function(y){which(arles_flux$year == y)}) # list of indices corresponding to each year

# Annual flux
annual_flux_ton.y <- sapply(index_years, function(idx){apply(flux_ton_mat[,idx], 1, sum, na.rm = T)}) # sum of fluxes per year, for each iteration of the bootstrap. Result is a matrix with nrow_boot rows and 19 columns (1 per year)
annual_flux_pi <- apply(annual_flux_ton.y, 2, quantile, probs = c(0.025, 0.5, 0.975), na.rm = T) # prediction interval for annual fluxes, per year. 3 lignes, 19 columns
annual_flux_mean <- colMeans(annual_flux_ton.y, na.rm = T) # mean annual flux per year. 1 vector
annual_flux_sd <- apply(annual_flux_ton.y, 2, sd, na.rm = T) # standard deviation of annual flux per year. Is just an estimate of goodness of mean, not as good as than the confidence interval. 

annual_flux_df <- data.frame(year = complete_years, 
                        annual_flux_mean = annual_flux_mean, 
                        annual_flux_variability = annual_flux_sd, 
                        annual_flux_pi_lower = annual_flux_pi[1,], 
                        annual_flux_pi_upper = annual_flux_pi[3,])

# Interannual fluxes
interannual_flux_ton.y <- rowMeans(annual_flux_ton.y, na.rm = T) # mean interannual flux per iteration of the bootstrap
interannual_flux_pi <- quantile(interannual_flux_ton.y, probs = c(0.025, 0.5, 0.975), na.rm = T) # prediction interval
interannual_flux_mean <- mean(interannual_flux_ton.y, na.rm = T) # mean interannual flux
interannual_flux_variability <- sd(annual_flux_mean, na.rm = T) # standard deviation of interannual flux per year

interannual_flux_df <- data.frame(year = "interannual", annual_flux_mean = interannual_flux_mean, 
                                  annual_flux_variability = interannual_flux_variability,
                        annual_flux_pi_lower = interannual_flux_pi[1], 
                        annual_flux_pi_upper = interannual_flux_pi[3])

total_flux_df <- rbind(annual_flux_df, interannual_flux_df)
total_flux_df$group <- c(rep("annual", nyears), "interannual")

ggplot()+
  geom_col(data = total_flux_df, aes(x=year, y = annual_flux_mean, fill = group))+
    geom_errorbar(data = total_flux_df, aes(x = year, ymin = annual_flux_pi_lower, ymax = annual_flux_pi_upper, col = "prediction interval"), width = 0.3, size = 0.8)+
  geom_errorbar(data = filter(total_flux_df, year == "interannual"), aes(x = year, ymin = annual_flux_mean - annual_flux_variability, ymax = annual_flux_mean + annual_flux_variability, col = "interannual variability"), width = 0.2, size = 0.8, linetype = 2)+
  scale_fill_manual(values = c("annual" = "lightblue", "interannual" = "indianred"))+
  scale_color_manual(values = c("prediction interval" = "darkblue", "interannual variability" = "darkred"), name = "")+
   labs(x = "Year", y = "Flux (ton/year)", fill = "")+
  theme_minimal(base_size = 15)+
  theme(axis.text.x = element_text(angle = 45, hjust = 1), legend.position = "bottom")

knitr::kable(total_flux_df, digits = 2, row.names = F) %>% kableExtra::kable_styling()

```

## Specific flux

```{r specific-flux}
sflux_ton_mat <- doc_mat*1e-9*q_mat*1e3*period_mat*60*60/bv # flux per period (period in seconds, so flux in ton/s is converted to flux per period). 
sflux_ton.s_mat <- doc_mat*1e-9*q_mat*1e3/bv # without period

annual_sflux_ton.y <- sapply(index_years, function(idx){apply(sflux_ton_mat[,idx], 1, sum, na.rm = T)}) # sum of fluxes per year, for each iteration of the bootstrap. Result is a matrix with nrow_boot rows and 19 columns (1 per year)
annual_sflux_pi <- apply(annual_sflux_ton.y, 2, quantile, probs = c(0.025, 0.5, 0.975), na.rm = T) # prediction interval for annual fluxes, per year. 3 lignes, 19 columns
annual_sflux_mean <- colMeans(annual_sflux_ton.y, na.rm = T) # mean annual flux per year. 1 vector
annual_sflux_sd <- apply(annual_sflux_ton.y, 2, sd, na.rm = T) # standard deviation of annual flux per year. Is just an estimate of goodness of mean, not as good as than the confidence interval. 

annual_sflux_df <- data.frame(year = complete_years, 
                        annual_flux_mean = annual_sflux_mean, 
                        annual_flux_variability = annual_sflux_sd, 
                        annual_flux_pi_lower = annual_sflux_pi[1,], 
                        annual_flux_pi_upper = annual_sflux_pi[3,])

# Interannual flux 
interannual_sflux_ton.y <- rowMeans(annual_sflux_ton.y, na.rm = T) # mean interannual flux per iteration of the bootstrap
interannual_sflux_pi <- quantile(interannual_sflux_ton.y, probs = c(0.025, 0.5, 0.975), na.rm = T) # prediction interval
interannual_sflux_mean <- mean(interannual_sflux_ton.y, na.rm = T) # mean interannual flux
interannual_sflux_variability <- sd(annual_sflux_mean, na.rm = T) # standard deviation of interannual flux per year

interannual_sflux_df <- data.frame(year = "interannual", annual_flux_mean = interannual_sflux_mean, 
                                  annual_flux_variability = interannual_sflux_variability,
                        annual_flux_pi_lower = interannual_sflux_pi[1], 
                        annual_flux_pi_upper = interannual_sflux_pi[3])

total_sflux_df <- rbind(annual_sflux_df, interannual_sflux_df)
total_sflux_df$group <- c(rep("annual", nyears), "interannual")

ggplot()+
  geom_col(data = total_sflux_df, aes(x=year, y = annual_flux_mean, fill = group), width = 0.8)+
    geom_errorbar(data = total_sflux_df, aes(x = year, ymin = annual_flux_pi_lower, ymax = annual_flux_pi_upper, col = "prediction interval"), width = 0.3, size = 0.8)+
  geom_errorbar(data = filter(total_sflux_df, year == "interannual"), aes(x = year, ymin = annual_flux_mean - annual_flux_variability, ymax = annual_flux_mean + annual_flux_variability, col = "interannual variability"), width = 0.2, size = 0.8, linetype = 2)+
  scale_fill_manual(values = c("annual" = "lightblue", "interannual" = "indianred"))+
  scale_color_manual(values = c("prediction interval" = "darkblue", "interannual variability" = "darkred"), name = "")+
   labs(x = "Year", y = "Flux (tons/km2/year)", fill = "")+
  theme_minimal(base_size = 15)+
  theme(axis.text.x = element_text(angle = 45, hjust = 1), legend.position = "bottom")

knitr::kable(total_sflux_df, digits = 6, row.names = F) %>% kableExtra::kable_styling()

ggsave("sflux_arles.svg")
```


```{r load-cache-specific-flux, eval = F}
list.files("arles_test_methode_cache/html/")
load_cache(label = "specific-flux", path = "arles_test_methode_cache/html/", envir = .GlobalEnv)
load("arles_test_method_cache/html/specific-flux_c3fe67b272eba528eebc27dbdf147908.RData")

```

# Time steps

Fluxes calculated as SPECIFIC -> divided by BV

```{r common-data-timestep}
arles_time <- arles_flux %>% select(c("Date", "period","doc_mg.L","q_m3.s"))
```


## 2 Days

```{r arles-day2, cache.lazy = F}
# prepare df
arles_group_day2 <- arles_time %>% mutate(day2 = floor(as.numeric(Date - min(Date)) / 2), year = year(Date)) %>% group_by(day2,year) # group arles_time by day
nrow_day2 <- n_groups(arles_group_day2)

# creates matrix for DOC
arles_doc_day2 <- arles_group_day2 %>% select(c("day2", "doc_mg.L","Date")) %>% summarize("list_doc" = list(doc_mg.L), "Date" = mean(Date)) %>% ungroup() # creates a list of mes for each day2
doc_random_day2 <- replicate(nrep, sapply(arles_doc_day2$list_doc, function(x) sample(x,1)))%>% t() # matrix of mes: one random sample per day2, replicated 1000 times

doc_cv_day2 <- 3.2*doc_random_day2^(-0.2)
rnorm_day2 <- matrix(rnorm(nrep*nrow_day2, mean = 0, sd = 1), nrow=nrep, ncol = nrow_day2)
doc_noise_day2 <- doc_cv_day2*rnorm_day2
doc_mat_day2 <- doc_random_day2 * (1 + doc_noise_day2/100) # final value of doc, with noise in percent

# matrix for q
q_day2 <- arles_group_day2 %>% select(c("day2", "q_m3.s")) %>% summarize_all(list("q_mean" = mean, "q_sd" = sd)) %>% ungroup() # mean of Q for each day2

q_day2_mean <-  matrix(q_day2$q_mean, nrow = nrep, ncol = nrow_day2, byrow = T)
q_noise <- matrix(rnorm(nrep*nrow_day2, mean = 0, sd = q_u), nrow = nrep, ncol = nrow_day2) # creates a noise in percent (proportion), between 0 and 10%
q_mat_day2 <- q_day2_mean * (1 + q_noise) # final MC of q, with noise. SD NOT INCLUDED: will not always be available

# period
arles_doc_day2$period <- with(arles_doc_day2, as.numeric(-(Date- lead(Date)))) # period is calculated in days
period_mat_day2 <- matrix(arles_doc_day2$period, nrow = nrep, ncol = nrow_day2, byrow = T)


# compute flux
flux_ton_mat_day2 <- doc_mat_day2*1e-9*q_mat_day2*1e3*60*60*24*period_mat_day2 #pred_day2 * mes_mat : poc in mg/L converted to ton; q_mat converted from m3/s to L/s. Period : nb of seconds in 1 day2. 

# Get index for columns by year
index_years <- lapply(complete_years, function(y){which(arles_doc_day2$year == y)}) # list of indices corresponding to each year

# annual flux
annual_flux_ton.y_day2 <- lapply(index_years, function(idx){apply(flux_ton_mat_day2[,idx], 1, sum, na.rm = T)}) %>% do.call("cbind", .)# sum of fluxes per year, for each iteration of the bootstrap. 
annual_flux_day2_pi <- apply(annual_flux_ton.y_day2, 2, quantile, probs = c(0.025, 0.5, 0.975), na.rm = T) # confidence interval for annual fluxes, per year. 3 lignes, 19 columns
annual_flux_day2_mean <- colMeans(annual_flux_ton.y_day2, na.rm = T) # mean annual flux per year. 1 vector
annual_flux_day2_sd <- apply(annual_flux_ton.y_day2, 2, sd, na.rm = T) # standard deviation of annual flux per year. Is just an estimate of goodness of mean, not as good as than the confidence interval. 
 
annual_flux_day2_df <- data.frame(year = complete_years, 
                        annual_flux_mean = annual_flux_day2_mean, 
                        annual_flux_variability = annual_flux_day2_sd, 
                        annual_flux_pi_lower = annual_flux_day2_pi[1,], 
                        annual_flux_pi_upper = annual_flux_day2_pi[3,])

interannual_flux_ton.y_day2 <- rowMeans(annual_flux_ton.y_day2, na.rm = T) # mean interannual flux per iteration of the bootstrap
interannual_flux_pi_day2 <- quantile(interannual_flux_ton.y_day2, probs = c(0.025, 0.5, 0.975), na.rm = T) # prediction interval
interannual_flux_mean_day2 <- mean(interannual_flux_ton.y_day2, na.rm = T) # mean interannual flux
interannual_flux_variability_day2 <- sd(annual_flux_day2_mean, na.rm = T) # standard deviation of interannual flux per year

interannual_flux_day2_df <- data.frame(year = "interannual", annual_flux_mean = interannual_flux_mean_day2, 
                                  annual_flux_variability = interannual_flux_variability_day2,
                        annual_flux_pi_lower = interannual_flux_pi_day2[1], 
                        annual_flux_pi_upper = interannual_flux_pi_day2[3])

total_flux_day2_df <- rbind(annual_flux_day2_df, interannual_flux_day2_df)
total_flux_day2_df$group <- c(rep("annual", nyears), "interannual")

ggplot()+
  geom_col(data = total_flux_day2_df, aes(x=year, y = annual_flux_mean, fill = group))+
    geom_errorbar(data = total_flux_day2_df, aes(x = year, ymin = annual_flux_pi_lower, ymax = annual_flux_pi_upper, col = "prediction interval"), width = 0.3, size = 0.8)+
  geom_errorbar(data = filter(total_flux_day2_df, year == "interannual"), aes(x = year, ymin = annual_flux_mean - annual_flux_variability, ymax = annual_flux_mean + annual_flux_variability, col = "interannual variability"), width = 0.2, size = 0.8, linetype = 2)+
  scale_fill_manual(values = c("annual" = "lightblue", "interannual" = "indianred"))+
  scale_color_manual(values = c("prediction interval" = "darkblue", "interannual variability" = "darkred"), name = "")+
   labs(x = "Year", y = "Flux, from bi-dayly mean values (ton/year)", fill = "")+
  theme_minimal(base_size = 15)+
  theme(axis.text.x = element_text(angle = 45, hjust = 1), legend.position = "bottom")

knitr::kable(total_flux_day2_df, digits = 6, row.names = F) %>% kableExtra::kable_styling()
```

```{r specific-arles-day2, cache.lazy = F}
# compute flux
sflux_ton_mat_day2 <- doc_mat_day2*1e-9*q_mat_day2*1e3*60*60*24*period_mat_day2/bv #doc in mg/L converted to ton; q_mat converted from m3/s to L/s. Period : in days. 

# Get index for columns by year
index_years <- lapply(complete_years, function(y){which(arles_doc_day2$year == y)}) # list of indices corresponding to each year

# annual flux
annual_sflux_ton.y_day2 <- lapply(index_years, function(idx){apply(sflux_ton_mat_day2[,idx], 1, sum, na.rm = T)}) %>% do.call("cbind", .)# sum of fluxes per year, for each iteration of the bootstrap. 
annual_sflux_day2_pi <- apply(annual_sflux_ton.y_day2, 2, quantile, probs = c(0.025, 0.5, 0.975), na.rm = T) # confidence interval for annual fluxes, per year. 3 lignes, 19 columns
annual_sflux_day2_mean <- colMeans(annual_sflux_ton.y_day2, na.rm = T) # mean annual flux per year. 1 vector
annual_sflux_day2_sd <- apply(annual_sflux_ton.y_day2, 2, sd, na.rm = T) # standard deviation of annual flux per year. Is just an estimate of goodness of mean, not as good as than the confidence interval. 
 
annual_sflux_day2_df <- data.frame(year = complete_years, 
                        annual_flux_mean = annual_sflux_day2_mean, 
                        annual_flux_variability = annual_sflux_day2_sd, 
                        annual_flux_pi_lower = annual_sflux_day2_pi[1,], 
                        annual_flux_pi_upper = annual_sflux_day2_pi[3,])

interannual_sflux_ton.y_day2 <- rowMeans(annual_sflux_ton.y_day2, na.rm = T) # mean interannual flux per iteration of the bootstrap
interannual_sflux_pi_day2 <- quantile(interannual_sflux_ton.y_day2, probs = c(0.025, 0.5, 0.975), na.rm = T) # prediction interval
interannual_sflux_mean_day2 <- mean(interannual_sflux_ton.y_day2, na.rm = T) # mean interannual flux
interannual_sflux_variability_day2 <- sd(annual_sflux_day2_mean, na.rm = T) # standard deviation of interannual flux per year

interannual_sflux_day2_df <- data.frame(year = "interannual", annual_flux_mean = interannual_sflux_mean_day2, 
                                  annual_flux_variability = interannual_sflux_variability_day2,
                        annual_flux_pi_lower = interannual_sflux_pi_day2[1], 
                        annual_flux_pi_upper = interannual_sflux_pi_day2[3])

total_sflux_day2_df <- rbind(annual_sflux_day2_df, interannual_sflux_day2_df)
total_sflux_day2_df$group <- c(rep("annual", nyears), "interannual")

ggplot()+
  geom_col(data = total_sflux_day2_df, aes(x=year, y = annual_flux_mean, fill = group))+
    geom_errorbar(data = total_sflux_day2_df, aes(x = year, ymin = annual_flux_pi_lower, ymax = annual_flux_pi_upper, col = "prediction interval"), width = 0.3, size = 0.8)+
  geom_errorbar(data = filter(total_sflux_day2_df, year == "interannual"), aes(x = year, ymin = annual_flux_mean - annual_flux_variability, ymax = annual_flux_mean + annual_flux_variability, col = "interannual variability"), width = 0.2, size = 0.8, linetype = 2)+
  scale_fill_manual(values = c("annual" = "lightblue", "interannual" = "indianred"))+
  scale_color_manual(values = c("prediction interval" = "darkblue", "interannual variability" = "darkred"), name = "")+
   labs(x = "Year", y = "Flux, from bi-dayly mean values (tons/km2/year)", fill = "")+
  theme_minimal(base_size = 15)+
  theme(axis.text.x = element_text(angle = 45, hjust = 1), legend.position = "bottom")

knitr::kable(total_sflux_day2_df, digits = 6, row.names = F) %>% kableExtra::kable_styling()
```

## 4 Days 

```{r arles-day4, cache.lazy = F}
# prepare df
arles_group_day4 <- arles_time %>% mutate(day4 = floor(as.numeric(Date - min(Date)) / 4), year = year(Date), DateHeure = NULL) %>% group_by(day4,year) # group arles_time by day
nrow_day4 <- n_groups(arles_group_day4)



# creates matrix for DOC
arles_doc_day4 <- arles_group_day4 %>% select(c("day4", "doc_mg.L","Date")) %>% summarize("list_doc" = list(doc_mg.L), "Date" = mean(Date)) %>% ungroup() # creates a list of mes for each day4
doc_random_day4 <- replicate(nrep, sapply(arles_doc_day4$list_doc, function(x) sample(x,1)))%>% t() # matrix of mes: one random sample per day4, replicated 1000 times
# doc_day4_noise <- matrix(rnorm(nrep*nrow_day4, mean = 0, sd = doc_u), nrow = nrep, ncol = nrow_day4) 
# doc_mat_day4 <- doc_day4_random * (1 + doc_day4_noise) # final value of mes, with noise
# 
# doc_mean <- colMeans(doc_mat_day4)

doc_cv_day4 <- 3.2*doc_random_day4^(-0.2)
rnorm_day4 <- matrix(rnorm(nrep*nrow_day4, mean = 0, sd = 1), nrow=nrep, ncol = nrow_day4)
doc_noise_day4 <- doc_cv_day4*rnorm_day4
doc_mat_day4 <- doc_random_day4 * (1 + doc_noise_day4/100) # final value of doc, with noise in percent



# matrix for q
q_day4 <- arles_group_day4 %>% select(c("day4", "q_m3.s")) %>% summarize_all(list("q_mean" = mean, "q_sd" = sd)) %>% ungroup() # mean of Q for each day4

q_day4_mean <-  matrix(q_day4$q_mean, nrow = nrep, ncol = nrow_day4, byrow = T)
q_noise <- matrix(rnorm(nrep*nrow_day4, mean = 0, sd = q_u), nrow = nrep, ncol = nrow_day4) # creates a noise in percent (proportion), between 0 and 10%
q_mat_day4 <- q_day4_mean * (1 + q_noise) # final MC of q, with noise. SD NOT INCLUDED: will not always be available

# period mat
# period
arles_doc_day4$period <- with(arles_doc_day4, as.numeric(-(Date- lead(Date)))) # period is calculated in days
period_mat_day4 <- matrix(arles_doc_day4$period, nrow = nrep, ncol = nrow_day4, byrow = T)


# compute flux
flux_ton_mat_day4 <- doc_mat_day4*1e-9*q_mat_day4*1e3*60*60*24*period_mat_day4 #doc in mg/L converted to ton; q_mat converted from m3/s to L/s. Period : nb of seconds in 1 day4. 

# Get index for columns by year
index_years <- lapply(complete_years, function(y){which(arles_doc_day4$year == y)}) # list of indices corresponding to each year

# annual flux
annual_flux_ton.y_day4 <- lapply(index_years, function(idx){apply(flux_ton_mat_day4[,idx], 1, sum, na.rm = T)}) %>% do.call("cbind", .)# sum of fluxes per year, for each iteration of the bootstrap. 
annual_flux_day4_pi <- apply(annual_flux_ton.y_day4, 2, quantile, probs = c(0.025, 0.5, 0.975), na.rm = T) # confidence interval for annual fluxes, per year. 3 lignes, 19 columns
annual_flux_day4_mean <- colMeans(annual_flux_ton.y_day4, na.rm = T) # mean annual flux per year. 1 vector
annual_flux_day4_sd <- apply(annual_flux_ton.y_day4, 2, sd, na.rm = T) # standard deviation of annual flux per year. Is just an estimate of goodness of mean, not as good as than the confidence interval. 
 
annual_flux_day4_df <- data.frame(year = complete_years, 
                        annual_flux_mean = annual_flux_day4_mean, 
                        annual_flux_variability = annual_flux_day4_sd, 
                        annual_flux_pi_lower = annual_flux_day4_pi[1,], 
                        annual_flux_pi_upper = annual_flux_day4_pi[3,])

interannual_flux_ton.y_day4 <- rowMeans(annual_flux_ton.y_day4, na.rm = T) # mean interannual flux per iteration of the bootstrap
interannual_flux_pi_day4 <- quantile(interannual_flux_ton.y_day4, probs = c(0.025, 0.5, 0.975), na.rm = T) # prediction interval
interannual_flux_mean_day4 <- mean(interannual_flux_ton.y_day4, na.rm = T) # mean interannual flux
interannual_flux_variability_day4 <- sd(annual_flux_day4_mean, na.rm = T) # standard deviation of interannual flux per year

interannual_flux_day4_df <- data.frame(year = "interannual", annual_flux_mean = interannual_flux_mean_day4, 
                                  annual_flux_variability = interannual_flux_variability_day4,
                        annual_flux_pi_lower = interannual_flux_pi_day4[1], 
                        annual_flux_pi_upper = interannual_flux_pi_day4[3])

total_flux_day4_df <- rbind(annual_flux_day4_df, interannual_flux_day4_df)
total_flux_day4_df$group <- c(rep("annual", nyears), "interannual")

ggplot()+
  geom_col(data = total_flux_day4_df, aes(x=year, y = annual_flux_mean, fill = group))+
    geom_errorbar(data = total_flux_day4_df, aes(x = year, ymin = annual_flux_pi_lower, ymax = annual_flux_pi_upper, col = "prediction interval"), width = 0.3, size = 0.8)+
  geom_errorbar(data = filter(total_flux_day4_df, year == "interannual"), aes(x = year, ymin = annual_flux_mean - annual_flux_variability, ymax = annual_flux_mean + annual_flux_variability, col = "interannual variability"), width = 0.2, size = 0.8, linetype = 2)+
  scale_fill_manual(values = c("annual" = "lightblue", "interannual" = "indianred"))+
  scale_color_manual(values = c("prediction interval" = "darkblue", "interannual variability" = "darkred"), name = "")+
   labs(x = "Year", y = "Flux, from bi-dayly mean values (ton/year)", fill = "")+
  theme_minimal(base_size = 15)+
  theme(axis.text.x = element_text(angle = 45, hjust = 1), legend.position = "bottom")

knitr::kable(total_flux_day4_df, digits = 6, row.names = F) %>% kableExtra::kable_styling()
```

```{r specific-arles-day4}
# compute flux
sflux_ton_mat_day4 <- doc_mat_day4*1e-9*q_mat_day4*1e3*60*60*24*period_mat_day4/bv #pred_day4 * mes_mat : poc in mg/L converted to ton; q_mat converted from m3/s to L/s. Period : nb of seconds in 1 day4. 

# Get index for columns by year
index_years <- lapply(complete_years, function(y){which(arles_doc_day4$year == y)}) # list of indices corresponding to each year

# annual flux
annual_sflux_ton.y_day4 <- lapply(index_years, function(idx){apply(sflux_ton_mat_day4[,idx], 1, sum, na.rm = T)}) %>% do.call("cbind", .)# sum of fluxes per year, for each iteration of the bootstrap. 
annual_sflux_day4_pi <- apply(annual_sflux_ton.y_day4, 2, quantile, probs = c(0.025, 0.5, 0.975), na.rm = T) # confidence interval for annual fluxes, per year. 3 lignes, 19 columns
annual_sflux_day4_mean <- colMeans(annual_sflux_ton.y_day4, na.rm = T) # mean annual flux per year. 1 vector
annual_sflux_day4_sd <- apply(annual_sflux_ton.y_day4, 2, sd, na.rm = T) # standard deviation of annual flux per year. Is just an estimate of goodness of mean, not as good as than the confidence interval. 
 
annual_sflux_day4_df <- data.frame(year = complete_years, 
                        annual_flux_mean = annual_sflux_day4_mean, 
                        annual_flux_variability = annual_sflux_day4_sd, 
                        annual_flux_pi_lower = annual_sflux_day4_pi[1,], 
                        annual_flux_pi_upper = annual_sflux_day4_pi[3,])

interannual_sflux_ton.y_day4 <- rowMeans(annual_sflux_ton.y_day4, na.rm = T) # mean interannual flux per iteration of the bootstrap
interannual_sflux_pi_day4 <- quantile(interannual_sflux_ton.y_day4, probs = c(0.025, 0.5, 0.975), na.rm = T) # prediction interval
interannual_sflux_mean_day4 <- mean(interannual_sflux_ton.y_day4, na.rm = T) # mean interannual flux
interannual_sflux_variability_day4 <- sd(annual_sflux_day4_mean, na.rm = T) # standard deviation of interannual flux per year

interannual_sflux_day4_df <- data.frame(year = "interannual", annual_flux_mean = interannual_sflux_mean_day4, 
                                  annual_flux_variability = interannual_sflux_variability_day4,
                        annual_flux_pi_lower = interannual_sflux_pi_day4[1], 
                        annual_flux_pi_upper = interannual_sflux_pi_day4[3])

total_sflux_day4_df <- rbind(annual_sflux_day4_df, interannual_sflux_day4_df)
total_sflux_day4_df$group <- c(rep("annual", nyears), "interannual")

ggplot()+
  geom_col(data = total_sflux_day4_df, aes(x=year, y = annual_flux_mean, fill = group))+
    geom_errorbar(data = total_sflux_day4_df, aes(x = year, ymin = annual_flux_pi_lower, ymax = annual_flux_pi_upper, col = "prediction interval"), width = 0.3, size = 0.8)+
  geom_errorbar(data = filter(total_sflux_day4_df, year == "interannual"), aes(x = year, ymin = annual_flux_mean - annual_flux_variability, ymax = annual_flux_mean + annual_flux_variability, col = "interannual variability"), width = 0.2, size = 0.8, linetype = 2)+
  scale_fill_manual(values = c("annual" = "lightblue", "interannual" = "indianred"))+
  scale_color_manual(values = c("prediction interval" = "darkblue", "interannual variability" = "darkred"), name = "")+
   labs(x = "Year", y = "Flux, from bi-dayly mean values (tons/km2/year)", fill = "")+
  theme_minimal(base_size = 15)+
  theme(axis.text.x = element_text(angle = 45, hjust = 1), legend.position = "bottom")

knitr::kable(total_sflux_day4_df, digits = 6, row.names = F) %>% kableExtra::kable_styling()
```


## 1 week

```{r arles-week, cache.lazy = F}
# prepare df
arles_group_week <- arles_time %>% mutate("week" = week(Date), year = year(Date), DateHeure = NULL) %>% group_by(week,year) # group arles_time by week
nrow_week <- n_groups(arles_group_week)


# creates matrix for DOC
arles_doc_week <- arles_group_week %>% select(c("week", "doc_mg.L")) %>% summarize("list_doc" = list(doc_mg.L)) %>% ungroup() # creates a list of mes for each week
doc_random_week <- replicate(nrep, sapply(arles_doc_week$list_doc, function(x) sample(x,1)))%>% t() # matrix of mes: one random sample per week, replicated 1000 times
# doc_week_noise <- matrix(rnorm(nrep*nrow_week, mean = 0, sd = doc_u), nrow = nrep, ncol = nrow_week) 
# doc_mat_week <- doc_week_random * (1 + doc_week_noise) # final value of mes, with noise
# doc_mean <- colMeans(doc_mat_week)

doc_cv_week <- 3.2*doc_random_week^(-0.2)
rnorm_week <- matrix(rnorm(nrep*nrow_week, mean = 0, sd = 1), nrow=nrep, ncol = nrow_week)
doc_noise_week <- doc_cv_week*rnorm_week
doc_mat_week <- doc_random_week * (1 + doc_noise_week/100) # final value of doc, with noise in percent


# matrix for q
q_week <- arles_group_week %>% select(c("week", "q_m3.s")) %>% summarize_all(list("q_mean" = mean, "q_sd" = sd)) %>% ungroup() # mean of Q for each week

q_week_mean <-  matrix(q_week$q_mean, nrow = nrep, ncol = nrow_week, byrow = T)
q_noise <- matrix(rnorm(nrep*nrow_week, mean = 0, sd = q_u), nrow = nrep, ncol = nrow_week) # creates a noise in percent (proportion), between 0 and 10%
q_mat_week <- q_week_mean * (1 + q_noise) # final MC of q, with noise. SD NOT INCLUDED: will not always be available

# compute flux
flux_ton_mat_week <- doc_mat_week*1e-9*q_mat_week*1e3*60*60*24*7 #doc in mg/L converted to ton; q_mat converted from m3/s to L/s. Period : nb of seconds in 1 week. 

# Get index for columns by year
index_years <- lapply(complete_years, function(y){which(arles_doc_week$year == y)}) # list of indices corresponding to each year

# annual flux
annual_flux_ton.y_week <- lapply(index_years, function(idx){apply(flux_ton_mat_week[,idx], 1, sum, na.rm = T)}) %>% do.call("cbind", .) # sum of fluxes per year, for each iteration of the bootstrap. 
annual_flux_week_pi <- apply(annual_flux_ton.y_week, 2, quantile, probs = c(0.025, 0.5, 0.975), na.rm = T) # confidence interval for annual fluxes, per year. 3 lignes, 19 columns
annual_flux_week_mean <- colMeans(annual_flux_ton.y_week, na.rm = T) # mean annual flux per year. 1 vector
annual_flux_week_sd <- apply(annual_flux_ton.y_week, 2, sd, na.rm = T) # standard deviation of annual flux per year. Is just an estimate of goodness of mean, not as good as than the confidence interval. 
 
annual_flux_week_df <- data.frame(year = complete_years, 
                        annual_flux_mean = annual_flux_week_mean, 
                        annual_flux_variability = annual_flux_week_sd, 
                        annual_flux_pi_lower = annual_flux_week_pi[1,], 
                        annual_flux_pi_upper = annual_flux_week_pi[3,])

interannual_flux_ton.y_week <- rowMeans(annual_flux_ton.y_week, na.rm = T) # mean interannual flux per iteration of the bootstrap
interannual_flux_pi_week <- quantile(interannual_flux_ton.y_week, probs = c(0.025, 0.5, 0.975), na.rm = T) # prediction interval
interannual_flux_mean_week <- mean(interannual_flux_ton.y_week, na.rm = T) # mean interannual flux
interannual_flux_variability_week <- sd(annual_flux_week_mean, na.rm = T) # standard deviation of interannual flux per year

interannual_flux_week_df <- data.frame(year = "interannual", annual_flux_mean = interannual_flux_mean_week, 
                                  annual_flux_variability = interannual_flux_variability_week,
                        annual_flux_pi_lower = interannual_flux_pi_week[1], 
                        annual_flux_pi_upper = interannual_flux_pi_week[3])

total_flux_week_df <- rbind(annual_flux_week_df, interannual_flux_week_df)
total_flux_week_df$group <- c(rep("annual", nyears), "interannual")

ggplot()+
  geom_col(data = total_flux_week_df, aes(x=year, y = annual_flux_mean, fill = group))+
    geom_errorbar(data = total_flux_week_df, aes(x = year, ymin = annual_flux_pi_lower, ymax = annual_flux_pi_upper, col = "prediction interval"), width = 0.3, size = 0.8)+
  geom_errorbar(data = filter(total_flux_week_df, year == "interannual"), aes(x = year, ymin = annual_flux_mean - annual_flux_variability, ymax = annual_flux_mean + annual_flux_variability, col = "interannual variability"), width = 0.2, size = 0.8, linetype = 2)+
  scale_fill_manual(values = c("annual" = "lightblue", "interannual" = "indianred"))+
  scale_color_manual(values = c("prediction interval" = "darkblue", "interannual variability" = "darkred"), name = "")+
   labs(x = "Year", y = "Flux, from bi-dayly mean values (ton/year)", fill = "")+
  theme_minimal(base_size = 15)+
  theme(axis.text.x = element_text(angle = 45, hjust = 1), legend.position = "bottom")

knitr::kable(total_flux_week_df, digits = 6, row.names = F) %>% kableExtra::kable_styling()
```

```{r specific-arles-week}

# compute flux
sflux_ton_mat_week <- doc_mat_week*1e-9*q_mat_week*1e3*60*60*24*7/bv #pred_week * mes_mat : poc in mg/L converted to ton; q_mat converted from m3/s to L/s. Period : nb of seconds in 1 week. 

# Get index for columns by year
index_years <- lapply(complete_years, function(y){which(arles_doc_week$year == y)}) # list of indices corresponding to each year

# annual flux
annual_sflux_ton.y_week <- lapply(index_years, function(idx){apply(flux_ton_mat_week[,idx], 1, sum, na.rm = T)}) %>% do.call("cbind", .) # sum of fluxes per year, for each iteration of the bootstrap. 
annual_sflux_week_pi <- apply(annual_sflux_ton.y_week, 2, quantile, probs = c(0.025, 0.5, 0.975), na.rm = T) # confidence interval for annual fluxes, per year. 3 lignes, 19 columns
annual_sflux_week_mean <- colMeans(annual_sflux_ton.y_week, na.rm = T) # mean annual flux per year. 1 vector
annual_sflux_week_sd <- apply(annual_sflux_ton.y_week, 2, sd, na.rm = T) # standard deviation of annual flux per year. Is just an estimate of goodness of mean, not as good as than the confidence interval. 
 
annual_sflux_week_df <- data.frame(year = complete_years, 
                        annual_flux_mean = annual_sflux_week_mean, 
                        annual_flux_variability = annual_sflux_week_sd, 
                        annual_flux_pi_lower = annual_sflux_week_pi[1,], 
                        annual_flux_pi_upper = annual_sflux_week_pi[3,])

interannual_sflux_ton.y_week <- rowMeans(annual_sflux_ton.y_week, na.rm = T) # mean interannual flux per iteration of the bootstrap
interannual_sflux_pi_week <- quantile(interannual_sflux_ton.y_week, probs = c(0.025, 0.5, 0.975), na.rm = T) # prediction interval
interannual_sflux_mean_week <- mean(interannual_sflux_ton.y_week, na.rm = T) # mean interannual flux
interannual_sflux_variability_week <- sd(annual_sflux_week_mean, na.rm = T) # standard deviation of interannual flux per year
interannual_sflux_week_df <- data.frame(year = "interannual", annual_flux_mean = interannual_sflux_mean_week, 
                                  annual_flux_variability = interannual_sflux_variability_week,
                        annual_flux_pi_lower = interannual_sflux_pi_week[1], 
                        annual_flux_pi_upper = interannual_sflux_pi_week[3])

total_sflux_week_df <- rbind(annual_sflux_week_df, interannual_sflux_week_df)
total_sflux_week_df$group <- c(rep("annual", nyears), "interannual")

ggplot()+
  geom_col(data = total_sflux_week_df, aes(x=year, y = annual_flux_mean, fill = group))+
    geom_errorbar(data = total_sflux_week_df, aes(x = year, ymin = annual_flux_pi_lower, ymax = annual_flux_pi_upper, col = "prediction interval"), width = 0.3, size = 0.8)+
  geom_errorbar(data = filter(total_sflux_week_df, year == "interannual"), aes(x = year, ymin = annual_flux_mean - annual_flux_variability, ymax = annual_flux_mean + annual_flux_variability, col = "interannual variability"), width = 0.2, size = 0.8, linetype = 2)+
  scale_fill_manual(values = c("annual" = "lightblue", "interannual" = "indianred"))+
  scale_color_manual(values = c("prediction interval" = "darkblue", "interannual variability" = "darkred"), name = "")+
   labs(x = "Year", y = "Flux, from bi-dayly mean values (tons/km2/year)", fill = "")+
  theme_minimal(base_size = 15)+
  theme(axis.text.x = element_text(angle = 45, hjust = 1), legend.position = "bottom")

knitr::kable(total_sflux_week_df, digits = 6, row.names = F) %>% kableExtra::kable_styling()
```
## 2 weeks

```{r arles-week2, cache.lazy = F}
# prepare df
arles_group_week2 <- arles_time %>% mutate(week = week(Date), week2 =  floor(as.numeric(week - min(week)) / 2), year = year(Date), Date = NULL) %>% group_by(week2,year) # group arles_time by week2
nrow_week2 <- n_groups(arles_group_week2)


# creates matrix for DOC
arles_doc_week2 <- arles_group_week2 %>% select(c("week2", "doc_mg.L")) %>% summarize("list_doc" = list(doc_mg.L)) %>% ungroup() # creates a list of mes for each week2
doc_random_week2 <- replicate(nrep, sapply(arles_doc_week2$list_doc, function(x) sample(x,1)))%>% t() # matrix of mes: one random sample per week2, replicated 1000 times
# doc_week2_noise <- matrix(rnorm(nrep*nrow_week2, mean = 0, sd = doc_u), nrow = nrep, ncol = nrow_week2) 
# doc_mat_week2 <- doc_week2_random * (1 + doc_week2_noise) # final value of mes, with noise
# doc_mean <- colMeans(doc_mat_week2)

doc_cv_week2 <- 3.2*doc_random_week2^(-0.2)
rnorm_week2 <- matrix(rnorm(nrep*nrow_week2, mean = 0, sd = 1), nrow=nrep, ncol = nrow_week2)
doc_noise_week2 <- doc_cv_week2*rnorm_week2
doc_mat_week2 <- doc_random_week2 * (1 + doc_noise_week2/100) # final value of doc, with noise in percent

# matrix for q
q_week2 <- arles_group_week2 %>% select(c("week2", "q_m3.s")) %>% summarize_all(list("q_mean" = mean, "q_sd" = sd)) %>% ungroup() # mean of Q for each week2

q_week2_mean <-  matrix(q_week2$q_mean, nrow = nrep, ncol = nrow_week2, byrow = T)
q_noise <- matrix(rnorm(nrep*nrow_week2, mean = 0, sd = q_u), nrow = nrep, ncol = nrow_week2) # creates a noise in percent (proportion), between 0 and 10%
q_mat_week2 <- q_week2_mean * (1 + q_noise) # final MC of q, with noise. SD NOT INCLUDED: will not always be available

# compute flux
flux_ton_mat_week2 <- doc_mat_week2*1e-9*q_mat_week2*1e3*60*60*24*14 #Doc in mg/L converted to ton; q_mat converted from m3/s to L/s. Period : nb of seconds in 1 week2. 

# Get index for columns by year
index_years <- lapply(complete_years, function(y){which(arles_doc_week2$year == y)}) # list of indices corresponding to each year

# annual flux
annual_flux_ton.y_week2 <- lapply(index_years, function(idx){apply(flux_ton_mat_week2[,idx], 1, sum, na.rm = T)}) %>% do.call("cbind", .) # sum of fluxes per year, for each iteration of the bootstrap. 
annual_flux_week2_pi <- apply(annual_flux_ton.y_week2, 2, quantile, probs = c(0.025, 0.5, 0.975), na.rm = T) # confidence interval for annual fluxes, per year. 3 lignes, 19 columns
annual_flux_week2_mean <- colMeans(annual_flux_ton.y_week2, na.rm = T) # mean annual flux per year. 1 vector
annual_flux_week2_sd <- apply(annual_flux_ton.y_week2, 2, sd, na.rm = T) # standard deviation of annual flux per year. Is just an estimate of goodness of mean, not as good as than the confidence interval. 
 
annual_flux_week2_df <- data.frame(year = complete_years, 
                        annual_flux_mean = annual_flux_week2_mean, 
                        annual_flux_variability = annual_flux_week2_sd, 
                        annual_flux_pi_lower = annual_flux_week2_pi[1,], 
                        annual_flux_pi_upper = annual_flux_week2_pi[3,])

interannual_flux_ton.y_week2 <- rowMeans(annual_flux_ton.y_week2, na.rm = T) # mean interannual flux per iteration of the bootstrap
interannual_flux_pi_week2 <- quantile(interannual_flux_ton.y_week2, probs = c(0.025, 0.5, 0.975), na.rm = T) # prediction interval
interannual_flux_mean_week2 <- mean(interannual_flux_ton.y_week2, na.rm = T) # mean interannual flux
interannual_flux_variability_week2 <- sd(annual_flux_week2_mean, na.rm = T) # standard deviation of interannual flux per year

interannual_flux_week2_df <- data.frame(year = "interannual", annual_flux_mean = interannual_flux_mean_week2, 
                                  annual_flux_variability = interannual_flux_variability_week2,
                        annual_flux_pi_lower = interannual_flux_pi_week2[1], 
                        annual_flux_pi_upper = interannual_flux_pi_week2[3])

total_flux_week2_df <- rbind(annual_flux_week2_df, interannual_flux_week2_df)
total_flux_week2_df$group <- c(rep("annual", nyears), "interannual")

ggplot()+
  geom_col(data = total_flux_week2_df, aes(x=year, y = annual_flux_mean, fill = group))+
    geom_errorbar(data = total_flux_week2_df, aes(x = year, ymin = annual_flux_pi_lower, ymax = annual_flux_pi_upper, col = "prediction interval"), width = 0.3, size = 0.8)+
  geom_errorbar(data = filter(total_flux_week2_df, year == "interannual"), aes(x = year, ymin = annual_flux_mean - annual_flux_variability, ymax = annual_flux_mean + annual_flux_variability, col = "interannual variability"), width = 0.2, size = 0.8, linetype = 2)+
  scale_fill_manual(values = c("annual" = "lightblue", "interannual" = "indianred"))+
  scale_color_manual(values = c("prediction interval" = "darkblue", "interannual variability" = "darkred"), name = "")+
   labs(x = "Year", y = "Flux, from bi-dayly mean values (ton/year)", fill = "")+
  theme_minimal(base_size = 15)+
  theme(axis.text.x = element_text(angle = 45, hjust = 1), legend.position = "bottom")
```
```{r specific-arles-week2}
# compute flux
flux_ton_mat_week2 <- doc_mat_week2*1e-9*q_mat_week2*1e3*60*60*24*14 #Doc in mg/L converted to ton; q_mat converted from m3/s to L/s. Period : nb of seconds in 1 week2. 

# Get index for columns by year
index_years <- lapply(complete_years, function(y){which(arles_doc_week2$year == y)}) # list of indices corresponding to each year

# annual flux
annual_flux_ton.y_week2 <- lapply(index_years, function(idx){apply(flux_ton_mat_week2[,idx], 1, sum, na.rm = T)}) %>% do.call("cbind", .) # sum of fluxes per year, for each iteration of the bootstrap. 
annual_flux_week2_pi <- apply(annual_flux_ton.y_week2, 2, quantile, probs = c(0.025, 0.5, 0.975), na.rm = T) # confidence interval for annual fluxes, per year. 3 lignes, 19 columns
annual_flux_week2_mean <- colMeans(annual_flux_ton.y_week2, na.rm = T) # mean annual flux per year. 1 vector
annual_flux_week2_sd <- apply(annual_flux_ton.y_week2, 2, sd, na.rm = T) # standard deviation of annual flux per year. Is just an estimate of goodness of mean, not as good as than the confidence interval. 
 
annual_flux_week2_df <- data.frame(year = complete_years, 
                        annual_flux_mean = annual_flux_week2_mean, 
                        annual_flux_variability = annual_flux_week2_sd, 
                        annual_flux_pi_lower = annual_flux_week2_pi[1,], 
                        annual_flux_pi_upper = annual_flux_week2_pi[3,])

interannual_flux_ton.y_week2 <- rowMeans(annual_flux_ton.y_week2, na.rm = T) # mean interannual flux per iteration of the bootstrap
interannual_flux_pi_week2 <- quantile(interannual_flux_ton.y_week2, probs = c(0.025, 0.5, 0.975), na.rm = T) # prediction interval
interannual_flux_mean_week2 <- mean(interannual_flux_ton.y_week2, na.rm = T) # mean interannual flux
interannual_flux_variability_week2 <- sd(annual_flux_week2_mean, na.rm = T) # standard deviation of interannual flux per year

interannual_flux_week2_df <- data.frame(year = "interannual", annual_flux_mean = interannual_flux_mean_week2, 
                                  annual_flux_variability = interannual_flux_variability_week2,
                        annual_flux_pi_lower = interannual_flux_pi_week2[1], 
                        annual_flux_pi_upper = interannual_flux_pi_week2[3])

total_flux_week2_df <- rbind(annual_flux_week2_df, interannual_flux_week2_df)
total_flux_week2_df$group <- c(rep("annual", nyears), "interannual")

ggplot()+
  geom_col(data = total_flux_week2_df, aes(x=year, y = annual_flux_mean, fill = group))+
    geom_errorbar(data = total_flux_week2_df, aes(x = year, ymin = annual_flux_pi_lower, ymax = annual_flux_pi_upper, col = "prediction interval"), width = 0.3, size = 0.8)+
  geom_errorbar(data = filter(total_flux_week2_df, year == "interannual"), aes(x = year, ymin = annual_flux_mean - annual_flux_variability, ymax = annual_flux_mean + annual_flux_variability, col = "interannual variability"), width = 0.2, size = 0.8, linetype = 2)+
  scale_fill_manual(values = c("annual" = "lightblue", "interannual" = "indianred"))+
  scale_color_manual(values = c("prediction interval" = "darkblue", "interannual variability" = "darkred"), name = "")+
   labs(x = "Year", y = "Flux, from bi-dayly mean values (ton/year)", fill = "")+
  theme_minimal(base_size = 15)+
  theme(axis.text.x = element_text(angle = 45, hjust = 1), legend.position = "bottom")
```


## Month

```{r arles-month, cache.lazy = F}
# prepare df
arles_group_month <- arles_time %>% mutate(week = week(Date), month =  floor(as.numeric(week - min(week)) / 2), year = year(Date), Date = NULL) %>% group_by(month,year) # group arles_time by month
nrow_month <- n_groups(arles_group_month)


# creates matrix for DOC
arles_doc_month <- arles_group_month %>% select(c("month", "doc_mg.L")) %>% summarize("list_doc" = list(doc_mg.L)) %>% ungroup() # creates a list of mes for each month
doc_random_month <- replicate(nrep, sapply(arles_doc_month$list_doc, function(x) sample(x,1)))%>% t() # matrix of mes: one random sample per month, replicated 1000 times

# doc_month_noise <- matrix(rnorm(nrep*nrow_month, mean = 0, sd = doc_u), nrow = nrep, ncol = nrow_month) 
# doc_mat_month <- doc_month_random * (1 + doc_month_noise) # final value of mes, with noise
# doc_mean <- colMeans(doc_mat_month)

doc_cv_month <- 3.2*doc_random_month^(-0.2)
rnorm_month <- matrix(rnorm(nrep*nrow_month, mean = 0, sd = 1), nrow=nrep, ncol = nrow_month)
doc_noise_month <- doc_cv_month*rnorm_month
doc_mat_month <- doc_random_month * (1 + doc_noise_month/100) # final value of doc, with noise in percent



# matrix for q
q_month <- arles_group_month %>% select(c("month", "q_m3.s")) %>% summarize_all(list("q_mean" = mean, "q_sd" = sd)) %>% ungroup() # mean of Q for each month

q_month_mean <-  matrix(q_month$q_mean, nrow = nrep, ncol = nrow_month, byrow = T)
q_noise <- matrix(rnorm(nrep*nrow_month, mean = 0, sd = q_u), nrow = nrep, ncol = nrow_month) # creates a noise in percent (proportion), between 0 and 10%
q_mat_month <- q_month_mean * (1 + q_noise) # final MC of q, with noise. SD NOT INCLUDED: will not always be available

# compute flux
flux_ton_mat_month <- doc_mat_month*1e-9*q_mat_month*1e3*60*60*24*14 #Doc in mg/L converted to ton; q_mat converted from m3/s to L/s. Period : nb of seconds in 1 month. 

# Get index for columns by year
index_years <- lapply(complete_years, function(y){which(arles_doc_month$year == y)}) # list of indices corresponding to each year

# annual flux
annual_flux_ton.y_month <- lapply(index_years, function(idx){apply(flux_ton_mat_month[,idx], 1, sum, na.rm = T)}) %>% do.call("cbind", .) # sum of fluxes per year, for each iteration of the bootstrap. 
annual_flux_month_pi <- apply(annual_flux_ton.y_month, 2, quantile, probs = c(0.025, 0.5, 0.975), na.rm = T) # confidence interval for annual fluxes, per year. 3 lignes, 19 columns
annual_flux_month_mean <- colMeans(annual_flux_ton.y_month, na.rm = T) # mean annual flux per year. 1 vector
annual_flux_month_sd <- apply(annual_flux_ton.y_month, 2, sd, na.rm = T) # standard deviation of annual flux per year. Is just an estimate of goodness of mean, not as good as than the confidence interval. 
 
annual_flux_month_df <- data.frame(year = complete_years, 
                        annual_flux_mean = annual_flux_month_mean, 
                        annual_flux_variability = annual_flux_month_sd, 
                        annual_flux_pi_lower = annual_flux_month_pi[1,], 
                        annual_flux_pi_upper = annual_flux_month_pi[3,])

interannual_flux_ton.y_month <- rowMeans(annual_flux_ton.y_month, na.rm = T) # mean interannual flux per iteration of the bootstrap
interannual_flux_pi_month <- quantile(interannual_flux_ton.y_month, probs = c(0.025, 0.5, 0.975), na.rm = T) # prediction interval
interannual_flux_mean_month <- mean(interannual_flux_ton.y_month, na.rm = T) # mean interannual flux
interannual_flux_variability_month <- sd(annual_flux_month_mean, na.rm = T) # standard deviation of interannual flux per year

interannual_flux_month_df <- data.frame(year = "interannual", annual_flux_mean = interannual_flux_mean_month, 
                                  annual_flux_variability = interannual_flux_variability_month,
                        annual_flux_pi_lower = interannual_flux_pi_month[1], 
                        annual_flux_pi_upper = interannual_flux_pi_month[3])

total_flux_month_df <- rbind(annual_flux_month_df, interannual_flux_month_df)
total_flux_month_df$group <- c(rep("annual", nyears), "interannual")

ggplot()+
  geom_col(data = total_flux_month_df, aes(x=year, y = annual_flux_mean, fill = group))+
    geom_errorbar(data = total_flux_month_df, aes(x = year, ymin = annual_flux_pi_lower, ymax = annual_flux_pi_upper, col = "prediction interval"), width = 0.3, size = 0.8)+
  geom_errorbar(data = filter(total_flux_month_df, year == "interannual"), aes(x = year, ymin = annual_flux_mean - annual_flux_variability, ymax = annual_flux_mean + annual_flux_variability, col = "interannual variability"), width = 0.2, size = 0.8, linetype = 2)+
  scale_fill_manual(values = c("annual" = "lightblue", "interannual" = "indianred"))+
  scale_color_manual(values = c("prediction interval" = "darkblue", "interannual variability" = "darkred"), name = "")+
   labs(x = "Year", y = "Flux, from bi-dayly mean values (ton/year)", fill = "")+
  theme_minimal(base_size = 15)+
  theme(axis.text.x = element_text(angle = 45, hjust = 1), legend.position = "bottom")
```

## Compare fluxes

```{r interannual-error-in-percent}
# relative error by Monte-Carlo world
error_day2 <- (interannual_flux_ton.y_day2 - interannual_flux_ton.y)/interannual_flux_ton.y * 100
error_day2_pi <- quantile(error_day2, probs = c(0.025, 0.5, 0.975), na.rm = T) # confidence interval for annual fluxes, per year. 3 lignes, 19 columns
error_day2_mean <- mean(error_day2)

error_day4 <- (interannual_flux_ton.y_day4 - interannual_flux_ton.y)/interannual_flux_ton.y * 100
error_day4_pi <- quantile(error_day4, probs = c(0.025, 0.5, 0.975), na.rm = T) # confidence interval for annual fluxes, per year. 3 lignes, 19 columns
error_day4_mean <- mean(error_day4)

error_week <- (interannual_flux_ton.y_week - interannual_flux_ton.y)/interannual_flux_ton.y * 100
error_week_pi <- quantile(error_week, probs = c(0.025, 0.5, 0.975), na.rm = T) # confidence interval for annual fluxes, per year. 3 lignes, 19 columns
error_week_mean <- mean(error_week)

error_week2 <- (interannual_flux_ton.y_week2 - interannual_flux_ton.y)/interannual_flux_ton.y * 100
error_week2_pi <- quantile(error_week2, probs = c(0.025, 0.5, 0.975), na.rm = T) # confidence interval for annual fluxes, per year. 3 lignes, 19 columns
error_week2_mean <- mean(error_week2)

error_month <- (interannual_flux_ton.y_month - interannual_flux_ton.y)/interannual_flux_ton.y * 100
error_month_pi <- quantile(error_month, probs = c(0.025, 0.5, 0.975), na.rm = T) # confidence interval for annual fluxes, per year. 3 lignes, 19 columns
error_month_mean <- mean(error_month)

error <- data.frame(time_step = factor(c("2days","4days","week","2weeks","month"), levels = c("day","2days","4days","week","2weeks","month")),
                    error = c(error_day2_mean, error_day4_mean, error_week_mean, error_week2_mean, error_month_mean),
                    pi_upr = c(error_day2_pi[3], error_day4_pi[3], error_week_pi[3], error_week2_pi[3], error_month_pi[3]),
                    pi_lwr = c(error_day2_pi[1], error_day4_pi[1], error_week_pi[1], error_week2_pi[1], error_month_pi[1])) 

ggplot(data=error, aes(x = time_step))+
  geom_point(aes(y = error))+
  geom_errorbar(aes(ymin=pi_lwr, ymax=pi_upr))+
  theme_minimal(base_size = 15)

error %>% knitr::kable(digits = 2, row.names = F) %>% kableExtra::kable_styling()
```


# Missing data 2008

```{r common-data-weighted-2008}
arles_2008 <- arles_flux %>% filter(year == 2008)

n_arl_2008 <- nrow(arles_2008)

mes_u <- 0.05
q_u <- 0.05

set.seed(503)

unique_years <- unique(arles_2008$year)
nyears <- length(unique_years)

n_rep <- 1000

index_2008 <- which(arles_flux$year == 2008) # list of indices corresponding to each year
flux_ton.s_mat_2008 <- flux_ton.s_mat[,index_2008]
flux_ton_mat_2008 <- flux_ton_mat[,index_2008]
q_mat_2008  <- q_mat[,index_2008]
mean_q_2008 <- apply(q_mat, 1, mean, na.rm = T)

# Completude?
cat("nb obs 2008:", dim(flux_ton_mat_2008)[2])
cat("Period in s in Avenelles = ", sum(arles_2008$period), "; nb of h in 1 year = ", 365*24)

```

## 10% missing

```{r percent10-2008}

waf_10_2008 <- list()

for(i in 1:n_rep){
  block_size <- floor(n_arl_2008*0.10)
  start_idx <- sample(1:n_arl_2008, 1) # choisit aléatoirement une colonne où faire commencer le bloc manquant
  # idx_block <- start_idx:(start_idx + block_size - 1) # idx des colonnes du bloc
  # 
  # Calculer les indices du bloc (avec retour au début si nécessaire)
  if(start_idx + block_size - 1 <= n_arl_2008){
    # Le bloc ne dépasse pas : bloc simple
    idx_block <- start_idx:(start_idx + block_size - 1)
  } else {
    # Le bloc dépasse : il se sépare en 2 parties
    # Partie 1 : de start_idx à la fin
    part1 <- start_idx:n_arl_2008
    # Partie 2 : du début jusqu'à compléter block_size
    remaining <- block_size - length(part1)
    part2 <- 1:remaining
    # Combiner les deux parties
    idx_block <- c(part1, part2)
  }
  
  ftsm_10_2008 <- flux_ton.s_mat_2008[,-idx_block]
  q_10_2008 <- q_mat_2008[, -idx_block]

  # Annual flux
  sum_instant_flux_ton.y_10 <- apply(ftsm_10_2008, 1, sum, na.rm = T)  # sum of fluxes per year, for each MC world computed previously. Result is a matrix with 1000 rows 
  sum_instant_q_10 <- apply(q_10_2008, 1, sum, na.rm = T) # same for Q
  mean_instant_q_10 <- apply(q_10_2008, 1, mean, na.rm = T) # same for mean Q: 1000 lines
  
  weighted_annual_flux_ton.y_10 <- sum_instant_flux_ton.y_10 / sum_instant_q_10 * mean_q_2008 * 60 * 60 * 24 *365 # 1000 lines and 3 columns of weignted annual fluxes
  
  waf_10_2008[[i]] <- weighted_annual_flux_ton.y_10 # stored in the big list
}

waf_10_mcmean <- lapply(waf_10_2008, mean) %>% unlist()# moyenne des simulations montecarlo pour chaque resampling 
waf_10_upr_2008 <- lapply(waf_10_2008, quantile, 0.975) %>% unlist()
waf_10_lwr_2008 <- lapply(waf_10_2008, quantile, 0.025) %>% unlist()

```


## 20% missing

```{r percent20-2008}


waf_20_2008 <- list()

for(i in 1:n_rep){
   block_size <- floor(n_arl_2008*0.20)
   start_idx <- sample(1:n_arl_2008, 1) # choisit aléatoirement une colonne où faire commencer le bloc manquant
  # idx_block <- start_idx:(start_idx + block_size - 1) # idx des colonnes du bloc
  # 
    # Calculer les indices du bloc (avec retour au début si nécessaire)
  if(start_idx + block_size - 1 <= n_arl_2008){
    # Le bloc ne dépasse pas : bloc simple
    idx_block <- start_idx:(start_idx + block_size - 1)
  } else {
    # Le bloc dépasse : il se sépare en 2 parties
    # Partie 1 : de start_idx à la fin
    part1 <- start_idx:n_arl_2008
    # Partie 2 : du début jusqu'à compléter block_size
    remaining <- block_size - length(part1)
    part2 <- 1:remaining
    # Combiner les deux parties
    idx_block <- c(part1, part2)
  }
  
  ftsm_20_2008 <- flux_ton.s_mat_2008[,-idx_block]
  q_20_2008 <- q_mat_2008[, -idx_block]

  # Annual flux
  sum_instant_flux_ton.y_20 <- apply(ftsm_20_2008, 1, sum, na.rm = T)  # sum of fluxes per year, for each MC world computed previously. Result is a matrix with 1000 rows and 3 columns  (1 per year)
  sum_instant_q_20 <- apply(q_20_2008, 1, sum, na.rm = T) # same for Q
  mean_instant_q_20 <- apply(q_20_2008, 1, mean, na.rm = T) # same for mean Q: 1000 lines, 3 columns
  
  weighted_annual_flux_ton.y_20 <- sum_instant_flux_ton.y_20 / sum_instant_q_20 * mean_q_2008 * 60 * 60 * 24 *365 # 1000 lines and 3 columns of weignted annual fluxes
  
  waf_20_2008[[i]] <- weighted_annual_flux_ton.y_20 # stored in the big list
}

waf_20_mcmean <- lapply(waf_20_2008, mean) %>% unlist()# moyenne des simulations montecarlo pour chaque resampling 
waf_20_upr_2008 <- lapply(waf_20_2008, quantile, 0.975) %>% unlist()
waf_20_lwr_2008 <- lapply(waf_20_2008, quantile, 0.025) %>% unlist()


```

## 30% missing

```{r percent30-2008}


waf_30_2008 <- list()

for(i in 1:n_rep){
 block_size <- floor(n_arl_2008*0.30)
 start_idx <- sample(1:n_arl_2008, 1) # choisit aléatoirement une colonne où faire commencer le bloc manquant
  # idx_block <- start_idx:(start_idx + block_size - 1) # idx des colonnes du bloc
  # 
    # Calculer les indices du bloc (avec retour au début si nécessaire)
  if(start_idx + block_size - 1 <= n_arl_2008){
    # Le bloc ne dépasse pas : bloc simple
    idx_block <- start_idx:(start_idx + block_size - 1)
  } else {
    # Le bloc dépasse : il se sépare en 2 parties
    # Partie 1 : de start_idx à la fin
    part1 <- start_idx:n_arl_2008
    # Partie 2 : du début jusqu'à compléter block_size
    remaining <- block_size - length(part1)
    part2 <- 1:remaining
    # Combiner les deux parties
    idx_block <- c(part1, part2)
  }
  
  ftsm_30_2008 <- flux_ton.s_mat_2008[,-idx_block]
  q_30_2008 <- q_mat_2008[, -idx_block]

  # Annual flux
  sum_instant_flux_ton.y_30 <- apply(ftsm_30_2008, 1, sum, na.rm = T)  # sum of fluxes per year, for each MC world computed previously. Result is a matrix with 1000 rows and 3 columns  (1 per year)
  sum_instant_q_30 <- apply(q_30_2008, 1, sum, na.rm = T) # same for Q
  mean_instant_q_30 <- apply(q_30_2008, 1, mean, na.rm = T) # same for mean Q: 1000 lines, 3 columns
  
  weighted_annual_flux_ton.y_30 <- sum_instant_flux_ton.y_30 / sum_instant_q_30 * mean_q_2008 * 60 * 60 * 24 *365 # 1000 lines and 3 columns of weignted annual fluxes
  
  waf_30_2008[[i]] <- weighted_annual_flux_ton.y_30 # stored in the big list
}

waf_30_mcmean <- lapply(waf_30_2008, mean) %>% unlist()# moyenne des simulations montecarlo pour chaque resampling 
waf_30_upr_2008 <- lapply(waf_30_2008, quantile, 0.975) %>% unlist()
waf_30_lwr_2008 <- lapply(waf_30_2008, quantile, 0.025) %>% unlist()


```

## 40% missing

```{r percent40-2008}


waf_40_2008 <- list()

for(i in 1:n_rep){
 block_size <- floor(n_arl_2008*0.40)
 start_idx <- sample(1:n_arl_2008, 1) # choisit aléatoirement une colonne où faire commencer le bloc manquant
  # idx_block <- start_idx:(start_idx + block_size - 1) # idx des colonnes du bloc
 
   # Calculer les indices du bloc (avec retour au début si nécessaire)
  if(start_idx + block_size - 1 <= n_arl_2008){
    # Le bloc ne dépasse pas : bloc simple
    idx_block <- start_idx:(start_idx + block_size - 1)
  } else {
    # Le bloc dépasse : il se sépare en 2 parties
    # Partie 1 : de start_idx à la fin
    part1 <- start_idx:n_arl_2008
    # Partie 2 : du début jusqu'à compléter block_size
    remaining <- block_size - length(part1)
    part2 <- 1:remaining
    # Combiner les deux parties
    idx_block <- c(part1, part2)
  }
  
  ftsm_40_2008 <- flux_ton.s_mat_2008[,-idx_block]
  q_40_2008 <- q_mat_2008[, -idx_block]

  # Annual flux
  sum_instant_flux_ton.y_40 <- apply(ftsm_40_2008, 1, sum, na.rm = T)  # sum of fluxes per year, for each MC world computed previously. Result is a matrix with 1000 rows and 3 columns  (1 per year)
  sum_instant_q_40 <- apply(q_40_2008, 1, sum, na.rm = T) # same for Q
  mean_instant_q_40 <- apply(q_40_2008, 1, mean, na.rm = T) # same for mean Q: 1000 lines, 3 columns
  
  weighted_annual_flux_ton.y_40 <- sum_instant_flux_ton.y_40 / sum_instant_q_40 * mean_q_2008 * 60 * 60 * 24 *365 # 1000 lines and 3 columns of weignted annual fluxes
  
  waf_40_2008[[i]] <- weighted_annual_flux_ton.y_40 # stored in the big list
}

waf_40_mcmean <- lapply(waf_40_2008, mean) %>% unlist() # moyenne des simulations montecarlo pour chaque resampling 
waf_40_upr_2008 <- lapply(waf_40_2008, quantile, 0.975) %>% unlist()
waf_40_lwr_2008 <- lapply(waf_40_2008, quantile, 0.025) %>% unlist()


```


## 50% missing

```{r percent50-2008}


waf_50_2008 <- list()

for(i in 1:n_rep){
 block_size <- floor(n_arl_2008*0.50)
 start_idx <- sample(1:n_arl_2008, 1) # choisit aléatoirement une colonne où faire commencer le bloc manquant
  # idx_block <- start_idx:(start_idx + block_size - 1) # idx des colonnes du bloc
 
   # Calculer les indices du bloc (avec retour au début si nécessaire)
  if(start_idx + block_size - 1 <= n_arl_2008){
    # Le bloc ne dépasse pas : bloc simple
    idx_block <- start_idx:(start_idx + block_size - 1)
  } else {
    # Le bloc dépasse : il se sépare en 2 parties
    # Partie 1 : de start_idx à la fin
    part1 <- start_idx:n_arl_2008
    # Partie 2 : du début jusqu'à compléter block_size
    remaining <- block_size - length(part1)
    part2 <- 1:remaining
    # Combiner les deux parties
    idx_block <- c(part1, part2)
  }
  
  ftsm_50_2008 <- flux_ton.s_mat_2008[,-idx_block]
  q_50_2008 <- q_mat_2008[, -idx_block]
  
  # Annual flux
  sum_instant_flux_ton.y_50 <- apply(ftsm_50_2008, 1, sum, na.rm = T)  # sum of fluxes per year, for each MC world computed previously. Result is a matrix with 1000 rows and 3 columns  (1 per year)
  sum_instant_q_50 <- apply(q_50_2008, 1, sum, na.rm = T) # same for Q
  mean_instant_q_50 <- apply(q_50_2008, 1, mean, na.rm = T) # same for mean Q: 1000 lines, 3 columns
  
  weighted_annual_flux_ton.y_50 <- sum_instant_flux_ton.y_50 / sum_instant_q_50 * mean_q_2008 * 60 * 60 * 24 *365 # 1000 lines and 3 columns of weignted annual fluxes
  
  waf_50_2008[[i]] <- weighted_annual_flux_ton.y_50 # stored in the big list
}

waf_50_mcmean <- lapply(waf_50_2008, mean) %>% unlist() # moyenne des simulations montecarlo pour chaque resampling 
waf_50_upr_2008 <- lapply(waf_50_2008, quantile, 0.975) %>% unlist()
waf_50_lwr_2008 <- lapply(waf_50_2008, quantile, 0.025) %>% unlist()


```

## 60% missing

from here we select a block instead of removing it

```{r percent60-2008}


waf_60_2008 <- list()

for(i in 1:n_rep){
  block_size <- floor(n_arl_2008*0.60)
   start_idx <- sample(1:n_arl_2008, 1) # choisit aléatoirement une colonne où faire commencer le bloc choisi
  # idx_block <- start_idx:(start_idx + block_size - 1) # idx des colonnes du bloc
  
    # Calculer les indices du bloc (avec retour au début si nécessaire)
  if(start_idx + block_size - 1 <= n_arl_2008){
    # Le bloc ne dépasse pas : bloc simple
    idx_block <- start_idx:(start_idx + block_size - 1)
  } else {
    # Le bloc dépasse : il se sépare en 2 parties
    # Partie 1 : de start_idx à la fin
    part1 <- start_idx:n_arl_2008
    # Partie 2 : du début jusqu'à compléter block_size
    remaining <- block_size - length(part1)
    part2 <- 1:remaining
    # Combiner les deux parties
    idx_block <- c(part1, part2)
  }
  
  ftsm_60_2008 <- flux_ton.s_mat_2008[,-idx_block]
  q_60_2008 <- q_mat_2008[, -idx_block]
  
  # Annual flux
  sum_instant_flux_ton.y_60 <- apply(ftsm_60_2008, 1, sum, na.rm = T)  # sum of fluxes per year, for each MC world computed previously. Result is a matrix with 1000 rows and 3 columns  (1 per year)
  sum_instant_q_60 <- apply(q_60_2008, 1, sum, na.rm = T) # same for Q
  mean_instant_q_60 <- apply(q_60_2008, 1, mean, na.rm = T) # same for mean Q: 1000 lines, 3 columns
  
  weighted_annual_flux_ton.y_60 <- sum_instant_flux_ton.y_60 / sum_instant_q_60 * mean_q_2008 * 60 * 60 * 24 *365 # 1000 lines and 3 columns of weignted annual fluxes
  
  waf_60_2008[[i]] <- weighted_annual_flux_ton.y_60 # stored in the big list
}

waf_60_mcmean <- lapply(waf_60_2008, mean) %>% unlist() # moyenne des simulations montecarlo pour chaque resampling 
waf_60_upr_2008 <- lapply(waf_60_2008, quantile, 0.975) %>% unlist()
waf_60_lwr_2008 <- lapply(waf_60_2008, quantile, 0.025) %>% unlist()


```

## 70% missing

```{r percent70-2008}


waf_70_2008 <- list()

for(i in 1:n_rep){
  block_size <- floor(n_arl_2008*0.70)
   start_idx <- sample(1:n_arl_2008, 1) # choisit aléatoirement une colonne où faire commencer le bloc choisi
  # idx_block <- start_idx:(start_idx + block_size - 1) # idx des colonnes du bloc
  # 
    # Calculer les indices du bloc (avec retour au début si nécessaire)
  if(start_idx + block_size - 1 <= n_arl_2008){
    # Le bloc ne dépasse pas : bloc simple
    idx_block <- start_idx:(start_idx + block_size - 1)
  } else {
    # Le bloc dépasse : il se sépare en 2 parties
    # Partie 1 : de start_idx à la fin
    part1 <- start_idx:n_arl_2008
    # Partie 2 : du début jusqu'à compléter block_size
    remaining <- block_size - length(part1)
    part2 <- 1:remaining
    # Combiner les deux parties
    idx_block <- c(part1, part2)
  }
  
  ftsm_70_2008 <- flux_ton.s_mat_2008[,-idx_block]
  q_70_2008 <- q_mat_2008[, -idx_block]
  
  # Annual flux
  sum_instant_flux_ton.y_70 <- apply(ftsm_70_2008, 1, sum, na.rm = T)  # sum of fluxes per year, for each MC world computed previously. Result is a matrix with 1000 rows and 3 columns  (1 per year)
  sum_instant_q_70 <- apply(q_70_2008, 1, sum, na.rm = T) # same for Q
  mean_instant_q_70 <- apply(q_70_2008, 1, mean, na.rm = T) # same for mean Q: 1000 lines, 3 columns
  
  weighted_annual_flux_ton.y_70 <- sum_instant_flux_ton.y_70 / sum_instant_q_70 * mean_q_2008 * 60 * 60 * 24 *365 # 1000 lines and 3 columns of weignted annual fluxes
  
  waf_70_2008[[i]] <- weighted_annual_flux_ton.y_70 # stored in the big list
}

waf_70_mcmean <- lapply(waf_70_2008, mean) %>% unlist()# moyenne des simulations montecarlo pour chaque resampling 
waf_70_upr_2008 <- lapply(waf_70_2008, quantile, 0.975) %>% unlist()
waf_70_lwr_2008 <- lapply(waf_70_2008, quantile, 0.025) %>% unlist()


```

## 80% missing

```{r percent80-2008}


waf_80_2008 <- list()

for(i in 1:n_rep){
 block_size <- floor(n_arl_2008*0.80)
   start_idx <- sample(1:n_arl_2008, 1) # choisit aléatoirement une colonne où faire commencer le bloc choisi
  # idx_block <- start_idx:(start_idx + block_size - 1) # idx des colonnes du bloc
 
   # Calculer les indices du bloc (avec retour au début si nécessaire)
  if(start_idx + block_size - 1 <= n_arl_2008){
    # Le bloc ne dépasse pas : bloc simple
    idx_block <- start_idx:(start_idx + block_size - 1)
  } else {
    # Le bloc dépasse : il se sépare en 2 parties
    # Partie 1 : de start_idx à la fin
    part1 <- start_idx:n_arl_2008
    # Partie 2 : du début jusqu'à compléter block_size
    remaining <- block_size - length(part1)
    part2 <- 1:remaining
    # Combiner les deux parties
    idx_block <- c(part1, part2)
  }
  # 
  ftsm_80_2008 <- flux_ton.s_mat_2008[,-idx_block]
  q_80_2008 <- q_mat_2008[, -idx_block]

  # Annual flux
  sum_instant_flux_ton.y_80 <- apply(ftsm_80_2008, 1, sum, na.rm = T)  # sum of fluxes per year, for each MC world computed previously. Result is a matrix with 1000 rows and 3 columns  (1 per year)
  sum_instant_q_80 <- apply(q_80_2008, 1, sum, na.rm = T) # same for Q
  mean_instant_q_80 <- apply(q_80_2008, 1, mean, na.rm = T) # same for mean Q: 1000 lines, 3 columns
  
  weighted_annual_flux_ton.y_80 <- sum_instant_flux_ton.y_80 / sum_instant_q_80 * mean_q_2008 * 60 * 60 * 24 *365 # 1000 lines and 3 columns of weignted annual fluxes
  
  waf_80_2008[[i]] <- weighted_annual_flux_ton.y_80 # stored in the big list
}

waf_80_mcmean <- lapply(waf_80_2008, mean) %>% unlist() # moyenne des simulations montecarlo pour chaque resampling 
waf_80_upr_2008 <- lapply(waf_80_2008, quantile, 0.975) %>% unlist()
waf_80_lwr_2008 <- lapply(waf_80_2008, quantile, 0.025) %>% unlist()


```

## 90% missing

```{r percent90-2008}


waf_90_2008 <- list()

for(i in 1:n_rep){
 block_size <- floor(n_arl_2008*0.90)
 start_idx <- sample(1:n_arl_2008, 1) # choisit aléatoirement une colonne où faire commencer le bloc choisi
  # idx_block <- start_idx:(start_idx + block_size - 1) # idx des colonnes du bloc
 
   # Calculer les indices du bloc (avec retour au début si nécessaire)
  if(start_idx + block_size - 1 <= n_arl_2008){
    # Le bloc ne dépasse pas : bloc simple
    idx_block <- start_idx:(start_idx + block_size - 1)
  } else {
    # Le bloc dépasse : il se sépare en 2 parties
    # Partie 1 : de start_idx à la fin
    part1 <- start_idx:n_arl_2008
    # Partie 2 : du début jusqu'à compléter block_size
    remaining <- block_size - length(part1)
    part2 <- 1:remaining
    # Combiner les deux parties
    idx_block <- c(part1, part2)
  }
  
  ftsm_90_2008 <- flux_ton.s_mat_2008[,-idx_block]
  q_90_2008 <- q_mat_2008[, -idx_block]

  # Annual flux
  sum_instant_flux_ton.y_90 <- apply(ftsm_90_2008, 1, sum, na.rm = T)  # sum of fluxes per year, for each MC world computed previously. Result is a matrix with 1000 rows and 3 columns  (1 per year)
  sum_instant_q_90 <- apply(q_90_2008, 1, sum, na.rm = T) # same for Q
  mean_instant_q_90 <- apply(q_90_2008, 1, mean, na.rm = T) # same for mean Q: 1000 lines, 3 columns
  
  weighted_annual_flux_ton.y_90 <- sum_instant_flux_ton.y_90 / sum_instant_q_90 * mean_q_2008 * 60 * 60 * 24 *365 # 1000 lines and 3 columns of weignted annual fluxes
  
  waf_90_2008[[i]] <- weighted_annual_flux_ton.y_90 # stored in the big list
}

waf_90_mcmean <- lapply(waf_90_2008, mean) %>% unlist() # moyenne des simulations montecarlo pour chaque resampling 
waf_90_upr_2008 <- lapply(waf_90_2008, quantile, 0.975) %>% unlist() # quantile superieur pour chaque resampling
waf_90_lwr_2008 <- lapply(waf_90_2008, quantile, 0.025) %>% unlist() # quantile inférieur pour chaque resampling


```

## No missing data

```{r percent100-2008}
# REF
flux_ref_2008 <- apply(flux_ton_mat_2008, 1, sum, na.rm = T)
flux_ref_2008_mean <- mean(flux_ref_2008)
flux_ref_2008_lwr <- quantile(flux_ref_2008, 0.025)
flux_ref_2008_upr <- quantile(flux_ref_2008, 0.975)

mean_q_2008 <- apply(q_mat, 1, mean, na.rm = T)
q_sum_2008<- apply(q_mat, 1, mean, na.rm = T)

# weighted
sum_instant_flux_ton.y_100 <- apply(flux_ton.s_mat_2008, 1, sum, na.rm = T)  # sum of fluxes per year, for each MC world computed previously. Result is a matrix with 1000 rows and 3 columns  (1 per year)
sum_instant_q_100 <- apply(q_mat_2008, 1, sum, na.rm = T) # same for Q

weighted_annual_flux_ton.y_100 <- sum_instant_flux_ton.y_100 / sum_instant_q_100 * mean_q_2008 * 60 * 60 * 24 *365 # 1000 lines and 3 columns of weignted annual fluxes

waf_100_mcmean <- mean(weighted_annual_flux_ton.y_100) # moyenne des simulations montecarlo 
waf_100_upr_2008 <- quantile(weighted_annual_flux_ton.y_100, 0.975) 
waf_100_lwr_2008 <- quantile(weighted_annual_flux_ton.y_100, 0.025) 


```

## Compare weighted fluxes

The "error" represents the range in which resampled interannual mean fall. Max value = 97.5% quantile of the 100 resampled means; minimum value = 2.5% quantile of the 100 resampled means; median value = median value of the 100 resampled means. 

```{r weighted-fluxes-compared-to-ref, cache = F}
error_mwf2008 <- data.frame(percent_missing_data = c(10,20,30,40,50,60,70,80,90,0,"Ref"),
  mean_wflux = c(mean((waf_10_mcmean-flux_ref_2008)/flux_ref_2008*100), 
                 mean((waf_20_mcmean-flux_ref_2008)/flux_ref_2008*100), 
                 mean((waf_30_mcmean-flux_ref_2008)/flux_ref_2008*100), 
                 mean((waf_40_mcmean-flux_ref_2008)/flux_ref_2008*100), 
                 mean((waf_50_mcmean-flux_ref_2008)/flux_ref_2008*100), 
                 mean((waf_60_mcmean-flux_ref_2008)/flux_ref_2008*100),
                 mean((waf_70_mcmean-flux_ref_2008)/flux_ref_2008*100),
                 mean((waf_80_mcmean-flux_ref_2008)/flux_ref_2008*100), 
                 mean((waf_90_mcmean-flux_ref_2008)/flux_ref_2008*100), 
                 mean((waf_100_mcmean-flux_ref_2008)/flux_ref_2008*100), 
                 mean((flux_ref_2008-flux_ref_2008)/flux_ref_2008*100)),
  max_mean = c(max((waf_10_mcmean-flux_ref_2008)/flux_ref_2008*100),
               max((waf_20_mcmean-flux_ref_2008)/flux_ref_2008*100), 
               max((waf_30_mcmean-flux_ref_2008)/flux_ref_2008*100), 
               max((waf_40_mcmean-flux_ref_2008)/flux_ref_2008*100), 
               max((waf_50_mcmean-flux_ref_2008)/flux_ref_2008*100), 
               max((waf_60_mcmean-flux_ref_2008)/flux_ref_2008*100), 
               max((waf_70_mcmean-flux_ref_2008)/flux_ref_2008*100), 
               max((waf_80_mcmean-flux_ref_2008)/flux_ref_2008*100), 
               max((waf_90_mcmean-flux_ref_2008)/flux_ref_2008*100), 
               max((waf_100_mcmean-flux_ref_2008)/flux_ref_2008*100), 
               max((flux_ref_2008-flux_ref_2008)/flux_ref_2008*100)),
  min_mean = c(min((waf_10_mcmean-flux_ref_2008)/flux_ref_2008*100),
               min((waf_20_mcmean-flux_ref_2008)/flux_ref_2008*100), 
               min((waf_30_mcmean-flux_ref_2008)/flux_ref_2008*100), 
               min((waf_40_mcmean-flux_ref_2008)/flux_ref_2008*100), 
               min((waf_50_mcmean-flux_ref_2008)/flux_ref_2008*100), 
               min((waf_60_mcmean-flux_ref_2008)/flux_ref_2008*100), 
               min((waf_70_mcmean-flux_ref_2008)/flux_ref_2008*100), 
               min((waf_80_mcmean-flux_ref_2008)/flux_ref_2008*100), 
               min((waf_90_mcmean-flux_ref_2008)/flux_ref_2008*100), 
               min((waf_100_mcmean-flux_ref_2008)/flux_ref_2008*100), 
               min((flux_ref_2008-flux_ref_2008)/flux_ref_2008*100)))

error_mwf2008$percent_missing_data <- factor(error_mwf2008$percent_missing_data, levels = c("Ref",0,10,20,30,40,50,60,70,80,90))

ggplot(data = error_mwf2008, aes(x = percent_missing_data))+
  geom_point(aes(y = mean_wflux))+
  geom_errorbar(aes(ymin = min_mean, ymax = max_mean, col = "Prediction interval range"))+
  labs(title = "Mean, max and min error of resampled fluxes", y = "Error in %")+
  theme_minimal(base_size = 15)+
  theme(legend.position = "bottom", axis.text.x = element_text(angle = 45))

error_mwf2008 %>% knitr::kable(digits = 2, row.names = F) %>% kableExtra::kable_styling()

# boxplot
error_boxplot <- data.frame("M10" = (waf_10_mcmean-flux_ref_2008)/flux_ref_2008*100,
                            "M20" = (waf_20_mcmean-flux_ref_2008)/flux_ref_2008*100,
                            "M30" = (waf_30_mcmean-flux_ref_2008)/flux_ref_2008*100,
                            "M40" = (waf_40_mcmean-flux_ref_2008)/flux_ref_2008*100,
                            "M50" = (waf_50_mcmean-flux_ref_2008)/flux_ref_2008*100,
                            "M60" = (waf_60_mcmean-flux_ref_2008)/flux_ref_2008*100,
                            "M70" = (waf_70_mcmean-flux_ref_2008)/flux_ref_2008*100,
                            "M80" = (waf_80_mcmean-flux_ref_2008)/flux_ref_2008*100,
                            "M90" = (waf_90_mcmean-flux_ref_2008)/flux_ref_2008*100,
                            "M0" = (waf_100_mcmean-flux_ref_2008)/flux_ref_2008*100,
                            "Ref" = (flux_ref_2008-flux_ref_2008)/flux_ref_2008*100
                            )

error_boxplot_long <- tidyr::pivot_longer(data = error_boxplot, cols = 1:11, names_to = "percent_missing", values_to = "error_percent")
error_boxplot_long$percent_missing <- factor(error_boxplot_long$percent_missing, levels = c("Ref","M0","M10","M20","M30","M40","M50","M60","M70","M80","M90"))
error_boxplot_long$Site <- "Arles"
error_boxplot_long$OC <- "DOC"

write.csv(error_boxplot_long, "error_boxplot_long_arles.csv")

ggplot(error_boxplot_long)+
  geom_boxplot(aes(y=error_percent, x=percent_missing))+
  theme_minimal()
```



# Compare biais weighting method

```{r load-data-for-biais, eval = F}
list.files("arles_cache/html/")
#load("arles_cache/html/constant-numbers_a01f3a223c35de779edf5e8e955f3746.RData")

knitr::load_cache(label = "constant-numbers", path = "arles_cache/html/", envir = .GlobalEnv)

```

```{r weighted-fluxes-100}
# 2007 ---- 
arles_2007 <- arles_flux %>% filter(year == 2007)

percent_year_2007 <- round(dim(arles_2007)[1]/365*100, digits = 2)

index_2007 <- which(arles_flux$year == 2007) # list of indices corresponding to each year
flux_ton.s_mat_2007 <- flux_ton.s_mat[,index_2007]
flux_ton_mat_2007 <- flux_ton_mat[,index_2007]
q_mat_2007  <- q_mat[,index_2007]
mean_q_2007 <- apply(q_mat, 1, mean, na.rm = T)


flux_ref_2007 <- apply(flux_ton_mat_2007, 1, sum, na.rm = T)
mean_q_2007 <- apply(q_mat, 1, mean, na.rm = T)
q_sum_2007 <- apply(q_mat, 1, mean, na.rm = T)

sum_instant_flux_ton.y_2007 <- apply(flux_ton.s_mat_2007, 1, sum, na.rm = T)  # sum of fluxes per year, for each MC world computed previously. Result is a matrix with 1000 rows and 3 columns  (1 per year)
sum_instant_q_2007 <- apply(q_mat_2007, 1, sum, na.rm = T) # same for Q
weighted_annual_flux_ton.y_2007 <- sum_instant_flux_ton.y_2007 / sum_instant_q_2007 * mean_q_2007 * 60 * 60 * 24 *365 # 1000 lines and 3 columns of weignted annual fluxes
waf_100_mcmean_2007 <- mean(weighted_annual_flux_ton.y_2007, na.rm = T) # moyenne des simulations montecarlo 

# 2008 ---- 
arles_2008 <- arles_flux %>% filter(year == 2008)

percent_year_2008 <- round(dim(arles_2008)[1]/365*100, digits = 2)

index_2008 <- which(arles_flux$year == 2008) # list of indices corresponding to each year
flux_ton.s_mat_2008 <- flux_ton.s_mat[,index_2008]
flux_ton_mat_2008 <- flux_ton_mat[,index_2008]
q_mat_2008  <- q_mat[,index_2008]
mean_q_2008 <- apply(q_mat, 1, mean, na.rm = T)

flux_ref_2008 <- apply(flux_ton_mat_2008, 1, sum, na.rm = T)
mean_q_2008 <- apply(q_mat, 1, mean, na.rm = T)
q_sum_2008 <- apply(q_mat, 1, mean, na.rm = T)

sum_instant_flux_ton.y_2008 <- apply(flux_ton.s_mat_2008, 1, sum, na.rm = T)  # sum of fluxes per year, for each MC world computed previously. Result is a matrix with 1000 rows and 3 columns  (1 per year)
sum_instant_q_2008 <- apply(q_mat_2008, 1, sum, na.rm = T) # same for Q
weighted_annual_flux_ton.y_2008 <- sum_instant_flux_ton.y_2008 / sum_instant_q_2008 * mean_q_2008 * 60 * 60 * 24 *365 # 1000 lines and 3 columns of weignted annual fluxes
waf_100_mcmean_2008 <- mean(weighted_annual_flux_ton.y_2008, na.rm = T) # moyenne des simulations montecarlo 

# 2009 ----
arles_2009 <- arles_flux %>% filter(year == 2009)

percent_year_2009 <- round(dim(arles_2009)[1]/365*100, digits = 2)

index_2009 <- which(arles_flux$year == 2009) # list of indices corresponding to each year
flux_ton.s_mat_2009 <- flux_ton.s_mat[,index_2009]
flux_ton_mat_2009 <- flux_ton_mat[,index_2009]
q_mat_2009  <- q_mat[,index_2009]
mean_q_2009 <- apply(q_mat, 1, mean, na.rm = T)

flux_ref_2009 <- apply(flux_ton_mat_2009, 1, sum, na.rm = T)
mean_q_2009 <- apply(q_mat, 1, mean, na.rm = T)
q_sum_2009 <- apply(q_mat, 1, mean, na.rm = T)

sum_instant_flux_ton.y_2009 <- apply(flux_ton.s_mat_2009, 1, sum, na.rm = T)  # sum of fluxes per year, for each MC world computed previously. Result is a matrix with 1000 rows and 3 columns  (1 per year)
sum_instant_q_2009 <- apply(q_mat_2009, 1, sum, na.rm = T) # same for Q
weighted_annual_flux_ton.y_2009 <- sum_instant_flux_ton.y_2009 / sum_instant_q_2009 * mean_q_2009 * 60 * 60 * 24 *365 # 1000 lines and 3 columns of weignted annual fluxes
waf_100_mcmean_2009 <- mean(weighted_annual_flux_ton.y_2009, na.rm = T) # moyenne des simulations montecarlo 
```


```{r compare-biais}
biais <- data.frame(year = c(2007,2008,2009),
                    percent_year = c(percent_year_2007, percent_year_2008, percent_year_2009),
                    mean_biais = c(mean((waf_100_mcmean_2007-flux_ref_2007)/flux_ref_2007*100),
                                   mean((waf_100_mcmean_2008-flux_ref_2008)/flux_ref_2008*100),
                                   mean((waf_100_mcmean_2009-flux_ref_2009)/flux_ref_2009*100)),
                    median_biais = c(median((waf_100_mcmean_2007-flux_ref_2007)/flux_ref_2007*100),
                                   median((waf_100_mcmean_2008-flux_ref_2008)/flux_ref_2008*100),
                                   median((waf_100_mcmean_2009-flux_ref_2009)/flux_ref_2009*100)),
                    max_biais = c(max((waf_100_mcmean_2007-flux_ref_2007)/flux_ref_2007*100),
                                  max((waf_100_mcmean_2008-flux_ref_2008)/flux_ref_2008*100),
                                  max((waf_100_mcmean_2009-flux_ref_2009)/flux_ref_2009*100)),
                    min_biais = c(min((waf_100_mcmean_2007-flux_ref_2007)/flux_ref_2007*100),
                                  min((waf_100_mcmean_2008-flux_ref_2008)/flux_ref_2008*100),
                                  min((waf_100_mcmean_2009-flux_ref_2009)/flux_ref_2009*100)),
                    qmean.qsum = c(median(mean_q_2007 / sum_instant_q_2007),
                                   median(mean_q_2008 / sum_instant_q_2008),
                                   median(mean_q_2009 / sum_instant_q_2009)),
                    K = c(median(mean_q_2007 / sum_instant_q_2007* 60 * 60 * 24 * 365),
                                   median(mean_q_2008 / sum_instant_q_2008* 60 * 60 * 24 * 365),
                                   median(mean_q_2009 / sum_instant_q_2009* 60 * 60 * 24 * 365)))


knitr::kable(biais, digits = 2) %>% kableExtra::kable_styling()

ggplot(biais)+geom_point(aes(x = K, y = median_biais, col = as.factor(year)))+
  geom_errorbar(aes(x = K, ymin = min_biais, ymax = max_biais))+
  theme_minimal()

lm(median_biais~K, data = biais) %>% summary()


biais_boxplot <- data.frame("2007" = (waf_100_mcmean_2007-flux_ref_2007)/flux_ref_2007*100,
                            "2008" = (waf_100_mcmean_2008-flux_ref_2008)/flux_ref_2008*100,
                            "2009" = (waf_100_mcmean_2009-flux_ref_2009)/flux_ref_2009*100)

biais_boxplot_long <- tidyr::pivot_longer(data = biais_boxplot, cols = 1:3, names_to = "year", values_to = "biais_percent")
biais_boxplot_long$percent_year <- rep(c(percent_year_2007, percent_year_2008, percent_year_2009),1000)

ggplot(biais_boxplot_long)+
  geom_boxplot(aes(y=biais_percent, x=percent_year, col = year))+
  theme_minimal()

q_boxplot <- data.frame("2007" = mean_q_2007 / sum_instant_q_2007 * 60 * 24 *365,
                            "2008" = mean_q_2008 / sum_instant_q_2008 * 60 * 24 *365,
                            "2009" = mean_q_2009 / sum_instant_q_2009 * 60 * 24 *365)

q_boxplot_long <- tidyr::pivot_longer(data = q_boxplot, cols = 1:3, names_to = "year", values_to = "qmean.qsum")

ggplot()+
  geom_boxplot(data = biais_boxplot_long, aes(y=biais_percent, x=year, col = "Biais"))+
  geom_boxplot(data = q_boxplot_long, aes(y=qmean.qsum, x=year, col = "Q"))+
    theme_minimal()

```




# Exit

```{r exit, cache = F}

knitr::knit_exit()
```




























# Archives
## Comparison between sum and weighted flux

```{r most-complete-years-function}
compare_docfluxes <- function(data, frac){ #results = c(sum doc kg/year, sum doc kg/s, weighted doc kg/y, nb obs, relative difference between weighted and sum for the year)
    results <<- c()
    df <- sample_frac(data, frac)
    df$doc_flux_mg <- with(df, doc_mg.L * q_m3.s * 1e3 * period * 3600) # conversion q from m3/s to L/period. Period is in hours.
    results[1] <<- sum(df$doc_flux_mg, na.rm = T)*1e-6 #sum of all periods amounts. 
    results[2] <<- sum(with(df, doc_mg.L* q_m3.s * 1e3), na.rm = T)*1e-6 #sum of daily amounts.
    results[3] <<- sum(with(df, doc_mg.L* q_m3.s * 1e3), na.rm = T)*1e-6 / with(df, sum(q_m3.s, na.rm = T)) * with(df, mean(q_m3.s, na.rm = T))  * 24 * 60 * 60 * 365
    results[4] <<- df %>% filter(!is.na(doc_mg.L)) %>% pull(doc_mg.L) %>% length()
    results[5] <<- results[3]/results[1]
    return(results)
    
}

compare_pocfluxes <- function(data, frac){ #results = c(sum poc kg/year, sum poc kg/s, weighted poc kg/y, nb obs, relative difference between weighted and sum for the year)
    results <<- c()
    df <- sample_frac(data, frac)
    df$poc_flux_mg <- with(df, poc_mg.L * q_m3.s * 1e3 * period * 3600) # conversion q from m3/s to L/period. Period is in hours.
    results[1] <<- sum(df$poc_flux_mg, na.rm = T)*1e-6 #sum of all periods amounts. 
    results[2] <<- sum(with(df, poc_mg.L* q_m3.s * 1e3), na.rm = T)*1e-6 #sum of daily amounts.
    results[3] <<- sum(with(df, poc_mg.L* q_m3.s * 1e3), na.rm = T)*1e-6 / with(df, sum(q_m3.s, na.rm = T)) * with(df, mean(q_m3.s, na.rm = T))  * 24 * 60 * 60 * 365
    results[4] <<- df %>% filter(!is.na(poc_mg.L)) %>% pull(poc_mg.L) %>% length()
    results[5] <<- results[3]/results[1]
    return(results)
    
}
```

### Year 2007 

```{r comparison-2007}
arles_2007 <- subset(arles, year == 2007)
#dim(arles_2007) # 365 lines --> 1 measure / day

doc_2007 <-  data.frame(compare_docfluxes(arles_2007, 1), 
                       compare_docfluxes(arles_2007, 0.1), 
                       compare_docfluxes(arles_2007, 0.25), 
                       compare_docfluxes(arles_2007, 0.5), 
                       compare_docfluxes(arles_2007, 0.75), 
                       compare_docfluxes(arles_2007, 0.9))

doc_2007 <- rbind(doc_2007, c(doc_2007[3,1]/doc_2007[1,1],
                              doc_2007[3,2]/doc_2007[1,1],
                              doc_2007[3,3]/doc_2007[1,1],
                              doc_2007[3,4]/doc_2007[1,1],
                              doc_2007[3,5]/doc_2007[1,1],
                              doc_2007[3,6]/doc_2007[1,1]))

rownames(doc_2007) <- c("Sum DOC kg/year", "Sum DOC kg/s", "Weighted DOC kg/year", "Number of observations", "W/S","W/S1")

knitr::kable(doc_2007, digits = 2, col.names = c("Full year", "10%", "25%","50%","75%","90%"), 
             caption = "DOC fluxes 2007") %>% 
  kableExtra::kable_styling()


poc_2007 <-  data.frame(compare_pocfluxes(arles_2007, 1), 
                       compare_pocfluxes(arles_2007, 0.1), 
                       compare_pocfluxes(arles_2007, 0.25), 
                       compare_pocfluxes(arles_2007, 0.5), 
                       compare_pocfluxes(arles_2007, 0.75), 
                       compare_pocfluxes(arles_2007, 0.9))

poc_2007 <- rbind(poc_2007, c(poc_2007[3,1]/poc_2007[1,1],
                              poc_2007[3,2]/poc_2007[1,1],
                              poc_2007[3,3]/poc_2007[1,1],
                              poc_2007[3,4]/poc_2007[1,1],
                              poc_2007[3,5]/poc_2007[1,1],
                              poc_2007[3,6]/poc_2007[1,1]))

rownames(poc_2007) <- c("Sum poc kg/year", "Sum poc kg/s", "Weighted poc kg/year", "Number of observations", "W/S","W/S1")

knitr::kable(poc_2007, digits = 2, col.names = c("Full year", "10%", "25%","50%","75%","90%"), 
             caption = "POC fluxes 2007") %>% 
  kableExtra::kable_styling()
```

### Year 2008 

```{r comparison-2008}
arles_2008 <- arles %>% subset(year == 2008)
doc_2008 <-  data.frame(compare_docfluxes(arles_2008, 1), 
                       compare_docfluxes(arles_2008, 0.1), 
                       compare_docfluxes(arles_2008, 0.25), 
                       compare_docfluxes(arles_2008, 0.5), 
                       compare_docfluxes(arles_2008, 0.75), 
                       compare_docfluxes(arles_2008, 0.9))

doc_2008 <- rbind(doc_2008, c(doc_2008[3,1]/doc_2008[1,1],
                              doc_2008[3,2]/doc_2008[1,1],
                              doc_2008[3,3]/doc_2008[1,1],
                              doc_2008[3,4]/doc_2008[1,1],
                              doc_2008[3,5]/doc_2008[1,1],
                              doc_2008[3,6]/doc_2008[1,1]))


rownames(doc_2008) <- c("Sum DOC kg/year", "Sum DOC kg/s", "Weighted DOC kg/year", "Number of observations", "W/S","W/S1")

knitr::kable(doc_2008, digits = 2, col.names = c("Full year", "10%", "25%","50%","75%","90%"), 
             caption = "DOC fluxes 2008") %>% 
  kableExtra::kable_styling()


poc_2008 <-  data.frame(compare_pocfluxes(arles_2008, 1), 
                       compare_pocfluxes(arles_2008, 0.1), 
                       compare_pocfluxes(arles_2008, 0.25), 
                       compare_pocfluxes(arles_2008, 0.5), 
                       compare_pocfluxes(arles_2008, 0.75), 
                       compare_pocfluxes(arles_2008, 0.9))

poc_2008 <- rbind(poc_2008, c(poc_2008[3,1]/poc_2008[1,1],
                              poc_2008[3,2]/poc_2008[1,1],
                              poc_2008[3,3]/poc_2008[1,1],
                              poc_2008[3,4]/poc_2008[1,1],
                              poc_2008[3,5]/poc_2008[1,1],
                              poc_2008[3,6]/poc_2008[1,1]))

rownames(poc_2008) <- c("Sum poc kg/year", "Sum poc kg/s", "Weighted poc kg/year", "Number of observations", "W/S","W/S1")

knitr::kable(poc_2008, digits = 2, col.names = c("Full year", "10%", "25%","50%","75%","90%"), 
             caption = "POC fluxes 2008") %>% 
  kableExtra::kable_styling()

```

### Year 2009 

```{r comparison-2009}
arles_2009 <- arles %>% subset(year == 2009)
doc_2009 <-  data.frame(compare_docfluxes(arles_2009, 1), 
                       compare_docfluxes(arles_2009, 0.1), 
                       compare_docfluxes(arles_2009, 0.25), 
                       compare_docfluxes(arles_2009, 0.5), 
                       compare_docfluxes(arles_2009, 0.75), 
                       compare_docfluxes(arles_2009, 0.9))

doc_2009 <- rbind(doc_2009, c(doc_2009[3,1]/doc_2009[1,1],
                              doc_2009[3,2]/doc_2009[1,1],
                              doc_2009[3,3]/doc_2009[1,1],
                              doc_2009[3,4]/doc_2009[1,1],
                              doc_2009[3,5]/doc_2009[1,1],
                              doc_2009[3,6]/doc_2009[1,1]))


rownames(doc_2009) <- c("Sum DOC kg/year", "Sum DOC kg/s", "Weighted DOC kg/year", "Number of observations", "W/S","W/S1")

knitr::kable(doc_2009, digits = 2, col.names = c("Full year", "10%", "25%","50%","75%","90%"), 
             caption = "DOC fluxes 2009") %>% 
  kableExtra::kable_styling()


poc_2009 <-  data.frame(compare_pocfluxes(arles_2009, 1), 
                       compare_pocfluxes(arles_2009, 0.1), 
                       compare_pocfluxes(arles_2009, 0.25), 
                       compare_pocfluxes(arles_2009, 0.5), 
                       compare_pocfluxes(arles_2009, 0.75), 
                       compare_pocfluxes(arles_2009, 0.9))

poc_2009 <- rbind(poc_2009, c(poc_2009[3,1]/poc_2009[1,1],
                              poc_2009[3,2]/poc_2009[1,1],
                              poc_2009[3,3]/poc_2009[1,1],
                              poc_2009[3,4]/poc_2009[1,1],
                              poc_2009[3,5]/poc_2009[1,1],
                              poc_2009[3,6]/poc_2009[1,1]))

rownames(poc_2009) <- c("Sum poc kg/year", "Sum poc kg/s", "Weighted poc kg/year", "Number of observations", "W/S","W/S1")

knitr::kable(poc_2009, digits = 2, col.names = c("Full year", "10%", "25%","50%","75%","90%"), 
             caption = "POC fluxes 2009") %>% 
  kableExtra::kable_styling()

```

## Comparison between sampling frequencies

### Year 2007

```{r frequency-2007}
arles_2007_day <- arles_2007 %>% group_by(Date) %>% summarize_all(mean, na.rm = T)
arles_2007_week <- arles_2007 %>% group_by(week) %>% summarize_all(mean, na.rm = T)
arles_2007_month <- arles_2007 %>% group_by(month) %>% summarize_all(mean, na.rm = T)

nb_days_doc_2007 <- arles_2007 %>% filter(!is.na(doc_mg.L)) %>% pull(Date) %>% unique() %>% length()
nb_days_poc_2007 <- arles_2007 %>% filter(!is.na(poc_mg.L)) %>% pull(Date) %>% unique() %>% length()

# DOC 

arles_2007_day$doc_flux_mg <- with(arles_2007_day, doc_mg.L * q_m3.s * 1e3 * 24 * 3600) %>% tidyr::replace_na(0) # conversion q from m3/s to L/period. 
sum_doc_flux_arles_2007_day <- sum(arles_2007_day$doc_flux_mg, na.rm = T)*1e-6

arles_2007_week$doc_flux_mg <- with(arles_2007_week, doc_mg.L * q_m3.s * 1e3 * 7 * 24 * 3600) %>% tidyr::replace_na(0) # conversion q from m3/s to L/period. Period is in hours.
sum_doc_flux_arles_2007_week <- sum(arles_2007_week$doc_flux_mg, na.rm = T)*1e-6

arles_2007_month$doc_flux_mg <- with(arles_2007_month, doc_mg.L * q_m3.s * 1e3 * 30.42 * 24 * 3600) %>% tidyr::replace_na(0) # conversion q from m3/s to L/period. Period is in hours.
sum_doc_flux_arles_2007_month <- sum(arles_2007_month$doc_flux_mg, na.rm = T)*1e-6

ggplot()+geom_point(data = arles_2007_day, aes(x = Date, y = cumsum(doc_flux_mg), col = "per day"), size = 1)+
  geom_point(data = arles_2007_week, aes(x = Date, y = cumsum(doc_flux_mg), col = "per week"), size = 2)+
  geom_point(data = arles_2007_month, aes(x = Date, y = cumsum(doc_flux_mg), col = "per month"), size = 3)+
  labs(y = "Somme cumulée du flux de DOC en mg", col = "Sampling frequency")+
  scale_x_date(labels = function(x) format(x, "%d-%b"), date_minor_breaks = "1 month")+
  theme_minimal(base_size = 15)+
  theme(legend.position = "bottom")

# POC

arles_2007_day$poc_flux_mg <- with(arles_2007_day, poc_mg.L * q_m3.s * 1e3 * 24 * 3600) %>% tidyr::replace_na(0) # conversion q from m3/s to L/period. 
sum_poc_flux_arles_2007_day <- sum(arles_2007_day$poc_flux_mg, na.rm = T)*1e-6

arles_2007_week$poc_flux_mg <- with(arles_2007_week, poc_mg.L * q_m3.s * 1e3 * 7 * 24 * 3600) %>% tidyr::replace_na(0) # conversion q from m3/s to L/period. Period is in hours.
sum_poc_flux_arles_2007_week <- sum(arles_2007_week$poc_flux_mg, na.rm = T)*1e-6

arles_2007_month$poc_flux_mg <- with(arles_2007_month, poc_mg.L * q_m3.s * 1e3 * 30.42 * 24 * 3600) %>% tidyr::replace_na(0) # conversion q from m3/s to L/period. Period is in hours.
sum_poc_flux_arles_2007_month <- sum(arles_2007_month$poc_flux_mg, na.rm = T)*1e-6

ggplot()+geom_point(data = arles_2007_day, aes(x = Date, y = cumsum(poc_flux_mg), col = "per day"), size = 1)+
  geom_point(data = arles_2007_week, aes(x = Date, y = cumsum(poc_flux_mg), col = "per week"), size = 2)+
  geom_point(data = arles_2007_month, aes(x = Date, y = cumsum(poc_flux_mg), col = "per month"), size = 3)+
  labs(y = "Somme cumulée du flux de POC en mg", col = "Sampling frequency")+
  scale_x_date(labels = function(x) format(x, "%d-%b"), date_minor_breaks = "1 month")+
  theme_minimal(base_size = 15)+
  theme(legend.position = "bottom")

ggplot(arles_2007_day)+geom_point(aes(x=Date, y = q_m3.s)) + scale_x_date(labels = function(x) format(x, "%d-%b"), date_minor_breaks = "1 month")+theme_minimal(base_size = 15)

ggplot()+geom_point(data = arles_2007_day, aes(x = Date, y = cumsum(tidyr::replace_na(q_m3.s,0)), col = "per day"), size = 1)+
  geom_point(data = arles_2007_week, aes(x = Date, y = cumsum(q_m3.s*7), col = "per week"), size = 2)+
  geom_point(data = arles_2007_month, aes(x = Date, y = cumsum(q_m3.s*30.42), col = "per month"), size = 3)+
  labs(y = "Somme cumulée du débit en m3/s", col = "Sampling frequency")+
  scale_x_date(labels = function(x) format(x, "%d-%b"), date_minor_breaks = "1 month")+
  theme_minimal(base_size = 15)+
  theme(legend.position = "bottom")


knitr::kable(data.frame(
  "nb of days sampled doc" = nb_days_doc_2007,
  "doc flux" = c(sum_doc_flux_arles_2007_day, sum_doc_flux_arles_2007_week, sum_doc_flux_arles_2007_month),
  "% of daily doc value" = c(sum_doc_flux_arles_2007_day/sum_doc_flux_arles_2007_day*100, sum_doc_flux_arles_2007_week/sum_doc_flux_arles_2007_day*100, sum_doc_flux_arles_2007_month/sum_doc_flux_arles_2007_day*100),
   "nb of days sampled poc" = nb_days_poc_2007,
  "poc flux" = c(sum_poc_flux_arles_2007_day, sum_poc_flux_arles_2007_week, sum_poc_flux_arles_2007_month),
  "% of daily poc value poc" = c(sum_poc_flux_arles_2007_day/sum_poc_flux_arles_2007_day*100, sum_poc_flux_arles_2007_week/sum_poc_flux_arles_2007_day*100, sum_poc_flux_arles_2007_month/sum_poc_flux_arles_2007_day*100),
  row.names = c("day","week","month")),
  digits = 2) %>% kableExtra::kable_styling
```


### Year 2008 

```{r frequency-2008}
arles_2008_day <- arles_2008 %>% group_by(Date) %>% summarize_all(mean, na.rm = T)
arles_2008_week <- arles_2008 %>% group_by(week) %>% summarize_all(mean, na.rm = T)
arles_2008_month <- arles_2008 %>% group_by(month) %>% summarize_all(mean, na.rm = T)

nb_days_doc_2008 <- arles_2008 %>% filter(!is.na(doc_mg.L)) %>% pull(Date) %>% unique() %>% length()
nb_days_poc_2008 <- arles_2008 %>% filter(!is.na(poc_mg.L)) %>% pull(Date) %>% unique() %>% length()

# DOC 

arles_2008_day$doc_flux_mg <- with(arles_2008_day, doc_mg.L * q_m3.s * 1e3 * 24 * 3600) %>% tidyr::replace_na(0) # conversion q from m3/s to L/period. 
sum_doc_flux_arles_2008_day <- sum(arles_2008_day$doc_flux_mg, na.rm = T)*1e-6

arles_2008_week$doc_flux_mg <- with(arles_2008_week, doc_mg.L * q_m3.s * 1e3 * 7 * 24 * 3600) %>% tidyr::replace_na(0) # conversion q from m3/s to L/period. Period is in hours.
sum_doc_flux_arles_2008_week <- sum(arles_2008_week$doc_flux_mg, na.rm = T)*1e-6

arles_2008_month$doc_flux_mg <- with(arles_2008_month, doc_mg.L * q_m3.s * 1e3 * 30.42 * 24 * 3600) %>% tidyr::replace_na(0) # conversion q from m3/s to L/period. Period is in hours.
sum_doc_flux_arles_2008_month <- sum(arles_2008_month$doc_flux_mg, na.rm = T)*1e-6

ggplot()+geom_point(data = arles_2008_day, aes(x = Date, y = cumsum(doc_flux_mg), col = "per day"), size = 1)+
  geom_point(data = arles_2008_week, aes(x = Date, y = cumsum(doc_flux_mg), col = "per week"), size = 2)+
  geom_point(data = arles_2008_month, aes(x = Date, y = cumsum(doc_flux_mg), col = "per month"), size = 3)+
  labs(y = "Somme cumulée du flux de DOC en mg", col = "Sampling frequency")+
  scale_x_date(labels = function(x) format(x, "%d-%b"), date_minor_breaks = "1 month")+
  theme_minimal(base_size = 15)+
  theme(legend.position = "bottom")

# POC

arles_2008_day$poc_flux_mg <- with(arles_2008_day, poc_mg.L * q_m3.s * 1e3 * 24 * 3600) %>% tidyr::replace_na(0) # conversion q from m3/s to L/period. 
sum_poc_flux_arles_2008_day <- sum(arles_2008_day$poc_flux_mg, na.rm = T)*1e-6

arles_2008_week$poc_flux_mg <- with(arles_2008_week, poc_mg.L * q_m3.s * 1e3 * 7 * 24 * 3600) %>% tidyr::replace_na(0) # conversion q from m3/s to L/period. Period is in hours.
sum_poc_flux_arles_2008_week <- sum(arles_2008_week$poc_flux_mg, na.rm = T)*1e-6

arles_2008_month$poc_flux_mg <- with(arles_2008_month, poc_mg.L * q_m3.s * 1e3 * 30.42 * 24 * 3600) %>% tidyr::replace_na(0) # conversion q from m3/s to L/period. Period is in hours.
sum_poc_flux_arles_2008_month <- sum(arles_2008_month$poc_flux_mg, na.rm = T)*1e-6

ggplot()+geom_point(data = arles_2008_day, aes(x = Date, y = cumsum(poc_flux_mg), col = "per day"), size = 1)+
  geom_point(data = arles_2008_week, aes(x = Date, y = cumsum(poc_flux_mg), col = "per week"), size = 2)+
  geom_point(data = arles_2008_month, aes(x = Date, y = cumsum(poc_flux_mg), col = "per month"), size = 3)+
  labs(y = "Somme cumulée du flux de POC en mg", col = "Sampling frequency")+
  scale_x_date(labels = function(x) format(x, "%d-%b"), date_minor_breaks = "1 month")+
  theme_minimal(base_size = 15)+
  theme(legend.position = "bottom")

ggplot(arles_2008_day)+geom_point(aes(x=Date, y = q_m3.s)) + scale_x_date(labels = function(x) format(x, "%d-%b"), date_minor_breaks = "1 month")+theme_minimal(base_size = 15)

ggplot()+geom_point(data = arles_2008_day, aes(x = Date, y = cumsum(tidyr::replace_na(q_m3.s,0)), col = "per day"), size = 1)+
  geom_point(data = arles_2008_week, aes(x = Date, y = cumsum(q_m3.s*7), col = "per week"), size = 2)+
  geom_point(data = arles_2008_month, aes(x = Date, y = cumsum(q_m3.s*30.42), col = "per month"), size = 3)+
  labs(y = "Somme cumulée du débit en m3/s", col = "Sampling frequency")+
  scale_x_date(labels = function(x) format(x, "%d-%b"), date_minor_breaks = "1 month")+
  theme_minimal(base_size = 15)+
  theme(legend.position = "bottom")

knitr::kable(data.frame(
  "nb of days sampled doc" = nb_days_doc_2008,
  "doc flux" = c(sum_doc_flux_arles_2008_day, sum_doc_flux_arles_2008_week, sum_doc_flux_arles_2008_month),
  "% of daily doc value" = c(sum_doc_flux_arles_2008_day/sum_doc_flux_arles_2008_day*100, sum_doc_flux_arles_2008_week/sum_doc_flux_arles_2008_day*100, sum_doc_flux_arles_2008_month/sum_doc_flux_arles_2008_day*100),
   "nb of days sampled poc" = nb_days_poc_2008,
  "poc flux" = c(sum_poc_flux_arles_2008_day, sum_poc_flux_arles_2008_week, sum_poc_flux_arles_2008_month),
  "% of daily poc value poc" = c(sum_poc_flux_arles_2008_day/sum_poc_flux_arles_2008_day*100, sum_poc_flux_arles_2008_week/sum_poc_flux_arles_2008_day*100, sum_poc_flux_arles_2008_month/sum_poc_flux_arles_2008_day*100),
  row.names = c("day","week","month")),
  digits = 2
) %>% kable_paper
```

### Year 2009 

```{r frequency-2009}
arles_2009_day <- arles_2009 %>% group_by(Date) %>% summarize_all(mean, na.rm = T)
arles_2009_week <- arles_2009 %>% group_by(week) %>% summarize_all(mean, na.rm = T)
arles_2009_month <- arles_2009 %>% group_by(month) %>% summarize_all(mean, na.rm = T)

nb_days_doc_2009 <- arles_2009 %>% filter(!is.na(doc_mg.L)) %>% pull(Date) %>% unique() %>% length()
nb_days_poc_2009 <- arles_2009 %>% filter(!is.na(poc_mg.L)) %>% pull(Date) %>% unique() %>% length()

# DOC 

arles_2009_day$doc_flux_mg <- with(arles_2009_day, doc_mg.L * q_m3.s * 1e3 * 24 * 3600) %>% tidyr::replace_na(0) # conversion q from m3/s to L/period. 
sum_doc_flux_arles_2009_day <- sum(arles_2009_day$doc_flux_mg, na.rm = T)*1e-6

arles_2009_week$doc_flux_mg <- with(arles_2009_week, doc_mg.L * q_m3.s * 1e3 * 7 * 24 * 3600) %>% tidyr::replace_na(0) # conversion q from m3/s to L/period. Period is in hours.
sum_doc_flux_arles_2009_week <- sum(arles_2009_week$doc_flux_mg, na.rm = T)*1e-6

arles_2009_month$doc_flux_mg <- with(arles_2009_month, doc_mg.L * q_m3.s * 1e3 * 30.42 * 24 * 3600) %>% tidyr::replace_na(0) # conversion q from m3/s to L/period. Period is in hours.
sum_doc_flux_arles_2009_month <- sum(arles_2009_month$doc_flux_mg, na.rm = T)*1e-6

ggplot()+geom_point(data = arles_2009_day, aes(x = Date, y = cumsum(doc_flux_mg), col = "per day"), size = 1)+
  geom_point(data = arles_2009_week, aes(x = Date, y = cumsum(doc_flux_mg), col = "per week"), size = 2)+
  geom_point(data = arles_2009_month, aes(x = Date, y = cumsum(doc_flux_mg), col = "per month"), size = 3)+
  labs(y = "Somme cumulée du flux de DOC en mg", col = "Sampling frequency")+
  scale_x_date(labels = function(x) format(x, "%d-%b"), date_minor_breaks = "1 month")+
  theme_minimal(base_size = 15)+
  theme(legend.position = "bottom")

# POC

arles_2009_day$poc_flux_mg <- with(arles_2009_day, poc_mg.L * q_m3.s * 1e3 * 24 * 3600) %>% tidyr::replace_na(0) # conversion q from m3/s to L/period. 
sum_poc_flux_arles_2009_day <- sum(arles_2009_day$poc_flux_mg, na.rm = T)*1e-6

arles_2009_week$poc_flux_mg <- with(arles_2009_week, poc_mg.L * q_m3.s * 1e3 * 7 * 24 * 3600) %>% tidyr::replace_na(0) # conversion q from m3/s to L/period. Period is in hours.
sum_poc_flux_arles_2009_week <- sum(arles_2009_week$poc_flux_mg, na.rm = T)*1e-6

arles_2009_month$poc_flux_mg <- with(arles_2009_month, poc_mg.L * q_m3.s * 1e3 * 30.42 * 24 * 3600) %>% tidyr::replace_na(0) # conversion q from m3/s to L/period. Period is in hours.
sum_poc_flux_arles_2009_month <- sum(arles_2009_month$poc_flux_mg, na.rm = T)*1e-6

ggplot()+geom_point(data = arles_2009_day, aes(x = Date, y = cumsum(poc_flux_mg), col = "per day"), size = 1)+
  geom_point(data = arles_2009_week, aes(x = Date, y = cumsum(poc_flux_mg), col = "per week"), size = 2)+
  geom_point(data = arles_2009_month, aes(x = Date, y = cumsum(poc_flux_mg), col = "per month"), size = 3)+
  labs(y = "Somme cumulée du flux de POC en mg", col = "Sampling frequency")+
  scale_x_date(labels = function(x) format(x, "%d-%b"), date_minor_breaks = "1 month")+
  theme_minimal(base_size = 15)+
  theme(legend.position = "bottom")

ggplot(arles_2009_day)+geom_point(aes(x=Date, y = q_m3.s)) + scale_x_date(labels = function(x) format(x, "%d-%b"), date_minor_breaks = "1 month")+theme_minimal(base_size = 15)

ggplot()+geom_point(data = arles_2009_day, aes(x = Date, y = cumsum(tidyr::replace_na(q_m3.s,0)), col = "per day"), size = 1)+
  geom_point(data = arles_2009_week, aes(x = Date, y = cumsum(q_m3.s*7), col = "per week"), size = 2)+
  geom_point(data = arles_2009_month, aes(x = Date, y = cumsum(q_m3.s*30.42), col = "per month"), size = 3)+
  labs(y = "Somme cumulée du débit en m3/s", col = "Sampling frequency")+
  scale_x_date(labels = function(x) format(x, "%d-%b"), date_minor_breaks = "1 month")+
  theme_minimal(base_size = 15)+
  theme(legend.position = "bottom")


knitr::kable(data.frame(
  "nb of days sampled doc" = nb_days_doc_2009,
  "doc flux" = c(sum_doc_flux_arles_2009_day, sum_doc_flux_arles_2009_week, sum_doc_flux_arles_2009_month),
  "% of daily doc value" = c(sum_doc_flux_arles_2009_day/sum_doc_flux_arles_2009_day*100, sum_doc_flux_arles_2009_week/sum_doc_flux_arles_2009_day*100, sum_doc_flux_arles_2009_month/sum_doc_flux_arles_2009_day*100),
   "nb of days sampled poc" = nb_days_poc_2009,
  "poc flux" = c(sum_poc_flux_arles_2009_day, sum_poc_flux_arles_2009_week, sum_poc_flux_arles_2009_month),
  "% of daily poc value poc" = c(sum_poc_flux_arles_2009_day/sum_poc_flux_arles_2009_day*100, sum_poc_flux_arles_2009_week/sum_poc_flux_arles_2009_day*100, sum_poc_flux_arles_2009_month/sum_poc_flux_arles_2009_day*100),
  row.names = c("day","week","month")),
  digits = 2
) %>% kable_paper
```




## Interpol or not?

### Year 2007

```{r random-datasets-2007}
set.seed(1)
arles_2007_1 <- sample_frac(arles_2007, 0.5) %>% select(c("Date", "q_m3.s", "year","month","week","poc_mg.L","doc_mg.L"))
set.seed(2)
arles_2007_2 <- sample_frac(arles_2007, 0.5) %>% select(c("Date", "q_m3.s", "year","month","week","poc_mg.L","doc_mg.L"))
set.seed(3)
arles_2007_3 <- sample_frac(arles_2007, 0.5) %>% select(c("Date", "q_m3.s", "year","month","week","poc_mg.L","doc_mg.L"))

ggpubr::ggarrange(
ggplot() + geom_point(data = arles_2007, aes(x=Date, y = doc_mg.L), size = 1, alpha = 0.5)+labs(x = "Arles, complet", y = "")+theme(legend.position = "none"),
ggplot() + geom_point(data = arles_2007_1, aes(x=Date, y = doc_mg.L), size = 1, alpha = 0.5)+labs(x = "Arles, 1", y = "")+theme(legend.position = "none"),
ggplot() + geom_point(data = arles_2007_2, aes(x=Date, y = doc_mg.L), size = 1, alpha = 0.5)+labs(x = "Arles, 2", y = "")+theme(legend.position = "none"),
ggplot() + geom_point(data = arles_2007_3, aes(x=Date, y = doc_mg.L), size = 1, alpha = 0.5)+labs(x = "Arles, 3", y = "")+theme(legend.position = "none")
)

ggpubr::ggarrange(
ggplot() + geom_point(data = arles_2007, aes(x=Date, y = poc_mg.L), size = 1, alpha = 0.5)+labs(x = "Arles, complet", y = "")+theme(legend.position = "none"),
ggplot() + geom_point(data = arles_2007_1, aes(x=Date, y = poc_mg.L), size = 1, alpha = 0.5)+labs(x = "Arles, 1", y = "")+theme(legend.position = "none"),
ggplot() + geom_point(data = arles_2007_2, aes(x=Date, y = poc_mg.L), size = 1, alpha = 0.5)+labs(x = "Arles, 2", y = "")+theme(legend.position = "none"),
ggplot() + geom_point(data = arles_2007_3, aes(x=Date, y = poc_mg.L), size = 1, alpha = 0.5)+labs(x = "Arles, 3", y = "")+theme(legend.position = "none")
)
```

```{r interpol-poc-2007}
arles_2007_11 <- merge(select(arles_2007, c("Date","q_m3.s","period")), arles_2007_1, all = T)
arles_2007_11$doc_mg.L <- na_interpolation(arles_2007_11$doc_mg.L, maxgap = 30)

arles_2007_22 <- merge(select(arles_2007, c("Date","q_m3.s","period")), arles_2007_2, all = T)
arles_2007_22$doc_mg.L <- na_interpolation(arles_2007_22$doc_mg.L, maxgap = 30)

arles_2007_33 <- merge(select(arles_2007, c("Date","q_m3.s","period")), arles_2007_3, all = T)
arles_2007_33$doc_mg.L <- na_interpolation(arles_2007_33$doc_mg.L, maxgap = 30)

arles_interpol <- data.frame(compare_docfluxes(arles_2007, 1), compare_docfluxes(arles_2007_11, 1), compare_docfluxes(arles_2007_22, 1), compare_docfluxes(arles_2007_33, 1))
arles_interpol <- rbind(arles_interpol, c(arles_interpol[1,1]/arles_interpol[1,1], 
                                          arles_interpol[1,2]/arles_interpol[1,1], 
                                          arles_interpol[1,3]/arles_interpol[1,1], 
                                          arles_interpol[1,4]/arles_interpol[1,1]))

rownames(arles_interpol) <- c("Sum doc kg/year", "Sum doc kg/s", "Weighted doc kg/year", "Number of observations","W/S", "ratio interpol / sampled")

knitr::kable(arles_interpol[c(1,4,6),], digits = 2, col.names = c("Full Arles", "sample arles 1", "sample arles 2", "sample arles 3"), 
             caption = "Arles interpol 2007") %>% 
  kableExtra::kable_styling()
```


### Year 2008

```{r random-datasets-2008}
set.seed(1)
arles_2008_1 <- sample_frac(arles_2008, 0.5) %>% select(c("Date", "q_m3.s", "year","month","week","poc_mg.L","doc_mg.L"))
set.seed(2)
arles_2008_2 <- sample_frac(arles_2008, 0.5) %>% select(c("Date", "q_m3.s", "year","month","week","poc_mg.L","doc_mg.L"))
set.seed(3)
arles_2008_3 <- sample_frac(arles_2008, 0.5) %>% select(c("Date", "q_m3.s", "year","month","week","poc_mg.L","doc_mg.L"))

ggpubr::ggarrange(
ggplot() + geom_point(data = arles_2008, aes(x=Date, y = doc_mg.L), size = 1, alpha = 0.5)+labs(x = "Arles, complet", y = "")+theme(legend.position = "none"),
ggplot() + geom_point(data = arles_2008_1, aes(x=Date, y = doc_mg.L), size = 1, alpha = 0.5)+labs(x = "Arles, 1", y = "")+theme(legend.position = "none"),
ggplot() + geom_point(data = arles_2008_2, aes(x=Date, y = doc_mg.L), size = 1, alpha = 0.5)+labs(x = "Arles, 2", y = "")+theme(legend.position = "none"),
ggplot() + geom_point(data = arles_2008_3, aes(x=Date, y = doc_mg.L), size = 1, alpha = 0.5)+labs(x = "Arles, 3", y = "")+theme(legend.position = "none")
)

ggpubr::ggarrange(
ggplot() + geom_point(data = arles_2008, aes(x=Date, y = poc_mg.L), size = 1, alpha = 0.5)+labs(x = "Arles, complet", y = "")+theme(legend.position = "none"),
ggplot() + geom_point(data = arles_2008_1, aes(x=Date, y = poc_mg.L), size = 1, alpha = 0.5)+labs(x = "Arles, 1", y = "")+theme(legend.position = "none"),
ggplot() + geom_point(data = arles_2008_2, aes(x=Date, y = poc_mg.L), size = 1, alpha = 0.5)+labs(x = "Arles, 2", y = "")+theme(legend.position = "none"),
ggplot() + geom_point(data = arles_2008_3, aes(x=Date, y = poc_mg.L), size = 1, alpha = 0.5)+labs(x = "Arles, 3", y = "")+theme(legend.position = "none")
)
```

```{r interpol-poc-2008}
arles_2008_11 <- merge(select(arles_2008, c("Date","q_m3.s","period")), arles_2008_1, all = T)
arles_2008_11$doc_mg.L <- na_interpolation(arles_2008_11$doc_mg.L, maxgap = 30)

arles_2008_22 <- merge(select(arles_2008, c("Date","q_m3.s","period")), arles_2008_2, all = T)
arles_2008_22$doc_mg.L <- na_interpolation(arles_2008_22$doc_mg.L, maxgap = 30)

arles_2008_33 <- merge(select(arles_2008, c("Date","q_m3.s","period")), arles_2008_3, all = T)
arles_2008_33$doc_mg.L <- na_interpolation(arles_2008_33$doc_mg.L, maxgap = 30)


arles_interpol <- data.frame(compare_docfluxes(arles_2008, 1), compare_docfluxes(arles_2008_11, 1), compare_docfluxes(arles_2008_22, 1), compare_docfluxes(arles_2008_33, 1))
arles_interpol <- rbind(arles_interpol, c(arles_interpol[1,1]/arles_interpol[1,1], 
                                          arles_interpol[1,2]/arles_interpol[1,1], 
                                          arles_interpol[1,3]/arles_interpol[1,1], 
                                          arles_interpol[1,4]/arles_interpol[1,1]))

rownames(arles_interpol) <- c("Sum doc kg/year", "Sum doc kg/s", "Weighted doc kg/year", "Number of observations","W/S", "ratio interpol / sampled")

knitr::kable(arles_interpol[c(1,4,6),], digits = 2, col.names = c("Full Arles", "sample arles 1", "sample arles 2", "sample arles 3"), 
             caption = "Arles interpol 2008") %>% 
  kableExtra::kable_styling()
```
