---
title: "Arles_method"
author: "CamilMC"
date: "2026-06-29"
output:
  html_document:
    toc: true
    toc_float: true
    number_sections: true
    code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = F, warning = F, error = F, fig.align = "center", collapse = T,
                      cache = T)
```

```{r libraries}
lapply(c("dplyr"), library, character.only = T)
lapply(c("ggplot2","ggpubr"), library, character.only = T)
lapply(c("lubridate"), library, character.only = T)
lapply(c("knitr","kableExtra"), library, character.only = T)
library(here)

```


# Data

## Get data

```{r bv-km2}
bv <- 95590
```


```{r prepare-data}
arles <- read_xlsx("arles.xlsx", sheet = "clean_data", col_types = c("date","text",rep("numeric",18))) 
arles$year <- year(arles$Date)
arles$month <- month(arles$Date)
arles$week <- week(arles$Date)

arles$Date <- as.Date(arles$Date)
arles$commondate <- as.Date(paste0("2000-", format(arles$Date,"%j")), "%Y-%j")
arles$period <- with(arles, end-start) # donne la périod en heure

arles$poc_mg.L <- with(arles, poc_umol.L*1e-3/12.011)
arles$poc_percent <- with(arles, poc_mg.L/mes_mg.L)
arles$doc_mg.L <- with(arles, doc_umol.L*1e-3/12.011)


```

```{r summary-data}
summary_arles <- merge(
arles %>% subset(!is.na(doc_mg.L)) %>% group_by(year) %>% summarise(nb_doc = n()),
arles %>% subset(!is.na(q_m3.s)) %>% group_by(year) %>% summarise(nb_q = n()), by = "year", all = T) %>% 
  merge(arles %>% subset(!is.na(period) & !is.na(q_m3.s) & !is.na(doc_mg.L)) %>% group_by(year) %>% summarise(total_period_j_nona = round(sum(period)/24)), by = "year", all = T)

knitr::kable(summary_arles) %>% kableExtra::kable_styling()

cat("mean Q", mean(arles$q_m3.s, na.rm = T))
cat("range OC (0-25-50-75-100)", quantile(with(arles, doc_mg.L), na.rm = T))
```

## Visualisation

```{r plot-by-year-doc, fig.dim = c(10,15)}


title <- expression(atop("Series of DOC and Q by year"))
plots <- ggarrange(
ggplot(arles, aes(x = commondate))+
  geom_point(aes(y = q_L.s, col = "Débit, L/s"), alpha = 0.5)+
  scale_x_date(labels = function(x) format(x, "%d-%b"), date_minor_breaks = "1 month", name = "")+
  scale_color_manual(values = c("lightblue"), name = "")+
  facet_grid(rows = vars(year))+
  labs(y = "Débit, L/s", col = "")+
  theme_bw(base_size = 15)+
  theme(legend.position = "none"),

ggplot(arles, aes(x = commondate))+
  geom_point(aes(y = doc_mg.L, col = "DOC, mg.L"), alpha = 0.5)+
  scale_x_date(labels = function(x) format(x, "%d-%b"), date_minor_breaks = "1 month", name = "")+
  scale_color_manual(values = c("palegreen4"), name = "")+
  facet_grid(rows = vars(year))+
  labs(y = "DOC, mg/L", col = "")+
  theme_bw(base_size = 15)+
  theme(legend.position = "none")
)

annotate_figure(plots, top = text_grob(title))

```

```{r arles-complete-years, fig.dim = c(10,15)}
complete_years <- c(2010,2011,2012,2013,2016,2017,2018,2019,2021)
arles_complete <- arles %>% subset(year %in% complete_years)
```

Years to use for test of methods: `r cat(complete_years)`

```{r plot-complete-years, fig.dim = c(10,15)}
title <- expression(atop("Series of DOC and Q by year"))
plots <- ggarrange(
ggplot(subset(arles_complete, year %in% complete_years), aes(x = commondate))+
  geom_point(aes(y = q_L.s, col = "Débit, L/s"), alpha = 0.5)+
  scale_x_date(labels = function(x) format(x, "%d-%b"), date_minor_breaks = "1 month", name = "")+
  scale_color_manual(values = c("lightblue"), name = "")+
  facet_grid(rows = vars(year))+
  labs(y = "Débit, L/s", col = "")+
  theme_bw(base_size = 15)+
  theme(legend.position = "none"),

ggplot(subset(arles, year %in% complete_years), aes(x = commondate))+
  geom_point(aes(y = doc_mg.L, col = "DOC, mg.L"), alpha = 0.5)+
  scale_x_date(labels = function(x) format(x, "%d-%b"), date_minor_breaks = "1 month", name = "")+
  scale_color_manual(values = c("palegreen4"), name = "")+
  facet_grid(rows = vars(year))+
  labs(y = "DOC, mg/L", col = "")+
  theme_bw(base_size = 15)+
  theme(legend.position = "none")
)

annotate_figure(plots, top = text_grob(title))

```

## Characteristics

```{r summary-data}
summary_arles <- merge(
arles %>% subset(!is.na(doc_mg.L)) %>% group_by(year) %>% summarise("Number of DOC observations" = n(), "DOC range, mg/L" = paste(quantile(doc_mg.L, probs = c(0,0.5,1), na.rm = T), collapse = " / ")),
arles %>% subset(!is.na(q_L.s)) %>% group_by(year) %>% summarise("Number of Q observations" = n(), "Q range, L/s" = paste(quantile(q_L.s, probs = c(0,0.5,1), na.rm = T), collapse = " / ")), by = "year", all = T) %>% 
  merge(arles %>% group_by(year) %>% summarise("Number of days sampled" = length(unique(Date))), by = "year", all = T) %>%
  merge(arles %>% group_by(year) %>% summarise("Correlation DOC/log(Q)" = round(cor(doc_mg.L, log(q_L.s), use = "pairwise.complete.obs"),2)), by = "year", all = T) %>%
  rbind(c("All years", 
          dim(subset(arles, !is.na(doc_mg.L)))[1], 
          paste(quantile(arles$doc_mg.L, probs = c(0,0.5,1), na.rm = T), collapse = " / "), 
          dim(subset(arles, !is.na(q_L.s)))[1], 
          paste(quantile(arles$q_L.s, probs = c(0,0.5,1), na.rm = T), collapse = " / "), 
          length(unique(arles$Date)),
          round(cor(arles$doc_mg.L, log(arles$q_L.s), use = "pairwise.complete.obs" ),2)
          )) %>%
    rbind(c("Complete years", 
          dim(subset(arles_complete, !is.na(doc_mg.L)))[1], 
          paste(quantile(arles_complete$doc_mg.L, probs = c(0,0.5,1), na.rm = T), collapse = " / "), 
          dim(subset(arles_complete, !is.na(q_L.s)))[1], 
          paste(quantile(arles_complete$q_L.s, probs = c(0,0.5,1), na.rm = T), collapse = " / "), 
          length(unique(arles_complete$Date)),
          round(cor(arles_complete$doc_mg.L, log(arles_complete$q_L.s), use = "pairwise.complete.obs" ),2)
          )
          )

knitr::kable(summary_arles, caption = "Summary table of arles data") %>% kableExtra::kable_styling()

```

```{r histograms}
ggarrange(
  ggplot(arles_complete)+geom_histogram(aes(q_L.s),fill = "lightblue")+labs(x= "Débit, L/s", y = "")+theme_bw(),
  ggplot(arles_complete)+geom_histogram(aes(doc_mg.L), fill = "palegreen4")+labs(x= "DOC, mg/L", y = "")+theme_bw(),
  ggplot(arles_complete)+geom_histogram(aes(log10(q_L.s)),fill = "lightblue")+labs(x= "Débit (log10), L/s", y = "")+theme_bw(),
  ggplot(arles_complete)+geom_histogram(aes(log(doc_mg.L)), fill = "palegreen4")+labs(x= "DOC (log10), mg/L", y = "")+theme_bw()
)
```

# Test of methods for estimating fluxes when data is missing

## Minimize bias on average flow, data randomly missing

```{r ref-load-random-load}
set.seed(1806)

ref_arles <- arles_complete%>% group_by(year) %>% summarise(annual_load = sum(doc_mg.L*q_L.s*period, na.rm = T), sum_q = sum(q_L.s, na.rm = T), mean_q = mean(q_L.s, na.rm = T), slq = cov(doc_mg.L*q_L.s*period, q_L.s, use = "pairwise.complete.obs"), n_obs = n()) 

# Fonction d'échantillonnage par bloc
sample_block <- function(df, frac) {
  n <- nrow(df)
  block_size <- round(n * frac)
  start <- sample(1:n, 1)
  indices <- ((start - 1 + 0:(block_size - 1)) %% n) + 1
  return(df[indices, ])
}

# Génération de toutes les listes en une seule fois
fracs <- seq(0.1, 1, by = 0.1)

list_random <- lapply(fracs, function(frac) {
  lapply(1:1000, function(i) {
    arles_complete %>%
      group_by(year) %>%
      group_modify(~ sample_block(.x, frac)) %>%
      data.frame()
  })
}) %>% setNames(paste0("p", fracs * 100))

```

```{r bias-rating-curve}
# un modèle par dataframe dans chaque sous-liste
doc_model <- lapply(list_random, function(i) {
  lapply(i, lm, formula = doc_mg.L~q_L.s)})


# prédiction par sous-dataframe
list_predicted <- lapply(seq_along(list_random), 
                         FUN = function(i) {lapply(seq_along(list_random[[i]]), 
                                                    FUN = function(j){df <- list_random[[i]][[j]]
                                                                      df$doc_predicted <- predict(doc_model[[i]][[j]], newdata = df)
                                                                      return(df)
                                                                      }
                                                    )
                                            }
                         )
  
  
# liste de dataframes avec le résultat des calculs
list_load <- lapply(list_predicted, 
                    function(i) {lapply(i, 
                                        function(df) {df %>% group_by(year) %>% summarise(load = sum(doc_predicted*q_L.s*period, na.rm = T), sum_q = sum(q_L.s, na.rm = T), mean_q = mean(q_L.s, na.rm = T))
                                                      }
                                        )
                                }
                    )


# Calcul du flux par année
load_rating <- lapply(list_load, function(i){
  do.call(what = cbind, lapply(i, '[[',"load")) %>% rowMeans #Retourne un vecteur avec une valeur de flux par année
})
load_rating_df <- as.data.frame(load_rating) %>% setNames(names(list_random)) %>% cbind(year = complete_years) %>% tidyr::pivot_longer(cols = -year, names_to = "percent", values_to = "load")


# Biais absolu par année
bias_rating <- lapply(list_load, 
                      function(i) {lapply(i,function(j){
                        abs((j$load-ref_arles$annual_load)/ref_arles$annual_load*100)})
                      })
                        
# Biais moyen absolu
mean_bias_rating <- lapply(bias_rating, function(i){
                            as.data.frame(do.call(cbind,i)) %>% rowMeans #Calcule le biais moyen absolu par année                          
})
mean_bias_rating_df <- as.data.frame(mean_bias_rating) %>% setNames(names(list_random)) %>% cbind(year = complete_years) %>% tidyr::pivot_longer(cols = -year, names_to = "percent", values_to = "bias")

results_rating_df <- merge(load_rating_df, mean_bias_rating_df, by = c("percent","year"))


ggplot(results_rating_df,aes(x=year))+geom_line(data = ref_arles, aes(y=annual_load), size = 1)+
  geom_line(aes(y = load, group = percent, col = percent))+
  scale_color_viridis_d(direction = -1)+
  labs(x= "Year", y = "Annual load, tons", col = "% of randomly sampled data",title = "Average DOC load by year depending on percentage of data included", subtitle = "Reference annual load in black")+
  scale_x_continuous(breaks = complete_years, minor_breaks = NULL)+
  theme_minimal()+
  theme(legend.position = "bottom", axis.text.x = element_text(angle = 45))


ggplot()+
  geom_line(data = ref_arles, aes(x = year, y=mean_q/5), size = 1)+
  geom_line(data = results_rating_df, aes(x=year, y=bias, group = percent, col = percent))+
  scale_color_viridis_d(direction = -1)+
  labs(x= "Year", y = "Average absolute bias,%", col = "% of randomly \n sampled data", title = "Average absolute bias by year depending on percentage of data included", subtitle = "Average annual discharge in black")+
  scale_x_continuous(breaks = complete_years, minor_breaks = NULL)+
  scale_y_continuous(sec.axis = sec_axis(~.*5, name = "Average annual discharge, L/s"))+
  theme_minimal()+
  theme(legend.position = "bottom", axis.text.x = element_text(angle = 45))
```


### Verhoff ratio 1980


Known to be biaised. Compute yearly flux by:

* Randomly sampling 10 to 90% of each year, 1000 times
* Calculate annual load with ratio method for each year
* Compare with reference load and estimate average bias

```{r test-verhoff}
list_verhoff <- function(list_df){
  
list_load <- lapply(list_df,function(i) {i %>% group_by(year) %>% summarise(load = sum(doc_mg.L*q_L.s, na.rm = T), sum_q = sum(q_L.s, na.rm = T), mean_q = mean(q_L.s, na.rm = T))}) # génère une liste de dataframes
load_verhoff <- lapply(list_load, function(i) {(i$load/i$sum_q*ref_arles$mean_q[match(i$year, ref_arles$year)]*60*60*24*365)}) %>% do.call(what = cbind) %>% rowMeans #Retourne un vecteur avec une valeur de flux par année
bias_verhoff <- lapply(list_load, function(i) {abs(((i$load/i$sum_q*ref_arles$mean_q[match(i$year, ref_arles$year)]*60*60*24*365)-ref_arles$annual_load[match(i$year, ref_arles$year)])/ref_arles$annual_load[match(i$year, ref_arles$year)]*100)}) #Retourne une liste de vecteurs avec les 1000 biais par année, en valeur absolue. 
mean_bias_verhoff <- as.data.frame(do.call(cbind,bias_verhoff)) %>% rowMeans #Calcule le biais moyen absolu par année    
  
return(list(load_verhoff = load_verhoff,   mean_bias_verhoff = mean_bias_verhoff))
}  
  
  
results_verhoff <- lapply(list_random, list_verhoff)
results_verhoff_listdf <- lapply(results_verhoff, as.data.frame) %>% lapply(cbind, year = complete_years)
results_verhoff_df <- bind_rows(results_verhoff_listdf, .id = "percent")


ggplot(results_verhoff_df,aes(x=year))+geom_line(data = ref_arles, aes(y=annual_load), size = 1)+
  geom_line(aes(y = load_verhoff, group = percent, col = percent))+
  scale_color_viridis_d(direction = -1)+
  labs(x= "Year", y = "Annual load, tons", col = "% of randomly sampled data",title = "Average DOC load by year depending on percentage of data included", subtitle = "Reference annual load in black")+
  scale_x_continuous(breaks = complete_years, minor_breaks = NULL)+
  theme_minimal()+
  theme(legend.position = "bottom", axis.text.x = element_text(angle = 45))

ggplot()+
  geom_line(data = ref_arles, aes(x = year, y=mean_q/4), size = 1)+
  geom_line(data = results_verhoff_df, aes(x=year, y=mean_bias_verhoff, group = percent, col = percent))+
  scale_color_viridis_d(direction = -1)+
  labs(x= "Year", y = "Average absolute bias,%", col = "% of randomly \n sampled data", title = "Average absolute bias by year depending on percentage of data included", subtitle = "Average annual discharge in black")+
  scale_x_continuous(breaks = complete_years, minor_breaks = NULL)+
  scale_y_continuous(sec.axis = sec_axis(~.*4, name = "Average annual discharge, L/s"))+
  theme_minimal()+
  theme(legend.position = "bottom", axis.text.x = element_text(angle = 45))



```

### Camille's ratio

Based on the observation that sum(Li)/sum(Qi) = sum(La)/sum(Qa)

Bias = absolute bias

```{r test-camille}
list_camille <- function(list_df){
  
list_load <- lapply(list_df,function(i) {i %>% group_by(year) %>% summarise(load = sum(doc_mg.L*q_L.s*period, na.rm = T), sum_q = sum(q_L.s, na.rm = T), mean_q = mean(q_L.s, na.rm = T))}) # génère une liste de dataframes
load_camille <- lapply(list_load, function(i) {i$load/i$sum_q*ref_arles$sum_q[match(i$year, ref_arles$year)]}) %>% do.call(what = cbind) %>% rowMeans #Retourne un vecteur avec une valeur de flux par année
bias_camille <- lapply(list_load, function(i) {abs(((i$load/i$sum_q*ref_arles$sum_q[match(i$year, ref_arles$year[match(i$year, ref_arles$year)])])-ref_arles$annual_load[match(i$year, ref_arles$year)])/ref_arles$annual_load[match(i$year, ref_arles$year)]*100)}) #Retourne une liste de vecteurs avec les 1000 biais par année, en valeur absolue. 
mean_bias_camille <- as.data.frame(do.call(cbind,bias_camille)) %>% rowMeans #Calcule le biais moyen absolu par année    
  
return(list(load_camille = load_camille,   mean_bias_camille = mean_bias_camille))
}  
  
  
results_camille <- lapply(list_random, list_camille)
results_camille_listdf <- lapply(results_camille, as.data.frame) %>% lapply(cbind, year = complete_years)
results_camille_df <- bind_rows(results_camille_listdf, .id = "percent")


ggplot(results_camille_df,aes(x=year))+geom_line(data = ref_arles, aes(y=annual_load), size = 1)+
  geom_line(aes(y = load_camille, group = percent, col = percent))+
  scale_color_viridis_d(direction = -1)+
  labs(x= "Year", y = "Annual load, tons", col = "% of randomly sampled data",title = "Average DOC load by year depending on percentage of data included", subtitle = "Reference annual load in black")+
  scale_x_continuous(breaks = complete_years, minor_breaks = NULL)+
  theme_minimal()+
  theme(legend.position = "bottom", axis.text.x = element_text(angle = 45))


ggplot()+
  geom_line(data = ref_arles, aes(x = year, y=mean_q/6), size = 1)+
  geom_line(data = results_camille_df, aes(x=year, y=mean_bias_camille, group = percent, col = percent))+
  scale_color_viridis_d(direction = -1)+
  labs(x= "Year", y = "Average absolute bias,%", col = "% of randomly \n sampled data", title = "Average absolute bias by year depending on percentage of data included", subtitle = "Average annual discharge in black")+
  scale_x_continuous(breaks = complete_years, minor_breaks = NULL)+
  scale_y_continuous(sec.axis = sec_axis(~.*6, name = "Average annual discharge, L/s"))+
  theme_minimal()+
  theme(legend.position = "bottom", axis.text.x = element_text(angle = 45))
```