---
title: "naizin"
output:
  html_document:
    toc: true
    toc_float: true
    number_sections: true
    code_folding: hide
date: "2025-06-06"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = F, warning = F, error = F, fig.align = "center", collapse = T,
                      cache = T)
```

```{r libraries}
library(ggplot2)
library(ggpubr)

library(dplyr)
library(readxl)
library(lubridate)
library(knitr)
library(kableExtra)
library(imputeTS)
```

# Liens

https://www.ozcar-ri.org/fr/agrhys/

Bassin versant:
https://geosas.fr/geonetwork/srv/api/records/404bc60a-2943-44b5-9f35-9b13cd7895b5

DOC et discharge:
https://geosas.fr/agrhys/
https://geosas.fr/stav/espace/telechargement/?config=/apps//stav/config/agrhys.json


Autres liens
Description du site sur CatOpidor
https://cat.opidor.fr/index.php/AGRHYS

Description du site sur GeoBretagne et accès aux jeux de données:
https://geobretagne.fr/geonetwork/srv/api/records/5514e0c5-4406-4880-9cff-4df6f39c0f4f

https://geobretagne.fr/geonetwork/srv/fre/catalog.search#/search?query_string=%7B%22linkProtocol%22:%7B%22WWW:DOWNLOAD-1.0-http--download%22:true%7D%7 https://geobretagne.fr/geonetwork/srv/fre/catalog.search#/search?query_string=%7B%22linkProtocol%22:%7B%22WWW:DOWNLOAD-1.0-http--download%22:true%7D%7D

 

# Load data

```{r load-data-from-excel, message = F}
discharge <- read.csv("Données brutes/Outlet Exutoire_Rating curve_discharge.csv", sep = ";", col.names = c("DateHeure","q_m3.s"))
discharge$DateHeure <- ymd_hms(discharge$DateHeure)
doc <- read.csv("Données brutes/Outlet Exutoire_Shimadzu TOC Analyser_dissolved organic carbon.csv", sep = ";")
doc$DateHeure <- ymd_hms(doc$DateHeure)

```


```{r merge}
naizin <- merge(discharge,doc,by = "DateHeure")
naizin$year <- year(naizin$DateHeure)
naizin$commondate <- as.Date(paste0("2000-", format(naizin$DateHeure,"%j")), "%Y-%j")
naizin$Date <- format(naizin$DateHeure, "%Y-%m-%d")
naizin$period <- with(naizin, as.numeric(-(DateHeure - lead(DateHeure)))) # period is calculated in hours
```

```{r summary-data}

summary_naizin <- merge(
naizin %>% subset(!is.na(doc_mg.L)) %>% group_by(year) %>% summarise(nb_doc = n()),
naizin %>% subset(!is.na(q_m3.s)) %>% group_by(year) %>% summarise(nb_q = n()),
by = "year", all = T)  

summary_naizin %>% knitr::kable(caption = "Nombre d'observations de DOC et débit par an") %>% kableExtra::kable_styling()
cat("mean Q", mean(naizin$q_m3.s, na.rm = T))
cat("range OC (0-25-50-75-100)", quantile(with(naizin, doc_mg.L), na.rm = T))


# for later
complete_years <- c(2000:2024)
bv <- 5

```

# View data

```{r plot, fig.dim = c(10, 20)}
ggarrange(
ggplot(naizin, aes(x = commondate))+
  geom_point(aes(y = q_m3.s), alpha = 0.5, col = "lightblue")+
  scale_x_date(labels = function(x) format(x, "%d-%b"), date_minor_breaks = "1 month", name = "")+
  facet_grid(rows = vars(year))+
  labs(y = "Débit, m3/s", col = "")+
  theme_minimal(base_size = 15)+
  theme(legend.position = "none"),

ggplot(naizin, aes(x = commondate))+
  geom_point(aes(y = doc_mg.L), col = "palegreen4", alpha = 0.5)+
  scale_x_date(labels = function(x) format(x, "%d-%b"), date_minor_breaks = "1 month", name = "")+
  facet_grid(rows = vars(year))+
  labs(y = "DOC, mg/L", col = "")+
  theme_minimal(base_size = 15)+
  theme(legend.position = "none"))
```


```{r mean-q}
meanQcommondate <- naizin %>% group_by(commondate) %>% summarise(meanQ = mean(q_m3.s, na.rm = T))

ggplot()+geom_line(data = naizin, aes(x=commondate, y = q_m3.s, group = year, col = as.character(year)), alpha = 0.2, na.rm =T)+
  geom_line(data = meanQcommondate, aes(x=commondate, y = meanQ), col = "black")+
  scale_color_viridis_d(option = "G", end = 0.8)+
  labs(x = "", y = "Débit, m3/s", col = "")+
  scale_x_date(labels = function(x) format(x, "%d-%b"), date_minor_breaks = "1 month")+
  theme_minimal()+
  theme(legend.position = "none")
```
```{r mean-doc}
meanDOCcommondate <- naizin %>% group_by(commondate) %>% summarise(meanDOC = mean(doc_mg.L, na.rm = T))

ggplot()+geom_line(data = naizin, aes(x=commondate, y = doc_mg.L, group = year, col = as.character(year)), alpha = 0.2)+
  geom_line(data = meanDOCcommondate, aes(x=commondate, y = meanDOC), col = "black")+
  scale_color_viridis_d(option = "G", end = 0.8)+
  labs(x = "", y = "DOC, mg/L", col = "")+
  scale_x_date(labels = function(x) format(x, "%d-%b"), date_minor_breaks = "1 month")+
  scale_y_continuous(trans = "log")+
  theme_minimal()+
  theme(legend.position = "none")
```
```{r variable-distribution}
hist
```





# Annual and interannual flux 

Années choisies: toutes les années sauf la première. le ruisseau est intermittent.

On considère que l'erreur sur DOC vient de la mesure par analyse TOC A REFAIRE.

```{r uncertainties}
nyears <- length(complete_years)

naizin_flux <- naizin %>% filter(year %in% complete_years)


q_u <- 0.1

nobs <- dim(naizin_flux)[1]
nrep <- 1000
```

## total flux

```{r compute-flux}
#doc matrix
doc_meas <- matrix(naizin_flux$doc_mg.L, nrow = nrep, ncol = nobs, byrow = T) # repeats nrep lines with observations

doc_cv <- 3.2*doc_meas^(-0.6) # from all data available on 29/05/2026
doc_random <- matrix(rnorm(nrep*nobs, mean = 0, sd = 1), nrow=nrep, ncol = nobs)
doc_noise <- doc_cv*doc_random
doc_mat <- doc_meas * (1 + doc_noise/100) # final value of doc, with noise in percent

# Q matrix
q_meas <- matrix(naizin_flux$q_m3.s, nrow = nrep, ncol = nobs, byrow = T) # repeats nrow_boot times the vector q_m3.s
q_noise <- matrix(rnorm(nrep*nobs, mean = 0, sd = q_u), nrow = nrep, ncol = nobs) # creates a noise in percent (proportion), between 0 and 10%
q_mat <- q_meas * (1 + q_noise) # final value of q, with noise


# Flux per time step
flux_ton_mat <- doc_mat*1e-9*q_mat*1e3*24*60*60 # flux per period (period is 24h, so flux in ton/s is converted to flux per period). 
flux_ton.s_mat <- doc_mat*1e-9*q_mat*1e3 # without period



# Annual flux
index_years <- lapply(complete_years, function(y){which(naizin_flux$year == y)}) # list of indices corresponding to each year
annual_flux_ton.y <- sapply(index_years, function(idx){apply(flux_ton_mat[,idx], 1, sum, na.rm = T)}) # sum of fluxes per year, for each iteration of the bootstrap. Result is a matrix with nrow_boot rows and 19 columns (1 per year)
annual_flux_pi <- apply(annual_flux_ton.y, 2, quantile, probs = c(0.025, 0.5, 0.975), na.rm = T) # prediction interval for annual fluxes, per year. 3 lignes, 19 columns
annual_flux_mean <- colMeans(annual_flux_ton.y, na.rm = T) # mean annual flux per year. 1 vector
annual_flux_sd <- apply(annual_flux_ton.y, 2, sd, na.rm = T) # standard deviation of annual flux per year. Is just an estimate of goodness of mean, not as good as than the confidence interval. 

annual_flux_df <- data.frame(year = complete_years, 
                        annual_flux_mean = annual_flux_mean, 
                        annual_flux_variability = annual_flux_sd, 
                        annual_flux_pi_lower = annual_flux_pi[1,], 
                        annual_flux_pi_upper = annual_flux_pi[3,])

# Interannual flux 
interannual_flux_ton.y <- rowMeans(annual_flux_ton.y, na.rm = T) # mean interannual flux per iteration of the bootstrap
interannual_flux_pi <- quantile(interannual_flux_ton.y, probs = c(0.025, 0.5, 0.975), na.rm = T) # prediction interval
interannual_flux_mean <- mean(interannual_flux_ton.y, na.rm = T) # mean interannual flux
interannual_flux_variability <- sd(annual_flux_mean, na.rm = T) # standard deviation of interannual flux per year

interannual_flux_df <- data.frame(year = "interannual", annual_flux_mean = interannual_flux_mean, 
                                  annual_flux_variability = interannual_flux_variability,
                        annual_flux_pi_lower = interannual_flux_pi[1], 
                        annual_flux_pi_upper = interannual_flux_pi[3])

total_flux_df <- rbind(annual_flux_df, interannual_flux_df)
total_flux_df$group <- c(rep("annual", nyears), "interannual")

# Q df ----

annual_q <- sapply(index_years, function(idx){apply(q_mat[,idx], 1, sum, na.rm = T)}) # sum of fluxes per year, for each iteration of the bootstrap. Result is a matrix with nrow_boot rows and 19 columns (1 per year)
annual_q_pi <- apply(annual_q, 2, quantile, probs = c(0.025, 0.5, 0.975), na.rm = T) # prediction interval for annual fluxes, per year. 3 lignes, 19 columns
annual_q_mean <- colMeans(annual_q, na.rm = T) # mean annual flux per year. 1 vector
annual_q_sd <- apply(annual_q, 2, sd, na.rm = T) # standard deviation of annual flux per year. Is just an estimate of goodness of mean, not as good as than the confidence interval. 
interannual_q <- rowMeans(annual_q, na.rm = T) # mean interannual flux per iteration of the bootstrap
interannual_q_pi <- quantile(interannual_q, probs = c(0.025, 0.5, 0.975), na.rm = T) # prediction interval
interannual_q_mean <- mean(interannual_q, na.rm = T) # mean interannual flux
interannual_q_variability <- sd(annual_q_mean, na.rm = T) # standard deviation of interannual flux per year

q_df <- data.frame(year = c(complete_years, "interannual"), 
                        q_mean = c(annual_q_mean, interannual_q_mean),
                        q_variability = c(annual_flux_sd, interannual_q_variability), 
                        q_pi_lower = c(annual_q_pi[1,], interannual_q_pi[1]), 
                        q_pi_upper = c(annual_q_pi[3,], interannual_q_pi[3]),
                   group = c(rep("annual", nyears), "interannual"))

# Plot -----
ggplot()+
  geom_col(data = total_flux_df, aes(x=year, y = annual_flux_mean, fill = group))+
    geom_errorbar(data = total_flux_df, aes(x = year, ymin = annual_flux_pi_lower, ymax = annual_flux_pi_upper, col = "prediction interval"), width = 0.3, size = 0.8)+
  geom_errorbar(data = filter(total_flux_df, year == "interannual"), aes(x = year, ymin = annual_flux_mean - annual_flux_variability, ymax = annual_flux_mean + annual_flux_variability, col = "interannual variability"), width = 0.2, size = 0.8, linetype = 2)+
  scale_fill_manual(values = c("annual" = "lightblue", "interannual" = "indianred"))+
  scale_color_manual(values = c("prediction interval" = "darkblue", "interannual variability" = "darkred"), name = "")+
   labs(x = "Year", y = "Flux (ton/year)", fill = "")+
  theme_minimal(base_size = 15)+
  theme(axis.text.x = element_text(angle = 45, hjust = 1), legend.position = "bottom")

ggplot()+
  geom_col(data = q_df, aes(x=year, y = q_mean, fill = group))+
    geom_errorbar(data = q_df, aes(x = year, ymin = q_pi_lower, ymax = q_pi_upper, col = "prediction interval"), width = 0.3, size = 0.8)+
  geom_errorbar(data = filter(q_df, year == "interannual"), aes(x = year, ymin = q_mean - q_variability, ymax = q_mean + q_variability, col = "interannual variability"), width = 0.2, size = 0.8, linetype = 2)+
  scale_fill_manual(values = c("annual" = "lightblue", "interannual" = "indianred"))+
  scale_color_manual(values = c("prediction interval" = "darkblue", "interannual variability" = "darkred"), name = "")+
   labs(x = "Year", y = "Discharge (m3/year)", fill = "")+
  theme_minimal(base_size = 15)+
  theme(axis.text.x = element_text(angle = 45, hjust = 1), legend.position = "bottom")

knitr::kable(total_flux_df, digits = 2, row.names = F) %>% kableExtra::kable_styling()

```

## Specific flux

```{r specific-flux}
sflux_ton_mat <- doc_mat*1e-9*q_mat*1e3*24*60*60/bv # flux per period (period in h, so flux in ton/s is converted to flux per period). 
sflux_ton.s_mat <- doc_mat*1e-9*q_mat*1e3/bv # without period

annual_sflux_ton.y <- sapply(index_years, function(idx){apply(sflux_ton_mat[,idx], 1, sum, na.rm = T)}) # sum of fluxes per year, for each iteration of the bootstrap. Result is a matrix with nrow_boot rows and 19 columns (1 per year)
annual_sflux_pi <- apply(annual_sflux_ton.y, 2, quantile, probs = c(0.025, 0.5, 0.975), na.rm = T) # prediction interval for annual fluxes, per year. 3 lignes, 19 columns
annual_sflux_mean <- colMeans(annual_sflux_ton.y, na.rm = T) # mean annual flux per year. 1 vector
annual_sflux_sd <- apply(annual_sflux_ton.y, 2, sd, na.rm = T) # standard deviation of annual flux per year. Is just an estimate of goodness of mean, not as good as than the confidence interval. 

annual_sflux_df <- data.frame(year = complete_years, 
                        annual_flux_mean = annual_sflux_mean, 
                        annual_flux_variability = annual_sflux_sd, 
                        annual_flux_pi_lower = annual_sflux_pi[1,], 
                        annual_flux_pi_upper = annual_sflux_pi[3,])

# Interannual flux 
interannual_sflux_ton.y <- rowMeans(annual_sflux_ton.y, na.rm = T) # mean interannual flux per iteration of the bootstrap
interannual_sflux_pi <- quantile(interannual_sflux_ton.y, probs = c(0.025, 0.5, 0.975), na.rm = T) # prediction interval
interannual_sflux_mean <- mean(interannual_sflux_ton.y, na.rm = T) # mean interannual flux
interannual_sflux_variability <- sd(annual_sflux_mean, na.rm = T) # standard deviation of interannual flux per year

interannual_sflux_df <- data.frame(year = "interannual", annual_flux_mean = interannual_sflux_mean, 
                                  annual_flux_variability = interannual_sflux_variability,
                        annual_flux_pi_lower = interannual_sflux_pi[1], 
                        annual_flux_pi_upper = interannual_sflux_pi[3])

total_sflux_df <- rbind(annual_sflux_df, interannual_sflux_df)
total_sflux_df$group <- c(rep("annual", nyears), "interannual")

ggplot()+
  geom_col(data = total_sflux_df, aes(x=year, y = annual_flux_mean, fill = group), width = 0.8)+
    geom_errorbar(data = total_sflux_df, aes(x = year, ymin = annual_flux_pi_lower, ymax = annual_flux_pi_upper, col = "prediction interval"), width = 0.3, size = 0.8)+
  geom_errorbar(data = filter(total_sflux_df, year == "interannual"), aes(x = year, ymin = annual_flux_mean - annual_flux_variability, ymax = annual_flux_mean + annual_flux_variability, col = "interannual variability"), width = 0.2, size = 0.8, linetype = 2)+
  scale_fill_manual(values = c("annual" = "lightblue", "interannual" = "indianred"))+
  scale_color_manual(values = c("prediction interval" = "darkblue", "interannual variability" = "darkred"), name = "")+
   labs(x = "Year", y = "Flux (tons/km2/year)", fill = "")+
  theme_minimal(base_size = 15)+
  theme(axis.text.x = element_text(angle = 45, hjust = 1), legend.position = "bottom")

ggsave("sflux_naizin.svg")

knitr::kable(total_sflux_df, digits = 3, row.names = F) %>% kableExtra::kable_styling()
```


```{r exit, cache = F}
knitr::knit_exit()
```


## Variance



```{r test}
C <- as.vector(doc_mat)
Q <- as.vector(q_mat)
F <- C * Q

# Décomposition exacte du produit
term1 <- mean(Q)^2 * var(C)          # effet C pur
term2 <- mean(C)^2 * var(Q)          # effet Q pur  
term3 <- var(C) * var(Q)             # interaction C×Q
term4 <- 2 * mean(C) * mean(Q) * cov(C, Q)  # covariance (≈0 dans ton cas)

cat("Var(F) observée       :", var(F), "\n")
cat("Var(F) reconstituée   :", term1 + term2 + term3 + term4, "\n")
cat("\nPart effet C pur      :", 100 * term1 / var(F), "%\n")
cat("Part effet Q pur      :", 100 * term2 / var(F), "%\n")
cat("Part interaction C×Q  :", 100 * term3 / var(F), "%\n")
```


```{r test-gel}
cat("tot var", var(as.vector(doc_mat*q_mat)),"\n")
cat("tot var units converted", var(as.vector(doc_mat*1e-9*q_mat*1e3*24*60*60)),"\n")
cat("var DOC fixed", var(as.vector(naizin_flux$doc_mg.L*1e-9*q_mat*1e3*24*60*60)),"\n")
cat("var Q fixed", var(as.vector(doc_mat*1e-9*naizin_flux$q_m3.s*1e3*24*60*60)),"\n")
cat("%var explained by DOC", var(as.vector(naizin_flux$doc_mg.L*1e-9*q_mat*1e3*24*60*60))/var(as.vector(doc_mat*1e-9*q_mat*1e3*24*60*60))*100, "% \n")
cat("%var explained by Q", var(as.vector(doc_mat*1e-9*naizin_flux$q_m3.s*1e3*24*60*60))/var(as.vector(doc_mat*1e-9*q_mat*1e3*24*60*60))*100, "% \n")

cat("tot var s", var(as.vector(doc_mat*1e-9*q_mat*1e3)),"\n")
cat("var DOC fixed", var(as.vector(naizin_flux$doc_mg.L*1e-9*q_mat*1e3)),"\n")
cat("var Q fixed", var(as.vector(doc_mat*1e-9*naizin_flux$q_m3.s*1e3)),"\n")
cat("%var explained by Q", var(as.vector(naizin_flux$doc_mg.L*1e-9*q_mat*1e3))/var(as.vector(doc_mat*1e-9*q_mat*1e3))*100, "% \n")
cat("%var explained by DOC", var(as.vector(doc_mat*1e-9*naizin_flux$q_m3.s*1e3))/var(as.vector(doc_mat*1e-9*q_mat*1e3))*100, "% \n")

```
```{r test-log-var}
log_doc <- log(as.vector(doc_mat*1e-9))
log_q <- log(as.vector(q_mat*1e3))
log_flux <- log(as.vector(doc_mat*1e-9*q_mat*1e3))

vcov_log <- cov(log_doc, log_q, use = "pairwise.complete.obs")

var_log_total <- var(log_doc)+var(log_q)+2*vcov_log

cat("\n=== Décomposition log-variance (exacte) ===\n")
cat(sprintf("Part de doc : %.1f %%\n", 100 * var(log_doc) / var_log_total))
cat(sprintf("Part de q: %.1f %%\n", 100 * var(log_q) / var_log_total))


```

Calculer la variance par année ? Par observation, pour voir dans les cas de DOC petit si la variance de DOC prend plus de place que la variance de Q ? 

```{r variance-per-obs}
q_var_perobs <- apply(naizin_flux$doc_mg.L*1e-9*q_mat*1e3, 2, var)
doc_var_perobs <- apply(doc_mat*1e-9*naizin_flux$q_m3.s*1e3, 2, var)
tot_var_perobs <- apply(doc_mat*1e-9*q_mat*1e3, 2, var)

cov_bycol <- function(mat1, mat2){
  n <- dim(mat1)[2]
  cov_vec <- vector("numeric", n)
  for(i in 1:n){
      cov_vec[i] <- cov(mat1[,i], mat2[,i])    
  }
return(cov_vec)
}

cov_perobs <- cov_bycol(doc_mat*1e-9, q_mat*1e3)

tot_var_perobs <- naizin_flux$q_m3.s^2*doc_var_perobs + naizin_flux$doc_mg.L*q_var_perobs+
  q_var_perobs*doc_var_perobs + 2*naizin_flux$q_m3.s*naizin_flux$doc_mg.L*cov_perobs


boxplot(q_var_perobs)
boxplot(doc_var_perobs)
boxplot(tot_var_perobs)

var_df <- cbind(q_var_perobs,doc_var_perobs,tot_var_perobs,naizin_flux$doc_mg.L, naizin_flux$q_m3.s) %>% as.data.frame()
names(var_df) <- c("q_var","doc_var","tot_var","doc_mg.L","q_m3.s")

ggplot(var_df, aes(x= doc_mg.L)) + 
  geom_col(aes(y = doc_var, fill = "doc_var")) + 
  geom_col(aes(y = q_var, fill = "q_var"))+
  geom_col(aes(y = tot_var, fill = "tot var"))


doc_var_perobs_percent <- doc_var_perobs/tot_var_perobs*100
q_var_perobs_percent <- q_var_perobs/tot_var_perobs*100

var_df_long <- rbind(cbind(naizin_flux$doc_mg.L,"doc",doc_var_perobs_percent),
                     cbind(naizin_flux$doc_mg.L,"Q",q_var_perobs_percent)) %>%
  as.data.frame()
ggplot(var_df_long)+
  geom_bar(aes(x=as.numeric(V1), y = as.numeric(doc_var_perobs_percent), fill = V2), position = "stack", stat = "identity")
```

