---
title: "Avenelles - méthodes"
author: "CamilMC"
date: "2026-06-17"
output:
  html_document:
    toc: true
    toc_float: true
    number_sections: true
    code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = F, warning = F, error = F, fig.align = "center", collapse = T,
                      cache = F)
```

```{r libraries}
lapply(c("dplyr"), library, character.only = T)
lapply(c("ggplot2","ggpubr"), library, character.only = T)
lapply(c("lubridate"), library, character.only = T)
lapply(c("knitr","kableExtra"), library, character.only = T)

```
# Data visualisation

## Get data

```{r bv-aire}
bv <- 45
```


```{r load-data-from-excel, message = F}

avenelles <- readxl::read_xlsx(path = "Data_Avenelles_DOC_DIC_Debit.xlsx", sheet = "Data_Avenelles_DOC_DIC_Debit", col_types = c("date","numeric", "text","numeric","text","numeric","text","text","numeric")) %>%  mutate(Site = NULL, bv_km2 = NULL) %>% unique()

avenelles$year <- year(avenelles$DateHeure)
avenelles$week <- week(avenelles$DateHeure)
avenelles$month <- month(avenelles$DateHeure)

avenelles$commondate <- as.Date(paste0("2000-", format(avenelles$DateHeure,"%j")), "%Y-%j")
avenelles$Date <- format(avenelles$DateHeure, "%Y-%m-%d") %>% as.Date()

avenelles$period <- with(avenelles, as.numeric(-(DateHeure - lead(DateHeure)))) # period in second between 2 lines. This leads to some large periods being calculated when data is missing / not sampled during a long interval. 
avenelles$periodj <- round(avenelles$period / 60 / 60 / 24, 0)
avenelles[which(avenelles$periodj > 4),"period"] <- 2*24*60*60 # the median time of sampling is every second day. This line replaces periods that are artificially longer than 2 days
avenelles[which(avenelles$periodj > 4),"periodj"] <- 2

avenelles <- unique(avenelles)
  
strange_periods_dates <- avenelles %>% subset(periodj > 4) %>% pull(Date) 

```

## Characteristics

```{r summary-data}
summary_avenelles <- merge(
avenelles %>% subset(!is.na(doc_mg.L)) %>% group_by(year) %>% summarise("Number of DOC observations" = n(), "DOC range, mg/L" = paste(quantile(doc_mg.L, probs = c(0,0.5,1), na.rm = T), collapse = " / ")),
avenelles %>% subset(!is.na(q_L.s)) %>% group_by(year) %>% summarise("Number of Q observations" = n(), "Q range, L/s" = paste(quantile(q_L.s, probs = c(0,0.5,1), na.rm = T), collapse = " / ")), by = "year", all = T) %>% 
  merge(avenelles %>% group_by(year) %>% summarise("Number of days sampled" = length(unique(Date))), by = "year", all = T) %>%
  merge(avenelles %>% group_by(year) %>% summarise("Correlation DOC/log(Q)" = round(cor(doc_mg.L, log(q_L.s), use = "pairwise.complete.obs"),2)), by = "year", all = T) %>%
  rbind(c("All years", 
          dim(subset(avenelles, !is.na(doc_mg.L)))[1], 
          paste(quantile(avenelles$doc_mg.L, probs = c(0,0.5,1), na.rm = T), collapse = " / "), 
          dim(subset(avenelles, !is.na(q_L.s)))[1], 
          paste(quantile(avenelles$q_L.s, probs = c(0,0.5,1), na.rm = T), collapse = " / "), 
          length(unique(avenelles$Date)),
          round(cor(avenelles$doc_mg.L, log(avenelles$q_L.s), use = "pairwise.complete.obs" ),2)
          ))

knitr::kable(summary_avenelles, caption = "Summary table of Avenelles data") %>% kableExtra::kable_styling()

```

```{r plot-by-year-doc, fig.dim = c(10,15)}


title <- expression(atop("Series of DOC and Q by year"))
plots <- ggarrange(
ggplot(avenelles, aes(x = commondate))+
  geom_point(aes(y = q_L.s, col = "Débit, L/s"), alpha = 0.5)+
  scale_x_date(labels = function(x) format(x, "%d-%b"), date_minor_breaks = "1 month", name = "")+
  scale_color_manual(values = c("lightblue"), name = "")+
  facet_grid(rows = vars(year))+
  labs(y = "Débit, L/s", col = "")+
  theme_minimal(base_size = 15)+
  theme(legend.position = "none"),

ggplot(avenelles, aes(x = commondate))+
  geom_point(aes(y = doc_mg.L, col = "DOC, mg.L"), alpha = 0.5)+
  scale_x_date(labels = function(x) format(x, "%d-%b"), date_minor_breaks = "1 month", name = "")+
  scale_color_manual(values = c("palegreen4"), name = "")+
  facet_grid(rows = vars(year))+
  labs(y = "DOC, mg/L", col = "")+
  theme_minimal(base_size = 15)+
  theme(legend.position = "none")
)

annotate_figure(plots, top = text_grob(title))

```

DOC observation for year 2014 are FALSE: there has been a mix between DIC and DOC data (confirmed by Sophie Guillon). 2014 is excluded from the analysis. Data for 2015 seem to be partially wrong as well. 

Years to use for test of methods: `r complete_years <- c(2006,2007,2008,2009,2010,2011,2012,2013,2016,2017,2018,2019,2021)`

# Test of methods

```{r ref-load-random-load}
set.seed(1806)

ref_load <- avenelles %>% subset(year %in% complete_years) %>% group_by(year) %>% summarise(annual_load = sum(doc_mg.L*q_L.s*period, na.rm = T), sum_q = sum(q_L.s, na.rm = T), mean_q = mean(q_L.s, na.rm = T)) 

avenelles_p10 <- lapply(1:1000, function(i) data.frame(avenelles %>% subset(year %in% complete_years) %>% group_by(year) %>% sample_frac(10*1e-2)))
avenelles_p20 <- lapply(1:1000, function(i) data.frame(avenelles %>% subset(year %in% complete_years) %>% group_by(year) %>% sample_frac(20*1e-2)))
avenelles_p30 <- lapply(1:1000, function(i) data.frame(avenelles %>% subset(year %in% complete_years) %>% group_by(year) %>% sample_frac(30*1e-2)))
avenelles_p40 <- lapply(1:1000, function(i) data.frame(avenelles %>% subset(year %in% complete_years) %>% group_by(year) %>% sample_frac(40*1e-2)))
avenelles_p50 <- lapply(1:1000, function(i) data.frame(avenelles %>% subset(year %in% complete_years) %>% group_by(year) %>% sample_frac(50*1e-2)))
avenelles_p60 <- lapply(1:1000, function(i) data.frame(avenelles %>% subset(year %in% complete_years) %>% group_by(year) %>% sample_frac(60*1e-2)))
avenelles_p70 <- lapply(1:1000, function(i) data.frame(avenelles %>% subset(year %in% complete_years) %>% group_by(year) %>% sample_frac(70*1e-2)))
avenelles_p80 <- lapply(1:1000, function(i) data.frame(avenelles %>% subset(year %in% complete_years) %>% group_by(year) %>% sample_frac(80*1e-2)))
avenelles_p90 <- lapply(1:1000, function(i) data.frame(avenelles %>% subset(year %in% complete_years) %>% group_by(year) %>% sample_frac(90*1e-2)))
avenelles_p100 <- lapply(1:1000, function(i) data.frame(avenelles %>% subset(year %in% complete_years) %>% group_by(year) %>% sample_frac(100*1e-2)))

```

## Verhoff ratio 1980


Known to be biaised. Compute yearly flux by:

* Randomly sampling 10 to 90% of each year, 1000 times
* Calculate annual load with ratio method for each year
* Compare with reference load and estimate average bias

```{r test-verhoff}

avenelles_p10_load <- lapply(avenelles_p10, function(i) {i %>% group_by(year) %>% summarise(load = sum(doc_mg.L*q_L.s, na.rm = T), sum_q = sum(q_L.s, na.rm = T), mean_q = mean(q_L.s))})
avenelles_p10_meanload <- lapply(avenelles_p10_load, function(i) {round((i$load/i$sum_q*ref_load$mean_q*60*60*24*365))}) %>% do.call(what = cbind) %>% rowMeans
avenelles_p10_bias <- lapply(avenelles_p10_load, function(i) {round(((i$load/i$sum_q*ref_load$mean_q*60*60*24*365)-ref_load$annual_load)/ref_load$annual_load*100)}) 
avenelles_p10_meanbiais <- as.data.frame(do.call(cbind,avenelles_p10_bias)) %>% rowMeans

avenelles_p20_load <- lapply(avenelles_p20, function(i) {i %>% group_by(year) %>% summarise(load = sum(doc_mg.L*q_L.s, na.rm = T), sum_q = sum(q_L.s, na.rm = T), mean_q = mean(q_L.s))})
avenelles_p20_meanload <- lapply(avenelles_p20_load, function(i) {round((i$load/i$sum_q*ref_load$mean_q*60*60*24*365))}) %>% do.call(what = cbind) %>% rowMeans
avenelles_p20_bias <- lapply(avenelles_p20_load, function(i) {round(((i$load/i$sum_q*ref_load$mean_q*60*60*24*365)-ref_load$annual_load)/ref_load$annual_load*100)}) 
avenelles_p20_meanbiais <- as.data.frame(do.call(cbind,avenelles_p20_bias)) %>% rowMeans

avenelles_p30_load <- lapply(avenelles_p30, function(i) {i %>% group_by(year) %>% summarise(load = sum(doc_mg.L*q_L.s, na.rm = T), sum_q = sum(q_L.s, na.rm = T), mean_q = mean(q_L.s))})
avenelles_p30_meanload <- lapply(avenelles_p30_load, function(i) {round((i$load/i$sum_q*ref_load$mean_q*60*60*24*365))}) %>% do.call(what = cbind) %>% rowMeans
avenelles_p30_bias <- lapply(avenelles_p30_load, function(i) {round(((i$load/i$sum_q*ref_load$mean_q*60*60*24*365)-ref_load$annual_load)/ref_load$annual_load*100)}) 
avenelles_p30_meanbiais <- as.data.frame(do.call(cbind,avenelles_p30_bias)) %>% rowMeans

avenelles_p40_load <- lapply(avenelles_p40, function(i) {i %>% group_by(year) %>% summarise(load = sum(doc_mg.L*q_L.s, na.rm = T), sum_q = sum(q_L.s, na.rm = T), mean_q = mean(q_L.s))})
avenelles_p40_meanload <- lapply(avenelles_p40_load, function(i) {round((i$load/i$sum_q*ref_load$mean_q*60*60*24*365))}) %>% do.call(what = cbind) %>% rowMeans
avenelles_p40_bias <- lapply(avenelles_p40_load, function(i) {round(((i$load/i$sum_q*ref_load$mean_q*60*60*24*365)-ref_load$annual_load)/ref_load$annual_load*100)}) 
avenelles_p40_meanbiais <- as.data.frame(do.call(cbind,avenelles_p40_bias)) %>% rowMeans

avenelles_p50_load <- lapply(avenelles_p50, function(i) {i %>% group_by(year) %>% summarise(load = sum(doc_mg.L*q_L.s, na.rm = T), sum_q = sum(q_L.s, na.rm = T), mean_q = mean(q_L.s))})
avenelles_p50_meanload <- lapply(avenelles_p50_load, function(i) {round((i$load/i$sum_q*ref_load$mean_q*60*60*24*365))}) %>% do.call(what = cbind) %>% rowMeans
avenelles_p50_bias <- lapply(avenelles_p50_load, function(i) {round(((i$load/i$sum_q*ref_load$mean_q*60*60*24*365)-ref_load$annual_load)/ref_load$annual_load*100)}) 
avenelles_p50_meanbiais <- as.data.frame(do.call(cbind,avenelles_p50_bias)) %>% rowMeans

avenelles_p60_load <- lapply(avenelles_p60, function(i) {i %>% group_by(year) %>% summarise(load = sum(doc_mg.L*q_L.s, na.rm = T), sum_q = sum(q_L.s, na.rm = T), mean_q = mean(q_L.s))})
avenelles_p60_meanload <- lapply(avenelles_p60_load, function(i) {round((i$load/i$sum_q*ref_load$mean_q*60*60*24*365))}) %>% do.call(what = cbind) %>% rowMeans
avenelles_p60_bias <- lapply(avenelles_p60_load, function(i) {round(((i$load/i$sum_q*ref_load$mean_q*60*60*24*365)-ref_load$annual_load)/ref_load$annual_load*100)}) 
avenelles_p60_meanbiais <- as.data.frame(do.call(cbind,avenelles_p60_bias)) %>% rowMeans

avenelles_p70_load <- lapply(avenelles_p70, function(i) {i %>% group_by(year) %>% summarise(load = sum(doc_mg.L*q_L.s, na.rm = T), sum_q = sum(q_L.s, na.rm = T), mean_q = mean(q_L.s))})
avenelles_p70_meanload <- lapply(avenelles_p70_load, function(i) {round((i$load/i$sum_q*ref_load$mean_q*60*60*24*365))}) %>% do.call(what = cbind) %>% rowMeans
avenelles_p70_bias <- lapply(avenelles_p70_load, function(i) {round(((i$load/i$sum_q*ref_load$mean_q*60*60*24*365)-ref_load$annual_load)/ref_load$annual_load*100)}) 
avenelles_p70_meanbiais <- as.data.frame(do.call(cbind,avenelles_p70_bias)) %>% rowMeans

avenelles_p80_load <- lapply(avenelles_p80, function(i) {i %>% group_by(year) %>% summarise(load = sum(doc_mg.L*q_L.s, na.rm = T), sum_q = sum(q_L.s, na.rm = T), mean_q = mean(q_L.s))})
avenelles_p80_meanload <- lapply(avenelles_p80_load, function(i) {round((i$load/i$sum_q*ref_load$mean_q*60*60*24*365))}) %>% do.call(what = cbind) %>% rowMeans
avenelles_p80_bias <- lapply(avenelles_p80_load, function(i) {round(((i$load/i$sum_q*ref_load$mean_q*60*60*24*365)-ref_load$annual_load)/ref_load$annual_load*100)}) 
avenelles_p80_meanbiais <- as.data.frame(do.call(cbind,avenelles_p80_bias)) %>% rowMeans

avenelles_p90_load <- lapply(avenelles_p90, function(i) {i %>% group_by(year) %>% summarise(load = sum(doc_mg.L*q_L.s, na.rm = T), sum_q = sum(q_L.s, na.rm = T), mean_q = mean(q_L.s))})
avenelles_p90_meanload <- lapply(avenelles_p90_load, function(i) {round((i$load/i$sum_q*ref_load$mean_q*60*60*24*365))}) %>% do.call(what = cbind) %>% rowMeans
avenelles_p90_bias <- lapply(avenelles_p90_load, function(i) {round(((i$load/i$sum_q*ref_load$mean_q*60*60*24*365)-ref_load$annual_load)/ref_load$annual_load*100)}) 
avenelles_p90_meanbiais <- as.data.frame(do.call(cbind,avenelles_p90_bias)) %>% rowMeans

avenelles_p100_load <- lapply(avenelles_p100, function(i) {i %>% group_by(year) %>% summarise(load = sum(doc_mg.L*q_L.s, na.rm = T), sum_q = sum(q_L.s, na.rm = T), mean_q = mean(q_L.s))})
avenelles_p100_meanload <- lapply(avenelles_p100_load, function(i) {round((i$load/i$sum_q*ref_load$mean_q*60*60*24*365))}) %>% do.call(what = cbind) %>% rowMeans
avenelles_p100_bias <- lapply(avenelles_p100_load, function(i) {round(((i$load/i$sum_q*ref_load$mean_q*60*60*24*365)-ref_load$annual_load)/ref_load$annual_load*100)}) 
avenelles_p100_meanbiais <- as.data.frame(do.call(cbind,avenelles_p100_bias)) %>% rowMeans

data.frame(
  Year = complete_years,
  "Annual load, tons" = ref_load$annual_load * 1e-9,
  "Average estimated load, 10% of data" = avenelles_p10_meanload * 1e-9,
  "Average bias, 10 % of data" = avenelles_p10_meanbiais,
    "Average estimated load, 20% of data" = avenelles_p20_meanload * 1e-9,
  "Average bias, 20 % of data" = avenelles_p20_meanbiais,
    "Average estimated load, 30% of data" = avenelles_p30_meanload * 1e-9,
  "Average bias, 30 % of data" = avenelles_p30_meanbiais,
    "Average estimated load, 40% of data" = avenelles_p40_meanload * 1e-9,
  "Average bias, 40 % of data" = avenelles_p40_meanbiais,
    "Average estimated load, 50% of data" = avenelles_p50_meanload * 1e-9,
  "Average bias, 50 % of data" = avenelles_p50_meanbiais,
    "Average estimated load, 60% of data" = avenelles_p60_meanload * 1e-9,
  "Average bias, 60 % of data" = avenelles_p60_meanbiais,
    "Average estimated load, 70% of data" = avenelles_p70_meanload * 1e-9,
  "Average bias, 70 % of data" = avenelles_p70_meanbiais,
    "Average estimated load, 80% of data" = avenelles_p80_meanload * 1e-9,
  "Average bias, 80 % of data" = avenelles_p80_meanbiais,
    "Average estimated load, 90% of data" = avenelles_p90_meanload * 1e-9,
  "Average bias, 90 % of data" = avenelles_p90_meanbiais,
    "Average estimated load, 100% of data" = avenelles_p100_meanload * 1e-9,
  "Average bias, 100 % of data" = avenelles_p100_meanbiais,
  check.names = F
)  %>% knitr::kable(digits = 2) %>% kableExtra::kable_styling()


summary_df <- data.frame(
  year = complete_years,
  annual_load_ref = ref_load$annual_load * 1e-9,
  annual_load_p10 = avenelles_p10_meanload * 1e-9,
  bias_p10 = avenelles_p10_meanbiais,
  annual_load_p20 = avenelles_p20_meanload * 1e-9,
  bias_p20 = avenelles_p20_meanbiais,
  annual_load_p30 = avenelles_p30_meanload * 1e-9,
  bias_p30 = avenelles_p30_meanbiais,
  annual_load_p40 = avenelles_p40_meanload * 1e-9,
  bias_p40 = avenelles_p40_meanbiais,
  annual_load_p50 = avenelles_p50_meanload * 1e-9,
  bias_p50 = avenelles_p50_meanbiais,
  annual_load_p60 = avenelles_p60_meanload * 1e-9,
  bias_p60 = avenelles_p60_meanbiais,
  annual_load_p70 = avenelles_p70_meanload * 1e-9,
  bias_p70 = avenelles_p70_meanbiais,
  annual_load_p80 = avenelles_p80_meanload * 1e-9,
  bias_p80 = avenelles_p80_meanbiais,
  annual_load_p90 = avenelles_p90_meanload * 1e-9,
  bias_p90 = avenelles_p90_meanbiais,
  annual_load_p100 = avenelles_p100_meanload * 1e-9,
  bias_p100 = avenelles_p100_meanbiais)

ggplot(summary_df,aes(x=year))+geom_line(aes(y=annual_load_ref), size = 1)+
  geom_line(aes(y=annual_load_p10, col = "10%"))+
    geom_line(aes(y=annual_load_p20, col = "20%"))+
    geom_line(aes(y=annual_load_p30, col = "30%"))+
    geom_line(aes(y=annual_load_p40, col = "40%"))+
    geom_line(aes(y=annual_load_p50, col = "50%"))+
    geom_line(aes(y=annual_load_p60, col = "60%"))+
    geom_line(aes(y=annual_load_p70, col = "70%"))+
    geom_line(aes(y=annual_load_p80, col = "80%"))+
    geom_line(aes(y=annual_load_p90, col = "90%"))+
    geom_line(aes(y=annual_load_p100, col = " 100%"))+
  scale_color_viridis_d(direction = -1)+
  labs(x= "Year", y = "Annual load, tons", col = "% of randomly sampled data",title = "Average DOC load by year depending on percentage of data included", subtitle = "Reference annual load in black")+
  scale_x_continuous(breaks = complete_years, minor_breaks = NULL)+
  theme_minimal()+
  theme(legend.position = "bottom", axis.text.x = element_text(angle = 45))

ggplot(summary_df,aes(x=year))+geom_line(data = ref_load, aes(x = year, y=mean_q/3), size = 1)+
  geom_line(aes(y=bias_p10, col = "10%"))+
    geom_line(aes(y=bias_p20, col = "20%"))+
    geom_line(aes(y=bias_p30, col = "30%"))+
    geom_line(aes(y=bias_p40, col = "40%"))+
    geom_line(aes(y=bias_p50, col = "50%"))+
    geom_line(aes(y=bias_p60, col = "60%"))+
    geom_line(aes(y=bias_p70, col = "70%"))+
    geom_line(aes(y=bias_p80, col = "80%"))+
    geom_line(aes(y=bias_p90, col = "90%"))+
    geom_line(aes(y=bias_p100, col = " 100%"))+
  scale_color_viridis_d(direction = -1)+
  labs(x= "Year", y = "Average bias,%", col = "% of randomly \n sampled data", title = "Average bias by year depending on percentage of data included", subtitle = "Average annual discharge in black")+
  scale_x_continuous(breaks = complete_years, minor_breaks = NULL)+
  scale_y_continuous(sec.axis = sec_axis(~.*3, name = "Average annual discharge, L/s"))+
  theme_minimal()+
  theme(legend.position = "bottom", axis.text.x = element_text(angle = 45))


```



## Camille's ratio

Based on the observation that sum(Li)/sum(Qi) = sum(La)/sum(Qa)

Bias = absolute bias

```{r test-camille}

avenelles_p10_load <- lapply(avenelles_p10, function(i) {i %>% group_by(year) %>% summarise(load = sum(doc_mg.L*q_L.s*period, na.rm = T), sum_q = sum(q_L.s, na.rm = T), mean_q = mean(q_L.s))})
avenelles_p10_meanload <- lapply(avenelles_p10_load, function(i) {round((i$load/i$sum_q*ref_load$sum_q))}) %>% do.call(what = cbind) %>% rowMeans
avenelles_p10_bias <- lapply(avenelles_p10_load, function(i) {round(((i$load/i$sum_q*ref_load$sum_q)-ref_load$annual_load)/ref_load$annual_load*100)}) 
avenelles_p10_meanbiais <- as.data.frame(do.call(cbind,avenelles_p10_bias)) %>% rowMeans

avenelles_p20_load <- lapply(avenelles_p20, function(i) {i %>% group_by(year) %>% summarise(load = sum(doc_mg.L*q_L.s*period, na.rm = T), sum_q = sum(q_L.s, na.rm = T), mean_q = mean(q_L.s))})
avenelles_p20_meanload <- lapply(avenelles_p20_load, function(i) {round((i$load/i$sum_q*ref_load$sum_q))}) %>% do.call(what = cbind) %>% rowMeans
avenelles_p20_bias <- lapply(avenelles_p20_load, function(i) {round(((i$load/i$sum_q*ref_load$sum_q)-ref_load$annual_load)/ref_load$annual_load*100)}) 
avenelles_p20_meanbiais <- as.data.frame(do.call(cbind,avenelles_p20_bias)) %>% rowMeans

avenelles_p30_load <- lapply(avenelles_p30, function(i) {i %>% group_by(year) %>% summarise(load = sum(doc_mg.L*q_L.s*period, na.rm = T), sum_q = sum(q_L.s, na.rm = T), mean_q = mean(q_L.s))})
avenelles_p30_meanload <- lapply(avenelles_p30_load, function(i) {round((i$load/i$sum_q*ref_load$sum_q))}) %>% do.call(what = cbind) %>% rowMeans
avenelles_p30_bias <- lapply(avenelles_p30_load, function(i) {round(((i$load/i$sum_q*ref_load$sum_q)-ref_load$annual_load)/ref_load$annual_load*100)}) 
avenelles_p30_meanbiais <- as.data.frame(do.call(cbind,avenelles_p30_bias)) %>% rowMeans

avenelles_p40_load <- lapply(avenelles_p40, function(i) {i %>% group_by(year) %>% summarise(load = sum(doc_mg.L*q_L.s*period, na.rm = T), sum_q = sum(q_L.s, na.rm = T), mean_q = mean(q_L.s))})
avenelles_p40_meanload <- lapply(avenelles_p40_load, function(i) {round((i$load/i$sum_q*ref_load$sum_q))}) %>% do.call(what = cbind) %>% rowMeans
avenelles_p40_bias <- lapply(avenelles_p40_load, function(i) {round(((i$load/i$sum_q*ref_load$sum_q)-ref_load$annual_load)/ref_load$annual_load*100)}) 
avenelles_p40_meanbiais <- as.data.frame(do.call(cbind,avenelles_p40_bias)) %>% rowMeans

avenelles_p50_load <- lapply(avenelles_p50, function(i) {i %>% group_by(year) %>% summarise(load = sum(doc_mg.L*q_L.s*period, na.rm = T), sum_q = sum(q_L.s, na.rm = T), mean_q = mean(q_L.s))})
avenelles_p50_meanload <- lapply(avenelles_p50_load, function(i) {round((i$load/i$sum_q*ref_load$sum_q))}) %>% do.call(what = cbind) %>% rowMeans
avenelles_p50_bias <- lapply(avenelles_p50_load, function(i) {round(((i$load/i$sum_q*ref_load$sum_q)-ref_load$annual_load)/ref_load$annual_load*100)}) 
avenelles_p50_meanbiais <- as.data.frame(do.call(cbind,avenelles_p50_bias)) %>% rowMeans

avenelles_p60_load <- lapply(avenelles_p60, function(i) {i %>% group_by(year) %>% summarise(load = sum(doc_mg.L*q_L.s*period, na.rm = T), sum_q = sum(q_L.s, na.rm = T), mean_q = mean(q_L.s))})
avenelles_p60_meanload <- lapply(avenelles_p60_load, function(i) {round((i$load/i$sum_q*ref_load$sum_q))}) %>% do.call(what = cbind) %>% rowMeans
avenelles_p60_bias <- lapply(avenelles_p60_load, function(i) {round(((i$load/i$sum_q*ref_load$sum_q)-ref_load$annual_load)/ref_load$annual_load*100)}) 
avenelles_p60_meanbiais <- as.data.frame(do.call(cbind,avenelles_p60_bias)) %>% rowMeans

avenelles_p70_load <- lapply(avenelles_p70, function(i) {i %>% group_by(year) %>% summarise(load = sum(doc_mg.L*q_L.s*period, na.rm = T), sum_q = sum(q_L.s, na.rm = T), mean_q = mean(q_L.s))})
avenelles_p70_meanload <- lapply(avenelles_p70_load, function(i) {round((i$load/i$sum_q*ref_load$sum_q))}) %>% do.call(what = cbind) %>% rowMeans
avenelles_p70_bias <- lapply(avenelles_p70_load, function(i) {round(((i$load/i$sum_q*ref_load$sum_q)-ref_load$annual_load)/ref_load$annual_load*100)}) 
avenelles_p70_meanbiais <- as.data.frame(do.call(cbind,avenelles_p70_bias)) %>% rowMeans

avenelles_p80_load <- lapply(avenelles_p80, function(i) {i %>% group_by(year) %>% summarise(load = sum(doc_mg.L*q_L.s*period, na.rm = T), sum_q = sum(q_L.s, na.rm = T), mean_q = mean(q_L.s))})
avenelles_p80_meanload <- lapply(avenelles_p80_load, function(i) {round((i$load/i$sum_q*ref_load$sum_q))}) %>% do.call(what = cbind) %>% rowMeans
avenelles_p80_bias <- lapply(avenelles_p80_load, function(i) {round(((i$load/i$sum_q*ref_load$sum_q)-ref_load$annual_load)/ref_load$annual_load*100)}) 
avenelles_p80_meanbiais <- as.data.frame(do.call(cbind,avenelles_p80_bias)) %>% rowMeans

avenelles_p90_load <- lapply(avenelles_p90, function(i) {i %>% group_by(year) %>% summarise(load = sum(doc_mg.L*q_L.s*period, na.rm = T), sum_q = sum(q_L.s, na.rm = T), mean_q = mean(q_L.s))})
avenelles_p90_meanload <- lapply(avenelles_p90_load, function(i) {round((i$load/i$sum_q*ref_load$sum_q))}) %>% do.call(what = cbind) %>% rowMeans
avenelles_p90_bias <- lapply(avenelles_p90_load, function(i) {round(((i$load/i$sum_q*ref_load$sum_q)-ref_load$annual_load)/ref_load$annual_load*100)}) 
avenelles_p90_meanbiais <- as.data.frame(do.call(cbind,avenelles_p90_bias)) %>% rowMeans

avenelles_p100_load <- lapply(avenelles_p100, function(i) {i %>% group_by(year) %>% summarise(load = sum(doc_mg.L*q_L.s*period, na.rm = T), sum_q = sum(q_L.s, na.rm = T), mean_q = mean(q_L.s))})
avenelles_p100_meanload <- lapply(avenelles_p100_load, function(i) {round((i$load/i$sum_q*ref_load$sum_q))}) %>% do.call(what = cbind) %>% rowMeans
avenelles_p100_bias <- lapply(avenelles_p100_load, function(i) {round(((i$load/i$sum_q*ref_load$sum_q)-ref_load$annual_load)/ref_load$annual_load*100)}) 
avenelles_p100_meanbiais <- as.data.frame(do.call(cbind,avenelles_p100_bias)) %>% rowMeans

data.frame(
  Year = complete_years,
  "Annual load, tons" = ref_load$annual_load * 1e-9,
  "Average estimated load, 10% of data" = avenelles_p10_meanload * 1e-9,
  "Average bias, 10 % of data" = avenelles_p10_meanbiais,
    "Average estimated load, 20% of data" = avenelles_p20_meanload * 1e-9,
  "Average bias, 20 % of data" = avenelles_p20_meanbiais,
    "Average estimated load, 30% of data" = avenelles_p30_meanload * 1e-9,
  "Average bias, 30 % of data" = avenelles_p30_meanbiais,
    "Average estimated load, 40% of data" = avenelles_p40_meanload * 1e-9,
  "Average bias, 40 % of data" = avenelles_p40_meanbiais,
    "Average estimated load, 50% of data" = avenelles_p50_meanload * 1e-9,
  "Average bias, 50 % of data" = avenelles_p50_meanbiais,
    "Average estimated load, 60% of data" = avenelles_p60_meanload * 1e-9,
  "Average bias, 60 % of data" = avenelles_p60_meanbiais,
    "Average estimated load, 70% of data" = avenelles_p70_meanload * 1e-9,
  "Average bias, 70 % of data" = avenelles_p70_meanbiais,
    "Average estimated load, 80% of data" = avenelles_p80_meanload * 1e-9,
  "Average bias, 80 % of data" = avenelles_p80_meanbiais,
    "Average estimated load, 90% of data" = avenelles_p90_meanload * 1e-9,
  "Average bias, 90 % of data" = avenelles_p90_meanbiais,
    "Average estimated load, 100% of data" = avenelles_p100_meanload * 1e-9,
  "Average bias, 100 % of data" = avenelles_p100_meanbiais,
  check.names = F
)  %>% knitr::kable(digits = 2) %>% kableExtra::kable_styling()


summary_df <- data.frame(
  year = complete_years,
  annual_load_ref = ref_load$annual_load * 1e-9,
  annual_load_p10 = avenelles_p10_meanload * 1e-9,
  bias_p10 = avenelles_p10_meanbiais,
  annual_load_p20 = avenelles_p20_meanload * 1e-9,
  bias_p20 = avenelles_p20_meanbiais,
  annual_load_p30 = avenelles_p30_meanload * 1e-9,
  bias_p30 = avenelles_p30_meanbiais,
  annual_load_p40 = avenelles_p40_meanload * 1e-9,
  bias_p40 = avenelles_p40_meanbiais,
  annual_load_p50 = avenelles_p50_meanload * 1e-9,
  bias_p50 = avenelles_p50_meanbiais,
  annual_load_p60 = avenelles_p60_meanload * 1e-9,
  bias_p60 = avenelles_p60_meanbiais,
  annual_load_p70 = avenelles_p70_meanload * 1e-9,
  bias_p70 = avenelles_p70_meanbiais,
  annual_load_p80 = avenelles_p80_meanload * 1e-9,
  bias_p80 = avenelles_p80_meanbiais,
  annual_load_p90 = avenelles_p90_meanload * 1e-9,
  bias_p90 = avenelles_p90_meanbiais,
  annual_load_p100 = avenelles_p100_meanload * 1e-9,
  bias_p100 = avenelles_p100_meanbiais)

ggplot(summary_df,aes(x=year))+geom_line(aes(y=annual_load_ref), size = 2)+
  geom_line(aes(y=annual_load_p10, col = "10%"))+
    geom_line(aes(y=annual_load_p20, col = "20%"))+
    geom_line(aes(y=annual_load_p30, col = "30%"))+
    geom_line(aes(y=annual_load_p40, col = "40%"))+
    geom_line(aes(y=annual_load_p50, col = "50%"))+
    geom_line(aes(y=annual_load_p60, col = "60%"))+
    geom_line(aes(y=annual_load_p70, col = "70%"))+
    geom_line(aes(y=annual_load_p80, col = "80%"))+
    geom_line(aes(y=annual_load_p90, col = "90%"))+
    geom_line(aes(y=annual_load_p100, col = " 100%"))+
  scale_color_viridis_d(direction = -1)+
  labs(x= "Year", y = "Annual load, tons", col = "% of randomly sampled data",title = "Average DOC load by year depending on percentage of data included", subtitle = "Reference annual load in black")+
  scale_x_continuous(breaks = complete_years, minor_breaks = NULL)+
  theme_minimal()+
  theme(legend.position = "bottom", axis.text.x = element_text(angle = 45))

ggplot(summary_df,aes(x=year))+#geom_line(data = ref_load, aes(x = year, y=mean_q/10), size = 1)+
  geom_line(aes(y=bias_p10, col = "10%"))+
    geom_line(aes(y=bias_p20, col = "20%"))+
    geom_line(aes(y=bias_p30, col = "30%"))+
    geom_line(aes(y=bias_p40, col = "40%"))+
    geom_line(aes(y=bias_p50, col = "50%"))+
    geom_line(aes(y=bias_p60, col = "60%"))+
    geom_line(aes(y=bias_p70, col = "70%"))+
    geom_line(aes(y=bias_p80, col = "80%"))+
    geom_line(aes(y=bias_p90, col = "90%"))+
  scale_color_viridis_d(direction = -1)+
  labs(x= "Year", y = "Absolute average bias,%", col = "% of randomly \n sampled data", title = "Average bias by year depending on percentage of data included", subtitle = "Average annual discharge in black")+
  scale_x_continuous(breaks = complete_years, minor_breaks = NULL)+
  scale_y_continuous(sec.axis = sec_axis(~.*10, name = "Average annual discharge, L/s"))+
  theme_minimal()+
  theme(legend.position = "bottom", axis.text.x = element_text(angle = 45))

ggplot(summary_df)+geom_point(aes(x=))

```
