---
title: "Avenelles - test méthode"
output:
  html_document:
    toc: true
    toc_float: true
    number_sections: true
    code_folding: hide
date: "2025-06-06"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = F, warning = F, error = F, fig.align = "center", collapse = T,
                      cache = F)
```

```{r libraries, cache = F}
library(ggplot2)
library(ggpubr)

library(dplyr)
library(readxl)
library(lubridate)

library(nlme)

library(knitr)
library(kableExtra)
```

# Get data

https://bdoh.inrae.fr/SITE-ATELIER-ARDIERES-MORCILLE/ 

https://onlinelibrary.wiley.com/doi/10.1002/hyp.14384


```{r load-data-from-excel, message = F}

avenelles <- readxl::read_xlsx(path = "Data_Avenelles_DOC_DIC_Debit.xlsx", sheet = "Data_Avenelles_DOC_DIC_Debit", col_types = c("date","numeric", "text","numeric","text","numeric","text","text","numeric")) %>%  mutate(Site = NULL, bv_km2 = NULL) %>% unique()

```

```{r merge}

#avenelles$q_L.s <- imputeTS::na_interpolation(avenelles$q_L.s) # fill empty Q

avenelles$year <- year(avenelles$DateHeure)
avenelles$week <- week(avenelles$DateHeure)
avenelles$month <- month(avenelles$DateHeure)

avenelles$commondate <- as.Date(paste0("2000-", format(avenelles$DateHeure,"%j")), "%Y-%j")
avenelles$Date <- format(avenelles$DateHeure, "%Y-%m-%d") %>% as.Date()

avenelles$period <- with(avenelles, as.numeric(-(DateHeure - lead(DateHeure)))) # period is calculated in second, we get it in days
avenelles$periodj <- round(avenelles$period / 60 / 60 / 24, 0)

avenelles <- unique(avenelles)
  
strange_periods_dates <- avenelles %>% subset(periodj > 3) %>% pull(Date) 

bv <- 45
```

Une mesure de doc par jour en général.

```{r summary-data}
summary_avenelles <- merge(
avenelles %>% subset(!is.na(doc_mg.L)) %>% group_by(year) %>% summarise(nb_doc = n()),
avenelles %>% subset(!is.na(q_L.s)) %>% group_by(year) %>% summarise(nb_q = n()), by = "year", all = T) %>% 
  merge(avenelles %>% subset(!is.na(doc_mg.L) ) %>% group_by(year) %>% summarise(total_period_j_nona = length(unique(DateHeure))), by = "year", all = T)

knitr::kable(summary_avenelles) %>% kableExtra::kable_styling()

cat("mean Q", mean(avenelles$q_L.s, na.rm = T))
cat("range OC (0-25-50-75-100)", quantile(with(avenelles, doc_mg.L), na.rm = T))


avenelles %>% filter(!is.na(doc_mg.L)) %>% group_by(year) %>% summarise(nb_obs = n(), nb_unique_date = length(unique(Date))) %>% kable() %>% kable_styling()
```


# View data

```{r plot-by-year-doc, fig.dim = c(10,15)}

ggarrange(
ggplot(avenelles, aes(x = commondate))+
  geom_point(aes(y = q_L.s, col = "Débit, L/s"), alpha = 0.5)+
  scale_x_date(labels = function(x) format(x, "%d-%b"), date_minor_breaks = "1 month", name = "")+
  scale_color_manual(values = c("lightblue"), name = "")+
  facet_grid(rows = vars(year))+
  labs(y = "Débit, L/s", col = "")+
  theme_minimal(base_size = 15)+
  theme(legend.position = "none"),

ggplot(avenelles, aes(x = commondate))+
  geom_point(aes(y = doc_mg.L, col = "DOC, mg.L"), alpha = 0.5)+
  scale_x_date(labels = function(x) format(x, "%d-%b"), date_minor_breaks = "1 month", name = "")+
  scale_color_manual(values = c("palegreen4"), name = "")+
  facet_grid(rows = vars(year))+
  labs(y = "DOC, mg/L", col = "")+
  theme_minimal(base_size = 15)+
  theme(legend.position = "none")
)

```

# Relation DOC-Q

```{r doc-avenelles}
doc_avenelles <- avenelles %>% filter(!is.na(doc_mg.L))

'%notin%' <- function(x,y) !(x %in% y)

ggplot(doc_avenelles)+geom_point(aes(x = q_L.s, y = doc_mg.L))
ggplot(doc_avenelles)+geom_point(aes(x = log(q_L.s), y = doc_mg.L, col = as.character(year), shape = as.character(year)))+scale_color_viridis_d()

ggplot(filter(doc_avenelles, year == 2014))+geom_point(aes(x = log(q_L.s), y = doc_mg.L))
ggplot(filter(doc_avenelles, year %notin% c(2009,2014,2015)), aes(x = q_L.s, y = doc_mg.L))+geom_point()+
  geom_smooth()

lm(doc_mg.L~q_L.s, data = doc_avenelles) %>% summary()
```


# Annual and interannual flux 

Années choisies: années avec des observations plus de 1 jour sur 2 (nobs > 365/2)

On considère que l'erreur sur DOC vient de la mesure par analyse TOC.

```{r uncertainties}
complete_years <- c(2009,2011,2012,2013,2015,2016,2017,2019,2021)
nyears <- length(complete_years)

avenelles_flux <- avenelles %>% filter(year %in% complete_years)


q_u <- 0.1

nobs <- dim(avenelles_flux)[1]
nrep <- 1000
```

## total flux

```{r compute-flux}
#doc matrix
doc_meas <- matrix(avenelles_flux$doc_mg.L, nrow = nrep, ncol = nobs, byrow = T) # repeats nrep lines with observations

doc_cv <- 3.2*doc_meas^(-0.2) # from quich check Claire, vaut pour TOC mais pas autres moyens de mesure
doc_random <- matrix(rnorm(nrep*nobs, mean = 0, sd = 1), nrow=nrep, ncol = nobs)
doc_noise <- doc_cv*doc_random
doc_mat <- doc_meas * (1 + doc_noise/100) # final value of doc, with noise in percent

# Q matrix
q_meas <- matrix(avenelles_flux$q_L.s, nrow = nrep, ncol = nobs, byrow = T) # repeats nrow_boot times the vector q_L.s
q_noise <- matrix(rnorm(nrep*nobs, mean = 0, sd = q_u), nrow = nrep, ncol = nobs) # creates a noise in percent (proportion), between 0 and 10%
q_mat <- q_meas * (1 + q_noise) # final value of q, with noise

period_mat <- matrix(avenelles_flux$period, nrow = nrep, ncol = nobs, byrow = T) # in seconds

# Flux per time step
flux_ton_mat <- doc_mat*1e-9*q_mat*period_mat # flux per period (period in seconds, so flux in ton/s is converted to flux per period). 
flux_ton.s_mat <- doc_mat*1e-9*q_mat # without period

index_years <- lapply(complete_years, function(y){which(avenelles_flux$year == y)}) # list of indices corresponding to each year

# Annual flux
annual_flux_ton.y <- sapply(index_years, function(idx){apply(flux_ton_mat[,idx], 1, sum, na.rm = T)}) # sum of fluxes per year, for each iteration of the bootstrap. Result is a matrix with nrow_boot rows and 19 columns (1 per year)
annual_flux_pi <- apply(annual_flux_ton.y, 2, quantile, probs = c(0.025, 0.5, 0.975), na.rm = T) # prediction interval for annual fluxes, per year. 3 lignes, 19 columns
annual_flux_mean <- colMeans(annual_flux_ton.y, na.rm = T) # mean annual flux per year. 1 vector
annual_flux_sd <- apply(annual_flux_ton.y, 2, sd, na.rm = T) # standard deviation of annual flux per year. Is just an estimate of goodness of mean, not as good as than the confidence interval. 

annual_flux_df <- data.frame(year = complete_years, 
                        annual_flux_mean = annual_flux_mean, 
                        annual_flux_variability = annual_flux_sd, 
                        annual_flux_pi_lower = annual_flux_pi[1,], 
                        annual_flux_pi_upper = annual_flux_pi[3,])

# Interannual flux 
interannual_flux_ton.y <- rowMeans(annual_flux_ton.y, na.rm = T) # mean interannual flux per iteration of the bootstrap
interannual_flux_pi <- quantile(interannual_flux_ton.y, probs = c(0.025, 0.5, 0.975), na.rm = T) # prediction interval
interannual_flux_mean <- mean(interannual_flux_ton.y, na.rm = T) # mean interannual flux
interannual_flux_variability <- sd(annual_flux_mean, na.rm = T) # standard deviation of interannual flux per year

interannual_flux_df <- data.frame(year = "interannual", annual_flux_mean = interannual_flux_mean, 
                                  annual_flux_variability = interannual_flux_variability,
                        annual_flux_pi_lower = interannual_flux_pi[1], 
                        annual_flux_pi_upper = interannual_flux_pi[3])

total_flux_df <- rbind(annual_flux_df, interannual_flux_df)
total_flux_df$group <- c(rep("annual", nyears), "interannual")

# Q df

annual_q <- sapply(index_years, function(idx){apply(q_mat[,idx], 1, sum, na.rm = T)}) # sum of fluxes per year, for each iteration of the bootstrap. Result is a matrix with nrow_boot rows and 19 columns (1 per year)
annual_q_pi <- apply(annual_q, 2, quantile, probs = c(0.025, 0.5, 0.975), na.rm = T) # prediction interval for annual fluxes, per year. 3 lignes, 19 columns
annual_q_mean <- colMeans(annual_q, na.rm = T) # mean annual flux per year. 1 vector
annual_q_sd <- apply(annual_q, 2, sd, na.rm = T) # standard deviation of annual flux per year. Is just an estimate of goodness of mean, not as good as than the confidence interval. 
interannual_q <- rowMeans(annual_q, na.rm = T) # mean interannual flux per iteration of the bootstrap
interannual_q_pi <- quantile(interannual_q, probs = c(0.025, 0.5, 0.975), na.rm = T) # prediction interval
interannual_q_mean <- mean(interannual_q, na.rm = T) # mean interannual flux
interannual_q_variability <- sd(annual_q_mean, na.rm = T) # standard deviation of interannual flux per year

q_df <- data.frame(year = c(complete_years, "interannual"), 
                        q_mean = c(annual_q_mean, interannual_q_mean),
                        q_variability = c(annual_flux_sd, interannual_q_variability), 
                        q_pi_lower = c(annual_q_pi[1,], interannual_q_pi[1]), 
                        q_pi_upper = c(annual_q_pi[3,], interannual_q_pi[3]),
                   group = c(rep("annual", nyears), "interannual"))

# Plot
ggplot()+
  geom_col(data = total_flux_df, aes(x=year, y = annual_flux_mean, fill = group))+
    geom_errorbar(data = total_flux_df, aes(x = year, ymin = annual_flux_pi_lower, ymax = annual_flux_pi_upper, col = "prediction interval"), width = 0.3, size = 0.8)+
  geom_errorbar(data = filter(total_flux_df, year == "interannual"), aes(x = year, ymin = annual_flux_mean - annual_flux_variability, ymax = annual_flux_mean + annual_flux_variability, col = "interannual variability"), width = 0.2, size = 0.8, linetype = 2)+
  scale_fill_manual(values = c("annual" = "lightblue", "interannual" = "indianred"))+
  scale_color_manual(values = c("prediction interval" = "darkblue", "interannual variability" = "darkred"), name = "")+
   labs(x = "Year", y = "Flux (ton/year)", fill = "")+
  theme_minimal(base_size = 15)+
  theme(axis.text.x = element_text(angle = 45, hjust = 1), legend.position = "bottom")

ggplot()+
  geom_col(data = q_df, aes(x=year, y = q_mean, fill = group))+
    geom_errorbar(data = q_df, aes(x = year, ymin = q_pi_lower, ymax = q_pi_upper, col = "prediction interval"), width = 0.3, size = 0.8)+
  geom_errorbar(data = filter(q_df, year == "interannual"), aes(x = year, ymin = q_mean - q_variability, ymax = q_mean + q_variability, col = "interannual variability"), width = 0.2, size = 0.8, linetype = 2)+
  scale_fill_manual(values = c("annual" = "lightblue", "interannual" = "indianred"))+
  scale_color_manual(values = c("prediction interval" = "darkblue", "interannual variability" = "darkred"), name = "")+
   labs(x = "Year", y = "Discharge (L/year)", fill = "")+
  theme_minimal(base_size = 15)+
  theme(axis.text.x = element_text(angle = 45, hjust = 1), legend.position = "bottom")

knitr::kable(total_flux_df, digits = 2, row.names = F) %>% kableExtra::kable_styling()

```

## Specific flux

```{r specific-flux}
sflux_ton_mat <- doc_mat*1e-9*q_mat*period_mat/bv # flux per period (period in seconds, so flux in ton/s is converted to flux per period). 
sflux_ton.s_mat <- doc_mat*1e-9*q_mat/bv # without period

annual_sflux_ton.y <- sapply(index_years, function(idx){apply(sflux_ton_mat[,idx], 1, sum, na.rm = T)}) # sum of fluxes per year, for each iteration of the bootstrap. Result is a matrix with nrow_boot rows and 19 columns (1 per year)
annual_sflux_pi <- apply(annual_sflux_ton.y, 2, quantile, probs = c(0.025, 0.5, 0.975), na.rm = T) # prediction interval for annual fluxes, per year. 3 lignes, 19 columns
annual_sflux_mean <- colMeans(annual_sflux_ton.y, na.rm = T) # mean annual flux per year. 1 vector
annual_sflux_sd <- apply(annual_sflux_ton.y, 2, sd, na.rm = T) # standard deviation of annual flux per year. Is just an estimate of goodness of mean, not as good as than the confidence interval. 

annual_sflux_df <- data.frame(year = complete_years, 
                        annual_flux_mean = annual_sflux_mean, 
                        annual_flux_variability = annual_sflux_sd, 
                        annual_flux_pi_lower = annual_sflux_pi[1,], 
                        annual_flux_pi_upper = annual_sflux_pi[3,])

# Interannual flux 
interannual_sflux_ton.y <- rowMeans(annual_sflux_ton.y, na.rm = T) # mean interannual flux per iteration of the bootstrap
interannual_sflux_pi <- quantile(interannual_sflux_ton.y, probs = c(0.025, 0.5, 0.975), na.rm = T) # prediction interval
interannual_sflux_mean <- mean(interannual_sflux_ton.y, na.rm = T) # mean interannual flux
interannual_sflux_variability <- sd(annual_sflux_mean, na.rm = T) # standard deviation of interannual flux per year

interannual_sflux_df <- data.frame(year = "interannual", annual_flux_mean = interannual_sflux_mean, 
                                  annual_flux_variability = interannual_sflux_variability,
                        annual_flux_pi_lower = interannual_sflux_pi[1], 
                        annual_flux_pi_upper = interannual_sflux_pi[3])

total_sflux_df <- rbind(annual_sflux_df, interannual_sflux_df)
total_sflux_df$group <- c(rep("annual", nyears), "interannual")

ggplot()+
  geom_col(data = total_sflux_df, aes(x=year, y = annual_flux_mean, fill = group), width = 0.8)+
    geom_errorbar(data = total_sflux_df, aes(x = year, ymin = annual_flux_pi_lower, ymax = annual_flux_pi_upper, col = "prediction interval"), width = 0.3, size = 0.8)+
  geom_errorbar(data = filter(total_sflux_df, year == "interannual"), aes(x = year, ymin = annual_flux_mean - annual_flux_variability, ymax = annual_flux_mean + annual_flux_variability, col = "interannual variability"), width = 0.2, size = 0.8, linetype = 2)+
  scale_fill_manual(values = c("annual" = "lightblue", "interannual" = "indianred"))+
  scale_color_manual(values = c("prediction interval" = "darkblue", "interannual variability" = "darkred"), name = "")+
   labs(x = "Year", y = "Flux (tons/km2/year)", fill = "")+
  theme_minimal(base_size = 15)+
  theme(axis.text.x = element_text(angle = 45, hjust = 1), legend.position = "bottom")

ggsave("sflux_avenelles.svg")

knitr::kable(total_sflux_df, digits = 2, row.names = F) %>% kableExtra::kable_styling()
```


# Time steps

```{r common-data-timestep}
avenelles_time <- avenelles_flux %>% select(c("DateHeure", "doc_mg.L","q_L.s"))
```


## 2 Days

```{r avenelles-day2, cache.lazy = F}
# prepare df
avenelles_group_day2 <- avenelles_time %>% mutate(day = as.numeric(as.Date(format(DateHeure, "%Y-%m-%d"))), month = month(DateHeure), day2 = floor((day - min(day)) / 2), year = year(DateHeure)) %>% group_by(day2, year) # group avenelles_time by day
nrow_day2 <- n_groups(avenelles_group_day2)


# creates matrix for DOC
avenelles_doc_day2 <- avenelles_group_day2 %>% select(c("DateHeure","day2", "doc_mg.L")) %>% summarize("DateHeure" = mean(DateHeure),"list_doc" = list(doc_mg.L)) %>% ungroup() # creates a list of doc for each day2
doc_random_day2 <- replicate(nrep, sapply(avenelles_doc_day2$list_doc, function(x) sample(x,1)))%>% t() # matrix of mes: one random sample per day2, replicated 1000 times

doc_cv_day2 <- 3.2*doc_random_day2^(-0.2)
rnorm_day2 <- matrix(rnorm(nrep*nrow_day2, mean = 0, sd = 1), nrow=nrep, ncol = nrow_day2)
doc_noise_day2 <- doc_cv_day2*rnorm_day2
doc_mat_day2 <- doc_random_day2 * (1 + doc_noise_day2/100) # final value of doc, with noise in percent

# matrix for q
q_day2 <- avenelles_group_day2 %>% select(c("day2", "q_L.s")) %>% summarize_all(list("q_mean" = mean, "q_sd" = sd)) %>% ungroup() # mean of Q for each day2

q_day2_mean <-  matrix(q_day2$q_mean, nrow = nrep, ncol = nrow_day2, byrow = T)
q_noise <- matrix(rnorm(nrep*nrow_day2, mean = 0, sd = q_u), nrow = nrep, ncol = nrow_day2) # creates a noise in percent (proportion), between 0 and 10%
q_mat_day2 <- q_day2_mean * (1 + q_noise) # final MC of q, with noise. SD NOT INCLUDED: will not always be available

# period matrix: too many missing 2-days
avenelles_doc_day2$period <- with(avenelles_doc_day2, as.numeric(-(DateHeure - lead(DateHeure)))) # period is calculated in hours
period_mat_day2 <- matrix(avenelles_doc_day2$period, nrow = nrep, ncol = nrow_day2, byrow = T) # in seconds

# compute flux
flux_ton_mat_day2 <- doc_mat_day2*1e-9*q_mat_day2*period_mat_day2*60*60*24 #doc in mg/L converted to ton; q_mat in L/s. Period : time between groups of days. Period is in days

# Get index for columns by year
index_years <- lapply(complete_years, function(y){which(avenelles_doc_day2$year == y)}) # list of indices corresponding to each year

# annual flux
annual_flux_ton.y_day2 <- lapply(index_years, function(idx){apply(flux_ton_mat_day2[,idx], 1, sum, na.rm = T)}) %>% do.call("cbind", .)# sum of fluxes per year, for each iteration of the bootstrap. 
annual_flux_day2_pi <- apply(annual_flux_ton.y_day2, 2, quantile, probs = c(0.025, 0.5, 0.975), na.rm = T) # confidence interval for annual fluxes, per year. 3 lignes, 19 columns
annual_flux_day2_mean <- colMeans(annual_flux_ton.y_day2, na.rm = T) # mean annual flux per year. 1 vector
annual_flux_day2_sd <- apply(annual_flux_ton.y_day2, 2, sd, na.rm = T) # standard deviation of annual flux per year. Is just an estimate of goodness of mean, not as good as than the confidence interval. 
 
annual_flux_day2_df <- data.frame(year = complete_years, 
                        annual_flux_mean = annual_flux_day2_mean, 
                        annual_flux_variability = annual_flux_day2_sd, 
                        annual_flux_pi_lower = annual_flux_day2_pi[1,], 
                        annual_flux_pi_upper = annual_flux_day2_pi[3,])

interannual_flux_ton.y_day2 <- rowMeans(annual_flux_ton.y_day2, na.rm = T) # mean interannual flux per iteration of the bootstrap
interannual_flux_pi_day2 <- quantile(interannual_flux_ton.y_day2, probs = c(0.025, 0.5, 0.975), na.rm = T) # prediction interval
interannual_flux_mean_day2 <- mean(interannual_flux_ton.y_day2, na.rm = T) # mean interannual flux
interannual_flux_variability_day2 <- sd(annual_flux_day2_mean, na.rm = T) # standard deviation of interannual flux per year

interannual_flux_day2_df <- data.frame(year = "interannual", annual_flux_mean = interannual_flux_mean_day2, 
                                  annual_flux_variability = interannual_flux_variability_day2,
                        annual_flux_pi_lower = interannual_flux_pi_day2[1], 
                        annual_flux_pi_upper = interannual_flux_pi_day2[3])

total_flux_day2_df <- rbind(annual_flux_day2_df, interannual_flux_day2_df)
total_flux_day2_df$group <- c(rep("annual", nyears), "interannual")

ggplot()+
  geom_col(data = total_flux_day2_df, aes(x=year, y = annual_flux_mean, fill = group))+
    geom_errorbar(data = total_flux_day2_df, aes(x = year, ymin = annual_flux_pi_lower, ymax = annual_flux_pi_upper, col = "prediction interval"), width = 0.3, size = 0.8)+
  geom_errorbar(data = filter(total_flux_day2_df, year == "interannual"), aes(x = year, ymin = annual_flux_mean - annual_flux_variability, ymax = annual_flux_mean + annual_flux_variability, col = "interannual variability"), width = 0.2, size = 0.8, linetype = 2)+
  scale_fill_manual(values = c("annual" = "lightblue", "interannual" = "indianred"))+
  scale_color_manual(values = c("prediction interval" = "darkblue", "interannual variability" = "darkred"), name = "")+
   labs(x = "Year", y = "Flux, from bi-dayly mean values (ton/year)", fill = "")+
  theme_minimal(base_size = 15)+
  theme(axis.text.x = element_text(angle = 45, hjust = 1), legend.position = "bottom")

knitr::kable(total_flux_day2_df, digits = 2, row.names = F) %>% kableExtra::kable_styling()
```

## 4 Days 

```{r avenelles-day4, cache.lazy = F}
# prepare df
avenelles_group_day4 <- avenelles_time %>% mutate(day = as.numeric(as.Date(format(DateHeure, "%Y-%m-%d"))), month = month(DateHeure), day4 = floor((day - min(day)) / 4), year = year(DateHeure)) %>% group_by(day4, year) # group avenelles_time by day
nrow_day4 <- n_groups(avenelles_group_day4)



# creates matrix for DOC
avenelles_doc_day4 <- avenelles_group_day4 %>% select(c("day4", "doc_mg.L")) %>% summarize("list_doc" = list(doc_mg.L)) %>% ungroup() # creates a list of mes for each day4
doc_random_day4 <- replicate(nrep, sapply(avenelles_doc_day4$list_doc, function(x) sample(x,1)))%>% t() # matrix of mes: one random sample per day4, replicated 1000 times
# doc_day4_noise <- matrix(rnorm(nrep*nrow_day4, mean = 0, sd = doc_u), nrow = nrep, ncol = nrow_day4) 
# doc_mat_day4 <- doc_day4_random * (1 + doc_day4_noise) # final value of mes, with noise
# 
# doc_mean <- colMeans(doc_mat_day4)

doc_cv_day4 <- 3.2*doc_random_day4^(-0.2)
rnorm_day4 <- matrix(rnorm(nrep*nrow_day4, mean = 0, sd = 1), nrow=nrep, ncol = nrow_day4)
doc_noise_day4 <- doc_cv_day4*rnorm_day4
doc_mat_day4 <- doc_random_day4 * (1 + doc_noise_day4/100) # final value of doc, with noise in percent



# matrix for q
q_day4 <- avenelles_group_day4 %>% select(c("day4", "q_L.s")) %>% summarize_all(list("q_mean" = mean, "q_sd" = sd)) %>% ungroup() # mean of Q for each day4

q_day4_mean <-  matrix(q_day4$q_mean, nrow = nrep, ncol = nrow_day4, byrow = T)
q_noise <- matrix(rnorm(nrep*nrow_day4, mean = 0, sd = q_u), nrow = nrep, ncol = nrow_day4) # creates a noise in percent (proportion), between 0 and 10%
q_mat_day4 <- q_day4_mean * (1 + q_noise) # final MC of q, with noise. SD NOT INCLUDED: will not always be available

# compute flux
flux_ton_mat_day4 <- doc_mat_day4*1e-9*q_mat_day4*60*60*24*4 #pred_day4 * mes_mat : poc in mg/L converted to ton; q_mat converted from m3/s to L/s. Period : nb of seconds in 1 day4. 

# Get index for columns by year
index_years <- lapply(complete_years, function(y){which(avenelles_doc_day4$year == y)}) # list of indices corresponding to each year

# annual flux
annual_flux_ton.y_day4 <- lapply(index_years, function(idx){apply(flux_ton_mat_day4[,idx], 1, sum, na.rm = T)}) %>% do.call("cbind", .)# sum of fluxes per year, for each iteration of the bootstrap. 
annual_flux_day4_pi <- apply(annual_flux_ton.y_day4, 2, quantile, probs = c(0.025, 0.5, 0.975), na.rm = T) # confidence interval for annual fluxes, per year. 3 lignes, 19 columns
annual_flux_day4_mean <- colMeans(annual_flux_ton.y_day4, na.rm = T) # mean annual flux per year. 1 vector
annual_flux_day4_sd <- apply(annual_flux_ton.y_day4, 2, sd, na.rm = T) # standard deviation of annual flux per year. Is just an estimate of goodness of mean, not as good as than the confidence interval. 
 
annual_flux_day4_df <- data.frame(year = complete_years, 
                        annual_flux_mean = annual_flux_day4_mean, 
                        annual_flux_variability = annual_flux_day4_sd, 
                        annual_flux_pi_lower = annual_flux_day4_pi[1,], 
                        annual_flux_pi_upper = annual_flux_day4_pi[3,])

interannual_flux_ton.y_day4 <- rowMeans(annual_flux_ton.y_day4, na.rm = T) # mean interannual flux per iteration of the bootstrap
interannual_flux_pi_day4 <- quantile(interannual_flux_ton.y_day4, probs = c(0.025, 0.5, 0.975), na.rm = T) # prediction interval
interannual_flux_mean_day4 <- mean(interannual_flux_ton.y_day4, na.rm = T) # mean interannual flux
interannual_flux_variability_day4 <- sd(annual_flux_day4_mean, na.rm = T) # standard deviation of interannual flux per year

interannual_flux_day4_df <- data.frame(year = "interannual", annual_flux_mean = interannual_flux_mean_day4, 
                                  annual_flux_variability = interannual_flux_variability_day4,
                        annual_flux_pi_lower = interannual_flux_pi_day4[1], 
                        annual_flux_pi_upper = interannual_flux_pi_day4[3])

total_flux_day4_df <- rbind(annual_flux_day4_df, interannual_flux_day4_df)
total_flux_day4_df$group <- c(rep("annual", nyears), "interannual")

ggplot()+
  geom_col(data = total_flux_day4_df, aes(x=year, y = annual_flux_mean, fill = group))+
    geom_errorbar(data = total_flux_day4_df, aes(x = year, ymin = annual_flux_pi_lower, ymax = annual_flux_pi_upper, col = "prediction interval"), width = 0.3, size = 0.8)+
  geom_errorbar(data = filter(total_flux_day4_df, year == "interannual"), aes(x = year, ymin = annual_flux_mean - annual_flux_variability, ymax = annual_flux_mean + annual_flux_variability, col = "interannual variability"), width = 0.2, size = 0.8, linetype = 2)+
  scale_fill_manual(values = c("annual" = "lightblue", "interannual" = "indianred"))+
  scale_color_manual(values = c("prediction interval" = "darkblue", "interannual variability" = "darkred"), name = "")+
   labs(x = "Year", y = "Flux, from bi-dayly mean values (ton/year)", fill = "")+
  theme_minimal(base_size = 15)+
  theme(axis.text.x = element_text(angle = 45, hjust = 1), legend.position = "bottom")

knitr::kable(total_flux_day4_df, digits = 2, row.names = F) %>% kableExtra::kable_styling()
```



## 1 week

```{r avenelles-week, cache.lazy = F}
# prepare df
avenelles_group_week <- avenelles_time %>% mutate("week" = week(DateHeure), year = year(DateHeure)) %>% group_by(week,year) # group isere_time by week
nrow_week <- n_groups(avenelles_group_week)


# creates matrix for DOC
avenelles_doc_week <- avenelles_group_week %>% select(c("week", "doc_mg.L")) %>% summarize("list_doc" = list(doc_mg.L)) %>% ungroup() # creates a list of mes for each week
doc_random_week <- replicate(nrep, sapply(avenelles_doc_week$list_doc, function(x) sample(x,1)))%>% t() # matrix of mes: one random sample per week, replicated 1000 times
# doc_week_noise <- matrix(rnorm(nrep*nrow_week, mean = 0, sd = doc_u), nrow = nrep, ncol = nrow_week) 
# doc_mat_week <- doc_week_random * (1 + doc_week_noise) # final value of mes, with noise
# doc_mean <- colMeans(doc_mat_week)

doc_cv_week <- 3.2*doc_random_week^(-0.2)
rnorm_week <- matrix(rnorm(nrep*nrow_week, mean = 0, sd = 1), nrow=nrep, ncol = nrow_week)
doc_noise_week <- doc_cv_week*rnorm_week
doc_mat_week <- doc_random_week * (1 + doc_noise_week/100) # final value of doc, with noise in percent


# matrix for q
q_week <- avenelles_group_week %>% select(c("week", "q_L.s")) %>% summarize_all(list("q_mean" = mean, "q_sd" = sd)) %>% ungroup() # mean of Q for each week

q_week_mean <-  matrix(q_week$q_mean, nrow = nrep, ncol = nrow_week, byrow = T)
q_noise <- matrix(rnorm(nrep*nrow_week, mean = 0, sd = q_u), nrow = nrep, ncol = nrow_week) # creates a noise in percent (proportion), between 0 and 10%
q_mat_week <- q_week_mean * (1 + q_noise) # final MC of q, with noise. SD NOT INCLUDED: will not always be available

# compute flux
flux_ton_mat_week <- doc_mat_week*1e-9*q_mat_week*60*60*24*7 #pred_week * mes_mat : poc in mg/L converted to ton; q_mat converted from m3/s to L/s. Period : nb of seconds in 1 week. 

# Get index for columns by year
index_years <- lapply(complete_years, function(y){which(avenelles_doc_week$year == y)}) # list of indices corresponding to each year

# annual flux
annual_flux_ton.y_week <- lapply(index_years, function(idx){apply(flux_ton_mat_week[,idx], 1, sum, na.rm = T)}) %>% do.call("cbind", .) # sum of fluxes per year, for each iteration of the bootstrap. 
annual_flux_week_pi <- apply(annual_flux_ton.y_week, 2, quantile, probs = c(0.025, 0.5, 0.975), na.rm = T) # confidence interval for annual fluxes, per year. 3 lignes, 19 columns
annual_flux_week_mean <- colMeans(annual_flux_ton.y_week, na.rm = T) # mean annual flux per year. 1 vector
annual_flux_week_sd <- apply(annual_flux_ton.y_week, 2, sd, na.rm = T) # standard deviation of annual flux per year. Is just an estimate of goodness of mean, not as good as than the confidence interval. 
 
annual_flux_week_df <- data.frame(year = complete_years, 
                        annual_flux_mean = annual_flux_week_mean, 
                        annual_flux_variability = annual_flux_week_sd, 
                        annual_flux_pi_lower = annual_flux_week_pi[1,], 
                        annual_flux_pi_upper = annual_flux_week_pi[3,])

interannual_flux_ton.y_week <- rowMeans(annual_flux_ton.y_week, na.rm = T) # mean interannual flux per iteration of the bootstrap
interannual_flux_pi_week <- quantile(interannual_flux_ton.y_week, probs = c(0.025, 0.5, 0.975), na.rm = T) # prediction interval
interannual_flux_mean_week <- mean(interannual_flux_ton.y_week, na.rm = T) # mean interannual flux
interannual_flux_variability_week <- sd(annual_flux_week_mean, na.rm = T) # standard deviation of interannual flux per year

interannual_flux_week_df <- data.frame(year = "interannual", annual_flux_mean = interannual_flux_mean_week, 
                                  annual_flux_variability = interannual_flux_variability_week,
                        annual_flux_pi_lower = interannual_flux_pi_week[1], 
                        annual_flux_pi_upper = interannual_flux_pi_week[3])

total_flux_week_df <- rbind(annual_flux_week_df, interannual_flux_week_df)
total_flux_week_df$group <- c(rep("annual", nyears), "interannual")

ggplot()+
  geom_col(data = total_flux_week_df, aes(x=year, y = annual_flux_mean, fill = group))+
    geom_errorbar(data = total_flux_week_df, aes(x = year, ymin = annual_flux_pi_lower, ymax = annual_flux_pi_upper, col = "prediction interval"), width = 0.3, size = 0.8)+
  geom_errorbar(data = filter(total_flux_week_df, year == "interannual"), aes(x = year, ymin = annual_flux_mean - annual_flux_variability, ymax = annual_flux_mean + annual_flux_variability, col = "interannual variability"), width = 0.2, size = 0.8, linetype = 2)+
  scale_fill_manual(values = c("annual" = "lightblue", "interannual" = "indianred"))+
  scale_color_manual(values = c("prediction interval" = "darkblue", "interannual variability" = "darkred"), name = "")+
   labs(x = "Year", y = "Flux, from bi-dayly mean values (ton/year)", fill = "")+
  theme_minimal(base_size = 15)+
  theme(axis.text.x = element_text(angle = 45, hjust = 1), legend.position = "bottom")
```
## 2 weeks

```{r avenelles-week2, cache.lazy = F}
# prepare df
avenelles_group_week2 <- avenelles_time %>% mutate(week = week(DateHeure), week2 =  floor(as.numeric(week - min(week)) / 2), year = year(DateHeure)) %>% group_by(week2,year) # group isere_time by week2
nrow_week2 <- n_groups(avenelles_group_week2)


# creates matrix for DOC
avenelles_doc_week2 <- avenelles_group_week2 %>% select(c("week2", "doc_mg.L")) %>% summarize("list_doc" = list(doc_mg.L)) %>% ungroup() # creates a list of mes for each week2
doc_random_week2 <- replicate(nrep, sapply(avenelles_doc_week2$list_doc, function(x) sample(x,1)))%>% t() # matrix of mes: one random sample per week2, replicated 1000 times
# doc_week2_noise <- matrix(rnorm(nrep*nrow_week2, mean = 0, sd = doc_u), nrow = nrep, ncol = nrow_week2) 
# doc_mat_week2 <- doc_week2_random * (1 + doc_week2_noise) # final value of mes, with noise
# doc_mean <- colMeans(doc_mat_week2)

doc_cv_week2 <- 3.2*doc_random_week2^(-0.2)
rnorm_week2 <- matrix(rnorm(nrep*nrow_week2, mean = 0, sd = 1), nrow=nrep, ncol = nrow_week2)
doc_noise_week2 <- doc_cv_week2*rnorm_week2
doc_mat_week2 <- doc_random_week2 * (1 + doc_noise_week2/100) # final value of doc, with noise in percent

# matrix for q
q_week2 <- avenelles_group_week2 %>% select(c("week2", "q_L.s")) %>% summarize_all(list("q_mean" = mean, "q_sd" = sd)) %>% ungroup() # mean of Q for each week2

q_week2_mean <-  matrix(q_week2$q_mean, nrow = nrep, ncol = nrow_week2, byrow = T)
q_noise <- matrix(rnorm(nrep*nrow_week2, mean = 0, sd = q_u), nrow = nrep, ncol = nrow_week2) # creates a noise in percent (proportion), between 0 and 10%
q_mat_week2 <- q_week2_mean * (1 + q_noise) # final MC of q, with noise. SD NOT INCLUDED: will not always be available

# compute flux
flux_ton_mat_week2 <- doc_mat_week2*1e-9*q_mat_week2*60*60*24*14 #Doc in mg/L converted to ton; q_mat converted from m3/s to L/s. Period : nb of seconds in 1 week2. 

# Get index for columns by year
index_years <- lapply(complete_years, function(y){which(avenelles_doc_week2$year == y)}) # list of indices corresponding to each year

# annual flux
annual_flux_ton.y_week2 <- lapply(index_years, function(idx){apply(flux_ton_mat_week2[,idx], 1, sum, na.rm = T)}) %>% do.call("cbind", .) # sum of fluxes per year, for each iteration of the bootstrap. 
annual_flux_week2_pi <- apply(annual_flux_ton.y_week2, 2, quantile, probs = c(0.025, 0.5, 0.975), na.rm = T) # confidence interval for annual fluxes, per year. 3 lignes, 19 columns
annual_flux_week2_mean <- colMeans(annual_flux_ton.y_week2, na.rm = T) # mean annual flux per year. 1 vector
annual_flux_week2_sd <- apply(annual_flux_ton.y_week2, 2, sd, na.rm = T) # standard deviation of annual flux per year. Is just an estimate of goodness of mean, not as good as than the confidence interval. 
 
annual_flux_week2_df <- data.frame(year = complete_years, 
                        annual_flux_mean = annual_flux_week2_mean, 
                        annual_flux_variability = annual_flux_week2_sd, 
                        annual_flux_pi_lower = annual_flux_week2_pi[1,], 
                        annual_flux_pi_upper = annual_flux_week2_pi[3,])

interannual_flux_ton.y_week2 <- rowMeans(annual_flux_ton.y_week2, na.rm = T) # mean interannual flux per iteration of the bootstrap
interannual_flux_pi_week2 <- quantile(interannual_flux_ton.y_week2, probs = c(0.025, 0.5, 0.975), na.rm = T) # prediction interval
interannual_flux_mean_week2 <- mean(interannual_flux_ton.y_week2, na.rm = T) # mean interannual flux
interannual_flux_variability_week2 <- sd(annual_flux_week2_mean, na.rm = T) # standard deviation of interannual flux per year

interannual_flux_week2_df <- data.frame(year = "interannual", annual_flux_mean = interannual_flux_mean_week2, 
                                  annual_flux_variability = interannual_flux_variability_week2,
                        annual_flux_pi_lower = interannual_flux_pi_week2[1], 
                        annual_flux_pi_upper = interannual_flux_pi_week2[3])

total_flux_week2_df <- rbind(annual_flux_week2_df, interannual_flux_week2_df)
total_flux_week2_df$group <- c(rep("annual", nyears), "interannual")

ggplot()+
  geom_col(data = total_flux_week2_df, aes(x=year, y = annual_flux_mean, fill = group))+
    geom_errorbar(data = total_flux_week2_df, aes(x = year, ymin = annual_flux_pi_lower, ymax = annual_flux_pi_upper, col = "prediction interval"), width = 0.3, size = 0.8)+
  geom_errorbar(data = filter(total_flux_week2_df, year == "interannual"), aes(x = year, ymin = annual_flux_mean - annual_flux_variability, ymax = annual_flux_mean + annual_flux_variability, col = "interannual variability"), width = 0.2, size = 0.8, linetype = 2)+
  scale_fill_manual(values = c("annual" = "lightblue", "interannual" = "indianred"))+
  scale_color_manual(values = c("prediction interval" = "darkblue", "interannual variability" = "darkred"), name = "")+
   labs(x = "Year", y = "Flux, from bi-dayly mean values (ton/year)", fill = "")+
  theme_minimal(base_size = 15)+
  theme(axis.text.x = element_text(angle = 45, hjust = 1), legend.position = "bottom")
```
## Month

```{r avenelles-month, cache.lazy = F}
# prepare df
avenelles_group_month <- avenelles_time %>% mutate(week = week(DateHeure), month =  floor(as.numeric(week - min(week)) / 2), year = year(DateHeure)) %>% group_by(month,year) # group isere_time by month
nrow_month <- n_groups(avenelles_group_month)


# creates matrix for DOC
avenelles_doc_month <- avenelles_group_month %>% select(c("month", "doc_mg.L")) %>% summarize("list_doc" = list(doc_mg.L)) %>% ungroup() # creates a list of mes for each month
doc_random_month <- replicate(nrep, sapply(avenelles_doc_month$list_doc, function(x) sample(x,1)))%>% t() # matrix of mes: one random sample per month, replicated 1000 times

# doc_month_noise <- matrix(rnorm(nrep*nrow_month, mean = 0, sd = doc_u), nrow = nrep, ncol = nrow_month) 
# doc_mat_month <- doc_month_random * (1 + doc_month_noise) # final value of mes, with noise
# doc_mean <- colMeans(doc_mat_month)

doc_cv_month <- 3.2*doc_random_month^(-0.2)
rnorm_month <- matrix(rnorm(nrep*nrow_month, mean = 0, sd = 1), nrow=nrep, ncol = nrow_month)
doc_noise_month <- doc_cv_month*rnorm_month
doc_mat_month <- doc_random_month * (1 + doc_noise_month/100) # final value of doc, with noise in percent



# matrix for q
q_month <- avenelles_group_month %>% select(c("month", "q_L.s")) %>% summarize_all(list("q_mean" = mean, "q_sd" = sd)) %>% ungroup() # mean of Q for each month

q_month_mean <-  matrix(q_month$q_mean, nrow = nrep, ncol = nrow_month, byrow = T)
q_noise <- matrix(rnorm(nrep*nrow_month, mean = 0, sd = q_u), nrow = nrep, ncol = nrow_month) # creates a noise in percent (proportion), between 0 and 10%
q_mat_month <- q_month_mean * (1 + q_noise) # final MC of q, with noise. SD NOT INCLUDED: will not always be available

# compute flux
flux_ton_mat_month <- doc_mat_month*1e-9*q_mat_month*60*60*24*14 #Doc in mg/L converted to ton; q_mat converted from m3/s to L/s. Period : nb of seconds in 1 month. 

# Get index for columns by year
index_years <- lapply(complete_years, function(y){which(avenelles_doc_month$year == y)}) # list of indices corresponding to each year

# annual flux
annual_flux_ton.y_month <- lapply(index_years, function(idx){apply(flux_ton_mat_month[,idx], 1, sum, na.rm = T)}) %>% do.call("cbind", .) # sum of fluxes per year, for each iteration of the bootstrap. 
annual_flux_month_pi <- apply(annual_flux_ton.y_month, 2, quantile, probs = c(0.025, 0.5, 0.975), na.rm = T) # confidence interval for annual fluxes, per year. 3 lignes, 19 columns
annual_flux_month_mean <- colMeans(annual_flux_ton.y_month, na.rm = T) # mean annual flux per year. 1 vector
annual_flux_month_sd <- apply(annual_flux_ton.y_month, 2, sd, na.rm = T) # standard deviation of annual flux per year. Is just an estimate of goodness of mean, not as good as than the confidence interval. 
 
annual_flux_month_df <- data.frame(year = complete_years, 
                        annual_flux_mean = annual_flux_month_mean, 
                        annual_flux_variability = annual_flux_month_sd, 
                        annual_flux_pi_lower = annual_flux_month_pi[1,], 
                        annual_flux_pi_upper = annual_flux_month_pi[3,])

interannual_flux_ton.y_month <- rowMeans(annual_flux_ton.y_month, na.rm = T) # mean interannual flux per iteration of the bootstrap
interannual_flux_pi_month <- quantile(interannual_flux_ton.y_month, probs = c(0.025, 0.5, 0.975), na.rm = T) # prediction interval
interannual_flux_mean_month <- mean(interannual_flux_ton.y_month, na.rm = T) # mean interannual flux
interannual_flux_variability_month <- sd(annual_flux_month_mean, na.rm = T) # standard deviation of interannual flux per year

interannual_flux_month_df <- data.frame(year = "interannual", annual_flux_mean = interannual_flux_mean_month, 
                                  annual_flux_variability = interannual_flux_variability_month,
                        annual_flux_pi_lower = interannual_flux_pi_month[1], 
                        annual_flux_pi_upper = interannual_flux_pi_month[3])

total_flux_month_df <- rbind(annual_flux_month_df, interannual_flux_month_df)
total_flux_month_df$group <- c(rep("annual", nyears), "interannual")

ggplot()+
  geom_col(data = total_flux_month_df, aes(x=year, y = annual_flux_mean, fill = group))+
    geom_errorbar(data = total_flux_month_df, aes(x = year, ymin = annual_flux_pi_lower, ymax = annual_flux_pi_upper, col = "prediction interval"), width = 0.3, size = 0.8)+
  geom_errorbar(data = filter(total_flux_month_df, year == "interannual"), aes(x = year, ymin = annual_flux_mean - annual_flux_variability, ymax = annual_flux_mean + annual_flux_variability, col = "interannual variability"), width = 0.2, size = 0.8, linetype = 2)+
  scale_fill_manual(values = c("annual" = "lightblue", "interannual" = "indianred"))+
  scale_color_manual(values = c("prediction interval" = "darkblue", "interannual variability" = "darkred"), name = "")+
   labs(x = "Year", y = "Flux, from bi-dayly mean values (ton/year)", fill = "")+
  theme_minimal(base_size = 15)+
  theme(axis.text.x = element_text(angle = 45, hjust = 1), legend.position = "bottom")
```

## Compare fluxes

```{r interannual-error-in-percent, cache = F}
# relative error by Monte-Carlo world
error_day2 <- (interannual_flux_ton.y_day2 - interannual_flux_ton.y)/interannual_flux_ton.y * 100
error_day2_pi <- quantile(error_day2, probs = c(0.025, 0.5, 0.975), na.rm = T) # confidence interval for annual fluxes, per year. 3 lignes, 19 columns
error_day2_mean <- mean(error_day2)

error_day4 <- (interannual_flux_ton.y_day4 - interannual_flux_ton.y)/interannual_flux_ton.y * 100
error_day4_pi <- quantile(error_day4, probs = c(0.025, 0.5, 0.975), na.rm = T) # confidence interval for annual fluxes, per year. 3 lignes, 19 columns
error_day4_mean <- mean(error_day4)

error_week <- (interannual_flux_ton.y_week - interannual_flux_ton.y)/interannual_flux_ton.y * 100
error_week_pi <- quantile(error_week, probs = c(0.025, 0.5, 0.975), na.rm = T) # confidence interval for annual fluxes, per year. 3 lignes, 19 columns
error_week_mean <- mean(error_week)

error_week2 <- (interannual_flux_ton.y_week2 - interannual_flux_ton.y)/interannual_flux_ton.y * 100
error_week2_pi <- quantile(error_week2, probs = c(0.025, 0.5, 0.975), na.rm = T) # confidence interval for annual fluxes, per year. 3 lignes, 19 columns
error_week2_mean <- mean(error_week2)

error_month <- (interannual_flux_ton.y_month - interannual_flux_ton.y)/interannual_flux_ton.y * 100
error_month_pi <- quantile(error_month, probs = c(0.025, 0.5, 0.975), na.rm = T) # confidence interval for annual fluxes, per year. 3 lignes, 19 columns
error_month_mean <- mean(error_month)

error <- data.frame(time_step = factor(c("2days","4days","week","2weeks","month"), levels = c("day","2days","4days","week","2weeks","month")),
                    error = c(error_day2_mean, error_day4_mean, error_week_mean, error_week2_mean, error_month_mean),
                    pi_upr = c(error_day2_pi[3], error_day4_pi[3], error_week_pi[3], error_week2_pi[3], error_month_pi[3]),
                    pi_lwr = c(error_day2_pi[1], error_day4_pi[1], error_week_pi[1], error_week2_pi[1], error_month_pi[1])) 

ggplot(data=error, aes(x = time_step))+
  geom_point(aes(y = error))+
  geom_errorbar(aes(ymin=pi_lwr, ymax=pi_upr))+
  theme_minimal(base_size = 15)

error %>% knitr::kable(digits = 2, row.names = F) %>% kableExtra::kable_styling()
```
Bond d'erreur entre 2 days et 4 days: peut-être parce que dans le prélèvement initial, on est plus proche de tous les 2 jours que de tous les jours ? 


# Missing data 2017

```{r common-data-weighted-2017}
avenelles_2017 <- avenelles_flux %>% filter(year == 2017)

n_ave_2017 <- nrow(avenelles_2017)

mes_u <- 0.05
q_u <- 0.05

set.seed(503)

unique_years <- unique(avenelles_2017$year)
nyears <- length(unique_years)

n_rep <- 100

index_2017 <- which(avenelles_flux$year == 2017) # list of indices corresponding to each year
flux_ton.s_mat_2017 <- flux_ton.s_mat[,index_2017]
flux_ton_mat_2017 <- flux_ton_mat[,index_2017]
q_mat_2017  <- q_mat[,index_2017]
mean_q_2017 <- apply(q_mat, 1, mean, na.rm = T)

# Completude?
cat("nb obs 2017:", dim(flux_ton_mat_2017)[2])
cat("Period in s in Avenelles = ", sum(avenelles_2017$period), "; nb of s in 1 year = ", 365*24*60*60)

```

## 10% missing

```{r percent10-2017}

waf_10_2017 <- list()

for(i in 1:n_rep){
  block_size <- floor(n_ave_2017*0.10)
  start_idx <- sample(1:n_ave_2017, 1) # choisit aléatoirement une colonne où faire commencer le bloc manquant
  # idx_block <- start_idx:(start_idx + block_size - 1) # idx des colonnes du bloc
  # 
  # Calculer les indices du bloc (avec retour au début si nécessaire)
  if(start_idx + block_size - 1 <= n_ave_2017){
    # Le bloc ne dépasse pas : bloc simple
    idx_block <- start_idx:(start_idx + block_size - 1)
  } else {
    # Le bloc dépasse : il se sépare en 2 parties
    # Partie 1 : de start_idx à la fin
    part1 <- start_idx:n_ave_2017
    # Partie 2 : du début jusqu'à compléter block_size
    remaining <- block_size - length(part1)
    part2 <- 1:remaining
    # Combiner les deux parties
    idx_block <- c(part1, part2)
  }
  
  ftsm_10_2017 <- flux_ton.s_mat_2017[,-idx_block]
  q_10_2017 <- q_mat_2017[, -idx_block]

  # Annual flux
  sum_instant_flux_ton.y_10 <- apply(ftsm_10_2017, 1, sum, na.rm = T)  # sum of fluxes per year, for each MC world computed previously. Result is a matrix with 1000 rows 
  sum_instant_q_10 <- apply(q_10_2017, 1, sum, na.rm = T) # same for Q
  mean_instant_q_10 <- apply(q_10_2017, 1, mean, na.rm = T) # same for mean Q: 1000 lines
  
  weighted_annual_flux_ton.y_10 <- sum_instant_flux_ton.y_10 / sum_instant_q_10 * mean_q_2017 * 60 * 60 * 24 *365 # 1000 lines and 3 columns of weignted annual fluxes
  
  waf_10_2017[[i]] <- weighted_annual_flux_ton.y_10 # stored in the big list
}

waf_10_mcmean <- lapply(waf_10_2017, mean) %>% unlist()# moyenne des simulations montecarlo pour chaque resampling 
waf_10_upr_2017 <- lapply(waf_10_2017, quantile, 0.975) %>% unlist()
waf_10_lwr_2017 <- lapply(waf_10_2017, quantile, 0.025) %>% unlist()

```


## 20% missing

```{r percent20-2017}


waf_20_2017 <- list()

for(i in 1:n_rep){
   block_size <- floor(n_ave_2017*0.20)
   start_idx <- sample(1:n_ave_2017, 1) # choisit aléatoirement une colonne où faire commencer le bloc manquant
  # idx_block <- start_idx:(start_idx + block_size - 1) # idx des colonnes du bloc
  # 
    # Calculer les indices du bloc (avec retour au début si nécessaire)
  if(start_idx + block_size - 1 <= n_ave_2017){
    # Le bloc ne dépasse pas : bloc simple
    idx_block <- start_idx:(start_idx + block_size - 1)
  } else {
    # Le bloc dépasse : il se sépare en 2 parties
    # Partie 1 : de start_idx à la fin
    part1 <- start_idx:n_ave_2017
    # Partie 2 : du début jusqu'à compléter block_size
    remaining <- block_size - length(part1)
    part2 <- 1:remaining
    # Combiner les deux parties
    idx_block <- c(part1, part2)
  }
  
  ftsm_20_2017 <- flux_ton.s_mat_2017[,-idx_block]
  q_20_2017 <- q_mat_2017[, -idx_block]

  # Annual flux
  sum_instant_flux_ton.y_20 <- apply(ftsm_20_2017, 1, sum, na.rm = T)  # sum of fluxes per year, for each MC world computed previously. Result is a matrix with 1000 rows and 3 columns  (1 per year)
  sum_instant_q_20 <- apply(q_20_2017, 1, sum, na.rm = T) # same for Q
  mean_instant_q_20 <- apply(q_20_2017, 1, mean, na.rm = T) # same for mean Q: 1000 lines, 3 columns
  
  weighted_annual_flux_ton.y_20 <- sum_instant_flux_ton.y_20 / sum_instant_q_20 * mean_q_2017 * 60 * 60 * 24 *365 # 1000 lines and 3 columns of weignted annual fluxes
  
  waf_20_2017[[i]] <- weighted_annual_flux_ton.y_20 # stored in the big list
}

waf_20_mcmean <- lapply(waf_20_2017, mean) %>% unlist()# moyenne des simulations montecarlo pour chaque resampling 
waf_20_upr_2017 <- lapply(waf_20_2017, quantile, 0.975) %>% unlist()
waf_20_lwr_2017 <- lapply(waf_20_2017, quantile, 0.025) %>% unlist()


```

## 30% missing

```{r percent30-2017}


waf_30_2017 <- list()

for(i in 1:n_rep){
 block_size <- floor(n_ave_2017*0.30)
 start_idx <- sample(1:n_ave_2017, 1) # choisit aléatoirement une colonne où faire commencer le bloc manquant
  # idx_block <- start_idx:(start_idx + block_size - 1) # idx des colonnes du bloc
  # 
    # Calculer les indices du bloc (avec retour au début si nécessaire)
  if(start_idx + block_size - 1 <= n_ave_2017){
    # Le bloc ne dépasse pas : bloc simple
    idx_block <- start_idx:(start_idx + block_size - 1)
  } else {
    # Le bloc dépasse : il se sépare en 2 parties
    # Partie 1 : de start_idx à la fin
    part1 <- start_idx:n_ave_2017
    # Partie 2 : du début jusqu'à compléter block_size
    remaining <- block_size - length(part1)
    part2 <- 1:remaining
    # Combiner les deux parties
    idx_block <- c(part1, part2)
  }
  
  ftsm_30_2017 <- flux_ton.s_mat_2017[,-idx_block]
  q_30_2017 <- q_mat_2017[, -idx_block]

  # Annual flux
  sum_instant_flux_ton.y_30 <- apply(ftsm_30_2017, 1, sum, na.rm = T)  # sum of fluxes per year, for each MC world computed previously. Result is a matrix with 1000 rows and 3 columns  (1 per year)
  sum_instant_q_30 <- apply(q_30_2017, 1, sum, na.rm = T) # same for Q
  mean_instant_q_30 <- apply(q_30_2017, 1, mean, na.rm = T) # same for mean Q: 1000 lines, 3 columns
  
  weighted_annual_flux_ton.y_30 <- sum_instant_flux_ton.y_30 / sum_instant_q_30 * mean_q_2017 * 60 * 60 * 24 *365 # 1000 lines and 3 columns of weignted annual fluxes
  
  waf_30_2017[[i]] <- weighted_annual_flux_ton.y_30 # stored in the big list
}

waf_30_mcmean <- lapply(waf_30_2017, mean) %>% unlist()# moyenne des simulations montecarlo pour chaque resampling 
waf_30_upr_2017 <- lapply(waf_30_2017, quantile, 0.975) %>% unlist()
waf_30_lwr_2017 <- lapply(waf_30_2017, quantile, 0.025) %>% unlist()


```

## 40% missing

```{r percent40-2017}


waf_40_2017 <- list()

for(i in 1:n_rep){
 block_size <- floor(n_ave_2017*0.40)
 start_idx <- sample(1:n_ave_2017, 1) # choisit aléatoirement une colonne où faire commencer le bloc manquant
  # idx_block <- start_idx:(start_idx + block_size - 1) # idx des colonnes du bloc
 
   # Calculer les indices du bloc (avec retour au début si nécessaire)
  if(start_idx + block_size - 1 <= n_ave_2017){
    # Le bloc ne dépasse pas : bloc simple
    idx_block <- start_idx:(start_idx + block_size - 1)
  } else {
    # Le bloc dépasse : il se sépare en 2 parties
    # Partie 1 : de start_idx à la fin
    part1 <- start_idx:n_ave_2017
    # Partie 2 : du début jusqu'à compléter block_size
    remaining <- block_size - length(part1)
    part2 <- 1:remaining
    # Combiner les deux parties
    idx_block <- c(part1, part2)
  }
  
  ftsm_40_2017 <- flux_ton.s_mat_2017[,-idx_block]
  q_40_2017 <- q_mat_2017[, -idx_block]

  # Annual flux
  sum_instant_flux_ton.y_40 <- apply(ftsm_40_2017, 1, sum, na.rm = T)  # sum of fluxes per year, for each MC world computed previously. Result is a matrix with 1000 rows and 3 columns  (1 per year)
  sum_instant_q_40 <- apply(q_40_2017, 1, sum, na.rm = T) # same for Q
  mean_instant_q_40 <- apply(q_40_2017, 1, mean, na.rm = T) # same for mean Q: 1000 lines, 3 columns
  
  weighted_annual_flux_ton.y_40 <- sum_instant_flux_ton.y_40 / sum_instant_q_40 * mean_q_2017 * 60 * 60 * 24 *365 # 1000 lines and 3 columns of weignted annual fluxes
  
  waf_40_2017[[i]] <- weighted_annual_flux_ton.y_40 # stored in the big list
}

waf_40_mcmean <- lapply(waf_40_2017, mean) %>% unlist() # moyenne des simulations montecarlo pour chaque resampling 
waf_40_upr_2017 <- lapply(waf_40_2017, quantile, 0.975) %>% unlist()
waf_40_lwr_2017 <- lapply(waf_40_2017, quantile, 0.025) %>% unlist()


```


## 50% missing

```{r percent50-2017}


waf_50_2017 <- list()

for(i in 1:n_rep){
 block_size <- floor(n_ave_2017*0.50)
 start_idx <- sample(1:n_ave_2017, 1) # choisit aléatoirement une colonne où faire commencer le bloc manquant
  # idx_block <- start_idx:(start_idx + block_size - 1) # idx des colonnes du bloc
 
   # Calculer les indices du bloc (avec retour au début si nécessaire)
  if(start_idx + block_size - 1 <= n_ave_2017){
    # Le bloc ne dépasse pas : bloc simple
    idx_block <- start_idx:(start_idx + block_size - 1)
  } else {
    # Le bloc dépasse : il se sépare en 2 parties
    # Partie 1 : de start_idx à la fin
    part1 <- start_idx:n_ave_2017
    # Partie 2 : du début jusqu'à compléter block_size
    remaining <- block_size - length(part1)
    part2 <- 1:remaining
    # Combiner les deux parties
    idx_block <- c(part1, part2)
  }
  
  ftsm_50_2017 <- flux_ton.s_mat_2017[,-idx_block]
  q_50_2017 <- q_mat_2017[, -idx_block]
  
  # Annual flux
  sum_instant_flux_ton.y_50 <- apply(ftsm_50_2017, 1, sum, na.rm = T)  # sum of fluxes per year, for each MC world computed previously. Result is a matrix with 1000 rows and 3 columns  (1 per year)
  sum_instant_q_50 <- apply(q_50_2017, 1, sum, na.rm = T) # same for Q
  mean_instant_q_50 <- apply(q_50_2017, 1, mean, na.rm = T) # same for mean Q: 1000 lines, 3 columns
  
  weighted_annual_flux_ton.y_50 <- sum_instant_flux_ton.y_50 / sum_instant_q_50 * mean_q_2017 * 60 * 60 * 24 *365 # 1000 lines and 3 columns of weignted annual fluxes
  
  waf_50_2017[[i]] <- weighted_annual_flux_ton.y_50 # stored in the big list
}

waf_50_mcmean <- lapply(waf_50_2017, mean) %>% unlist() # moyenne des simulations montecarlo pour chaque resampling 
waf_50_upr_2017 <- lapply(waf_50_2017, quantile, 0.975) %>% unlist()
waf_50_lwr_2017 <- lapply(waf_50_2017, quantile, 0.025) %>% unlist()


```

## 60% missing

from here we select a block instead of removing it

```{r percent60-2017}


waf_60_2017 <- list()

for(i in 1:n_rep){
  block_size <- floor(n_ave_2017*0.60)
   start_idx <- sample(1:n_ave_2017, 1) # choisit aléatoirement une colonne où faire commencer le bloc choisi
  # idx_block <- start_idx:(start_idx + block_size - 1) # idx des colonnes du bloc
  
    # Calculer les indices du bloc (avec retour au début si nécessaire)
  if(start_idx + block_size - 1 <= n_ave_2017){
    # Le bloc ne dépasse pas : bloc simple
    idx_block <- start_idx:(start_idx + block_size - 1)
  } else {
    # Le bloc dépasse : il se sépare en 2 parties
    # Partie 1 : de start_idx à la fin
    part1 <- start_idx:n_ave_2017
    # Partie 2 : du début jusqu'à compléter block_size
    remaining <- block_size - length(part1)
    part2 <- 1:remaining
    # Combiner les deux parties
    idx_block <- c(part1, part2)
  }
  
  ftsm_60_2017 <- flux_ton.s_mat_2017[,-idx_block]
  q_60_2017 <- q_mat_2017[, -idx_block]
  
  # Annual flux
  sum_instant_flux_ton.y_60 <- apply(ftsm_60_2017, 1, sum, na.rm = T)  # sum of fluxes per year, for each MC world computed previously. Result is a matrix with 1000 rows and 3 columns  (1 per year)
  sum_instant_q_60 <- apply(q_60_2017, 1, sum, na.rm = T) # same for Q
  mean_instant_q_60 <- apply(q_60_2017, 1, mean, na.rm = T) # same for mean Q: 1000 lines, 3 columns
  
  weighted_annual_flux_ton.y_60 <- sum_instant_flux_ton.y_60 / sum_instant_q_60 * mean_q_2017 * 60 * 60 * 24 *365 # 1000 lines and 3 columns of weignted annual fluxes
  
  waf_60_2017[[i]] <- weighted_annual_flux_ton.y_60 # stored in the big list
}

waf_60_mcmean <- lapply(waf_60_2017, mean) %>% unlist() # moyenne des simulations montecarlo pour chaque resampling 
waf_60_upr_2017 <- lapply(waf_60_2017, quantile, 0.975) %>% unlist()
waf_60_lwr_2017 <- lapply(waf_60_2017, quantile, 0.025) %>% unlist()


```

## 70% missing

```{r percent70-2017}


waf_70_2017 <- list()

for(i in 1:n_rep){
  block_size <- floor(n_ave_2017*0.70)
   start_idx <- sample(1:n_ave_2017, 1) # choisit aléatoirement une colonne où faire commencer le bloc choisi
  # idx_block <- start_idx:(start_idx + block_size - 1) # idx des colonnes du bloc
  # 
    # Calculer les indices du bloc (avec retour au début si nécessaire)
  if(start_idx + block_size - 1 <= n_ave_2017){
    # Le bloc ne dépasse pas : bloc simple
    idx_block <- start_idx:(start_idx + block_size - 1)
  } else {
    # Le bloc dépasse : il se sépare en 2 parties
    # Partie 1 : de start_idx à la fin
    part1 <- start_idx:n_ave_2017
    # Partie 2 : du début jusqu'à compléter block_size
    remaining <- block_size - length(part1)
    part2 <- 1:remaining
    # Combiner les deux parties
    idx_block <- c(part1, part2)
  }
  
  ftsm_70_2017 <- flux_ton.s_mat_2017[,-idx_block]
  q_70_2017 <- q_mat_2017[, -idx_block]
  
  # Annual flux
  sum_instant_flux_ton.y_70 <- apply(ftsm_70_2017, 1, sum, na.rm = T)  # sum of fluxes per year, for each MC world computed previously. Result is a matrix with 1000 rows and 3 columns  (1 per year)
  sum_instant_q_70 <- apply(q_70_2017, 1, sum, na.rm = T) # same for Q
  mean_instant_q_70 <- apply(q_70_2017, 1, mean, na.rm = T) # same for mean Q: 1000 lines, 3 columns
  
  weighted_annual_flux_ton.y_70 <- sum_instant_flux_ton.y_70 / sum_instant_q_70 * mean_q_2017 * 60 * 60 * 24 *365 # 1000 lines and 3 columns of weignted annual fluxes
  
  waf_70_2017[[i]] <- weighted_annual_flux_ton.y_70 # stored in the big list
}

waf_70_mcmean <- lapply(waf_70_2017, mean) %>% unlist()# moyenne des simulations montecarlo pour chaque resampling 
waf_70_upr_2017 <- lapply(waf_70_2017, quantile, 0.975) %>% unlist()
waf_70_lwr_2017 <- lapply(waf_70_2017, quantile, 0.025) %>% unlist()


```

## 80% missing

```{r percent80-2017}


waf_80_2017 <- list()

for(i in 1:n_rep){
 block_size <- floor(n_ave_2017*0.80)
   start_idx <- sample(1:n_ave_2017, 1) # choisit aléatoirement une colonne où faire commencer le bloc choisi
  # idx_block <- start_idx:(start_idx + block_size - 1) # idx des colonnes du bloc
 
   # Calculer les indices du bloc (avec retour au début si nécessaire)
  if(start_idx + block_size - 1 <= n_ave_2017){
    # Le bloc ne dépasse pas : bloc simple
    idx_block <- start_idx:(start_idx + block_size - 1)
  } else {
    # Le bloc dépasse : il se sépare en 2 parties
    # Partie 1 : de start_idx à la fin
    part1 <- start_idx:n_ave_2017
    # Partie 2 : du début jusqu'à compléter block_size
    remaining <- block_size - length(part1)
    part2 <- 1:remaining
    # Combiner les deux parties
    idx_block <- c(part1, part2)
  }
  # 
  ftsm_80_2017 <- flux_ton.s_mat_2017[,-idx_block]
  q_80_2017 <- q_mat_2017[, -idx_block]

  # Annual flux
  sum_instant_flux_ton.y_80 <- apply(ftsm_80_2017, 1, sum, na.rm = T)  # sum of fluxes per year, for each MC world computed previously. Result is a matrix with 1000 rows and 3 columns  (1 per year)
  sum_instant_q_80 <- apply(q_80_2017, 1, sum, na.rm = T) # same for Q
  mean_instant_q_80 <- apply(q_80_2017, 1, mean, na.rm = T) # same for mean Q: 1000 lines, 3 columns
  
  weighted_annual_flux_ton.y_80 <- sum_instant_flux_ton.y_80 / sum_instant_q_80 * mean_q_2017 * 60 * 60 * 24 *365 # 1000 lines and 3 columns of weignted annual fluxes
  
  waf_80_2017[[i]] <- weighted_annual_flux_ton.y_80 # stored in the big list
}

waf_80_mcmean <- lapply(waf_80_2017, mean) %>% unlist() # moyenne des simulations montecarlo pour chaque resampling 
waf_80_upr_2017 <- lapply(waf_80_2017, quantile, 0.975) %>% unlist()
waf_80_lwr_2017 <- lapply(waf_80_2017, quantile, 0.025) %>% unlist()


```

## 90% missing

```{r percent90-2017}


waf_90_2017 <- list()

for(i in 1:n_rep){
 block_size <- floor(n_ave_2017*0.90)
 start_idx <- sample(1:n_ave_2017, 1) # choisit aléatoirement une colonne où faire commencer le bloc choisi
  # idx_block <- start_idx:(start_idx + block_size - 1) # idx des colonnes du bloc
 
   # Calculer les indices du bloc (avec retour au début si nécessaire)
  if(start_idx + block_size - 1 <= n_ave_2017){
    # Le bloc ne dépasse pas : bloc simple
    idx_block <- start_idx:(start_idx + block_size - 1)
  } else {
    # Le bloc dépasse : il se sépare en 2 parties
    # Partie 1 : de start_idx à la fin
    part1 <- start_idx:n_ave_2017
    # Partie 2 : du début jusqu'à compléter block_size
    remaining <- block_size - length(part1)
    part2 <- 1:remaining
    # Combiner les deux parties
    idx_block <- c(part1, part2)
  }
  
  ftsm_90_2017 <- flux_ton.s_mat_2017[,-idx_block]
  q_90_2017 <- q_mat_2017[, -idx_block]

  # Annual flux
  sum_instant_flux_ton.y_90 <- apply(ftsm_90_2017, 1, sum, na.rm = T)  # sum of fluxes per year, for each MC world computed previously. Result is a matrix with 1000 rows and 3 columns  (1 per year)
  sum_instant_q_90 <- apply(q_90_2017, 1, sum, na.rm = T) # same for Q
  mean_instant_q_90 <- apply(q_90_2017, 1, mean, na.rm = T) # same for mean Q: 1000 lines, 3 columns
  
  weighted_annual_flux_ton.y_90 <- sum_instant_flux_ton.y_90 / sum_instant_q_90 * mean_q_2017 * 60 * 60 * 24 *365 # 1000 lines and 3 columns of weignted annual fluxes
  
  waf_90_2017[[i]] <- weighted_annual_flux_ton.y_90 # stored in the big list
}

waf_90_mcmean <- lapply(waf_90_2017, mean) %>% unlist() # moyenne des simulations montecarlo pour chaque resampling 
waf_90_upr_2017 <- lapply(waf_90_2017, quantile, 0.975) %>% unlist() # quantile superieur pour chaque resampling
waf_90_lwr_2017 <- lapply(waf_90_2017, quantile, 0.025) %>% unlist() # quantile inférieur pour chaque resampling


```

## No missing data

```{r percent100-2017}
# REF
flux_ref_2017 <- apply(flux_ton_mat_2017, 1, sum, na.rm = T)
flux_ref_2017_mean <- mean(flux_ref_2017)
flux_ref_2017_lwr <- quantile(flux_ref_2017, 0.025)
flux_ref_2017_upr <- quantile(flux_ref_2017, 0.975)

mean_q_2017 <- apply(q_mat, 1, mean, na.rm = T)
q_sum_2017<- apply(q_mat, 1, mean, na.rm = T)

# weighted
sum_instant_flux_ton.y_100 <- apply(flux_ton.s_mat_2017, 1, sum, na.rm = T)  # sum of fluxes per year, for each MC world computed previously. Result is a matrix with 1000 rows and 3 columns  (1 per year)
sum_instant_q_100 <- apply(q_mat_2017, 1, sum, na.rm = T) # same for Q

weighted_annual_flux_ton.y_100 <- sum_instant_flux_ton.y_100 / sum_instant_q_100 * mean_q_2017 * 60 * 60 * 24 *365 # 1000 lines and 3 columns of weignted annual fluxes

waf_100_mcmean <- mean(weighted_annual_flux_ton.y_100) # moyenne des simulations montecarlo 
waf_100_upr_2017 <- quantile(weighted_annual_flux_ton.y_100, 0.975) 
waf_100_lwr_2017 <- quantile(weighted_annual_flux_ton.y_100, 0.025) 


```

## Compare weighted fluxes

The "error" represents the range in which resampled interannual mean fall. Max value = 97.5% quantile of the 100 resampled means; minimum value = 2.5% quantile of the 100 resampled means; median value = median value of the 100 resampled means. 

```{r weighted-fluxes-compared-to-ref}

error_mwf2017 <- data.frame(percent_missing_data = c(10,20,30,40,50,60,70,80,90,0,"Ref"),
  mean_wflux = c(mean((waf_10_mcmean-flux_ref_2017)/flux_ref_2017*100), 
                 mean((waf_20_mcmean-flux_ref_2017)/flux_ref_2017*100), 
                 mean((waf_30_mcmean-flux_ref_2017)/flux_ref_2017*100), 
                 mean((waf_40_mcmean-flux_ref_2017)/flux_ref_2017*100), 
                 mean((waf_50_mcmean-flux_ref_2017)/flux_ref_2017*100), 
                 mean((waf_60_mcmean-flux_ref_2017)/flux_ref_2017*100),
                 mean((waf_70_mcmean-flux_ref_2017)/flux_ref_2017*100),
                 mean((waf_80_mcmean-flux_ref_2017)/flux_ref_2017*100), 
                 mean((waf_90_mcmean-flux_ref_2017)/flux_ref_2017*100), 
                 mean((waf_100_mcmean-flux_ref_2017)/flux_ref_2017*100), 
                 mean((flux_ref_2017-flux_ref_2017)/flux_ref_2017*100)),
  max_mean = c(max((waf_10_mcmean-flux_ref_2017)/flux_ref_2017*100),
               max((waf_20_mcmean-flux_ref_2017)/flux_ref_2017*100), 
               max((waf_30_mcmean-flux_ref_2017)/flux_ref_2017*100), 
               max((waf_40_mcmean-flux_ref_2017)/flux_ref_2017*100), 
               max((waf_50_mcmean-flux_ref_2017)/flux_ref_2017*100), 
               max((waf_60_mcmean-flux_ref_2017)/flux_ref_2017*100), 
               max((waf_70_mcmean-flux_ref_2017)/flux_ref_2017*100), 
               max((waf_80_mcmean-flux_ref_2017)/flux_ref_2017*100), 
               max((waf_90_mcmean-flux_ref_2017)/flux_ref_2017*100), 
               max((waf_100_mcmean-flux_ref_2017)/flux_ref_2017*100), 
               max((flux_ref_2017-flux_ref_2017)/flux_ref_2017*100)),
  min_mean = c(min((waf_10_mcmean-flux_ref_2017)/flux_ref_2017*100),
               min((waf_20_mcmean-flux_ref_2017)/flux_ref_2017*100), 
               min((waf_30_mcmean-flux_ref_2017)/flux_ref_2017*100), 
               min((waf_40_mcmean-flux_ref_2017)/flux_ref_2017*100), 
               min((waf_50_mcmean-flux_ref_2017)/flux_ref_2017*100), 
               min((waf_60_mcmean-flux_ref_2017)/flux_ref_2017*100), 
               min((waf_70_mcmean-flux_ref_2017)/flux_ref_2017*100), 
               min((waf_80_mcmean-flux_ref_2017)/flux_ref_2017*100), 
               min((waf_90_mcmean-flux_ref_2017)/flux_ref_2017*100), 
               min((waf_100_mcmean-flux_ref_2017)/flux_ref_2017*100), 
               min((flux_ref_2017-flux_ref_2017)/flux_ref_2017*100)))

error_mwf2017$percent_missing_data <- factor(error_mwf2017$percent_missing_data, levels = c("Ref",0,10,20,30,40,50,60,70,80,90))

ggplot(data = error_mwf2017, aes(x = percent_missing_data))+
  geom_point(aes(y = mean_wflux))+
  geom_errorbar(aes(ymin = min_mean, ymax = max_mean, col = "Prediction interval range"))+
  labs(title = "Mean, max and min error of resampled fluxes", y = "Error in %")+
  theme_minimal(base_size = 15)+
  theme(legend.position = "bottom", axis.text.x = element_text(angle = 45))

error_mwf2017 %>% knitr::kable(digits = 2, row.names = F) %>% kableExtra::kable_styling()

# boxplot
error_boxplot <- data.frame("M10" = (waf_10_mcmean-flux_ref_2017)/flux_ref_2017*100,
                            "M20" = (waf_20_mcmean-flux_ref_2017)/flux_ref_2017*100,
                            "M30" = (waf_30_mcmean-flux_ref_2017)/flux_ref_2017*100,
                            "M40" = (waf_40_mcmean-flux_ref_2017)/flux_ref_2017*100,
                            "M50" = (waf_50_mcmean-flux_ref_2017)/flux_ref_2017*100,
                            "M60" = (waf_60_mcmean-flux_ref_2017)/flux_ref_2017*100,
                            "M70" = (waf_70_mcmean-flux_ref_2017)/flux_ref_2017*100,
                            "M80" = (waf_80_mcmean-flux_ref_2017)/flux_ref_2017*100,
                            "M90" = (waf_90_mcmean-flux_ref_2017)/flux_ref_2017*100,
                            "M0" = (waf_100_mcmean-flux_ref_2017)/flux_ref_2017*100,
                            "Ref" = (flux_ref_2017-flux_ref_2017)/flux_ref_2017*100
                            )

error_boxplot_long <- tidyr::pivot_longer(data = error_boxplot, cols = 1:11, names_to = "percent_missing", values_to = "error_percent")
error_boxplot_long$percent_missing <- factor(error_boxplot_long$percent_missing, levels = c("Ref","M0","M10","M20","M30","M40","M50","M60","M70","M80","M90"))
error_boxplot_long$Site <- "Avenelles"
error_boxplot_long$OC <- "DOC"

write.csv(error_boxplot_long, "error_boxplot_long_avenelles.csv")

ggplot(error_boxplot_long)+
  geom_boxplot(aes(y=error_percent, x=percent_missing))+
  theme_minimal()
```





# Compare biais weighting method

```{r load-data-for-biais, eval = F}
list.files("avenelles_cache/html/")
#load("avenelles_cache/html/constant-numbers_a01f3a223c35de779edf5e8e955f3746.RData")

knitr::load_cache(label = "constant-numbers", path = "avenelles_cache/html/", envir = .GlobalEnv)

```

```{r weighted-fluxes-100}
# 2009 ---- 
avenelles_2009 <- avenelles_flux %>% filter(year == 2009)

percent_year_2009 <- round(dim(avenelles_2009)[1]/365*100, digits = 2)

index_2009 <- which(avenelles_flux$year == 2009) # list of indices corresponding to each year
flux_ton.s_mat_2009 <- flux_ton.s_mat[,index_2009]
flux_ton_mat_2009 <- flux_ton_mat[,index_2009]
q_mat_2009  <- q_mat[,index_2009]
mean_q_2009 <- apply(q_mat, 1, mean, na.rm = T)


flux_ref_2009 <- apply(flux_ton_mat_2009, 1, sum, na.rm = T)
mean_q_2009 <- apply(q_mat, 1, mean, na.rm = T)
q_sum_2009 <- apply(q_mat, 1, mean, na.rm = T)

sum_instant_flux_ton.y_2009 <- apply(flux_ton.s_mat_2009, 1, sum, na.rm = T)  # sum of fluxes per year, for each MC world computed previously. Result is a matrix with 1000 rows and 3 columns  (1 per year)
sum_instant_q_2009 <- apply(q_mat_2009, 1, sum, na.rm = T) # same for Q
weighted_annual_flux_ton.y_2009 <- sum_instant_flux_ton.y_2009 / sum_instant_q_2009 * mean_q_2009 * 60 * 60 * 24 *365 # 1000 lines and 3 columns of weignted annual fluxes
waf_100_mcmean_2009 <- mean(weighted_annual_flux_ton.y_2009, na.rm = T) # moyenne des simulations montecarlo 

# 2011 ----
avenelles_2011 <- avenelles_flux %>% filter(year == 2011)

percent_year_2011 <- round(dim(avenelles_2011)[1]/365*100, digits = 2)

index_2011 <- which(avenelles_flux$year == 2011) # list of indices corresponding to each year
flux_ton.s_mat_2011 <- flux_ton.s_mat[,index_2011]
flux_ton_mat_2011 <- flux_ton_mat[,index_2011]
q_mat_2011  <- q_mat[,index_2011]
mean_q_2011 <- apply(q_mat, 1, mean, na.rm = T)

flux_ref_2011 <- apply(flux_ton_mat_2011, 1, sum, na.rm = T)
mean_q_2011 <- apply(q_mat, 1, mean, na.rm = T)
q_sum_2011 <- apply(q_mat, 1, mean, na.rm = T)

sum_instant_flux_ton.y_2011 <- apply(flux_ton.s_mat_2011, 1, sum, na.rm = T)  # sum of fluxes per year, for each MC world computed previously. Result is a matrix with 1000 rows and 3 columns  (1 per year)
sum_instant_q_2011 <- apply(q_mat_2011, 1, sum, na.rm = T) # same for Q
weighted_annual_flux_ton.y_2011 <- sum_instant_flux_ton.y_2011 / sum_instant_q_2011 * mean_q_2009 * 60 * 60 * 24 *365 # 1000 lines and 3 columns of weignted annual fluxes
waf_100_mcmean_2011 <- mean(weighted_annual_flux_ton.y_2011, na.rm = T) # moyenne des simulations montecarlo 

# 2012 ----
avenelles_2012 <- avenelles_flux %>% filter(year == 2012)

percent_year_2012 <- round(dim(avenelles_2012)[1]/365*100, digits = 2)

index_2012 <- which(avenelles_flux$year == 2012) # list of indices corresponding to each year
flux_ton.s_mat_2012 <- flux_ton.s_mat[,index_2012]
flux_ton_mat_2012 <- flux_ton_mat[,index_2012]
q_mat_2012  <- q_mat[,index_2012]
mean_q_2012 <- apply(q_mat, 1, mean, na.rm = T)

flux_ref_2012 <- apply(flux_ton_mat_2012, 1, sum, na.rm = T)
mean_q_2012 <- apply(q_mat, 1, mean, na.rm = T)
q_sum_2012 <- apply(q_mat, 1, mean, na.rm = T)

sum_instant_flux_ton.y_2012 <- apply(flux_ton.s_mat_2012, 1, sum, na.rm = T)  # sum of fluxes per year, for each MC world computed previously. Result is a matrix with 1000 rows and 3 columns  (1 per year)
sum_instant_q_2012 <- apply(q_mat_2012, 1, sum, na.rm = T) # same for Q
weighted_annual_flux_ton.y_2012 <- sum_instant_flux_ton.y_2012 / sum_instant_q_2012 * mean_q_2009 * 60 * 60 * 24 *365 # 1000 lines and 3 columns of weignted annual fluxes
waf_100_mcmean_2012 <- mean(weighted_annual_flux_ton.y_2012, na.rm = T) # moyenne des simulations montecarlo 

# 2013 ----
avenelles_2013 <- avenelles_flux %>% filter(year == 2013)

percent_year_2013 <- round(dim(avenelles_2013)[1]/365*100, digits = 2)

index_2013 <- which(avenelles_flux$year == 2013) # list of indices corresponding to each year
flux_ton.s_mat_2013 <- flux_ton.s_mat[,index_2013]
flux_ton_mat_2013 <- flux_ton_mat[,index_2013]
q_mat_2013  <- q_mat[,index_2013]
mean_q_2013 <- apply(q_mat, 1, mean, na.rm = T)

flux_ref_2013 <- apply(flux_ton_mat_2013, 1, sum, na.rm = T)
mean_q_2013 <- apply(q_mat, 1, mean, na.rm = T)
q_sum_2013 <- apply(q_mat, 1, mean, na.rm = T)

sum_instant_flux_ton.y_2013 <- apply(flux_ton.s_mat_2013, 1, sum, na.rm = T)  # sum of fluxes per year, for each MC world computed previously. Result is a matrix with 1000 rows and 3 columns  (1 per year)
sum_instant_q_2013 <- apply(q_mat_2013, 1, sum, na.rm = T) # same for Q
weighted_annual_flux_ton.y_2013 <- sum_instant_flux_ton.y_2013 / sum_instant_q_2013 * mean_q_2009 * 60 * 60 * 24 *365 # 1000 lines and 3 columns of weignted annual fluxes
waf_100_mcmean_2013 <- mean(weighted_annual_flux_ton.y_2013, na.rm = T) # moyenne des simulations montecarlo 

# 2014 ----
avenelles_2014 <- avenelles_flux %>% filter(year == 2014)

percent_year_2014 <- round(dim(avenelles_2014)[1]/365*100, digits = 2)

index_2014 <- which(avenelles_flux$year == 2014) # list of indices corresponding to each year
flux_ton.s_mat_2014 <- flux_ton.s_mat[,index_2014]
flux_ton_mat_2014 <- flux_ton_mat[,index_2014]
q_mat_2014  <- q_mat[,index_2014]
mean_q_2014 <- apply(q_mat, 1, mean, na.rm = T)

flux_ref_2014 <- apply(flux_ton_mat_2014, 1, sum, na.rm = T)
mean_q_2014 <- apply(q_mat, 1, mean, na.rm = T)
q_sum_2014 <- apply(q_mat, 1, mean, na.rm = T)

sum_instant_flux_ton.y_2014 <- apply(flux_ton.s_mat_2014, 1, sum, na.rm = T)  # sum of fluxes per year, for each MC world computed previously. Result is a matrix with 1000 rows and 3 columns  (1 per year)
sum_instant_q_2014 <- apply(q_mat_2014, 1, sum, na.rm = T) # same for Q
weighted_annual_flux_ton.y_2014 <- sum_instant_flux_ton.y_2014 / sum_instant_q_2014 * mean_q_2009 * 60 * 60 * 24 *365 # 1000 lines and 3 columns of weignted annual fluxes
waf_100_mcmean_2014 <- mean(weighted_annual_flux_ton.y_2014, na.rm = T) # moyenne des simulations montecarlo 

# 2015 ----
avenelles_2015 <- avenelles_flux %>% filter(year == 2015)

percent_year_2015 <- round(dim(avenelles_2015)[1]/365*100, digits = 2)

index_2015 <- which(avenelles_flux$year == 2015) # list of indices corresponding to each year
flux_ton.s_mat_2015 <- flux_ton.s_mat[,index_2015]
flux_ton_mat_2015 <- flux_ton_mat[,index_2015]
q_mat_2015  <- q_mat[,index_2015]
mean_q_2015 <- apply(q_mat, 1, mean, na.rm = T)

flux_ref_2015 <- apply(flux_ton_mat_2015, 1, sum, na.rm = T)
mean_q_2015 <- apply(q_mat, 1, mean, na.rm = T)
q_sum_2015 <- apply(q_mat, 1, mean, na.rm = T)

sum_instant_flux_ton.y_2015 <- apply(flux_ton.s_mat_2015, 1, sum, na.rm = T)  # sum of fluxes per year, for each MC world computed previously. Result is a matrix with 1000 rows and 3 columns  (1 per year)
sum_instant_q_2015 <- apply(q_mat_2015, 1, sum, na.rm = T) # same for Q
weighted_annual_flux_ton.y_2015 <- sum_instant_flux_ton.y_2015 / sum_instant_q_2015 * mean_q_2009 * 60 * 60 * 24 *365 # 1000 lines and 3 columns of weignted annual fluxes
waf_100_mcmean_2015 <- mean(weighted_annual_flux_ton.y_2015, na.rm = T) # moyenne des simulations montecarlo 

# 2016 ----
avenelles_2016 <- avenelles_flux %>% filter(year == 2016)

percent_year_2016 <- round(dim(avenelles_2016)[1]/365*100, digits = 2)

index_2016 <- which(avenelles_flux$year == 2016) # list of indices corresponding to each year
flux_ton.s_mat_2016 <- flux_ton.s_mat[,index_2016]
flux_ton_mat_2016 <- flux_ton_mat[,index_2016]
q_mat_2016  <- q_mat[,index_2016]
mean_q_2016 <- apply(q_mat, 1, mean, na.rm = T)

flux_ref_2016 <- apply(flux_ton_mat_2016, 1, sum, na.rm = T)
mean_q_2016 <- apply(q_mat, 1, mean, na.rm = T)
q_sum_2016 <- apply(q_mat, 1, mean, na.rm = T)

sum_instant_flux_ton.y_2016 <- apply(flux_ton.s_mat_2016, 1, sum, na.rm = T)  # sum of fluxes per year, for each MC world computed previously. Result is a matrix with 1000 rows and 3 columns  (1 per year)
sum_instant_q_2016 <- apply(q_mat_2016, 1, sum, na.rm = T) # same for Q
weighted_annual_flux_ton.y_2016 <- sum_instant_flux_ton.y_2016 / sum_instant_q_2016 * mean_q_2009 * 60 * 60 * 24 *365 # 1000 lines and 3 columns of weignted annual fluxes
waf_100_mcmean_2016 <- mean(weighted_annual_flux_ton.y_2016, na.rm = T) # moyenne des simulations montecarlo 

# 2021 ----
avenelles_2021 <- avenelles_flux %>% filter(year == 2021)

percent_year_2021 <- round(dim(avenelles_2021)[1]/365*100, digits = 2)

index_2021 <- which(avenelles_flux$year == 2021) # list of indices corresponding to each year
flux_ton.s_mat_2021 <- flux_ton.s_mat[,index_2021]
flux_ton_mat_2021 <- flux_ton_mat[,index_2021]
q_mat_2021  <- q_mat[,index_2021]
mean_q_2021 <- apply(q_mat, 1, mean, na.rm = T)

flux_ref_2021 <- apply(flux_ton_mat_2021, 1, sum, na.rm = T)
mean_q_2021 <- apply(q_mat, 1, mean, na.rm = T)
q_sum_2021 <- apply(q_mat, 1, mean, na.rm = T)

sum_instant_flux_ton.y_2021 <- apply(flux_ton.s_mat_2021, 1, sum, na.rm = T)  # sum of fluxes per year, for each MC world computed previously. Result is a matrix with 1000 rows and 3 columns  (1 per year)
sum_instant_q_2021 <- apply(q_mat_2021, 1, sum, na.rm = T) # same for Q
weighted_annual_flux_ton.y_2021 <- sum_instant_flux_ton.y_2021 / sum_instant_q_2021 * mean_q_2009 * 60 * 60 * 24 *365 # 1000 lines and 3 columns of weignted annual fluxes
waf_100_mcmean_2021 <- mean(weighted_annual_flux_ton.y_2021, na.rm = T) # moyenne des simulations montecarlo 


```


```{r compare-biais}
biais <- data.frame(year = c(2009,2011,2012,2013,2014,2015,2016,2021),
                    percent_year = c(percent_year_2009, percent_year_2011, percent_year_2012, percent_year_2013, percent_year_2014, percent_year_2015, percent_year_2016, percent_year_2021),
                    mean_biais = c(mean((waf_100_mcmean_2009-flux_ref_2009)/flux_ref_2009*100),
                                   mean((waf_100_mcmean_2011-flux_ref_2011)/flux_ref_2011*100),
                                   mean((waf_100_mcmean_2012-flux_ref_2012)/flux_ref_2012*100),
                                   mean((waf_100_mcmean_2013-flux_ref_2013)/flux_ref_2013*100),
                                   mean((waf_100_mcmean_2014-flux_ref_2014)/flux_ref_2014*100),
                                   mean((waf_100_mcmean_2015-flux_ref_2015)/flux_ref_2015*100),
                                   mean((waf_100_mcmean_2016-flux_ref_2016)/flux_ref_2016*100),
                                   mean((waf_100_mcmean_2021-flux_ref_2021)/flux_ref_2021*100)),
                    median_biais = c(median((waf_100_mcmean_2009-flux_ref_2009)/flux_ref_2009*100),
                                   median((waf_100_mcmean_2011-flux_ref_2011)/flux_ref_2011*100),
                                   median((waf_100_mcmean_2012-flux_ref_2012)/flux_ref_2012*100),
                                   median((waf_100_mcmean_2013-flux_ref_2013)/flux_ref_2013*100),
                                   median((waf_100_mcmean_2014-flux_ref_2014)/flux_ref_2014*100),
                                   median((waf_100_mcmean_2015-flux_ref_2015)/flux_ref_2015*100),
                                   median((waf_100_mcmean_2016-flux_ref_2016)/flux_ref_2016*100),
                                   median((waf_100_mcmean_2021-flux_ref_2021)/flux_ref_2021*100)),
                    max_biais = c(max((waf_100_mcmean_2009-flux_ref_2009)/flux_ref_2009*100),
                                  max((waf_100_mcmean_2011-flux_ref_2011)/flux_ref_2011*100),
                                  max((waf_100_mcmean_2012-flux_ref_2012)/flux_ref_2012*100),
                                  max((waf_100_mcmean_2013-flux_ref_2013)/flux_ref_2013*100),
                                  max((waf_100_mcmean_2014-flux_ref_2014)/flux_ref_2014*100),
                                  max((waf_100_mcmean_2015-flux_ref_2015)/flux_ref_2015*100),
                                  max((waf_100_mcmean_2016-flux_ref_2016)/flux_ref_2016*100),
                                  max((waf_100_mcmean_2021-flux_ref_2021)/flux_ref_2021*100)),
                    min_biais = c(min((waf_100_mcmean_2009-flux_ref_2009)/flux_ref_2009*100),
                                  min((waf_100_mcmean_2011-flux_ref_2011)/flux_ref_2011*100),
                                  min((waf_100_mcmean_2012-flux_ref_2012)/flux_ref_2012*100),
                                  min((waf_100_mcmean_2013-flux_ref_2013)/flux_ref_2013*100),
                                  min((waf_100_mcmean_2014-flux_ref_2014)/flux_ref_2014*100),
                                  min((waf_100_mcmean_2015-flux_ref_2015)/flux_ref_2015*100),
                                  min((waf_100_mcmean_2016-flux_ref_2016)/flux_ref_2016*100),
                                  min((waf_100_mcmean_2021-flux_ref_2021)/flux_ref_2021*100)),
                    qmean.qsum = c(median(mean_q_2009 / sum_instant_q_2009),
                                   median(mean_q_2011 / sum_instant_q_2011),
                                   median(mean_q_2012 / sum_instant_q_2012),
                                   median(mean_q_2013 / sum_instant_q_2013),
                                   median(mean_q_2014 / sum_instant_q_2014),
                                   median(mean_q_2015 / sum_instant_q_2015),
                                   median(mean_q_2016 / sum_instant_q_2016),
                                   median(mean_q_2021 / sum_instant_q_2021)),
                    K = c(median(mean_q_2009 / sum_instant_q_2009 * 60 * 60 * 24 * 365),
                          median(mean_q_2011 / sum_instant_q_2011* 60 * 60 * 24 * 365),
                          median(mean_q_2012 / sum_instant_q_2012* 60 * 60 * 24 * 365),
                          median(mean_q_2013 / sum_instant_q_2013* 60 * 60 * 24 * 365),
                          median(mean_q_2014 / sum_instant_q_2014* 60 * 60 * 24 * 365),
                          median(mean_q_2015 / sum_instant_q_2015* 60 * 60 * 24 * 365),
                          median(mean_q_2016 / sum_instant_q_2016* 60 * 60 * 24 * 365),
                          median(mean_q_2021 / sum_instant_q_2021* 60 * 60 * 24 * 365)))


knitr::kable(biais, digits = 2) %>% kableExtra::kable_styling()

ggplot(biais)+geom_point(aes(x = K, y = median_biais, col = as.factor(year)))+
  geom_errorbar(aes(x = K, ymin = min_biais, ymax = max_biais))+
  theme_minimal()

lm(median_biais~K, data = biais) %>% summary()


biais_boxplot <- data.frame("2009" = (waf_100_mcmean_2009-flux_ref_2009)/flux_ref_2009*100,
                            "2011" = (waf_100_mcmean_2011-flux_ref_2011)/flux_ref_2011*100,
                            "2012" = (waf_100_mcmean_2012-flux_ref_2012)/flux_ref_2012*100,
                            "2013" = (waf_100_mcmean_2013-flux_ref_2013)/flux_ref_2013*100,
                            "2014" = (waf_100_mcmean_2014-flux_ref_2014)/flux_ref_2014*100,
                            "2015" = (waf_100_mcmean_2015-flux_ref_2015)/flux_ref_2015*100,
                            "2016" = (waf_100_mcmean_2016-flux_ref_2016)/flux_ref_2016*100,
                            "2021" = (waf_100_mcmean_2021-flux_ref_2021)/flux_ref_2021*100)

biais_boxplot_long <- tidyr::pivot_longer(data = biais_boxplot, cols = 1:8, names_to = "year", values_to = "biais_percent")
biais_boxplot_long$percent_year <- rep(c(percent_year_2009, percent_year_2011, percent_year_2012, percent_year_2013, percent_year_2014, percent_year_2015, percent_year_2016, percent_year_2021),1000)

ggplot(biais_boxplot_long)+
  geom_boxplot(aes(y=biais_percent, x=percent_year, col = year))+
  theme_minimal()

q_boxplot <- data.frame("2009" = mean_q_2009 / sum_instant_q_2009 * 24 *365,
                            "2011" = mean_q_2011 / sum_instant_q_2011 * 24 *365,
                        "2012" = mean_q_2012 / sum_instant_q_2012 * 24 *365,
                        "2013" = mean_q_2013 / sum_instant_q_2013 * 24 *365,
                        "2014" = mean_q_2014 / sum_instant_q_2014  * 24 *365,
                        "2015" = mean_q_2015 / sum_instant_q_2015  * 24 *365,
                        "2016" = mean_q_2016 / sum_instant_q_2016  * 24 *365,
                        "2021" = mean_q_2021 / sum_instant_q_2021 * 24 *365)

q_boxplot_long <- tidyr::pivot_longer(data = q_boxplot, cols = 1:8, names_to = "year", values_to = "qmean.qsum")

ggplot()+
  geom_boxplot(data = biais_boxplot_long, aes(y=biais_percent, x=year, col = "Biais"))+
  geom_boxplot(data = q_boxplot_long, aes(y=qmean.qsum, x=year, col = "Q"))+
    theme_minimal()

```


# Random missing values and weighting method

Corresponds to the case in which discharge is measured continuously while DOC is not. 
Using same code as earlier, only the data is not removed by block but randomly. 


```{r common-data-2017}
avenelles_2017 <- avenelles_flux %>% filter(year == 2017)

n_ave_2017 <- nrow(avenelles_2017)

mes_u <- 0.05
q_u <- 0.05

set.seed(503)

unique_years <- unique(avenelles_2017$year)
nyears <- length(unique_years)

n_rep <- 100

index_2017 <- which(avenelles_flux$year == 2017) # list of indices corresponding to each year
flux_ton.s_mat_2017 <- flux_ton.s_mat[,index_2017]
flux_ton_mat_2017 <- flux_ton_mat[,index_2017]
q_mat_2017  <- q_mat[,index_2017]
mean_q_2017 <- apply(q_mat, 1, mean, na.rm = T)
doc_mat_2017 <- doc_mat[, index_2017]


# Completude?
cat("nb obs 2017:", dim(flux_ton_mat_2017)[2], "\n")
cat("Period in s in Avenelles = ", sum(avenelles_2017$period), "\n Nb of s in 1 year = ", 365*24*60*60)
```



## 10% missing

```{r percent10-random-2017}

waf_10_2017 <- list()

for(i in 1:n_rep){
  idx <- sample(1:n_ave_2017, n_ave_2017*0.1)
  
  ftsm_10_2017 <- flux_ton.s_mat_2017[,-idx]
  q_10_2017 <- q_mat_2017[, -idx]

  # Annual flux
  sum_instant_flux_ton.y_10 <- apply(ftsm_10_2017, 1, sum, na.rm = T)  # sum of fluxes per year, for each MC world computed previously. Result is a matrix with 1000 rows 
  sum_instant_q_10 <- apply(q_10_2017, 1, sum, na.rm = T) # same for Q
  mean_instant_q_10 <- apply(q_10_2017, 1, mean, na.rm = T) # same for mean Q: 1000 lines
  
  weighted_annual_flux_ton.y_10 <- sum_instant_flux_ton.y_10 / sum_instant_q_10 * mean_q_2017 * 60 * 60 * 24 *365 # 1000 lines and 3 columns of weignted annual fluxes
  
  waf_10_2017[[i]] <- weighted_annual_flux_ton.y_10 # stored in the big list
}

waf_10_mcmean <- lapply(waf_10_2017, mean) %>% unlist()# moyenne des simulations montecarlo pour chaque resampling 
waf_10_upr_2017 <- lapply(waf_10_2017, quantile, 0.975) %>% unlist()
waf_10_lwr_2017 <- lapply(waf_10_2017, quantile, 0.025) %>% unlist()

```

## 20% missing

```{r percent20-random-2017}

waf_20_2017 <- list()

for(i in 1:n_rep){
  idx <- sample(1:n_ave_2017, n_ave_2017*0.20)
  
  ftsm_20_2017 <- flux_ton.s_mat_2017[,-idx]
  q_20_2017 <- q_mat_2017[, -idx]

  # Annual flux
  sum_instant_flux_ton.y_20 <- apply(ftsm_20_2017, 1, sum, na.rm = T)  # sum of fluxes per year, for each MC world computed previously. Result is a matrix with 1000 rows 
  sum_instant_q_20 <- apply(q_20_2017, 1, sum, na.rm = T) # same for Q
  mean_instant_q_20 <- apply(q_20_2017, 1, mean, na.rm = T) # same for mean Q: 1000 lines
  
  weighted_annual_flux_ton.y_20 <- sum_instant_flux_ton.y_20 / sum_instant_q_20 * mean_q_2017 * 60 * 60 * 24 *365 # 1000 lines and 3 columns of weignted annual fluxes
  
  waf_20_2017[[i]] <- weighted_annual_flux_ton.y_20 # stored in the big list
}

waf_20_mcmean <- lapply(waf_20_2017, mean) %>% unlist()# moyenne des simulations montecarlo pour chaque resampling 
waf_20_upr_2017 <- lapply(waf_20_2017, quantile, 0.975) %>% unlist()
waf_20_lwr_2017 <- lapply(waf_20_2017, quantile, 0.025) %>% unlist()

```

## 30% missing

```{r percent30-random-2017}

waf_30_2017 <- list()

for(i in 1:n_rep){
  idx <- sample(1:n_ave_2017, n_ave_2017*0.30)
  
  ftsm_30_2017 <- flux_ton.s_mat_2017[,-idx]
  q_30_2017 <- q_mat_2017[, -idx]

  # Annual flux
  sum_instant_flux_ton.y_30 <- apply(ftsm_30_2017, 1, sum, na.rm = T)  # sum of fluxes per year, for each MC world computed previously. Result is a matrix with 1000 rows 
  sum_instant_q_30 <- apply(q_30_2017, 1, sum, na.rm = T) # same for Q
  mean_instant_q_30 <- apply(q_30_2017, 1, mean, na.rm = T) # same for mean Q: 1000 lines
  
  weighted_annual_flux_ton.y_30 <- sum_instant_flux_ton.y_30 / sum_instant_q_30 * mean_q_2017 * 60 * 60 * 24 *365 # 1000 lines and 3 columns of weignted annual fluxes
  
  waf_30_2017[[i]] <- weighted_annual_flux_ton.y_30 # stored in the big list
}

waf_30_mcmean <- lapply(waf_30_2017, mean) %>% unlist()# moyenne des simulations montecarlo pour chaque resampling 
waf_30_upr_2017 <- lapply(waf_30_2017, quantile, 0.975) %>% unlist()
waf_30_lwr_2017 <- lapply(waf_30_2017, quantile, 0.025) %>% unlist()

```

## 40% missing

```{r percent40-random-2017}

waf_40_2017 <- list()

for(i in 1:n_rep){
  idx <- sample(1:n_ave_2017, n_ave_2017*0.40)
  
  ftsm_40_2017 <- flux_ton.s_mat_2017[,-idx]
  q_40_2017 <- q_mat_2017[, -idx]

  # Annual flux
  sum_instant_flux_ton.y_40 <- apply(ftsm_40_2017, 1, sum, na.rm = T)  # sum of fluxes per year, for each MC world computed previously. Result is a matrix with 1000 rows 
  sum_instant_q_40 <- apply(q_40_2017, 1, sum, na.rm = T) # same for Q
  mean_instant_q_40 <- apply(q_40_2017, 1, mean, na.rm = T) # same for mean Q: 1000 lines
  
  weighted_annual_flux_ton.y_40 <- sum_instant_flux_ton.y_40 / sum_instant_q_40 * mean_q_2017 * 60 * 60 * 24 *365 # 1000 lines and 3 columns of weignted annual fluxes
  
  waf_40_2017[[i]] <- weighted_annual_flux_ton.y_40 # stored in the big list
}

waf_40_mcmean <- lapply(waf_40_2017, mean) %>% unlist()# moyenne des simulations montecarlo pour chaque resampling 
waf_40_upr_2017 <- lapply(waf_40_2017, quantile, 0.975) %>% unlist()
waf_40_lwr_2017 <- lapply(waf_40_2017, quantile, 0.025) %>% unlist()

```

## 50% missing

```{r percent50-random-2017}

waf_50_2017 <- list()

for(i in 1:n_rep){
  idx <- sample(1:n_ave_2017, n_ave_2017*0.50)
  
  ftsm_50_2017 <- flux_ton.s_mat_2017[,-idx]
  q_50_2017 <- q_mat_2017[, -idx]

  # Annual flux
  sum_instant_flux_ton.y_50 <- apply(ftsm_50_2017, 1, sum, na.rm = T)  # sum of fluxes per year, for each MC world computed previously. Result is a matrix with 1000 rows 
  sum_instant_q_50 <- apply(q_50_2017, 1, sum, na.rm = T) # same for Q
  mean_instant_q_50 <- apply(q_50_2017, 1, mean, na.rm = T) # same for mean Q: 1000 lines
  
  weighted_annual_flux_ton.y_50 <- sum_instant_flux_ton.y_50 / sum_instant_q_50 * mean_q_2017 * 60 * 60 * 24 *365 # 1000 lines and 3 columns of weignted annual fluxes
  
  waf_50_2017[[i]] <- weighted_annual_flux_ton.y_50 # stored in the big list
}

waf_50_mcmean <- lapply(waf_50_2017, mean) %>% unlist()# moyenne des simulations montecarlo pour chaque resampling 
waf_50_upr_2017 <- lapply(waf_50_2017, quantile, 0.975) %>% unlist()
waf_50_lwr_2017 <- lapply(waf_50_2017, quantile, 0.025) %>% unlist()

```

## 60% missing

```{r percent60-random-2017}

waf_60_2017 <- list()

for(i in 1:n_rep){
  idx <- sample(1:n_ave_2017, n_ave_2017*0.60)
  
  ftsm_60_2017 <- flux_ton.s_mat_2017[,-idx]
  q_60_2017 <- q_mat_2017[, -idx]

  # Annual flux
  sum_instant_flux_ton.y_60 <- apply(ftsm_60_2017, 1, sum, na.rm = T)  # sum of fluxes per year, for each MC world computed previously. Result is a matrix with 1000 rows 
  sum_instant_q_60 <- apply(q_60_2017, 1, sum, na.rm = T) # same for Q
  mean_instant_q_60 <- apply(q_60_2017, 1, mean, na.rm = T) # same for mean Q: 1000 lines
  
  weighted_annual_flux_ton.y_60 <- sum_instant_flux_ton.y_60 / sum_instant_q_60 * mean_q_2017 * 60 * 60 * 24 *365 # 1000 lines and 3 columns of weignted annual fluxes
  
  waf_60_2017[[i]] <- weighted_annual_flux_ton.y_60 # stored in the big list
}

waf_60_mcmean <- lapply(waf_60_2017, mean) %>% unlist()# moyenne des simulations montecarlo pour chaque resampling 
waf_60_upr_2017 <- lapply(waf_60_2017, quantile, 0.975) %>% unlist()
waf_60_lwr_2017 <- lapply(waf_60_2017, quantile, 0.025) %>% unlist()

```

## 70% missing

```{r percent70-random-2017}

waf_70_2017 <- list()

for(i in 1:n_rep){
  idx <- sample(1:n_ave_2017, n_ave_2017*0.70)
  
  ftsm_70_2017 <- flux_ton.s_mat_2017[,-idx]
  q_70_2017 <- q_mat_2017[, -idx]

  # Annual flux
  sum_instant_flux_ton.y_70 <- apply(ftsm_70_2017, 1, sum, na.rm = T)  # sum of fluxes per year, for each MC world computed previously. Result is a matrix with 1000 rows 
  sum_instant_q_70 <- apply(q_70_2017, 1, sum, na.rm = T) # same for Q
  mean_instant_q_70 <- apply(q_70_2017, 1, mean, na.rm = T) # same for mean Q: 1000 lines
  
  weighted_annual_flux_ton.y_70 <- sum_instant_flux_ton.y_70 / sum_instant_q_70 * mean_q_2017 * 60 * 60 * 24 *365 # 1000 lines and 3 columns of weignted annual fluxes
  
  waf_70_2017[[i]] <- weighted_annual_flux_ton.y_70 # stored in the big list
}

waf_70_mcmean <- lapply(waf_70_2017, mean) %>% unlist()# moyenne des simulations montecarlo pour chaque resampling 
waf_70_upr_2017 <- lapply(waf_70_2017, quantile, 0.975) %>% unlist()
waf_70_lwr_2017 <- lapply(waf_70_2017, quantile, 0.025) %>% unlist()

```

## 80% missing

```{r percent80-random-2017}

waf_80_2017 <- list()

for(i in 1:n_rep){
  idx <- sample(1:n_ave_2017, n_ave_2017*0.80)
  
  ftsm_80_2017 <- flux_ton.s_mat_2017[,-idx]
  q_80_2017 <- q_mat_2017[, -idx]

  # Annual flux
  sum_instant_flux_ton.y_80 <- apply(ftsm_80_2017, 1, sum, na.rm = T)  # sum of fluxes per year, for each MC world computed previously. Result is a matrix with 1000 rows 
  sum_instant_q_80 <- apply(q_80_2017, 1, sum, na.rm = T) # same for Q
  mean_instant_q_80 <- apply(q_80_2017, 1, mean, na.rm = T) # same for mean Q: 1000 lines
  
  weighted_annual_flux_ton.y_80 <- sum_instant_flux_ton.y_80 / sum_instant_q_80 * mean_q_2017 * 60 * 60 * 24 *365 # 1000 lines and 3 columns of weignted annual fluxes
  
  waf_80_2017[[i]] <- weighted_annual_flux_ton.y_80 # stored in the big list
}

waf_80_mcmean <- lapply(waf_80_2017, mean) %>% unlist()# moyenne des simulations montecarlo pour chaque resampling 
waf_80_upr_2017 <- lapply(waf_80_2017, quantile, 0.975) %>% unlist()
waf_80_lwr_2017 <- lapply(waf_80_2017, quantile, 0.025) %>% unlist()

```

## 90% missing

```{r percent90-random-2017}

waf_90_2017 <- list()

for(i in 1:n_rep){
  idx <- sample(1:n_ave_2017, n_ave_2017*0.90)
  
  ftsm_90_2017 <- flux_ton.s_mat_2017[,-idx]
  q_90_2017 <- q_mat_2017[, -idx]

  # Annual flux
  sum_instant_flux_ton.y_90 <- apply(ftsm_90_2017, 1, sum, na.rm = T)  # sum of fluxes per year, for each MC world computed previously. Result is a matrix with 1000 rows 
  sum_instant_q_90 <- apply(q_90_2017, 1, sum, na.rm = T) # same for Q
  mean_instant_q_90 <- apply(q_90_2017, 1, mean, na.rm = T) # same for mean Q: 1000 lines
  
  weighted_annual_flux_ton.y_90 <- sum_instant_flux_ton.y_90 / sum_instant_q_90 * mean_q_2017 * 60 * 60 * 24 *365 # 1000 lines and 3 columns of weignted annual fluxes
  
  waf_90_2017[[i]] <- weighted_annual_flux_ton.y_90 # stored in the big list
}

waf_90_mcmean <- lapply(waf_90_2017, mean) %>% unlist()# moyenne des simulations montecarlo pour chaque resampling 
waf_90_upr_2017 <- lapply(waf_90_2017, quantile, 0.975) %>% unlist()
waf_90_lwr_2017 <- lapply(waf_90_2017, quantile, 0.025) %>% unlist()

```

## No missing data

```{r percent100-random-2017}

# REF
flux_ref_2017 <- apply(flux_ton_mat_2017, 1, sum, na.rm = T)
flux_ref_2017_mean <- mean(flux_ref_2017)
flux_ref_2017_lwr <- quantile(flux_ref_2017, 0.025)
flux_ref_2017_upr <- quantile(flux_ref_2017, 0.975)

flux_ton.s_2017_mean <- apply(flux_ton.s_mat_2017, 1, sum, na.rm = T) %>% mean()

mean_q_2017 <- apply(q_mat, 1, mean, na.rm = T)
q_sum_2017<- apply(q_mat, 1, mean, na.rm = T)

# weighted
sum_instant_flux_ton.y_100 <- apply(flux_ton.s_mat_2017, 1, sum, na.rm = T)  # sum of fluxes per year, for each MC world computed previously. Result is a matrix with 1000 rows and 3 columns  (1 per year)
sum_instant_q_100 <- apply(q_mat_2017, 1, sum, na.rm = T) # same for Q

weighted_annual_flux_ton.y_100 <- sum_instant_flux_ton.y_100 / sum_instant_q_100 * mean_q_2017 * 60 * 60 * 24 *365 # 1000 lines and 3 columns of weighted annual fluxes

waf_100_mcmean <- mean(weighted_annual_flux_ton.y_100) # moyenne des simulations montecarlo 
waf_100_upr_2017 <- quantile(weighted_annual_flux_ton.y_100, 0.975) 
waf_100_lwr_2017 <- quantile(weighted_annual_flux_ton.y_100, 0.025) 


```

## Compare weighted fluxes

The "error" represents the range in which resampled interannual mean fall. Max value = 97.5% quantile of the 100 resampled means; minimum value = 2.5% quantile of the 100 resampled means; median value = median value of the 100 resampled means. 

```{r random-weighted-fluxes-compared-to-ref}

error_mwf2017 <- data.frame(percent_missing_data = c(10,20,30,40,50,60,70,80,90,0,"Ref"),
  mean_wflux = c(mean((waf_10_mcmean-flux_ref_2017)/flux_ref_2017*100), 
                 mean((waf_20_mcmean-flux_ref_2017)/flux_ref_2017*100), 
                 mean((waf_30_mcmean-flux_ref_2017)/flux_ref_2017*100), 
                 mean((waf_40_mcmean-flux_ref_2017)/flux_ref_2017*100), 
                 mean((waf_50_mcmean-flux_ref_2017)/flux_ref_2017*100), 
                 mean((waf_60_mcmean-flux_ref_2017)/flux_ref_2017*100),
                 mean((waf_70_mcmean-flux_ref_2017)/flux_ref_2017*100),
                 mean((waf_80_mcmean-flux_ref_2017)/flux_ref_2017*100), 
                 mean((waf_90_mcmean-flux_ref_2017)/flux_ref_2017*100), 
                 mean((waf_100_mcmean-flux_ref_2017)/flux_ref_2017*100), 
                 mean((flux_ref_2017-flux_ref_2017)/flux_ref_2017*100)),
  max_mean = c(max((waf_10_mcmean-flux_ref_2017)/flux_ref_2017*100),
               max((waf_20_mcmean-flux_ref_2017)/flux_ref_2017*100), 
               max((waf_30_mcmean-flux_ref_2017)/flux_ref_2017*100), 
               max((waf_40_mcmean-flux_ref_2017)/flux_ref_2017*100), 
               max((waf_50_mcmean-flux_ref_2017)/flux_ref_2017*100), 
               max((waf_60_mcmean-flux_ref_2017)/flux_ref_2017*100), 
               max((waf_70_mcmean-flux_ref_2017)/flux_ref_2017*100), 
               max((waf_80_mcmean-flux_ref_2017)/flux_ref_2017*100), 
               max((waf_90_mcmean-flux_ref_2017)/flux_ref_2017*100), 
               max((waf_100_mcmean-flux_ref_2017)/flux_ref_2017*100), 
               max((flux_ref_2017-flux_ref_2017)/flux_ref_2017*100)),
  min_mean = c(min((waf_10_mcmean-flux_ref_2017)/flux_ref_2017*100),
               min((waf_20_mcmean-flux_ref_2017)/flux_ref_2017*100), 
               min((waf_30_mcmean-flux_ref_2017)/flux_ref_2017*100), 
               min((waf_40_mcmean-flux_ref_2017)/flux_ref_2017*100), 
               min((waf_50_mcmean-flux_ref_2017)/flux_ref_2017*100), 
               min((waf_60_mcmean-flux_ref_2017)/flux_ref_2017*100), 
               min((waf_70_mcmean-flux_ref_2017)/flux_ref_2017*100), 
               min((waf_80_mcmean-flux_ref_2017)/flux_ref_2017*100), 
               min((waf_90_mcmean-flux_ref_2017)/flux_ref_2017*100), 
               min((waf_100_mcmean-flux_ref_2017)/flux_ref_2017*100), 
               min((flux_ref_2017-flux_ref_2017)/flux_ref_2017*100)))

error_mwf2017$percent_missing_data <- factor(error_mwf2017$percent_missing_data, levels = c("Ref",0,10,20,30,40,50,60,70,80,90))

ggplot(data = error_mwf2017, aes(x = percent_missing_data))+
  geom_point(aes(y = mean_wflux))+
  geom_errorbar(aes(ymin = min_mean, ymax = max_mean, col = "Prediction interval range"))+
  labs(title = "Mean, max and min error of resampled fluxes", y = "Error in %")+
  theme_minimal(base_size = 15)+
  theme(legend.position = "bottom", axis.text.x = element_text(angle = 45))

error_mwf2017 %>% knitr::kable(digits = 2, row.names = F) %>% kableExtra::kable_styling()

# boxplot
error_boxplot <- data.frame("M10" = (waf_10_mcmean-flux_ref_2017)/flux_ref_2017*100,
                            "M20" = (waf_20_mcmean-flux_ref_2017)/flux_ref_2017*100,
                            "M30" = (waf_30_mcmean-flux_ref_2017)/flux_ref_2017*100,
                            "M40" = (waf_40_mcmean-flux_ref_2017)/flux_ref_2017*100,
                            "M50" = (waf_50_mcmean-flux_ref_2017)/flux_ref_2017*100,
                            "M60" = (waf_60_mcmean-flux_ref_2017)/flux_ref_2017*100,
                            "M70" = (waf_70_mcmean-flux_ref_2017)/flux_ref_2017*100,
                            "M80" = (waf_80_mcmean-flux_ref_2017)/flux_ref_2017*100,
                            "M90" = (waf_90_mcmean-flux_ref_2017)/flux_ref_2017*100,
                            "M0" = (waf_100_mcmean-flux_ref_2017)/flux_ref_2017*100,
                            "Ref" = (flux_ref_2017-flux_ref_2017)/flux_ref_2017*100
                            )

error_boxplot_long <- tidyr::pivot_longer(data = error_boxplot, cols = 1:11, names_to = "percent_missing", values_to = "error_percent")
error_boxplot_long$percent_missing <- factor(error_boxplot_long$percent_missing, levels = c("Ref","M0","M10","M20","M30","M40","M50","M60","M70","M80","M90"))
error_boxplot_long$Site <- "Avenelles"
error_boxplot_long$OC <- "DOC"

write.csv(error_boxplot_long, "error_boxplot_long_avenelles.csv")

ggplot(error_boxplot_long)+
  geom_boxplot(aes(y=error_percent, x=percent_missing))+
  theme_minimal()
```
## Origin of bias: negative correlation between doc and Q?

```{r}

```


# Over formulas for weighting

Dans l'ordre de citation de Walling & Webb 1985, Table 1 : 10.1016/0025-326X(85)90382-0

## Verhoff et al 1980

```{r total-load-verhoff}

sum_doc.n_2017 <- apply(doc_mat_2017*1e-9/n_ave_2017,1,sum, na.rm = T)
sum_q.n_2017 <- apply(q_mat_2017/n_ave_2017,1,sum, na.rm = T)

verhoff_2017 <- sum_doc.n_2017*sum_q.n_2017*60*60*24*365
verhoff_2017_mcmean <- mean(verhoff_2017)
verhoff_2017_upr <- quantile(verhoff_2017, 0.975) 
verhoff_2017_lwr <- quantile(verhoff_2017, 0.025) 

cat(verhoff_2017_mcmean, "compared to", flux_ref_2017_mean,"\n +",(verhoff_2017_mcmean-flux_ref_2017_mean)/flux_ref_2017_mean*100,"%")

```
## Rodda & Jones 1983

```{r total-load-rodda}

# Qp est le débit moyen pour l'intervalle entre chaque Ci. Ici on utilise l'année complète, donc Qp = Qi 
sum_qdoc.n_2017 <- apply(doc_mat_2017*1e-9*q_mat_2017,1,sum, na.rm = T)

rodd_2017 <- sum_qdoc.n_2017*60*60*24*365
rodd_2017_mcmean <- mean(rodd_2017)
rodd_2017_upr <- quantile(rodd_2017, 0.975) 
rodd_2017_lwr <- quantile(rodd_2017, 0.025) 

cat(rodd_2017_mcmean, "compared to", flux_ref_2017_mean,"\n +",(rodd_2017_mcmean-flux_ref_2017_mean)/flux_ref_2017_mean*100,"%")

```
## Walling & Webb 1981

```{r total-load-walling}

sum_qdoc_2017 <- apply(doc_mat_2017*1e-9*q_mat_2017,1,sum, na.rm = T)

walling_2017 <- sum_qdoc_2017*60*60*24*365
walling_2017_mcmean <- mean(walling_2017)
walling_2017_upr <- quantile(walling_2017, 0.975) 
walling_2017_lwr <- quantile(walling_2017, 0.025) 

cat(walling_2017_mcmean, "compared to", flux_ref_2017_mean,"\n +",(walling_2017_mcmean-flux_ref_2017_mean)/flux_ref_2017_mean*100,"%")

```
## Ongley 1973

```{r total-load-ongley}

# le flux moyen sur la période correspond à mean_q_2017

ongley_2017 <- sum_doc.n_2017*mean_q_2017*60*60*24*365
ongley_2017_mcmean <- mean(ongley_2017)
ongley_2017_upr <- quantile(ongley_2017, 0.975) 
ongley_2017_lwr <- quantile(ongley_2017, 0.025) 

cat(ongley_2017_mcmean, "compared to", flux_ref_2017_mean,"\n +",(ongley_2017_mcmean-flux_ref_2017_mean)/flux_ref_2017_mean*100,"%")

```
## Unbiaised Kendall 1983

Eq 6 in @Cooper2002


```{r total-load-kendall}

m_q <- apply(q_mat_2017, 1, sum, na.rm = T) / n_ave_2017 # ici mu_q = m_q

m_doc <- apply(doc_mat_2017*1e-9, 1, sum, na.rm = T) / n_ave_2017

m_flux <- apply(doc_mat_2017*1e-9*q_mat_2017, 1, sum, na.rm = T) / n_ave_2017

kendall_2017 <- n_ave_2017*m_flux + (m_flux-m_doc*m_q) 
kendall_2017_mcmean <- mean(kendall_2017)
kendall_2017_upr <- quantile(kendall_2017, 0.975) 
kendall_2017_lwr <- quantile(kendall_2017, 0.025) 

cat(kendall_2017_mcmean, "compared to", flux_ref_2017_mean,"\n",(kendall_2017_mcmean-flux_ref_2017_mean)/flux_ref_2017_mean*100,"%")

```

Quand on prend toutes les obs, kendall_2017_mcmean est égal à la somme des flux instantanés flux_ton.s_2017_mean. 

## Beales

```{r total-load-beales}
library(funtimes)

q_2017 <- avenelles_2017$q_L.s
flux_2017 <- avenelles_2017$doc_mg.L*avenelles_2017$q_L.s 
flux_p50 <- flux_2017 %>% replace(sample(n_ave_2017, n_ave_2017*0.5), NA)

B2017 <- beales(q_2017, flux_2017)

B2017_0.5 <- beales(q_2017, flux_p50)
```
Beales utile pour calculer le flux moyen par seconde, mais pas le flux annuel (comme unbiaised Kendall ???)

```{r relation-doc-q-2017}
ggplot(avenelles_2017, aes(x=q_L.s, y = doc_mg.L))+geom_point()+geom_smooth()+
  labs(subtitle = paste("R = ", round(cor(avenelles_2017$q_L.s, avenelles_2017$doc_mg.L),2)))
ggplot(avenelles_2017, aes(x=log(q_L.s), y = doc_mg.L))+geom_point()+geom_smooth()+
  labs(subtitle = paste("R = ", round(cor(log(avenelles_2017$q_L.s), avenelles_2017$doc_mg.L),2)))
ggplot(avenelles_2017, aes(x=log(q_L.s), y = log(doc_mg.L)))+geom_point()+geom_smooth()+
  labs(subtitle = paste("R = ", round(cor(log(avenelles_2017$q_L.s), log(avenelles_2017$doc_mg.L)),2)))

ggarrange(
ggplot(avenelles_2017, aes(x=DateHeure, y = dic_mg.L)) + geom_point(),
  ggplot(avenelles_2017, aes(x=DateHeure, y = doc_mg.L)) + geom_point(),
ggplot(avenelles_2017, aes(x=DateHeure, y = q_L.s)) + geom_abline(slope = 0, intercept = 134) + geom_point(),
nrow = 3)
```

# Exit

```{r exit, cache = F}
knitr::knit_exit()
```


```{r stratification}
quantile(avenelles_2017$q_L.s)
quantile(avenelles$q_L.s, na.rm = T)
ggplot(subset(avenelles_2017, q_L.s > 134), aes(x = q_L.s, y = doc_mg.L)) + geom_point()

subset(avenelles_2017, q_L.s < 134) %>% pull(doc_mg.L) %>% boxplot()

ave2017_etiage <- subset(avenelles_2017, q_L.s < 134)
ave2017_crues <- subset(avenelles_2017, q_L.s > 134)

load_etiage_mg.s <- with(ave2017_etiage, q_L.s*doc_mg.L)
q_etiage_L.s <- ave2017_etiage$q_L.s
B2017_etiage <- beales(q_etiage_L.s, replace(load_etiage_mg.s, 6, NA))
B2017_etiage_p50 <- beales(q_etiage_L.s, replace(load_etiage_mg.s, sample(1:104,52), NA))


load_crues_mg.s <- with(ave2017_crues, q_L.s*doc_mg.L)
q_crues_L.s <- ave2017_crues$q_L.s
B2017_crues <- beales(q_crues_L.s, replace(load_crues_mg.s, 6, NA))
B2017_crues_p50 <- beales(q_crues_L.s, replace(load_crues_mg.s, sample(1:104,52), NA))

cat("flux_ref_2017_mg =", formatC(sum(with(avenelles_2017[-6,], q_L.s*doc_mg.L*period))), "\n")
cat("flux_ref_2017_mg.s =", formatC(sum(with(avenelles_2017[-6,], q_L.s*doc_mg.L))), "\n")
cat("beales etiage mg/s =", formatC(B2017_etiage$estimate), "\n")
cat("beales crues mg/s =", formatC(B2017_crues$estimate), "\n")
cat("beales mg = ", formatC(B2017_etiage$estimate * 60 * 60 * 24 * 182 + B2017_crues$estimate * 60 * 60 * 24 * 182), "\n") 
cat("beales mg.s = ", formatC(B2017_etiage$estimate + B2017_crues$estimate), "\n") 

cat("beales p50 etiage mg/s =", formatC(B2017_etiage_p50$estimate), "\n")
cat("beales p50 crues mg/s =", formatC(B2017_crues_p50$estimate), "\n")
cat("beales p50 mg = ", formatC(B2017_etiage_p50$estimate * 60 * 60 * 24 * 182 + B2017_crues_p50$estimate * 60 * 60 * 24 * 182), "\n") 
cat("beales p50 mg.s = ", formatC(B2017_etiage_p50$estimate + B2017_crues_p50$estimate), "\n") 

cat("WW biaised mg=", formatC(sum(avenelles_2017$q_L.s*avenelles_2017$doc_mg.L)/sum(q_2017_L.s)*mean(q_2017_L.s)*60*60*24*365), "\n")
cat("WW stratified mg=", formatC(sum(load_crues_mg.s)/sum(q_crues_L.s)*mean(q_crues_L.s)*60*60*24*182 + sum(load_etiage_mg.s)/sum(q_etiage_L.s)*mean(q_etiage_L.s)*60*60*24*182))


q_2017 <- avenelles_2017$q_L.s
doc_2017 <- avenelles_2017$doc_mg.L
load_2017 <- q_2017*doc_2017
period_2017 <- avenelles_2017$period

ave2017_p50 <- sample_n(avenelles_2017, 104) 
q_2017_p50 <- ave2017_p50$q_L.s
doc_2017_p50 <- ave2017_p50$doc_mg.L
load_2017_p50 <- q_2017_p50*doc_2017_p50
period_2017_p50 <- ave2017_p50$period

mean(load_2017)/mean(q_2017)
mean(load_2017_p50/mean(q_2017_p50))
mean(load_2017_p50/mean(q_2017_p50))*mean(q_2017)

sum(load_2017*period_2017)/sum(q_2017)
sum(load_2017_p50*period_2017_p50)/sum(q_2017_p50)
sum(load_2017_p50*period_2017_p50)/sum(q_2017_p50)*sum(q_2017)
sum(load_2017_p50*period_2017_p50)/sum(q_2017_p50)*sum(q_2017) / sum(load_2017*period_2017)



mean(load_2017)*60*60*24*365*1e-9 # donne trop de poids aux crues
sum(load_2017*period_2017)*1e-9 # ref


quantile(load_2017_p50)
quantile(load_2017)

hist(log(load_2017_p50))
hist(log(load_2017))

cor(load_2017,q_2017)
cor(load_2017_p50,q_2017_p50)

cov(load_2017,q_2017)
cov(load_2017_p50,q_2017_p50)

median(load_2017)/median(q_2017)
median(load_2017_p50/median(q_2017_p50))
median(load_2017_p50/median(q_2017_p50))*median(q_2017)

median(load_2017)

median(load_2017)*60*60*24*365*1e-9 # ne donne pas assez de poids aux crues
sum(load_2017*period_2017)*1e-9 # ref

# stratification entre crues et étiage
q_2017_etiage <- avenelles_2017 %>% subset(q_L.s < 134) %>% pull(q_L.s)
doc_2017_etiage <- avenelles_2017 %>% subset(q_L.s < 134) %>% pull(doc_mg.L)
load_2017_etiage <- q_2017_etiage*doc_2017_etiage 

avenelles_2017_etiage_p50 <- avenelles_2017 %>% subset(q_L.s < 134) %>% sample_frac(0.5)
q_2017_etiage_p50 <- avenelles_2017_etiage_p50$q_L.s
doc_2017_etiage_p50 <- avenelles_2017_etiage_p50$doc_mg.L
load_2017_etiage_p50 <- q_2017_etiage_p50*doc_2017_etiage_p50


mean(load_2017_etiage_p50)/mean(q_2017_etiage_p50)*mean(q_2017_etiage)
mean(load_2017_etiage)

q_2017_crues <- avenelles_2017 %>% subset(q_L.s > 134) %>% pull(q_L.s)
doc_2017_crues <- avenelles_2017 %>% subset(q_L.s > 134) %>% pull(doc_mg.L)
load_2017_crues <- q_2017_crues*doc_2017_crues 

avenelles_2017_crues_p50 <- avenelles_2017 %>% subset(q_L.s > 134) %>% sample_frac(0.5)
q_2017_crues_p50 <- avenelles_2017_crues_p50$q_L.s
doc_2017_crues_p50 <- avenelles_2017_crues_p50$doc_mg.L
load_2017_crues_p50 <- q_2017_crues_p50*doc_2017_crues_p50

mean(load_2017_crues_p50)/mean(q_2017_crues_p50)*mean(q_2017_crues)
mean(load_2017_crues)

mean(load_2017_etiage)*60*60*24*182
mean(load_2017_crues)*60*60*24*182
1/2*mean(load_2017_etiage)*60*60*24*182 + 1/2*mean(load_2017_crues)*60*60*24*182
sum(load_2017*period_2017)

(mean(load_2017_etiage)*60*60*24*182 + mean(load_2017_crues)*60*60*24*182)/sum(load_2017*period_2017)

# stratification entre crues et étiage, limite = quantile 0.75
q_2017_etiage <- avenelles_2017 %>% subset(q_L.s < 329) %>% pull(q_L.s)
doc_2017_etiage <- avenelles_2017 %>% subset(q_L.s < 329) %>% pull(doc_mg.L)
load_2017_etiage <- q_2017_etiage*doc_2017_etiage 

avenelles_2017_etiage_p50 <- avenelles_2017 %>% subset(q_L.s < 329) %>% sample_frac(0.5)
q_2017_etiage_p50 <- avenelles_2017_etiage_p50$q_L.s
doc_2017_etiage_p50 <- avenelles_2017_etiage_p50$doc_mg.L
load_2017_etiage_p50 <- q_2017_etiage_p50*doc_2017_etiage_p50


mean(load_2017_etiage_p50)/mean(q_2017_etiage_p50)*mean(q_2017_etiage)
mean(load_2017_etiage)

q_2017_crues <- avenelles_2017 %>% subset(q_L.s > 329) %>% pull(q_L.s)
doc_2017_crues <- avenelles_2017 %>% subset(q_L.s > 329) %>% pull(doc_mg.L)
load_2017_crues <- q_2017_crues*doc_2017_crues 

avenelles_2017_crues_p50 <- avenelles_2017 %>% subset(q_L.s > 329) %>% sample_frac(0.5)
q_2017_crues_p50 <- avenelles_2017_crues_p50$q_L.s
doc_2017_crues_p50 <- avenelles_2017_crues_p50$doc_mg.L
load_2017_crues_p50 <- q_2017_crues_p50*doc_2017_crues_p50

mean(load_2017_crues_p50)/mean(q_2017_crues_p50)*mean(q_2017_crues)
mean(load_2017_crues)

mean(load_2017_etiage)*60*60*24*365*(3/4)
mean(load_2017_crues)*60*60*24*365*(1/4)
(3/4)*mean(load_2017_etiage)*60*60*24*365 + (1/4)*mean(load_2017_crues)*60*60*24*365
sum(load_2017*period_2017)


beales_load_2017_etiage_p50 <- replace(load_2017_etiage, sample(1:length(load_2017_etiage), length(load_2017_etiage)*0.5),NA)
beales_load_2017_crues_p50 <- replace(load_2017_crues, sample(1:length(load_2017_crues), length(load_2017_crues)*0.5),NA)
beales(q_2017_etiage, beales_load_2017_etiage_p50)$estimate * (3/4)*60*60*24*365 + beales(q_2017_crues,beales_load_2017_crues_p50)$estimate * (1/4)*60*60*24*365
sum(load_2017*period_2017)



```

```{r comparaison-ratios}

q_2017 <- avenelles_2017$q_L.s
doc_2017 <- avenelles_2017$doc_mg.L
load_2017 <- q_2017*doc_2017
period_2017 <- avenelles_2017$period

ave2017_p50 <- sample_n(avenelles_2017, 104) 
q_2017_p50 <- ave2017_p50$q_L.s
doc_2017_p50 <- ave2017_p50$doc_mg.L
load_2017_p50 <- q_2017_p50*doc_2017_p50
period_2017_p50 <- ave2017_p50$period

sum(load_2017*period_2017)/sum(q_2017)
sum(load_2017_p50*period_2017_p50)/sum(q_2017_p50)
sum(load_2017_p50*period_2017_p50)/sum(q_2017_p50)*sum(q_2017)
sum(load_2017_p50*period_2017_p50)/sum(q_2017_p50)*sum(q_2017) / sum(load_2017*period_2017)


annual_values <- avenelles %>% filter(year %in% complete_years) %>% group_by(year) %>% summarise(load = sum(q_L.s*doc_mg.L*period, na.rm = T), q = sum(q_L.s, na.rm = T), l.q = load/q) 
p50_values <- avenelles %>% filter(year %in% complete_years) %>% sample_frac(0.5) %>% group_by(year) %>% summarise(loadp50 = sum(q_L.s*doc_mg.L*period, na.rm = T), qp50 = sum(q_L.s, na.rm = T), l.qp50 = loadp50/qp50) 

ratios <- merge(annual_values, p50_values, by = "year") 
with(ratios, l.q/l.qp50)

with(ratios, l.qp50*q/load) 

with(ratios, (l.qp50*q-load)/load * 100) # bias



annual_values <- avenelles %>% filter(year %in% complete_years) %>% group_by(year) %>% summarise(load = sum(q_L.s*doc_mg.L*period, na.rm = T), q = sum(q_L.s, na.rm = T), l.q = load/q) 
p80_values <- avenelles %>% filter(year %in% complete_years) %>% sample_frac(80*1e-2) %>% group_by(year) %>% summarise(loadp80 = sum(q_L.s*doc_mg.L*period, na.rm = T), qp80 = sum(q_L.s, na.rm = T), l.qp80 = loadp80/qp80) 

ratios <- merge(annual_values, p80_values, by = "year") 
with(ratios, l.q/l.qp80)

with(ratios, l.qp80*q/load) 

with(ratios, (l.qp80*q-load)/load * 100) # bias

# QUEL EST LE PB AVEC 2019?
```



















