---
title: "Avenelles - méthodes"
author: "CamilMC"
date: "2026-06-17"
output:
  html_document:
    toc: true
    toc_float: true
    number_sections: true
    code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = F, warning = F, error = F, fig.align = "center", collapse = T,
                      cache = T)
```

```{r libraries}
lapply(c("dplyr"), library, character.only = T)
lapply(c("ggplot2","ggpubr"), library, character.only = T)
lapply(c("lubridate"), library, character.only = T)
lapply(c("knitr","kableExtra"), library, character.only = T)
library(here)

```
# Data

Données récupérées sur BDOH: https://bdoh.inrae.fr/ORACLE/

Contact: Sophie Guillon

Description du site (https://www.ozcar-ri.org/fr/observatoire-oracle/): L’observatoire de recherche ORACLE est l’un des plus anciens observatoires français de la zone critique. Il est situé dans le bassin parisien (70 km à l’Est de Paris) et se compose de trois bassins versants : le Grand Morin, le Petit Morin (deux affluents de la Marne couvrant une surface totale de 1 800 km²) et de l’Orgeval (104 km²), affluent du Grand Morin, plus petit mais qui concentre l’essentiel de l’instrumentation. Le relief est constitué du plateau de la Brie (130m, NGF) incisé par des vallées (80m, NGF). ORACLE est soumis à un climat océanique tempéré (température moyenne annuelle de 11,3°C et précipitation annuelles de 740 mm). La géologie est typique d’un bassin sédimentaire avec une alternance de couches argileuses et calcaires (dont le calcaire de Brie contenant la nappe du même nom), couvertes d’un vernis limoneux où se développent des sols épais. L’occupation du sol est essentiellement agricole, emblématique de la grande culture céréalière du Bassin de Paris. Les sols sont hydromorphes, majoritairement drainés par des réseaux de tuyaux enterrés.

## Get data

```{r bv-area}
bv <- 45
```


```{r load-data-from-excel, message = F}

avenelles <- readxl::read_xlsx(path = "Data_Avenelles_DOC_DIC_Debit.xlsx", sheet = "Data_Avenelles_DOC_DIC_Debit", col_types = c("date","numeric", "text","numeric","text","numeric","text","text","numeric")) %>%  mutate(Site = NULL, bv_km2 = NULL) %>% unique()

avenelles$year <- year(avenelles$DateHeure)
avenelles$week <- week(avenelles$DateHeure)
avenelles$month <- month(avenelles$DateHeure)

avenelles$commondate <- as.Date(paste0("2000-", format(avenelles$DateHeure,"%j")), "%Y-%j")
avenelles$Date <- format(avenelles$DateHeure, "%Y-%m-%d") %>% as.Date()

avenelles$period <- with(avenelles, as.numeric(-(DateHeure - lead(DateHeure)))) # period in second between 2 lines. This leads to some large periods being calculated when data is missing / not sampled during a long interval. 
avenelles$periodj <- round(avenelles$period / 60 / 60 / 24, 0)
avenelles[which(avenelles$periodj > 4),"period"] <- 24*60*60 # the median time of sampling is every second day. This line replaces periods that are artificially longer than 4 days
avenelles[which(avenelles$periodj > 4),"periodj"] <- 1

avenelles <- unique(avenelles)
  
strange_periods_dates <- avenelles %>% subset(periodj > 4) %>% pull(Date) 

```



## Visualisation

```{r plot-by-year-doc, fig.dim = c(10,15)}


title <- expression(atop("Series of DOC and Q by year"))
plots <- ggarrange(
ggplot(avenelles, aes(x = commondate))+
  geom_point(aes(y = q_L.s, col = "Débit, L/s"), alpha = 0.5)+
  scale_x_date(labels = function(x) format(x, "%d-%b"), date_minor_breaks = "1 month", name = "")+
  scale_color_manual(values = c("lightblue"), name = "")+
  facet_grid(rows = vars(year))+
  labs(y = "Débit, L/s", col = "")+
  theme_bw(base_size = 15)+
  theme(legend.position = "none"),

ggplot(avenelles, aes(x = commondate))+
  geom_point(aes(y = doc_mg.L, col = "DOC, mg.L"), alpha = 0.5)+
  scale_x_date(labels = function(x) format(x, "%d-%b"), date_minor_breaks = "1 month", name = "")+
  scale_color_manual(values = c("palegreen4"), name = "")+
  facet_grid(rows = vars(year))+
  labs(y = "DOC, mg/L", col = "")+
  theme_bw(base_size = 15)+
  theme(legend.position = "none")
)

annotate_figure(plots, top = text_grob(title))



```

DOC observation for year 2014 are FALSE: there has been a mix between DIC and DOC data (confirmed by Sophie Guillon). 2014 is excluded from the analysis. Data for 2015 seem to be partially wrong as well. 

```{r avenelles-complete-years, fig.dim = c(10,15)}
complete_years <- c(2010,2011,2012,2013,2016,2017,2018,2019,2021)
avenelles_complete <- avenelles %>% subset(year %in% complete_years)
```

Years to use for test of methods: `r cat(complete_years)`

```{r plot-complete-years, fig.dim = c(10,15)}
title <- expression(atop("Series of DOC and Q by year"))
plots <- ggarrange(
ggplot(subset(avenelles_complete, year %in% complete_years), aes(x = commondate))+
  geom_point(aes(y = q_L.s, col = "Débit, L/s"), alpha = 0.5)+
  scale_x_date(labels = function(x) format(x, "%d-%b"), date_minor_breaks = "1 month", name = "")+
  scale_color_manual(values = c("lightblue"), name = "")+
  facet_grid(rows = vars(year))+
  labs(y = "Débit, L/s", col = "")+
  theme_bw(base_size = 15)+
  theme(legend.position = "none"),

ggplot(subset(avenelles, year %in% complete_years), aes(x = commondate))+
  geom_point(aes(y = doc_mg.L, col = "DOC, mg.L"), alpha = 0.5)+
  scale_x_date(labels = function(x) format(x, "%d-%b"), date_minor_breaks = "1 month", name = "")+
  scale_color_manual(values = c("palegreen4"), name = "")+
  facet_grid(rows = vars(year))+
  labs(y = "DOC, mg/L", col = "")+
  theme_bw(base_size = 15)+
  theme(legend.position = "none")
)

annotate_figure(plots, top = text_grob(title))

```

## Characteristics

```{r summary-data}
summary_avenelles <- merge(
avenelles %>% subset(!is.na(doc_mg.L)) %>% group_by(year) %>% summarise("Number of DOC observations" = n(), "DOC range, mg/L" = paste(quantile(doc_mg.L, probs = c(0,0.5,1), na.rm = T), collapse = " / ")),
avenelles %>% subset(!is.na(q_L.s)) %>% group_by(year) %>% summarise("Number of Q observations" = n(), "Q range, L/s" = paste(quantile(q_L.s, probs = c(0,0.5,1), na.rm = T), collapse = " / ")), by = "year", all = T) %>% 
  merge(avenelles %>% group_by(year) %>% summarise("Number of days sampled" = length(unique(Date))), by = "year", all = T) %>%
  merge(avenelles %>% group_by(year) %>% summarise("Correlation DOC/log(Q)" = round(cor(doc_mg.L, log(q_L.s), use = "pairwise.complete.obs"),2)), by = "year", all = T) %>%
  rbind(c("All years", 
          dim(subset(avenelles, !is.na(doc_mg.L)))[1], 
          paste(quantile(avenelles$doc_mg.L, probs = c(0,0.5,1), na.rm = T), collapse = " / "), 
          dim(subset(avenelles, !is.na(q_L.s)))[1], 
          paste(quantile(avenelles$q_L.s, probs = c(0,0.5,1), na.rm = T), collapse = " / "), 
          length(unique(avenelles$Date)),
          round(cor(avenelles$doc_mg.L, log(avenelles$q_L.s), use = "pairwise.complete.obs" ),2)
          )) %>%
    rbind(c("Complete years", 
          dim(subset(avenelles_complete, !is.na(doc_mg.L)))[1], 
          paste(quantile(avenelles_complete$doc_mg.L, probs = c(0,0.5,1), na.rm = T), collapse = " / "), 
          dim(subset(avenelles_complete, !is.na(q_L.s)))[1], 
          paste(quantile(avenelles_complete$q_L.s, probs = c(0,0.5,1), na.rm = T), collapse = " / "), 
          length(unique(avenelles_complete$Date)),
          round(cor(avenelles_complete$doc_mg.L, log(avenelles_complete$q_L.s), use = "pairwise.complete.obs" ),2)
          )
          )

knitr::kable(summary_avenelles, caption = "Summary table of Avenelles data") %>% kableExtra::kable_styling()

```



```{r histograms}
ggarrange(
  ggplot(avenelles_complete)+geom_histogram(aes(q_L.s),fill = "lightblue")+labs(x= "Débit, L/s", y = "")+theme_bw(),
  ggplot(avenelles_complete)+geom_histogram(aes(doc_mg.L), fill = "palegreen4")+labs(x= "DOC, mg/L", y = "")+theme_bw(),
  ggplot(avenelles_complete)+geom_histogram(aes(log10(q_L.s)),fill = "lightblue")+labs(x= "Débit (log10), L/s", y = "")+theme_bw(),
  ggplot(avenelles_complete)+geom_histogram(aes(log(doc_mg.L)), fill = "palegreen4")+labs(x= "DOC (log10), mg/L", y = "")+theme_bw()
)
```




# Test of methods for estimating fluxes when data is missing

## Minimize bias on average flow, data randomly missing

```{r ref-load-random-load}
set.seed(1806)

ref_avenelles <- avenelles_complete%>% group_by(year) %>% summarise(annual_load = sum(doc_mg.L*q_L.s*period, na.rm = T), sum_q = sum(q_L.s, na.rm = T), mean_q = mean(q_L.s, na.rm = T), slq = cov(doc_mg.L*q_L.s*period, q_L.s, use = "pairwise.complete.obs"), n_obs = n()) 

# Fonction d'échantillonnage par bloc
sample_block <- function(df, frac) {
  n <- nrow(df)
  block_size <- round(n * frac)
  start <- sample(1:n, 1)
  indices <- ((start - 1 + 0:(block_size - 1)) %% n) + 1
  return(df[indices, ])
}

# Génération de toutes les listes en une seule fois
fracs <- seq(0.1, 1, by = 0.1)

list_random <- lapply(fracs, function(frac) {
  lapply(1:1000, function(i) {
    avenelles_complete %>%
      group_by(year) %>%
      group_modify(~ sample_block(.x, frac)) %>%
      data.frame()
  })
}) %>% setNames(paste0("p", fracs * 100))

```

### Rating curve

```{r doc_q_rating-curve}
ggplot(avenelles_complete)+
  geom_point(aes(x=log(q_L.s), y = doc_mg.L, col = as.factor(year)))+
  labs(x="log(Q)", y = "DOC, mg/L", col = "Year", title = cat("Pearson's R = ", round(with(avenelles_complete, cor(doc_mg.L, log(q_L.s), use = "pairwise.complete.obs")),2), sep = " "))+
  scale_color_viridis_d()+
  theme_bw()

doc_model <- lm(doc_mg.L~log(q_L.s), data = avenelles_complete)
summary(doc_model)

doc_model2 <- lm(log(doc_mg.L)~log(q_L.s), data = subset(avenelles_complete, doc_mg.L > 0))
summary(doc_model2)

avenelles_complete$doc_predicted <- predict(doc_model, newdata = avenelles_complete)

ggplot(avenelles_complete)+
  geom_point(aes(x=doc_mg.L, y = doc_predicted, col = as.factor(year)))+
    labs(x="DOC observed", y = "DOC predicted", col = "Year", title = "DOC predicted vs DOC observed (mg/L)")+
  scale_color_viridis_d()+
  theme_bw()
```


```{r plot-doc-predicted, fig.dim = c(10,20)}
ggplot(avenelles_complete, aes(x = commondate))+
  geom_point(aes(y = doc_mg.L, col = "DOC, mg.L"), alpha = 0.5)+
  geom_point(aes(y = doc_predicted, col = "DOC predicted, mg.L"), alpha = 0.5)+  
  scale_x_date(labels = function(x) format(x, "%d-%b"), date_minor_breaks = "1 month", name = "")+
  scale_color_manual(values = c("palegreen4","lightblue"), name = "")+
  facet_grid(rows = vars(year))+
  labs(y = "DOC, mg/L", col = "")+
  theme_bw(base_size = 15)+
  theme(legend.position = "bottom")
```



```{r bias-rating-curve}
# un modèle par dataframe dans chaque sous-liste
doc_model <- lapply(list_random, function(i) {
  lapply(i, lm, formula = doc_mg.L~q_L.s)})


# prédiction par sous-dataframe
list_predicted <- lapply(seq_along(list_random), 
                         FUN = function(i) {lapply(seq_along(list_random[[i]]), 
                                                    FUN = function(j){df <- list_random[[i]][[j]]
                                                                      df$doc_predicted <- predict(doc_model[[i]][[j]], newdata = df)
                                                                      return(df)
                                                                      }
                                                    )
                                            }
                         )
  
  
# liste de dataframes avec le résultat des calculs
list_load <- lapply(list_predicted, 
                    function(i) {lapply(i, 
                                        function(df) {df %>% group_by(year) %>% summarise(load = sum(doc_predicted*q_L.s*period, na.rm = T), sum_q = sum(q_L.s, na.rm = T), mean_q = mean(q_L.s, na.rm = T))
                                                      }
                                        )
                                }
                    )


# Calcul du flux par année
load_rating <- lapply(list_load, function(i){
  do.call(what = cbind, lapply(i, '[[',"load")) %>% rowMeans #Retourne un vecteur avec une valeur de flux par année
})
load_rating_df <- as.data.frame(load_rating) %>% setNames(names(list_random)) %>% cbind(year = complete_years) %>% tidyr::pivot_longer(cols = -year, names_to = "percent", values_to = "load")


# Biais absolu par année
bias_rating <- lapply(list_load, 
                      function(i) {lapply(i,function(j){
                        abs((j$load-ref_avenelles$annual_load)/ref_avenelles$annual_load*100)})
                      })
                        
# Biais moyen absolu
mean_bias_rating <- lapply(bias_rating, function(i){
                            as.data.frame(do.call(cbind,i)) %>% rowMeans #Calcule le biais moyen absolu par année                          
})
mean_bias_rating_df <- as.data.frame(mean_bias_rating) %>% setNames(names(list_random)) %>% cbind(year = complete_years) %>% tidyr::pivot_longer(cols = -year, names_to = "percent", values_to = "bias")

results_rating_df <- merge(load_rating_df, mean_bias_rating_df, by = c("percent","year"))


ggplot(results_rating_df,aes(x=year))+geom_line(data = ref_avenelles, aes(y=annual_load), size = 1)+
  geom_line(aes(y = load, group = percent, col = percent))+
  scale_color_viridis_d(direction = -1)+
  labs(x= "Year", y = "Annual load, tons", col = "% of randomly sampled data",title = "Average DOC load by year depending on percentage of data included", subtitle = "Reference annual load in black")+
  scale_x_continuous(breaks = complete_years, minor_breaks = NULL)+
  theme_minimal()+
  theme(legend.position = "bottom", axis.text.x = element_text(angle = 45))


ggplot()+
  geom_line(data = ref_avenelles, aes(x = year, y=mean_q/5), size = 1)+
  geom_line(data = results_rating_df, aes(x=year, y=bias, group = percent, col = percent))+
  scale_color_viridis_d(direction = -1)+
  labs(x= "Year", y = "Average absolute bias,%", col = "% of randomly \n sampled data", title = "Average absolute bias by year depending on percentage of data included", subtitle = "Average annual discharge in black")+
  scale_x_continuous(breaks = complete_years, minor_breaks = NULL)+
  scale_y_continuous(sec.axis = sec_axis(~.*5, name = "Average annual discharge, L/s"))+
  theme_minimal()+
  theme(legend.position = "bottom", axis.text.x = element_text(angle = 45))
```



### Verhoff ratio 1980


Known to be biaised. Compute yearly flux by:

* Randomly sampling 10 to 90% of each year, 1000 times
* Calculate annual load with ratio method for each year
* Compare with reference load and estimate average bias

```{r test-verhoff}
list_verhoff <- function(list_df){
  
list_load <- lapply(list_df,function(i) {i %>% group_by(year) %>% summarise(load = sum(doc_mg.L*q_L.s, na.rm = T), sum_q = sum(q_L.s, na.rm = T), mean_q = mean(q_L.s, na.rm = T))}) # génère une liste de dataframes
load_verhoff <- lapply(list_load, function(i) {(i$load/i$sum_q*ref_avenelles$mean_q[match(i$year, ref_avenelles$year)]*60*60*24*365)}) %>% do.call(what = cbind) %>% rowMeans #Retourne un vecteur avec une valeur de flux par année
bias_verhoff <- lapply(list_load, function(i) {abs(((i$load/i$sum_q*ref_avenelles$mean_q[match(i$year, ref_avenelles$year)]*60*60*24*365)-ref_avenelles$annual_load[match(i$year, ref_avenelles$year)])/ref_avenelles$annual_load[match(i$year, ref_avenelles$year)]*100)}) #Retourne une liste de vecteurs avec les 1000 biais par année, en valeur absolue. 
mean_bias_verhoff <- as.data.frame(do.call(cbind,bias_verhoff)) %>% rowMeans #Calcule le biais moyen absolu par année    
  
return(list(load_verhoff = load_verhoff,   mean_bias_verhoff = mean_bias_verhoff))
}  
  
  
results_verhoff <- lapply(list_random, list_verhoff)
results_verhoff_listdf <- lapply(results_verhoff, as.data.frame) %>% lapply(cbind, year = complete_years)
results_verhoff_df <- bind_rows(results_verhoff_listdf, .id = "percent")


ggplot(results_verhoff_df,aes(x=year))+geom_line(data = ref_avenelles, aes(y=annual_load), size = 1)+
  geom_line(aes(y = load_verhoff, group = percent, col = percent))+
  scale_color_viridis_d(direction = -1)+
  labs(x= "Year", y = "Annual load, tons", col = "% of randomly sampled data",title = "Average DOC load by year depending on percentage of data included", subtitle = "Reference annual load in black")+
  scale_x_continuous(breaks = complete_years, minor_breaks = NULL)+
  theme_minimal()+
  theme(legend.position = "bottom", axis.text.x = element_text(angle = 45))

ggplot()+
  geom_line(data = ref_avenelles, aes(x = year, y=mean_q/4), size = 1)+
  geom_line(data = results_verhoff_df, aes(x=year, y=mean_bias_verhoff, group = percent, col = percent))+
  scale_color_viridis_d(direction = -1)+
  labs(x= "Year", y = "Average absolute bias,%", col = "% of randomly \n sampled data", title = "Average absolute bias by year depending on percentage of data included", subtitle = "Average annual discharge in black")+
  scale_x_continuous(breaks = complete_years, minor_breaks = NULL)+
  scale_y_continuous(sec.axis = sec_axis(~.*4, name = "Average annual discharge, L/s"))+
  theme_minimal()+
  theme(legend.position = "bottom", axis.text.x = element_text(angle = 45))



```

### Beales ratio

```{r test-beales}
list_beales <- function(list_df){

  
    
list_load <- lapply(list_df,function(i) {i %>% group_by(year) %>% summarise(load = sum(doc_mg.L*q_L.s, na.rm = T), sum_q = sum(q_L.s, na.rm = T), mean_q = mean(q_L.s, na.rm = T), sqq = var(q_L.s, na.rm = T))}) # génère une liste de dataframes
load_beales <- lapply(list_load, function(i) {
  i$load/i$sum_q*ref_avenelles$mean_q[match(i$year, ref_avenelles$year)]* 60*60*24*365 * 
  ((1+(1/length(i$load-1/ref_avenelles$n_obs[match(i$year, ref_avenelles$year)])*ref_avenelles$slq[match(i$year, ref_avenelles$year)]/(i$load*ref_avenelles$mean_q[match(i$year, ref_avenelles$year)])))/
    1+ 1/length(i$load-1/ref_avenelles$n_obs[match(i$year, ref_avenelles$year)])*i$sqq/sqrt(ref_avenelles$mean_q[match(i$year, ref_avenelles$year)])
     )}) %>% 
  do.call(what = cbind) %>% rowMeans(na.rm = T) #Retourne un vecteur avec une valeur de flux par année
bias_beales <- lapply(list_load, function(i) {abs((load_beales-ref_avenelles$annual_load[match(i$year, ref_avenelles$year)])/ref_avenelles$annual_load[match(i$year, ref_avenelles$year)]*100)}) #Retourne une liste de vecteurs avec les 1000 biais par année, en valeur absolue. 
mean_bias_beales <- as.data.frame(do.call(cbind,bias_beales)) %>% rowMeans #Calcule le biais moyen absolu par année    
  
return(list(load_beales = load_beales,   mean_bias_beales = mean_bias_beales))
}  
  
  
results_beales <- lapply(list_random, list_beales)
results_beales_listdf <- lapply(results_beales, as.data.frame) %>% lapply(cbind, year = complete_years)
results_beales_df <- bind_rows(results_beales_listdf, .id = "percent")


ggplot(results_beales_df,aes(x=year))+geom_line(data = ref_avenelles, aes(y=annual_load), size = 1)+
  geom_line(aes(y = load_beales, group = percent, col = percent))+
  scale_color_viridis_d(direction = -1)+
  labs(x= "Year", y = "Annual load, tons", col = "% of randomly sampled data",title = "Average DOC load by year depending on percentage of data included", subtitle = "Reference annual load in black")+
  scale_x_continuous(breaks = complete_years, minor_breaks = NULL)+
  theme_minimal()+
  theme(legend.position = "bottom", axis.text.x = element_text(angle = 45))

ggplot()+
  geom_line(data = ref_avenelles, aes(x = year, y=mean_q/3), size = 1)+
  geom_line(data = results_beales_df, aes(x=year, y=mean_bias_beales, group = percent, col = percent))+
  scale_color_viridis_d(direction = -1)+
  labs(x= "Year", y = "Average absolute bias,%", col = "% of randomly \n sampled data", title = "Average absolute bias by year depending on percentage of data included", subtitle = "Average annual discharge in black")+
  scale_x_continuous(breaks = complete_years, minor_breaks = NULL)+
  scale_y_continuous(sec.axis = sec_axis(~.*3, name = "Average annual discharge, L/s"))+
  theme_minimal()+
  theme(legend.position = "bottom", axis.text.x = element_text(angle = 45))

```


### Camille's ratio

Based on the observation that sum(Li)/sum(Qi) = sum(La)/sum(Qa)

Bias = absolute bias

```{r test-camille}
list_camille <- function(list_df){
  
list_load <- lapply(list_df,function(i) {i %>% group_by(year) %>% summarise(load = sum(doc_mg.L*q_L.s*period, na.rm = T), sum_q = sum(q_L.s, na.rm = T), mean_q = mean(q_L.s, na.rm = T))}) # génère une liste de dataframes
load_camille <- lapply(list_load, function(i) {i$load/i$sum_q*ref_avenelles$sum_q[match(i$year, ref_avenelles$year)]}) %>% do.call(what = cbind) %>% rowMeans #Retourne un vecteur avec une valeur de flux par année
bias_camille <- lapply(list_load, function(i) {abs(((i$load/i$sum_q*ref_avenelles$sum_q[match(i$year, ref_avenelles$year[match(i$year, ref_avenelles$year)])])-ref_avenelles$annual_load[match(i$year, ref_avenelles$year)])/ref_avenelles$annual_load[match(i$year, ref_avenelles$year)]*100)}) #Retourne une liste de vecteurs avec les 1000 biais par année, en valeur absolue. 
mean_bias_camille <- as.data.frame(do.call(cbind,bias_camille)) %>% rowMeans #Calcule le biais moyen absolu par année    
  
return(list(load_camille = load_camille,   mean_bias_camille = mean_bias_camille))
}  
  
  
results_camille <- lapply(list_random, list_camille)
results_camille_listdf <- lapply(results_camille, as.data.frame) %>% lapply(cbind, year = complete_years)
results_camille_df <- bind_rows(results_camille_listdf, .id = "percent")


ggplot(results_camille_df,aes(x=year))+geom_line(data = ref_avenelles, aes(y=annual_load), size = 1)+
  geom_line(aes(y = load_camille, group = percent, col = percent))+
  scale_color_viridis_d(direction = -1)+
  labs(x= "Year", y = "Annual load, tons", col = "% of randomly sampled data",title = "Average DOC load by year depending on percentage of data included", subtitle = "Reference annual load in black")+
  scale_x_continuous(breaks = complete_years, minor_breaks = NULL)+
  theme_minimal()+
  theme(legend.position = "bottom", axis.text.x = element_text(angle = 45))


ggplot()+
  geom_line(data = ref_avenelles, aes(x = year, y=mean_q/6), size = 1)+
  geom_line(data = results_camille_df, aes(x=year, y=mean_bias_camille, group = percent, col = percent))+
  scale_color_viridis_d(direction = -1)+
  labs(x= "Year", y = "Average absolute bias,%", col = "% of randomly \n sampled data", title = "Average absolute bias by year depending on percentage of data included", subtitle = "Average annual discharge in black")+
  scale_x_continuous(breaks = complete_years, minor_breaks = NULL)+
  scale_y_continuous(sec.axis = sec_axis(~.*6, name = "Average annual discharge, L/s"))+
  theme_minimal()+
  theme(legend.position = "bottom", axis.text.x = element_text(angle = 45))
```


## Minimize bias on average flow, data randomly missing, data missing by block

```{r ref-load-block}
set.seed(2606)

ref_avenelles <- avenelles_complete%>% group_by(year) %>% summarise(annual_load = sum(doc_mg.L*q_L.s*period, na.rm = T), sum_q = sum(q_L.s, na.rm = T), mean_q = mean(q_L.s, na.rm = T), slq = cov(doc_mg.L*q_L.s*period, q_L.s, use = "pairwise.complete.obs"), n_obs = n()) 

sample_block <- function(df, frac) {
  n <- nrow(df)
  block_size <- round(n * frac)
  
  # Tirage aléatoire du point de départ (avec retour au début si le bloc dépasse la fin)
  start <- sample(1:n, 1)
  indices <- ((start - 1 + 0:(block_size - 1)) %% n) + 1
  
  return(df[indices, ])
}

# Génération des 1000 tirages par bloc pour chaque pourcentage
fracs <- c(0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 0.9, 1.0)

list_random <- lapply(fracs, function(frac) {
  lapply(1:1000, function(i) {
    avenelles_complete %>%
      group_by(year) %>%
      group_modify(~ sample_block(.x, frac)) %>%
      data.frame()
  })
}) %>% setNames(paste0("p", fracs * 100))


```

### Rating curve

```{r bias-rating-curve-block}
# un modèle par dataframe dans chaque sous-liste
doc_model <- lapply(list_random, function(i) {
  lapply(i, lm, formula = doc_mg.L~q_L.s)})


# prédiction par sous-dataframe
list_predicted <- lapply(seq_along(list_random), 
                         FUN = function(i) {lapply(seq_along(list_random[[i]]), 
                                                    FUN = function(j){df <- list_random[[i]][[j]]
                                                                      df$doc_predicted <- predict(doc_model[[i]][[j]], newdata = df)
                                                                      return(df)
                                                                      }
                                                    )
                                            }
                         )
  
  
# liste de dataframes avec le résultat des calculs
list_load <- lapply(list_predicted, 
                    function(i) {lapply(i, 
                                        function(df) {df %>% group_by(year) %>% summarise(load = sum(doc_predicted*q_L.s*period, na.rm = T), sum_q = sum(q_L.s, na.rm = T), mean_q = mean(q_L.s, na.rm = T))
                                                      }
                                        )
                                }
                    )


# Calcul du flux par année
load_rating <- lapply(list_load, function(i){
  do.call(what = cbind, lapply(i, '[[',"load")) %>% rowMeans #Retourne un vecteur avec une valeur de flux par année
})
load_rating_df <- as.data.frame(load_rating) %>% setNames(names(list_random)) %>% cbind(year = complete_years) %>% tidyr::pivot_longer(cols = -year, names_to = "percent", values_to = "load")


# Biais absolu par année
bias_rating <- lapply(list_load, 
                      function(i) {lapply(i,function(j){
                        abs((j$load-ref_avenelles$annual_load)/ref_avenelles$annual_load*100)})
                      })
                        
# Biais moyen absolu
mean_bias_rating <- lapply(bias_rating, function(i){
                            as.data.frame(do.call(cbind,i)) %>% rowMeans #Calcule le biais moyen absolu par année                          
})
mean_bias_rating_df <- as.data.frame(mean_bias_rating) %>% setNames(names(list_random)) %>% cbind(year = complete_years) %>% tidyr::pivot_longer(cols = -year, names_to = "percent", values_to = "bias")

results_rating_df <- merge(load_rating_df, mean_bias_rating_df, by = c("percent","year"))


ggplot(results_rating_df,aes(x=year))+geom_line(data = ref_avenelles, aes(y=annual_load), size = 1)+
  geom_line(aes(y = load, group = percent, col = percent))+
  scale_color_viridis_d(direction = -1)+
  labs(x= "Year", y = "Annual load, tons", col = "% of randomly sampled data",title = "Average DOC load by year depending on percentage of data included", subtitle = "Reference annual load in black")+
  scale_x_continuous(breaks = complete_years, minor_breaks = NULL)+
  theme_minimal()+
  theme(legend.position = "bottom", axis.text.x = element_text(angle = 45))


ggplot()+
  geom_line(data = ref_avenelles, aes(x = year, y=mean_q/5), size = 1)+
  geom_line(data = results_rating_df, aes(x=year, y=bias, group = percent, col = percent))+
  scale_color_viridis_d(direction = -1)+
  labs(x= "Year", y = "Average absolute bias,%", col = "% of randomly \n sampled data", title = "Average absolute bias by year depending on percentage of data included", subtitle = "Average annual discharge in black")+
  scale_x_continuous(breaks = complete_years, minor_breaks = NULL)+
  scale_y_continuous(sec.axis = sec_axis(~.*5, name = "Average annual discharge, L/s"))+
  theme_minimal()+
  theme(legend.position = "bottom", axis.text.x = element_text(angle = 45))
```



### Verhoff ratio 1980


Known to be biaised. Compute yearly flux by:

* Randomly sampling 10 to 90% of each year, 1000 times
* Calculate annual load with ratio method for each year
* Compare with reference load and estimate average bias

```{r test-verhoff-block}
list_verhoff <- function(list_df){
  
list_load <- lapply(list_df,function(i) {i %>% group_by(year) %>% summarise(load = sum(doc_mg.L*q_L.s, na.rm = T), sum_q = sum(q_L.s, na.rm = T), mean_q = mean(q_L.s, na.rm = T))}) # génère une liste de dataframes
load_verhoff <- lapply(list_load, function(i) {(i$load/i$sum_q*ref_avenelles$mean_q[match(i$year, ref_avenelles$year)]*60*60*24*365)}) %>% do.call(what = cbind) %>% rowMeans #Retourne un vecteur avec une valeur de flux par année
bias_verhoff <- lapply(list_load, function(i) {abs(((i$load/i$sum_q*ref_avenelles$mean_q[match(i$year, ref_avenelles$year)]*60*60*24*365)-ref_avenelles$annual_load[match(i$year, ref_avenelles$year)])/ref_avenelles$annual_load[match(i$year, ref_avenelles$year)]*100)}) #Retourne une liste de vecteurs avec les 1000 biais par année, en valeur absolue. 
mean_bias_verhoff <- as.data.frame(do.call(cbind,bias_verhoff)) %>% rowMeans #Calcule le biais moyen absolu par année    
  
return(list(load_verhoff = load_verhoff,   mean_bias_verhoff = mean_bias_verhoff))
}  
  
  
results_verhoff <- lapply(list_random, list_verhoff)
results_verhoff_listdf <- lapply(results_verhoff, as.data.frame) %>% lapply(cbind, year = complete_years)
results_verhoff_df <- bind_rows(results_verhoff_listdf, .id = "percent")


ggplot(results_verhoff_df,aes(x=year))+geom_line(data = ref_avenelles, aes(y=annual_load), size = 1)+
  geom_line(aes(y = load_verhoff, group = percent, col = percent))+
  scale_color_viridis_d(direction = -1)+
  labs(x= "Year", y = "Annual load, tons", col = "% of randomly sampled data",title = "Average DOC load by year depending on percentage of data included", subtitle = "Reference annual load in black")+
  scale_x_continuous(breaks = complete_years, minor_breaks = NULL)+
  theme_minimal()+
  theme(legend.position = "bottom", axis.text.x = element_text(angle = 45))

ggplot()+
  geom_line(data = ref_avenelles, aes(x = year, y=mean_q/4), size = 1)+
  geom_line(data = results_verhoff_df, aes(x=year, y=mean_bias_verhoff, group = percent, col = percent))+
  scale_color_viridis_d(direction = -1)+
  labs(x= "Year", y = "Average absolute bias,%", col = "% of randomly \n sampled data", title = "Average absolute bias by year depending on percentage of data included", subtitle = "Average annual discharge in black")+
  scale_x_continuous(breaks = complete_years, minor_breaks = NULL)+
  scale_y_continuous(sec.axis = sec_axis(~.*4, name = "Average annual discharge, L/s"))+
  theme_minimal()+
  theme(legend.position = "bottom", axis.text.x = element_text(angle = 45))


```

### Beales ratio

```{r test-beales-block}
list_beales <- function(list_df){

  
    
list_load <- lapply(list_df,function(i) {i %>% group_by(year) %>% summarise(load = sum(doc_mg.L*q_L.s, na.rm = T), sum_q = sum(q_L.s, na.rm = T), mean_q = mean(q_L.s, na.rm = T), sqq = var(q_L.s, na.rm = T))}) # génère une liste de dataframes
load_beales <- lapply(list_load, function(i) {
  i$load/i$sum_q*ref_avenelles$mean_q[match(i$year, ref_avenelles$year)]* 60*60*24*365 * 
  ((1+(1/length(i$load-1/ref_avenelles$n_obs[match(i$year, ref_avenelles$year)])*ref_avenelles$slq[match(i$year, ref_avenelles$year)]/(i$load*ref_avenelles$mean_q[match(i$year, ref_avenelles$year)])))/
    1+ 1/length(i$load-1/ref_avenelles$n_obs[match(i$year, ref_avenelles$year)])*i$sqq/sqrt(ref_avenelles$mean_q[match(i$year, ref_avenelles$year)])
     )}) %>% 
  do.call(what = cbind) %>% rowMeans(na.rm = T) #Retourne un vecteur avec une valeur de flux par année
bias_beales <- lapply(list_load, function(i) {abs((load_beales-ref_avenelles$annual_load[match(i$year, ref_avenelles$year)])/ref_avenelles$annual_load[match(i$year, ref_avenelles$year)]*100)}) #Retourne une liste de vecteurs avec les 1000 biais par année, en valeur absolue. 
mean_bias_beales <- as.data.frame(do.call(cbind,bias_beales)) %>% rowMeans #Calcule le biais moyen absolu par année    
  
return(list(load_beales = load_beales,   mean_bias_beales = mean_bias_beales))
}  
  
  
results_beales <- lapply(list_random, list_beales)
results_beales_listdf <- lapply(results_beales, as.data.frame) %>% lapply(cbind, year = complete_years)
results_beales_df <- bind_rows(results_beales_listdf, .id = "percent")


ggplot(results_beales_df,aes(x=year))+geom_line(data = ref_avenelles, aes(y=annual_load), size = 1)+
  geom_line(aes(y = load_beales, group = percent, col = percent))+
  scale_color_viridis_d(direction = -1)+
  labs(x= "Year", y = "Annual load, tons", col = "% of randomly sampled data",title = "Average DOC load by year depending on percentage of data included", subtitle = "Reference annual load in black")+
  scale_x_continuous(breaks = complete_years, minor_breaks = NULL)+
  theme_minimal()+
  theme(legend.position = "bottom", axis.text.x = element_text(angle = 45))

ggplot()+
  geom_line(data = ref_avenelles, aes(x = year, y=mean_q/3), size = 1)+
  geom_line(data = results_beales_df, aes(x=year, y=mean_bias_beales, group = percent, col = percent))+
  scale_color_viridis_d(direction = -1)+
  labs(x= "Year", y = "Average absolute bias,%", col = "% of randomly \n sampled data", title = "Average absolute bias by year depending on percentage of data included", subtitle = "Average annual discharge in black")+
  scale_x_continuous(breaks = complete_years, minor_breaks = NULL)+
  scale_y_continuous(sec.axis = sec_axis(~.*3, name = "Average annual discharge, L/s"))+
  theme_minimal()+
  theme(legend.position = "bottom", axis.text.x = element_text(angle = 45))


```



### Camille's ratio

Based on the observation that sum(Li)/sum(Qi) = sum(La)/sum(Qa)

Bias = absolute bias

```{r test-camille-block}
list_camille <- function(list_df){
  
list_load <- lapply(list_df,function(i) {i %>% group_by(year) %>% summarise(load = sum(doc_mg.L*q_L.s*period, na.rm = T), sum_q = sum(q_L.s, na.rm = T), mean_q = mean(q_L.s, na.rm = T))}) # génère une liste de dataframes
load_camille <- lapply(list_load, function(i) {i$load/i$sum_q*ref_avenelles$sum_q[match(i$year, ref_avenelles$year)]}) %>% do.call(what = cbind) %>% rowMeans #Retourne un vecteur avec une valeur de flux par année
bias_camille <- lapply(list_load, function(i) {abs(((i$load/i$sum_q*ref_avenelles$sum_q[match(i$year, ref_avenelles$year[match(i$year, ref_avenelles$year)])])-ref_avenelles$annual_load[match(i$year, ref_avenelles$year)])/ref_avenelles$annual_load[match(i$year, ref_avenelles$year)]*100)}) #Retourne une liste de vecteurs avec les 1000 biais par année, en valeur absolue. 
mean_bias_camille <- as.data.frame(do.call(cbind,bias_camille)) %>% rowMeans #Calcule le biais moyen absolu par année    
  
return(list(load_camille = load_camille,   mean_bias_camille = mean_bias_camille))
}  
  
  
results_camille <- lapply(list_random, list_camille)
results_camille_listdf <- lapply(results_camille, as.data.frame) %>% lapply(cbind, year = complete_years)
results_camille_df <- bind_rows(results_camille_listdf, .id = "percent")


ggplot(results_camille_df,aes(x=year))+geom_line(data = ref_avenelles, aes(y=annual_load), size = 1)+
  geom_line(aes(y = load_camille, group = percent, col = percent))+
  scale_color_viridis_d(direction = -1)+
  labs(x= "Year", y = "Annual load, tons", col = "% of randomly sampled data",title = "Average DOC load by year depending on percentage of data included", subtitle = "Reference annual load in black")+
  scale_x_continuous(breaks = complete_years, minor_breaks = NULL)+
  theme_minimal()+
  theme(legend.position = "bottom", axis.text.x = element_text(angle = 45))


ggplot()+
  geom_line(data = ref_avenelles, aes(x = year, y=mean_q/6), size = 1)+
  geom_line(data = results_camille_df, aes(x=year, y=mean_bias_camille, group = percent, col = percent))+
  scale_color_viridis_d(direction = -1)+
  labs(x= "Year", y = "Average absolute bias,%", col = "% of randomly \n sampled data", title = "Average absolute bias by year depending on percentage of data included", subtitle = "Average annual discharge in black")+
  scale_x_continuous(breaks = complete_years, minor_breaks = NULL)+
  scale_y_continuous(sec.axis = sec_axis(~.*6, name = "Average annual discharge, L/s"))+
  theme_minimal()+
  theme(legend.position = "bottom", axis.text.x = element_text(angle = 45))
```


## Bias with less frequent sampling (only plain sum)

```{r list-aggregated-df}
set.seed(2606)

ref_avenelles <- avenelles_complete %>% group_by(year) %>% summarise(annual_load = sum(doc_mg.L*q_L.s*period, na.rm = T), sum_q = sum(q_L.s, na.rm = T), mean_q = mean(q_L.s, na.rm = T), slq = cov(doc_mg.L*q_L.s*period, q_L.s, use = "pairwise.complete.obs"), n_obs = n()) 

# Fonction d'agrégation par bloc de n jours avec tirage aléatoire
aggregate_block <- function(df, n_days) {
  df %>%
    mutate(block = as.numeric(as.Date(DateHeure) - min(as.Date(DateHeure))) %/% n_days) %>%
    group_by(block) %>%
  group_modify(~ {
      valid_idx <- which(!is.na(.x))
      if (length(valid_idx) == 0) {
        # renvoyer une ligne de NA avec les bonnes colonnes
        .x[1, ] %>% mutate(across(everything(), ~ NA))
      } else {
        idx <- sample(valid_idx, 1)
        .x[idx, ]
      }
    }) %>%
    ungroup() %>%
    select(-block)
}

# 1000 tirages pour chaque agrégation
n_days_vec <- c(1,2, 4, 6, 8, 10, 12, 14)

list_aggregated <- lapply(n_days_vec, function(n_days) {
  lapply(1:20, function(i) {
    avenelles_complete %>%
      group_by(year) %>%
      group_modify(~ aggregate_block(.x, n_days)) %>%
      data.frame() %>% mutate(periodj = n_days)
  })
}) %>% setNames(paste0("d", n_days_vec))

```

```{r annual-load-aggregated}
list_agg_sum <- function(list_df){
  
list_load <- lapply(list_df,function(i) {i %>% group_by(year) %>% summarise(load = sum(doc_mg.L*q_L.s*periodj*24*60*60, na.rm = T), sum_q = sum(q_L.s, na.rm = T), mean_q = mean(q_L.s, na.rm = T), slq = cov(doc_mg.L*q_L.s*period, q_L.s, use = "pairwise.complete.obs"))}) # génère une liste de dataframes
load_aggregated <- as.data.frame(do.call(cbind,list_load)) %>% rowMeans(na.rm=T) #Calcule le load moyen par année  
bias_aggregated <- lapply(list_load, function(i) {abs((i$load-ref_avenelles$annual_load[match(i$year, ref_avenelles$year)])/ref_avenelles$annual_load[match(i$year, ref_avenelles$year)]*100)}) #Retourne une liste de vecteurs avec les 1000 biais par année, en valeur absolue. 
mean_bias_aggregated <- as.data.frame(do.call(cbind,bias_aggregated)) %>% rowMeans #Calcule le biais moyen absolu par année    
  
return(list(load_aggregated = load_aggregated, load_med = load_aggregated_med, load_max = load_aggregated_max, load_min = load_aggregated_min, mean_bias_aggregated = mean_bias_aggregated))
}  
  
results_aggregated <- lapply(list_aggregated, list_agg_sum)
results_aggregated_listdf <- lapply(results_aggregated, as.data.frame) %>% lapply(cbind, year = complete_years)
results_aggregated_df <- bind_rows(results_aggregated_listdf, .id = "nb_days")

results_aggregated_df$nb_days <- factor(results_aggregated_df$nb_days, levels = c("d1","d2","d4","d6","d8","d10","d12","d14"))

ggplot(results_aggregated_df,aes(x=year))+geom_line(data = ref_avenelles, aes(y=annual_load), size = 1)+
  #geom_ribbon(aes(ymin = load_min, ymax = load_max, fill = nb_days), alpha = 0.5)+
  geom_line(aes(y = load_aggregated, group = nb_days, col = nb_days))+
  scale_color_viridis_d(direction = -1)+
  labs(x= "Year", y = "Annual load, tons", col = "Nb days aggregated",title = "Average DOC load by year depending on sampling frequency", subtitle = "Reference annual load in black")+
  scale_x_continuous(breaks = complete_years, minor_breaks = NULL)+
  theme_minimal()+
  theme(legend.position = "bottom", axis.text.x = element_text(angle = 45))
# 
# ggplot()+
#   geom_line(data = ref_avenelles, aes(x = year, y=annual_load*5e-10), size = 1)+
#   geom_line(data = results_aggregated_df, aes(x=year, y=mean_bias_aggregated, group = nb_days, col = nb_days))+
#   scale_color_viridis_d(direction = -1)+
#   labs(x= "Year", y = "Average absolute bias,%", col = "Nb days aggregated", title = "Average absolute bias by year depending on sampling frequency", subtitle = "Average annual discharge in black")+
#   scale_x_continuous(breaks = complete_years, minor_breaks = NULL)+
#   scale_y_continuous(sec.axis = sec_axis(~.*5e10, name = "Average annual load, tons"))+
#   theme_minimal()+
#   theme(legend.position = "bottom", axis.text.x = element_text(angle = 45))


```
```{r test-2018}
avenelles_2018 <- avenelles %>% subset(year == 2018)

ggplot()+geom_point(data = avenelles, aes(x=DateHeure, y = doc_mg.L*q_L.s, col = as.character(periodj)))+scale_color_viridis_d(option = "H")+theme_bw()
ggplot()+geom_point(data = avenelles_2018, aes(x=DateHeure, y = doc_mg.L*q_L.s, col = as.character(periodj)))+scale_color_viridis_d(option = "H")+theme_bw()


avenelles_2018$periodj %>% print
annual_load_2018 <- with(avenelles_2018, sum(doc_mg.L*q_L.s*period, na.rm = T))

ave_aggregated_2018 <- lapply(n_days_vec, function(n_days){
    avenelles_2018 %>%
      group_by(year) %>%
      group_modify(~ aggregate_block(.x, n_days)) %>%
      data.frame() %>% mutate(periodj = n_days)
  }) %>% setNames(paste0("d", n_days_vec))




loads_2018 <- vapply(ave_aggregated_2018, function(i) {with(i, sum(doc_mg.L*q_L.s*period, na.rm = T))}, FUN.VALUE = numeric(1)) %>% tibble::enframe(name = "nb_days", value = "load") %>% rbind(c(nb_days = "all", load = annual_load_2018))


```

# Annual and interannual flux 

On considère que l'erreur sur DOC vient de la mesure par analyse TOC.

```{r uncertainties}
nyears <- length(complete_years)

avenelles_complete <- avenelles %>% filter(year %in% complete_years)

q_u <- 0.1

nobs <- dim(avenelles_complete)[1]
nrep <- 1000
```

## Total flux

```{r compute-flux}
#doc matrix
doc_meas <- matrix(avenelles_complete$doc_mg.L, nrow = nrep, ncol = nobs, byrow = T) # repeats nrep lines with observations

doc_cv <- 3.2*doc_meas^(-0.2) # from quich check Claire, vaut pour TOC mais pas autres moyens de mesure
doc_random <- matrix(rnorm(nrep*nobs, mean = 0, sd = 1), nrow=nrep, ncol = nobs)
doc_noise <- doc_cv*doc_random
doc_mat <- doc_meas * (1 + doc_noise/100) # final value of doc, with noise in percent

# Q matrix
q_meas <- matrix(avenelles_complete$q_L.s, nrow = nrep, ncol = nobs, byrow = T) # repeats nrow_boot times the vector q_L.s
q_noise <- matrix(rnorm(nrep*nobs, mean = 0, sd = q_u), nrow = nrep, ncol = nobs) # creates a noise in percent (proportion), between 0 and 10%
q_mat <- q_meas * (1 + q_noise) # final value of q, with noise

# period matrix
period_mat <- matrix(avenelles_complete$period, nrow = nrep, ncol = nobs, byrow = T) # in seconds

# Flux per time step
flux_ton_mat <- doc_mat*1e-9*q_mat*period_mat # flux per period (period in seconds, so flux in ton/s is converted to flux per period). 
flux_ton.s_mat <- doc_mat*1e-9*q_mat # without period

index_years <- lapply(complete_years, function(y){which(avenelles_complete$year == y)}) # list of indices corresponding to each year

# Annual flux
annual_flux_ton.y <- sapply(index_years, function(idx){apply(flux_ton_mat[,idx], 1, sum, na.rm = T)}) # sum of fluxes per year, for each iteration of the bootstrap. Result is a matrix with nrow_boot rows and 19 columns (1 per year)
annual_flux_pi <- apply(annual_flux_ton.y, 2, quantile, probs = c(0.025, 0.5, 0.975), na.rm = T) # prediction interval for annual fluxes, per year. 3 lignes, 19 columns
annual_flux_mean <- colMeans(annual_flux_ton.y, na.rm = T) # mean annual flux per year. 1 vector
annual_flux_sd <- apply(annual_flux_ton.y, 2, sd, na.rm = T) # standard deviation of annual flux per year. Is just an estimate of goodness of mean, not as good as than the confidence interval. 

annual_flux_df <- data.frame(year = complete_years, 
                        annual_flux_mean = annual_flux_mean, 
                        annual_flux_variability = annual_flux_sd, 
                        annual_flux_pi_lower = annual_flux_pi[1,], 
                        annual_flux_pi_upper = annual_flux_pi[3,])

# Interannual flux 
interannual_flux_ton.y <- rowMeans(annual_flux_ton.y, na.rm = T) # mean interannual flux per iteration of the bootstrap
interannual_flux_pi <- quantile(interannual_flux_ton.y, probs = c(0.025, 0.5, 0.975), na.rm = T) # prediction interval
interannual_flux_mean <- mean(interannual_flux_ton.y, na.rm = T) # mean interannual flux
interannual_flux_variability <- sd(annual_flux_mean, na.rm = T) # standard deviation of interannual flux per year

interannual_flux_df <- data.frame(year = "interannual", annual_flux_mean = interannual_flux_mean, 
                                  annual_flux_variability = interannual_flux_variability,
                        annual_flux_pi_lower = interannual_flux_pi[1], 
                        annual_flux_pi_upper = interannual_flux_pi[3])

total_flux_df <- rbind(annual_flux_df, interannual_flux_df)
total_flux_df$group <- c(rep("annual", nyears), "interannual")

# Q df

annual_q <- sapply(index_years, function(idx){apply(q_mat[,idx], 1, sum, na.rm = T)}) # sum of fluxes per year, for each iteration of the bootstrap. Result is a matrix with nrow_boot rows and 19 columns (1 per year)
annual_q_pi <- apply(annual_q, 2, quantile, probs = c(0.025, 0.5, 0.975), na.rm = T) # prediction interval for annual fluxes, per year. 3 lignes, 19 columns
annual_q_mean <- colMeans(annual_q, na.rm = T) # mean annual flux per year. 1 vector
annual_q_sd <- apply(annual_q, 2, sd, na.rm = T) # standard deviation of annual flux per year. Is just an estimate of goodness of mean, not as good as than the confidence interval. 
interannual_q <- rowMeans(annual_q, na.rm = T) # mean interannual flux per iteration of the bootstrap
interannual_q_pi <- quantile(interannual_q, probs = c(0.025, 0.5, 0.975), na.rm = T) # prediction interval
interannual_q_mean <- mean(interannual_q, na.rm = T) # mean interannual flux
interannual_q_variability <- sd(annual_q_mean, na.rm = T) # standard deviation of interannual flux per year

q_df <- data.frame(year = c(complete_years, "interannual"), 
                        q_mean = c(annual_q_mean, interannual_q_mean),
                        q_variability = c(annual_flux_sd, interannual_q_variability), 
                        q_pi_lower = c(annual_q_pi[1,], interannual_q_pi[1]), 
                        q_pi_upper = c(annual_q_pi[3,], interannual_q_pi[3]),
                   group = c(rep("annual", nyears), "interannual"))

# Plot
ggplot()+
  geom_col(data = total_flux_df, aes(x=year, y = annual_flux_mean, fill = group))+
    geom_errorbar(data = total_flux_df, aes(x = year, ymin = annual_flux_pi_lower, ymax = annual_flux_pi_upper, col = "prediction interval"), width = 0.3, size = 0.8)+
  geom_errorbar(data = filter(total_flux_df, year == "interannual"), aes(x = year, ymin = annual_flux_mean - annual_flux_variability, ymax = annual_flux_mean + annual_flux_variability, col = "interannual variability"), width = 0.2, size = 0.8, linetype = 2)+
  scale_fill_manual(values = c("annual" = "lightblue", "interannual" = "indianred"))+
  scale_color_manual(values = c("prediction interval" = "darkblue", "interannual variability" = "darkred"), name = "")+
   labs(x = "Year", y = "Flux (ton/year)", fill = "")+
  theme_minimal(base_size = 15)+
  theme(axis.text.x = element_text(angle = 45, hjust = 1), legend.position = "bottom")

ggplot()+
  geom_col(data = q_df, aes(x=year, y = q_mean, fill = group))+
    geom_errorbar(data = q_df, aes(x = year, ymin = q_pi_lower, ymax = q_pi_upper, col = "prediction interval"), width = 0.3, size = 0.8)+
  geom_errorbar(data = filter(q_df, year == "interannual"), aes(x = year, ymin = q_mean - q_variability, ymax = q_mean + q_variability, col = "interannual variability"), width = 0.2, size = 0.8, linetype = 2)+
  scale_fill_manual(values = c("annual" = "lightblue", "interannual" = "indianred"))+
  scale_color_manual(values = c("prediction interval" = "darkblue", "interannual variability" = "darkred"), name = "")+
   labs(x = "Year", y = "Discharge (L/year)", fill = "")+
  theme_minimal(base_size = 15)+
  theme(axis.text.x = element_text(angle = 45, hjust = 1), legend.position = "bottom")

knitr::kable(total_flux_df, digits = 2, row.names = F) %>% kableExtra::kable_styling()

```

## Specific flux

```{r specific-flux}
# sflux_ton_mat <- doc_mat*1e-9*q_mat*period_mat/bv # flux per period (period in seconds, so flux in ton/s is converted to flux per period). 
# sflux_ton.s_mat <- doc_mat*1e-9*q_mat/bv # without period
# 
# annual_sflux_ton.y <- sapply(index_years, function(idx){apply(sflux_ton_mat[,idx], 1, sum, na.rm = T)}) # sum of fluxes per year, for each iteration of the bootstrap. Result is a matrix with nrow_boot rows and 19 columns (1 per year)
# annual_sflux_pi <- apply(annual_sflux_ton.y, 2, quantile, probs = c(0.025, 0.5, 0.975), na.rm = T) # prediction interval for annual fluxes, per year. 3 lignes, 19 columns
# annual_sflux_mean <- colMeans(annual_sflux_ton.y, na.rm = T) # mean annual flux per year. 1 vector
# annual_sflux_sd <- apply(annual_sflux_ton.y, 2, sd, na.rm = T) # standard deviation of annual flux per year. Is just an estimate of goodness of mean, not as good as than the confidence interval. 
# 
# annual_sflux_df <- data.frame(year = complete_years, 
#                         annual_flux_mean = annual_sflux_mean, 
#                         annual_flux_variability = annual_sflux_sd, 
#                         annual_flux_pi_lower = annual_sflux_pi[1,], 
#                         annual_flux_pi_upper = annual_sflux_pi[3,])
# 
# # Interannual flux 
# interannual_sflux_ton.y <- rowMeans(annual_sflux_ton.y, na.rm = T) # mean interannual flux per iteration of the bootstrap
# interannual_sflux_pi <- quantile(interannual_sflux_ton.y, probs = c(0.025, 0.5, 0.975), na.rm = T) # prediction interval
# interannual_sflux_mean <- mean(interannual_sflux_ton.y, na.rm = T) # mean interannual flux
# interannual_sflux_variability <- sd(annual_sflux_mean, na.rm = T) # standard deviation of interannual flux per year
# 
# interannual_sflux_df <- data.frame(year = "interannual", annual_flux_mean = interannual_sflux_mean, 
#                                   annual_flux_variability = interannual_sflux_variability,
#                         annual_flux_pi_lower = interannual_sflux_pi[1], 
#                         annual_flux_pi_upper = interannual_sflux_pi[3])


total_sflux_df <- cbind(total_flux_df[,"year"], total_flux_df[,2:5] / bv, total_flux_df[,"group"]) %>% setNames(names(total_flux_df))
#total_sflux_df <- rbind(annual_sflux_df, interannual_sflux_df)
total_sflux_df$group <- c(rep("annual", nyears), "interannual")

ggplot()+
  geom_col(data = total_sflux_df, aes(x=year, y = annual_flux_mean, fill = group), width = 0.8)+
    geom_errorbar(data = total_sflux_df, aes(x = year, ymin = annual_flux_pi_lower, ymax = annual_flux_pi_upper, col = "prediction interval"), width = 0.3, size = 0.8)+
  geom_errorbar(data = filter(total_sflux_df, year == "interannual"), aes(x = year, ymin = annual_flux_mean - annual_flux_variability, ymax = annual_flux_mean + annual_flux_variability, col = "interannual variability"), width = 0.2, size = 0.8, linetype = 2)+
  scale_fill_manual(values = c("annual" = "lightblue", "interannual" = "indianred"))+
  scale_color_manual(values = c("prediction interval" = "darkblue", "interannual variability" = "darkred"), name = "")+
   labs(x = "Year", y = "Flux (tons/km2/year)", fill = "")+
  theme_minimal(base_size = 15)+
  theme(axis.text.x = element_text(angle = 45, hjust = 1), legend.position = "bottom")

ggsave(here("figures","sflux_avenelles.svg"))

knitr::kable(total_sflux_df, digits = 2, row.names = F) %>% kableExtra::kable_styling()
```

# Export données

```{r exporter-valeurs-dans-csv-commun}

library(readxl)
library(writexl)


rmd_id <- "Avenelles"

rmd_values <- data.frame(
  rmd = rmd_id,
  carbon  = "DOC",
  flux_ton = total_flux_df$annual_flux_mean[total_flux_df$year == "interannual"],
    flux_ton_sd = total_flux_df$annual_flux_variability[total_flux_df$year == "interannual"],
    flux_ton_pil = total_flux_df$annual_flux_pi_lower[total_flux_df$year == "interannual"],
    flux_ton_piu = total_flux_df$annual_flux_pi_upper[total_flux_df$year == "interannual"],
    flux_ton_km2 = total_sflux_df$annual_flux_mean[total_flux_df$year == "interannual"],
   flux_ton_km2_sd = total_sflux_df$annual_flux_variability[total_flux_df$year == "interannual"],
   flux_ton_km2_pil = total_sflux_df$annual_flux_pi_lower[total_flux_df$year == "interannual"],
   flux_ton_km2_piu = total_sflux_df$annual_flux_pi_upper[total_flux_df$year == "interannual"],
  nb_years = length(complete_years)
  # ... autres colonnes
)

# Lire le fichier existant ou créer un dataframe vide
if (file.exists(here("resultats.xlsx"))) {
  df_shared <- read_xlsx(here("resultats.xlsx"))
} else {
  df_shared <- data.frame()
}

# Mettre à jour la ligne du Rmd ou l'ajouter si absente
if (rmd_id %in% df_shared$rmd) {
  df_shared[df_shared$rmd == rmd_id, ] <- rmd_values  # mise à jour
} else {
  df_shared <- rbind(df_shared, rmd_values)            # ajout
}



# Réécrire
write_xlsx(df_shared, here("resultats.xlsx"))
```

