---
title: "Avenelles - méthodes"
author: "CamilMC"
date: "2026-06-17"
output:
  html_document:
    toc: true
    toc_float: true
    number_sections: true
    code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = F, warning = F, error = F, fig.align = "center", collapse = T,
                      cache = T)
```

```{r libraries}
lapply(c("dplyr"), library, character.only = T)
lapply(c("ggplot2","ggpubr"), library, character.only = T)
lapply(c("lubridate"), library, character.only = T)
lapply(c("knitr","kableExtra"), library, character.only = T)

```
# Data visualisation

## Get data

```{r bv-aire}
bv <- 45
```


```{r load-data-from-excel, message = F}

avenelles <- readxl::read_xlsx(path = "Data_Avenelles_DOC_DIC_Debit.xlsx", sheet = "Data_Avenelles_DOC_DIC_Debit", col_types = c("date","numeric", "text","numeric","text","numeric","text","text","numeric")) %>%  mutate(Site = NULL, bv_km2 = NULL) %>% unique()

avenelles$year <- year(avenelles$DateHeure)
avenelles$week <- week(avenelles$DateHeure)
avenelles$month <- month(avenelles$DateHeure)

avenelles$commondate <- as.Date(paste0("2000-", format(avenelles$DateHeure,"%j")), "%Y-%j")
avenelles$Date <- format(avenelles$DateHeure, "%Y-%m-%d") %>% as.Date()

avenelles$period <- with(avenelles, as.numeric(-(DateHeure - lead(DateHeure)))) # period in second between 2 lines. This leads to some large periods being calculated when data is missing / not sampled during a long interval. 
avenelles$periodj <- round(avenelles$period / 60 / 60 / 24, 0)
avenelles[which(avenelles$periodj > 4),"period"] <- 2*24*60*60 # the median time of sampling is every second day. This line replaces periods that are artificially longer than 2 days
avenelles[which(avenelles$periodj > 4),"periodj"] <- 2

avenelles <- unique(avenelles)
  
strange_periods_dates <- avenelles %>% subset(periodj > 4) %>% pull(Date) 

```

## Characteristics

```{r summary-data}
summary_avenelles <- merge(
avenelles %>% subset(!is.na(doc_mg.L)) %>% group_by(year) %>% summarise("Number of DOC observations" = n(), "DOC range, mg/L" = paste(quantile(doc_mg.L, probs = c(0,0.5,1), na.rm = T), collapse = " / ")),
avenelles %>% subset(!is.na(q_L.s)) %>% group_by(year) %>% summarise("Number of Q observations" = n(), "Q range, L/s" = paste(quantile(q_L.s, probs = c(0,0.5,1), na.rm = T), collapse = " / ")), by = "year", all = T) %>% 
  merge(avenelles %>% group_by(year) %>% summarise("Number of days sampled" = length(unique(Date))), by = "year", all = T) %>%
  merge(avenelles %>% group_by(year) %>% summarise("Correlation DOC/log(Q)" = round(cor(doc_mg.L, log(q_L.s), use = "pairwise.complete.obs"),2)), by = "year", all = T) %>%
  rbind(c("All years", 
          dim(subset(avenelles, !is.na(doc_mg.L)))[1], 
          paste(quantile(avenelles$doc_mg.L, probs = c(0,0.5,1), na.rm = T), collapse = " / "), 
          dim(subset(avenelles, !is.na(q_L.s)))[1], 
          paste(quantile(avenelles$q_L.s, probs = c(0,0.5,1), na.rm = T), collapse = " / "), 
          length(unique(avenelles$Date)),
          round(cor(avenelles$doc_mg.L, log(avenelles$q_L.s), use = "pairwise.complete.obs" ),2)
          ))

knitr::kable(summary_avenelles, caption = "Summary table of Avenelles data") %>% kableExtra::kable_styling()

```

```{r plot-by-year-doc, fig.dim = c(10,15)}


title <- expression(atop("Series of DOC and Q by year"))
plots <- ggarrange(
ggplot(avenelles, aes(x = commondate))+
  geom_point(aes(y = q_L.s, col = "Débit, L/s"), alpha = 0.5)+
  scale_x_date(labels = function(x) format(x, "%d-%b"), date_minor_breaks = "1 month", name = "")+
  scale_color_manual(values = c("lightblue"), name = "")+
  facet_grid(rows = vars(year))+
  labs(y = "Débit, L/s", col = "")+
  theme_minimal(base_size = 15)+
  theme(legend.position = "none"),

ggplot(avenelles, aes(x = commondate))+
  geom_point(aes(y = doc_mg.L, col = "DOC, mg.L"), alpha = 0.5)+
  scale_x_date(labels = function(x) format(x, "%d-%b"), date_minor_breaks = "1 month", name = "")+
  scale_color_manual(values = c("palegreen4"), name = "")+
  facet_grid(rows = vars(year))+
  labs(y = "DOC, mg/L", col = "")+
  theme_minimal(base_size = 15)+
  theme(legend.position = "none")
)

annotate_figure(plots, top = text_grob(title))

```

DOC observation for year 2014 are FALSE: there has been a mix between DIC and DOC data (confirmed by Sophie Guillon). 2014 is excluded from the analysis. Data for 2015 seem to be partially wrong as well. 

Years to use for test of methods: `r complete_years <- c(2006,2007,2010,2011,2012,2013,2016,2017,2018,2019,2021)` 
`r print(complete_years)`

```{r plot-complete-years, fig.dim = c(10,15)}

avenelles_complete <- avenelles %>% subset(year %in% complete_years)

title <- expression(atop("Series of DOC and Q by year"))
plots <- ggarrange(
ggplot(subset(avenelles_complete, year %in% complete_years), aes(x = commondate))+
  geom_point(aes(y = q_L.s, col = "Débit, L/s"), alpha = 0.5)+
  scale_x_date(labels = function(x) format(x, "%d-%b"), date_minor_breaks = "1 month", name = "")+
  scale_color_manual(values = c("lightblue"), name = "")+
  facet_grid(rows = vars(year))+
  labs(y = "Débit, L/s", col = "")+
  theme_minimal(base_size = 15)+
  theme(legend.position = "none"),

ggplot(subset(avenelles, year %in% complete_years), aes(x = commondate))+
  geom_point(aes(y = doc_mg.L, col = "DOC, mg.L"), alpha = 0.5)+
  scale_x_date(labels = function(x) format(x, "%d-%b"), date_minor_breaks = "1 month", name = "")+
  scale_color_manual(values = c("palegreen4"), name = "")+
  facet_grid(rows = vars(year))+
  labs(y = "DOC, mg/L", col = "")+
  theme_minimal(base_size = 15)+
  theme(legend.position = "none")
)

annotate_figure(plots, top = text_grob(title))

```

# Test of methods

```{r ref-load-random-load}
set.seed(1806)

ref_avenelles <- avenelles_complete%>% group_by(year) %>% summarise(annual_load = sum(doc_mg.L*q_L.s*period, na.rm = T), sum_q = sum(q_L.s, na.rm = T), mean_q = mean(q_L.s, na.rm = T), slq = cov(doc_mg.L*q_L.s*period, q_L.s, use = "pairwise.complete.obs"), n_obs = n()) 

avenelles_p10 <- lapply(1:1000, function(i) data.frame(avenelles_complete %>% group_by(year) %>% sample_frac(10*1e-2)))
avenelles_p20 <- lapply(1:1000, function(i) data.frame(avenelles_complete %>% group_by(year) %>% sample_frac(20*1e-2)))
avenelles_p30 <- lapply(1:1000, function(i) data.frame(avenelles_complete %>% group_by(year) %>% sample_frac(30*1e-2)))
avenelles_p40 <- lapply(1:1000, function(i) data.frame(avenelles_complete %>% group_by(year) %>% sample_frac(40*1e-2)))
avenelles_p50 <- lapply(1:1000, function(i) data.frame(avenelles_complete %>% group_by(year) %>% sample_frac(50*1e-2)))
avenelles_p60 <- lapply(1:1000, function(i) data.frame(avenelles_complete %>% group_by(year) %>% sample_frac(60*1e-2)))
avenelles_p70 <- lapply(1:1000, function(i) data.frame(avenelles_complete %>% group_by(year) %>% sample_frac(70*1e-2)))
avenelles_p80 <- lapply(1:1000, function(i) data.frame(avenelles_complete %>% group_by(year) %>% sample_frac(80*1e-2)))
avenelles_p90 <- lapply(1:1000, function(i) data.frame(avenelles_complete %>% group_by(year) %>% sample_frac(90*1e-2)))
avenelles_p100 <- lapply(1:1000, function(i) data.frame(avenelles_complete %>% group_by(year) %>% sample_frac(100*1e-2)))

list_random <- list(p10 = avenelles_p10, p20 = avenelles_p20, p30 = avenelles_p30, p40 = avenelles_p40, p50 = avenelles_p50, p60 = avenelles_p60, p70 = avenelles_p70, p80 = avenelles_p80, p90 = avenelles_p90, p100 = avenelles_p100)

```

## Verhoff ratio 1980


Known to be biaised. Compute yearly flux by:

* Randomly sampling 10 to 90% of each year, 1000 times
* Calculate annual load with ratio method for each year
* Compare with reference load and estimate average bias

```{r test-verhoff}
list_verhoff <- function(list_df){
  
list_load <- lapply(list_df,function(i) {i %>% group_by(year) %>% summarise(load = sum(doc_mg.L*q_L.s, na.rm = T), sum_q = sum(q_L.s, na.rm = T), mean_q = mean(q_L.s, na.rm = T))}) # génère une liste de dataframes
load_verhoff <- lapply(list_load, function(i) {(i$load/i$sum_q*ref_avenelles$mean_q*60*60*24*365)}) %>% do.call(what = cbind) %>% rowMeans #Retourne un vecteur avec une valeur de flux par année
bias_verhoff <- lapply(list_load, function(i) {abs(((i$load/i$sum_q*ref_avenelles$mean_q*60*60*24*365)-ref_avenelles$annual_load)/ref_avenelles$annual_load*100)}) #Retourne une liste de vecteurs avec les 1000 biais par année, en valeur absolue. 
mean_bias_verhoff <- as.data.frame(do.call(cbind,bias_verhoff)) %>% rowMeans #Calcule le biais moyen absolu par année    
  
return(list(load_verhoff = load_verhoff,   mean_bias_verhoff = mean_bias_verhoff))
}  
  
  
results_verhoff <- lapply(list_random, list_verhoff)
results_verhoff_listdf <- lapply(results_verhoff, as.data.frame) %>% lapply(cbind, year = complete_years)
results_verhoff_df <- bind_rows(results_verhoff_listdf, .id = "percent")


ggplot(results_verhoff_df,aes(x=year))+geom_line(data = ref_avenelles, aes(y=annual_load), size = 1)+
  geom_line(aes(y = load_verhoff, group = percent, col = percent))+
  scale_color_viridis_d(direction = -1)+
  labs(x= "Year", y = "Annual load, tons", col = "% of randomly sampled data",title = "Average DOC load by year depending on percentage of data included", subtitle = "Reference annual load in black")+
  scale_x_continuous(breaks = complete_years, minor_breaks = NULL)+
  theme_minimal()+
  theme(legend.position = "bottom", axis.text.x = element_text(angle = 45))

ggplot()+
  geom_line(data = ref_avenelles, aes(x = year, y=mean_q/3), size = 1)+
  geom_line(data = results_verhoff_df, aes(x=year, y=mean_bias_verhoff, group = percent, col = percent))+
  scale_color_viridis_d(direction = -1)+
  labs(x= "Year", y = "Average absolute bias,%", col = "% of randomly \n sampled data", title = "Average absolute bias by year depending on percentage of data included", subtitle = "Average annual discharge in black")+
  scale_x_continuous(breaks = complete_years, minor_breaks = NULL)+
  scale_y_continuous(sec.axis = sec_axis(~.*3, name = "Average annual discharge, L/s"))+
  theme_minimal()+
  theme(legend.position = "bottom", axis.text.x = element_text(angle = 45))



```


```{r test-verhoff-deprecated, eval = F}

load_function <- function(list) {list_df <- lapply(list,function(i) {i %>% group_by(year) %>% summarise(load = sum(doc_mg.L*q_L.s, na.rm = T), sum_q = sum(q_L.s, na.rm = T), mean_q = mean(q_L.s, na.rm = T))}) 
                                  return(list_df)} # génère une liste de dataframes
load_verhoff <- function(list) {load <- lapply(list, function(i) {round((i$load/i$sum_q*ref_avenelles$mean_q*60*60*24*365))}) %>% do.call(what = cbind) %>% rowMeans
                                return(load)} # Conçue pour le résultat de load_function. Retourne un vecteur avec une valeur de flux par année

bias_verhoff <- function(list) {list_df <- lapply(list, function(i) {abs(((i$load/i$sum_q*ref_avenelles$mean_q*60*60*24*365)-ref_avenelles$annual_load)/ref_avenelles$annual_load*100)}) 
                                return(list_df)}  # Conçue pour le résultat de load_function. Retourne une liste de vecteurs avec les 1000 biais par année, en valeur absolue. 
mean_bias_verhoff <- function(list) {bias <- as.data.frame(do.call(cbind,list)) %>% rowMeans 
                                      return(bias)} # Conçue pour le résultat de bias_verhoff. Calcule le biais moyen absolu par année
avenelles_p10_load <- lapply(avenelles_p10, function(i) {i %>% group_by(year) %>% summarise(load = sum(doc_mg.L*q_L.s, na.rm = T), sum_q = sum(q_L.s, na.rm = T), mean_q = mean(q_L.s, na.rm = T))})
avenelles_p10_meanload <- lapply(avenelles_p10_load, function(i) {round((i$load/i$sum_q*ref_avenelles$mean_q*60*60*24*365))}) %>% do.call(what = cbind) %>% rowMeans
avenelles_p10_bias <- lapply(avenelles_p10_load, function(i) {round(((i$load/i$sum_q*ref_avenelles$mean_q*60*60*24*365)-ref_avenelles$annual_load)/ref_avenelles$annual_load*100)}) 
avenelles_p10_meanbiais <- as.data.frame(do.call(cbind,avenelles_p10_bias)) %>% rowMeans

avenelles_p20_load <- lapply(avenelles_p20, function(i) {i %>% group_by(year) %>% summarise(load = sum(doc_mg.L*q_L.s, na.rm = T), sum_q = sum(q_L.s, na.rm = T), mean_q = mean(q_L.s, na.rm = T))})
avenelles_p20_meanload <- lapply(avenelles_p20_load, function(i) {round((i$load/i$sum_q*ref_avenelles$mean_q*60*60*24*365))}) %>% do.call(what = cbind) %>% rowMeans
avenelles_p20_bias <- lapply(avenelles_p20_load, function(i) {round(((i$load/i$sum_q*ref_avenelles$mean_q*60*60*24*365)-ref_avenelles$annual_load)/ref_avenelles$annual_load*100)}) 
avenelles_p20_meanbiais <- as.data.frame(do.call(cbind,avenelles_p20_bias)) %>% rowMeans

avenelles_p30_load <- lapply(avenelles_p30, function(i) {i %>% group_by(year) %>% summarise(load = sum(doc_mg.L*q_L.s, na.rm = T), sum_q = sum(q_L.s, na.rm = T), mean_q = mean(q_L.s, na.rm = T))})
avenelles_p30_meanload <- lapply(avenelles_p30_load, function(i) {round((i$load/i$sum_q*ref_avenelles$mean_q*60*60*24*365))}) %>% do.call(what = cbind) %>% rowMeans
avenelles_p30_bias <- lapply(avenelles_p30_load, function(i) {round(((i$load/i$sum_q*ref_avenelles$mean_q*60*60*24*365)-ref_avenelles$annual_load)/ref_avenelles$annual_load*100)}) 
avenelles_p30_meanbiais <- as.data.frame(do.call(cbind,avenelles_p30_bias)) %>% rowMeans

avenelles_p40_load <- lapply(avenelles_p40, function(i) {i %>% group_by(year) %>% summarise(load = sum(doc_mg.L*q_L.s, na.rm = T), sum_q = sum(q_L.s, na.rm = T), mean_q = mean(q_L.s, na.rm = T))})
avenelles_p40_meanload <- lapply(avenelles_p40_load, function(i) {round((i$load/i$sum_q*ref_avenelles$mean_q*60*60*24*365))}) %>% do.call(what = cbind) %>% rowMeans
avenelles_p40_bias <- lapply(avenelles_p40_load, function(i) {round(((i$load/i$sum_q*ref_avenelles$mean_q*60*60*24*365)-ref_avenelles$annual_load)/ref_avenelles$annual_load*100)}) 
avenelles_p40_meanbiais <- as.data.frame(do.call(cbind,avenelles_p40_bias)) %>% rowMeans

avenelles_p50_load <- lapply(avenelles_p50, function(i) {i %>% group_by(year) %>% summarise(load = sum(doc_mg.L*q_L.s, na.rm = T), sum_q = sum(q_L.s, na.rm = T), mean_q = mean(q_L.s, na.rm = T))})
avenelles_p50_meanload <- lapply(avenelles_p50_load, function(i) {round((i$load/i$sum_q*ref_avenelles$mean_q*60*60*24*365))}) %>% do.call(what = cbind) %>% rowMeans
avenelles_p50_bias <- lapply(avenelles_p50_load, function(i) {round(((i$load/i$sum_q*ref_avenelles$mean_q*60*60*24*365)-ref_avenelles$annual_load)/ref_avenelles$annual_load*100)}) 
avenelles_p50_meanbiais <- as.data.frame(do.call(cbind,avenelles_p50_bias)) %>% rowMeans

avenelles_p60_load <- lapply(avenelles_p60, function(i) {i %>% group_by(year) %>% summarise(load = sum(doc_mg.L*q_L.s, na.rm = T), sum_q = sum(q_L.s, na.rm = T), mean_q = mean(q_L.s, na.rm = T))})
avenelles_p60_meanload <- lapply(avenelles_p60_load, function(i) {round((i$load/i$sum_q*ref_avenelles$mean_q*60*60*24*365))}) %>% do.call(what = cbind) %>% rowMeans
avenelles_p60_bias <- lapply(avenelles_p60_load, function(i) {round(((i$load/i$sum_q*ref_avenelles$mean_q*60*60*24*365)-ref_avenelles$annual_load)/ref_avenelles$annual_load*100)}) 
avenelles_p60_meanbiais <- as.data.frame(do.call(cbind,avenelles_p60_bias)) %>% rowMeans

avenelles_p70_load <- lapply(avenelles_p70, function(i) {i %>% group_by(year) %>% summarise(load = sum(doc_mg.L*q_L.s, na.rm = T), sum_q = sum(q_L.s, na.rm = T), mean_q = mean(q_L.s, na.rm = T))})
avenelles_p70_meanload <- lapply(avenelles_p70_load, function(i) {round((i$load/i$sum_q*ref_avenelles$mean_q*60*60*24*365))}) %>% do.call(what = cbind) %>% rowMeans
avenelles_p70_bias <- lapply(avenelles_p70_load, function(i) {round(((i$load/i$sum_q*ref_avenelles$mean_q*60*60*24*365)-ref_avenelles$annual_load)/ref_avenelles$annual_load*100)}) 
avenelles_p70_meanbiais <- as.data.frame(do.call(cbind,avenelles_p70_bias)) %>% rowMeans

avenelles_p80_load <- lapply(avenelles_p80, function(i) {i %>% group_by(year) %>% summarise(load = sum(doc_mg.L*q_L.s, na.rm = T), sum_q = sum(q_L.s, na.rm = T), mean_q = mean(q_L.s, na.rm = T))})
avenelles_p80_meanload <- lapply(avenelles_p80_load, function(i) {round((i$load/i$sum_q*ref_avenelles$mean_q*60*60*24*365))}) %>% do.call(what = cbind) %>% rowMeans
avenelles_p80_bias <- lapply(avenelles_p80_load, function(i) {round(((i$load/i$sum_q*ref_avenelles$mean_q*60*60*24*365)-ref_avenelles$annual_load)/ref_avenelles$annual_load*100)}) 
avenelles_p80_meanbiais <- as.data.frame(do.call(cbind,avenelles_p80_bias)) %>% rowMeans

avenelles_p90_load <- lapply(avenelles_p90, function(i) {i %>% group_by(year) %>% summarise(load = sum(doc_mg.L*q_L.s, na.rm = T), sum_q = sum(q_L.s, na.rm = T), mean_q = mean(q_L.s, na.rm = T))})
avenelles_p90_meanload <- lapply(avenelles_p90_load, function(i) {round((i$load/i$sum_q*ref_avenelles$mean_q*60*60*24*365))}) %>% do.call(what = cbind) %>% rowMeans
avenelles_p90_bias <- lapply(avenelles_p90_load, function(i) {round(((i$load/i$sum_q*ref_avenelles$mean_q*60*60*24*365)-ref_avenelles$annual_load)/ref_avenelles$annual_load*100)}) 
avenelles_p90_meanbiais <- as.data.frame(do.call(cbind,avenelles_p90_bias)) %>% rowMeans

avenelles_p100_load <- lapply(avenelles_p100, function(i) {i %>% group_by(year) %>% summarise(load = sum(doc_mg.L*q_L.s, na.rm = T), sum_q = sum(q_L.s, na.rm = T), mean_q = mean(q_L.s, na.rm = T))})
avenelles_p100_meanload <- lapply(avenelles_p100_load, function(i) {round((i$load/i$sum_q*ref_avenelles$mean_q*60*60*24*365))}) %>% do.call(what = cbind) %>% rowMeans
avenelles_p100_bias <- lapply(avenelles_p100_load, function(i) {round(((i$load/i$sum_q*ref_avenelles$mean_q*60*60*24*365)-ref_avenelles$annual_load)/ref_avenelles$annual_load*100)}) 
avenelles_p100_meanbiais <- as.data.frame(do.call(cbind,avenelles_p100_bias)) %>% rowMeans

data.frame(
  Year = complete_years,
  "Annual load, tons" = ref_avenelles$annual_load * 1e-9,
  "Average estimated load, 10% of data" = avenelles_p10_meanload * 1e-9,
  "Average bias, 10 % of data" = avenelles_p10_meanbiais,
    "Average estimated load, 20% of data" = avenelles_p20_meanload * 1e-9,
  "Average bias, 20 % of data" = avenelles_p20_meanbiais,
    "Average estimated load, 30% of data" = avenelles_p30_meanload * 1e-9,
  "Average bias, 30 % of data" = avenelles_p30_meanbiais,
    "Average estimated load, 40% of data" = avenelles_p40_meanload * 1e-9,
  "Average bias, 40 % of data" = avenelles_p40_meanbiais,
    "Average estimated load, 50% of data" = avenelles_p50_meanload * 1e-9,
  "Average bias, 50 % of data" = avenelles_p50_meanbiais,
    "Average estimated load, 60% of data" = avenelles_p60_meanload * 1e-9,
  "Average bias, 60 % of data" = avenelles_p60_meanbiais,
    "Average estimated load, 70% of data" = avenelles_p70_meanload * 1e-9,
  "Average bias, 70 % of data" = avenelles_p70_meanbiais,
    "Average estimated load, 80% of data" = avenelles_p80_meanload * 1e-9,
  "Average bias, 80 % of data" = avenelles_p80_meanbiais,
    "Average estimated load, 90% of data" = avenelles_p90_meanload * 1e-9,
  "Average bias, 90 % of data" = avenelles_p90_meanbiais,
    "Average estimated load, 100% of data" = avenelles_p100_meanload * 1e-9,
  "Average bias, 100 % of data" = avenelles_p100_meanbiais,
  check.names = F
)  %>% knitr::kable(digits = 2) %>% kableExtra::kable_styling()


summary_df <- data.frame(
  year = complete_years,
  annual_load_ref = ref_avenelles$annual_load * 1e-9,
  annual_load_p10 = avenelles_p10_meanload * 1e-9,
  bias_p10 = avenelles_p10_meanbiais,
  annual_load_p20 = avenelles_p20_meanload * 1e-9,
  bias_p20 = avenelles_p20_meanbiais,
  annual_load_p30 = avenelles_p30_meanload * 1e-9,
  bias_p30 = avenelles_p30_meanbiais,
  annual_load_p40 = avenelles_p40_meanload * 1e-9,
  bias_p40 = avenelles_p40_meanbiais,
  annual_load_p50 = avenelles_p50_meanload * 1e-9,
  bias_p50 = avenelles_p50_meanbiais,
  annual_load_p60 = avenelles_p60_meanload * 1e-9,
  bias_p60 = avenelles_p60_meanbiais,
  annual_load_p70 = avenelles_p70_meanload * 1e-9,
  bias_p70 = avenelles_p70_meanbiais,
  annual_load_p80 = avenelles_p80_meanload * 1e-9,
  bias_p80 = avenelles_p80_meanbiais,
  annual_load_p90 = avenelles_p90_meanload * 1e-9,
  bias_p90 = avenelles_p90_meanbiais,
  annual_load_p100 = avenelles_p100_meanload * 1e-9,
  bias_p100 = avenelles_p100_meanbiais)

ggplot(summary_df,aes(x=year))+geom_line(aes(y=annual_load_ref), size = 1)+
  geom_line(aes(y=annual_load_p10, col = "10%"))+
    geom_line(aes(y=annual_load_p20, col = "20%"))+
    geom_line(aes(y=annual_load_p30, col = "30%"))+
    geom_line(aes(y=annual_load_p40, col = "40%"))+
    geom_line(aes(y=annual_load_p50, col = "50%"))+
    geom_line(aes(y=annual_load_p60, col = "60%"))+
    geom_line(aes(y=annual_load_p70, col = "70%"))+
    geom_line(aes(y=annual_load_p80, col = "80%"))+
    geom_line(aes(y=annual_load_p90, col = "90%"))+
    geom_line(aes(y=annual_load_p100, col = " 100%"))+
  scale_color_viridis_d(direction = -1)+
  labs(x= "Year", y = "Annual load, tons", col = "% of randomly sampled data",title = "Average DOC load by year depending on percentage of data included", subtitle = "Reference annual load in black")+
  scale_x_continuous(breaks = complete_years, minor_breaks = NULL)+
  theme_minimal()+
  theme(legend.position = "bottom", axis.text.x = element_text(angle = 45))

ggplot(summary_df,aes(x=year))+geom_line(data = ref_avenelles, aes(x = year, y=mean_q/3), size = 1)+
  geom_line(aes(y=bias_p10, col = "10%"))+
    geom_line(aes(y=bias_p20, col = "20%"))+
    geom_line(aes(y=bias_p30, col = "30%"))+
    geom_line(aes(y=bias_p40, col = "40%"))+
    geom_line(aes(y=bias_p50, col = "50%"))+
    geom_line(aes(y=bias_p60, col = "60%"))+
    geom_line(aes(y=bias_p70, col = "70%"))+
    geom_line(aes(y=bias_p80, col = "80%"))+
    geom_line(aes(y=bias_p90, col = "90%"))+
    geom_line(aes(y=bias_p100, col = " 100%"))+
  scale_color_viridis_d(direction = -1)+
  labs(x= "Year", y = "Average bias,%", col = "% of randomly \n sampled data", title = "Average bias by year depending on percentage of data included", subtitle = "Average annual discharge in black")+
  scale_x_continuous(breaks = complete_years, minor_breaks = NULL)+
  scale_y_continuous(sec.axis = sec_axis(~.*3, name = "Average annual discharge, L/s"))+
  theme_minimal()+
  theme(legend.position = "bottom", axis.text.x = element_text(angle = 45))


```



## Camille's ratio

Based on the observation that sum(Li)/sum(Qi) = sum(La)/sum(Qa)

Bias = absolute bias

```{r test-camille}
list_camille <- function(list_df){
  
list_load <- lapply(list_df,function(i) {i %>% group_by(year) %>% summarise(load = sum(doc_mg.L*q_L.s*period, na.rm = T), sum_q = sum(q_L.s, na.rm = T), mean_q = mean(q_L.s, na.rm = T))}) # génère une liste de dataframes
load_camille <- lapply(list_load, function(i) {i$load/i$sum_q*ref_avenelles$sum_q}) %>% do.call(what = cbind) %>% rowMeans #Retourne un vecteur avec une valeur de flux par année
bias_camille <- lapply(list_load, function(i) {abs(((i$load/i$sum_q*ref_avenelles$sum_q)-ref_avenelles$annual_load)/ref_avenelles$annual_load*100)}) #Retourne une liste de vecteurs avec les 1000 biais par année, en valeur absolue. 
mean_bias_camille <- as.data.frame(do.call(cbind,bias_camille)) %>% rowMeans #Calcule le biais moyen absolu par année    
  
return(list(load_camille = load_camille,   mean_bias_camille = mean_bias_camille))
}  
  
  
results_camille <- lapply(list_random, list_camille)
results_camille_listdf <- lapply(results_camille, as.data.frame) %>% lapply(cbind, year = complete_years)
results_camille_df <- bind_rows(results_camille_listdf, .id = "percent")


ggplot(results_camille_df,aes(x=year))+geom_line(data = ref_avenelles, aes(y=annual_load), size = 1)+
  geom_line(aes(y = load_camille, group = percent, col = percent))+
  scale_color_viridis_d(direction = -1)+
  labs(x= "Year", y = "Annual load, tons", col = "% of randomly sampled data",title = "Average DOC load by year depending on percentage of data included", subtitle = "Reference annual load in black")+
  scale_x_continuous(breaks = complete_years, minor_breaks = NULL)+
  theme_minimal()+
  theme(legend.position = "bottom", axis.text.x = element_text(angle = 45))


ggplot()+
  geom_line(data = ref_avenelles, aes(x = year, y=mean_q/5), size = 1)+
  geom_line(data = results_camille_df, aes(x=year, y=mean_bias_camille, group = percent, col = percent))+
  scale_color_viridis_d(direction = -1)+
  labs(x= "Year", y = "Average absolute bias,%", col = "% of randomly \n sampled data", title = "Average absolute bias by year depending on percentage of data included", subtitle = "Average annual discharge in black")+
  scale_x_continuous(breaks = complete_years, minor_breaks = NULL)+
  scale_y_continuous(sec.axis = sec_axis(~.*5, name = "Average annual discharge, L/s"))+
  theme_minimal()+
  theme(legend.position = "bottom", axis.text.x = element_text(angle = 45))
```


```{r test-camille-deprecated, eval = F}
avenelles_p10_load <- lapply(avenelles_p10, function(i) {i %>% group_by(year) %>% summarise(load = sum(doc_mg.L*q_L.s*period, na.rm = T), sum_q = sum(q_L.s, na.rm = T), mean_q = mean(q_L.s, na.rm = T))})
avenelles_p10_meanload <- lapply(avenelles_p10_load, function(i) {round((i$load/i$sum_q*ref_avenelles$sum_q))}) %>% do.call(what = cbind) %>% rowMeans
avenelles_p10_bias <- lapply(avenelles_p10_load, function(i) {round(((i$load/i$sum_q*ref_avenelles$sum_q)-ref_avenelles$annual_load)/ref_avenelles$annual_load*100)}) 
avenelles_p10_meanbiais <- as.data.frame(do.call(cbind,avenelles_p10_bias)) %>% rowMeans

avenelles_p20_load <- lapply(avenelles_p20, function(i) {i %>% group_by(year) %>% summarise(load = sum(doc_mg.L*q_L.s*period, na.rm = T), sum_q = sum(q_L.s, na.rm = T), mean_q = mean(q_L.s, na.rm = T))})
avenelles_p20_meanload <- lapply(avenelles_p20_load, function(i) {round((i$load/i$sum_q*ref_avenelles$sum_q))}) %>% do.call(what = cbind) %>% rowMeans
avenelles_p20_bias <- lapply(avenelles_p20_load, function(i) {round(((i$load/i$sum_q*ref_avenelles$sum_q)-ref_avenelles$annual_load)/ref_avenelles$annual_load*100)}) 
avenelles_p20_meanbiais <- as.data.frame(do.call(cbind,avenelles_p20_bias)) %>% rowMeans

avenelles_p30_load <- lapply(avenelles_p30, function(i) {i %>% group_by(year) %>% summarise(load = sum(doc_mg.L*q_L.s*period, na.rm = T), sum_q = sum(q_L.s, na.rm = T), mean_q = mean(q_L.s, na.rm = T))})
avenelles_p30_meanload <- lapply(avenelles_p30_load, function(i) {round((i$load/i$sum_q*ref_avenelles$sum_q))}) %>% do.call(what = cbind) %>% rowMeans
avenelles_p30_bias <- lapply(avenelles_p30_load, function(i) {round(((i$load/i$sum_q*ref_avenelles$sum_q)-ref_avenelles$annual_load)/ref_avenelles$annual_load*100)}) 
avenelles_p30_meanbiais <- as.data.frame(do.call(cbind,avenelles_p30_bias)) %>% rowMeans

avenelles_p40_load <- lapply(avenelles_p40, function(i) {i %>% group_by(year) %>% summarise(load = sum(doc_mg.L*q_L.s*period, na.rm = T), sum_q = sum(q_L.s, na.rm = T), mean_q = mean(q_L.s, na.rm = T))})
avenelles_p40_meanload <- lapply(avenelles_p40_load, function(i) {round((i$load/i$sum_q*ref_avenelles$sum_q))}) %>% do.call(what = cbind) %>% rowMeans
avenelles_p40_bias <- lapply(avenelles_p40_load, function(i) {round(((i$load/i$sum_q*ref_avenelles$sum_q)-ref_avenelles$annual_load)/ref_avenelles$annual_load*100)}) 
avenelles_p40_meanbiais <- as.data.frame(do.call(cbind,avenelles_p40_bias)) %>% rowMeans

avenelles_p50_load <- lapply(avenelles_p50, function(i) {i %>% group_by(year) %>% summarise(load = sum(doc_mg.L*q_L.s*period, na.rm = T), sum_q = sum(q_L.s, na.rm = T), mean_q = mean(q_L.s, na.rm = T))})
avenelles_p50_meanload <- lapply(avenelles_p50_load, function(i) {round((i$load/i$sum_q*ref_avenelles$sum_q))}) %>% do.call(what = cbind) %>% rowMeans
avenelles_p50_bias <- lapply(avenelles_p50_load, function(i) {round(((i$load/i$sum_q*ref_avenelles$sum_q)-ref_avenelles$annual_load)/ref_avenelles$annual_load*100)}) 
avenelles_p50_meanbiais <- as.data.frame(do.call(cbind,avenelles_p50_bias)) %>% rowMeans

avenelles_p60_load <- lapply(avenelles_p60, function(i) {i %>% group_by(year) %>% summarise(load = sum(doc_mg.L*q_L.s*period, na.rm = T), sum_q = sum(q_L.s, na.rm = T), mean_q = mean(q_L.s, na.rm = T))})
avenelles_p60_meanload <- lapply(avenelles_p60_load, function(i) {round((i$load/i$sum_q*ref_avenelles$sum_q))}) %>% do.call(what = cbind) %>% rowMeans
avenelles_p60_bias <- lapply(avenelles_p60_load, function(i) {round(((i$load/i$sum_q*ref_avenelles$sum_q)-ref_avenelles$annual_load)/ref_avenelles$annual_load*100)}) 
avenelles_p60_meanbiais <- as.data.frame(do.call(cbind,avenelles_p60_bias)) %>% rowMeans

avenelles_p70_load <- lapply(avenelles_p70, function(i) {i %>% group_by(year) %>% summarise(load = sum(doc_mg.L*q_L.s*period, na.rm = T), sum_q = sum(q_L.s, na.rm = T), mean_q = mean(q_L.s, na.rm = T))})
avenelles_p70_meanload <- lapply(avenelles_p70_load, function(i) {round((i$load/i$sum_q*ref_avenelles$sum_q))}) %>% do.call(what = cbind) %>% rowMeans
avenelles_p70_bias <- lapply(avenelles_p70_load, function(i) {round(((i$load/i$sum_q*ref_avenelles$sum_q)-ref_avenelles$annual_load)/ref_avenelles$annual_load*100)}) 
avenelles_p70_meanbiais <- as.data.frame(do.call(cbind,avenelles_p70_bias)) %>% rowMeans

avenelles_p80_load <- lapply(avenelles_p80, function(i) {i %>% group_by(year) %>% summarise(load = sum(doc_mg.L*q_L.s*period, na.rm = T), sum_q = sum(q_L.s, na.rm = T), mean_q = mean(q_L.s, na.rm = T))})
avenelles_p80_meanload <- lapply(avenelles_p80_load, function(i) {round((i$load/i$sum_q*ref_avenelles$sum_q))}) %>% do.call(what = cbind) %>% rowMeans
avenelles_p80_bias <- lapply(avenelles_p80_load, function(i) {round(((i$load/i$sum_q*ref_avenelles$sum_q)-ref_avenelles$annual_load)/ref_avenelles$annual_load*100)}) 
avenelles_p80_meanbiais <- as.data.frame(do.call(cbind,avenelles_p80_bias)) %>% rowMeans

avenelles_p90_load <- lapply(avenelles_p90, function(i) {i %>% group_by(year) %>% summarise(load = sum(doc_mg.L*q_L.s*period, na.rm = T), sum_q = sum(q_L.s, na.rm = T), mean_q = mean(q_L.s, na.rm = T))})
avenelles_p90_meanload <- lapply(avenelles_p90_load, function(i) {round((i$load/i$sum_q*ref_avenelles$sum_q))}) %>% do.call(what = cbind) %>% rowMeans
avenelles_p90_bias <- lapply(avenelles_p90_load, function(i) {round(((i$load/i$sum_q*ref_avenelles$sum_q)-ref_avenelles$annual_load)/ref_avenelles$annual_load*100)}) 
avenelles_p90_meanbiais <- as.data.frame(do.call(cbind,avenelles_p90_bias)) %>% rowMeans

avenelles_p100_load <- lapply(avenelles_p100, function(i) {i %>% group_by(year) %>% summarise(load = sum(doc_mg.L*q_L.s*period, na.rm = T), sum_q = sum(q_L.s, na.rm = T), mean_q = mean(q_L.s, na.rm = T))})
avenelles_p100_meanload <- lapply(avenelles_p100_load, function(i) {round((i$load/i$sum_q*ref_avenelles$sum_q))}) %>% do.call(what = cbind) %>% rowMeans
avenelles_p100_bias <- lapply(avenelles_p100_load, function(i) {round(((i$load/i$sum_q*ref_avenelles$sum_q)-ref_avenelles$annual_load)/ref_avenelles$annual_load*100)}) 
avenelles_p100_meanbiais <- as.data.frame(do.call(cbind,avenelles_p100_bias)) %>% rowMeans

data.frame(
  Year = complete_years,
  "Annual load, tons" = ref_avenelles$annual_load * 1e-9,
  "Average estimated load, 10% of data" = avenelles_p10_meanload * 1e-9,
  "Average bias, 10 % of data" = avenelles_p10_meanbiais,
    "Average estimated load, 20% of data" = avenelles_p20_meanload * 1e-9,
  "Average bias, 20 % of data" = avenelles_p20_meanbiais,
    "Average estimated load, 30% of data" = avenelles_p30_meanload * 1e-9,
  "Average bias, 30 % of data" = avenelles_p30_meanbiais,
    "Average estimated load, 40% of data" = avenelles_p40_meanload * 1e-9,
  "Average bias, 40 % of data" = avenelles_p40_meanbiais,
    "Average estimated load, 50% of data" = avenelles_p50_meanload * 1e-9,
  "Average bias, 50 % of data" = avenelles_p50_meanbiais,
    "Average estimated load, 60% of data" = avenelles_p60_meanload * 1e-9,
  "Average bias, 60 % of data" = avenelles_p60_meanbiais,
    "Average estimated load, 70% of data" = avenelles_p70_meanload * 1e-9,
  "Average bias, 70 % of data" = avenelles_p70_meanbiais,
    "Average estimated load, 80% of data" = avenelles_p80_meanload * 1e-9,
  "Average bias, 80 % of data" = avenelles_p80_meanbiais,
    "Average estimated load, 90% of data" = avenelles_p90_meanload * 1e-9,
  "Average bias, 90 % of data" = avenelles_p90_meanbiais,
    "Average estimated load, 100% of data" = avenelles_p100_meanload * 1e-9,
  "Average bias, 100 % of data" = avenelles_p100_meanbiais,
  check.names = F
)  %>% knitr::kable(digits = 2) %>% kableExtra::kable_styling()


summary_df <- data.frame(
  year = complete_years,
  annual_load_ref = ref_avenelles$annual_load * 1e-9,
  annual_load_p10 = avenelles_p10_meanload * 1e-9,
  bias_p10 = avenelles_p10_meanbiais,
  annual_load_p20 = avenelles_p20_meanload * 1e-9,
  bias_p20 = avenelles_p20_meanbiais,
  annual_load_p30 = avenelles_p30_meanload * 1e-9,
  bias_p30 = avenelles_p30_meanbiais,
  annual_load_p40 = avenelles_p40_meanload * 1e-9,
  bias_p40 = avenelles_p40_meanbiais,
  annual_load_p50 = avenelles_p50_meanload * 1e-9,
  bias_p50 = avenelles_p50_meanbiais,
  annual_load_p60 = avenelles_p60_meanload * 1e-9,
  bias_p60 = avenelles_p60_meanbiais,
  annual_load_p70 = avenelles_p70_meanload * 1e-9,
  bias_p70 = avenelles_p70_meanbiais,
  annual_load_p80 = avenelles_p80_meanload * 1e-9,
  bias_p80 = avenelles_p80_meanbiais,
  annual_load_p90 = avenelles_p90_meanload * 1e-9,
  bias_p90 = avenelles_p90_meanbiais,
  annual_load_p100 = avenelles_p100_meanload * 1e-9,
  bias_p100 = avenelles_p100_meanbiais)

ggplot(summary_df,aes(x=year))+geom_line(aes(y=annual_load_ref), size = 2)+
  geom_line(aes(y=annual_load_p10, col = "10%"))+
    geom_line(aes(y=annual_load_p20, col = "20%"))+
    geom_line(aes(y=annual_load_p30, col = "30%"))+
    geom_line(aes(y=annual_load_p40, col = "40%"))+
    geom_line(aes(y=annual_load_p50, col = "50%"))+
    geom_line(aes(y=annual_load_p60, col = "60%"))+
    geom_line(aes(y=annual_load_p70, col = "70%"))+
    geom_line(aes(y=annual_load_p80, col = "80%"))+
    geom_line(aes(y=annual_load_p90, col = "90%"))+
    geom_line(aes(y=annual_load_p100, col = " 100%"))+
  scale_color_viridis_d(direction = -1)+
  labs(x= "Year", y = "Annual load, tons", col = "% of randomly sampled data",title = "Average DOC load by year depending on percentage of data included", subtitle = "Reference annual load in black")+
  scale_x_continuous(breaks = complete_years, minor_breaks = NULL)+
  theme_minimal()+
  theme(legend.position = "bottom", axis.text.x = element_text(angle = 45))

ggplot(summary_df,aes(x=year))+#geom_line(data = ref_avenelles, aes(x = year, y=mean_q/10), size = 1)+
  geom_line(aes(y=bias_p10, col = "10%"))+
    geom_line(aes(y=bias_p20, col = "20%"))+
    geom_line(aes(y=bias_p30, col = "30%"))+
    geom_line(aes(y=bias_p40, col = "40%"))+
    geom_line(aes(y=bias_p50, col = "50%"))+
    geom_line(aes(y=bias_p60, col = "60%"))+
    geom_line(aes(y=bias_p70, col = "70%"))+
    geom_line(aes(y=bias_p80, col = "80%"))+
    geom_line(aes(y=bias_p90, col = "90%"))+
  scale_color_viridis_d(direction = -1)+
  labs(x= "Year", y = "Absolute average bias,%", col = "% of randomly \n sampled data", title = "Average bias by year depending on percentage of data included", subtitle = "Average annual discharge in black")+
  scale_x_continuous(breaks = complete_years, minor_breaks = NULL)+
  scale_y_continuous(sec.axis = sec_axis(~.*10, name = "Average annual discharge, L/s"))+
  theme_minimal()+
  theme(legend.position = "bottom", axis.text.x = element_text(angle = 45))


```



## Beales ratio

```{r test-beales}
list_beales <- function(list_df){

  
    
list_load <- lapply(list_df,function(i) {i %>% group_by(year) %>% summarise(load = sum(doc_mg.L*q_L.s, na.rm = T), sum_q = sum(q_L.s, na.rm = T), mean_q = mean(q_L.s, na.rm = T), sqq = var(q_L.s))}) # génère une liste de dataframes
load_beales <- lapply(list_load, function(i) {
  i$load/i$sum_q*ref_avenelles$mean_q*60*60*24*365 * 
  ((1+(1/length(i$load-1/ref_avenelles$n_obs)*ref_avenelles$slq/(i$load*ref_avenelles$mean_q)))/
    1+ 1/length(i$load-1/ref_avenelles$n_obs)*i$sqq/sqrt(ref_avenelles$mean_q)
     )}) %>% 
  do.call(what = cbind) %>% rowMeans #Retourne un vecteur avec une valeur de flux par année
bias_beales <- lapply(list_load, function(i) {abs((load_beales-ref_avenelles$annual_load)/ref_avenelles$annual_load*100)}) #Retourne une liste de vecteurs avec les 1000 biais par année, en valeur absolue. 
mean_bias_beales <- as.data.frame(do.call(cbind,bias_beales)) %>% rowMeans #Calcule le biais moyen absolu par année    
  
return(list(load_beales = load_beales,   mean_bias_beales = mean_bias_beales))
}  
  
  
results_beales <- lapply(list_random, list_beales)
results_beales_listdf <- lapply(results_beales, as.data.frame) %>% lapply(cbind, year = complete_years)
results_beales_df <- bind_rows(results_beales_listdf, .id = "percent")


ggplot(results_beales_df,aes(x=year))+geom_line(data = ref_avenelles, aes(y=annual_load), size = 1)+
  geom_line(aes(y = load_beales, group = percent, col = percent))+
  scale_color_viridis_d(direction = -1)+
  labs(x= "Year", y = "Annual load, tons", col = "% of randomly sampled data",title = "Average DOC load by year depending on percentage of data included", subtitle = "Reference annual load in black")+
  scale_x_continuous(breaks = complete_years, minor_breaks = NULL)+
  theme_minimal()+
  theme(legend.position = "bottom", axis.text.x = element_text(angle = 45))

ggplot()+
  geom_line(data = ref_avenelles, aes(x = year, y=mean_q/3), size = 1)+
  geom_line(data = results_beales_df, aes(x=year, y=mean_bias_beales, group = percent, col = percent))+
  scale_color_viridis_d(direction = -1)+
  labs(x= "Year", y = "Average absolute bias,%", col = "% of randomly \n sampled data", title = "Average absolute bias by year depending on percentage of data included", subtitle = "Average annual discharge in black")+
  scale_x_continuous(breaks = complete_years, minor_breaks = NULL)+
  scale_y_continuous(sec.axis = sec_axis(~.*3, name = "Average annual discharge, L/s"))+
  theme_minimal()+
  theme(legend.position = "bottom", axis.text.x = element_text(angle = 45))



```

## Rating curve

```{r doc_q_rating-curve}
with(subset(avenelles, year %in% complete_years), cor(doc_mg.L, log(q_L.s), use = "pairwise.complete.obs"))

ggplot(avenelles_complete)+
  geom_point(aes(x=log(q_L.s), y = doc_mg.L, col = as.factor(year)))+
  labs(x="log(Q)", y = "DOC, mg/L", col = "Year")+
  scale_color_viridis_d()+
  theme_minimal()

doc_model <- lm(doc_mg.L~log(q_L.s), data = avenelles_complete)
summary(doc_model)

avenelles_complete$doc_predicted <- predict(doc_model, newdata = avenelles_complete)

ggplot(avenelles_complete)+
  geom_point(aes(x=doc_mg.L, y = doc_predicted, col = as.factor(year)))+
    labs(x="DOC observed", y = "DOC predicted", col = "Year")+
  scale_color_viridis_d()+
  theme_minimal()
```


```{r plot-doc-predicted, fig.dim = c(10,20)}
ggplot(avenelles_complete, aes(x = commondate))+
  geom_point(aes(y = doc_mg.L, col = "DOC, mg.L"), alpha = 0.5)+
  geom_point(aes(y = doc_predicted, col = "DOC predicted, mg.L"), alpha = 0.5)+  
  scale_x_date(labels = function(x) format(x, "%d-%b"), date_minor_breaks = "1 month", name = "")+
  scale_color_manual(values = c("palegreen4","lightblue"), name = "")+
  facet_grid(rows = vars(year))+
  labs(y = "DOC, mg/L", col = "")+
  theme_minimal(base_size = 15)+
  theme(legend.position = "bottom")


                            
```
```{r bias-rating-curve}
list_rating  <- function(list_df){
  
list_load <- lapply(list_df,function(i) {i %>% group_by(year) %>% summarise(load = sum(doc_predicted*q_L.s*period, na.rm = T), sum_q = sum(q_L.s, na.rm = T), mean_q = mean(q_L.s, na.rm = T))}) # génère une liste de dataframes
load_rating <- do.call(list_load, what = cbind) %>% rowMeans #Retourne un vecteur avec une valeur de flux par année
bias_rating <- lapply(list_load, function(i) {abs((i$load-ref_avenelles$annual_load)/ref_avenelles$annual_load*100)}) #Retourne une liste de vecteurs avec les 1000 biais par année, en valeur absolue. 
mean_bias_rating <- as.data.frame(do.call(cbind,bias_rating)) %>% rowMeans #Calcule le biais moyen absolu par année    
  
return(list(load_rating = load_rating, mean_bias_rating = mean_bias_rating))
}  
  
  
results_rating <- lapply(list_random, list_rating)
results_rating_listdf <- lapply(results_rating, as.data.frame) %>% lapply(cbind, year = complete_years)
results_rating_df <- bind_rows(results_rating_listdf, .id = "percent")


ggplot(results_rating_df,aes(x=year))+geom_line(data = ref_avenelles, aes(y=annual_load), size = 1)+
  geom_line(aes(y = load_rating, group = percent, col = percent))+
  scale_color_viridis_d(direction = -1)+
  labs(x= "Year", y = "Annual load, tons", col = "% of randomly sampled data",title = "Average DOC load by year depending on percentage of data included", subtitle = "Reference annual load in black")+
  scale_x_continuous(breaks = complete_years, minor_breaks = NULL)+
  theme_minimal()+
  theme(legend.position = "bottom", axis.text.x = element_text(angle = 45))


ggplot()+
  geom_line(data = ref_avenelles, aes(x = year, y=mean_q/5), size = 1)+
  geom_line(data = results_rating_df, aes(x=year, y=mean_bias_rating, group = percent, col = percent))+
  scale_color_viridis_d(direction = -1)+
  labs(x= "Year", y = "Average absolute bias,%", col = "% of randomly \n sampled data", title = "Average absolute bias by year depending on percentage of data included", subtitle = "Average annual discharge in black")+
  scale_x_continuous(breaks = complete_years, minor_breaks = NULL)+
  scale_y_continuous(sec.axis = sec_axis(~.*5, name = "Average annual discharge, L/s"))+
  theme_minimal()+
  theme(legend.position = "bottom", axis.text.x = element_text(angle = 45))
```

# Annual and interannual flux 

On considère que l'erreur sur DOC vient de la mesure par analyse TOC.

```{r uncertainties}
nyears <- length(complete_years)

avenelles_flux <- avenelles %>% filter(year %in% complete_years)

q_u <- 0.1

nobs <- dim(avenelles_flux)[1]
nrep <- 1000
```

## total flux

```{r compute-flux}
#doc matrix
doc_meas <- matrix(avenelles_flux$doc_mg.L, nrow = nrep, ncol = nobs, byrow = T) # repeats nrep lines with observations

doc_cv <- 3.2*doc_meas^(-0.2) # from quich check Claire, vaut pour TOC mais pas autres moyens de mesure
doc_random <- matrix(rnorm(nrep*nobs, mean = 0, sd = 1), nrow=nrep, ncol = nobs)
doc_noise <- doc_cv*doc_random
doc_mat <- doc_meas * (1 + doc_noise/100) # final value of doc, with noise in percent

# Q matrix
q_meas <- matrix(avenelles_flux$q_L.s, nrow = nrep, ncol = nobs, byrow = T) # repeats nrow_boot times the vector q_L.s
q_noise <- matrix(rnorm(nrep*nobs, mean = 0, sd = q_u), nrow = nrep, ncol = nobs) # creates a noise in percent (proportion), between 0 and 10%
q_mat <- q_meas * (1 + q_noise) # final value of q, with noise

# period matrix
period_mat <- matrix(avenelles_flux$period, nrow = nrep, ncol = nobs, byrow = T) # in seconds

# Flux per time step
flux_ton_mat <- doc_mat*1e-9*q_mat*period_mat # flux per period (period in seconds, so flux in ton/s is converted to flux per period). 
flux_ton.s_mat <- doc_mat*1e-9*q_mat # without period

index_years <- lapply(complete_years, function(y){which(avenelles_flux$year == y)}) # list of indices corresponding to each year

# Annual flux
annual_flux_ton.y <- sapply(index_years, function(idx){apply(flux_ton_mat[,idx], 1, sum, na.rm = T)}) # sum of fluxes per year, for each iteration of the bootstrap. Result is a matrix with nrow_boot rows and 19 columns (1 per year)
annual_flux_pi <- apply(annual_flux_ton.y, 2, quantile, probs = c(0.025, 0.5, 0.975), na.rm = T) # prediction interval for annual fluxes, per year. 3 lignes, 19 columns
annual_flux_mean <- colMeans(annual_flux_ton.y, na.rm = T) # mean annual flux per year. 1 vector
annual_flux_sd <- apply(annual_flux_ton.y, 2, sd, na.rm = T) # standard deviation of annual flux per year. Is just an estimate of goodness of mean, not as good as than the confidence interval. 

annual_flux_df <- data.frame(year = complete_years, 
                        annual_flux_mean = annual_flux_mean, 
                        annual_flux_variability = annual_flux_sd, 
                        annual_flux_pi_lower = annual_flux_pi[1,], 
                        annual_flux_pi_upper = annual_flux_pi[3,])

# Interannual flux 
interannual_flux_ton.y <- rowMeans(annual_flux_ton.y, na.rm = T) # mean interannual flux per iteration of the bootstrap
interannual_flux_pi <- quantile(interannual_flux_ton.y, probs = c(0.025, 0.5, 0.975), na.rm = T) # prediction interval
interannual_flux_mean <- mean(interannual_flux_ton.y, na.rm = T) # mean interannual flux
interannual_flux_variability <- sd(annual_flux_mean, na.rm = T) # standard deviation of interannual flux per year

interannual_flux_df <- data.frame(year = "interannual", annual_flux_mean = interannual_flux_mean, 
                                  annual_flux_variability = interannual_flux_variability,
                        annual_flux_pi_lower = interannual_flux_pi[1], 
                        annual_flux_pi_upper = interannual_flux_pi[3])

total_flux_df <- rbind(annual_flux_df, interannual_flux_df)
total_flux_df$group <- c(rep("annual", nyears), "interannual")

# Q df

annual_q <- sapply(index_years, function(idx){apply(q_mat[,idx], 1, sum, na.rm = T)}) # sum of fluxes per year, for each iteration of the bootstrap. Result is a matrix with nrow_boot rows and 19 columns (1 per year)
annual_q_pi <- apply(annual_q, 2, quantile, probs = c(0.025, 0.5, 0.975), na.rm = T) # prediction interval for annual fluxes, per year. 3 lignes, 19 columns
annual_q_mean <- colMeans(annual_q, na.rm = T) # mean annual flux per year. 1 vector
annual_q_sd <- apply(annual_q, 2, sd, na.rm = T) # standard deviation of annual flux per year. Is just an estimate of goodness of mean, not as good as than the confidence interval. 
interannual_q <- rowMeans(annual_q, na.rm = T) # mean interannual flux per iteration of the bootstrap
interannual_q_pi <- quantile(interannual_q, probs = c(0.025, 0.5, 0.975), na.rm = T) # prediction interval
interannual_q_mean <- mean(interannual_q, na.rm = T) # mean interannual flux
interannual_q_variability <- sd(annual_q_mean, na.rm = T) # standard deviation of interannual flux per year

q_df <- data.frame(year = c(complete_years, "interannual"), 
                        q_mean = c(annual_q_mean, interannual_q_mean),
                        q_variability = c(annual_flux_sd, interannual_q_variability), 
                        q_pi_lower = c(annual_q_pi[1,], interannual_q_pi[1]), 
                        q_pi_upper = c(annual_q_pi[3,], interannual_q_pi[3]),
                   group = c(rep("annual", nyears), "interannual"))

# Plot
ggplot()+
  geom_col(data = total_flux_df, aes(x=year, y = annual_flux_mean, fill = group))+
    geom_errorbar(data = total_flux_df, aes(x = year, ymin = annual_flux_pi_lower, ymax = annual_flux_pi_upper, col = "prediction interval"), width = 0.3, size = 0.8)+
  geom_errorbar(data = filter(total_flux_df, year == "interannual"), aes(x = year, ymin = annual_flux_mean - annual_flux_variability, ymax = annual_flux_mean + annual_flux_variability, col = "interannual variability"), width = 0.2, size = 0.8, linetype = 2)+
  scale_fill_manual(values = c("annual" = "lightblue", "interannual" = "indianred"))+
  scale_color_manual(values = c("prediction interval" = "darkblue", "interannual variability" = "darkred"), name = "")+
   labs(x = "Year", y = "Flux (ton/year)", fill = "")+
  theme_minimal(base_size = 15)+
  theme(axis.text.x = element_text(angle = 45, hjust = 1), legend.position = "bottom")

ggplot()+
  geom_col(data = q_df, aes(x=year, y = q_mean, fill = group))+
    geom_errorbar(data = q_df, aes(x = year, ymin = q_pi_lower, ymax = q_pi_upper, col = "prediction interval"), width = 0.3, size = 0.8)+
  geom_errorbar(data = filter(q_df, year == "interannual"), aes(x = year, ymin = q_mean - q_variability, ymax = q_mean + q_variability, col = "interannual variability"), width = 0.2, size = 0.8, linetype = 2)+
  scale_fill_manual(values = c("annual" = "lightblue", "interannual" = "indianred"))+
  scale_color_manual(values = c("prediction interval" = "darkblue", "interannual variability" = "darkred"), name = "")+
   labs(x = "Year", y = "Discharge (L/year)", fill = "")+
  theme_minimal(base_size = 15)+
  theme(axis.text.x = element_text(angle = 45, hjust = 1), legend.position = "bottom")

knitr::kable(total_flux_df, digits = 2, row.names = F) %>% kableExtra::kable_styling()

```

## Specific flux

```{r specific-flux}
sflux_ton_mat <- doc_mat*1e-9*q_mat*period_mat/bv # flux per period (period in seconds, so flux in ton/s is converted to flux per period). 
sflux_ton.s_mat <- doc_mat*1e-9*q_mat/bv # without period

annual_sflux_ton.y <- sapply(index_years, function(idx){apply(sflux_ton_mat[,idx], 1, sum, na.rm = T)}) # sum of fluxes per year, for each iteration of the bootstrap. Result is a matrix with nrow_boot rows and 19 columns (1 per year)
annual_sflux_pi <- apply(annual_sflux_ton.y, 2, quantile, probs = c(0.025, 0.5, 0.975), na.rm = T) # prediction interval for annual fluxes, per year. 3 lignes, 19 columns
annual_sflux_mean <- colMeans(annual_sflux_ton.y, na.rm = T) # mean annual flux per year. 1 vector
annual_sflux_sd <- apply(annual_sflux_ton.y, 2, sd, na.rm = T) # standard deviation of annual flux per year. Is just an estimate of goodness of mean, not as good as than the confidence interval. 

annual_sflux_df <- data.frame(year = complete_years, 
                        annual_flux_mean = annual_sflux_mean, 
                        annual_flux_variability = annual_sflux_sd, 
                        annual_flux_pi_lower = annual_sflux_pi[1,], 
                        annual_flux_pi_upper = annual_sflux_pi[3,])

# Interannual flux 
interannual_sflux_ton.y <- rowMeans(annual_sflux_ton.y, na.rm = T) # mean interannual flux per iteration of the bootstrap
interannual_sflux_pi <- quantile(interannual_sflux_ton.y, probs = c(0.025, 0.5, 0.975), na.rm = T) # prediction interval
interannual_sflux_mean <- mean(interannual_sflux_ton.y, na.rm = T) # mean interannual flux
interannual_sflux_variability <- sd(annual_sflux_mean, na.rm = T) # standard deviation of interannual flux per year

interannual_sflux_df <- data.frame(year = "interannual", annual_flux_mean = interannual_sflux_mean, 
                                  annual_flux_variability = interannual_sflux_variability,
                        annual_flux_pi_lower = interannual_sflux_pi[1], 
                        annual_flux_pi_upper = interannual_sflux_pi[3])

total_sflux_df <- rbind(annual_sflux_df, interannual_sflux_df)
total_sflux_df$group <- c(rep("annual", nyears), "interannual")

ggplot()+
  geom_col(data = total_sflux_df, aes(x=year, y = annual_flux_mean, fill = group), width = 0.8)+
    geom_errorbar(data = total_sflux_df, aes(x = year, ymin = annual_flux_pi_lower, ymax = annual_flux_pi_upper, col = "prediction interval"), width = 0.3, size = 0.8)+
  geom_errorbar(data = filter(total_sflux_df, year == "interannual"), aes(x = year, ymin = annual_flux_mean - annual_flux_variability, ymax = annual_flux_mean + annual_flux_variability, col = "interannual variability"), width = 0.2, size = 0.8, linetype = 2)+
  scale_fill_manual(values = c("annual" = "lightblue", "interannual" = "indianred"))+
  scale_color_manual(values = c("prediction interval" = "darkblue", "interannual variability" = "darkred"), name = "")+
   labs(x = "Year", y = "Flux (tons/km2/year)", fill = "")+
  theme_minimal(base_size = 15)+
  theme(axis.text.x = element_text(angle = 45, hjust = 1), legend.position = "bottom")

ggsave("sflux_avenelles.svg")

knitr::kable(total_sflux_df, digits = 2, row.names = F) %>% kableExtra::kable_styling()
```


