---
title: "Galabre"
output: 
  html_document:
    code_folding: hide
date: "2025-06-20"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = F, warning = F, error = F, fig.align = "center", collapse = T,
                      cache = T)
```

```{r libraries}

library(ggplot2)
library(ggpubr)
library(dplyr)
library(readxl)
library(lubridate)

#for gnls
library(nlme)

```


# Data

## Load 

Sur BDOH les chroniques de débit et MES sont disponibles jusqu'à 2019.


```{r load-data}
crues <- readxl::read_xlsx(path = "galabre.xlsx", sheet = "Crues") 
crues$mes_for_fit <- crues$mes_g.L 

mes <- readxl::read_xlsx(path = "galabre.xlsx", sheet = "SSC", col_types = c("date","numeric")) 

debit <- readxl::read_xlsx(path = "galabre.xlsx", sheet = "Debit", col_types = c("date","numeric")) 

galabre_old <- merge(debit, mes, by = "DateHeure") %>% unique() # 4 duplicated in 2017, no q

galabre_new <- readxl::read_xlsx(path = "Galabre_outlet.xlsx", sheet = "Galabre_outlet_noduplicated") %>% unique() # 2019 was duplicated (also in galabre_old). Some duplicated still exist, removed by "unique"

galabre_tot <- rbind(galabre_old, galabre_new)

#galabre_tot[which(duplicated(galabre_tot$DateHeure) == T), ] %>% View()

galabre <- merge(galabre_tot, crues, by = "DateHeure", all = T)  
galabre$year <- year(galabre$DateHeure)
galabre$commondate <- as.Date(paste0("2000-", format(galabre$DateHeure,"%j")), "%Y-%j")
galabre$period <- as.numeric(-(galabre$DateHeure - lead(galabre$DateHeure))) # period in s

# from galabre

summary_galabre <- merge(
galabre %>% subset(!is.na(poc_percent)) %>% group_by(year) %>% summarise(nb_poc = n()),
galabre %>% subset(!is.na(cmes_g.L)) %>% group_by(year) %>% summarise(nb_cmes = n()),
by = "year", all = T) %>% 
  merge(galabre %>% subset(!is.na(q_m3.s)) %>% group_by(year) %>% summarise(nb_q = n()), by = "year", all = T) %>%
  merge(galabre %>% subset(!is.na(period)) %>% group_by(year) %>% summarise(total_period_j = round(sum(period)/(24*60*60))), by = "year", all = T)
  
summary_galabre %>% knitr::kable(caption = "Nombre d'observations de DOC, POC, CMES et débit par an") %>% kableExtra::kable_styling()

```


## Explore data

```{r mes-poc}
galabre$poc_g.L <- galabre$mes_g.L * galabre$poc_percent / 100


ggplot(galabre)+geom_point(aes(x=mes_g.L, y = poc_percent, col = crue, shape = crue))+
  scale_color_viridis_d()+
  labs(x = "MES, g/L", y = "POC, %", col = "", shape = "")+
  lims(y=c(0,2))+
  theme_minimal()+
  theme(legend.position = "bottom")


ggplot(galabre, aes(x=log10(mes_g.L), y = log10(poc_percent)))+geom_point(aes(col = crue))+
  scale_color_viridis_d()+
  facet_grid(cols = vars(Saison))+
  geom_smooth(se = T, method = "lm")+
  theme_minimal()+
  theme(legend.position = "bottom")
```

```{r annual-q-mes, fig.dim = c(10, 15)}

ggarrange(
ggplot(galabre, aes(x = commondate)) + 
  geom_point(aes(y = q_m3.s), col = "lightblue", size = 0.5) +
  scale_x_date(labels = function(x) format(x, "%d-%b"), date_minor_breaks = "1 month", name = "")+
  facet_grid(rows = vars(year))+
  labs(x = "", y = "Q, m3/s") +
  theme_minimal()+
  theme(legend.position = "bottom"),

ggplot(galabre, aes(x = commondate)) + 
  geom_point(aes(y = cmes_g.L), col = "palegreen4", size = 0.5) +
  scale_x_date(labels = function(x) format(x, "%d-%b"), date_minor_breaks = "1 month", name = "")+
  facet_grid(rows = vars(year))+
  labs(x = "", y = "CMES, g/L") +
  theme_minimal()+
  theme(legend.position = "bottom"),

ncol = 2
)

```
## Regression MES (POC) and CMES

```{r mes-cmes}
galabre[which(galabre$cmes_g.L == galabre$mes_g.L), ] # only 6, including 4 zero -> can be used for mes_u

fit_mes <- lm(Cmes_g.L~mes_g.L, data = galabre)
summary(fit_mes)

cmes_u <- summary(fit_mes)$coef[2,2] # standard error on cmes

ggplot(galabre) + geom_point(aes(x=cmes_g.L, y = mes_g.L, col = crue, shape = crue))+
  scale_color_viridis_d()+
  scale_shape_manual(values = c(1,2,3,4,5,6,7,8,9,10,11))+
  geom_abline(slope = 1, intercept =0, col ="darkred")+
  geom_abline(intercept = coef(fit_mes)[1], slope = coef(fit_mes)[2], linetype = 2)+
  xlim(0,200)+
  theme_minimal()

ggplot(galabre) + geom_point(aes(x=cmes_g.L, y = mes_g.L, col = crue, shape = crue))+
  scale_color_viridis_d()+
  scale_shape_manual(values = c(1,2,3,4,5,6,7,8,9,10,11))+
  geom_abline(slope = 1, intercept =0, col ="darkred")+
  geom_abline(intercept = coef(fit_mes)[1], slope = coef(fit_mes)[2], linetype = 2)+
  xlim(0,50)+ylim(0,50)+
  theme_minimal()

ggplot(galabre) + geom_point(aes(x=cmes_g.L, y = mes_g.L, col = crue, shape = crue))+
  scale_color_viridis_d()+
  scale_shape_manual(values = c(1,2,3,4,5,6,7,8,9,10,11))+
  geom_abline(slope = 1, intercept =0, col ="darkred")+
  geom_abline(intercept = coef(fit_mes)[1], slope = coef(fit_mes)[2], linetype = 2)+
  xlim(0,10)+ylim(0,10)+
  theme_minimal()

```



# Fit MES POC

mes_for_fit in mg/L.

q in m3/s.

## Fit all events

```{r prepare-df}
poc_galabre <- galabre %>% filter(!is.na(poc_percent)) %>% mutate(mes_for_fit = mes_g.L) %>% filter(!is.na(mes_for_fit) & mes_for_fit !=0) # has to be !=0 for the bootstrap

```


### NLS

```{r get-starting-values}


fit_linear <- lm(log(poc_percent)~log(mes_g.L), data = subset(crues, !is.na(poc_percent) & !is.na(mes_g.L) & poc_percent != 0 & mes_g.L != 0)) 

start_a <- exp(coef(fit_linear)[1])
start_b <- coef(fit_linear)[2]

ggplot(poc_galabre)+
  geom_point(aes(x=log(mes_g.L), y = log(poc_percent), col = "measured"))+ 
  labs(x = "MES, mg/L", y = "POC, %")+
  geom_abline(slope = coef(fit_linear)[2], intercept = coef(fit_linear)[1], linetype = 2)+
  scale_color_manual(values = c("lightblue"))+
  theme_minimal()+
  theme(legend.position = "none")

```

```{r fit-poc-mes-nls}

# find asymptotic value
aspt_value <- poc_galabre[order(poc_galabre$mes_g.L, decreasing = T),] %>% pull(poc_percent) %>% head(dim(crues)[1]/10) %>% median() # 10% of poc_percent corresponding to the max cmes

# add mes for POC 2011
poc_galabre$mes_for_fit <- poc_galabre$mes_g.L
poc_galabre$aspt <- aspt_value

# nls avec aspt
pocfit <- nls(
  poc_percent ~ a * mes_for_fit^b + aspt,
  data = subset(poc_galabre, !is.na(poc_percent) & !is.na(mes_for_fit) & poc_percent != 0 & mes_g.L != 0),
  start = list(a = start_a, b = start_b)
)

summary(pocfit)
poc_galabre$poc_nls_fitted <- predict(pocfit, poc_galabre)

formula_pocfit <- paste("NLS : POC =", round(coef(pocfit)[1],2), "* MES (mg/L) ^", round(coef(pocfit)[2],2), "+", round(aspt_value,2))

ggplot(poc_galabre)+
  geom_point(aes(x=mes_for_fit, y = poc_percent, col = "measured"))+ 
  geom_point(aes(x=mes_for_fit, y = poc_nls_fitted, col = "fitted"))+ 
  geom_abline(slope = 0, intercept = aspt_value, col = "darkred")+
  annotate(geom = "label", label = formula_pocfit, x = Inf, y = Inf, hjust = 1.1, vjust = 1.1)+
  scale_color_manual(values = c("darkblue", "lightblue"))+
  labs(x = "MES, mg/L", y = "POC, %")+
  theme_minimal()

plot(pocfit)

# nls sans aspt
pocfitnas <- nls(
  poc_percent ~ a * mes_for_fit^b,
  data = subset(poc_galabre, !is.na(poc_percent) & !is.na(mes_for_fit) & poc_percent != 0 & mes_g.L != 0),
  start = list(a = start_a, b = start_b)
)

summary(pocfitnas)
poc_galabre$poc_nls_fitted <- predict(pocfitnas, poc_galabre)

formula_pocfitnas <- paste("NLS : POC =", round(coef(pocfitnas)[1],2), "* MES (mg/L) ^", round(coef(pocfitnas)[2],2))

ggplot(poc_galabre)+
  geom_point(aes(x=mes_for_fit, y = poc_percent, col = "measured"))+ 
  geom_point(aes(x=mes_for_fit, y = poc_nls_fitted, col = "fitted"))+ 
  geom_abline(slope = 0, intercept = aspt_value, col = "darkred")+
  annotate(geom = "label", label = formula_pocfitnas, x = Inf, y = Inf, hjust = 1.1, vjust = 1.1)+
  scale_color_manual(values = c("darkblue", "lightblue"))+
  labs(x = "MES, mg/L", y = "POC, %")+
  theme_minimal()

plot(pocfitnas)

```
#### NLS Bootstrap

```{r nls-bootstrap-with-aspt}

n_boot <- 1000
n_obs <- nrow(poc_galabre)

coefs_wboot_nls <- matrix(NA, nrow = n_boot, ncol = 2, dimnames = list(NULL, c("a","b")))


for(i in seq_len(n_boot)){
  
  weights <- sample(c(-1,1), size = length(residuals(pocfit)), replace = T)
  resid_wboot <- residuals(pocfit) * weights
  
  y_wboot <- fitted(pocfit) + resid_wboot
  
  df_wboot <- poc_galabre %>% mutate(poc_percent = y_wboot)
  
  tryCatch(
    {pocfit_wb <- nls(
      poc_percent~a*mes_for_fit^b+aspt,
      data = df_wboot,
      start = coef(pocfit))
    coefs_wboot_nls[i,] <- coef(pocfit_wb)}, 
    error = function(e) NULL) 
}

coefs_wboot_nls <- na.omit(coefs_wboot_nls) 
length(coefs_wboot_nls)
apply(coefs_wboot_nls, 2, quantile, probs = c(0.025, 0.975)) #ic coef


ggplot(as.data.frame(coefs_wboot_nls))+
  geom_point(aes(x = a, y = b))+
  theme_minimal()+
  theme(legend.position = "none")


fitted_wboot_nls <- apply(coefs_wboot_nls, 1, function(p){p["a"] * poc_galabre$mes_for_fit^p["b"] + aspt_value}) # les MC worlds sont en colonne

fitted_wboot_nls_ic <- apply(fitted_wboot_nls, 1, quantile,
                 probs = c(0.025, 0.5, 0.975), na.rm = TRUE)
fitted_wboot_nls_mean <- apply(fitted_wboot_nls, 1, mean)

poc_galabre_wboot_nls <- poc_galabre %>% mutate(poc_fitted = fitted_wboot_nls_mean, upr = fitted_wboot_nls_ic[3, ], lwr = fitted_wboot_nls_ic[1,])

ggplot(poc_galabre_wboot_nls)+
  geom_point(aes(x=mes_for_fit, y = poc_percent, col = "measured", shape = "measured"))+ 
  geom_point(aes(x=mes_for_fit, y = poc_fitted, col = "fitted", shape = "fitted"))+ 
  geom_ribbon(aes(x = mes_for_fit, ymin = lwr, ymax = upr), fill = "gray80", alpha = 0.5)+
  geom_abline(slope = 0, intercept = aspt_value, col = "darkred")+
  annotate(geom = "label", label = formula_pocfit, x = Inf, y = Inf, hjust = 1.1, vjust = 1.1)+
  scale_color_manual(values = c("darkblue", "lightblue"))+
  labs(x = "MES, g/L", y = "POC, %", colour = "", shape = "", title = "POC% measured and fitted vs MES measured",subtitle = "Confidence interval in grey")+
  theme_minimal()

ggplot(poc_galabre_wboot_nls, aes(x=poc_percent))+
  geom_point(aes(y=poc_fitted), col = "darkblue")+ 
  geom_errorbar(aes(ymin = lwr, ymax = upr), col = "gray80", alpha = 0.5)+
  geom_abline(slope = 1, intercept = 0, col = "darkred")+
  annotate(geom = "label", label = formula_pocfit, x = Inf, y = Inf, hjust = 1.1, vjust = 1.1)+
  labs(x = "POC measured", y = "POC fitted", colour = "", shape = "", title = "POC fitted vs measured",subtitle = "Confidence interval in grey")+
  theme_minimal()

```

```{r nls-bootstrap-no-aspt}

n_boot <- 1000
n_obs <- nrow(poc_galabre)

coefs_wboot_nls <- matrix(NA, nrow = n_boot, ncol = 2, dimnames = list(NULL, c("a","b")))


for(i in seq_len(n_boot)){
  
  weights <- sample(c(-1,1), size = length(residuals(pocfit)), replace = T)
  resid_wboot <- residuals(pocfit) * weights
  
  y_wboot <- fitted(pocfitnas) + resid_wboot
  
  df_wboot <- poc_galabre %>% mutate(poc_percent = y_wboot)
  
  tryCatch(
    {pocfit_wb <- nls(
      poc_percent~a*mes_for_fit^b,
      data = df_wboot,
      start = coef(pocfit))
    coefs_wboot_nls[i,] <- coef(pocfit_wb)}, 
    error = function(e) NULL) 
}

coefs_wboot_nls <- na.omit(coefs_wboot_nls) 
length(coefs_wboot_nls)
apply(coefs_wboot_nls, 2, quantile, probs = c(0.025, 0.975)) #ic coef


ggplot(as.data.frame(coefs_wboot_nls))+
  geom_point(aes(x = a, y = b))+
  theme_minimal()+
  theme(legend.position = "none")


fitted_wboot_nls <- apply(coefs_wboot_nls, 1, function(p){p["a"] * poc_galabre$mes_for_fit^p["b"]}) # les MC worlds sont en colonne

fitted_wboot_nls_ic <- apply(fitted_wboot_nls, 1, quantile,
                 probs = c(0.025, 0.5, 0.975), na.rm = TRUE)
fitted_wboot_nls_mean <- apply(fitted_wboot_nls, 1, mean)

poc_galabre_wboot_nls <- poc_galabre %>% mutate(poc_fitted = fitted_wboot_nls_mean, upr = fitted_wboot_nls_ic[3, ], lwr = fitted_wboot_nls_ic[1,])

ggplot(poc_galabre_wboot_nls)+
  geom_point(aes(x=mes_for_fit, y = poc_percent, col = "measured", shape = "measured"))+ 
  geom_point(aes(x=mes_for_fit, y = poc_fitted, col = "fitted", shape = "fitted"))+ 
  geom_ribbon(aes(x = mes_for_fit, ymin = lwr, ymax = upr), fill = "gray80", alpha = 0.5)+
  geom_abline(slope = 0, intercept = aspt_value, col = "darkred")+
  annotate(geom = "label", label = formula_pocfit, x = Inf, y = Inf, hjust = 1.1, vjust = 1.1)+
  scale_color_manual(values = c("darkblue", "lightblue"))+
  labs(x = "MES, g/L", y = "POC, %", colour = "", shape = "", title = "POC% measured and fitted vs MES measured",subtitle = "Confidence interval in grey")+
  theme_minimal()

ggplot(poc_galabre_wboot_nls, aes(x=poc_percent))+
  geom_point(aes(y=poc_fitted), col = "darkblue")+ 
  geom_errorbar(aes(ymin = lwr, ymax = upr), col = "gray80", alpha = 0.5)+
  geom_abline(slope = 1, intercept = 0, col = "darkred")+
  annotate(geom = "label", label = formula_pocfit, x = Inf, y = Inf, hjust = 1.1, vjust = 1.1)+
  labs(x = "POC measured", y = "POC fitted", colour = "", shape = "", title = "POC fitted vs measured",subtitle = "Confidence interval in grey")+
  theme_minimal()

```


### GNLS

#### Model

```{r fit-poc-mes-gnls}

# on utilise les valeurs de pocfit NLS comme coefficients initiaux

pocfitg <- gnls(
  model = poc_percent ~ a*mes_for_fit^b + aspt,
  data = select(poc_galabre, c(mes_for_fit, poc_percent, aspt)), #select columns to avoid NA in other columns - makes gnls unhappy
  params = list(a~1, b~1),
  start = list(a = coef(pocfit)[1], b = coef(pocfit)[2]),
  weights = varPower(value = 1, form = ~ fitted(.)),
#  control = gnlsControl(nlsTol = 1e-3, tolerance = 1e-4)
)

formula_pocfitg <- paste("GNLS:", round(coef(pocfitg)[1], 3), "x MES ^", round(coef(pocfitg)[2],3), "+", round(aspt_value, 3), sep = "")

poc_galabre$poc_gnls_fitted <- predict(pocfitg, poc_galabre)

ggplot(poc_galabre)+
  geom_point(aes(x=mes_for_fit, y = poc_percent, col = "measured"))+ 
  geom_point(aes(x=mes_for_fit, y = poc_gnls_fitted, col = "fitted"))+ 
  geom_abline(slope = 0, intercept = aspt_value, col = "darkred")+
  annotate(geom = "label", label = formula_pocfitg, x = Inf, y = Inf, hjust = 1.1, vjust = 1.1)+
  scale_color_manual(values = c("darkblue", "lightblue"))+
  labs(x = "MES, mg/L", y = "POC, %")+
  theme_minimal()

plot(pocfitg)

# Sans asymptote

pocfitgnas <- gnls(
  model = poc_percent ~ a*mes_for_fit^b,
  data = select(poc_galabre, c(mes_for_fit, poc_percent, aspt)), #select columns to avoid NA in other columns - makes gnls unhappy
  params = list(a~1, b~1),
  start = list(a = coef(pocfitnas)[1], b = coef(pocfitnas)[2]),
  weights = varPower(value = 1, form = ~ fitted(.)),
#  control = gnlsControl(nlsTol = 1e-3, tolerance = 1e-4)
)

formula_pocfitgnas <- paste("GNLS:", round(coef(pocfitgnas)[1], 3), "x MES ^", round(coef(pocfitgnas)[2],3), "+", round(aspt_value, 3), sep = "")

poc_galabre$poc_gnls_fitted <- predict(pocfitg, poc_galabre)

ggplot(poc_galabre)+
  geom_point(aes(x=mes_for_fit, y = poc_percent, col = "measured"))+ 
  geom_point(aes(x=mes_for_fit, y = poc_gnls_fitted, col = "fitted"))+ 
  geom_abline(slope = 0, intercept = aspt_value, col = "darkred")+
  annotate(geom = "label", label = formula_pocfitg, x = Inf, y = Inf, hjust = 1.1, vjust = 1.1)+
  scale_color_manual(values = c("darkblue", "lightblue"))+
  labs(x = "MES, mg/L", y = "POC, %")+
  theme_minimal()

plot(pocfitg)
```


#### GNLS bootstrap

```{r intervalles-de-confiance-bootstrap}
n_boot <- 1000
n_obs <- nrow(poc_galabre)

coefs_boot <- matrix(NA, nrow = n_boot, ncol = 2, dimnames = list(NULL, c("a","b")))
                     

for(i in seq_len(n_boot)){
  
  idx_boot <- sample(n_obs, replace = T)
  df_boot <- poc_galabre[idx_boot, c("mes_for_fit","poc_percent","aspt")]
  
  tryCatch(
    {fit_init <- nls(
      poc_percent ~ a * mes_for_fit^b + aspt,
      data = df_boot,
      start = coef(pocfitg))
      # fit init is necessary to find the correct starting values for gnls. Otherwise, too much convergence result in extreme values in a and b

      pocfit_bg <- gnls(
      poc_percent~a*mes_for_fit^b+aspt,
      data = df_boot,
      start = coef(fit_init),
      weights = varPower(form = ~fitted(.)),
      control = gnlsControl(nlsTol = 1e-3, tolerance = 1e-4, maxIter = 200))
      
      coefs_boot[i,] <- coef(pocfit_bg)
      }, 
    error = function(e) NULL) 
}

coefs_boot <- na.omit(coefs_boot)
length(coefs_boot)
apply(coefs_boot, 2, quantile, probs = c(0.025, 0.975)) #ic coef



ggplot(as.data.frame(coefs_boot))+
  geom_point(aes(x = a, y = b))+
  theme_minimal()+
  theme(legend.position = "none")

mes_for_fit <- poc_galabre$mes_for_fit
fitted_boot <- apply(coefs_boot, 1, function(p){p["a"] * mes_for_fit^p["b"] + aspt_value}) # les MC worlds sont en colonne

fitted_boot_ic <- apply(fitted_boot, 1, quantile,
                 probs = c(0.025, 0.5, 0.975), na.rm = TRUE)
fitted_boot_mean <- apply(fitted_boot, 1, mean)

poc_galabre_boot <- poc_galabre %>% mutate(poc_fitted = fitted_boot_mean, upr = fitted_boot_ic[3, ], lwr = fitted_boot_ic[1,])

ggplot(poc_galabre_boot)+
  geom_point(aes(x=mes_for_fit, y = poc_percent, col = "measured", shape = "measured"))+ 
  geom_point(aes(x=mes_for_fit, y = poc_fitted, col = "fitted", shape = "fitted"))+ 
  geom_ribbon(aes(x = mes_for_fit, ymin = lwr, ymax = upr), fill = "gray80", alpha = 0.5)+
  geom_abline(slope = 0, intercept = aspt_value, col = "darkred")+
  annotate(geom = "label", label = formula_pocfitg, x = Inf, y = Inf, hjust = 1.1, vjust = 1.1)+
  scale_color_manual(values = c("darkblue", "lightblue"))+
  labs(x = "MES, mg/L", y = "POC, %", colour = "", shape = "", title = "POC% measured and fitted vs MES measured",subtitle = "Confidence interval in grey")+
  theme_minimal()

ggplot(poc_galabre_boot, aes(x=poc_percent))+
  geom_point(aes(y=poc_fitted), col = "darkblue")+ 
  geom_errorbar(aes(ymin = lwr, ymax = upr), col = "gray80", alpha = 0.5)+
  geom_abline(slope = 1, intercept = 0, col = "darkred")+
  annotate(geom = "label", label = formula_pocfitg, x = Inf, y = Inf, hjust = 1.1, vjust = 1.1)+
  labs(x = "POC measured", y = "POC fitted", colour = "", shape = "", title = "POC fitted vs measured",subtitle = "Confidence interval in grey")+
  theme_minimal()
```

```{r intervalles-de-confiance-bootstrap-nas}
n_boot <- 1000
n_obs <- nrow(poc_galabre)

coefs_boot_nas <- matrix(NA, nrow = n_boot, ncol = 2, dimnames = list(NULL, c("a","b")))
                     

for(i in seq_len(n_boot)){
  
  idx_boot <- sample(n_obs, replace = T)
  df_boot <- poc_galabre[idx_boot, c("mes_for_fit","poc_percent","aspt")]
  
  tryCatch(
    {fit_init <- nls(
      poc_percent ~ a * mes_for_fit^b,
      data = df_boot,
      start = coef(pocfitgnas))
      # fit init is necessary to find the correct starting values for gnls. Otherwise, too much convergence result in extreme values in a and b

      pocfit_bg <- gnls(
      poc_percent~a*mes_for_fit^b,
      data = df_boot,
      start = coef(fit_init),
      weights = varPower(form = ~fitted(.)),
      control = gnlsControl(nlsTol = 1e-3, tolerance = 1e-4, maxIter = 200))
      
      coefs_boot_nas[i,] <- coef(pocfit_bg)
      }, 
    error = function(e) NULL) 
}

coefs_boot_nas <- na.omit(coefs_boot_nas)
length(coefs_boot_nas)
apply(coefs_boot_nas, 2, quantile, probs = c(0.025, 0.975)) #ic coef



ggplot(as.data.frame(coefs_boot_nas))+
  geom_point(aes(x = a, y = b))+
  theme_minimal()+
  theme(legend.position = "none")

fitted_boot_nas <- apply(coefs_boot_nas, 1, function(p){p["a"] * poc_galabre$mes_for_fit^p["b"]}) # les MC worlds sont en colonne

fitted_boot_nas_ic <- apply(fitted_boot_nas, 1, quantile,
                 probs = c(0.025, 0.5, 0.975), na.rm = TRUE)
fitted_boot_nas_mean <- apply(fitted_boot_nas, 1, mean)

poc_galabre_boot_nas <- poc_galabre %>% mutate(poc_fitted = fitted_boot_nas_mean, upr = fitted_boot_nas_ic[3, ], lwr = fitted_boot_nas_ic[1,])

ggplot(poc_galabre_boot_nas)+
  geom_point(aes(x=mes_for_fit, y = poc_percent, col = "measured", shape = "measured"))+ 
  geom_point(aes(x=mes_for_fit, y = poc_fitted, col = "fitted", shape = "fitted"))+ 
  geom_ribbon(aes(x = mes_for_fit, ymin = lwr, ymax = upr), fill = "gray80", alpha = 0.5)+
  geom_abline(slope = 0, intercept = aspt_value, col = "darkred")+
  annotate(geom = "label", label = formula_pocfitgnas, x = Inf, y = Inf, hjust = 1.1, vjust = 1.1)+
  scale_color_manual(values = c("darkblue", "lightblue"))+
  labs(x = "MES, mg/L", y = "POC, %", colour = "", shape = "", title = "POC% measured and fitted vs MES measured",subtitle = "Confidence interval in grey")+
  theme_minimal()

ggplot(poc_galabre_boot_nas, aes(x=poc_percent))+
  geom_point(aes(y=poc_fitted), col = "darkblue")+ 
  geom_errorbar(aes(ymin = lwr, ymax = upr), col = "gray80", alpha = 0.5)+
  geom_abline(slope = 1, intercept = 0, col = "darkred")+
  annotate(geom = "label", label = formula_pocfitgnas, x = Inf, y = Inf, hjust = 1.1, vjust = 1.1)+
  labs(x = "POC measured", y = "POC fitted", colour = "", shape = "", title = "POC fitted vs measured",subtitle = "Confidence interval in grey")+
  theme_minimal()
```

```{r comparaison-nls-gnls}

par(mfrow = c(2, 2))

# nls : les résidus montrent un pattern en éventail
plot(fitted(pocfit), residuals(pocfit),
     main = "Résidus nls (non pondérés)",
     xlab = "Fitted", ylab = "Résidus")
abline(h = 0, col = "red")

# gnls : les résidus normalisés sont homoscédastiques
plot(fitted(pocfitg), residuals(pocfitg, type = "normalized"),
     main = "Résidus gnls (normalisés)",
     xlab = "Fitted", ylab = "Résidus normalisés")
abline(h = 0, col = "red")
       
# nls : les résidus montrent un pattern en éventail
plot(fitted(pocfitnas), residuals(pocfitnas),
     main = "Résidus nls (non pondérés)",
     xlab = "Fitted", ylab = "Résidus")
abline(h = 0, col = "red")

# gnls : les résidus normalisés sont homoscédastiques
plot(fitted(pocfitgnas), residuals(pocfitgnas, type = "normalized"),
     main = "Résidus gnls (normalisés)",
     xlab = "Fitted", ylab = "Résidus normalisés")
abline(h = 0, col = "red")       
       

```
### NLS extension to Galabre

No difference of residuals between gnls and nls + 2/3 of mes_for_fit are 0


```{r nls-extention-galabre-aspt}

# prepare dataframe
with(galabre, sum(mes_for_fit == 0 | is.na(mes_for_fit), na.rm = T)) # 144 -> removed from df because model unstable with zero (when 0^(-b))
galabre_nls <- galabre %>% filter(mes_for_fit != 0 & !is.na(mes_for_fit))


galabre_nls$aspt <- aspt_value # from nls fitting
nrow_galabre <- nrow(galabre_nls)
nrow_boot <- nrow(coefs_wboot_nls) # number of bootstrap for the NLS coefficients

# predict POC pour mes > 0
galabre_nls$poc_fitted <- predict(pocfit, newdata = galabre_nls) 


# Prediction interval
mes_mat_nls <- matrix(NA_real_, nrow = nrow_boot, ncol = nrow_galabre)

for(i in 1:nrow_galabre){
  mes_mat_nls[,i] <-rnorm(nrow_boot, mean = galabre_nls$mes_for_fit[i], sd = mes_u) # chaque colonne de la matrice correspond à une observation de MES
}


## model function 
f <- function(x, a, b){
  a * x ^ b + aspt_value
}

## paramètres de variance
sigma_nls <- summary(pocfit)$sigma


### Matrice de prédictions, sans bruit

mu_nls <- matrix(NA_real_, nrow = nrow_boot, ncol = nrow_galabre)
for(i in 1:nrow_boot){
   mu_nls[i,] <- with(as.list(coefs_wboot_nls[i,]), # listing the coefficients allows to have 2 named numbers to be used in the function
                      f(mes_mat_nls[i, ], a, b))
}


galabre_nls$poc_var_mean <- apply(mu_nls, 2, var) # variance of fit parameters + MES 

# adds noise
noise_mat_nls <- matrix(rnorm(nrow_boot*nrow_galabre, mean = 0, sd = sigma_nls), nrow = nrow_boot, ncol = nrow_galabre)

pred_nls <- mu_nls + noise_mat_nls

### computes variance, y-wise
galabre_nls$poc_var_tot <- apply(pred_nls, 2, var) # total variance per prediction, for prediction total uncertainty

## computes prediction interval 
pi <- t(
  apply(pred_nls, 2, quantile, probs = c(0.025, 0.975), na.rm = T)
)

colnames(pi) <- c("lower", "upper")

boot_pred_nls <- colMeans(pred_nls, na.rm = T)

## insert in galabre_for_nls

galabre_nls <- galabre_nls %>% mutate(poc_boot_pred = boot_pred_nls,
                          poc_pred_lower = pi[,1],
                          poc_pred_upper = pi[,2])

# plot

ggplot(galabre_nls, aes(x = mes_for_fit))+
  geom_line(aes(y = poc_pred_lower), col = "black")+
  geom_line(aes(y = poc_pred_upper), col = "black")+
  geom_point(aes(y = poc_percent, col = "measured"), alpha = 0.5)+
  geom_point(aes(y = poc_fitted, col = "fitted with all events"), size = 2)+
  geom_point(aes(y = poc_boot_pred, col ="poc_boot_pred"), alpha = 0.5, size = 1)+
  scale_color_manual(values = c("darkblue","gray50","lightblue"))+
  geom_abline(slope = 0, intercept = aspt_value, col = "darkred")+
  annotate(geom = "label", label = formula_pocfit, x = Inf, y = Inf, hjust = 1.1, vjust = 1.1)+
  labs(x = "MES, g/L", y = "POC, %", colour = "", shape = "", title = "POC predicted from MES",subtitle = "Prediction interval in grey")+
  theme_minimal()+
  theme(legend.position = "bottom")

```
```{r nls-extention-galabre-no-aspt}

# prepare dataframe
with(galabre, sum(mes_for_fit == 0 | is.na(mes_for_fit), na.rm = T)) # 144 -> removed from df because model unstable with zero (when 0^(-b))
galabre_nls_nas <- galabre %>% filter(mes_for_fit != 0 & !is.na(mes_for_fit))

nrow_galabre <- nrow(galabre_nls_nas)
nrow_boot <- nrow(coefs_wboot_nls) # number of bootstrap for the NLS coefficients

# predict POC pour mes > 0
galabre_nls_nas$poc_fitted <- predict(pocfitnas, newdata = galabre_nls_nas) 


# Prediction interval
mes_mat_nls <- matrix(NA_real_, nrow = nrow_boot, ncol = nrow_galabre)

for(i in 1:nrow_galabre){
  mes_mat_nls[,i] <-rnorm(nrow_boot, mean = galabre_nls_nas$mes_for_fit[i], sd = mes_u) # chaque colonne de la matrice correspond à une observation de MES
}


## model function 
f <- function(x, a, b){
  a * x ^ b
}

## paramètres de variance
sigma_nls <- summary(pocfit)$sigma


### Matrice de prédictions, sans bruit


mu_nls <- matrix(NA_real_, nrow = nrow_boot, ncol = nrow_galabre)
for(i in 1:nrow_boot){
   mu_nls[i,] <- with(as.list(coefs_wboot_nls[i,]), # listing the coefficients allows to have 2 named numbers to be used in the function
                      f(mes_mat_nls[i, ], a, b))
}


galabre_nls_nas$poc_var_mean <- apply(mu_nls, 2, var) # variance of fit parameters + MES 

# adds noise
noise_mat_nls <- matrix(rnorm(nrow_boot*nrow_galabre, mean = 0, sd = sigma_nls), nrow = nrow_boot, ncol = nrow_galabre)

pred_nls <- mu_nls + noise_mat_nls

### computes variance, y-wise
galabre_nls_nas$poc_var_tot <- apply(pred_nls, 2, var) # total variance per prediction, for prediction total uncertainty

## computes prediction interval 
pi <- t(
  apply(pred_nls, 2, quantile, probs = c(0.025, 0.975), na.rm = T)
)

colnames(pi) <- c("lower", "upper")

boot_pred_nls <- colMeans(pred_nls, na.rm = T)

## insert in galabre_nls_nas

galabre_nls_nas <- galabre_nls_nas %>% mutate(poc_boot_pred = boot_pred_nls,
                          poc_pred_lower = pi[,1],
                          poc_pred_upper = pi[,2])

# plot

ggplot(galabre_nls_nas, aes(x = mes_for_fit))+
  geom_line(aes(y = poc_pred_lower), col = "black")+
  geom_line(aes(y = poc_pred_upper), col = "black")+
  geom_point(aes(y = poc_percent, col = "measured"), alpha = 0.5)+
  geom_point(aes(y = poc_fitted, col = "fitted with all events"), size = 2)+
  geom_point(aes(y = poc_boot_pred, col ="poc_boot_pred"), alpha = 0.5, size = 1)+
  scale_color_manual(values = c("darkblue","gray50","lightblue"))+
  geom_abline(slope = 0, intercept = aspt_value, col = "darkred")+
  annotate(geom = "label", label = formula_pocfit, x = Inf, y = Inf, hjust = 1.1, vjust = 1.1)+
  labs(x = "MES, g/L", y = "POC, %", colour = "", shape = "", title = "POC predicted from MES",subtitle = "Prediction interval in grey")+
  theme_minimal()+
  theme(legend.position = "bottom")

```
#### GNLS extension to Galabre

```{r pred-isere-gnls, cache.lazy = F}
galabre$mes_for_fit <- galabre$cmes_g.L 
with(galabre, sum(mes_for_fit == 0 | is.na(mes_for_fit), na.rm = T)) # 144 -> removed from df because model unstable with zero (when 0^(-b))

galabre_for_gnls <- galabre %>% filter(mes_for_fit != 0 & !is.na(mes_for_fit))

galabre_for_gnls$aspt <- aspt_value

nrow_galabre <- nrow(galabre_for_gnls)
nrow_boot <- nrow(coefs_boot)

# predict POC pour mes > 0
galabre_for_gnls$poc_fitted <- predict(pocfitg, newdata = galabre_for_gnls, na.action = na.pass) 


# Prediction interval
mes_mat_gnls <- matrix(NA_real_, nrow = nrow_boot, ncol = nrow_galabre)

for(i in 1:nrow(galabre_for_gnls)){
  mes_mat_gnls[,i] <-rnorm(nrow_boot, mean = galabre_for_gnls$mes_for_fit[i], sd = mes_u) # chaque colonne de la matrice correspond à une observation de MES. Exactly same code as when working on lines.
}


## model function 
f <- function(x, a, b){
  a * x ^ b + aspt_value
}

## paramètres de variance
theta <- as.numeric(coef(pocfitg$modelStruct$varStruct, unconstrained = F))
sigma_gnls <- pocfitg$sigma


### Matrice de prédictions, sans bruit


mu_gnls <- matrix(NA_real_, nrow = nrow_boot, ncol = nrow_galabre)
for(i in 1:nrow_boot){
   mu_gnls[i,] <- with(as.list(coefs_boot[i,]), # listing the coefficients allows to have 2 named numbers to be used in the function
                      f(mes_mat_gnls[i, ], a, b))
}


galabre_for_gnls$poc_var_mean <- apply(mu_gnls, 2, var) # variance of fit parameters + MES 

# adds noise
noise_mat_gnls <- matrix(NA_real_, nrow = nrow_boot, ncol = nrow_galabre)
sigma_mat_gnls <- sigma_gnls * abs(mu_gnls)^theta

noise_mat_gnls <- matrix(rnorm(nrow_boot*nrow_galabre, mean = 0, sd = 1), nrow = nrow_boot, ncol = nrow_galabre)
noise_mat_gnls <- noise_mat_gnls*sigma_mat_gnls

pred_gnls <- mu_gnls + noise_mat_gnls

pred_gnls <- pmin(pmax(pred_gnls, 0), 1) # clampe pred_nls pour éviter les intervalles de prédiction en dessous de zéro

### computes variance, y-wise
galabre_for_gnls$poc_var_tot <- apply(pred_gnls, 2, var) # total variance per prediction, for prediction total uncertainty

## computes prediction interval 
pi <- t(
  apply(pred_gnls, 2, quantile, probs = c(0.025, 0.975), na.rm = T)
)

colnames(pi) <- c("lower", "upper")

boot_pred_gnls <- colMeans(pred_gnls, na.rm = T)

## insert in galabre_for_gnls

galabre_for_gnls <- galabre_for_gnls %>% mutate(poc_boot_pred = boot_pred_gnls,
                          poc_pred_lower = pi[,1],
                          poc_pred_upper = pi[,2])

# plot

ggplot(galabre_for_gnls, aes(x = mes_for_fit))+
  geom_line(aes(y = poc_pred_lower, ymax = poc_pred_upper), col = "black")+
  geom_line(aes(y = poc_pred_upper), col = "black")+
  geom_point(aes(y = poc_percent, col = "measured"), alpha = 0.5)+
  geom_point(aes(y = poc_fitted, col = "fitted with all events"), size = 2)+
  geom_point(aes(y = poc_boot_pred, col ="poc_boot_pred"), alpha = 0.5, size = 0.5)+
  labs(x = "MES, mg.L", y = "POC, %", col = "")+
  scale_color_manual(values = c("darkblue","gray50","lightblue"))+
  geom_abline(slope = 0, intercept = aspt_value, col = "darkred")+
  annotate(geom = "label", label = formula_pocfitg, x = Inf, y = Inf, hjust = 1.1, vjust = 1.1)+
  labs(x = "MES, mg/L", y = "POC,prop", colour = "", shape = "", title = "POC predicted from MES",subtitle = "Prediction interval in grey")+
  theme_minimal()+
  theme(legend.position = "bottom")+
  ylim(-0.05,0.1)

ggplot(galabre_for_gnls, aes(x = mes_for_fit))+
  geom_line(aes(y = poc_pred_lower, ymax = poc_pred_upper), col = "black")+
  geom_line(aes(y = poc_pred_upper), col = "black")+
  geom_point(aes(y = poc_percent, col = "measured"), alpha = 0.5)+
  geom_point(aes(y = poc_fitted, col = "fitted with all events"), size = 2)+
  geom_point(aes(y = poc_boot_pred, col ="poc_boot_pred"), alpha = 0.5, size = 0.5)+
  labs(x = "MES, mg.L", y = "POC, %", col = "")+
  scale_color_manual(values = c("darkblue","gray50","lightblue"))+
  scale_x_continuous(trans = "log", breaks = c(1,10,100,1000))+
  geom_abline(slope = 0, intercept = aspt_value, col = "darkred")+
  annotate(geom = "label", label = formula_pocfitg, x = Inf, y = Inf, hjust = 1.1, vjust = 1.1)+
  labs(x = "MES, mg/L", y = "POC,prop", colour = "", shape = "", title = "POC predicted from MES",subtitle = "Prediction interval in grey")+
  theme_minimal()+
  theme(legend.position = "bottom")
```




```{r exit, cache = F}
knitr::knit_exit()
```




# Flux 

## Annual flux based on gnls model + Monte Carlo


```{r annual-flux-reference, cache.lazy=F}
# create matrix of q
q_u = 0.1 # Cédric - avis d'expert NOT WORKING; has to be 10% of the Q measured, not ALWAYS 0.1!

q_meas <- matrix(isere_for_gnls$q_m3.s, nrow = nrow_boot, ncol = nrow_isere, byrow = T) # repeats nrow_boot times the vector isere_for_gnls$q_m3.s

q_noise <- matrix(rnorm(nrow_boot*nrow_isere, mean = 0, sd = q_u), nrow = nrow_boot, ncol = nrow_isere) # creates a noise in percent (proportion), between 0 and 10%

q_mat <- q_meas * (1 + q_noise) # final value of q, with noise


# compute flux
period_mat <- matrix(isere_for_gnls$period, nrow = nrow_boot, ncol = nrow_isere, byrow = T)

flux_kg.s_mat <- pred_gnls*mes_mat_gnls*q_mat*1e-2*period_mat #pred_gnls * mes_mat : poc in mg/L; q_mat converted from m3/s to L/s. We consider no uncertainty on period. 

index_years <- sapply(unique(isere_for_gnls$year), function(y){which(isere_for_gnls$year == y)}) # list of indices corresponding to each year

annual_flux_kg.y <- sapply(index_years, function(idx){apply(flux_kg.s_mat[,idx], 1, sum, na.rm = T)}) # sum of fluxes per year, for each iteration of the bootstrap. Result is a matrix with nrow_boot rows and 19 columns (1 per year)

annual_flux_ci <- apply(annual_flux_kg.y, 2, quantile, probs = c(0.025, 0.5, 0.975), na.rm = T) # confidence interval for annual fluxes, per year. 3 lignes, 19 columns
annual_flux_mean <- colMeans(annual_flux_kg.y, na.rm = T) # mean annual flux per year. 1 vector

annual_flux_sd <- apply(annual_flux_kg.y, 2, sd, na.rm = T) # standard deviation of annual flux per year. Is just an estimate of goodness of mean, not as good as than the confidence interval. 
 

annual_flux_df <- data.frame(year = unique(isere_for_gnls$year), 
                        annual_flux_mean = annual_flux_mean, 
                        annual_flux_variability = rep(NA, 19), # no physical sense in calculating "annual variability". Would be standard deviation of annual flux. But we prefer to show the prediction interval.
                        annual_flux_ci_lower = annual_flux_ci[1,], 
                        annual_flux_ci_upper = annual_flux_ci[3,])

ggplot(annual_flux_df)+
  geom_col(aes(x=year, y = annual_flux_mean), fill = "lightblue")+
  geom_errorbar(aes(x = year, ymin = annual_flux_ci_lower, ymax = annual_flux_ci_upper), width = 0.2)+
  theme_minimal()
```

# Archives

```{r crues-without-na}
crues_nona <- crues %>% filter(!if_any(everything(), is.na)) %>% subset(crue != "Crue du 13/07/2011") %>% filter(mes_g.L != 0)

crues_nona <- tibble::rownames_to_column(crues_nona, "id")

crues_train <- crues_nona %>% sample_frac(.75)
crues_test <- crues_nona %>% dplyr::anti_join(crues_train, by = "id")
```

```{r power-law-poc-percent}
adjust_pocpercent <- lm(log(poc_percent)~log(mes_g.L), data = crues_train) 

summary(adjust_pocpercent)

coefs_pocpercent <- summary(adjust_pocpercent)$coefficients %>% as.data.frame() %>% mutate_if(is.numeric, round, digits = 2)
powerlaw_pocpercent <- paste0("POC (g/L) = (",round(exp(coefs_pocpercent[1,1]),2), " ± ", round(exp(coefs_pocpercent[2,1]),2), ") *", " MES (g/L)^(", coefs_pocpercent[1,2], "±", coefs_pocpercent[2,2],")")

crues_test$log_pocpercent_pred <- predict(object = adjust_pocpercent, newdata = crues_test)
crues_test$pocpercent_pred <- exp(crues_test$log_pocpercent_pred)

crues_test$log_pocpercent_pred_se <- predict(object = adjust_pocpercent, newdata = crues_test, se.fit = T)$se.fit
crues_test$pocpercent_pred_se <- exp(crues_test$log_pocpercent_pred_se)

ggplot(crues_test, aes(x= mes_g.L))+geom_point(aes(y = poc_percent, col = "measured"))+
  geom_point(aes(y = pocpercent_pred, col = "predicted"))+
  geom_errorbar(aes(ymin = pocpercent_pred-pocpercent_pred_se, ymax = pocpercent_pred + pocpercent_pred_se, col = "predicted"), width = 0.05)+
  #scale_x_continuous(transform = "log10")+
  # scale_y_continuous(transform = "log10")+
  scale_color_manual(values = c("palegreen4", "lightblue"))+
  theme_minimal()
```


```{r power-law-poc-percent-on-crues}
crues_nona$log_pocpercent_pred <- predict(object = adjust_pocpercent, newdata = crues_nona)
crues_nona$pocpercent_pred <- exp(crues_nona$log_pocpercent_pred)

crues_nona$log_pocpercent_pred_se <- predict(object = adjust_pocpercent, newdata = crues_nona, se.fit = T)$se.fit
crues_nona$pocpercent_pred_se <- exp(crues_nona$log_pocpercent_pred_se)

ggplot(crues_nona, aes(x= mes_g.L))+geom_point(aes(y = poc_percent, col = "measured"), size = 2)+
  geom_point(aes(y = pocpercent_pred, col = "predicted"))+
  scale_color_manual(values = c("palegreen4", "lightblue"))+
  labs(x = "MES, g/L", y = "POC, %", col = "")+
  annotate(x = 25, y = 0.8, geom = "label", label = powerlaw_pocpercent)+
  theme_minimal(base_size = 15)+
    theme(legend.position = "bottom")


```

```{r lm-pocgl-mes}
lm_pocgl <- lm(poc_g.L~mes_g.L, data = crues_train) 
summary(lm_pocgl)


coefs_pocgl <- summary(lm_pocgl)$coefficients %>% as.data.frame() %>% mutate_if(is.numeric, round, digits = 4)
lmformula_pocgl <- paste0("POC (g/L) = (" , coefs_pocgl[1,1] , " ± " , coefs_pocgl[2,1] , ") + MES (g/L) * (", coefs_pocgl[1,2], "±", coefs_pocgl[2,2], ")")


crues_test$pocgl_pred <- predict(object = lm_pocgl, newdata = crues_test)
crues_test$pocgl_pred_se <- predict(object = lm_pocgl, newdata = crues_test, se.fit = T)$se.fit

crues_train$pocgl_pred <- predict(object = lm_pocgl)
crues_train$pocgl_pred_se <- predict(object = lm_pocgl, se.fit = T)$se.fit

ggplot(crues_test, aes(x = mes_g.L))+geom_point(aes(y = poc_g.L, col = "measured"))+
  geom_point(aes(y = pocgl_pred, col = "predicted"))+
  geom_errorbar(aes(ymin = pocgl_pred - pocgl_pred_se, ymax = pocgl_pred + pocgl_pred_se, col = "predicted"), width = 0.05)+
  scale_color_manual(values = c("palegreen4", "lightblue"))+
  scale_x_continuous(transform = "log10")+
  scale_y_continuous(transform = "log10")+
  theme_minimal()

ggplot(crues_test, aes(x = mes_g.L))+geom_point(aes(y = poc_g.L, col = "measured"))+
  geom_point(aes(y = pocgl_pred, col = "predicted"))+
  geom_errorbar(aes(ymin = pocgl_pred - pocgl_pred_se, ymax = pocgl_pred + pocgl_pred_se, col = "predicted"), width = 1)+
    annotate(x = 70, y = 0.10, geom = "label", label = lmformula_pocgl)+
  scale_color_manual(values = c("palegreen4", "lightblue"))+
  theme_minimal()

ggplot(crues_train, aes(x = mes_g.L))+geom_point(aes(y = poc_g.L, col = "measured"))+
  geom_point(aes(y = pocgl_pred, col = "predicted"))+
  geom_errorbar(aes(ymin = pocgl_pred - pocgl_pred_se, ymax = pocgl_pred + pocgl_pred_se, col = "predicted"), width = 1)+
    annotate(x = 100, y = 0.10, geom = "label", label = lmformula_pocgl)+
  scale_color_manual(values = c("palegreen4", "lightblue"))+
  theme_minimal()

```

```{r power-law-mes-pocgl}

adjust_pocgl <- lm(log(poc_g.L)~log(mes_g.L), data = crues_train)
summary(adjust_pocgl)

coefs_pocgl <- summary(adjust_pocgl)$coefficients %>% as.data.frame() %>% mutate_if(is.numeric, round, digits = 2)
powerlaw_pocgl <- paste0("POC (g/L) = (",round(exp(coefs_pocgl[1,1]),2), " ± ", round(exp(coefs_pocgl[2,1]),2), ") *", " MES (g/L)^(", coefs_pocgl[1,2], "±", coefs_pocgl[2,2],")")

crues_test$log_pocgl_pred <- predict(object = adjust_pocgl, newdata = crues_test)
crues_test$pl_pocgl_pred <- exp(crues_test$log_pocgl_pred)

crues_test$log_pocgl_pred_se <- predict(object = adjust_pocgl, newdata = crues_test, se.fit = T)$se.fit
crues_test$pl_pocgl_pred_se <- exp(crues_test$log_pocgl_pred_se)


ggplot(crues_test, aes(x= mes_g.L))+geom_point(aes(y = poc_g.L, col = "measured"))+
  geom_point(aes(y = pl_pocgl_pred, col = "predicted"))+
  geom_errorbar(aes(ymin = pl_pocgl_pred - pl_pocgl_pred_se, ymax = pl_pocgl_pred + pl_pocgl_pred_se, col = "predicted"), width = 1)+
  scale_color_manual(values = c("palegreen4", "lightblue"))+
  scale_x_continuous(transform = "log10")+
  scale_y_continuous(transform = "log10")+
  theme_minimal()


ggplot(crues_test, aes(x= mes_g.L))+geom_point(aes(y = poc_g.L, col = "measured"))+
  geom_point(aes(y = pl_pocgl_pred, col = "predicted"))+
  geom_errorbar(aes(ymin = pl_pocgl_pred - pl_pocgl_pred_se, ymax = pl_pocgl_pred + pl_pocgl_pred_se, col = "predicted"), width = 1)+
  scale_color_manual(values = c("palegreen4", "lightblue"))+
  annotate(x = 70, y = -0.5, geom = "label", label = powerlaw_pocgl)+
  theme_minimal()

```

```{r merge-q-mes}

galabre <- merge(debit, mes, by = "DateHeure")

sum(is.na(galabre$mes_g.L) == T)

galabre$year <- year(galabre$DateHeure)
galabre$commondate <- as.Date(paste0("2000-", format(galabre$DateHeure,"%j")), "%Y-%j")
galabre <- galabre %>%
  mutate(Saison = case_when(month(DateHeure) %in% c(12, 1, 2) ~ "Hiver", 
                            month(DateHeure) %in% c(3, 4, 5) ~ "Printemps", 
                            month(DateHeure) %in% c(6, 7, 8) ~ "Ete", 
                            TRUE ~ "Automne"))

galabre$Saison <- ordered(galabre$Saison, levels = c("Automne", "Hiver", "Printemps", "Ete"))


ggpubr::ggarrange(
ggplot(subset(galabre, year %in% c(2010,2014,2018)))+ 
  geom_point(aes(x=commondate, y= mes_g.L,col="mes g/L"), alpha = 0.5, size = 0.5) +
  scale_color_manual(values = c("palegreen4"))+
  scale_x_date(labels = function(x) format(x, "%d-%b"), date_minor_breaks = "1 month", name = "")+
  scale_y_continuous( name = "MES g/L")+
  facet_grid(cols = vars(year), scales = "free")+
  theme_minimal()+
  theme(legend.position = "none", axis.text.x = element_blank()),

ggplot(subset(galabre, year %in% c(2010,2014,2018)))+ 
  geom_point(aes(x=commondate, y= q_m3.s,col="discharge_m3/s"), alpha = 0.5, size = 0.5) +
  scale_color_manual(values = c("lightblue"))+
  scale_x_date(labels = function(x) format(x, "%d-%b"), date_minor_breaks = "1 month", name = "")+
  scale_y_continuous( name = "Discharge, m3/s")+
  facet_grid(cols = vars(year), scales = "free")+
  theme_minimal()+
  theme(legend.position = "none", axis.text.x = element_text(angle = 90), strip.text.x = element_blank()),

nrow = 2)

ggplot(sample_n(galabre,5000))+
  geom_point(aes(x = q_m3.s, y = mes_g.L, col = Saison))+
  scale_color_viridis_d()+
  labs(x = "Débit, m3/s", y = "MES, g/L", col = "Saison")+
  facet_grid(cols = vars(Saison))+
  scale_color_manual(values = c("orange","grey80","chartreuse4","goldenrod2"))+
    scale_x_continuous(transform = "log10")+
  theme_minimal()+
  theme(legend.position = "none")

ggplot(sample_n(galabre,5000))+
  geom_point(aes(x = q_m3.s, y = mes_g.L, col = Saison))+
  scale_color_viridis_d()+
  labs(x = "Débit, m3/s", y = "MES, g/L", col = "Saison")+
  facet_grid(cols = vars(Saison))+
  scale_color_manual(values = c("orange","grey80","chartreuse4","goldenrod2"))+
  theme_minimal()+
  theme(legend.position = "none")

ggplot(sample_n(galabre,5000))+
  geom_point(aes(x = q_m3.s, y = mes_g.L, col = Saison))+
  scale_color_viridis_d()+
  labs(x = "Débit, m3/s", y = "MES, g/L", col = "Saison")+
  scale_color_manual(values = c("orange","grey80","chartreuse4","goldenrod2"))+
  theme_minimal()+
  theme(legend.position = "none")
```

## predict fluxes using LM POC g/L ~ MES

```{r predict-poc-lm}
galabre$pocgl_pred <- predict(lm_pocgl, newdata = galabre)
galabre$pocgl_pred_se <- predict(lm_pocgl, newdata = galabre, se.fit = T)$se.fit

ggplot(subset(galabre, year %in% c(2010,2014,2018)))+ 
  geom_point(aes(x=commondate, y= pocgl_pred,col="POC predicted, g/L"), alpha = 0.5, size = 0.5) +
  scale_color_manual(values = c("lightblue"))+
  scale_x_date(labels = function(x) format(x, "%d-%b"), date_minor_breaks = "1 month", name = "")+
  scale_y_continuous( name = "POC predicted, g/L")+
  facet_grid(cols = vars(year), scales = "free")+
  theme_minimal()+
  theme(legend.position = "none", axis.text.x = element_text(angle = 90), strip.text.x = element_blank())

```

```{r carbon-flux}

yearly_fluxes <- galabre %>% group_by(year) %>% 
  summarise(
    fpoc_kg.year = sum(pocgl_pred * q_m3.s * 10 * 60, na.rm = T), # poc in g/L equivalent to kg/m3, discharge in m3/s converted to L/s, and then in L/10 min. So we sum the amount of poc that flows for 10 min, for each 10-min interval
    sum_fpoc_kg.s = sum(pocgl_pred * q_m3.s, na.rm = T), # g/L equivalent to kg/m3 -> fpoc obtained in kg/s
    percent_of_year_included = sum(!is.na(pocgl_pred) & !is.na(q_m3.s))/n()*100, # how many missing data is there
    sum_discharge_m3.s = sum(q_m3.s, na.rm = T),  #sum of instant fluxes 
    mean_discharge_m3.s = mean(q_m3.s, na.rm = T), #mean of fluxes for year 
    sd_discharge_m3.s = sd(q_m3.s, na.rm = T)) #sd

bv <- 20 # from Justin
  
# fluxes by adding all 10min fluxes, with uncertainty depending on the nb of observations per year
yearly_fluxes$fpoc_kg.year.km2 <- yearly_fluxes$fpoc_kg.year/bv

# fluxes with ponderation method @Nemery2013 citing Walling and Webb 1985
yearly_fluxes$fpoc_ww_kg.year.km2 <- with(yearly_fluxes, sum_fpoc_kg.s/sum_discharge_m3.s*mean_discharge_m3.s* 365*24*60*60) / bv # fpoc obtained in kg/s, then converted to kg/year

knitr::kable(yearly_fluxes)
```

```{r plot-fluxes}
yearly_fluxes$label <- paste(round(yearly_fluxes$percent_of_year_included,2), " %")
ggplot(yearly_fluxes, aes(x = year))+
  geom_col(aes(y = fpoc_kg.year.km2, fill = "POC flux as sum"), position = position_nudge(-0.2), width = 0.4)+
  geom_col(aes(y = fpoc_ww_kg.year.km2, fill = "POC flux as weigthed"), position = position_nudge(0.2), width = 0.4)+
  geom_label(aes(x = year, y = fpoc_ww_kg.year.km2, label = label), nudge_y = 500, label.size = 0.1)+
  scale_x_continuous(breaks = c(unique(yearly_fluxes$year)), minor_breaks = NULL)+
  scale_size_continuous(range = c(0.1,10))+
  scale_fill_manual(values = c("palegreen4", "lightblue"))+
  labs(x = "", fill = "", y = "Flux de POC, kg/year/km2")+
  theme_minimal()+
  theme(legend.position = "bottom")


```

## predict fluxes using powerlaw POC % ~ MES

```{r predict-poc-power}
galabre$log_pocpercent_pred <- predict(adjust_pocpercent, newdata = galabre)
galabre$pocpercent_pred <- exp(galabre$log_pocpercent_pred)

galabre$pocpercent_pred[which(galabre$mes_g.L == 0)] <- 0

galabre$log_pocpercent_pred_se <- predict(adjust_pocpercent, newdata = galabre, se.fit = T)$se.fit
galabre$pocpercent_pred_se <- exp(galabre$log_pocpercent_pred_se)

galabre$poc_g.L_pred <- with(galabre, pocpercent_pred / 100 * mes_g.L)
  
ggplot(galabre)+geom_boxplot(aes(y = pocpercent_pred))

ggplot(subset(galabre, year %in% c(2010,2014,2018)))+ 
  geom_point(aes(x=commondate, y= pocpercent_pred,col="POC predicted, %"), alpha = 0.5, size = 0.5) +
  scale_color_manual(values = c("lightblue"))+
  scale_x_date(labels = function(x) format(x, "%d-%b"), date_minor_breaks = "1 month", name = "")+
  scale_y_continuous( name = "POC predicted, %")+
  facet_grid(cols = vars(year), scales = "free")+
  theme_minimal()+
  theme(legend.position = "none", axis.text.x = element_text(angle = 90), strip.text.x = element_blank())

```

```{r carbon-flux-p}

yearly_fluxes_p <- galabre %>% group_by(year) %>% 
  summarise(
    fpoc_kg.year = sum(poc_g.L_pred * q_m3.s * 10 * 60, na.rm = T), # poc in g/L equivalent to kg/m3, discharge in m3/s converted to L/s, and then in L/10 min. So we sum the amount of poc that flows for 10 min, for each 10-min interval
    sum_fpoc_kg.s = sum(poc_g.L_pred * q_m3.s, na.rm = T), # g/L equivalent to kg/m3 -> fpoc obtained in kg/s
    percent_of_year_included = sum(!is.na(poc_g.L_pred) & !is.na(q_m3.s))/n()*100, # how many missing data is there
    sum_discharge_m3.s = sum(q_m3.s, na.rm = T),  #sum of instant fluxes 
    mean_discharge_m3.s = mean(q_m3.s, na.rm = T), #mean of fluxes for year 
    sd_discharge_m3.s = sd(q_m3.s, na.rm = T)) #sd

bv <- 20 # from Justin
  
# fluxes by adding all 10min fluxes, with uncertainty depending on the nb of observations per year
yearly_fluxes_p$fpoc_kg.year.km2 <- yearly_fluxes_p$fpoc_kg.year/bv

# fluxes with ponderation method @Nemery2013 citing Walling and Webb 1985
yearly_fluxes_p$fpoc_ww_kg.year.km2 <- with(yearly_fluxes_p, sum_fpoc_kg.s/sum_discharge_m3.s*mean_discharge_m3.s* 365*24*60*60) / bv # fpoc obtained in kg/s, then converted to kg/year

knitr::kable(yearly_fluxes_p)


print(paste("Mean FPOC (sum) = ", round(mean(yearly_fluxes_p$fpoc_kg.year.km2),2), "kg/year/km2"))
print(paste("sd FPOC (sum) = ", round(sd(yearly_fluxes_p$fpoc_kg.year.km2),2), "kg/year/km2"))

print(paste("Mean FPOC (weighted) = ", round(mean(yearly_fluxes_p$fpoc_ww_kg.year.km2),2), "kg/year/km2"))
print(paste("sd FPOC (weighted) = ", round(sd(yearly_fluxes_p$fpoc_ww_kg.year.km2),2), "kg/year/km2"))


print(paste("Mean FPOC (sum) = ", round(mean(yearly_fluxes_p$fpoc_kg.year.km2),2), "kg/year/km2"))
print(paste("sd FPOC (sum) = ", round(sd(yearly_fluxes_p$fpoc_kg.year.km2),2), "kg/year/km2"))

print(paste("Débit moyen = ", round(mean(galabre$q_m3.s),2), "kg/year/km2"))
print(paste("sd FPOC (weighted) = ", round(sd(yearly_fluxes_p$fpoc_ww_kg.year.km2),2), "kg/year/km2"))
```

```{r plot-fluxes-p}
yearly_fluxes_p$label <- paste(round(yearly_fluxes_p$percent_of_year_included,2), " %")
ggplot(yearly_fluxes_p, aes(x = year))+
  geom_col(aes(y = fpoc_kg.year.km2, fill = "POC flux as sum"), position = position_nudge(-0.2), width = 0.4)+
  geom_col(aes(y = fpoc_ww_kg.year.km2, fill = "POC flux as weigthed"), position = position_nudge(0.2), width = 0.4)+
  geom_label(aes(x = year, y = fpoc_ww_kg.year.km2, label = label), nudge_y = 500, label.size = 0.1)+
  scale_x_continuous(breaks = c(unique(yearly_fluxes$year)), minor_breaks = NULL)+
  scale_size_continuous(range = c(0.1,10))+
  scale_fill_manual(values = c("palegreen4", "lightblue"))+
  labs(x = "", fill = "", y = "Flux de POC, kg/year/km2")+
  theme_minimal(base_size = 15)+
  theme(legend.position = "bottom")



```
