---
title: "Galabre"
output: 
  html_document:
    code_folding: hide
date: "2025-06-20"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = F, warning = F, error = F, fig.align = "center", collapse = T,
                      cache = F)
```

```{r libraries}

library(ggplot2)
library(ggpubr)
library(dplyr)
library(readxl)
library(lubridate)

#for gnls
library(nlme)

```


# Data

## Load 

Sur BDOH les chroniques de débit et MES sont disponibles jusqu'à 2019. Données 2020-2021 fournies par Ophélie. 

Vérifier l'unité de "period"


```{r prepare-data, eval = F}
crues <- readxl::read_xlsx(path = "galabre.xlsx", sheet = "Crues") 

mes <- readxl::read_xlsx(path = "galabre.xlsx", sheet = "SSC", col_types = c("date","numeric")) 

debit <- readxl::read_xlsx(path = "galabre.xlsx", sheet = "Debit", col_types = c("date","numeric")) 

galabre_old <- merge(debit, mes, by = "DateHeure") %>% unique() # 4 duplicated in 2017, no q

galabre_new <- readxl::read_xlsx(path = "Galabre_outlet.xlsx", sheet = "Galabre_outlet_noduplicated") %>% unique() # 2019 was duplicated (also in galabre_old). Some duplicated still exist, removed by "unique"

galabre_tot <- rbind(galabre_old, galabre_new)

#galabre_tot[which(duplicated(galabre_tot$DateHeure) == T), ] %>% View()

galabre <- merge(galabre_tot, crues, by = "DateHeure", all = T)  
galabre$year <- year(galabre$DateHeure)
galabre$commondate <- as.Date(paste0("2000-", format(galabre$DateHeure,"%j")), "%Y-%j")
galabre$period <- as.numeric(-(galabre$DateHeure - lead(galabre$DateHeure))) # period in s

write.csv(galabre, "galabre.csv")
```


```{r load-data}

galabre <- read.csv("galabre.csv")
# from galabre

summary_galabre <- merge(
galabre %>% subset(!is.na(poc_percent)) %>% group_by(year) %>% summarise(nb_poc = n()),
galabre %>% subset(!is.na(cmes_g.L)) %>% group_by(year) %>% summarise(nb_cmes = n()),
by = "year", all = T) %>% 
  merge(galabre %>% subset(!is.na(q_m3.s)) %>% group_by(year) %>% summarise(nb_q = n()), by = "year", all = T) %>%
  merge(galabre %>% subset(!is.na(q_m3.s)) %>% group_by(year) %>% summarise(period_q = round(n()*20/(24*60),0)), by = "year", all = T) 


summary_galabre %>% knitr::kable(caption = "Nombre d'observations de DOC, POC, CMES et débit par an") %>% kableExtra::kable_styling()

complete_years <- c(2009:2014)

```



## Explore data

```{r mes-poc}
galabre$poc_g.L <- galabre$mes_g.L * galabre$poc_percent / 100


ggplot(galabre)+geom_point(aes(x=mes_g.L, y = poc_percent, col = crue, shape = crue))+
  scale_color_viridis_d()+
  labs(x = "MES, g/L", y = "POC, %", col = "", shape = "")+
  lims(y=c(0,2))+
  theme_minimal()+
  theme(legend.position = "bottom")


ggplot(galabre, aes(x=log10(mes_g.L), y = log10(poc_percent)))+geom_point(aes(col = crue))+
  scale_color_viridis_d()+
  facet_grid(cols = vars(Saison))+
  geom_smooth(se = T, method = "lm")+
  theme_minimal()+
  theme(legend.position = "bottom")
```

```{r annual-q-mes, fig.dim = c(10, 15)}

ggarrange(
ggplot(galabre, aes(x = as.Date(commondate))) + 
  geom_point(aes(y = q_m3.s), col = "lightblue", size = 0.5) +
  scale_x_date(labels = function(x) format(x, "%d-%b"), date_minor_breaks = "1 month", name = "")+
  facet_grid(rows = vars(year))+
  labs(x = "", y = "Q, m3/s") +
  theme_minimal()+
  theme(legend.position = "bottom"),

ggplot(galabre, aes(x = as.Date(commondate))) + 
  geom_point(aes(y = cmes_g.L), col = "palegreen4", size = 0.5) +
  scale_x_date(labels = function(x) format(x, "%d-%b"), date_minor_breaks = "1 month", name = "")+
  facet_grid(rows = vars(year))+
  labs(x = "", y = "CMES, g/L") +
  theme_minimal()+
  theme(legend.position = "bottom"),

ncol = 2
)

```

`

# Fit MES-POC

Objectif: construire la relation MES-POC pour pouvoir reconstruire la chronique de POC à partir de la chronique de MES. Cette relation prend la forme de $POC\% = a*MES^b + c$. Le modèle est fitté sur les données de crues dont la concentration en POC a été mesurée: **poc_galabre**.

```{r poc-galabre}
poc_galabre <- galabre %>% filter(!is.na(poc_percent) & !is.na(mes_g.L) & mes_g.L != 0) # one missing value for MES, one MES = 0

poc_galabre$mes_for_fit <- poc_galabre$mes_g.L 

n_obs <- nrow(poc_galabre)
n_boot <- 1000
```


```{r uncertainties}
q_u <- 0.1 # vérifier chiffre galabre
mes_u <- 0.05 # au pif
```

On cherche à fitter le modèle $POC (prop) = a \* MES^{b} + aspt$. Deux fonctions R sont disponibles : *nls* et *gnls*. nls est robuste, mais gnls permet de choisir la structure de la variance. On sait que la variance diminue pour les hautes valeurs de MES (on tend vers l'asymptote). L'erreur dépend probablement de $y*\sigma^{2\delta}.

```{r asymptot}
# find asymptotic value : arbitrarily decide that it corresponds to the median of the 10% of poc_percent corresponding to the 10% of highest MES values.
aspt_value <- poc_galabre[order(poc_galabre$cmes_g.L, decreasing = T),] %>% pull(poc_percent) %>% head(dim(poc_galabre)[1]/10) %>% mean() 
aspt_value_sd <- poc_galabre[order(poc_galabre$cmes_g.L, decreasing = T),] %>% pull(poc_percent) %>% head(dim(poc_galabre)[1]/10) %>% sd() 

poc_galabre$aspt <- aspt_value
```

## Regression MES (POC) and CMES

```{r mes-cmes}

fit_mes <- lm(cmes_g.L~mes_g.L, data = poc_galabre)
summary(fit_mes)

cmes_u <- summary(fit_mes)$coef[2,2] # standard error on cmes

ggarrange(
ggplot(poc_galabre) + geom_point(aes(x=cmes_g.L, y = mes_g.L, col = crue, shape = crue))+
  scale_color_viridis_d()+
  scale_shape_manual(values = c(1,2,3,4,5,6,7,8,9,10,11))+
  geom_abline(slope = 1, intercept =0, col ="darkred")+
  geom_abline(intercept = coef(fit_mes)[1], slope = coef(fit_mes)[2], linetype = 2)+
  xlim(0,200)+
  theme_minimal(),

ggplot(poc_galabre) + geom_point(aes(x=cmes_g.L, y = mes_g.L, col = crue, shape = crue))+
  scale_color_viridis_d()+
  scale_shape_manual(values = c(1,2,3,4,5,6,7,8,9,10,11))+
  geom_abline(slope = 1, intercept =0, col ="darkred")+
  geom_abline(intercept = coef(fit_mes)[1], slope = coef(fit_mes)[2], linetype = 2)+
  xlim(0,50)+ylim(0,50)+
  theme_minimal(),

ggplot(poc_galabre) + geom_point(aes(x=cmes_g.L, y = mes_g.L, col = crue, shape = crue))+
  scale_color_viridis_d()+
  scale_shape_manual(values = c(1,2,3,4,5,6,7,8,9,10,11))+
  geom_abline(slope = 1, intercept =0, col ="darkred")+
  geom_abline(intercept = coef(fit_mes)[1], slope = coef(fit_mes)[2], linetype = 2)+
  xlim(0,10)+ylim(0,10)+
  theme_minimal(),

ncol = 3, common.legend = T, legend = "bottom")

```

## Log-log linear regression: get starting values


```{r lm-poc-mes}
pocfit <- lm(log(poc_percent)~log(mes_for_fit), data = select(poc_galabre, c(poc_percent, mes_for_fit)))

summary(pocfit)
```


## GNLS with aspt 

### Fit GNLS model 

```{r fit-poc-mes-gnls}

# fit gnls
pocfitg <- gnls(
  poc_percent ~ a*mes_for_fit^b + aspt,
  data = select(poc_galabre, c(mes_for_fit, poc_percent, aspt)),
  start = list(a = coef(pocfit)[[2]], b = coef(pocfit)[[1]]), # on utilise les valeurs de pocfit comme coefficients initiaux
  weights = varPower(value = 1, form = ~ fitted(.)),
  control = gnlsControl(nlsTol = 1e-3, tolerance = 1e-4)
)

# summary 
summary(pocfitg) %>% print()

# variance parameters
theta <- as.numeric(coef(pocfitg$modelStruct$varStruct, unconstrained = F))
sigma_gnls <- pocfitg$sigma

# formula
formula_pocfitg <- paste("GNLS:", round(coef(pocfitg)[1], 3), "x MES ^", round(coef(pocfitg)[2],3), "+", round(aspt_value, 3), sep = "")

## model function 
f <- function(x, a, b, aspt){
  a * x ^ b + aspt
}
```


### GNLS bootstrap

```{r intervalles-de-confiance-bootstrap}

coefs_boot <- matrix(NA, nrow = n_boot, ncol = 2, dimnames = list(NULL, c("a","b")))
                     

for(i in seq_len(n_boot)){
  
  idx_boot <- sample(n_obs, replace = T)
  df_boot <- poc_galabre[idx_boot, c("mes_for_fit","poc_percent","aspt")]
  
  tryCatch(
    {fit_init <- nls(
      poc_percent ~ a * mes_for_fit^b + aspt,
      data = df_boot,
      start = coef(pocfitg))
      # fit init is necessary to find the correct starting values for gnls. Otherwise, too much convergence result in extreme values in a and b

      pocfit_bg <- gnls(
      poc_percent~a*mes_for_fit^b+aspt,
      data = df_boot,
      start = coef(fit_init),
      weights = varPower(form = ~fitted(.)),
      control = gnlsControl(nlsTol = 1e-3, tolerance = 1e-4, maxIter = 200))
      
      coefs_boot[i,] <- coef(pocfit_bg)
      }, 
    error = function(e) NULL) 
}

# removes NA
coefs_boot <- na.omit(coefs_boot)
apply(coefs_boot, 2, quantile, probs = c(0.025, 0.975)) %>% knitr::kable() #ic coef
ggplot(as.data.frame(coefs_boot))+
  geom_point(aes(x = a, y = b))+
  theme_minimal()+
  theme(legend.position = "none")

# adds uncertainty around aspt
coefs_boot <- cbind(coefs_boot, "aspt" = rnorm(length(coefs_boot)/2, mean = aspt_value, sd = aspt_value_sd))

# compute POC
fitted_boot <- apply(coefs_boot, 1, function(p){p["a"] * poc_galabre$mes_for_fit^p["b"] + p["aspt"]}) # MC worlds in columns
fitted_boot_ic <- apply(fitted_boot, 1, quantile, 
                 probs = c(0.025, 0.5, 0.975), na.rm = TRUE) # prediction intervals
fitted_boot_mean <- apply(fitted_boot, 1, mean) # meet bottstrapped valur

# intergrates in poc_galabre
poc_galabre_boot_gnls <- poc_galabre %>% mutate(poc_fitted = fitted_boot_mean, upr = fitted_boot_ic[3, ], lwr = fitted_boot_ic[1,])

ggplot(poc_galabre_boot_gnls)+
  geom_point(aes(x=mes_for_fit, y = poc_percent, col = "measured", shape = "measured"))+ 
  geom_point(aes(x=mes_for_fit, y = poc_fitted, col = "fitted", shape = "fitted"))+ 
  geom_ribbon(aes(x = mes_for_fit, ymin = lwr, ymax = upr), fill = "gray80", alpha = 0.5)+
  geom_abline(slope = 0, intercept = aspt_value, col = "darkred")+
  annotate(geom = "label", label = formula_pocfitg, x = Inf, y = Inf, hjust = 1.1, vjust = 1.1)+
  scale_color_manual(values = c("darkblue", "lightblue"))+
  labs(x = "MES, mg/L", y = "POC, %", colour = "", shape = "", title = "POC% measured and fitted vs MES measured",subtitle = "Confidence interval in grey")+
  theme_minimal()

ggplot(poc_galabre_boot_gnls, aes(x=poc_percent))+
  geom_point(aes(y=poc_fitted), col = "darkblue")+ 
  geom_errorbar(aes(ymin = lwr, ymax = upr), fill = "gray80", alpha = 0.5)+
  geom_abline(slope = 1, intercept = 0, col = "darkred")+
  annotate(geom = "label", label = formula_pocfitg, x = Inf, y = Inf, hjust = 1.1, vjust = 1.1)+
  labs(x = "POC measured", y = "POC fitted", colour = "", shape = "", title = "POC fitted vs measured",subtitle = "Confidence interval in grey")+
  theme_minimal()
```


### GNLS extension to galabre

**mes_for_fit** contient beaucoup de zéros (462553). Ils ne peuvent pas être inclus dans le modèle parce qu'il est instable avec 0^(-b). On va fitter les autres lignes et imposer POC% = 0 pour les lignes où MES = 0. 

Pour la méthode, on utilise uniquement les années où les chroniques de débit sont complètes... de 2009 à 2014. 

```{r constant-numbers}
# prepare dataframe
galabre_gnls <- galabre %>% filter(year %in% complete_years)
galabre_gnls$mes_for_fit <- galabre_gnls$cmes_g.L
with(galabre_gnls, sum(mes_for_fit == 0 | is.na(mes_for_fit), na.rm = T)) # 291686

na_lines <- which(is.na(galabre_gnls$mes_for_fit)) # 0
zero_lines <- which(galabre_gnls$mes_for_fit == 0)
fit_lines <- which(galabre_gnls$mes_for_fit != 0 & !is.na(galabre_gnls$mes_for_fit))

galabre_pwl_gnls <- galabre_gnls[fit_lines, ]
galabre_pwl_gnls$aspt <- aspt_value # from nls fitting

nrow_boot <- nrow(coefs_boot)
nrow_galabre_gnls <- nrow(galabre_gnls)
```


```{r pred-galabre-gnls, cache.lazy = F}

# predict POC pour mes > 0
poc_fitted <- predict(pocfitg, newdata = galabre_pwl_gnls, na.action = na.pass)
galabre_gnls$poc_fitted <- NA
galabre_gnls[fit_lines, ]$poc_fitted <- poc_fitted
galabre_gnls[zero_lines, ]$poc_fitted <- 0


# MES matrix
mes_meas <- matrix(galabre_gnls$mes_for_fit, nrow = nrow_boot, ncol = nrow_galabre_gnls, byrow = T) # repeats nrow_boot times the vector isere_for_gnls$q_m3.s
mes_noise <- matrix(rnorm(nrow_boot*nrow_galabre_gnls, mean = 0, sd = mes_u), nrow = nrow_boot, ncol = nrow_galabre_gnls) # 
mes_mat <- mes_meas * (1 + mes_noise) # final value of q, with noise. 


# Prediction matrix, no model noise
mu_gnls <- f(mes_mat, coefs_boot[,"a"], coefs_boot[,"b"], coefs_boot[,"aspt"])

# Prediction matrix, with noise
noise_mat_gnls <- matrix(NA_real_, nrow = nrow_boot, ncol = nrow_galabre_gnls)
sigma_mat_gnls <- sigma_gnls * abs(mu_gnls)^theta # variance depends on predicted value

noise_mat_gnls <- matrix(rnorm(nrow_boot*nrow_galabre_gnls, mean = 0, sd = 1), nrow = nrow_boot, ncol = nrow_galabre_gnls)
noise_mat_gnls <- noise_mat_gnls*sigma_mat_gnls

pred_gnls <- mu_gnls + noise_mat_gnls

mes_mat_zeros <- which(mes_mat == 0)
pred_gnls[mes_mat_zeros] <- 0
#pred_gnls <- pmin(pmax(pred_gnls, 0), 100) # clampe pred_nls pour éviter les intervalles de prédiction en dessous de zéro et au dessus de 100 (no case)

# Prediction interval 
pi <- t(apply(pred_gnls, 2, quantile, probs = c(0.025, 0.975), na.rm = T))
colnames(pi) <- c("lower", "upper")

# Mean bootstrap value
boot_pred_gnls <- colMeans(pred_gnls, na.rm = T)

## insert in galabre_for_gnls
galabre_gnls <- galabre_gnls %>% mutate(poc_boot_pred = boot_pred_gnls,
                          poc_pred_lower = pi[,1],
                          poc_pred_upper = pi[,2])

# variances
galabre_gnls$poc_var_mean <- apply(mu_gnls, 2, var) # variance of fit parameters + MES 
galabre_gnls$poc_var_tot <- apply(pred_gnls, 2, var) # total variance per prediction, for prediction total uncertainty

# plot
ggplot(galabre_gnls, aes(x = mes_for_fit))+
  geom_line(aes(y = poc_pred_lower, ymax = poc_pred_upper), col = "gray50")+
  geom_line(aes(y = poc_pred_upper), col = "gray50")+
  geom_point(aes(y = poc_percent, col = "measured"), alpha = 0.5, size = 0.5)+
  geom_point(aes(y = poc_fitted, col = "fitted with all events"), size = 2)+
  geom_point(aes(y = poc_boot_pred, col ="poc_boot_pred"), alpha = 0.5, size = 1)+
  scale_color_manual(values = c("darkblue","gray50","lightblue"))+
  geom_abline(slope = 0, intercept = aspt_value, col = "darkred")+
  annotate(geom = "label", label = formula_pocfitg, x = Inf, y = Inf, hjust = 1.1, vjust = 1.1)+
  labs(x = "MES, mg/L", y = "POC, %", colour = "", shape = "", title = "POC predicted from MES",subtitle = "Prediction interval in grey")+
  theme_minimal()+
  theme(legend.position = "bottom")

# plot variance
ggplot(galabre_gnls, aes(x = mes_for_fit))+
  geom_line(aes(y = poc_var_mean, col = "model variance"))+
  geom_line(aes(y = poc_var_tot, col = "total variance (includes noise)"))+
  scale_color_manual(values = c("lightblue", "darkblue"))+
  scale_x_continuous(trans = "log", breaks = c(0.01,0.1,1,10,50))+
  labs(x = "MES, g/L", y = "variance")+
  theme_minimal()
    
```

## No aspt

### Fit GNLS model 

```{r fit-poc-mes-gnls-nas}

# fit gnls
pocfitg_nas <- gnls(
  poc_percent ~ a*mes_for_fit^b,
  data = select(poc_galabre, c(mes_for_fit, poc_percent)),
  start = list(a = coef(pocfit)[[2]], b = coef(pocfit)[[1]]), # on utilise les valeurs de pocfit comme coefficients initiaux
  weights = varPower(value = 1, form = ~ fitted(.)),
  control = gnlsControl(nlsTol = 1e-3, tolerance = 1e-4)
)

# summary 
summary(pocfitg_nas) %>% print()

# variance parameters
theta_nas <- as.numeric(coef(pocfitg_nas$modelStruct$varStruct, unconstrained = F))
sigma_gnls_nas <- pocfitg_nas$sigma

# formula
formula_pocfitg_nas <- paste("GNLS:", round(coef(pocfitg_nas)[1], 3), "x MES ^", round(coef(pocfitg_nas)[2],3), sep = "")

## model function 
f <- function(x, a, b){
  a * x ^ b
}
```


### GNLS bootstrap

```{r intervalles-de-confiance-bootstrap-nas, eval = T}
coefs_boot_nas <- matrix(NA, nrow = n_boot, ncol = 2, dimnames = list(NULL, c("a","b")))
                     

for(i in seq_len(n_boot)){
  
  idx_boot <- sample(n_obs, replace = T)
  df_boot <- poc_galabre[idx_boot, c("mes_for_fit","poc_percent")]
  
  tryCatch(
    {fit_init <- nls(
      poc_percent ~ a * mes_for_fit^b,
      data = df_boot,
      start = coef(pocfitg_nas))
      # fit init is necessary to find the correct starting values for gnls. Otherwise, too much convergence result in extreme values in a and b

      pocfit_bg <- gnls(
      poc_percent~a*mes_for_fit^b,
      data = df_boot,
      start = coef(fit_init),
      weights = varPower(form = ~fitted(.)),
      control = gnlsControl(nlsTol = 1e-3, tolerance = 1e-4, maxIter = 200))
      
      coefs_boot_nas[i,] <- coef(pocfit_bg)
      }, 
    error = function(e) NULL) 
}

# removes NA
coefs_boot_nas <- na.omit(coefs_boot_nas)

# compute POC
fitted_boot_nas <- apply(coefs_boot_nas, 1, function(p){p["a"] * poc_galabre$mes_for_fit^p["b"]}) # MC worlds in columns
fitted_boot_nas_ic <- apply(fitted_boot_nas, 1, quantile, 
                 probs = c(0.025, 0.5, 0.975), na.rm = TRUE) # prediction intervals
fitted_boot__nasmean <- apply(fitted_boot_nas, 1, mean) # meet bottstrapped valur

# intergrates in poc_galabre
poc_galabre_boot_nas <- poc_galabre %>% mutate(poc_fitted = fitted_boot__nasmean, upr = fitted_boot_nas_ic[3, ], lwr = fitted_boot_nas_ic[1,])

```



```{r get-coefs-if-no-knit, eval = F}
write.csv(coefs_boot_nas, "coefs_boot_nas.csv")
write.csv(poc_galabre_boot_nas, "poc_galabre_boot_nas.csv")

coefs_boot_nas <- read.csv("coefs_boot_nas.csv")
poc_galabre_boot_nas <- read.csv("poc_galabre_boot_nas.csv")
```

```{r plot-intervalles-de-confiance-bootstrap-nas}

apply(coefs_boot_nas, 2, quantile, probs = c(0.025, 0.975)) %>% knitr::kable() #ic coef

ggplot(as.data.frame(coefs_boot_nas))+
  geom_point(aes(x = a, y = b))+
  theme_minimal()+
  theme(legend.position = "none")

ggplot(poc_galabre_boot_nas)+
  geom_point(aes(x=mes_for_fit, y = poc_percent, col = "measured", shape = "measured"))+ 
  geom_point(aes(x=mes_for_fit, y = poc_fitted, col = "fitted", shape = "fitted"))+ 
  geom_ribbon(aes(x = mes_for_fit, ymin = lwr, ymax = upr), fill = "gray80", alpha = 0.5)+
  geom_abline(slope = 0, intercept = aspt_value, col = "darkred")+
  annotate(geom = "label", label = formula_pocfitg_nas, x = Inf, y = Inf, hjust = 1.1, vjust = 1.1)+
  scale_color_manual(values = c("darkblue", "lightblue"))+
  labs(x = "MES, mg/L", y = "POC, %", colour = "", shape = "", title = "POC% measured and fitted vs MES measured",subtitle = "Confidence interval in grey")+
  theme_minimal()

ggplot(poc_galabre_boot_nas, aes(x=poc_percent))+
  geom_point(aes(y=poc_fitted), col = "darkblue")+ 
  geom_errorbar(aes(ymin = lwr, ymax = upr), fill = "gray80", alpha = 0.5)+
  geom_abline(slope = 1, intercept = 0, col = "darkred")+
  annotate(geom = "label", label = formula_pocfitg_nas, x = Inf, y = Inf, hjust = 1.1, vjust = 1.1)+
  labs(x = "POC measured", y = "POC fitted", colour = "", shape = "", title = "POC fitted vs measured",subtitle = "Confidence interval in grey")+
  theme_minimal()
```


### GNLS extension to galabre

**mes_for_fit** contient beaucoup de zéros. Ils ne peuvent pas être inclus dans le modèle parce qu'il est instable avec 0^(-b). On va fitter les autres lignes et imposer POC% = 0 pour les lignes où MES = 0

```{r constant-numbers-nas}
# prepare dataframe
galabre_nas <- galabre %>% filter(year %in% complete_years)
galabre_nas$mes_for_fit <- galabre_nas$cmes_g.L
with(galabre_nas, sum(mes_for_fit == 0 | is.na(mes_for_fit), na.rm = T)) # 462553

na_lines <- which(is.na(galabre_nas$mes_for_fit)) # 0
zero_lines <- which(galabre_nas$mes_for_fit == 0)
fit_lines <- which(galabre_nas$mes_for_fit != 0 & !is.na(galabre_nas$mes_for_fit))

galabre_nas_pwl <- galabre_nas[fit_lines, ]
galabre_nas_pwl$aspt <- aspt_value # from nls fitting

nrow_boot <- nrow(coefs_boot_nas)
nrow_galabre_nas <- nrow(galabre_nas)
```


```{r pred-galabre-gnls-nas, cache.lazy = F}
# predict POC pour mes > 0
poc_fitted_nas <- predict(pocfitg_nas, newdata = galabre_nas_pwl, na.action = na.pass)
galabre_nas$poc_fitted <- NA
galabre_nas[fit_lines, ]$poc_fitted <- poc_fitted_nas
galabre_nas[zero_lines, ]$poc_fitted <- 0


# MES matrix
mes_meas <- matrix(galabre_nas$mes_for_fit, nrow = nrow_boot, ncol = nrow_galabre_nas, byrow = T) # repeats nrow_boot times the vector isere_for_gnls$q_m3.s
mes_noise <- matrix(rnorm(nrow_boot*nrow_galabre_nas, mean = 0, sd = mes_u), nrow = nrow_boot, ncol = nrow_galabre_nas) # 
mes_mat <- mes_meas * (1 + mes_noise) # final value of q, with noise. 

# Prediction matrix, no model noise
mu_gnls <- f(mes_mat, coefs_boot_nas[,"a"], coefs_boot_nas[,"b"])

# Prediction matrix, with noise
noise_mat_gnls <- matrix(NA_real_, nrow = nrow_boot, ncol = nrow_galabre_nas)
sigma_mat_gnls <- sigma_gnls_nas * abs(mu_gnls)^theta_nas # variance depends on predicted value

noise_mat_gnls <- matrix(rnorm(nrow_boot*nrow_galabre_nas, mean = 0, sd = 1), nrow = nrow_boot, ncol = nrow_galabre_nas)
noise_mat_gnls <- noise_mat_gnls*sigma_mat_gnls

pred_gnls <- mu_gnls + noise_mat_gnls

mes_mat_zeros <- which(mes_mat == 0)
pred_gnls[mes_mat_zeros] <- 0

#pred_gnls <- pmin(pmax(pred_gnls, 0), 100) # clampe pred_nls pour éviter les intervalles de prédiction en dessous de zéro (et au dessus de 100, mais on ne devrait pas avoir ce cas) 

# Prediction interval 
pi <- t(apply(pred_gnls, 2, quantile, probs = c(0.025, 0.975), na.rm = T))
colnames(pi) <- c("lower", "upper")

# Mean bootstrap value
boot_pred_gnls <- colMeans(pred_gnls, na.rm = T)

## insert in galabre_nas
galabre_nas <- galabre_nas %>% mutate(poc_boot_pred = boot_pred_gnls,
                          poc_pred_lower = pi[,1],
                          poc_pred_upper = pi[,2])

```

```{r get-galabre-if-no-knit}
write.csv(galabre_nas, "galabre_nas.csv")

galabre_nas <- read.csv("galabre_nas.csv")

```


```{r plot-galabre-nas}

# plot
ggplot(galabre_nas, aes(x = mes_for_fit))+
  geom_line(aes(y = poc_pred_lower), col = "gray70")+
  geom_line(aes(y = poc_pred_upper), col = "gray70")+
  geom_point(aes(y = poc_percent, col = "measured"), alpha = 0.5, size = 0.5)+
  geom_point(aes(y = poc_fitted, col = "fitted with all events"), size = 2)+
  geom_point(aes(y = poc_boot_pred, col ="poc_boot_pred"), alpha = 0.5, size = 1)+
  scale_color_manual(values = c("darkblue","gray50","lightblue"))+
  geom_abline(slope = 0, intercept = aspt_value, col = "darkred")+
  annotate(geom = "label", label = formula_pocfitg_nas, x = Inf, y = Inf, hjust = 1.1, vjust = 1.1)+
  labs(x = "MES, mg/L", y = "POC, %", colour = "", shape = "", title = "POC predicted from MES",subtitle = "Prediction interval in grey")+
  theme_minimal()+
  theme(legend.position = "bottom")
```


```{r variance, eval = F}
mu_gnls <- readRDS("mu_ref.rds")
pred_gnls <- readRDS("pred_ref.rds")

# variances
galabre_nas$poc_var_mean <- apply(mu_gnls, 2, var) # variance of fit parameters + MES 
galabre_nas$poc_var_tot <- apply(pred_gnls, 2, var) # total variance per prediction, for prediction total uncertainty


# plot variance
ggplot(galabre_nas, aes(x = mes_for_fit))+
  geom_line(aes(y = poc_var_mean, col = "model variance"))+
  geom_line(aes(y = poc_var_tot, col = "total variance (includes noise)"))+
  scale_color_manual(values = c("lightblue", "darkblue"))+
  scale_x_continuous(trans = "log", breaks = c(0.01,0.1,1,10,50))+
  labs(x = "MES, g/L", y = "variance")+
  theme_minimal()
    
```


# Reference annual and interannual fluxes 



```{r annual-flux-reference, eval = T, cache.lazy = F}
# create matrix of q
q_meas <- matrix(galabre_nas$q_m3.s, nrow = nrow_boot, ncol = nrow_galabre_nas, byrow = T) # repeats nrow_boot times the vector galabre_nas$q_m3.s
q_noise <- matrix(rnorm(nrow_boot*nrow_galabre_nas, mean = 0, sd = q_u), nrow = nrow_boot, ncol = nrow_galabre_nas) # creates a noise in percent (proportion), between 0 and 10%
q_mat <- q_meas * (1 + q_noise) # final value of q, with noise

# Instant flux matrix
flux_ton.s_mat <- pred_gnls*mes_mat*1e-6*q_mat*1e-2*10*60 #pred_gnls * mes_mat : poc in g/L converted to ton/L; q_mat converted from m3/s to L/s. We consider no uncertainty on period, that is uniformely 10 minutes. 

# Get index for the columns corresponding to the same year
index_years <- sapply(unique(galabre_nas$year), function(y){which(galabre_nas$year == y)}) # list of indices corresponding to each year

# Annual flux
annual_flux_ton.y <- sapply(index_years, function(idx){apply(flux_ton.s_mat[,idx], 1, sum, na.rm = T)}) # sum of fluxes per year, for each iteration of the bootstrap. Result is a matrix with nrow_boot rows and 19 columns (1 per year)
annual_flux_pi <- apply(annual_flux_ton.y, 2, quantile, probs = c(0.025, 0.5, 0.975), na.rm = T) # prediction interval for annual fluxes, per year. 3 lignes, 19 columns
annual_flux_mean <- colMeans(annual_flux_ton.y, na.rm = T) # mean annual flux per year. 1 vector
annual_flux_sd <- apply(annual_flux_ton.y, 2, sd, na.rm = T) # standard deviation of annual flux per year. Is just an estimate of goodness of mean, not as good as than the confidence interval. 

# Merge in df
annual_flux_df <- data.frame(year = unique(galabre_nas$year), 
                        annual_flux_mean = annual_flux_mean, 
                        annual_flux_variability = annual_flux_sd, 
                        annual_flux_pi_lower = annual_flux_pi[1,], 
                        annual_flux_pi_upper = annual_flux_pi[3,])
```



```{r interannual-flux-reference, eval = T}
interannual_flux_ton.y <- rowMeans(annual_flux_ton.y, na.rm = T) # mean interannual flux per iteration of the bootstrap
interannual_flux_pi <- quantile(interannual_flux_ton.y, probs = c(0.025, 0.5, 0.975), na.rm = T) # prediction interval
interannual_flux_mean <- mean(interannual_flux_ton.y, na.rm = T) # mean interannual flux
interannual_flux_variability <- sd(annual_flux_mean, na.rm = T) # standard deviation of interannual flux per year

interannual_flux_df <- data.frame(year = "interannual", annual_flux_mean = interannual_flux_mean, 
                                  annual_flux_variability = interannual_flux_variability,
                        annual_flux_pi_lower = interannual_flux_pi[1], 
                        annual_flux_pi_upper = interannual_flux_pi[3])

total_flux_df <- rbind(annual_flux_df, interannual_flux_df)
total_flux_df$group <- c(rep("annual", length(unique(galabre_nas$year))), "interannual")
```


```{r write-interannual-flux-reference, eval = F}
write.csv(total_flux_df, "total_flux_df.csv")
```

```{r run-of-no-knit-interranual flux, eval = F}
total_flux_df <- read.csv("total_flux_df.csv")
```


```{r interannual-flux-reference-plot}

ggplot()+
  geom_col(data = total_flux_df, aes(x=year, y = annual_flux_mean, fill = group))+
    geom_errorbar(data = total_flux_df, aes(x = year, ymin = annual_flux_pi_lower, ymax = annual_flux_pi_upper, col = "prediction interval"), width = 0.3, linewidth = 0.8)+
  geom_errorbar(data = filter(total_flux_df, year == "interannual"), aes(x = year, ymin = annual_flux_mean - annual_flux_variability, ymax = annual_flux_mean + annual_flux_variability, col = "interannual variability"), width = 0.2, linewidth = 0.8, linetype = 2)+
  scale_fill_manual(values = c("annual" = "lightblue", "interannual" = "indianred"))+
  scale_color_manual(values = c("prediction interval" = "darkblue", "interannual variability" = "darkred"), name = "")+
   labs(x = "Year", y = "Flux (ton/year)", fill = "")+
  theme_minimal()+
  theme(axis.text.x = element_text(angle = 45, hjust = 1), legend.position = "bottom")

knitr::kable(total_flux_df, digits = 2, row.names = F) %>% kableExtra::kable_styling()


```


```{r clean, eval = F}
saveRDS(mes_mat, "mes_mat_ref.rds")
saveRDS(q_mat, "q_mat_ref.rds")
saveRDS(flux_ton.s_mat, "flux_ton.s_mat_ref.rds")
saveRDS(pred_gnls, "pred_ref.rds")
saveRDS(mu_gnls, "mu_ref.rds")

write.csv(interannual_flux_ton.y, "interannual_flux_ton.y.csv")

sort(sapply(ls(), function(x) object.size(get(x))), decreasing = TRUE)

rm(poc_galabre)
rm(poc_galabre_boot_nas)
rm(galabre_nas_pwl)
rm(galabre) 
rm(galabre_nas)

rm(mes_mat)
rm(mes_meas)
rm(mes_noise)
rm(mes_mat_zeros)

rm(mu_gnls) 
rm(sigma_mat_gnls)
rm(noise_mat_gnls)

rm(q_mat)
rm(q_meas)
rm(q_noise)

rm(pred_gnls)
rm(boot_pred_gnls)
rm(pi)
rm(poc_fitted_nas)
rm(flux_ton.s_mat)

gc()
```

# Time steps

Time step for CMES and Q: 10 min 

```{r common-data-time-steps}
galabre_time <- galabre_nas

mes_u <- 0.05
q_u <- 0.1

set.seed(2502)

nrow_boot <- nrow(coefs_boot_nas)

library(future.apply)
plan(multisession, workers = 6)

```


Random CMES over timer period: mean Q, then GNLS. 

## 1-Hour

```{r pred-galabre-gnls-hour, cache.lazy = F}
# prepare df
galabre_group_hour <- galabre_time %>% 
  mutate(day = format(as.Date(DateHeure), "%Y-%m-%d"), 
         year = year(DateHeure),
         hour =  hour(DateHeure),
         DateHeure = NULL) %>% group_by(hour,day,year) # group galabre_time by hour
nrow_hour <- n_groups(galabre_group_hour)

# get mean q
q_hour <- galabre_group_hour %>% select(c("hour", "q_m3.s")) %>% summarize_all(list("q_mean" = mean, "q_sd" = sd)) %>% ungroup() # mean of Q for each hour2


# creates matrix for MES
galabre_mes_hour <- galabre_group_hour %>% select(c("hour", "mes_for_fit")) %>% summarize("list_mes" = list(mes_for_fit)) %>% ungroup() # creates a list of mes for each hour2

list_mes_hour <- galabre_mes_hour$list_mes
mes_hour_random <- future_replicate(nrow_boot, vapply(list_mes_hour, 
                                                function(x) sample(x,1), numeric(1)),
                              future.seed = T) %>% 
                    t() # matrix of mes: one random sample per hour2, replicated 1000 times


mes_hour_noise <- matrix(rnorm(nrow_boot*nrow_hour, mean = 0, sd = mes_u), nrow = nrow_boot, ncol = nrow_hour) 
mes_mat_hour <- mes_hour_random * (1 + mes_hour_noise) # final value of mes, with noise

mes_mean <- colMeans(mes_mat_hour) # mean mes: that would be the mean of the 1000-times randomly choosen MES+noise. tiré vers le haut par les fortes valeurs, alors qu'il y a bcp de zéros
mes_median <- apply(mes_mat_hour, 2, median)

# Prediction matrix
mu_hour <- f(mes_mat_hour, coefs_boot_nas[,"a"], coefs_boot_nas[,"b"])


# Prediction matrix, with noise
sigma_mat_hour <- sigma_gnls_nas * abs(mu_hour)^theta_nas

noise_mat_hour <- matrix(rnorm(nrow_boot*nrow_hour, mean = 0, sd = 1), nrow = nrow_boot, ncol = nrow_hour)
noise_mat_hour <- noise_mat_hour*sigma_mat_hour

pred_hour <- mu_hour + noise_mat_hour

zero_mes_mat <- which(mes_hour_random == 0)
pred_hour[zero_mes_mat] <- 0

## computes prediction interval 
pi_hour <- t(apply(pred_hour, 2, quantile, probs = c(0.025, 0.975), na.rm = T))

colnames(pi_hour) <- c("lower", "upper")

boot_pred_hour <- colMeans(pred_hour, na.rm = T)



## insert in galabre_hour2
galabre_hour <- q_hour %>% mutate(
                          mes_for_fit = mes_mean, # keep name for "fitting model"predict" function
                          poc_boot_pred = boot_pred_hour,
                          poc_pred_lower = pi_hour[,"lower"],
                          poc_pred_upper = pi_hour[,"upper"],
                          aspt = aspt_value)

galabre_hour$poc_fitted <- predict(pocfitg_nas, galabre_hour)

# variance 
galabre_hour$poc_var_mean <- apply(mu_hour, 2, var) # variance of fit parameters + MES 
galabre_hour$poc_var_tot <- apply(pred_hour, 2, var) # total variance per prediction, for prediction total uncertainty


# plot

ggplot(galabre_hour, aes(x = mes_for_fit))+
  #geom_line(aes(y = poc_pred_lower), col = "gray70")+
  #geom_line(aes(y = poc_pred_upper), col = "gray70")+
  geom_ribbon(aes(ymin = poc_pred_lower, ymax = poc_pred_upper), fill = "gray90", alpha = 0.5)+
  geom_point(aes(y = poc_fitted, col = "fitted with all events"), size = 2)+
  geom_point(aes(y = poc_boot_pred, col ="poc_boot_pred"), alpha = 0.5, size = 1)+
  scale_color_manual(values = c("darkblue","lightblue"))+
  geom_abline(slope = 0, intercept = aspt_value, col = "darkred")+
  annotate(geom = "label", label = formula_pocfitg_nas, x = Inf, y = Inf, hjust = 1.1, vjust = 1.1)+
  labs(x = "MES, g/L", y = "POC %", colour = "", shape = "", title = "POC predicted from MES, random sampling every hour", subtitle = "Prediction interval in grey")+
  theme_minimal()+
  theme(legend.position = "bottom")

```
```{r annual-flux-hour, cache.lazy= F}

# creates matrix for Q

q_hour_mean <-  matrix(q_hour$q_mean, nrow = nrow_boot, ncol = nrow_hour, byrow = T)
q_noise <- matrix(rnorm(nrow_boot*nrow_hour, mean = 0, sd = q_u), nrow = nrow_boot, ncol = nrow_hour) # creates a noise in percent (proportion), between 0 and 10%
q_mat_hour <- q_hour_mean * (1 + q_noise) # final MC of q, with noise. SD NOT INCLUDED: will not always be available


# compute flux
flux_ton.s_mat_hour <- pred_hour*mes_mat_hour*1e-6*q_mat_hour*1e-2*60*60*1 #pred_hour * mes_mat : poc in mg/L converted to ton; q_mat converted from m3/s to L/s. Period : nb of seconds in 1 hour. 

# Get index for columns by year
index_years <- sapply(unique(galabre_hour$year), function(y){which(galabre_hour$year == y)}) # list of indices corresponding to each year

# annual flux
annual_flux_ton.y_hour <- sapply(index_years, function(idx){apply(flux_ton.s_mat_hour[,idx], 1, sum, na.rm = T)}) # sum of fluxes per year, for each iteration of the bootstrap. Result is a matrix with nrow_boot rows and 19 columns (1 per year)

annual_flux_hour_pi <- apply(annual_flux_ton.y_hour, 2, quantile, probs = c(0.025, 0.5, 0.975), na.rm = T) # confidence interval for annual fluxes, per year. 3 lignes, 19 columns
annual_flux_hour_mean <- colMeans(annual_flux_ton.y_hour, na.rm = T) # mean annual flux per year. 1 vector

annual_flux_hour_sd <- apply(annual_flux_ton.y_hour, 2, sd, na.rm = T) # standard deviation of annual flux per year. Is just an estimate of goodness of mean, not as good as than the confidence interval. 
 

annual_flux_hour_df <- data.frame(year = unique(galabre_hour$year), 
                        annual_flux_mean = annual_flux_hour_mean, 
                        annual_flux_variability = annual_flux_hour_sd, 
                        annual_flux_pi_lower = annual_flux_hour_pi[1,], 
                        annual_flux_pi_upper = annual_flux_hour_pi[3,])

interannual_flux_ton.y_hour <- rowMeans(annual_flux_ton.y_hour, na.rm = T) # mean interannual flux per iteration of the bootstrap
interannual_flux_pi_hour <- quantile(interannual_flux_ton.y_hour, probs = c(0.025, 0.5, 0.975), na.rm = T) # prediction interval
interannual_flux_mean_hour <- mean(interannual_flux_ton.y_hour, na.rm = T) # mean interannual flux
interannual_flux_variability_hour <- sd(annual_flux_hour_mean, na.rm = T) # standard deviation of interannual flux per year

interannual_flux_hour_df <- data.frame(year = "interannual", annual_flux_mean = interannual_flux_mean_hour, 
                                  annual_flux_variability = interannual_flux_variability_hour,
                        annual_flux_pi_lower = interannual_flux_pi_hour[1], 
                        annual_flux_pi_upper = interannual_flux_pi_hour[3])

total_flux_hour_df <- rbind(annual_flux_hour_df, interannual_flux_hour_df)
total_flux_hour_df$group <- c(rep("annual", length(unique(galabre_hour$year))), "interannual")

ggplot()+
  geom_col(data = total_flux_hour_df, 
           aes(x=year, y = annual_flux_mean, fill = group))+
  geom_errorbar(data = total_flux_hour_df, 
                aes(x = year, ymin = annual_flux_pi_lower, ymax = annual_flux_pi_upper, col = "prediction interval"),
                width = 0.3, size = 0.8)+
  geom_errorbar(data = filter(total_flux_hour_df, year == "interannual"), 
                aes(x = year, ymin = annual_flux_mean - annual_flux_variability, 
                    ymax = annual_flux_mean + annual_flux_variability, col = "interannual variability"),
                width = 0.2, size = 0.8, linetype = 2)+
  scale_fill_manual(values = c("annual" = "lightblue", "interannual" = "indianred"))+
  scale_color_manual(values = c("prediction interval" = "darkblue", "interannual variability" = "darkred"), name = "")+
   labs(x = "Year", y = "Flux, from 2-hourly mean values (ton/year)", fill = "")+
  theme_minimal()+
  theme(axis.text.x = element_text(angle = 45, hjust = 1), legend.position = "bottom")
```

## 2-Hour

```{r pred-galabre-gnls-hour2, cache.lazy = F}
# prepare df
galabre_group_hour2 <- galabre_time %>% 
  mutate(day = format(as.Date(DateHeure), "%Y-%m-%d"), 
         year = year(DateHeure),
         hour2 =  floor(hour(DateHeure) / 2) * 2, # creates a 2-hours interval
         DateHeure = NULL) %>% group_by(hour2,day,year) # group galabre_time by hour
nrow_hour2 <- n_groups(galabre_group_hour2)

# get mean q
q_hour2 <- galabre_group_hour2 %>% select(c("hour2", "q_m3.s")) %>% summarize_all(list("q_mean" = mean, "q_sd" = sd)) %>% ungroup() # mean of Q for each hour2


# creates matrix for MES
galabre_mes_hour2 <- galabre_group_hour2 %>% select(c("hour2", "mes_for_fit")) %>% summarize("list_mes" = list(mes_for_fit)) %>% ungroup() # creates a list of mes for each hour2

list_mes_hour2 <- galabre_mes_hour2$list_mes
mes_hour2_random <- future_replicate(nrow_boot, vapply(list_mes_hour2, 
                                                function(x) sample(x,1), numeric(1)),
                              future.seed = T) %>% 
                    t() # matrix of mes: one random sample per hour2, replicated 1000 times

zero_mes_mat2 <- which(mes_hour2_random == 0)

mes_hour2_noise <- matrix(rnorm(nrow_boot*nrow_hour2, mean = 0, sd = mes_u), nrow = nrow_boot, ncol = nrow_hour2) 
mes_mat_hour2 <- mes_hour2_random * (1 + mes_hour2_noise) # final value of mes, with noise

mes_mean <- colMeans(mes_mat_hour2)

# Prediction matrix
mu_hour2 <- f(mes_mat_hour2, coefs_boot_nas[,"a"], coefs_boot_nas[,"b"])


# Prediction matrix, with noise
sigma_mat_hour2 <- sigma_gnls_nas * abs(mu_hour2)^theta_nas

noise_mat_hour2 <- matrix(rnorm(nrow_boot*nrow_hour2, mean = 0, sd = 1), nrow = nrow_boot, ncol = nrow_hour2)
noise_mat_hour2 <- noise_mat_hour2*sigma_mat_hour2

pred_hour2 <- mu_hour2 + noise_mat_hour2
pred_hour2[zero_mes_mat2] <- 0
#pred_hour2 <- pmin(pmax(pred_hour2, 0), 100) # clampe pred_nls pour éviter les intervalles de prédiction en dessous de zéro


## computes prediction interval 
pi_hour2 <- t(
  apply(pred_hour2, 2, quantile, probs = c(0.025, 0.975), na.rm = T)
)

colnames(pi_hour2) <- c("lower", "upper")

boot_pred_hour2 <- colMeans(pred_hour2, na.rm = T)

## insert in galabre_hour2
galabre_hour2 <- q_hour2 %>% mutate(
                          mes_for_fit = mes_mean, # keep name for "fitting model"predict" function
                          poc_boot_pred = boot_pred_hour2,
                          poc_pred_lower = pi_hour2[,"lower"],
                          poc_pred_upper = pi_hour2[,"upper"],
                          aspt = aspt_value)

galabre_hour2$poc_fitted <- predict(pocfitg_nas, galabre_hour2)

# variance 
galabre_hour2$poc_var_mean <- apply(mu_hour2, 2, var) # variance of fit parameters + MES 
galabre_hour2$poc_var_tot <- apply(pred_hour2, 2, var) # total variance per prediction, for prediction total uncertainty


# plot

ggplot(galabre_hour2, aes(x = mes_for_fit))+
  geom_line(aes(y = poc_pred_lower), col = "gray70")+
  geom_line(aes(y = poc_pred_upper), col = "gray70")+
  geom_point(aes(y = poc_fitted, col = "fitted with all events"), size = 2)+
  geom_point(aes(y = poc_boot_pred, col ="poc_boot_pred"), alpha = 0.5, size = 0.5)+
  scale_color_manual(values = c("darkblue","lightblue"))+
  geom_abline(slope = 0, intercept = aspt_value, col = "darkred")+
  annotate(geom = "label", label = formula_pocfitg_nas, x = Inf, y = Inf, hjust = 1.1, vjust = 1.1)+
  labs(x = "MES, g/L", y = "POC %", colour = "", shape = "", title = "POC predicted from MES, random sampling every 2nd hour", subtitle = "Prediction interval in grey")+
  theme_minimal()+
  theme(legend.position = "bottom")

```

```{r annual-flux-hour2, cache.lazy= F}

# creates matrix for Q

q_hour2_mean <-  matrix(q_hour2$q_mean, nrow = nrow_boot, ncol = nrow_hour2, byrow = T)
q_noise <- matrix(rnorm(nrow_boot*nrow_hour2, mean = 0, sd = q_u), nrow = nrow_boot, ncol = nrow_hour2) # creates a noise in percent (proportion), between 0 and 10%
q_mat_hour2 <- q_hour2_mean * (1 + q_noise) # final MC of q, with noise. SD NOT INCLUDED: will not always be available


# compute flux
flux_ton.s_mat_hour2 <- pred_hour2*mes_mat_hour2*1e-6*q_mat_hour2*1e-2*60*60*2 #pred_hour2 * mes_mat : poc in mg/L converted to ton; q_mat converted from m3/s to L/s. Period : nb of seconds in 1 hour2. 

# Get index for columns by year
index_years <- sapply(unique(galabre_hour2$year), function(y){which(galabre_hour2$year == y)}) # list of indices corresponding to each year

# annual flux
annual_flux_ton.y_hour2 <- sapply(index_years, function(idx){apply(flux_ton.s_mat_hour2[,idx], 1, sum, na.rm = T)}) # sum of fluxes per year, for each iteration of the bootstrap. Result is a matrix with nrow_boot rows and 19 columns (1 per year)

annual_flux_hour2_pi <- apply(annual_flux_ton.y_hour2, 2, quantile, probs = c(0.025, 0.5, 0.975), na.rm = T) # confidence interval for annual fluxes, per year. 3 lignes, 19 columns
annual_flux_hour2_mean <- colMeans(annual_flux_ton.y_hour2, na.rm = T) # mean annual flux per year. 1 vector

annual_flux_hour2_sd <- apply(annual_flux_ton.y_hour2, 2, sd, na.rm = T) # standard deviation of annual flux per year. Is just an estimate of goodness of mean, not as good as than the confidence interval. 
 

annual_flux_hour2_df <- data.frame(year = unique(galabre_hour2$year), 
                        annual_flux_mean = annual_flux_hour2_mean, 
                        annual_flux_variability = annual_flux_hour2_sd, 
                        annual_flux_pi_lower = annual_flux_hour2_pi[1,], 
                        annual_flux_pi_upper = annual_flux_hour2_pi[3,])

interannual_flux_ton.y_hour2 <- rowMeans(annual_flux_ton.y_hour2, na.rm = T) # mean interannual flux per iteration of the bootstrap
interannual_flux_pi_hour2 <- quantile(interannual_flux_ton.y_hour2, probs = c(0.025, 0.5, 0.975), na.rm = T) # prediction interval
interannual_flux_mean_hour2 <- mean(interannual_flux_ton.y_hour2, na.rm = T) # mean interannual flux
interannual_flux_variability_hour2 <- sd(annual_flux_hour2_mean, na.rm = T) # standard deviation of interannual flux per year

interannual_flux_hour2_df <- data.frame(year = "interannual", annual_flux_mean = interannual_flux_mean_hour2, 
                                  annual_flux_variability = interannual_flux_variability_hour2,
                        annual_flux_pi_lower = interannual_flux_pi_hour2[1], 
                        annual_flux_pi_upper = interannual_flux_pi_hour2[3])

total_flux_hour2_df <- rbind(annual_flux_hour2_df, interannual_flux_hour2_df)
total_flux_hour2_df$group <- c(rep("annual", length(unique(galabre_hour2$year))), "interannual")

ggplot()+
  geom_col(data = total_flux_hour2_df, 
           aes(x=year, y = annual_flux_mean, fill = group))+
  geom_errorbar(data = total_flux_hour2_df, 
                aes(x = year, ymin = annual_flux_pi_lower, ymax = annual_flux_pi_upper, col = "prediction interval"),
                width = 0.3, size = 0.8)+
  geom_errorbar(data = filter(total_flux_hour2_df, year == "interannual"), 
                aes(x = year, ymin = annual_flux_mean - annual_flux_variability, 
                    ymax = annual_flux_mean + annual_flux_variability, col = "interannual variability"),
                width = 0.2, size = 0.8, linetype = 2)+
  scale_fill_manual(values = c("annual" = "lightblue", "interannual" = "indianred"))+
  scale_color_manual(values = c("prediction interval" = "darkblue", "interannual variability" = "darkred"), name = "")+
   labs(x = "Year", y = "Flux, from 2-hourly mean values (ton/year)", fill = "")+
  theme_minimal()+
  theme(axis.text.x = element_text(angle = 45, hjust = 1), legend.position = "bottom")
```


## 4-Hour

```{r pred-galabre-gnls-hour4, cache.lazy = F}
# prepare df
galabre_group_hour4 <- galabre_time %>% 
  mutate(day = format(as.Date(DateHeure), "%Y-%m-%d"), 
         year = year(DateHeure),
         hour4 =  floor(hour(DateHeure) / 4) * 4, # creates a 2-hours interval
         DateHeure = NULL) %>% group_by(hour4,day,year) # group galabre_time by hour
nrow_hour4 <- n_groups(galabre_group_hour4)

# get mean q
q_hour4 <- galabre_group_hour4 %>% select(c("hour4", "q_m3.s")) %>% summarize_all(list("q_mean" = mean, "q_sd" = sd)) %>% ungroup() # mean of Q for each hour4


# creates matrix for MES
galabre_mes_hour4 <- galabre_group_hour4 %>% select(c("hour4", "mes_for_fit")) %>% summarize("list_mes" = list(mes_for_fit)) %>% ungroup() # creates a list of mes for each hour4

list_mes_hour4 <- galabre_mes_hour4$list_mes
mes_hour4_random <- future_replicate(nrow_boot, vapply(list_mes_hour4, 
                                                function(x) sample(x,1), numeric(1)),
                              future.seed = T) %>% 
                    t() # matrix of mes: one random sample per hour4, replicated 1000 times

mes_hour4_noise <- matrix(rnorm(nrow_boot*nrow_hour4, mean = 0, sd = mes_u), nrow = nrow_boot, ncol = nrow_hour4) 
mes_mat_hour4 <- mes_hour4_random * (1 + mes_hour4_noise) # final value of mes, with noise

zero_mes_mat4 <- which(mes_hour4_random == 0)

mes_mean <- colMeans(mes_mat_hour4)

# Prediction matrix
mu_hour4 <- f(mes_mat_hour4, coefs_boot_nas[,"a"], coefs_boot_nas[,"b"])


# Prediction matrix, with noise
sigma_mat_hour4 <- sigma_gnls_nas * abs(mu_hour4)^theta_nas

noise_mat_hour4 <- matrix(rnorm(nrow_boot*nrow_hour4, mean = 0, sd = 1), nrow = nrow_boot, ncol = nrow_hour4)
noise_mat_hour4 <- noise_mat_hour4*sigma_mat_hour4

pred_hour4 <- mu_hour4 + noise_mat_hour4
#pred_hour4 <- pmin(pmax(pred_hour4, 0), 100) # clampe pred_nls pour éviter les intervalles de prédiction en dessous de zéro
pred_hour4[zero_mes_mat4] <- 0


## computes prediction interval 
pi_hour4 <- t(
  apply(pred_hour4, 2, quantile, probs = c(0.025, 0.975), na.rm = T)
)

colnames(pi_hour4) <- c("lower", "upper")

boot_pred_hour4 <- colMeans(pred_hour4, na.rm = T)

## insert in galabre_hour4
galabre_hour4 <- q_hour4 %>% mutate(
                          mes_for_fit = mes_mean, # keep name for "fitting model"predict" function
                          poc_boot_pred = boot_pred_hour4,
                          poc_pred_lower = pi_hour4[,"lower"],
                          poc_pred_upper = pi_hour4[,"upper"],
                          aspt = aspt_value)

galabre_hour4$poc_fitted <- predict(pocfitg_nas, galabre_hour4)

# variance 
galabre_hour4$poc_var_mean <- apply(mu_hour4, 2, var) # variance of fit parameters + MES 
galabre_hour4$poc_var_tot <- apply(pred_hour4, 2, var) # total variance per prediction, for prediction total uncertainty


# plot

ggplot(galabre_hour4, aes(x = mes_for_fit))+
  geom_line(aes(y = poc_pred_lower), col = "gray70")+
  geom_line(aes(y = poc_pred_upper), col = "gray70")+
  geom_point(aes(y = poc_fitted, col = "fitted with all events"), size = 2)+
  geom_point(aes(y = poc_boot_pred, col ="poc_boot_pred"), alpha = 0.5, size = 0.5)+
  scale_color_manual(values = c("darkblue","lightblue"))+
  geom_abline(slope = 0, intercept = aspt_value, col = "darkred")+
  annotate(geom = "label", label = formula_pocfitg_nas, x = Inf, y = Inf, hjust = 1.1, vjust = 1.1)+
  labs(x = "MES, g/L", y = "POC %", colour = "", shape = "", title = "POC predicted from MES, random sampling every 4 hour", subtitle = "Prediction interval in grey")+
  theme_minimal()+
  theme(legend.position = "bottom")


```

```{r annual-flux-hour4, cache.lazy= F}

# creates matrix for Q

q_hour4_mean <-  matrix(q_hour4$q_mean, nrow = nrow_boot, ncol = nrow_hour4, byrow = T)
q_noise <- matrix(rnorm(nrow_boot*nrow_hour4, mean = 0, sd = q_u), nrow = nrow_boot, ncol = nrow_hour4) # creates a noise in percent (proportion), between 0 and 10%
q_mat_hour4 <- q_hour4_mean * (1 + q_noise) # final MC of q, with noise. SD NOT INCLUDED: will not always be available


# compute flux
flux_ton.s_mat_hour4 <- pred_hour4*mes_mat_hour4*1e-6*q_mat_hour4*1e-2*60*60*4 #pred_hour4 * mes_mat : poc in mg/L converted to ton; q_mat converted from m3/s to L/s. Period : nb of seconds in 1 hour4. 

# Get index for columns by year
index_years <- sapply(unique(galabre_hour4$year), function(y){which(galabre_hour4$year == y)}) # list of indices corresponding to each year

# annual flux
annual_flux_ton.y_hour4 <- sapply(index_years, function(idx){apply(flux_ton.s_mat_hour4[,idx], 1, sum, na.rm = T)}) # sum of fluxes per year, for each iteration of the bootstrap. Result is a matrix with nrow_boot rows and 19 columns (1 per year)

annual_flux_hour4_pi <- apply(annual_flux_ton.y_hour4, 2, quantile, probs = c(0.025, 0.5, 0.975), na.rm = T) # confidence interval for annual fluxes, per year. 3 lignes, 19 columns
annual_flux_hour4_mean <- colMeans(annual_flux_ton.y_hour4, na.rm = T) # mean annual flux per year. 1 vector

annual_flux_hour4_sd <- apply(annual_flux_ton.y_hour4, 2, sd, na.rm = T) # standard deviation of annual flux per year. Is just an estimate of goodness of mean, not as good as than the confidence interval. 
 

annual_flux_hour4_df <- data.frame(year = unique(galabre_hour4$year), 
                        annual_flux_mean = annual_flux_hour4_mean, 
                        annual_flux_variability = annual_flux_hour4_sd, 
                        annual_flux_pi_lower = annual_flux_hour4_pi[1,], 
                        annual_flux_pi_upper = annual_flux_hour4_pi[3,])

interannual_flux_ton.y_hour4 <- rowMeans(annual_flux_ton.y_hour4, na.rm = T) # mean interannual flux per iteration of the bootstrap
interannual_flux_pi_hour4 <- quantile(interannual_flux_ton.y_hour4, probs = c(0.025, 0.5, 0.975), na.rm = T) # prediction interval
interannual_flux_mean_hour4 <- mean(interannual_flux_ton.y_hour4, na.rm = T) # mean interannual flux
interannual_flux_variability_hour4 <- sd(annual_flux_hour4_mean, na.rm = T) # standard deviation of interannual flux per year

interannual_flux_hour4_df <- data.frame(year = "interannual", annual_flux_mean = interannual_flux_mean_hour4, 
                                  annual_flux_variability = interannual_flux_variability_hour4,
                        annual_flux_pi_lower = interannual_flux_pi_hour4[1], 
                        annual_flux_pi_upper = interannual_flux_pi_hour4[3])

total_flux_hour4_df <- rbind(annual_flux_hour4_df, interannual_flux_hour4_df)
total_flux_hour4_df$group <- c(rep("annual", length(unique(galabre_hour4$year))), "interannual")

ggplot()+
  geom_col(data = total_flux_hour4_df, 
           aes(x=year, y = annual_flux_mean, fill = group))+
  geom_errorbar(data = total_flux_hour4_df, 
                aes(x = year, ymin = annual_flux_pi_lower, ymax = annual_flux_pi_upper, col = "prediction interval"),
                width = 0.3, size = 0.8)+
  geom_errorbar(data = filter(total_flux_hour4_df, year == "interannual"), 
                aes(x = year, ymin = annual_flux_mean - annual_flux_variability, 
                    ymax = annual_flux_mean + annual_flux_variability, col = "interannual variability"),
                width = 0.2, size = 0.8, linetype = 2)+
  scale_fill_manual(values = c("annual" = "lightblue", "interannual" = "indianred"))+
  scale_color_manual(values = c("prediction interval" = "darkblue", "interannual variability" = "darkred"), name = "")+
   labs(x = "Year", y = "Flux, from 4-hourly mean values (ton/year)", fill = "")+
  theme_minimal()+
  theme(axis.text.x = element_text(angle = 45, hjust = 1), legend.position = "bottom")
```



## 8-Hour

```{r pred-galabre-gnls-hour8, cache.lazy = F}
# prepare df
galabre_group_hour8 <- galabre_time %>% 
  mutate(day = format(as.Date(DateHeure), "%Y-%m-%d"), 
         year = year(DateHeure),
         hour8 =  floor(hour(DateHeure) / 8) * 8, # creates a 2-hours interval
         DateHeure = NULL) %>% group_by(hour8,day,year) # group galabre_time by hour
nrow_hour8 <- n_groups(galabre_group_hour8)

# get mean q
q_hour8 <- galabre_group_hour8 %>% select(c("hour8", "q_m3.s")) %>% summarize_all(list("q_mean" = mean, "q_sd" = sd)) %>% ungroup() # mean of Q for each hour8


# creates matrix for MES
galabre_mes_hour8 <- galabre_group_hour8 %>% select(c("hour8", "mes_for_fit")) %>% summarize("list_mes" = list(mes_for_fit)) %>% ungroup() # creates a list of mes for each hour8

list_mes_hour8 <- galabre_mes_hour8$list_mes
mes_hour8_random <- future_replicate(nrow_boot, vapply(list_mes_hour8, 
                                                function(x) sample(x,1), numeric(1)),
                              future.seed = T) %>% 
                    t() # matrix of mes: one random sample per hour8, replicated 1000 times

mes_hour8_noise <- matrix(rnorm(nrow_boot*nrow_hour8, mean = 0, sd = mes_u), nrow = nrow_boot, ncol = nrow_hour8) 
mes_mat_hour8 <- mes_hour8_random * (1 + mes_hour8_noise) # final value of mes, with noise

mes_mean <- colMeans(mes_mat_hour8)

zero_mes_mat8 <- which(mes_hour8_random == 0)

# Prediction matrix
mu_hour8 <- f(mes_mat_hour8, coefs_boot_nas[,"a"], coefs_boot_nas[,"b"])


# Prediction matrix, with noise
sigma_mat_hour8 <- sigma_gnls_nas * abs(mu_hour8)^theta_nas

noise_mat_hour8 <- matrix(rnorm(nrow_boot*nrow_hour8, mean = 0, sd = 1), nrow = nrow_boot, ncol = nrow_hour8)
noise_mat_hour8 <- noise_mat_hour8*sigma_mat_hour8

pred_hour8 <- mu_hour8 + noise_mat_hour8
pred_hour8[zero_mes_mat8] <- 0
#pred_hour8 <- pmin(pmax(pred_hour8, 0), 100) # clampe pred_nls pour éviter les intervalles de prédiction en dessous de zéro


## computes prediction interval 
pi_hour8 <- t(
  apply(pred_hour8, 2, quantile, probs = c(0.025, 0.975), na.rm = T)
)

colnames(pi_hour8) <- c("lower", "upper")

boot_pred_hour8 <- colMeans(pred_hour8, na.rm = T)

## insert in galabre_hour8
galabre_hour8 <- q_hour8 %>% mutate(
                          mes_for_fit = mes_mean, # keep name for "fitting model"predict" function
                          poc_boot_pred = boot_pred_hour8,
                          poc_pred_lower = pi_hour8[,"lower"],
                          poc_pred_upper = pi_hour8[,"upper"],
                          aspt = aspt_value)

galabre_hour8$poc_fitted <- predict(pocfitg_nas, galabre_hour8)

# variance 
galabre_hour8$poc_var_mean <- apply(mu_hour8, 2, var) # variance of fit parameters + MES 
galabre_hour8$poc_var_tot <- apply(pred_hour8, 2, var) # total variance per prediction, for prediction total uncertainty


# plot

ggplot(galabre_hour8, aes(x = mes_for_fit))+
  geom_line(aes(y = poc_pred_lower), col = "gray70")+
  geom_line(aes(y = poc_pred_upper), col = "gray70")+
  geom_point(aes(y = poc_fitted, col = "fitted with all events"), size = 2)+
  geom_point(aes(y = poc_boot_pred, col ="poc_boot_pred"), alpha = 0.5, size = 0.5)+
  scale_color_manual(values = c("darkblue","lightblue"))+
  geom_abline(slope = 0, intercept = aspt_value, col = "darkred")+
  annotate(geom = "label", label = formula_pocfitg_nas, x = Inf, y = Inf, hjust = 1.1, vjust = 1.1)+
  labs(x = "MES, g/L", y = "POC %", colour = "", shape = "", title = "POC predicted from MES, random sampling every 8 hour", subtitle = "Prediction interval in grey")+
  theme_minimal()+
  theme(legend.position = "bottom")

```

```{r annual-flux-hour8, cache.lazy= F}

# creates matrix for Q

q_hour8_mean <-  matrix(q_hour8$q_mean, nrow = nrow_boot, ncol = nrow_hour8, byrow = T)
q_noise <- matrix(rnorm(nrow_boot*nrow_hour8, mean = 0, sd = q_u), nrow = nrow_boot, ncol = nrow_hour8) # creates a noise in percent (proportion), between 0 and 10%
q_mat_hour8 <- q_hour8_mean * (1 + q_noise) # final MC of q, with noise. SD NOT INCLUDED: will not always be available


# compute flux
flux_ton.s_mat_hour8 <- pred_hour8*mes_mat_hour8*1e-6*q_mat_hour8*1e-2*60*60*8 #pred_hour8 * mes_mat : poc in mg/L converted to ton; q_mat converted from m3/s to L/s. Period : nb of seconds in 1 hour8. 

# Get index for columns by year
index_years <- sapply(unique(galabre_hour8$year), function(y){which(galabre_hour8$year == y)}) # list of indices corresponding to each year

# annual flux
annual_flux_ton.y_hour8 <- sapply(index_years, function(idx){apply(flux_ton.s_mat_hour8[,idx], 1, sum, na.rm = T)}) # sum of fluxes per year, for each iteration of the bootstrap. Result is a matrix with nrow_boot rows and 19 columns (1 per year)

annual_flux_hour8_pi <- apply(annual_flux_ton.y_hour8, 2, quantile, probs = c(0.025, 0.5, 0.975), na.rm = T) # confidence interval for annual fluxes, per year. 3 lignes, 19 columns
annual_flux_hour8_mean <- colMeans(annual_flux_ton.y_hour8, na.rm = T) # mean annual flux per year. 1 vector

annual_flux_hour8_sd <- apply(annual_flux_ton.y_hour8, 2, sd, na.rm = T) # standard deviation of annual flux per year. Is just an estimate of goodness of mean, not as good as than the confidence interval. 
 

annual_flux_hour8_df <- data.frame(year = unique(galabre_hour8$year), 
                        annual_flux_mean = annual_flux_hour8_mean, 
                        annual_flux_variability = annual_flux_hour8_sd, 
                        annual_flux_pi_lower = annual_flux_hour8_pi[1,], 
                        annual_flux_pi_upper = annual_flux_hour8_pi[3,])


interannual_flux_ton.y_hour8 <- rowMeans(annual_flux_ton.y_hour8, na.rm = T) # mean interannual flux per iteration of the bootstrap
interannual_flux_pi_hour8 <- quantile(interannual_flux_ton.y_hour8, probs = c(0.025, 0.5, 0.975), na.rm = T) # prediction interval
interannual_flux_mean_hour8 <- mean(interannual_flux_ton.y_hour8, na.rm = T) # mean interannual flux
interannual_flux_variability_hour8 <- sd(annual_flux_hour8_mean, na.rm = T) # standard deviation of interannual flux per year

interannual_flux_hour8_df <- data.frame(year = "interannual", annual_flux_mean = interannual_flux_mean_hour8, 
                                  annual_flux_variability = interannual_flux_variability_hour8,
                        annual_flux_pi_lower = interannual_flux_pi_hour8[1], 
                        annual_flux_pi_upper = interannual_flux_pi_hour8[3])

total_flux_hour8_df <- rbind(annual_flux_hour8_df, interannual_flux_hour8_df)
total_flux_hour8_df$group <- c(rep("annual", length(unique(galabre_hour8$year))), "interannual")

ggplot()+
  geom_col(data = total_flux_hour8_df, 
           aes(x=year, y = annual_flux_mean, fill = group))+
  geom_errorbar(data = total_flux_hour8_df, 
                aes(x = year, ymin = annual_flux_pi_lower, ymax = annual_flux_pi_upper, col = "prediction interval"),
                width = 0.3, size = 0.8)+
  geom_errorbar(data = filter(total_flux_hour8_df, year == "interannual"), 
                aes(x = year, ymin = annual_flux_mean - annual_flux_variability, 
                    ymax = annual_flux_mean + annual_flux_variability, col = "interannual variability"),
                width = 0.2, size = 0.8, linetype = 2)+
  scale_fill_manual(values = c("annual" = "lightblue", "interannual" = "indianred"))+
  scale_color_manual(values = c("prediction interval" = "darkblue", "interannual variability" = "darkred"), name = "")+
   labs(x = "Year", y = "Flux, from 4-hourly mean values (ton/year)", fill = "")+
  theme_minimal()+
  theme(axis.text.x = element_text(angle = 45, hjust = 1), legend.position = "bottom")
```


## Day 

```{r pred-galabre-gnls-day, cache.lazy = F}
# prepare df
galabre_group_day <- galabre_time %>% mutate(day = format(as.Date(DateHeure), "%Y-%m-%d"), 
                                             year = year(DateHeure), 
                                             DateHeure = NULL) %>% 
                                      group_by(day,year) # group galabre_time by day
nrow_day <- n_groups(galabre_group_day)

# get mean q
q_day <- galabre_group_day %>% select(c("day", "q_m3.s")) %>% summarize_all(list("q_mean" = mean, "q_sd" = sd)) %>% ungroup() # mean of Q for each day


# creates matrix for MES
galabre_mes_day <- galabre_group_day %>% select(c("day", "mes_for_fit")) %>% summarize("list_mes" = list(mes_for_fit)) %>% ungroup() # creates a list of mes for each day
mes_day_random <- replicate(nrow_boot, sapply(galabre_mes_day$list_mes, function(x) sample(x,1)))%>% t() # matrix of mes: one random sample per day, replicated 1000 times
mes_day_noise <- matrix(rnorm(nrow_boot*nrow_day, mean = 0, sd = mes_u), nrow = nrow_boot, ncol = nrow_day) 
mes_mat_day <- mes_day_random * (1 + mes_day_noise) # final value of mes, with noise

mes_mean <- colMeans(mes_mat_day)

# Prediction matrix
mu_day <- f(mes_mat_day, coefs_boot_nas[,"a"], coefs_boot_nas[,"b"])


# Prediction matrix, with noise
sigma_mat_day <- sigma_gnls_nas * abs(mu_day)^theta_nas

noise_mat_day <- matrix(rnorm(nrow_boot*nrow_day, mean = 0, sd = 1), nrow = nrow_boot, ncol = nrow_day)
noise_mat_day <- noise_mat_day*sigma_mat_day

pred_day <- mu_day + noise_mat_day

zero_mes_day <- which(mes_day_random == 0)
pred_day[zero_mes_day] <- 0
#pred_day <- pmin(pmax(pred_day, 0), 100) # clampe pred_nls pour éviter les intervalles de prédiction en dessous de zéro


## computes prediction interval 
pi_day <- t(
  apply(pred_day, 2, quantile, probs = c(0.025, 0.975), na.rm = T)
)

colnames(pi_day) <- c("lower", "upper")

boot_pred_day <- colMeans(pred_day, na.rm = T)

## insert in galabre_day
galabre_day <- q_day %>% mutate(
                          mes_for_fit = mes_mean, # keep name for "fitting model"predict" function
                          poc_boot_pred = boot_pred_day,
                          poc_pred_lower = pi_day[,"lower"],
                          poc_pred_upper = pi_day[,"upper"],
                          aspt = aspt_value)

galabre_day$poc_fitted <- predict(pocfitg_nas, galabre_day)

# variance 
galabre_day$poc_var_mean <- apply(mu_day, 2, var) # variance of fit parameters + MES 
galabre_day$poc_var_tot <- apply(pred_day, 2, var) # total variance per prediction, for prediction total uncertainty


# plot

ggplot(galabre_day, aes(x = mes_for_fit))+
  geom_line(aes(y = poc_pred_lower), col = "gray70")+
  geom_line(aes(y = poc_pred_upper), col = "gray50")+
  geom_point(aes(y = poc_fitted, col = "fitted with all events"), size = 2)+
  geom_point(aes(y = poc_boot_pred, col ="poc_boot_pred"), alpha = 0.5, size = 0.5)+
  scale_color_manual(values = c("darkblue","lightblue"))+
  geom_abline(slope = 0, intercept = aspt_value, col = "darkred")+
  annotate(geom = "label", label = formula_pocfitg_nas, x = Inf, y = Inf, hjust = 1.1, vjust = 1.1)+
  labs(x = "MES, g/L", y = "POC %", colour = "", shape = "", title = "POC predicted from MES, random sampling every day", subtitle = "Prediction interval in grey")+
  theme_minimal()+
  theme(legend.position = "bottom")

```

```{r annual-flux-day, cache.lazy=F}

# creates matrix for Q

q_day_mean <-  matrix(q_day$q_mean, nrow = nrow_boot, ncol = nrow_day, byrow = T)
q_noise <- matrix(rnorm(nrow_boot*nrow_day, mean = 0, sd = q_u), nrow = nrow_boot, ncol = nrow_day) # creates a noise in percent (proportion), between 0 and 10%
q_mat_day <- q_day_mean * (1 + q_noise) # final MC of q, with noise. SD NOT INCLUDED: will not always be available


# compute flux
flux_ton.s_mat_day <- pred_day*mes_mat_day*1e-6*q_mat_day*1e-2*60*60*24 #pred_day * mes_mat : poc in mg/L converted to ton; q_mat converted from m3/s to L/s. Period : nb of seconds in 1 day. 

# Get index for columns by year
index_years <- sapply(unique(galabre_day$year), function(y){which(galabre_day$year == y)}) # list of indices corresponding to each year

# annual flux
annual_flux_ton.y_day <- sapply(index_years, function(idx){apply(flux_ton.s_mat_day[,idx], 1, sum, na.rm = T)}) # sum of fluxes per year, for each iteration of the bootstrap. Result is a matrix with nrow_boot rows and 19 columns (1 per year)

annual_flux_day_pi <- apply(annual_flux_ton.y_day, 2, quantile, probs = c(0.025, 0.5, 0.975), na.rm = T) # confidence interval for annual fluxes, per year. 3 lignes, 19 columns
annual_flux_day_mean <- colMeans(annual_flux_ton.y_day, na.rm = T) # mean annual flux per year. 1 vector

annual_flux_day_sd <- apply(annual_flux_ton.y_day, 2, sd, na.rm = T) # standard deviation of annual flux per year. Is just an estimate of goodness of mean, not as good as than the confidence interval. 
 

annual_flux_day_df <- data.frame(year = unique(galabre_day$year), 
                        annual_flux_mean = annual_flux_day_mean, 
                        annual_flux_variability = annual_flux_day_sd, 
                        annual_flux_pi_lower = annual_flux_day_pi[1,], 
                        annual_flux_pi_upper = annual_flux_day_pi[3,])

interannual_flux_ton.y_day <- rowMeans(annual_flux_ton.y_day, na.rm = T) # mean interannual flux per iteration of the bootstrap
interannual_flux_pi_day <- quantile(interannual_flux_ton.y_day, probs = c(0.025, 0.5, 0.975), na.rm = T) # prediction interval
interannual_flux_mean_day <- mean(interannual_flux_ton.y_day, na.rm = T) # mean interannual flux
interannual_flux_variability_day <- sd(annual_flux_day_mean, na.rm = T) # standard deviation of interannual flux per year

interannual_flux_day_df <- data.frame(year = "interannual", annual_flux_mean = interannual_flux_mean_day, 
                                  annual_flux_variability = interannual_flux_variability_day,
                        annual_flux_pi_lower = interannual_flux_pi_day[1], 
                        annual_flux_pi_upper = interannual_flux_pi_day[3])

total_flux_day_df <- rbind(annual_flux_day_df, interannual_flux_day_df)
total_flux_day_df$group <- c(rep("annual", length(unique(galabre_day$year))), "interannual")

ggplot()+
  geom_col(data = total_flux_day_df, aes(x=year, y = annual_flux_mean, fill = group))+
    geom_errorbar(data = total_flux_day_df, aes(x = year, ymin = annual_flux_pi_lower, ymax = annual_flux_pi_upper, col = "prediction interval"), width = 0.3, size = 0.8)+
  geom_errorbar(data = filter(total_flux_day_df, year == "interannual"), aes(x = year, ymin = annual_flux_mean - annual_flux_variability, ymax = annual_flux_mean + annual_flux_variability, col = "interannual variability"), width = 0.2, size = 0.8, linetype = 2)+
  scale_fill_manual(values = c("annual" = "lightblue", "interannual" = "indianred"))+
  scale_color_manual(values = c("prediction interval" = "darkblue", "interannual variability" = "darkred"), name = "")+
   labs(x = "Year", y = "Flux, from dayly mean values (ton/year)", fill = "")+
  theme_minimal()+
  theme(axis.text.x = element_text(angle = 45, hjust = 1), legend.position = "bottom")
```

## 2 Day 

```{r pred-galabre-gnls-day2, cache.lazy = F}
# prepare df
galabre_group_day2 <- galabre_time %>% mutate(day = as.Date(format(as.Date(DateHeure), "%Y-%m-%d")), day2 = floor(as.numeric(day - min(day)) / 2), year = year(DateHeure), DateHeure = NULL) %>% group_by(day2,year) # group galabre_time by day
nrow_day2 <- n_groups(galabre_group_day2)

# get mean q
q_day2 <- galabre_group_day2 %>% select(c("day2", "q_m3.s")) %>% summarize_all(list("q_mean" = mean, "q_sd" = sd)) %>% ungroup() # mean of Q for each day2


# creates matrix for MES
galabre_mes_day2 <- galabre_group_day2 %>% select(c("day2", "mes_for_fit")) %>% summarize("list_mes" = list(mes_for_fit)) %>% ungroup() # creates a list of mes for each day2
mes_day2_random <- replicate(nrow_boot, sapply(galabre_mes_day2$list_mes, function(x) sample(x,1)))%>% t() # matrix of mes: one random sample per day2, replicated 1000 times
mes_day2_noise <- matrix(rnorm(nrow_boot*nrow_day2, mean = 0, sd = mes_u), nrow = nrow_boot, ncol = nrow_day2) 
mes_mat_day2 <- mes_day2_random * (1 + mes_day2_noise) # final value of mes, with noise

mes_mean <- colMeans(mes_mat_day2)

# Prediction matrix
mu_day2 <- f(mes_mat_day2, coefs_boot_nas[,"a"], coefs_boot_nas[,"b"])


# Prediction matrix, with noise
sigma_mat_day2 <- sigma_gnls_nas * abs(mu_day2)^theta_nas

noise_mat_day2 <- matrix(rnorm(nrow_boot*nrow_day2, mean = 0, sd = 1), nrow = nrow_boot, ncol = nrow_day2)
noise_mat_day2 <- noise_mat_day2*sigma_mat_day2

pred_day2 <- mu_day2 + noise_mat_day2
zero_mes_day2 <- which(mes_day2_random == 0)
pred_day2[zero_mes_day2] <- 0
#pred_day2 <- pmin(pmax(pred_day2, 0), 100) # clampe pred_nls pour éviter les intervalles de prédiction en dessous de zéro


## computes prediction interval 
pi_day2 <- t(
  apply(pred_day2, 2, quantile, probs = c(0.025, 0.975), na.rm = T)
)

colnames(pi_day2) <- c("lower", "upper")

boot_pred_day2 <- colMeans(pred_day2, na.rm = T)

## insert in galabre_day2
galabre_day2 <- q_day2 %>% mutate(
                          mes_for_fit = mes_mean, # keep name for "fitting model"predict" function
                          poc_boot_pred = boot_pred_day2,
                          poc_pred_lower = pi_day2[,"lower"],
                          poc_pred_upper = pi_day2[,"upper"],
                          aspt = aspt_value)

galabre_day2$poc_fitted <- predict(pocfitg_nas, galabre_day2)

# variance 
galabre_day2$poc_var_mean <- apply(mu_day2, 2, var) # variance of fit parameters + MES 
galabre_day2$poc_var_tot <- apply(pred_day2, 2, var) # total variance per prediction, for prediction total uncertainty


# plot

ggplot(galabre_day2, aes(x = mes_for_fit))+
  geom_line(aes(y = poc_pred_lower), col = "gray70")+
  geom_line(aes(y = poc_pred_upper), col = "gray70")+
  geom_point(aes(y = poc_fitted, col = "fitted with all events"), size = 2)+
  geom_point(aes(y = poc_boot_pred, col ="poc_boot_pred"), alpha = 0.5, size = 0.5)+
  scale_color_manual(values = c("darkblue","lightblue"))+
  geom_abline(slope = 0, intercept = aspt_value, col = "darkred")+
  annotate(geom = "label", label = formula_pocfitg_nas, x = Inf, y = Inf, hjust = 1.1, vjust = 1.1)+
  labs(x = "MES, g/L", y = "POC %", colour = "", shape = "", title = "POC predicted from MES, random sampling every 2nd day", subtitle = "Prediction interval in grey")+
  theme_minimal()+
  theme(legend.position = "bottom")

```

```{r annual-flux-day2, cache.lazy=F}

# creates matrix for Q

q_day2_mean <-  matrix(q_day2$q_mean, nrow = nrow_boot, ncol = nrow_day2, byrow = T)
q_noise <- matrix(rnorm(nrow_boot*nrow_day2, mean = 0, sd = q_u), nrow = nrow_boot, ncol = nrow_day2) # creates a noise in percent (proportion), between 0 and 10%
q_mat_day2 <- q_day2_mean * (1 + q_noise) # final MC of q, with noise. SD NOT INCLUDED: will not always be available


# compute flux
flux_ton.s_mat_day2 <- pred_day2*mes_mat_day2*1e-6*q_mat_day2*1e-2*60*60*24*2 #pred_day2 * mes_mat : poc in mg/L converted to ton; q_mat converted from m3/s to L/s. Period : nb of seconds in 1 day2. 

# Get index for columns by year
index_years <- sapply(unique(galabre_day2$year), function(y){which(galabre_day2$year == y)}) # list of indices corresponding to each year

# annual flux
annual_flux_ton.y_day2 <- sapply(index_years, function(idx){apply(flux_ton.s_mat_day2[,idx], 1, sum, na.rm = T)}) # sum of fluxes per year, for each iteration of the bootstrap. Result is a matrix with nrow_boot rows and 19 columns (1 per year)

annual_flux_day2_pi <- apply(annual_flux_ton.y_day2, 2, quantile, probs = c(0.025, 0.5, 0.975), na.rm = T) # confidence interval for annual fluxes, per year. 3 lignes, 19 columns
annual_flux_day2_mean <- colMeans(annual_flux_ton.y_day2, na.rm = T) # mean annual flux per year. 1 vector

annual_flux_day2_sd <- apply(annual_flux_ton.y_day2, 2, sd, na.rm = T) # standard deviation of annual flux per year. Is just an estimate of goodness of mean, not as good as than the confidence interval. 
 

annual_flux_day2_df <- data.frame(year = unique(galabre_day2$year), 
                        annual_flux_mean = annual_flux_day2_mean, 
                        annual_flux_variability = annual_flux_day2_sd, 
                        annual_flux_pi_lower = annual_flux_day2_pi[1,], 
                        annual_flux_pi_upper = annual_flux_day2_pi[3,])


interannual_flux_ton.y_day2 <- rowMeans(annual_flux_ton.y_day2, na.rm = T) # mean interannual flux per iteration of the bootstrap
interannual_flux_pi_day2 <- quantile(interannual_flux_ton.y_day2, probs = c(0.025, 0.5, 0.975), na.rm = T) # prediction interval
interannual_flux_mean_day2 <- mean(interannual_flux_ton.y_day2, na.rm = T) # mean interannual flux
interannual_flux_variability_day2 <- sd(annual_flux_day2_mean, na.rm = T) # standard deviation of interannual flux per year

interannual_flux_day2_df <- data.frame(year = "interannual", annual_flux_mean = interannual_flux_mean_day2, 
                                  annual_flux_variability = interannual_flux_variability_day2,
                        annual_flux_pi_lower = interannual_flux_pi_day2[1], 
                        annual_flux_pi_upper = interannual_flux_pi_day2[3])

total_flux_day2_df <- rbind(annual_flux_day2_df, interannual_flux_day2_df)
total_flux_day2_df$group <- c(rep("annual", length(unique(galabre_day2$year))), "interannual")

ggplot()+
  geom_col(data = total_flux_day2_df, aes(x=year, y = annual_flux_mean, fill = group))+
    geom_errorbar(data = total_flux_day2_df, aes(x = year, ymin = annual_flux_pi_lower, ymax = annual_flux_pi_upper, col = "prediction interval"), width = 0.3, size = 0.8)+
  geom_errorbar(data = filter(total_flux_day2_df, year == "interannual"), aes(x = year, ymin = annual_flux_mean - annual_flux_variability, ymax = annual_flux_mean + annual_flux_variability, col = "interannual variability"), width = 0.2, size = 0.8, linetype = 2)+
  scale_fill_manual(values = c("annual" = "lightblue", "interannual" = "indianred"))+
  scale_color_manual(values = c("prediction interval" = "darkblue", "interannual variability" = "darkred"), name = "")+
   labs(x = "Year", y = "Flux, from bi-dayly mean values (ton/year)", fill = "")+
  theme_minimal()+
  theme(axis.text.x = element_text(angle = 45, hjust = 1), legend.position = "bottom")
```

## 4 days

```{r pred-galabre-gnls-day4, cache.lazy = F}
# prepare df
galabre_group_day4 <- galabre_time %>% mutate(day = as.Date(format(as.Date(DateHeure), "%Y-%m-%d")), day4 = floor(as.numeric(day - min(day)) / 4), year = year(DateHeure), DateHeure = NULL) %>% group_by(day4,year) # group galabre_time by day
nrow_day4 <- n_groups(galabre_group_day4)

# get mean q
q_day4 <- galabre_group_day4 %>% select(c("day4", "q_m3.s")) %>% summarize_all(list("q_mean" = mean, "q_sd" = sd)) %>% ungroup() # mean of Q for each day4


# creates matrix for MES
galabre_mes_day4 <- galabre_group_day4 %>% select(c("day4", "mes_for_fit")) %>% summarize("list_mes" = list(mes_for_fit)) %>% ungroup() # creates a list of mes for each day4
mes_day4_random <- replicate(nrow_boot, sapply(galabre_mes_day4$list_mes, function(x) sample(x,1)))%>% t() # matrix of mes: one random sample per day4, replicated 1000 times
mes_day4_noise <- matrix(rnorm(nrow_boot*nrow_day4, mean = 0, sd = mes_u), nrow = nrow_boot, ncol = nrow_day4) 
mes_mat_day4 <- mes_day4_random * (1 + mes_day4_noise) # final value of mes, with noise

mes_mean <- colMeans(mes_mat_day4)

# Prediction matrix
mu_day4 <- f(mes_mat_day4, coefs_boot_nas[,"a"], coefs_boot_nas[,"b"])


# Prediction matrix, with noise
sigma_mat_day4 <- sigma_gnls_nas * abs(mu_day4)^theta_nas

noise_mat_day4 <- matrix(rnorm(nrow_boot*nrow_day4, mean = 0, sd = 1), nrow = nrow_boot, ncol = nrow_day4)
noise_mat_day4 <- noise_mat_day4*sigma_mat_day4

pred_day4 <- mu_day4 + noise_mat_day4
zero_mes_day4 <- which(mes_day4_random == 0)
pred_day4[zero_mes_day4] <- 0
#pred_day4 <- pmin(pmax(pred_day4, 0), 100) # clampe pred_nls pour éviter les intervalles de prédiction en dessous de zéro


## computes prediction interval 
pi_day4 <- t(
  apply(pred_day4, 2, quantile, probs = c(0.025, 0.975), na.rm = T)
)

colnames(pi_day4) <- c("lower", "upper")

boot_pred_day4 <- colMeans(pred_day4, na.rm = T)

## insert in galabre_day4
galabre_day4 <- q_day4 %>% mutate(
                          mes_for_fit = mes_mean, # keep name for "fitting model"predict" function
                          poc_boot_pred = boot_pred_day4,
                          poc_pred_lower = pi_day4[,"lower"],
                          poc_pred_upper = pi_day4[,"upper"],
                          aspt = aspt_value)

galabre_day4$poc_fitted <- predict(pocfitg_nas, galabre_day4)

# variance 
galabre_day4$poc_var_mean <- apply(mu_day4, 2, var) # variance of fit parameters + MES 
galabre_day4$poc_var_tot <- apply(pred_day4, 2, var) # total variance per prediction, for prediction total uncertainty


# plot

ggplot(galabre_day4, aes(x = mes_for_fit))+
  geom_line(aes(y = poc_pred_lower), col = "gray70")+
  geom_line(aes(y = poc_pred_upper), col = "gray70")+
  geom_point(aes(y = poc_fitted, col = "fitted with all events"), size = 2)+
  geom_point(aes(y = poc_boot_pred, col ="poc_boot_pred"), alpha = 0.5, size = 1)+
  scale_color_manual(values = c("darkblue","lightblue"))+
  geom_abline(slope = 0, intercept = aspt_value, col = "darkred")+
  annotate(geom = "label", label = formula_pocfitg_nas, x = Inf, y = Inf, hjust = 1.1, vjust = 1.1)+
  labs(x = "MES, g/L", y = "POC %", colour = "", shape = "", title = "POC predicted from MES, random sampling every 4 day", subtitle = "Prediction interval in grey")+
  theme_minimal()+
  theme(legend.position = "bottom")

```

```{r annual-flux-day4, cache.lazy=F}

# creates matrix for Q

q_day4_mean <-  matrix(q_day4$q_mean, nrow = nrow_boot, ncol = nrow_day4, byrow = T)
q_noise <- matrix(rnorm(nrow_boot*nrow_day4, mean = 0, sd = q_u), nrow = nrow_boot, ncol = nrow_day4) # creates a noise in percent (proportion), between 0 and 10%
q_mat_day4 <- q_day4_mean * (1 + q_noise) # final MC of q, with noise. SD NOT INCLUDED: will not always be available


# compute flux
flux_ton.s_mat_day4 <- pred_day4*mes_mat_day4*1e-6*q_mat_day4*1e-2*60*60*24*4 #pred_day4 * mes_mat : poc in mg/L converted to ton; q_mat converted from m3/s to L/s. Period : nb of seconds in 1 day4. 

# Get index for columns by year
index_years <- sapply(unique(galabre_day4$year), function(y){which(galabre_day4$year == y)}) # list of indices corresponding to each year

# annual flux
annual_flux_ton.y_day4 <- sapply(index_years, function(idx){apply(flux_ton.s_mat_day4[,idx], 1, sum, na.rm = T)}) # sum of fluxes per year, for each iteration of the bootstrap. Result is a matrix with nrow_boot rows and 19 columns (1 per year)

annual_flux_day4_pi <- apply(annual_flux_ton.y_day4, 2, quantile, probs = c(0.025, 0.5, 0.975), na.rm = T) # confidence interval for annual fluxes, per year. 3 lignes, 19 columns
annual_flux_day4_mean <- colMeans(annual_flux_ton.y_day4, na.rm = T) # mean annual flux per year. 1 vector

annual_flux_day4_sd <- apply(annual_flux_ton.y_day4, 2, sd, na.rm = T) # standard deviation of annual flux per year. Is just an estimate of goodness of mean, not as good as than the confidence interval. 
 

annual_flux_day4_df <- data.frame(year = unique(galabre_day4$year), 
                        annual_flux_mean = annual_flux_day4_mean, 
                        annual_flux_variability = annual_flux_day4_sd, 
                        annual_flux_pi_lower = annual_flux_day4_pi[1,], 
                        annual_flux_pi_upper = annual_flux_day4_pi[3,])


interannual_flux_ton.y_day4 <- rowMeans(annual_flux_ton.y_day4, na.rm = T) # mean interannual flux per iteration of the bootstrap
interannual_flux_pi_day4 <- quantile(interannual_flux_ton.y_day4, probs = c(0.025, 0.5, 0.975), na.rm = T) # prediction interval
interannual_flux_mean_day4 <- mean(interannual_flux_ton.y_day4, na.rm = T) # mean interannual flux
interannual_flux_variability_day4 <- sd(annual_flux_day4_mean, na.rm = T) # standard deviation of interannual flux per year

interannual_flux_day4_df <- data.frame(year = "interannual", annual_flux_mean = interannual_flux_mean_day4, 
                                  annual_flux_variability = interannual_flux_variability_day4,
                        annual_flux_pi_lower = interannual_flux_pi_day4[1], 
                        annual_flux_pi_upper = interannual_flux_pi_day4[3])

total_flux_day4_df <- rbind(annual_flux_day4_df, interannual_flux_day4_df)
total_flux_day4_df$group <- c(rep("annual", length(unique(galabre_day4$year))), "interannual")

ggplot()+
  geom_col(data = total_flux_day4_df, aes(x=year, y = annual_flux_mean, fill = group))+
    geom_errorbar(data = total_flux_day4_df, aes(x = year, ymin = annual_flux_pi_lower, ymax = annual_flux_pi_upper, col = "prediction interval"), width = 0.3, size = 0.8)+
  geom_errorbar(data = filter(total_flux_day4_df, year == "interannual"), aes(x = year, ymin = annual_flux_mean - annual_flux_variability, ymax = annual_flux_mean + annual_flux_variability, col = "interannual variability"), width = 0.2, size = 0.8, linetype = 2)+
  scale_fill_manual(values = c("annual" = "lightblue", "interannual" = "indianred"))+
  scale_color_manual(values = c("prediction interval" = "darkblue", "interannual variability" = "darkred"), name = "")+
   labs(x = "Year", y = "Flux, from bi-dayly mean values (ton/year)", fill = "")+
  theme_minimal()+
  theme(axis.text.x = element_text(angle = 45, hjust = 1), legend.position = "bottom")
```


## Week

```{r pred-galabre-gnls-week, cache.lazy = F}
# prepare df
galabre_group_week <- galabre_time %>% mutate("week" = week(DateHeure), year = year(DateHeure), DateHeure = NULL) %>% group_by(week,year) # group galabre_time by week
nrow_week <- n_groups(galabre_group_week)

# get mean q
q_week <- galabre_group_week %>% select(c("week", "q_m3.s")) %>% summarize_all(list("q_mean" = mean, "q_sd" = sd)) %>% ungroup() # mean of Q for each week


# creates matrix for MES
galabre_mes_week <- galabre_group_week %>% select(c("week", "mes_for_fit")) %>% summarize("list_mes" = list(mes_for_fit)) %>% ungroup() # creates a list of mes for each week
mes_week_random <- replicate(nrow_boot, sapply(galabre_mes_week$list_mes, function(x) sample(x,1)))%>% t() # matrix of mes: one random sample per week, replicated 1000 times
mes_week_noise <- matrix(rnorm(nrow_boot*nrow_week, mean = 0, sd = mes_u), nrow = nrow_boot, ncol = nrow_week) 
mes_mat_week <- mes_week_random * (1 + mes_week_noise) # final value of mes, with noise

mes_mean <- colMeans(mes_mat_week)

# Prediction matrix
mu_week <- f(mes_mat_week, coefs_boot_nas[,"a"], coefs_boot_nas[,"b"])


# Prediction matrix, with noise
sigma_mat_week <- sigma_gnls_nas * abs(mu_week)^theta_nas

noise_mat_week <- matrix(rnorm(nrow_boot*nrow_week, mean = 0, sd = 1), nrow = nrow_boot, ncol = nrow_week)
noise_mat_week <- noise_mat_week*sigma_mat_week

pred_week <- mu_week + noise_mat_week
zero_mes_week <- which(mes_week_random == 0)
pred_week[zero_mes_week] <- 0
#pred_week <- pmin(pmax(pred_week, 0), 100) # clampe pred_nls pour éviter les intervalles de prédiction en dessous de zéro


## computes prediction interval 
pi_week <- t(
  apply(pred_week, 2, quantile, probs = c(0.025, 0.975), na.rm = T)
)

colnames(pi_week) <- c("lower", "upper")

boot_pred_week <- colMeans(pred_week, na.rm = T)

## insert in galabre_week
galabre_week <-q_week %>% mutate(
                          mes_for_fit = mes_mean, # keep name for "fitting model"predict" function
                          poc_boot_pred = boot_pred_week,
                          poc_pred_lower = pi_week[,"lower"],
                          poc_pred_upper = pi_week[,"upper"],
                          aspt = aspt_value)

galabre_week$poc_fitted <- predict(pocfitg_nas, galabre_week)
galabre_week$poc_fitted2

# variance 
galabre_week$poc_var_mean <- apply(mu_week, 2, var) # variance of fit parameters + MES 
galabre_week$poc_var_tot <- apply(pred_week, 2, var) # total variance per prediction, for prediction total uncertainty


# plot

ggplot(galabre_week, aes(x = mes_for_fit))+
  geom_line(aes(y = poc_pred_lower, ymax = poc_pred_upper), col = "gray50")+
  geom_line(aes(y = poc_pred_upper), col = "gray50")+
  geom_point(aes(y = poc_fitted, col = "fitted with all events"), size = 2)+
  geom_point(aes(y = poc_boot_pred, col ="poc_boot_pred"), alpha = 0.5, size = 0.5)+
  scale_color_manual(values = c("darkblue","lightblue"))+
  geom_abline(slope = 0, intercept = aspt_value, col = "darkred")+
  annotate(geom = "label", label = formula_pocfitg_nas, x = Inf, y = Inf, hjust = 1.1, vjust = 1.1)+
  labs(x = "MES, g/L", y = "POC %", colour = "", shape = "", title = "POC predicted from MES, random sampling every week", subtitle = "Prediction interval in grey")+
  theme_minimal()+
  theme(legend.position = "bottom")
```

```{r annual-flux-week, cache.lazy=F}

# creates matrix for Q

q_week_mean <-  matrix(q_week$q_mean, nrow = nrow_boot, ncol = nrow_week, byrow = T)
q_noise <- matrix(rnorm(nrow_boot*nrow_week, mean = 0, sd = q_u), nrow = nrow_boot, ncol = nrow_week) # creates a noise in percent (proportion), between 0 and 10%
q_mat_week <- q_week_mean * (1 + q_noise) # final MC of q, with noise. SD NOT INCLUDED: will not always be available


# compute flux
flux_ton.s_mat_week <- pred_week*mes_mat_week*1e-6*q_mat_week*1e-2*60*60*24*7 #pred_week * mes_mat : poc in mg/L converted to ton; q_mat converted from m3/s to L/s. Period : nb of seconds in 1 week. 

# Get index for columns by year
index_years <- sapply(unique(galabre_week$year), function(y){which(galabre_week$year == y)}) # list of indices corresponding to each year

# annual flux
annual_flux_ton.y_week <- sapply(index_years, function(idx){apply(flux_ton.s_mat_week[,idx], 1, sum, na.rm = T)}) # sum of fluxes per year, for each iteration of the bootstrap. Result is a matrix with nrow_boot rows and 19 columns (1 per year)

annual_flux_week_pi <- apply(annual_flux_ton.y_week, 2, quantile, probs = c(0.025, 0.5, 0.975), na.rm = T) # confidence interval for annual fluxes, per year. 3 lignes, 19 columns
annual_flux_week_mean <- colMeans(annual_flux_ton.y_week, na.rm = T) # mean annual flux per year. 1 vector

annual_flux_week_sd <- apply(annual_flux_ton.y_week, 2, sd, na.rm = T) # standard deviation of annual flux per year. Is just an estimate of goodness of mean, not as good as than the confidence interval. 
 

annual_flux_week_df <- data.frame(year = unique(galabre_week$year), 
                        annual_flux_mean = annual_flux_week_mean, 
                        annual_flux_variability = annual_flux_week_sd, 
                        annual_flux_pi_lower = annual_flux_week_pi[1,], 
                        annual_flux_pi_upper = annual_flux_week_pi[3,])

interannual_flux_ton.y_week <- rowMeans(annual_flux_ton.y_week, na.rm = T) # mean interannual flux per iteration of the bootstrap
interannual_flux_pi_week <- quantile(interannual_flux_ton.y_week, probs = c(0.025, 0.5, 0.975), na.rm = T) # prediction interval
interannual_flux_mean_week <- mean(interannual_flux_ton.y_week, na.rm = T) # mean interannual flux
interannual_flux_variability_week <- sd(annual_flux_week_mean, na.rm = T) # standard deviation of interannual flux per year

interannual_flux_week_df <- data.frame(year = "interannual", annual_flux_mean = interannual_flux_mean_week, 
                                  annual_flux_variability = interannual_flux_variability_week,
                        annual_flux_pi_lower = interannual_flux_pi_week[1], 
                        annual_flux_pi_upper = interannual_flux_pi_week[3])

total_flux_week_df <- rbind(annual_flux_week_df, interannual_flux_week_df)
total_flux_week_df$group <- c(rep("annual", length(unique(galabre_week$year))), "interannual")

ggplot()+
  geom_col(data = total_flux_week_df, aes(x=year, y = annual_flux_mean, fill = group))+
    geom_errorbar(data = total_flux_week_df, aes(x = year, ymin = annual_flux_pi_lower, ymax = annual_flux_pi_upper, col = "prediction interval"), width = 0.3, size = 0.8)+
  geom_errorbar(data = filter(total_flux_week_df, year == "interannual"), aes(x = year, ymin = annual_flux_mean - annual_flux_variability, ymax = annual_flux_mean + annual_flux_variability, col = "interannual variability"), width = 0.2, size = 0.8, linetype = 2)+
  scale_fill_manual(values = c("annual" = "lightblue", "interannual" = "indianred"))+
  scale_color_manual(values = c("prediction interval" = "darkblue", "interannual variability" = "darkred"), name = "")+
   labs(x = "Year", y = "Flux, from weekly mean values (ton/year)", fill = "")+
  theme_minimal()+
  theme(axis.text.x = element_text(angle = 45, hjust = 1), legend.position = "bottom")
```

## Bi-weekly

```{r pred-galabre-gnls-week2, cache.lazy = F}
# prepare df
galabre_group_week2 <- galabre_time %>% mutate(week2 = week(DateHeure), week2 =  floor(as.numeric(week2 - min(week2)) / 2), year = year(DateHeure), DateHeure = NULL) %>% group_by(week2,year) # group galabre_time by week2
nrow_week2 <- n_groups(galabre_group_week2)

# get mean q
q_week2 <- galabre_group_week2 %>% select(c("week2", "q_m3.s")) %>% summarize_all(list("q_mean" = mean, "q_sd" = sd)) %>% ungroup() # mean of Q for each week2


# creates matrix for MES
galabre_mes_week2 <- galabre_group_week2 %>% select(c("week2", "mes_for_fit")) %>% summarize("list_mes" = list(mes_for_fit)) %>% ungroup() # creates a list of mes for each week2
mes_week2_random <- replicate(nrow_boot, sapply(galabre_mes_week2$list_mes, function(x) sample(x,1)))%>% t() # matrix of mes: one random sample per week2, replicated 1000 times
mes_week2_noise <- matrix(rnorm(nrow_boot*nrow_week2, mean = 0, sd = mes_u), nrow = nrow_boot, ncol = nrow_week2) 
mes_mat_week2 <- mes_week2_random * (1 + mes_week2_noise) # final value of mes, with noise

mes_mean <- colMeans(mes_mat_week2)

# Prediction matrix
mu_week2 <- f(mes_mat_week2, coefs_boot_nas[,"a"], coefs_boot_nas[,"b"])


# Prediction matrix, with noise
sigma_mat_week2 <- sigma_gnls_nas * abs(mu_week2)^theta_nas

noise_mat_week2 <- matrix(rnorm(nrow_boot*nrow_week2, mean = 0, sd = 1), nrow = nrow_boot, ncol = nrow_week2)
noise_mat_week2 <- noise_mat_week2*sigma_mat_week2

pred_week2 <- mu_week2 + noise_mat_week2
zero_mes_week2 <- which(mes_week2_random == 0)
pred_week2[zero_mes_week2] <- 0
#pred_week2 <- pmin(pmax(pred_week2, 0), 100) # clampe pred_nls pour éviter les intervalles de prédiction en dessous de zéro


## computes prediction interval 
pi_week2 <- t(
  apply(pred_week2, 2, quantile, probs = c(0.025, 0.975), na.rm = T)
)

colnames(pi_week2) <- c("lower", "upper")

boot_pred_week2 <- colMeans(pred_week2, na.rm = T)

## insert in galabre_week2
galabre_week2 <-q_week2 %>% mutate(
                          mes_for_fit = mes_mean, # keep name for "fitting model"predict" function
                          poc_boot_pred = boot_pred_week2,
                          poc_pred_lower = pi_week2[,"lower"],
                          poc_pred_upper = pi_week2[,"upper"],
                          aspt = aspt_value)

galabre_week2$poc_fitted <- predict(pocfitg_nas, galabre_week2)

# variance 
galabre_week2$poc_var_mean <- apply(mu_week2, 2, var) # variance of fit parameters + MES 
galabre_week2$poc_var_tot <- apply(pred_week2, 2, var) # total variance per prediction, for prediction total uncertainty


# plot

ggplot(galabre_week2, aes(x = mes_for_fit))+
  geom_line(aes(y = poc_pred_lower, ymax = poc_pred_upper), col = "gray50")+
  geom_line(aes(y = poc_pred_upper), col = "gray50")+
  geom_point(aes(y = poc_fitted, col = "fitted with all events"), size = 2)+
  geom_point(aes(y = poc_boot_pred, col ="poc_boot_pred"), alpha = 0.5, size = 0.5)+
  scale_color_manual(values = c("darkblue","lightblue"))+
  geom_abline(slope = 0, intercept = aspt_value, col = "darkred")+
  annotate(geom = "label", label = formula_pocfitg_nas, x = Inf, y = Inf, hjust = 1.1, vjust = 1.1)+
  labs(x = "MES, g/L", y = "POC %", colour = "", shape = "", title = "POC predicted from MES, random sampling every 2nd week", subtitle = "Prediction interval in grey")+
  theme_minimal()+
  theme(legend.position = "bottom")

```

```{r annual-flux-week2, cache.lazy=F}

# creates matrix for Q

q_week2_mean <-  matrix(q_week2$q_mean, nrow = nrow_boot, ncol = nrow_week2, byrow = T)
q_noise <- matrix(rnorm(nrow_boot*nrow_week2, mean = 0, sd = q_u), nrow = nrow_boot, ncol = nrow_week2) # creates a noise in percent (proportion), between 0 and 10%
q_mat_week2 <- q_week2_mean * (1 + q_noise) # final MC of q, with noise. SD NOT INCLUDED: will not always be available


# compute flux
flux_ton.s_mat_week2 <- pred_week2*mes_mat_week2*1e-6*q_mat_week2*1e-2*60*60*24*14 #pred_week2 * mes_mat : poc in mg/L converted to ton; q_mat converted from m3/s to L/s. Period : nb of seconds in 1 week2. 

# Get index for columns by year
index_years <- sapply(unique(galabre_week2$year), function(y){which(galabre_week2$year == y)}) # list of indices corresponding to each year

# annual flux
annual_flux_ton.y_week2 <- sapply(index_years, function(idx){apply(flux_ton.s_mat_week2[,idx], 1, sum, na.rm = T)}) # sum of fluxes per year, for each iteration of the bootstrap. Result is a matrix with nrow_boot rows and 19 columns (1 per year)

annual_flux_week2_pi <- apply(annual_flux_ton.y_week2, 2, quantile, probs = c(0.025, 0.5, 0.975), na.rm = T) # confidence interval for annual fluxes, per year. 3 lignes, 19 columns
annual_flux_week2_mean <- colMeans(annual_flux_ton.y_week2, na.rm = T) # mean annual flux per year. 1 vector

annual_flux_week2_sd <- apply(annual_flux_ton.y_week2, 2, sd, na.rm = T) # standard deviation of annual flux per year. Is just an estimate of goodness of mean, not as good as than the confidence interval. 
 

annual_flux_week2_df <- data.frame(year = unique(galabre_week2$year), 
                        annual_flux_mean = annual_flux_week2_mean, 
                        annual_flux_variability = annual_flux_week2_sd, 
                        annual_flux_pi_lower = annual_flux_week2_pi[1,], 
                        annual_flux_pi_upper = annual_flux_week2_pi[3,])

interannual_flux_ton.y_week2 <- rowMeans(annual_flux_ton.y_week2, na.rm = T) # mean interannual flux per iteration of the bootstrap
interannual_flux_pi_week2 <- quantile(interannual_flux_ton.y_week2, probs = c(0.025, 0.5, 0.975), na.rm = T) # prediction interval
interannual_flux_mean_week2 <- mean(interannual_flux_ton.y_week2, na.rm = T) # mean interannual flux
interannual_flux_variability_week2 <- sd(annual_flux_week2_mean, na.rm = T) # standard deviation of interannual flux per year

interannual_flux_week2_df <- data.frame(year = "interannual", annual_flux_mean = interannual_flux_mean_week2, 
                                  annual_flux_variability = interannual_flux_variability_week2,
                        annual_flux_pi_lower = interannual_flux_pi_week2[1], 
                        annual_flux_pi_upper = interannual_flux_pi_week2[3])

total_flux_week2_df <- rbind(annual_flux_week2_df, interannual_flux_week2_df)
total_flux_week2_df$group <- c(rep("annual", length(unique(galabre_week2$year))), "interannual")

ggplot()+
  geom_col(data = total_flux_week2_df, aes(x=year, y = annual_flux_mean, fill = group))+
    geom_errorbar(data = total_flux_week2_df, aes(x = year, ymin = annual_flux_pi_lower, ymax = annual_flux_pi_upper, col = "prediction interval"), width = 0.3, size = 0.8)+
  geom_errorbar(data = filter(total_flux_week2_df, year == "interannual"), aes(x = year, ymin = annual_flux_mean - annual_flux_variability, ymax = annual_flux_mean + annual_flux_variability, col = "interannual variability"), width = 0.2, size = 0.8, linetype = 2)+
  scale_fill_manual(values = c("annual" = "lightblue", "interannual" = "indianred"))+
  scale_color_manual(values = c("prediction interval" = "darkblue", "interannual variability" = "darkred"), name = "")+
   labs(x = "Year", y = "Flux, from week2ly mean values (ton/year)", fill = "")+
  theme_minimal()+
  theme(axis.text.x = element_text(angle = 45, hjust = 1), legend.position = "bottom")
```

## Month

```{r pred-galabre-gnls-month, cache.lazy = F}
# prepare df
galabre_group_month <- galabre_time %>% mutate(month = month(DateHeure), year = year(DateHeure), DateHeure = NULL) %>% group_by(month,year) # group galabre_time by month
nrow_month <- n_groups(galabre_group_month)

# get mean q
q_month <- galabre_group_month %>% select(c("month", "q_m3.s")) %>% summarize_all(list("q_mean" = mean, "q_sd" = sd)) %>% ungroup() # mean of Q for each month

# creates matrix for MES
galabre_mes_month <- galabre_group_month %>% select(c("month", "mes_for_fit")) %>% summarize("list_mes" = list(mes_for_fit)) %>% ungroup() # creates a list of mes for each month
mes_month_random <- replicate(nrow_boot, sapply(galabre_mes_month$list_mes, function(x) sample(x,1)))%>% t() # matrix of mes: one random sample per month, replicated 1000 times
mes_month_noise <- matrix(rnorm(nrow_boot*nrow_month, mean = 0, sd = mes_u), nrow = nrow_boot, ncol = nrow_month) 
mes_mat_month <- mes_month_random * (1 + mes_month_noise) # final value of mes, with noise

mes_mean <- colMeans(mes_mat_month)

# Prediction matrix
mu_month <- f(mes_mat_month, coefs_boot_nas[,"a"], coefs_boot_nas[,"b"])


# Prediction matrix, with noise
sigma_mat_month <- sigma_gnls_nas * abs(mu_month)^theta_nas

noise_mat_month <- matrix(rnorm(nrow_boot*nrow_month, mean = 0, sd = 1), nrow = nrow_boot, ncol = nrow_month)
noise_mat_month <- noise_mat_month*sigma_mat_month

pred_month <- mu_month + noise_mat_month
zero_mes_month <- which(mes_month_random == 0)
pred_month[zero_mes_month] <- 0
#pred_month <- pmin(pmax(pred_month, 0), 100) # clampe pred_nls pour éviter les intervalles de prédiction en dessous de zéro


## computes prediction interval 
pi_month <- t(
  apply(pred_month, 2, quantile, probs = c(0.025, 0.975), na.rm = T)
)

colnames(pi_month) <- c("lower", "upper")

boot_pred_month <- colMeans(pred_month, na.rm = T)

## insert in galabre_month
galabre_month <-q_month %>% mutate(
                          mes_for_fit = mes_mean, # keep name for "fitting model"predict" function
                          poc_boot_pred = boot_pred_month,
                          poc_pred_lower = pi_month[,"lower"],
                          poc_pred_upper = pi_month[,"upper"],
                          aspt = aspt_value)

galabre_month$poc_fitted <- predict(pocfitg_nas, galabre_month)

# variance 
galabre_month$poc_var_mean <- apply(mu_month, 2, var) # variance of fit parameters + MES 
galabre_month$poc_var_tot <- apply(pred_month, 2, var) # total variance per prediction, for prediction total uncertainty


# plot

ggplot(galabre_month, aes(x = mes_for_fit))+
  geom_line(aes(y = poc_pred_lower, ymax = poc_pred_upper), col = "gray50")+
  geom_line(aes(y = poc_pred_upper), col = "gray50")+
  geom_point(aes(y = poc_fitted, col = "fitted with all events"), size = 2)+
  geom_point(aes(y = poc_boot_pred, col ="poc_boot_pred"), alpha = 0.5, size = 0.5)+
  scale_color_manual(values = c("darkblue","lightblue"))+
  geom_abline(slope = 0, intercept = aspt_value, col = "darkred")+
  annotate(geom = "label", label = formula_pocfitg_nas, x = Inf, y = Inf, hjust = 1.1, vjust = 1.1)+
  labs(x = "MES, g/L", y = "POC %", colour = "", shape = "", title = "POC predicted from MES, random sampling every month", subtitle = "Prediction interval in grey")+
  theme_minimal()+
  theme(legend.position = "bottom")

```

```{r annual-flux-month, cache.lazy=F}

# creates matrix for Q

q_month_mean <-  matrix(q_month$q_mean, nrow = nrow_boot, ncol = nrow_month, byrow = T)
q_noise <- matrix(rnorm(nrow_boot*nrow_month, mean = 0, sd = q_u), nrow = nrow_boot, ncol = nrow_month) # creates a noise in percent (proportion), between 0 and 10%
q_mat_month <- q_month_mean * (1 + q_noise) # final MC of q, with noise. SD NOT INCLUDED: will not always be available


# compute flux
flux_ton.s_mat_month <- pred_month*mes_mat_month*1e-6*q_mat_month*1e-2*60*60*24*60 #pred_month * mes_mat : poc in mg/L converted to ton; q_mat converted from m3/s to L/s. Period : nb of seconds in 1 month. 

# Get index for columns by year
index_years <- sapply(unique(galabre_month$year), function(y){which(galabre_month$year == y)}) # list of indices corresponding to each year

# annual flux
annual_flux_ton.y_month <- apply(index_years, 2, function(idx){apply(flux_ton.s_mat_month[,idx], 1, sum, na.rm = T)}) # sum of fluxes per year, for each iteration of the bootstrap. Result is a matrix with nrow_boot rows and 19 columns (1 per year)

annual_flux_month_pi <- apply(annual_flux_ton.y_month, 2, quantile, probs = c(0.025, 0.5, 0.975), na.rm = T) # confidence interval for annual fluxes, per year. 3 lignes, 19 columns
annual_flux_month_mean <- colMeans(annual_flux_ton.y_month, na.rm = T) # mean annual flux per year. 1 vector

annual_flux_month_sd <- apply(annual_flux_ton.y_month, 2, sd, na.rm = T) # standard deviation of annual flux per year. Is just an estimate of goodness of mean, not as good as than the confidence interval. 
 

annual_flux_month_df <- data.frame(year = unique(galabre_month$year), 
                        annual_flux_mean = annual_flux_month_mean, 
                        annual_flux_variability = annual_flux_month_sd, 
                        annual_flux_pi_lower = annual_flux_month_pi[1,], 
                        annual_flux_pi_upper = annual_flux_month_pi[3,])

interannual_flux_ton.y_month <- rowMeans(annual_flux_ton.y_month, na.rm = T) # mean interannual flux per iteration of the bootstrap
interannual_flux_pi_month <- quantile(interannual_flux_ton.y_month, probs = c(0.025, 0.5, 0.975), na.rm = T) # prediction interval
interannual_flux_mean_month <- mean(interannual_flux_ton.y_month, na.rm = T) # mean interannual flux
interannual_flux_variability_month <- sd(annual_flux_month_mean, na.rm = T) # standard deviation of interannual flux per year

interannual_flux_month_df <- data.frame(year = "interannual", annual_flux_mean = interannual_flux_mean_month, 
                                  annual_flux_variability = interannual_flux_variability_month,
                        annual_flux_pi_lower = interannual_flux_pi_month[1], 
                        annual_flux_pi_upper = interannual_flux_pi_month[3])

total_flux_month_df <- rbind(annual_flux_month_df, interannual_flux_month_df)
total_flux_month_df$group <- c(rep("annual", length(unique(galabre_month$year))), "interannual")

ggplot()+
  geom_col(data = total_flux_month_df, aes(x=year, y = annual_flux_mean, fill = group))+
    geom_errorbar(data = total_flux_month_df, aes(x = year, ymin = annual_flux_pi_lower, ymax = annual_flux_pi_upper, col = "prediction interval"), width = 0.3, size = 0.8)+
  geom_errorbar(data = filter(total_flux_month_df, year == "interannual"), aes(x = year, ymin = annual_flux_mean - annual_flux_variability, ymax = annual_flux_mean + annual_flux_variability, col = "interannual variability"), width = 0.2, size = 0.8, linetype = 2)+
  scale_fill_manual(values = c("annual" = "lightblue", "interannual" = "indianred"))+
  scale_color_manual(values = c("prediction interval" = "darkblue", "interannual variability" = "darkred"), name = "")+
   labs(x = "Year", y = "Flux, from monthly mean values (ton/year)", fill = "")+
  theme_minimal()+
  theme(axis.text.x = element_text(angle = 45, hjust = 1), legend.position = "bottom")
```



## Compare fluxes

```{r run-if-no-knit, eval = F}
interannual_flux_ton.y <- read.csv("interannual_flux_ton.y.csv")[,2] %>% as.vector()
```

```{r interannual-error-in-percent}

# relative error by Monte-Carlo world
error_hour <- (interannual_flux_ton.y_hour - interannual_flux_ton.y)/interannual_flux_ton.y * 100
error_hour_pi <- quantile(error_hour, probs = c(0.025, 0.5, 0.975), na.rm = T) # confidence interval for annual fluxes, per year. 3 lignes, 19 columns
error_hour_mean <- mean(error_hour)

error_hour2 <- (interannual_flux_ton.y_hour2 - interannual_flux_ton.y)/interannual_flux_ton.y * 100
error_hour2_pi <- quantile(error_hour2, probs = c(0.025, 0.5, 0.975), na.rm = T) # confidence interval for annual fluxes, per year. 3 lignes, 19 columns
error_hour2_mean <- mean(error_hour2)

error_hour4 <- (interannual_flux_ton.y_hour4 - interannual_flux_ton.y)/interannual_flux_ton.y * 100
error_hour4_pi <- quantile(error_hour4, probs = c(0.025, 0.5, 0.975), na.rm = T) # confidence interval for annual fluxes, per year. 3 lignes, 19 columns
error_hour4_mean <- mean(error_hour4)

error_hour8 <- (interannual_flux_ton.y_hour8 - interannual_flux_ton.y)/interannual_flux_ton.y * 100
error_hour8_pi <- quantile(error_hour8, probs = c(0.025, 0.5, 0.975), na.rm = T) # confidence interval for annual fluxes, per year. 3 lignes, 19 columns
error_hour8_mean <- mean(error_hour8)

error_day <- (interannual_flux_ton.y_day - interannual_flux_ton.y)/interannual_flux_ton.y * 100
error_day_pi <- quantile(error_day, probs = c(0.025, 0.5, 0.975), na.rm = T) # confidence interval for annual fluxes, per year. 3 lignes, 19 columns
error_day_mean <- mean(error_day)

error_day2 <- (interannual_flux_ton.y_day2 - interannual_flux_ton.y)/interannual_flux_ton.y * 100
error_day2_pi <- quantile(error_day2, probs = c(0.025, 0.5, 0.975), na.rm = T) # confidence interval for annual fluxes, per year. 3 lignes, 19 columns
error_day2_mean <- mean(error_day2)

error_day4 <- (interannual_flux_ton.y_day4 - interannual_flux_ton.y)/interannual_flux_ton.y * 100
error_day4_pi <- quantile(error_day4, probs = c(0.025, 0.5, 0.975), na.rm = T) # confidence interval for annual fluxes, per year. 3 lignes, 19 columns
error_day4_mean <- mean(error_day4)

error_week <- (interannual_flux_ton.y_week - interannual_flux_ton.y)/interannual_flux_ton.y * 100
error_week_pi <- quantile(error_week, probs = c(0.025, 0.5, 0.975), na.rm = T) # confidence interval for annual fluxes, per year. 3 lignes, 19 columns
error_week_mean <- mean(error_week)

error_week2 <- (interannual_flux_ton.y_week2 - interannual_flux_ton.y)/interannual_flux_ton.y * 100
error_week2_pi <- quantile(error_week2, probs = c(0.025, 0.5, 0.975), na.rm = T) # confidence interval for annual fluxes, per year. 3 lignes, 19 columns
error_week2_mean <- mean(error_week2)

error_month <- (interannual_flux_ton.y_month - interannual_flux_ton.y)/interannual_flux_ton.y * 100
error_month_pi <- quantile(error_month, probs = c(0.025, 0.5, 0.975), na.rm = T) # confidence interval for annual fluxes, per year. 3 lignes, 19 columns
error_month_mean <- mean(error_month)

error <- data.frame(time_step = factor(c("1hour","2hours","4hours","8hours","day","2days","4days","week","2weeks","month"), levels = c("1hour","2hours","4hours","8hours","day","2days","4days","week","2weeks","month")),
                    error = c(error_hour_mean, error_hour2_mean, error_hour4_mean, error_hour8_mean, error_day_mean, error_day2_mean, error_day4_mean, error_week_mean, error_week2_mean, error_month_mean),
                    pi_upr = c(error_hour_pi[3], error_hour2_pi[3], error_hour4_pi[3], error_hour8_pi[3], error_day_pi[3], error_day2_pi[3], error_day4_pi[3], error_week_pi[3], error_week2_pi[3], error_month_pi[3]),
                    pi_lwr = c(error_hour_pi[1], error_hour2_pi[1], error_hour4_pi[1], error_hour8_pi[1], error_day_pi[1], error_day2_pi[1], error_day4_pi[1], error_week_pi[1], error_week2_pi[1], error_month_pi[1])) 

ggplot2::ggplot(data=error, aes(x = time_step))+
  geom_point(aes(y = error))+
  geom_errorbar(aes(ymin=pi_lwr, ymax=pi_upr))+
  theme_minimal()

error %>% knitr::kable(digits = 2, row.names = F) %>% kableExtra::kable_styling()
```



# Dégradation de la mesure - % mesures and weighting

Randomly selects 10, 20... 90% of the data (100 times), weigths them by year, and computes interannual flux. 

```{r load-monte-carlo-matrices-if-no-knit, eval = F}
flux_ton.s_mat <- readRDS("flux_ton.s_mat_ref.rds")
q_mat <- readRDS("q_mat_ref.rds")
interannual_flux_ton.y <- read.csv("interannual_flux_ton.y.csv")[,2] %>% as.vector()
galabre_nas <- read.csv("galabre_nas.csv")

```

```{r common-data-weighted}
galabre_w <- galabre_nas
n_gal <- nrow(galabre_w)

mes_u <- 0.05
q_u <- 0.05

set.seed(0403)

unique_years <- unique(galabre_w$year)

n_rep <- 1000
```


## 10 %

```{r percent10}
set.seed(403)

waf_10 <- list()

for(i in 1:n_rep){
  idx_10 <- sample(n_gal, n_gal/10)
  ftsm_10 <- flux_ton.s_mat[,idx_10]
  q_10 <- q_mat[, idx_10]

  # Get index for the columns corresponding to the same year
  index_years <- sapply(unique_years, function(y){which(galabre_w$year[idx_10] == y)}) # list of indices corresponding to each year

  # Annual flux
  sum_instant_flux_ton.y_10 <- sapply(index_years, function(idx){apply(ftsm_10[,idx], 1, sum, na.rm = T)}) # sum of fluxes per year, for each iteration of the bootstrap. Result is a matrix with nrow_boot rows and  (1 column per year)
  sum_instant_q_10 <- sapply(index_years, function(idx){apply(q_10[,idx], 1, sum, na.rm = T)}) # sum of discharge per year, for each iteration of the bootstrap. Result is a matrix with nrow_boot rows and 1 columns per year
  mean_instant_q_10 <- sapply(index_years, function(idx){apply(q_10[,idx], 1, mean, na.rm = T)}) # mean discharge per year

  weighted_annual_flux_ton.y_10 <- sum_instant_flux_ton.y_10 / sum_instant_q_10 * mean_instant_q_10 *6*24*365 # time step of observations is 10 min
  
  waf_10[[i]] <- weighted_annual_flux_ton.y_10
}

```

```{r 10-percent-mean}
waf_10_mean <- c()
waf_10_upr <- c()
waf_10_lwr <- c()

for(i in 1:length(unique_years)){
  waf_10_mean[i] <- lapply(waf_10, function(x) x[,i]) %>% unlist() %>% mean()
  waf_10_upr[i] <- lapply(waf_10, function(x) x[,i]) %>% unlist() %>% quantile(0.975)
  waf_10_lwr[i] <- lapply(waf_10, function(x) x[,i]) %>% unlist() %>% quantile(0.025)
  }

wiaf_10 <- matrix(NA_real_, nrow = 1000, ncol = nrep*length(unique_years))
for(i in 1:1000){
  mci <- lapply(waf_10, function(x) x[i, ]) %>% unlist # flux interannual pour monde MC i, pour les 6 ans
  wiaf_10[i,] <- mci
}


wiaf_10_rowmean <- rowMeans(wiaf_10)
wiaf_10_mean <- mean(wiaf_10_rowmean)
wiaf_10_sd <- sd(wiaf_10_rowmean)
wiaf_10_upr <- quantile(wiaf_10_rowmean) %>% quantile(0.975)
wiaf_10_lwr <- quantile(wiaf_10_rowmean) %>% quantile(0.025)
```


```{r visualisation-wiaf-10, eval = F}
# Merge in df
weighted_total_flux_df_10 <- data.frame(year = c(unique(galabre_w$year), "interannual"), 
                        annual_flux_mean = c(waf_10_mean, wiaf_10_mean), 
                        annual_flux_variability = c(rep(NA, 6), wiaf_10_sd), 
                        annual_flux_pi_lower = c(waf_10_lwr, wiaf_10_lwr), 
                        annual_flux_pi_upper = c(waf_10_upr, wiaf_10_upr),
                        group = c(rep("annual",6),"interannual"))

ggplot()+
  geom_col(data = weighted_total_flux_df_10, aes(x=year, y = annual_flux_mean, fill = group))+
    geom_errorbar(data = weighted_total_flux_df_10, aes(x = year, ymin = annual_flux_pi_lower, ymax = annual_flux_pi_upper, col = "prediction interval"), width = 0.3, linewidth = 0.8)+
  geom_errorbar(data = filter(weighted_total_flux_df_10, year == "interannual"), aes(x = year, ymin = annual_flux_mean - annual_flux_variability, ymax = annual_flux_mean + annual_flux_variability, col = "interannual variability"), width = 0.2, linewidth = 0.8, linetype = 2)+
  scale_fill_manual(values = c("annual" = "lightblue", "interannual" = "indianred"))+
  scale_color_manual(values = c("prediction interval" = "darkblue", "interannual variability" = "darkred"), name = "")+
   labs(x = "Year", y = "Flux (ton/year)", fill = "")+
  theme_minimal()+
  theme(axis.text.x = element_text(angle = 45, hjust = 1), legend.position = "bottom")

```

## 20 %

```{r percent20}
set.seed(403)

waf_20 <- list()

for(i in 1:n_rep){
  idx_20 <- sample(n_gal, n_gal/20)
  ftsm_20 <- flux_ton.s_mat[,idx_20]
  q_20 <- q_mat[, idx_20]

  # Get index for the columns corresponding to the same year
  index_years <- sapply(unique_years, function(y){which(galabre_w$year[idx_20] == y)}) # list of indices corresponding to each year

  # Annual flux
  sum_instant_flux_ton.y_20 <- sapply(index_years, function(idx){apply(ftsm_20[,idx], 1, sum, na.rm = T)}) # sum of fluxes per year, for each iteration of the bootstrap. Result is a matrix with nrow_boot rows and  (1 column per year)
  sum_instant_q_20 <- sapply(index_years, function(idx){apply(q_20[,idx], 1, sum, na.rm = T)}) # sum of discharge per year, for each iteration of the bootstrap. Result is a matrix with nrow_boot rows and 1 columns per year
  mean_instant_q_20 <- sapply(index_years, function(idx){apply(q_20[,idx], 1, mean, na.rm = T)}) # mean discharge per year

  weighted_annual_flux_ton.y_20 <- sum_instant_flux_ton.y_20 / sum_instant_q_20 * mean_instant_q_20 *6*24*365 # time step of observations is 10 min: flux by 10 min is converted in flux per second, then per year
  
  waf_20[[i]] <- weighted_annual_flux_ton.y_20
}

```

```{r 20-percent-mean}
waf_20_mean <- c()
waf_20_upr <- c()
waf_20_lwr <- c()

for(i in 1:length(unique_years)){
  waf_20_mean[i] <- lapply(waf_20, function(x) x[,i]) %>% unlist() %>% mean()
  waf_20_upr[i] <- lapply(waf_20, function(x) x[,i]) %>% unlist() %>% quantile(0.975)
  waf_20_lwr[i] <- lapply(waf_20, function(x) x[,i]) %>% unlist() %>% quantile(0.025)
  }

wiaf_20 <-  matrix(NA_real_, nrow = 1000, ncol = nrep*length(unique_years))
for(i in 1:1000){
  mci <- lapply(waf_20, function(x) x[i, ]) %>% unlist # flux interannual pour monde MC i, pour les 6 ans
  wiaf_20[i,] <- mci
}


wiaf_20_rowmean <- rowMeans(wiaf_20)
wiaf_20_mean <- mean(wiaf_20_rowmean)
wiaf_20_sd <- sd(wiaf_20_rowmean)
wiaf_20_upr <- quantile(wiaf_20_rowmean) %>% quantile(0.975)
wiaf_20_lwr <- quantile(wiaf_20_rowmean) %>% quantile(0.025)
```


```{r visualisation-wiaf-20, eval = F}
# Merge in df
weighted_total_flux_df_20 <- data.frame(year = c(unique(galabre_w$year), "interannual"), 
                        annual_flux_mean = c(waf_20_mean, wiaf_20_mean), 
                        annual_flux_variability = c(rep(NA, 6), wiaf_20_sd), 
                        annual_flux_pi_lower = c(waf_20_lwr, wiaf_20_lwr), 
                        annual_flux_pi_upper = c(waf_20_upr, wiaf_20_upr),
                        group = c(rep("annual",6),"interannual"))

ggplot()+
  geom_col(data = weighted_total_flux_df_20, aes(x=year, y = annual_flux_mean, fill = group))+
    geom_errorbar(data = weighted_total_flux_df_20, aes(x = year, ymin = annual_flux_pi_lower, ymax = annual_flux_pi_upper, col = "prediction interval"), width = 0.3, linewidth = 0.8)+
  geom_errorbar(data = filter(weighted_total_flux_df_20, year == "interannual"), aes(x = year, ymin = annual_flux_mean - annual_flux_variability, ymax = annual_flux_mean + annual_flux_variability, col = "interannual variability"), width = 0.2, linewidth = 0.8, linetype = 2)+
  scale_fill_manual(values = c("annual" = "lightblue", "interannual" = "indianred"))+
  scale_color_manual(values = c("prediction interval" = "darkblue", "interannual variability" = "darkred"), name = "")+
   labs(x = "Year", y = "Flux (ton/year)", fill = "")+
  theme_minimal()+
  theme(axis.text.x = element_text(angle = 45, hjust = 1), legend.position = "bottom")

```







## 30 %

```{r percent30}
set.seed(403)

waf_30 <- list()

for(i in 1:n_rep){
  idx_30 <- sample(n_gal, n_gal/30)
  ftsm_30 <- flux_ton.s_mat[,idx_30]
  q_30 <- q_mat[, idx_30]

  # Get index for the columns corresponding to the same year
  index_years <- sapply(unique_years, function(y){which(galabre_w$year[idx_30] == y)}) # list of indices corresponding to each year

  # Annual flux
  sum_instant_flux_ton.y_30 <- sapply(index_years, function(idx){apply(ftsm_30[,idx], 1, sum, na.rm = T)}) # sum of fluxes per year, for each iteration of the bootstrap. Result is a matrix with nrow_boot rows and  (1 column per year)
  sum_instant_q_30 <- sapply(index_years, function(idx){apply(q_30[,idx], 1, sum, na.rm = T)}) # sum of discharge per year, for each iteration of the bootstrap. Result is a matrix with nrow_boot rows and 1 columns per year
  mean_instant_q_30 <- sapply(index_years, function(idx){apply(q_30[,idx], 1, mean, na.rm = T)}) # mean discharge per year

  weighted_annual_flux_ton.y_30 <- sum_instant_flux_ton.y_30 / sum_instant_q_30 * mean_instant_q_30 *6*24*365 # time step of observations is 10 min
  
  waf_30[[i]] <- weighted_annual_flux_ton.y_30
}

```

```{r 30-percent-mean}
waf_30_mean <- c()
waf_30_upr <- c()
waf_30_lwr <- c()

for(i in 1:length(unique_years)){
  waf_30_mean[i] <- lapply(waf_30, function(x) x[,i]) %>% unlist() %>% mean()
  waf_30_upr[i] <- lapply(waf_30, function(x) x[,i]) %>% unlist() %>% quantile(0.975)
  waf_30_lwr[i] <- lapply(waf_30, function(x) x[,i]) %>% unlist() %>% quantile(0.025)
  }

wiaf_30 <-  matrix(NA_real_, nrow = 1000, ncol = nrep*length(unique_years))
for(i in 1:1000){
  mci <- lapply(waf_30, function(x) x[i, ]) %>% unlist # flux interannual pour monde MC i, pour les 6 ans
  wiaf_30[i,] <- mci
}


wiaf_30_rowmean <- rowMeans(wiaf_30)
wiaf_30_mean <- mean(wiaf_30_rowmean)
wiaf_30_sd <- sd(wiaf_30_rowmean)
wiaf_30_upr <- quantile(wiaf_30_rowmean) %>% quantile(0.975)
wiaf_30_lwr <- quantile(wiaf_30_rowmean) %>% quantile(0.025)
```


```{r visualisation-wiaf-30, eval = F}
# Merge in df
weighted_total_flux_df_30 <- data.frame(year = c(unique(galabre_w$year), "interannual"), 
                        annual_flux_mean = c(waf_30_mean, wiaf_30_mean), 
                        annual_flux_variability = c(rep(NA, 6), wiaf_30_sd), 
                        annual_flux_pi_lower = c(waf_30_lwr, wiaf_30_lwr), 
                        annual_flux_pi_upper = c(waf_30_upr, wiaf_30_upr),
                        group = c(rep("annual",6),"interannual"))

ggplot()+
  geom_col(data = weighted_total_flux_df_30, aes(x=year, y = annual_flux_mean, fill = group))+
    geom_errorbar(data = weighted_total_flux_df_30, aes(x = year, ymin = annual_flux_pi_lower, ymax = annual_flux_pi_upper, col = "prediction interval"), width = 0.3, linewidth = 0.8)+
  geom_errorbar(data = filter(weighted_total_flux_df_20, year == "interannual"), aes(x = year, ymin = annual_flux_mean - annual_flux_variability, ymax = annual_flux_mean + annual_flux_variability, col = "interannual variability"), width = 0.2, linewidth = 0.8, linetype = 2)+
  scale_fill_manual(values = c("annual" = "lightblue", "interannual" = "indianred"))+
  scale_color_manual(values = c("prediction interval" = "darkblue", "interannual variability" = "darkred"), name = "")+
   labs(x = "Year", y = "Flux (ton/year)", fill = "")+
  theme_minimal()+
  theme(axis.text.x = element_text(angle = 45, hjust = 1), legend.position = "bottom")

```







## 40 %

```{r percent40}
set.seed(403)

waf_40 <- list()

for(i in 1:n_rep){
  idx_40 <- sample(n_gal, n_gal/40)
  ftsm_40 <- flux_ton.s_mat[,idx_40]
  q_40 <- q_mat[, idx_40]

  # Get index for the columns corresponding to the same year
  index_years <- sapply(unique_years, function(y){which(galabre_w$year[idx_40] == y)}) # list of indices corresponding to each year

  # Annual flux
  sum_instant_flux_ton.y_40 <- sapply(index_years, function(idx){apply(ftsm_40[,idx], 1, sum, na.rm = T)}) # sum of fluxes per year, for each iteration of the bootstrap. Result is a matrix with nrow_boot rows and  (1 column per year)
  sum_instant_q_40 <- sapply(index_years, function(idx){apply(q_40[,idx], 1, sum, na.rm = T)}) # sum of discharge per year, for each iteration of the bootstrap. Result is a matrix with nrow_boot rows and 1 columns per year
  mean_instant_q_40 <- sapply(index_years, function(idx){apply(q_40[,idx], 1, mean, na.rm = T)}) # mean discharge per year

  weighted_annual_flux_ton.y_40 <- sum_instant_flux_ton.y_40 / sum_instant_q_40 * mean_instant_q_40 *6*24*365 # time step of observations is 10 min
  
  waf_40[[i]] <- weighted_annual_flux_ton.y_40
}

```

```{r 40-percent-mean}
waf_40_mean <- c()
waf_40_upr <- c()
waf_40_lwr <- c()

for(i in 1:length(unique_years)){
  waf_40_mean[i] <- lapply(waf_40, function(x) x[,i]) %>% unlist() %>% mean()
  waf_40_upr[i] <- lapply(waf_40, function(x) x[,i]) %>% unlist() %>% quantile(0.975)
  waf_40_lwr[i] <- lapply(waf_40, function(x) x[,i]) %>% unlist() %>% quantile(0.025)
  }

wiaf_40 <-  matrix(NA_real_, nrow = 1000, ncol = nrep*length(unique_years))
for(i in 1:1000){
  mci <- lapply(waf_40, function(x) x[i, ]) %>% unlist # flux interannual pour monde MC i, pour les 6 ans
  wiaf_40[i,] <- mci
}


wiaf_40_rowmean <- rowMeans(wiaf_40)
wiaf_40_mean <- mean(wiaf_40_rowmean)
wiaf_40_sd <- sd(wiaf_40_rowmean)
wiaf_40_upr <- quantile(wiaf_40_rowmean) %>% quantile(0.975)
wiaf_40_lwr <- quantile(wiaf_40_rowmean) %>% quantile(0.025)
```


```{r visualisation-wiaf-40, eval = F}
# Merge in df
weighted_total_flux_df_40 <- data.frame(year = c(unique(galabre_w$year), "interannual"), 
                        annual_flux_mean = c(waf_40_mean, wiaf_40_mean), 
                        annual_flux_variability = c(rep(NA, 6), wiaf_40_sd), 
                        annual_flux_pi_lower = c(waf_40_lwr, wiaf_40_lwr), 
                        annual_flux_pi_upper = c(waf_40_upr, wiaf_40_upr),
                        group = c(rep("annual",6),"interannual"))

ggplot()+
  geom_col(data = weighted_total_flux_df_40, aes(x=year, y = annual_flux_mean, fill = group))+
    geom_errorbar(data = weighted_total_flux_df_40, aes(x = year, ymin = annual_flux_pi_lower, ymax = annual_flux_pi_upper, col = "prediction interval"), width = 0.3, linewidth = 0.8)+
  geom_errorbar(data = filter(weighted_total_flux_df_20, year == "interannual"), aes(x = year, ymin = annual_flux_mean - annual_flux_variability, ymax = annual_flux_mean + annual_flux_variability, col = "interannual variability"), width = 0.2, linewidth = 0.8, linetype = 2)+
  scale_fill_manual(values = c("annual" = "lightblue", "interannual" = "indianred"))+
  scale_color_manual(values = c("prediction interval" = "darkblue", "interannual variability" = "darkred"), name = "")+
   labs(x = "Year", y = "Flux (ton/year)", fill = "")+
  theme_minimal()+
  theme(axis.text.x = element_text(angle = 45, hjust = 1), legend.position = "bottom")

```

## 50 %

```{r percent50}
set.seed(403)

waf_50 <- list()

for(i in 1:n_rep){
  idx_50 <- sample(n_gal, n_gal/50)
  ftsm_50 <- flux_ton.s_mat[,idx_50]
  q_50 <- q_mat[, idx_50]

  # Get index for the columns corresponding to the same year
  index_years <- sapply(unique_years, function(y){which(galabre_w$year[idx_50] == y)}) # list of indices corresponding to each year

  # Annual flux
  sum_instant_flux_ton.y_50 <- sapply(index_years, function(idx){apply(ftsm_50[,idx], 1, sum, na.rm = T)}) # sum of fluxes per year, for each iteration of the bootstrap. Result is a matrix with nrow_boot rows and  (1 column per year)
  sum_instant_q_50 <- sapply(index_years, function(idx){apply(q_50[,idx], 1, sum, na.rm = T)}) # sum of discharge per year, for each iteration of the bootstrap. Result is a matrix with nrow_boot rows and 1 columns per year
  mean_instant_q_50 <- sapply(index_years, function(idx){apply(q_50[,idx], 1, mean, na.rm = T)}) # mean discharge per year

  weighted_annual_flux_ton.y_50 <- sum_instant_flux_ton.y_50 / sum_instant_q_50 * mean_instant_q_50 *6*24*365 # time step of observations is 10 min
  
  waf_50[[i]] <- weighted_annual_flux_ton.y_50
}

```

```{r 50-percent-mean}
waf_50_mean <- c()
waf_50_upr <- c()
waf_50_lwr <- c()

for(i in 1:length(unique_years)){
  waf_50_mean[i] <- lapply(waf_50, function(x) x[,i]) %>% unlist() %>% mean()
  waf_50_upr[i] <- lapply(waf_50, function(x) x[,i]) %>% unlist() %>% quantile(0.975)
  waf_50_lwr[i] <- lapply(waf_50, function(x) x[,i]) %>% unlist() %>% quantile(0.025)
  }

wiaf_50 <-  matrix(NA_real_, nrow = 1000, ncol = nrep*length(unique_years))
for(i in 1:1000){
  mci <- lapply(waf_50, function(x) x[i, ]) %>% unlist # flux interannual pour monde MC i, pour les 6 ans
  wiaf_50[i,] <- mci
}


wiaf_50_rowmean <- rowMeans(wiaf_50)
wiaf_50_mean <- mean(wiaf_50_rowmean)
wiaf_50_sd <- sd(wiaf_50_rowmean)
wiaf_50_upr <- quantile(wiaf_50_rowmean) %>% quantile(0.975)
wiaf_50_lwr <- quantile(wiaf_50_rowmean) %>% quantile(0.025)
```


```{r visualisation-wiaf-50, eval = F}
# Merge in df
weighted_total_flux_df_50 <- data.frame(year = c(unique(galabre_w$year), "interannual"), 
                        annual_flux_mean = c(waf_50_mean, wiaf_50_mean), 
                        annual_flux_variability = c(rep(NA, 6), wiaf_50_sd), 
                        annual_flux_pi_lower = c(waf_50_lwr, wiaf_50_lwr), 
                        annual_flux_pi_upper = c(waf_50_upr, wiaf_50_upr),
                        group = c(rep("annual",6),"interannual"))

ggplot()+
  geom_col(data = weighted_total_flux_df_50, aes(x=year, y = annual_flux_mean, fill = group))+
    geom_errorbar(data = weighted_total_flux_df_50, aes(x = year, ymin = annual_flux_pi_lower, ymax = annual_flux_pi_upper, col = "prediction interval"), width = 0.3, linewidth = 0.8)+
  geom_errorbar(data = filter(weighted_total_flux_df_20, year == "interannual"), aes(x = year, ymin = annual_flux_mean - annual_flux_variability, ymax = annual_flux_mean + annual_flux_variability, col = "interannual variability"), width = 0.2, linewidth = 0.8, linetype = 2)+
  scale_fill_manual(values = c("annual" = "lightblue", "interannual" = "indianred"))+
  scale_color_manual(values = c("prediction interval" = "darkblue", "interannual variability" = "darkred"), name = "")+
   labs(x = "Year", y = "Flux (ton/year)", fill = "")+
  theme_minimal()+
  theme(axis.text.x = element_text(angle = 45, hjust = 1), legend.position = "bottom")

```

## 60 %

```{r percent60}
set.seed(403)

waf_60 <- list()

for(i in 1:n_rep){
  idx_60 <- sample(n_gal, n_gal/60)
  ftsm_60 <- flux_ton.s_mat[,idx_60]
  q_60 <- q_mat[, idx_60]

  # Get index for the columns corresponding to the same year
  index_years <- sapply(unique_years, function(y){which(galabre_w$year[idx_60] == y)}) # list of indices corresponding to each year

  # Annual flux
  sum_instant_flux_ton.y_60 <- sapply(index_years, function(idx){apply(ftsm_60[,idx], 1, sum, na.rm = T)}) # sum of fluxes per year, for each iteration of the bootstrap. Result is a matrix with nrow_boot rows and  (1 column per year)
  sum_instant_q_60 <- sapply(index_years, function(idx){apply(q_60[,idx], 1, sum, na.rm = T)}) # sum of discharge per year, for each iteration of the bootstrap. Result is a matrix with nrow_boot rows and 1 columns per year
  mean_instant_q_60 <- sapply(index_years, function(idx){apply(q_60[,idx], 1, mean, na.rm = T)}) # mean discharge per year

  weighted_annual_flux_ton.y_60 <- sum_instant_flux_ton.y_60 / sum_instant_q_60 * mean_instant_q_60 *6*24*365 # time step of observations is 10 min
  
  waf_60[[i]] <- weighted_annual_flux_ton.y_60
}

```

```{r 60-percent-mean}
waf_60_mean <- c()
waf_60_upr <- c()
waf_60_lwr <- c()

for(i in 1:length(unique_years)){
  waf_60_mean[i] <- lapply(waf_60, function(x) x[,i]) %>% unlist() %>% mean()
  waf_60_upr[i] <- lapply(waf_60, function(x) x[,i]) %>% unlist() %>% quantile(0.975)
  waf_60_lwr[i] <- lapply(waf_60, function(x) x[,i]) %>% unlist() %>% quantile(0.025)
  }

wiaf_60 <-  matrix(NA_real_, nrow = 1000, ncol = nrep*length(unique_years))
for(i in 1:1000){
  mci <- lapply(waf_60, function(x) x[i, ]) %>% unlist # flux interannual pour monde MC i, pour les 6 ans
  wiaf_60[i,] <- mci
}


wiaf_60_rowmean <- rowMeans(wiaf_60)
wiaf_60_mean <- mean(wiaf_60_rowmean)
wiaf_60_sd <- sd(wiaf_60_rowmean)
wiaf_60_upr <- quantile(wiaf_60_rowmean) %>% quantile(0.975)
wiaf_60_lwr <- quantile(wiaf_60_rowmean) %>% quantile(0.025)
```


```{r visualisation-wiaf-60, eval = F}
# Merge in df
weighted_total_flux_df_60 <- data.frame(year = c(unique(galabre_w$year), "interannual"), 
                        annual_flux_mean = c(waf_60_mean, wiaf_60_mean), 
                        annual_flux_variability = c(rep(NA, 6), wiaf_60_sd), 
                        annual_flux_pi_lower = c(waf_60_lwr, wiaf_60_lwr), 
                        annual_flux_pi_upper = c(waf_60_upr, wiaf_60_upr),
                        group = c(rep("annual",6),"interannual"))

ggplot()+
  geom_col(data = weighted_total_flux_df_60, aes(x=year, y = annual_flux_mean, fill = group))+
    geom_errorbar(data = weighted_total_flux_df_60, aes(x = year, ymin = annual_flux_pi_lower, ymax = annual_flux_pi_upper, col = "prediction interval"), width = 0.3, linewidth = 0.8)+
  geom_errorbar(data = filter(weighted_total_flux_df_20, year == "interannual"), aes(x = year, ymin = annual_flux_mean - annual_flux_variability, ymax = annual_flux_mean + annual_flux_variability, col = "interannual variability"), width = 0.2, linewidth = 0.8, linetype = 2)+
  scale_fill_manual(values = c("annual" = "lightblue", "interannual" = "indianred"))+
  scale_color_manual(values = c("prediction interval" = "darkblue", "interannual variability" = "darkred"), name = "")+
   labs(x = "Year", y = "Flux (ton/year)", fill = "")+
  theme_minimal()+
  theme(axis.text.x = element_text(angle = 45, hjust = 1), legend.position = "bottom")

```

















## 70 %

```{r percent70}
set.seed(403)

waf_70 <- list()

for(i in 1:n_rep){
  idx_70 <- sample(n_gal, n_gal/70)
  ftsm_70 <- flux_ton.s_mat[,idx_70]
  q_70 <- q_mat[, idx_70]

  # Get index for the columns corresponding to the same year
  index_years <- sapply(unique_years, function(y){which(galabre_w$year[idx_70] == y)}) # list of indices corresponding to each year

  # Annual flux
  sum_instant_flux_ton.y_70 <- sapply(index_years, function(idx){apply(ftsm_70[,idx], 1, sum, na.rm = T)}) # sum of fluxes per year, for each iteration of the bootstrap. Result is a matrix with nrow_boot rows and  (1 column per year)
  sum_instant_q_70 <- sapply(index_years, function(idx){apply(q_70[,idx], 1, sum, na.rm = T)}) # sum of discharge per year, for each iteration of the bootstrap. Result is a matrix with nrow_boot rows and 1 columns per year
  mean_instant_q_70 <- sapply(index_years, function(idx){apply(q_70[,idx], 1, mean, na.rm = T)}) # mean discharge per year

  weighted_annual_flux_ton.y_70 <- sum_instant_flux_ton.y_70 / sum_instant_q_70 * mean_instant_q_70 *6*24*365 # time step of observations is 10 min
  
  waf_70[[i]] <- weighted_annual_flux_ton.y_70
}

```

```{r 70-percent-mean}
waf_70_mean <- c()
waf_70_upr <- c()
waf_70_lwr <- c()

for(i in 1:length(unique_years)){
  waf_70_mean[i] <- lapply(waf_70, function(x) x[,i]) %>% unlist() %>% mean()
  waf_70_upr[i] <- lapply(waf_70, function(x) x[,i]) %>% unlist() %>% quantile(0.975)
  waf_70_lwr[i] <- lapply(waf_70, function(x) x[,i]) %>% unlist() %>% quantile(0.025)
  }

wiaf_70 <- matrix(NA_real_, nrow = 1000, ncol = 600)
for(i in 1:1000){
  mci <- lapply(waf_70, function(x) x[i, ]) %>% unlist # flux interannual pour monde MC i, pour les 6 ans
  wiaf_70[i,] <- mci
}


wiaf_70_rowmean <- rowMeans(wiaf_70)
wiaf_70_mean <- mean(wiaf_70_rowmean)
wiaf_70_sd <- sd(wiaf_70_rowmean)
wiaf_70_upr <- quantile(wiaf_70_rowmean) %>% quantile(0.975)
wiaf_70_lwr <- quantile(wiaf_70_rowmean) %>% quantile(0.025)
```


```{r visualisation-wiaf-70, eval = F}
# Merge in df
weighted_total_flux_df_70 <- data.frame(year = c(unique(galabre_w$year), "interannual"), 
                        annual_flux_mean = c(waf_70_mean, wiaf_70_mean), 
                        annual_flux_variability = c(rep(NA, 6), wiaf_70_sd), 
                        annual_flux_pi_lower = c(waf_70_lwr, wiaf_70_lwr), 
                        annual_flux_pi_upper = c(waf_70_upr, wiaf_70_upr),
                        group = c(rep("annual",6),"interannual"))

ggplot()+
  geom_col(data = weighted_total_flux_df_70, aes(x=year, y = annual_flux_mean, fill = group))+
    geom_errorbar(data = weighted_total_flux_df_70, aes(x = year, ymin = annual_flux_pi_lower, ymax = annual_flux_pi_upper, col = "prediction interval"), width = 0.3, linewidth = 0.8)+
  geom_errorbar(data = filter(weighted_total_flux_df_20, year == "interannual"), aes(x = year, ymin = annual_flux_mean - annual_flux_variability, ymax = annual_flux_mean + annual_flux_variability, col = "interannual variability"), width = 0.2, linewidth = 0.8, linetype = 2)+
  scale_fill_manual(values = c("annual" = "lightblue", "interannual" = "indianred"))+
  scale_color_manual(values = c("prediction interval" = "darkblue", "interannual variability" = "darkred"), name = "")+
   labs(x = "Year", y = "Flux (ton/year)", fill = "")+
  theme_minimal()+
  theme(axis.text.x = element_text(angle = 45, hjust = 1), legend.position = "bottom")

```






## 80 %

```{r percent80}
set.seed(403)
n_rep <- 100

waf_80 <- list()

for(i in 1:n_rep){
  idx_80 <- sample(n_gal, n_gal/80)
  ftsm_80 <- flux_ton.s_mat[,idx_80]
  q_80 <- q_mat[, idx_80]

  # Get index for the columns corresponding to the same year
  index_years <- sapply(unique_years, function(y){which(galabre_w$year[idx_80] == y)}) # list of indices corresponding to each year

  # Annual flux
  sum_instant_flux_ton.y_80 <- sapply(index_years, function(idx){apply(ftsm_80[,idx], 1, sum, na.rm = T)}) # sum of fluxes per year, for each iteration of the bootstrap. Result is a matrix with nrow_boot rows and  (1 column per year)
  sum_instant_q_80 <- sapply(index_years, function(idx){apply(q_80[,idx], 1, sum, na.rm = T)}) # sum of discharge per year, for each iteration of the bootstrap. Result is a matrix with nrow_boot rows and 1 columns per year
  mean_instant_q_80 <- sapply(index_years, function(idx){apply(q_80[,idx], 1, mean, na.rm = T)}) # mean discharge per year

  weighted_annual_flux_ton.y_80 <- sum_instant_flux_ton.y_80 / sum_instant_q_80 * mean_instant_q_80 *6*24*365 # time step of observations is 10 min
  
  waf_80[[i]] <- weighted_annual_flux_ton.y_80
}

```

```{r 80-percent-mean}
waf_80_mean <- c()
waf_80_upr <- c()
waf_80_lwr <- c()

for(i in 1:length(unique_years)){
  waf_80_mean[i] <- lapply(waf_80, function(x) x[,i]) %>% unlist() %>% mean()
  waf_80_upr[i] <- lapply(waf_80, function(x) x[,i]) %>% unlist() %>% quantile(0.975)
  waf_80_lwr[i] <- lapply(waf_80, function(x) x[,i]) %>% unlist() %>% quantile(0.025)
  }

wiaf_80 <- matrix(NA_real_, nrow = 1000, ncol = 600)
for(i in 1:1000){
  mci <- lapply(waf_80, function(x) x[i, ]) %>% unlist # flux interannual pour monde MC i, pour les 6 ans
  wiaf_80[i,] <- mci
}

wiaf_80_rowmean <- rowMeans(wiaf_80)
wiaf_80_mean <- mean(wiaf_80_rowmean)
wiaf_80_sd <- sd(wiaf_80_rowmean)
wiaf_80_upr <- quantile(wiaf_80_rowmean) %>% quantile(0.975)
wiaf_80_lwr <- quantile(wiaf_80_rowmean) %>% quantile(0.025)
```


```{r visualisation-wiaf-80, eval = F}
# Merge in df
weighted_total_flux_df_80 <- data.frame(year = c(unique(galabre_w$year), "interannual"), 
                        annual_flux_mean = c(waf_80_mean, wiaf_80_mean), 
                        annual_flux_variability = c(rep(NA, 6), wiaf_80_sd), 
                        annual_flux_pi_lower = c(waf_80_lwr, wiaf_80_lwr), 
                        annual_flux_pi_upper = c(waf_80_upr, wiaf_80_upr),
                        group = c(rep("annual",6),"interannual"))

ggplot()+
  geom_col(data = weighted_total_flux_df_80, aes(x=year, y = annual_flux_mean, fill = group))+
    geom_errorbar(data = weighted_total_flux_df_80, aes(x = year, ymin = annual_flux_pi_lower, ymax = annual_flux_pi_upper, col = "prediction interval"), width = 0.3, linewidth = 0.8)+
  geom_errorbar(data = filter(weighted_total_flux_df_20, year == "interannual"), aes(x = year, ymin = annual_flux_mean - annual_flux_variability, ymax = annual_flux_mean + annual_flux_variability, col = "interannual variability"), width = 0.2, linewidth = 0.8, linetype = 2)+
  scale_fill_manual(values = c("annual" = "lightblue", "interannual" = "indianred"))+
  scale_color_manual(values = c("prediction interval" = "darkblue", "interannual variability" = "darkred"), name = "")+
   labs(x = "Year", y = "Flux (ton/year)", fill = "")+
  theme_minimal()+
  theme(axis.text.x = element_text(angle = 45, hjust = 1), legend.position = "bottom")

```






## 90 %

```{r percent90}
set.seed(403)
n_rep <- 100

waf_90 <- list()

for(i in 1:n_rep){
  idx_90 <- sample(n_gal, n_gal/90)
  ftsm_90 <- flux_ton.s_mat[,idx_90]
  q_90 <- q_mat[, idx_90]

  # Get index for the columns corresponding to the same year
  index_years <- sapply(unique_years, function(y){which(galabre_w$year[idx_90] == y)}) # list of indices corresponding to each year

  # Annual flux
  sum_instant_flux_ton.y_90 <- sapply(index_years, function(idx){apply(ftsm_90[,idx], 1, sum, na.rm = T)}) # sum of fluxes per year, for each iteration of the bootstrap. Result is a matrix with nrow_boot rows and  (1 column per year)
  sum_instant_q_90 <- sapply(index_years, function(idx){apply(q_90[,idx], 1, sum, na.rm = T)}) # sum of discharge per year, for each iteration of the bootstrap. Result is a matrix with nrow_boot rows and 1 columns per year
  mean_instant_q_90 <- sapply(index_years, function(idx){apply(q_90[,idx], 1, mean, na.rm = T)}) # mean discharge per year

  weighted_annual_flux_ton.y_90 <- sum_instant_flux_ton.y_90 / sum_instant_q_90 * mean_instant_q_90 *6*24*365 # time step of observations is 10 min
  
  waf_90[[i]] <- weighted_annual_flux_ton.y_90
}

```

```{r 90-percent-mean}
waf_90_mean <- c()
waf_90_upr <- c()
waf_90_lwr <- c()

for(i in 1:length(unique_years)){
  waf_90_mean[i] <- lapply(waf_90, function(x) x[,i]) %>% unlist() %>% mean()
  waf_90_upr[i] <- lapply(waf_90, function(x) x[,i]) %>% unlist() %>% quantile(0.975)
  waf_90_lwr[i] <- lapply(waf_90, function(x) x[,i]) %>% unlist() %>% quantile(0.025)
  }

wiaf_90 <- matrix(NA_real_, nrow = 1000, ncol = 600)
for(i in 1:1000){
  mci <- lapply(waf_90, function(x) x[i, ]) %>% unlist # flux interannual pour monde MC i, pour les 6 ans
  wiaf_90[i,] <- mci
}


wiaf_90_rowmean <- rowMeans(wiaf_90)
wiaf_90_mean <- mean(wiaf_90_rowmean)
wiaf_90_sd <- sd(wiaf_90_rowmean)
wiaf_90_upr <- quantile(wiaf_90_rowmean) %>% quantile(0.975)
wiaf_90_lwr <- quantile(wiaf_90_rowmean) %>% quantile(0.025)
```


```{r visualisation-wiaf-90, eval = F}
# Merge in df
weighted_total_flux_df_90 <- data.frame(year = c(unique(galabre_w$year), "interannual"), 
                        annual_flux_mean = c(waf_90_mean, wiaf_90_mean), 
                        annual_flux_variability = c(rep(NA, 6), wiaf_90_sd), 
                        annual_flux_pi_lower = c(waf_90_lwr, wiaf_90_lwr), 
                        annual_flux_pi_upper = c(waf_90_upr, wiaf_90_upr),
                        group = c(rep("annual",6),"interannual"))

ggplot()+
  geom_col(data = weighted_total_flux_df_90, aes(x=year, y = annual_flux_mean, fill = group))+
    geom_errorbar(data = weighted_total_flux_df_30, aes(x = year, ymin = annual_flux_pi_lower, ymax = annual_flux_pi_upper, col = "prediction interval"), width = 0.3, linewidth = 0.8)+
  geom_errorbar(data = filter(weighted_total_flux_df_20, year == "interannual"), aes(x = year, ymin = annual_flux_mean - annual_flux_variability, ymax = annual_flux_mean + annual_flux_variability, col = "interannual variability"), width = 0.2, linewidth = 0.8, linetype = 2)+
  scale_fill_manual(values = c("annual" = "lightblue", "interannual" = "indianred"))+
  scale_color_manual(values = c("prediction interval" = "darkblue", "interannual variability" = "darkred"), name = "")+
   labs(x = "Year", y = "Flux (ton/year)", fill = "")+
  theme_minimal()+
  theme(axis.text.x = element_text(angle = 45, hjust = 1), legend.position = "bottom")

```

## Compare weighted fluxes

```{r compare-weighted-fluxes}
error_10 <- (wiaf_10_rowmean - interannual_flux_ton.y)/interannual_flux_ton.y * 100
error_10_pi <- quantile(error_10, probs = c(0.025, 0.5, 0.975), na.rm = T) # confidence interval for annual fluxes, per year. 3 lignes, 19 columns
error_10_mean <- mean(error_10)

error_20 <- (wiaf_20_rowmean - interannual_flux_ton.y)/interannual_flux_ton.y * 100
error_20_pi <- quantile(error_20, probs = c(0.025, 0.5, 0.975), na.rm = T) # confidence interval for annual fluxes, per year. 3 lignes, 19 columns
error_20_mean <- mean(error_20)

error_30 <- (wiaf_30_rowmean - interannual_flux_ton.y)/interannual_flux_ton.y * 100
error_30_pi <- quantile(error_30, probs = c(0.025, 0.5, 0.975), na.rm = T) # confidence interval for annual fluxes, per year. 3 lignes, 19 columns
error_30_mean <- mean(error_30)

error_40 <- (wiaf_40_rowmean - interannual_flux_ton.y)/interannual_flux_ton.y * 100
error_40_pi <- quantile(error_40, probs = c(0.025, 0.5, 0.975), na.rm = T) # confidence interval for annual fluxes, per year. 3 lignes, 19 columns
error_40_mean <- mean(error_40)

error_50 <- (wiaf_50_rowmean - interannual_flux_ton.y)/interannual_flux_ton.y * 100
error_50_pi <- quantile(error_50, probs = c(0.025, 0.5, 0.975), na.rm = T) # confidence interval for annual fluxes, per year. 3 lignes, 19 columns
error_50_mean <- mean(error_50)

error_60 <- (wiaf_60_rowmean - interannual_flux_ton.y)/interannual_flux_ton.y * 100
error_60_pi <- quantile(error_60, probs = c(0.025, 0.5, 0.975), na.rm = T) # confidence interval for annual fluxes, per year. 3 lignes, 19 columns
error_60_mean <- mean(error_60)

error_70 <- (wiaf_70_rowmean - interannual_flux_ton.y)/interannual_flux_ton.y * 100
error_70_pi <- quantile(error_70, probs = c(0.025, 0.5, 0.975), na.rm = T) # confidence interval for annual fluxes, per year. 3 lignes, 19 columns
error_70_mean <- mean(error_70)

error_80 <- (wiaf_80_rowmean - interannual_flux_ton.y)/interannual_flux_ton.y * 100
error_80_pi <- quantile(error_80, probs = c(0.025, 0.5, 0.975), na.rm = T) # confidence interval for annual fluxes, per year. 3 lignes, 19 columns
error_80_mean <- mean(error_80)

error_90 <- (wiaf_90_rowmean - interannual_flux_ton.y)/interannual_flux_ton.y * 100
error_90_pi <- quantile(error_90, probs = c(0.025, 0.5, 0.975), na.rm = T) # confidence interval for annual fluxes, per year. 3 lignes, 19 columns
error_90_mean <- mean(error_90)


weighted_error <- data.frame(percent_data = factor(c("10","20","30","40","50","60","70","80","90"),
                                          levels = c("10","20","30","40","50","60","70","80","90")),
                    error = c(error_10_mean, error_20_mean, error_30_mean, error_40_mean, error_50_mean, error_60_mean, error_70_mean, error_80_mean, error_90_mean),
                    pi_upr = c(error_10_pi[3], error_20_pi[3], error_30_pi[3], error_40_pi[3], error_50_pi[3], error_60_pi[3], error_70_pi[3], error_80_pi[3], error_90_pi[3]),
                    pi_lwr = c(error_10_pi[1], error_20_pi[1], error_30_pi[1], error_40_pi[1], error_50_pi[1], error_60_pi[1], error_70_pi[1], error_80_pi[1], error_90_pi[1]))

ggplot(data= weighted_error, aes(x = percent_data))+
  geom_point(aes(y = error))+
  geom_errorbar(aes(ymin=pi_lwr, ymax=pi_upr))+
  theme_minimal()

weighted_error %>% knitr::kable(digits = 2, row.names = F) %>% kableExtra::kable_styling()

```




