---
title: "lods"
output:
  html_document:
    toc: true
    toc_float: true
    number_sections: true
    code_folding: hide
date: "2025-06-06"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = F, warning = F, error = F, fig.align = "center", collapse = T,
                      cache = F)
```


```{r libraries}
lapply(c("dplyr", "data.table", "readxl"), library, character.only = T)
lapply(c("ggplot2","ggpubr"), library, character.only = T)
lapply(c("lubridate"), library, character.only = T)
lapply(c("knitr","kableExtra"), library, character.only = T)
library(here)

```
# Questions au responsable de site

Pourquoi y a-t-il des données DOC manquantes (après 2015) --> données sonde ? 

# Liens

https://sokarst.org/en/9-observatories-in-france/jurassic-karst-en/

cite data: https://catalogue.theia.data-terra.org/meta/TheiaOZCAR.KARS_DAT_LOUE-LI-8-JURASIK

# Load data

```{r bv}
bv <- 37 #from shapefile, 35 sur le site
unit_flux <- "ton"
```


```{r load-data-from-excel, message = F}

oc <- readxl::read_xlsx(path = "lods.xlsx", sheet = "OC", col_types = c("date",rep("numeric",9))) %>% unique()

debit <- readxl::read_xlsx(path = "lods.xlsx", sheet = "debit", col_types = c("date", "numeric", "numeric")) %>% unique()


lods <- merge(oc, debit, by = "DateHeure", all = T)

lods <- lods %>% mutate(
  year = year(lods$DateHeure),
  commondate = update(DateHeure, year = 2000),
  period = as.numeric(difftime(shift(DateHeure, type = "lead"), DateHeure, units = "secs")),
  q_L.s = q_m3.s*1e3
  )

```


## Visualisation

```{r plot-by-year-doc, fig.dim = c(10,20)}

title <- expression(atop("Series of Q and DOC by year"))

plots <- ggarrange(
ggplot(lods, aes(x = as.Date(commondate)))+
  geom_point(aes(y = q_L.s, col = "Débit, L/s"), alpha = 0.5)+
  scale_x_date(labels = function(x) format(x, "%d-%b"), date_minor_breaks = "1 month", name = "")+
  scale_color_manual(values = c("lightblue"), name = "")+
  facet_grid(rows = vars(year))+
  labs(y = "Débit, L/s", col = "")+
  theme_bw(base_size = 15)+
  theme(legend.position = "none"),

ggplot(lods, aes(x = as.Date(commondate)))+
  geom_point(aes(y = doc_mg.L, col = "DOC, mg.L"), alpha = 0.5)+
  scale_x_date(labels = function(x) format(x, "%d-%b"), date_minor_breaks = "1 month", name = "")+
  scale_color_manual(values = c("palegreen4"), name = "")+
  facet_grid(rows = vars(year))+
  labs(y = "DOC, mg/L", col = "")+
  theme_bw(base_size = 15)+
  theme(legend.position = "none")
)

annotate_figure(plots, top = text_grob(title))

```

```{r histograms}
ggarrange(
  ggplot(lods)+geom_histogram(aes(q_L.s),fill = "lightblue")+labs(x= "Débit, L/s", y = "")+theme_bw(),
  ggplot(lods)+geom_histogram(aes(doc_mg.L), fill = "palegreen4")+labs(x= "DOC, mg/L", y = "")+theme_bw(),
  ggplot(lods)+geom_histogram(aes(log10(q_L.s)),fill = "lightblue")+labs(x= "Débit (log10), L/s", y = "")+theme_bw(),
  ggplot(lods)+geom_histogram(aes(log(doc_mg.L)), fill = "palegreen4")+labs(x= "DOC (log10), mg/L", y = "")+theme_bw()
)
```



## Complete years


Retrait des trois premières années. Valeurs manquantes DOC: pb de capteur ou absence de flux ?

```{r complete-years}
complete_years <- unique(lods$year)[-c(1,2,3,5)]
lods_complete <- lods %>% filter(year %in% complete_years)
```


## Characteristics

```{r summary-data}
summary_lods <- merge(
lods %>% subset(!is.na(doc_mg.L)) %>% group_by(year) %>% summarise("Number of DOC observations" = n(), "DOC range, mg/L" = paste(round(quantile(doc_mg.L, probs = c(0,0.5,1), na.rm = T),1), collapse = " / ")),
lods %>% subset(!is.na(q_L.s)) %>% group_by(year) %>% summarise("Number of Q observations" = n(), "Q range, L/s" = paste(round(quantile(q_L.s, probs = c(0,0.5,1), na.rm = T),1), collapse = " / ")), by = "year", all = T) %>% 
  merge(lods %>% group_by(year) %>% summarise("Number of days sampled" = length(unique(as.Date(DateHeure)))), by = "year", all = T) %>%
  merge(lods %>% group_by(year) %>% summarise("Correlation DOC/Q" = round(cor(doc_mg.L, q_L.s, use = "pairwise.complete.obs"),2)), by = "year", all = T) %>%
  merge(lods %>% group_by(year) %>% summarise("Median sampling interval, min" = round(median(period, na.rm = T)/60,1)), by = "year", all = T) %>%
  rbind(c("All years", 
          dim(subset(lods, !is.na(doc_mg.L)))[1], 
          paste(quantile(lods$doc_mg.L, probs = c(0,0.5,1), na.rm = T), collapse = " / "), 
          dim(subset(lods, !is.na(q_L.s)))[1], 
          paste(round(quantile(lods$q_L.s, probs = c(0,0.5,1), na.rm = T),1), collapse = " / "), 
          length(unique(as.Date(lods$DateHeure))),
          round(cor(lods$doc_mg.L, lods$q_L.s, use = "pairwise.complete.obs" ),2),
          round(median(lods$period, na.rm = T)/60,1)
           ))  %>%
      rbind(c("Complete years", 
            dim(subset(lods_complete, !is.na(doc_mg.L)))[1], 
            paste(quantile(lods_complete$doc_mg.L, probs = c(0,0.5,1), na.rm = T), collapse = " / "), 
            dim(subset(lods_complete, !is.na(q_L.s)))[1], 
            paste(round(quantile(lods_complete$q_L.s, probs = c(0,0.5,1), na.rm = T),1), collapse = " / "), 
            length(unique(as.Date(lods_complete$DateHeure))),
            round(cor(lods_complete$doc_mg.L, lods_complete$q_L.s, use = "pairwise.complete.obs" ),2),
            round(median(lods_complete$period, na.rm = T)/60,1)
            )
            )

knitr::kable(summary_lods, caption = "Summary table of lods data") %>% kableExtra::kable_styling()

```


# Annual and interannual flux 


DOC est mesurée par sonde. Quelle incertitude ? 


```{r uncertainties}
nyears <- length(complete_years)

q_u <- 0.1

nobs <- dim(lods_complete)[1]
nrep <- 1000
```

## Total flux

```{r compute-flux}
#doc matrix
doc_meas <- matrix(lods_complete$doc_mg.L, nrow = nrep, ncol = nobs, byrow = T) # repeats nrep lines with observations

# doc_cv <- 3.3*doc_meas^(-0.6) # from all data available on 29/05/2026
# doc_random <- matrix(rnorm(nrep*nobs, mean = 0, sd = 1), nrow=nrep, ncol = nobs)
# doc_noise <- doc_cv*doc_random
doc_mat <- doc_meas #* (1 + doc_noise/100) # final value of doc, with noise in percent

# Q matrix
q_meas <- matrix(lods_complete$q_L.s, nrow = nrep, ncol = nobs, byrow = T) # repeats nrow_boot times the vector q_L.s
q_noise <- matrix(rnorm(nrep*nobs, mean = 0, sd = q_u), nrow = nrep, ncol = nobs) # creates a noise in percent (proportion), between 0 and 10%
q_mat <- q_meas * (1 + q_noise) # final value of q, with noise

# period mat
period_mat <- matrix(lods_complete$period, nrow = nrep, ncol = nobs, byrow = T) # in hours



# Flux per time step
flux_ton_mat <- doc_mat*1e-9*q_mat*period_mat # period_mat is in s 
flux_ton.s_mat <- doc_mat*1e-9*q_mat # without period



# Annual flux
index_years <- lapply(complete_years, function(y){which(lods_complete$year == y)}) # list of indices corresponding to each year
annual_flux_ton.y <- sapply(index_years, function(idx){apply(flux_ton_mat[,idx], 1, sum, na.rm = T)}) # sum of fluxes per year, for each iteration of the bootstrap. Result is a matrix with nrow_boot rows and n_years columns 



annual_flux_pi <- apply(annual_flux_ton.y, 2, quantile, probs = c(0.025, 0.5, 0.975), na.rm = T) # prediction interval for annual fluxes, per year. 3 lignes, 19 columns
annual_flux_mean <- colMeans(annual_flux_ton.y, na.rm = T) # mean annual flux per year. 1 vector
annual_flux_sd <- apply(annual_flux_ton.y, 2, sd, na.rm = T) # standard deviation of annual flux per year. Is just an estimate of goodness of mean, not as good as than the confidence interval. 

annual_flux_df <- data.frame(year = complete_years, 
                        annual_flux_mean = annual_flux_mean, 
                        annual_flux_variability = annual_flux_sd, 
                        annual_flux_pi_lower = annual_flux_pi[1,], 
                        annual_flux_pi_upper = annual_flux_pi[3,])

# Interannual flux 
interannual_flux_ton.y <- rowMeans(annual_flux_ton.y, na.rm = T) # mean interannual flux per iteration of the bootstrap
interannual_flux_pi <- quantile(interannual_flux_ton.y, probs = c(0.025, 0.5, 0.975), na.rm = T) # prediction interval
interannual_flux_mean <- mean(interannual_flux_ton.y, na.rm = T) # mean interannual flux
interannual_flux_variability <- sd(annual_flux_mean, na.rm = T) # standard deviation of interannual flux per year

interannual_flux_df <- data.frame(year = "interannual", annual_flux_mean = interannual_flux_mean, 
                                  annual_flux_variability = interannual_flux_variability,
                        annual_flux_pi_lower = interannual_flux_pi[1], 
                        annual_flux_pi_upper = interannual_flux_pi[3])

total_flux_df <- rbind(annual_flux_df, interannual_flux_df)
total_flux_df$group <- c(rep("annual", nyears), "interannual")

# Q df ----

annual_q <- sapply(index_years, function(idx){apply(q_mat[,idx], 1, sum, na.rm = T)}) # sum of fluxes per year, for each iteration of the bootstrap. Result is a matrix with nrow_boot rows and 19 columns (1 per year)
annual_q_pi <- apply(annual_q, 2, quantile, probs = c(0.025, 0.5, 0.975), na.rm = T) # prediction interval for annual fluxes, per year. 3 lignes, 19 columns
annual_q_mean <- colMeans(annual_q, na.rm = T) # mean annual flux per year. 1 vector
annual_q_sd <- apply(annual_q, 2, sd, na.rm = T) # standard deviation of annual flux per year. Is just an estimate of goodness of mean, not as good as than the confidence interval. 
interannual_q <- rowMeans(annual_q, na.rm = T) # mean interannual flux per iteration of the bootstrap
interannual_q_pi <- quantile(interannual_q, probs = c(0.025, 0.5, 0.975), na.rm = T) # prediction interval
interannual_q_mean <- mean(interannual_q, na.rm = T) # mean interannual flux
interannual_q_variability <- sd(annual_q_mean, na.rm = T) # standard deviation of interannual flux per year

q_df <- data.frame(year = c(complete_years, "interannual"), 
                        q_mean = c(annual_q_mean, interannual_q_mean),
                        q_variability = c(annual_flux_sd, interannual_q_variability), 
                        q_pi_lower = c(annual_q_pi[1,], interannual_q_pi[1]), 
                        q_pi_upper = c(annual_q_pi[3,], interannual_q_pi[3]),
                   group = c(rep("annual", nyears), "interannual"))

# Plot -----
ggplot()+
  geom_col(data = total_flux_df, aes(x=year, y = annual_flux_mean, fill = group))+
    geom_errorbar(data = total_flux_df, aes(x = year, ymin = annual_flux_pi_lower, ymax = annual_flux_pi_upper, col = "prediction interval"), width = 0.3, size = 0.8)+
  geom_errorbar(data = filter(total_flux_df, year == "interannual"), aes(x = year, ymin = annual_flux_mean - annual_flux_variability, ymax = annual_flux_mean + annual_flux_variability, col = "interannual variability"), width = 0.2, size = 0.8, linetype = 2)+
  scale_fill_manual(values = c("annual" = "lightblue", "interannual" = "indianred"))+
  scale_color_manual(values = c("prediction interval" = "darkblue", "interannual variability" = "darkred"), name = "")+
   labs(x = "Year", y = "Flux (ton/year)", fill = "")+
  theme_minimal(base_size = 15)+
  theme(axis.text.x = element_text(angle = 45, hjust = 1), legend.position = "bottom")

ggplot()+
  geom_col(data = q_df, aes(x=year, y = q_mean, fill = group))+
    geom_errorbar(data = q_df, aes(x = year, ymin = q_pi_lower, ymax = q_pi_upper, col = "prediction interval"), width = 0.3, size = 0.8)+
  geom_errorbar(data = filter(q_df, year == "interannual"), aes(x = year, ymin = q_mean - q_variability, ymax = q_mean + q_variability, col = "interannual variability"), width = 0.2, size = 0.8, linetype = 2)+
  scale_fill_manual(values = c("annual" = "lightblue", "interannual" = "indianred"))+
  scale_color_manual(values = c("prediction interval" = "darkblue", "interannual variability" = "darkred"), name = "")+
   labs(x = "Year", y = "Discharge (m3/year)", fill = "")+
  theme_minimal(base_size = 15)+
  theme(axis.text.x = element_text(angle = 45, hjust = 1), legend.position = "bottom")

knitr::kable(total_flux_df, digits = 2, row.names = F) %>% kableExtra::kable_styling()

```

## Specific flux

```{r specific-flux}
total_sflux_df <- cbind(total_flux_df[,"year"], total_flux_df[,2:5] / bv, total_flux_df[,"group"]) %>% setNames(names(total_flux_df))
#total_sflux_df <- rbind(annual_sflux_df, interannual_sflux_df)
total_sflux_df$group <- c(rep("annual", nyears), "interannual")

ggplot()+
  geom_col(data = total_sflux_df, aes(x=year, y = annual_flux_mean, fill = group), width = 0.8)+
    geom_errorbar(data = total_sflux_df, aes(x = year, ymin = annual_flux_pi_lower, ymax = annual_flux_pi_upper, col = "prediction interval"), width = 0.3, size = 0.8)+
  geom_errorbar(data = filter(total_sflux_df, year == "interannual"), aes(x = year, ymin = annual_flux_mean - annual_flux_variability, ymax = annual_flux_mean + annual_flux_variability, col = "interannual variability"), width = 0.2, size = 0.8, linetype = 2)+
  scale_fill_manual(values = c("annual" = "lightblue", "interannual" = "indianred"))+
  scale_color_manual(values = c("prediction interval" = "darkblue", "interannual variability" = "darkred"), name = "")+
   labs(x = "Year", y = "Flux (tons/km2/year)", fill = "")+
  theme_minimal(base_size = 15)+
  theme(axis.text.x = element_text(angle = 45, hjust = 1), legend.position = "bottom")

ggsave(here("figures","sflux_naizin.svg"))

knitr::kable(total_sflux_df, digits = 2, row.names = F) %>% kableExtra::kable_styling()
```


## Variance decomposition

Comme flux = DOC × Q × période, on a exactement : ln(flux) = ln(DOC) + ln(Q) + ln(période)
Et donc, sans approximation : Var(ln flux) = Var(ln DOC) + Var(ln Q) + 2·Cov(ln DOC, ln Q)
(Claude)

Les lignes où Q = 0 sont exclues du calcul de variance.

```{r variance}
## Variances par année

list_var <- lapply(index_years, function(idx){
  
lnQ <- as.vector(log(q_mat[,idx]))
lnDOC <- as.vector(log(doc_mat[,idx]))
lnp <- as.vector(log(period_mat[,idx]))

mask <- complete.cases(lnDOC, lnQ, lnp)  &
        is.finite(lnDOC) & is.finite(lnQ) & is.finite(lnp)

M <- cbind(DOC = lnDOC[mask], Q = lnQ[mask], p = lnp[mask])

cov_matrix <- cov(M, use = "pairwise.complete.obs") 

# verif
var_lnF_check <- sum(cov_matrix)
var_lnF_direct <- var(rowSums(M))

if(var_lnF_check != var_lnF_direct){warning("Attention : les variances ne correspondent pas")}

return(cov_matrix)
})

var_flux_by_year <- lapply(list_var, function(i){
  var_flux = sum(i)
  setNames(var_flux, "var_lnF")}) %>% bind_rows(.id = "year")
vars_by_year <- lapply(list_var, diag) %>% bind_rows(.id = "year") # variance des paramètres par année
cov_by_year <- lapply(list_var, function(i){
  vals <- i[upper.tri(i)]
  setNames(as.list(vals), c("cov_qdoc","cov_pdoc","cov_pq"))}) %>% 
  bind_rows(.id = "year") 

annual_variances <- merge(var_flux_by_year, vars_by_year, by = "year") %>% merge(cov_by_year, by = "year")
annual_variances$year <- complete_years


# Variance interannuelle

lnQ <- as.vector(log(q_mat))
lnDOC <- as.vector(log(doc_mat))
lnp <- as.vector(log(period_mat))

mask <- complete.cases(lnDOC, lnQ, lnp)  &
        is.finite(lnDOC) & is.finite(lnQ) & is.finite(lnp)

M <- cbind(DOC = lnDOC[mask], Q = lnQ[mask], p = lnp[mask])

cov_matrix <- cov(M, use = "pairwise.complete.obs") 

# verif
var_lnF_check <- sum(cov_matrix)
var_lnF <- var(rowSums(M))

if(var_lnF_check != var_lnF){warning("Attention : les variances ne correspondent pas")}


# put results in df
vars_interannual <- c(var_lnF, diag(cov_matrix)) # variance des paramètres par année
cov_interannual <- cov_matrix[upper.tri(cov_matrix)] %>%
  setNames(c("cov_qdoc","cov_pdoc","cov_pq")) 

interannual_variances <- c(year = "Interrannuel", vars_interannual, cov_interannual)

all_variances <- rbind(annual_variances, interannual_variances) %>% mutate(across(where(is.character) & !any_of("year"), as.numeric))



variance_decomposition <- all_variances  %>% 
  mutate(part_Q = Q/var_lnF, part_DOC = DOC/var_lnF, part_p = p/var_lnF, 
         part_covqdoc = 2*cov_qdoc/var_lnF, part_covpq = 2*cov_pq/var_lnF, part_covpdoc = 2*cov_pdoc/var_lnF, 
         part_p_tot = part_p+part_covpq+part_covpdoc, 
         check = part_Q+part_DOC+part_p+part_covqdoc+part_covpq+part_covpdoc)


vd_long <- variance_decomposition %>%
  select(year, part_Q, part_DOC, part_covqdoc, part_p_tot) %>%
  tidyr::pivot_longer(cols = c(part_Q, part_DOC, part_covqdoc, part_p_tot),
               names_to = "terme", values_to = "part")  %>%
  mutate(terme = recode(terme,
                         part_Q = "Débit (Q)",
                         part_DOC = "DOC",
                         part_covqdoc = "Covariance Q-DOC",
                        part_p_tot = "Variance due aux intervalles de prélèvement"))

ggplot(vd_long, aes(x = year, y = part, fill = terme)) +
  geom_col(position = "stack") +
  geom_hline(yintercept = 0, linetype = "dashed", color = "grey40") +
  scale_fill_manual(values = c("Débit (Q)" = "lightblue",
                                "DOC" = "indianred",
                                "Covariance Q-DOC" = "darkblue",
                               "Variance due aux intervalles de prélèvement" = "darkred")) +
  scale_y_continuous(labels = scales::percent, breaks = c(-0.40,-0.20,0,0.20,0.40,0.60,0.80,1.00,1.2,1.4)) +
  labs(x = "Année", y = "Part de la variance du log-flux",
       fill = "Terme",
       title = "Contribution de Q, DOC et de leur covariance à la variance du flux") +
  theme_bw() + theme(legend.position = "bottom", axis.text.x = element_text(angle = 45, vjust = 0.5))

vd_long_abs <- variance_decomposition %>%
  select(year, Q, DOC, p, cov_qdoc, cov_pq, cov_pdoc) %>%
  tidyr::pivot_longer(cols = -year, names_to = "terme", values_to = "valeur")

ggplot(vd_long_abs, aes(x = year, y = valeur, fill = terme)) +
  geom_col(position = "dodge") +
  geom_point(data = variance_decomposition, aes(x = year, y = var_lnF),
             inherit.aes = FALSE, shape = 18, size = 3) +
  scale_fill_manual(values = c("darkblue","lightblue","darkred","indianred","palegreen4","cornsilk3"))+
   theme_bw() + theme(legend.position = "bottom", axis.text.x = element_text(angle = 45, vjust = 0.5))+
  labs(y = "Variance (échelle log)", title = "Termes de la décomposition (valeurs absolues)")

```

# Export données

```{r exporter-valeurs-dans-csv-commun}

library(readxl)
library(writexl)


rmd_id <- "lods"

if(unit_flux == "ton"){
rmd_values <- data.frame(
  rmd = rmd_id,
  carbon  = "DOC",
  flux_ton = total_flux_df$annual_flux_mean[total_flux_df$year == "interannual"],
    flux_ton_sd = total_flux_df$annual_flux_variability[total_flux_df$year == "interannual"],
    flux_ton_pil = total_flux_df$annual_flux_pi_lower[total_flux_df$year == "interannual"],
    flux_ton_piu = total_flux_df$annual_flux_pi_upper[total_flux_df$year == "interannual"],
    flux_ton_km2 = total_sflux_df$annual_flux_mean[total_flux_df$year == "interannual"],
   flux_ton_km2_sd = total_sflux_df$annual_flux_variability[total_flux_df$year == "interannual"],
   flux_ton_km2_pil = total_sflux_df$annual_flux_pi_lower[total_flux_df$year == "interannual"],
   flux_ton_km2_piu = total_sflux_df$annual_flux_pi_upper[total_flux_df$year == "interannual"],
  nb_years = length(complete_years)
)
} else if(unit_flux == "kg"){
  rmd_values <- data.frame(
  rmd = rmd_id,
  carbon  = "DOC",
  flux_ton = total_flux_df$annual_flux_mean[total_flux_df$year == "interannual"]*1e-3,
    flux_ton_sd = total_flux_df$annual_flux_variability[total_flux_df$year == "interannual"]*1e-3,
    flux_ton_pil = total_flux_df$annual_flux_pi_lower[total_flux_df$year == "interannual"]*1e-3,
    flux_ton_piu = total_flux_df$annual_flux_pi_upper[total_flux_df$year == "interannual"]*1e-3,
    flux_ton_km2 = total_sflux_df$annual_flux_mean[total_flux_df$year == "interannual"]*1e-3,
   flux_ton_km2_sd = total_sflux_df$annual_flux_variability[total_flux_df$year == "interannual"]*1e-3,
   flux_ton_km2_pil = total_sflux_df$annual_flux_pi_lower[total_flux_df$year == "interannual"]*1e-3,
   flux_ton_km2_piu = total_sflux_df$annual_flux_pi_upper[total_flux_df$year == "interannual"]*1e-3,
  nb_years = length(complete_years)
  )
}


# Lire le fichier existant ou créer un dataframe vide
if (file.exists(here("resultats.xlsx"))) {
  df_shared <- read_xlsx(here("resultats.xlsx"))
} else {
  df_shared <- data.frame()
}

# Mettre à jour la ligne du Rmd ou l'ajouter si absente
if (rmd_id %in% df_shared$rmd) {
  df_shared[df_shared$rmd == rmd_id, ] <- rmd_values  # mise à jour
} else {
  df_shared <- rbind(df_shared, rmd_values)            # ajout
}



# Réécrire
write_xlsx(df_shared, here("resultats.xlsx"))
```


```{r exit}
knitr::knit_exit()
```


**************

# Previous code

```{r plot, fig.dim = c(10, 10)}
n <- 2

ggplot(data = subset(lods, !year %in% c(1991, 1992, 1994, 1996)), aes(x=commondate))+ 
  geom_point(aes(y= TOC*n, col = "TOC, m3/L"), alpha = 0.5, size = 1) +
  geom_point(aes(y= q_m3.s, col = "Discharge, m3/s"), alpha = 0.5, size = 1) +
  scale_x_date(labels = function(x) format(x, "%d %B"), date_minor_breaks = "1 month")+
  #scale_y_continuous(sec.axis = sec_axis(~./n, name = "TOC, mg/L"))+
  scale_color_manual(values = c("palegreen4","lightblue","firebrick"))+
  facet_grid(rows = vars(year), scales = "free")+
  labs(title = "Discharge (m3/s) and TOC (mg/L)", x = "", y = "Discharge, m3/s", col = "")+
  theme_minimal()+
  theme(legend.position = "bottom", axis.text.x = element_text(angle = 90))
```

```{r debit-toc}
ggplot(lods, aes(x = q_m3.s))+
  geom_point(aes(y=TOC), size = 1)+
  scale_color_viridis_d()+
  theme_minimal()
```

```{r toc-pred}

lmtoc <- lm(TOC~q_m3.s, data = lods)
summary(lmtoc)

lods$toc_pred <- predict(lmtoc, newdata = lods)


ggplot(lods, aes(x = q_m3.s))+
  geom_point(aes(y=TOC, col = "TOC measured"), size = 1)+
  geom_point(aes(y=toc_pred, col = "TOC pred"), size = 0.5)+
  scale_color_manual(values = c("lightblue","palegreen4")) +
  theme_minimal()


pltoc <- lm(log(TOC)~log(q_m3.s), data = subset(lods, TOC != 0 & q_m3.s != 0))
summary(pltoc)

lods$toc_pred2 <- predict(pltoc, newdata = lods) %>% exp()


ggplot(lods, aes(x = q_m3.s))+
  geom_point(aes(y=TOC, col = "TOC measured"), size = 1)+
  geom_point(aes(y=toc_pred2, col = "TOC pred"), size = 0.5)+
  scale_color_manual(values = c("lightblue","palegreen4")) +
  theme_minimal()

```

```{r nb-toc-values}

print(paste("pred = ", dim(subset(lods, !is.na(toc_pred)))[1]))
print(paste("measured = ", dim(subset(lods, !is.na(TOC)))[1]))
```

# Flux TOC

```{r step-fluxes-measured-toc, eval = T}
lods$ftoc_kg.s <- with(lods, TOC * 1e-6/1e-3 * q_m3.s) # mg/L converted to kg/m3
```


https://sokarst.org/en/9-observatories-in-france/jurassic-karst-en/

```{r calcul-yearly-flux-measured-toc, eval = T} 

yearly_fluxes <- lods %>%
                  group_by(year) %>% 
                    summarise(ftoc_kg.year = sum(ftoc_kg.s * periodj * 24 * 60 * 60, na.rm = T), # period in days  -> we get kg, for each year 
                              ftoc_kg.s_sum = sum(ftoc_kg.s, na.rm = T), # sum of kg/s in kg/s
                              percent_poc_included = sum(!is.na(ftoc_kg.s))/n()*100,
                              nb_days_sampled = length(unique(Date)),
                              nb_days_sampled_toc = length(unique(Date[!is.na(TOC)])),
                              sum_discharge.year = sum(q_m3.s[!is.na(ftoc_kg.s)], na.rm = T),  # faut-il inclure les débits correspondants à des heures où le POC n'est pas mesuré?
                              mean_discharge.year = mean(q_m3.s[!is.na(ftoc_kg.s)], na.rm = T), 
                              sd_discharge.year = sd(q_m3.s[!is.na(ftoc_kg.s)], na.rm = T)) 
bv <- 35 

# fluxes by adding all hourly fluxes, with uncertainty depending on the nb of observations per year
yearly_fluxes$ftoc_kg.year.km2 <- yearly_fluxes$ftoc_kg.year/bv

# fluxes with ponderation method @Nemery2013 citing Walling and Webb 1985
#yearly_fluxes$ftoc_ww_kg.year <- with(yearly_fluxes, ftoc_kg.s_sum/sum_discharge.year*mean_discharge.year) * 60 * 60 * 24 * 365
yearly_fluxes$ftoc_ww_kg.year.km2 <- with(yearly_fluxes, ftoc_kg.s_sum/sum_discharge.year*mean_discharge.year) * 60 * 60 * 24 * 365 / bv
```

the weight method works if all discharge values are included not only those with a poc value??

```{r figures-flux-measured-toc, eval = F} 
yearly_fluxes %>% dplyr::mutate_if(is.numeric, funs(as.character(signif(., 3)))) %>% knitr::kable() %>% kableExtra::kable_styling()
```

```{r compare-fluxes-measured-toc}
yearly_fluxes$label <- paste(round(yearly_fluxes$nb_days_sampled,2), "d Q\n", round(yearly_fluxes$nb_days_sampled_toc,2), " d toc")

ggplot(yearly_fluxes, aes(x = year))+
  geom_col(aes(y = ftoc_kg.year.km2, fill = "TOC flux as sum"), position = position_nudge(-0.2), width = 0.4)+
  geom_col(aes(y = ftoc_ww_kg.year.km2, fill = "POC flux as weigthed"), position = position_nudge(0.2), width = 0.4)+
  geom_label(aes(x = year, y = ftoc_ww_kg.year.km2, label = label), nudge_y = 2, label.size = 0.1, size = 2)+
  scale_x_continuous(breaks = c(unique(yearly_fluxes$year)), minor_breaks = NULL)+
  scale_size_continuous(range = c(0.1,10))+
  scale_fill_manual(values = c("palegreen4", "lightblue"))+
  labs(x = "", fill = "", y = "Flux de POC, kg/year/km2")+
  theme_minimal()+
  theme(legend.position = "bottom")

ggplot(subset(yearly_fluxes, !year %in% c(2013, 2014)), aes(x = as.character(year)))+
  geom_col(aes(y = ftoc_kg.year.km2, fill = "TOC flux as sum"), position = position_nudge(-0.2), width = 0.4)+ 
  geom_col(aes(y = ftoc_ww_kg.year.km2, fill = "POC flux as weigthed"), position = position_nudge(0.2), width = 0.4)+
  geom_label(aes(x = as.character(year), y = ftoc_ww_kg.year.km2, label = label), nudge_y = 10, label.size = 0.1, size = 2)+
  scale_size_continuous(range = c(0.1,10))+
  scale_fill_manual(values = c("palegreen4", "lightblue"))+
  labs(x = "", fill = "", y = "Flux de POC, kg/year/km2")+
  theme_minimal()+
  theme(legend.position = "bottom")
```

```{r interrannual-fluxes-measured-toc}
yf <- yearly_fluxes %>% subset(!year %in% c(2013,2014))

mixedfluxes_mean <- with(yf, ifelse(nb_days_sampled_toc < 200, ftoc_ww_kg.year.km2, ftoc_kg.year.km2)) %>% mean(na.rm = T)
mixedfluxes_sd <- with(yf, ifelse(nb_days_sampled_toc < 200, ftoc_ww_kg.year.km2, ftoc_kg.year.km2)) %>% sd(na.rm = T)

means <- data.frame(
  "Mean fdoc sum, kg/year" = mean(yf$ftoc_kg.year.km2, na.rm = T),
  "Sd fdoc sum" = sd(yf$ftoc_kg.year.km2, na.rm = T),
  "Mean fdoc weighted, kg/year" = mean(yf$ftoc_ww_kg.year.km2, na.rm = T),
  "Sd fdoc weighted" = sd(yf$ftoc_ww_kg.year.km2, na.rm = T),
    "Mean fdoc mixed" = mixedfluxes_mean,
  "Sd fdoc mixed" = mixedfluxes_sd
)

knitr::kable(t(means), digits = 3) %>% kableExtra::kable_styling()
```


# DOC

```{r plot-doc, fig.dim = c(10, 10)}
n <- 2

ggplot(data = subset(lods, !year %in% c(1991, 1992, 1994, 1996)), aes(x=commondate))+ 
  geom_point(aes(y= DOC*n, col = "DOC, m3/L"), alpha = 0.5, size = 1) +
  geom_point(aes(y= q_m3.s, col = "Discharge, m3/s"), alpha = 0.5, size = 1) +
  scale_x_date(labels = function(x) format(x, "%d %B"), date_minor_breaks = "1 month")+
  #scale_y_continuous(sec.axis = sec_axis(~./n, name = "DOC, mg/L"))+
  scale_color_manual(values = c("palegreen4","lightblue","firebrick"))+
  facet_grid(rows = vars(year), scales = "free")+
  labs(title = "Discharge (m3/s) and DOC (mg/L)", x = "", y = "Discharge, m3/s", col = "")+
  theme_minimal()+
  theme(legend.position = "bottom", axis.text.x = element_text(angle = 90))
```

```{r debit-doc}
ggplot(lods, aes(x = q_m3.s))+
  geom_point(aes(y=DOC), size = 1)+
  scale_color_viridis_d()+
  theme_minimal()
```

```{r doc-pred}

lmdoc <- lm(DOC~q_m3.s, data = lods)
summary(lmdoc)

lods$doc_pred <- predict(lmdoc, newdata = lods)


ggplot(lods, aes(x = q_m3.s))+
  geom_point(aes(y=DOC, col = "DOC measured"), size = 1)+
  geom_point(aes(y=doc_pred, col = "DOC pred"), size = 0.5)+
  scale_color_manual(values = c("lightblue","palegreen4")) +
  theme_minimal()


pldoc <- lm(log(DOC)~log(q_m3.s), data = subset(lods, DOC != 0 & q_m3.s != 0))
summary(pldoc)

lods$doc_pred2 <- predict(pldoc, newdata = lods) %>% exp()


ggplot(lods, aes(x = q_m3.s))+
  geom_point(aes(y=DOC, col = "TOC measured"), size = 1)+
  geom_point(aes(y=doc_pred2, col = "TOC pred"), size = 0.5)+
  scale_color_manual(values = c("lightblue","palegreen4")) +
  theme_minimal()

```

```{r nb-doc-values}

print(paste("pred = ", dim(subset(lods, !is.na(doc_pred)))[1]))
print(paste("measured = ", dim(subset(lods, !is.na(DOC)))[1]))
```

# Flux DOC

```{r step-fluxes-measured-doc, eval = T}
lods$fdoc_kg.s <- with(lods, DOC * 1e-6/1e-3 * q_m3.s) # mg/L converted to kg/m3
```


https://sokarst.org/en/9-observatories-in-france/jurassic-karst-en/

```{r calcul-yearly-flux-measured-doc, eval = T} 

yearly_fluxes <- lods %>%
                  group_by(year) %>% 
                    summarise(fdoc_kg.year = sum(fdoc_kg.s * periodj * 24 * 60 * 60, na.rm = T), # period in days  -> we get kg, for each year 
                              fdoc_kg.s_sum = sum(fdoc_kg.s, na.rm = T), # sum of kg/s in kg/s
                              percent_poc_included = sum(!is.na(fdoc_kg.s))/n()*100,
                              nb_days_sampled = length(unique(Date)),
                              nb_days_sampled_doc = length(unique(Date[!is.na(DOC)])),
                              sum_discharge.year = sum(q_m3.s[!is.na(fdoc_kg.s)], na.rm = T),  # faut-il inclure les débits correspondants à des heures où le POC n'est pas mesuré?
                              mean_discharge.year = mean(q_m3.s[!is.na(fdoc_kg.s)], na.rm = T), 
                              sd_discharge.year = sd(q_m3.s[!is.na(fdoc_kg.s)], na.rm = T)) 
bv <- 35 

# fluxes by adding all hourly fluxes, with uncertainty depending on the nb of observations per year
yearly_fluxes$fdoc_kg.year.km2 <- yearly_fluxes$fdoc_kg.year/bv

# fluxes with ponderation method @Nemery2013 citing Walling and Webb 1985
#yearly_fluxes$fdoc_ww_kg.year <- with(yearly_fluxes, fdoc_kg.s_sum/sum_discharge.year*mean_discharge.year) * 60 * 60 * 24 * 365
yearly_fluxes$fdoc_ww_kg.year.km2 <- with(yearly_fluxes, fdoc_kg.s_sum/sum_discharge.year*mean_discharge.year) * 60 * 60 * 24 * 365 / bv
```

the weight method works if all discharge values are included not only those with a poc value??

```{r figures-flux-measured-doc, eval = F} 
yearly_fluxes %>% dplyr::mutate_if(is.numeric, funs(as.character(signif(., 3)))) %>% knitr::kable() %>% kableExtra::kable_styling()
```

```{r compare-fluxes-measured-doc}
yearly_fluxes$label <- paste(round(yearly_fluxes$nb_days_sampled,2), "d Q\n", round(yearly_fluxes$nb_days_sampled_doc,2), " d doc")

ggplot(yearly_fluxes, aes(x = year))+
  geom_col(aes(y = fdoc_kg.year.km2, fill = "DOC flux as sum"), position = position_nudge(-0.2), width = 0.4)+
  geom_col(aes(y = fdoc_ww_kg.year.km2, fill = "DOC flux as weigthed"), position = position_nudge(0.2), width = 0.4)+
  geom_label(aes(x = year, y = fdoc_ww_kg.year.km2, label = label), nudge_y = 2, label.size = 0.1, size = 2)+
  scale_x_continuous(breaks = c(unique(yearly_fluxes$year)), minor_breaks = NULL)+
  scale_size_continuous(range = c(0.1,10))+
  scale_fill_manual(values = c("palegreen4", "lightblue"))+
  labs(x = "", fill = "", y = "Flux de POC, kg/year/km2")+
  theme_minimal()+
  theme(legend.position = "bottom")

ggplot(subset(yearly_fluxes, year %in% c(2000, 2001)), aes(x = as.character(year)))+
  geom_col(aes(y = fdoc_kg.year.km2, fill = "DOC flux as sum"), position = position_nudge(-0.2), width = 0.4)+ 
  geom_col(aes(y = fdoc_ww_kg.year.km2, fill = "POC flux as weigthed"), position = position_nudge(0.2), width = 0.4)+
  geom_label(aes(x = as.character(year), y = fdoc_ww_kg.year.km2, label = label), nudge_y = 10, label.size = 0.1, size = 2)+
  scale_size_continuous(range = c(0.1,10))+
  scale_fill_manual(values = c("palegreen4", "lightblue"))+
  labs(x = "", fill = "", y = "Flux de POC, kg/year/km2")+
  theme_minimal()+
  theme(legend.position = "bottom")
```

```{r interrannual-fluxes-measured-doc}
yf <- yearly_fluxes %>% subset(!year %in% c(2013,2014))

mixedfluxes_mean <- with(yf, ifelse(nb_days_sampled_doc < 200, fdoc_ww_kg.year.km2, fdoc_kg.year.km2)) %>% mean(na.rm = T)
mixedfluxes_sd <- with(yf, ifelse(nb_days_sampled_doc < 200, fdoc_ww_kg.year.km2, fdoc_kg.year.km2)) %>% sd(na.rm = T)

means <- data.frame(
  "Mean fdoc sum, kg/year" = mean(yf$fdoc_kg.year.km2, na.rm = T),
  "Sd fdoc sum" = sd(yf$fdoc_kg.year.km2, na.rm = T),
  "Mean fdoc weighted, kg/year" = mean(yf$fdoc_ww_kg.year.km2, na.rm = T),
  "Sd fdoc weighted" = sd(yf$fdoc_ww_kg.year.km2, na.rm = T),
    "Mean fdoc mixed" = mixedfluxes_mean,
  "Sd fdoc mixed" = mixedfluxes_sd
)

knitr::kable(t(means), digits = 3) %>% kableExtra::kable_styling()
```