---
title: "Isere Campus"
output: 
  html_document:
    code_folding: hide
    toc: true
    toc_float: true
    number_section: true
date: "2025-06-30"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = F, warning = F, error = F, fig.align = "center", collapse = T,
                      cache = T)
```

```{r libraries}

library(ggplot2)
library(ggpubr)

library(dplyr)
library(readxl)
library(lubridate)

library(nlme)

set.seed(1902)
```


# Données

Les données dont on dispose pour la station de mesures d'Isère - campus sont: 

* débits horaires de 2005 à 2025
* CMES de 2006 à 2025
* POC mesuré (et non calculé): 
    - Carbonisère: suivi hebdo de 2006 à 2008 + crue du 19 mai 2006  + chasse du 27/06/2006 + crue du 30/08/2006 + chasse du 5/06/2006
    - crues du 19/08/2022 (lave torrentielle) et chasse du 22/06/2022
    - suivi hebdo Carbonium (pas encore disponible)
* DOC: 
  - Carbonisère: suivi hebdo de 2006 à 2008 + crue du 19 mai 2006  + chasse du 27/06/2006 + crue du 30/08/2006 + chasse du 5/06/2006
  - suivi hebdo Carbonium (pas encore dispo)

## Charger les données

```{r data}

# Crues
carbonisere <- read_xlsx("Bilan carbonisère.xlsx")


crues_2022 <- read_xlsx(path = "Crues_Isère_2022.xlsx", sheet = "test_match") 
crues_2022$mes_mg.L <- NA
crues_2022$debit_m3.s <- NA
crues_2022$doc_mg.L <- NA

doc_isere_2011 <- read_excel("doc_isere_2011-2012.xls")
doc_isere_2011$name <- "DOC 2011"
doc_isere_2011$poc_percent <- NA
doc_isere_2011$mes_mg.L <- doc_isere_2011$mes_g.L * 1e3

poc_isere_2011 <- read_excel("poc_isere_2011-2012.xls")
poc_isere_2011$doc_mg.L <- NA
poc_isere_2011$name <- "POC 2011"
poc_isere_2011$mes_mg.L <- poc_isere_2011$mes_g.L * 1e3

crues <- rbind(select(carbonisere, c("DateHeure","name","debit_m3.s","mes_mg.L","poc_percent", "doc_mg.L")),select(crues_2022, c("DateHeure","name","debit_m3.s", "mes_mg.L","poc_percent", "doc_mg.L"))) %>%
  rbind(select(doc_isere_2011, c("DateHeure","name","debit_m3.s","mes_mg.L","poc_percent", "doc_mg.L"))) %>% rbind(select(poc_isere_2011, c("DateHeure","name","debit_m3.s","mes_mg.L","poc_percent", "doc_mg.L")))

# Chroniques BDOH
cmes <- readxl::read_xlsx(path = "isere.xlsx", sheet = "cmes", col_types = c("date","numeric","text")) %>% subset(Qualite == "v") %>% mutate(Qualite = NULL)
debit <- readxl::read_xlsx(path = "isere.xlsx", sheet = "debit", col_types = c("date","numeric","text")) %>% subset(Qualite == "v") %>% mutate(Qualite = NULL)


# Merge dataframe
isere <- merge(debit, cmes, by="DateHeure") %>% merge(crues, by = "DateHeure", all = T) 
isere$year <- year(isere$DateHeure)
isere$commondate <- as.Date(paste0("2000-", format(isere$Date,"%j")), "%Y-%j")

isere$period <- as.numeric(-(isere$DateHeure - lead(isere$DateHeure))) # period in s

summary_isere <- merge(
isere %>% subset(!is.na(poc_percent)) %>% group_by(year) %>% summarise(nb_poc = n()),
isere %>% subset(!is.na(cmes_g.L)) %>% group_by(year) %>% summarise(nb_cmes = n()),
by = "year", all = T) %>% 
  merge(isere %>% subset(!is.na(doc_mg.L)) %>% group_by(year) %>% summarise(nb_doc = n()), by = "year", all = T) %>%
  merge(isere %>% subset(!is.na(q_m3.s)) %>% group_by(year) %>% summarise(nb_q = n()), by = "year", all = T) %>%
  merge(isere %>% subset(!is.na(period)) %>% group_by(year) %>% summarise(total_period_j = round(sum(period)/(24*60*60))), by = "year", all = T)

isere$mes_for_fit <- isere$cmes_g.L
  
summary_isere %>% knitr::kable(caption = "Nombre d'observations de DOC, POC, CMES et débit par an") %>% kableExtra::kable_styling()

# poc_isere: only rows with defined poc_percent to fit model MES~POC
poc_isere <- filter(isere, !is.na(poc_percent))
poc_isere$mes_for_fit <- poc_isere$mes_mg.L/1000
poc_isere$mes_for_fit[which(is.na(poc_isere$mes_for_fit))] <-  poc_isere$cmes_g.L[which(is.na(poc_isere$mes_for_fit))] # add mes for POC 2011 to poc_isere (were not measured, but we have cmes)
poc_isere <- poc_isere %>% subset(!is.na(mes_for_fit))
```

## Aperçu débit, MES, DOC et POC par année

```{r annual-q-mes, fig.dim = c(10, 15)}

ggarrange(
ggplot(isere, aes(x = commondate)) + 
  geom_point(aes(y = q_m3.s), col = "lightblue", size = 0.5) +
  scale_x_date(labels = function(x) format(x, "%d-%b"), date_minor_breaks = "1 month", name = "")+
  facet_grid(rows = vars(year))+
  labs(x = "", y = "Q, m3/s") +
  theme_minimal()+
  theme(legend.position = "bottom"),

ggplot(isere, aes(x = commondate)) + 
  geom_point(aes(y = cmes_g.L), col = "palegreen4", size = 0.5) +
  scale_x_date(labels = function(x) format(x, "%d-%b"), date_minor_breaks = "1 month", name = "")+
  facet_grid(rows = vars(year))+
  labs(x = "", y = "CMES, g/L") +
  theme_minimal()+
  theme(legend.position = "bottom"),

ncol = 2
) %>%
  annotate_figure(top = text_grob("Mesures de débit et CMES", face = "bold", size = 14))

```

```{r annual-doc-poc, fig.dim = c(10, 5)}

ggarrange(

ggplot(subset(isere, !is.na(doc_mg.L)), aes(x = commondate)) + 
  geom_point(aes(y = doc_mg.L), col = "orange") +
  scale_x_date(labels = function(x) format(x, "%d-%b"), date_minor_breaks = "1 month", name = "")+
  facet_grid(rows = vars(year))+
  labs(x = "", y = "DOC, mg/L") +
  theme_minimal()+
  theme(legend.position = "bottom"),

ggplot(subset(isere, !is.na(poc_percent)), aes(x = commondate)) + 
  geom_point(aes(y = poc_percent), col = "darkred") +
  scale_x_date(labels = function(x) format(x, "%d-%b"), date_minor_breaks = "1 month", name = "")+
  facet_grid(rows = vars(year))+
  labs(x = "", y = "POC, %") +
  theme_minimal()+
  theme(legend.position = "bottom"),

ncol = 2
) %>%
  annotate_figure(top = text_grob("Mesures de DOC et POC", face = "bold", size = 14))



```

## Comparaison MES/CMES

Les mesures de **POC** sont réalisées parallèlement à des mesures de **MES**. La valeur de **MES** mesurée à cette occasion est légèrement différente de la valeur de **CMES** reconstruire à partir des sondes de turbidité. 

```{r compare-cmes-and-mes}
ggplot(isere)+
  geom_point(aes(x=cmes_g.L, y = mes_mg.L/1000, col = name))+
  geom_abline(slope = 1, intercept = 0)+
  scale_colour_viridis_d()+
  labs(title = "Comparaison entre CMES et MES", x = "CMES, g/L", y = "MES, g/L", name = "")+
  scale_x_continuous(limits = c(0,20))+ 
  theme_minimal()+
  theme(legend.position = "bottom")

ggarrange(
  ggplot(isere)+
    geom_point(aes(x = mes_mg.L, y = poc_percent, col = name))+
    scale_color_viridis_d()+
    scale_x_continuous(trans = "log", breaks = c(10,100,1000,2000))+scale_y_continuous(trans = "log", breaks = c(1,2,4,8))+
    labs( x = "MES, mg/L", y = "POC%", name = "")+
    theme_minimal(),
  ggplot(isere)+
    geom_point(aes(x = cmes_g.L*1000, y = poc_percent, col = name))+
        scale_color_viridis_d()+
      scale_x_continuous(trans = "log", breaks = c(10,100,1000,2000))+scale_y_continuous(trans = "log", breaks = c(1,2,4,8))+
        labs( x = "CMES, mg/L", y = "POC%", name = "")+
    theme_minimal(),
  ncol = 2, common.legend = T, legend = "bottom"
) %>%
  annotate_figure(top = text_grob("POC% et valeur associée de MES et CMES", face = "bold", size = 14))


```

On obtient l'incertitude sur les MES en réalisant une régression linéaire MES~CMES. L'incertitude **cmes_sd** sera utilisée pour les prédictions de **poc_percent** par Monte-Carlo. ????

```{r fit-mes-cmes}
## Uncertainty on MES
poc_isere$mes_g.L <- poc_isere$mes_mg.L / 1000
fit_cmes <- lm(cmes_g.L~mes_g.L, data = poc_isere)
summary(fit_cmes) %>% print()

cmes_sd <- summary(fit_cmes)$coefficients[4]
cat("Uncertainty on CMES = ", format(cmes_sd, scientific = T, digits = 3))
cmes_sigma <- sigma(fit_cmes)
cat("Uncertainty on CMES = ", format(cmes_sigma, scientific = T, digits = 3))

plot(fit_cmes)
hist(residuals(fit_cmes))

confint(fit_cmes)

ci_cmes <- predict(fit_cmes, poc_isere, interval = "confidence")

poc_isere$cmes_fitted <- ci_cmes[,"fit"]
poc_isere$cmes_ci_upr <- ci_cmes[,"upr"]
poc_isere$cmes_ci_lwr <- ci_cmes[,"lwr"]

pi_cmes <- predict(fit_cmes, poc_isere, interval = "prediction")

poc_isere$cmes_pi_upr <- pi_cmes[,"upr"]
poc_isere$cmes_pi_lwr <- pi_cmes[,"lwr"]

ggplot(poc_isere, aes( x= mes_g.L)) +
  geom_ribbon(aes(ymin =cmes_pi_lwr, ymax = cmes_pi_upr, fill = "prediction interval"), alpha = 0.5)+
  geom_ribbon(aes(ymin = cmes_ci_lwr, ymax = cmes_ci_upr, fill = "confidence interval"), alpha = 0.5)+
  geom_point(aes(y = cmes_g.L, col = "measured"))+
  geom_point(aes(y = cmes_fitted, col = "fitted"))+
  scale_color_manual(values = c("lightblue", "darkblue"))+
  scale_fill_manual(values = c("confidence interval" = "gray60", "prediction interval" = "gray80"))+
  labs(title = "CMES fitted vs CMES measured", col = "CMES", fill = "")+
  theme_minimal()
  
```


## Example of data - Carbonisere

Visualisation des données de la campagne Carbonisère: DOC et POC mesurés sur les années 2006-2007-2009. 

```{r view-fluxes}

ggplot(carbonisere)+
  geom_point(aes(x=as.Date(DateHeure), y = debit_m3.s), col = "cadetblue4")+
  geom_abline(slope = 0, intercept = mean(carbonisere$debit_m3.s, na.rm = T), col = "darkred")+
 annotate(geom = "label", label = round(mean(carbonisere$debit_m3.s, na.rm = T), 2), x= as.Date("2008-01-01"), y = 250)+
   scale_x_date(labels = function(x) format(x, "%d-%b-%y"), date_breaks = "1 year", date_minor_breaks = "1 month",name = "", limits = c(as.Date("2006-01-01"), as.Date("2008-03-31")))+ 
  labs(y = "Débit, m3/s")+
  theme_minimal(base_size = 15)

isere678 <- subset(isere, year == c(2006,2007,2008))

ggplot(isere678)+
  geom_point(aes(x=as.Date(DateHeure), y = q_m3.s), col = "cadetblue4", size = 1)+
  geom_abline(slope = 0, intercept = mean(isere678$q_m3.s, na.rm = T), col = "darkred")+
 annotate(geom = "label", label = round(mean(isere678$q_m3.s, na.rm = T), 2), x= as.Date("2006-01-01"), y = 200)+
   scale_x_date(labels = function(x) format(x, "%d-%b-%y"), date_breaks = "1 year", date_minor_breaks = "1 month",name = "", limits = c(as.Date("2006-01-01"), as.Date("2008-03-31")))+ 
  labs(y = "Débit, m3/s")+
  theme_minimal(base_size = 15)

ggplot(carbonisere)+
  geom_point(aes(x=as.Date(DateHeure), y = doc_mg.L), col = "darkolivegreen4")+
  geom_abline(slope = 0, intercept = mean(carbonisere$doc_mg.L, na.rm = T), col = "darkred")+
 annotate(geom = "label", label = round(mean(carbonisere$doc_mg.L, na.rm = T), 2), x= as.Date("2008-01-01"), y = 3)+
   scale_x_date(labels = function(x) format(x, "%d-%b-%y"), date_breaks = "1 year", date_minor_breaks = "1 month",name = "", limits = c(as.Date("2006-01-01"), as.Date("2008-03-31")))+ 
  labs(y = "Carbone Organique Dissous, mg/L")+
  theme_minimal(base_size = 15)


ggplot(carbonisere)+
  geom_point(aes(x=as.Date(DateHeure), y = poc_percent*mes_mg.L), col = "darkolivegreen4")+
 #  geom_abline(slope = 0, intercept = mean(carbonisere$poc_percent * carbonisere$mes_mg.L, na.rm = T), col = "darkred")+
 # annotate(geom = "label", label = round(mean(carbonisere$poc_percent * carbonisere$mes_mg.L, na.rm = T), 2), x= as.Date("2008-01-01"), y = 3)+
   scale_x_date(labels = function(x) format(x, "%d-%b-%y"), date_breaks = "1 year", date_minor_breaks = "1 month",name = "", limits = c(as.Date("2006-01-01"), as.Date("2008-03-31")))+ 
  labs(y = "Carbone Organique Particulaire, mg/L")+
  theme_minimal(base_size = 15)

```





# Fit MES-POC

Objectif: construire la relation MES-POC pour pouvoir reconstruire la chronique de POC à partir de la chronique de MES. Cette relation prend la forme de $POC\% = a*MES^b + c$.

```{r uncertainties}
q_u <- 0.05 # vérifier chiffre Isère
mes_u <- 0.05 # au pif
```


## Test : should we fit with distinct events ?

Que se passe-t-il si on n'effectue pas le fit avec tous les évènements mesurés ?

### Fit par série

Quelle est la différente de fit si on effectue le fit MES-POC sur chacun des évènements analysées (crue, chasse, suivi)?

```{r fit-by-event, eval = T, fig.dim = c(5,5)}
name_crues <- subset(poc_isere, !is.na(name) & name != "DOC 2011") %>% pull(name) %>% unique()
mes_for_fit <- poc_isere$mes_for_fit

for(i in name_crues){
  df <- poc_isere
  dfi <- subset(df, name == i &!is.na(poc_percent))
  
  dfi$aspt <- dfi[order(dfi$mes_for_fit, decreasing = T),] %>% pull(poc_percent) %>% head(dim(dfi)[1]/10) %>% median() # 10% of poc_percent corresponding to the max cmes
  
  a_i <- dfi$poc_percent %>% max()
  b_i <- - dfi$aspt[1]/2
    
  fiti <-  tryCatch(
    nls(poc_percent ~ a * mes_for_fit^b + aspt, data = dfi, start = list(a = a_i, b = b_i)),
    error = function(e) {lm(poc_percent ~ mes_for_fit, data = dfi)}
  )
  
  if(class(fiti)=="nls"){
    coef1 <- coef(fiti)[1]
    coef2 <- coef(fiti)[2]
    formula_fiti <- paste("NLS : POC =", format(coef1, scientific = T, digits = 3), "* MES (g/L) ^", round(coef2,3), "+", round(dfi$aspt[1],3))
  } else {
    coef1 <- coef(fiti)[1]
    coef2 <- coef(fiti)[2]
    formula_fiti <- paste("LM : POC =", format(coef2, scientific = T, digits = 3), "* MES (g/L) +", round(coef1))
 }

  df$poc_percent_fiti <- predict(fiti, newdata = df)
  
 g <- ggplot(subset(df, name ==i), aes(x = mes_for_fit))+
  geom_point(aes(y = poc_percent, col = "measured", shape = "measured"), size = 2)+
   geom_point(aes(y = poc_percent_fiti, col = "fitted only with this event", shape = "fitted only with this event"), size = 2)+
#  geom_point(aes(y = poc_nls_fitted, col = "fitted with all events", shape = "fitted with all events"), size = 2)+
  labs(title = i, x = "MES, mg.L", y = "POC, %", col = "", shape = "")+
  scale_color_manual(values = c("darkblue","lightblue"))+
  geom_abline(slope = 0, intercept = dfi$aspt[1], col = "darkred")+
  annotate(geom = "label", label = formula_fiti, x = Inf, y = Inf, hjust = 1.1, vjust = 1.1)+
  theme_minimal()+
  theme(legend.position = "bottom")
  
 print(g)
}

```

### All but one fit

```{r leave-one-out-event-to-fit-the-last, eval = T, fig.dim = c(5,5)}
name_crues <- subset(poc_isere, !is.na(name) & name != "DOC 2011") %>% pull(name) %>% unique()

for(i in name_crues){
  df <- poc_isere
  dfi <- subset(df, name != i &!is.na(poc_percent))
  
  dfi$aspt <- dfi[order(dfi$mes_mg.L, decreasing = T),] %>% pull(poc_percent) %>% head(dim(dfi)[1]/10) %>% median() # 10% of poc_percent corresponding to the max cmes
  
  a_i <- dfi$poc_percent %>% max()
  b_i <- - dfi$aspt[1]/2
    
  fiti <-  tryCatch(
    nls(poc_percent ~ a * mes_for_fit^b + aspt, data = dfi, start = list(a = a_i, b = b_i)),
    error = function(e) {lm(poc_percent ~ mes_for_fit, data = dfi)}
  )
  
  if(class(fiti)=="nls"){
    coef1 <- coef(fiti)[1]
    coef2 <- coef(fiti)[2]
    formula_fiti <- paste("NLS : POC =", format(coef1, scientific = T, digits = 2), "* MES (g/L) ^", round(coef2,2), "+", round(dfi$aspt[1],2))
  } else {
    coef1 <- coef(fiti)[1]
    coef2 <- coef(fiti)[2]
    formula_fiti <- paste("LM : POC =", format(coef2, scientific = T, digits = 2), "* MES (g/L) +", round(coef1))
 }

  df$poc_percent_fiti <- predict(fiti, newdata = df)
  
 g <- ggplot(subset(df, name == i), aes(x = mes_for_fit))+
  geom_point(aes(y = poc_percent, col = "measured", shape = "measured"))+
  geom_point(aes(y = poc_percent_fiti, col = "fitted with all events except this one", shape = "fitted with all events except this one"))+
  labs(title = i, x = "MES, g/L", y = "POC, %", col = "", shape = "")+
  scale_color_manual(values = c("darkblue","lightblue"))+
  geom_abline(slope = 0, intercept = dfi$aspt[1], col = "darkred")+
  annotate(geom = "label", label = formula_fiti, x = Inf, y = Inf, hjust = 1.1, vjust = 1.1)+
  theme_minimal()+
  theme(legend.position = "bottom")
  
 print(g)
}
```




## Powerlaw

On cherche à fitter le modèle $POC (prop) = a \* MES^{b} + aspt$. Deux fonctions R sont disponibles : *nls* et *gnls*. nls est robuste, mais gnls permet de choisir la structure de la variance. On sait que la variance diminue pour les hautes valeurs de MES (on tend vers l'asymptote). L'erreur dépend probablement de $y*\sigma^{2\delta}.

```{r asymptot}
# find asymptotic value : arbitrarily decide that it corresponds to the median of the 10% of poc_percent corresponding to the 10% of highest MES values.
aspt_value <- poc_isere[order(poc_isere$cmes_g.L, decreasing = T),] %>% pull(poc_percent) %>% head(dim(poc_isere)[1]/10) %>% mean() 
aspt_value_sd <- poc_isere[order(poc_isere$cmes_g.L, decreasing = T),] %>% pull(poc_percent) %>% head(dim(poc_isere)[1]/10) %>% sd() 

```

```{r constant-numbers}
n_boot <- 1000
n_obs <- nrow(poc_isere)
```


### NLS

#### Fit NLS model 

```{r fit-poc-mes-nls}
poc_isere$aspt <- aspt_value


#fit nls
pocfit <- nls(
  poc_percent ~ a * mes_for_fit^b + aspt,
  data = poc_isere,
  start = list(a = 1, b = -0.5)
)

# print summary
summary(pocfit) %>% print()

# paramètres de variance
sigma_nls <- summary(pocfit)$sigma

# predicted values (from original data)
poc_isere$poc_nls_fitted <- predict(pocfit, poc_isere)
poc_isere$poc_nls_resid <- residuals(pocfit)

# formula
formula_pocfit <- paste("NLS:", round(coef(pocfit)[1],3), "x MES ^", round(coef(pocfit)[2],3), "+", round(aspt_value, 3))

# model function 
f <- function(x, a, b, aspt){
  a * x ^ b + aspt
}

```


#### Confidence interval with wild bootstrap

```{r nls-wild-bootstrap}
coefs_wboot_nls <- matrix(NA, nrow = n_boot, ncol = 2, dimnames = list(NULL, c("a","b")))


for(i in seq_len(n_boot)){
  
  weights <- sample(c(-1,1), size = length(residuals(pocfit)), replace = T)
  resid_wboot <- residuals(pocfit) * weights
  
  y_wboot <- fitted(pocfit) + resid_wboot
  
  df_wboot <- poc_isere %>% mutate(poc_percent = y_wboot)
  
  tryCatch(
    {pocfit_wb <- nls(
      poc_percent~a*mes_for_fit^b+aspt,
      data = df_wboot,
      start = coef(pocfit))
    coefs_wboot_nls[i,] <- coef(pocfit_wb)}, 
    error = function(e) NULL) 
}

coefs_wboot_nls <- na.omit(coefs_wboot_nls)
apply(coefs_wboot_nls, 2, quantile, probs = c(0.025, 0.975)) %>% print() #ic coef 

coefs_wboot_nls <- cbind(coefs_wboot_nls, "aspt" = rnorm(length(coefs_wboot_nls)/2, mean = aspt_value, sd = aspt_value_sd))

ggplot(as.data.frame(coefs_wboot_nls))+
  geom_point(aes(x = a, y = b))+
  labs(title = "a and b coefficients with wild bootstrap", subtitle = paste(length(coefs_wboot_nls)/2, "iterations", sep = " "))+
  theme_minimal()+
  theme(legend.position = "none")


fitted_wboot_nls <- apply(coefs_wboot_nls, 1, function(p){p["a"] * mes_for_fit^p["b"] + p["aspt"]}) # les MC worlds sont en colonne

fitted_wboot_nls_ic <- apply(fitted_wboot_nls, 1, quantile,
                 probs = c(0.025, 0.5, 0.975), na.rm = TRUE)
fitted_wboot_nls_mean <- apply(fitted_wboot_nls, 1, mean)

poc_isere_wboot_nls <- poc_isere %>% mutate(poc_fitted = fitted_wboot_nls_mean, upr = fitted_wboot_nls_ic[3, ], lwr = fitted_wboot_nls_ic[1,])

ggplot(poc_isere_wboot_nls)+
  geom_point(aes(x=mes_for_fit, y = poc_percent, col = "measured", shape = "measured"))+ 
  geom_point(aes(x=mes_for_fit, y = poc_fitted, col = "fitted", shape = "fitted"))+ 
  geom_ribbon(aes(x = mes_for_fit, ymin = lwr, ymax = upr), fill = "gray80", alpha = 0.5)+
  geom_abline(slope = 0, intercept = aspt_value, col = "darkred")+
  annotate(geom = "label", label = formula_pocfit, x = Inf, y = Inf, hjust = 1.1, vjust = 1.1)+
  scale_color_manual(values = c("darkblue", "lightblue"))+
  labs(x = "MES, g/L", y = "POC, %", colour = "", shape = "", title = "POC% measured and fitted vs MES measured",subtitle = "Confidence interval in grey")+
  theme_minimal()

ggplot(poc_isere_wboot_nls, aes(x=poc_percent))+
  geom_point(aes(y=poc_fitted), col = "darkblue")+ 
  geom_errorbar(aes(ymin = lwr, ymax = upr), col = "gray60", alpha = 0.5)+
  geom_abline(slope = 1, intercept = 0, col = "darkred")+
  annotate(geom = "label", label = formula_pocfit, x = Inf, y = Inf, hjust = 1.1, vjust = 1.1)+
  labs(x = "POC measured", y = "POC fitted", colour = "", shape = "", title = "POC fitted vs measured",subtitle = "Confidence interval in grey")+
  theme_minimal()
```

#### NLS extention to Isère

```{r pred-isere-nls, cache.lazy = F}

# prepare dataframe
with(isere, sum(mes_for_fit == 0 | is.na(mes_for_fit), na.rm = T)) # 144 -> removed from df because model unstable with zero (when 0^(-b))

isere_for_nls <- isere %>% filter(mes_for_fit != 0 & !is.na(mes_for_fit))
isere_for_nls$aspt <- aspt_value # from nls fitting

nrow_boot <- nrow(coefs_wboot_nls) # number of bootstrap for the NLS coefficients

# predict POC pour mes > 0
isere_for_nls$poc_fitted <- predict(pocfit, newdata = isere_for_nls) 

# MES matrix
mes_mat_nls <- matrix(NA_real_, nrow = nrow_boot, ncol = nrow_isere)
mes_meas <- matrix(isere_for_nls$mes_for_fit, nrow = nrow_boot, ncol = nrow_isere, byrow = T) # repeats nrow_boot times the vector isere_for_gnls$q_m3.s
mes_noise <- matrix(rnorm(nrow_boot*nrow_isere, mean = 0, sd = mes_u), nrow = nrow_boot, ncol = nrow_isere) # 
mes_mat_nls <- mes_meas * (1 + mes_noise) # final value of q, with noise

# Prediction matrix, no noise
mu_nls <- f(mes_mat_nls, coefs_wboot_nls[,"a"], coefs_wboot_nls[,"b"], coefs_wboot_nls[,"aspt"])

# Prediction matrix, with noise
noise_mat_nls <- matrix(rnorm(nrow_boot*nrow_isere, mean = 0, sd = sigma_nls), nrow = nrow_boot, ncol = nrow_isere)

pred_nls <- mu_nls + noise_mat_nls

# Prediction interval 
pi <- t(apply(pred_nls, 2, quantile, probs = c(0.025, 0.975), na.rm = T))
colnames(pi) <- c("lower", "upper")

# Mean bootstrap value
boot_pred_nls <- colMeans(pred_nls, na.rm = T)

# insert in isere_for_nls
isere_for_nls <- isere_for_nls %>% mutate(poc_boot_pred = boot_pred_nls,
                          poc_pred_lower = pi[,1],
                          poc_pred_upper = pi[,2])

# variances 
isere_for_nls$poc_var_mean <- apply(mu_nls, 2, var) # variance of fit parameters + MES 
isere_for_nls$poc_var_tot <- apply(pred_nls, 2, var) # total variance per prediction, for prediction total uncertainty


# plot

ggplot(isere_for_nls, aes(x = mes_for_fit))+
  geom_line(aes(y = poc_pred_lower, ymax = poc_pred_upper), col = "gray60")+
  geom_line(aes(y = poc_pred_upper), col = "gray60")+
  geom_point(aes(y = poc_percent, col = "measured"), alpha = 0.5)+
  geom_point(aes(y = poc_fitted, col = "fitted with all events"), size = 2)+
  geom_point(aes(y = poc_boot_pred, col ="poc_boot_pred"), alpha = 0.5, size = 1)+
  scale_color_manual(values = c("darkblue","gray50","lightblue"))+
  geom_abline(slope = 0, intercept = aspt_value, col = "darkred")+
  annotate(geom = "label", label = formula_pocfit, x = Inf, y = Inf, hjust = 1.1, vjust = 1.1)+
  labs(x = "MES, g/L", y = "POC, %", colour = "", shape = "", title = "POC predicted from MES",subtitle = "Prediction interval in grey")+
  theme_minimal()+
  theme(legend.position = "bottom")

# Plot variance

ggplot(isere_for_nls, aes(x = mes_for_fit))+
  geom_line(aes(y = poc_var_mean, col = "model variance"))+
  geom_line(aes(y = poc_var_tot, col = "total variance (includes noise)"))+
  scale_color_manual(values = c("lightblue", "darkblue"))+
  scale_x_continuous(trans = "log", breaks = c(0.01,0.1,1,10,50))+
  labs(x = "MES, g/L", y = "variance")+
  theme_minimal()

```


### GNLS

#### Fit GNLS model 

```{r fit-poc-mes-gnls}
# fit gnls
pocfitg <- gnls(
  poc_percent ~ a*mes_for_fit^b + aspt,
  data = select(poc_isere, c(mes_for_fit, poc_percent, aspt)),
  start = coef(pocfit), # on utilise les valeurs de pocfit comme coefficients initiaux
  weights = varPower(value = 1, form = ~ fitted(.)),
  control = gnlsControl(nlsTol = 1e-3, tolerance = 1e-4)
)

# summary 
summary(pocfitg) %>% print()

# variance parameters
theta <- as.numeric(coef(pocfitg$modelStruct$varStruct, unconstrained = F))
sigma_gnls <- pocfitg$sigma

# formula
formula_pocfitg <- paste("GNLS:", round(coef(pocfitg)[1], 3), "x MES ^", round(coef(pocfitg)[2],3), "+", round(aspt_value, 3), sep = "")

## model function 
f <- function(x, a, b, aspt){
  a * x ^ b + aspt
}
```


#### GNLS bootstrap

```{r intervalles-de-confiance-bootstrap}

coefs_boot <- matrix(NA, nrow = n_boot, ncol = 2, dimnames = list(NULL, c("a","b")))
                     

for(i in seq_len(n_boot)){
  
  idx_boot <- sample(n_obs, replace = T)
  df_boot <- poc_isere[idx_boot, c("mes_for_fit","poc_percent","aspt")]
  
  tryCatch(
    {fit_init <- nls(
      poc_percent ~ a * mes_for_fit^b + aspt,
      data = df_boot,
      start = coef(pocfitg))
      # fit init is necessary to find the correct starting values for gnls. Otherwise, too much convergence result in extreme values in a and b

      pocfit_bg <- gnls(
      poc_percent~a*mes_for_fit^b+aspt,
      data = df_boot,
      start = coef(fit_init),
      weights = varPower(form = ~fitted(.)),
      control = gnlsControl(nlsTol = 1e-3, tolerance = 1e-4, maxIter = 200))
      
      coefs_boot[i,] <- coef(pocfit_bg)
      }, 
    error = function(e) NULL) 
}

# removes NA
coefs_boot <- na.omit(coefs_boot)
apply(coefs_boot, 2, quantile, probs = c(0.025, 0.975)) %>% knitr::kable() #ic coef
ggplot(as.data.frame(coefs_boot))+
  geom_point(aes(x = a, y = b))+
  theme_minimal()+
  theme(legend.position = "none")

# adds uncertainty around aspt
coefs_boot <- cbind(coefs_boot, "aspt" = rnorm(length(coefs_boot)/2, mean = aspt_value, sd = aspt_value_sd))

# compute POC
fitted_boot <- apply(coefs_boot, 1, function(p){p["a"] * poc_isere$mes_for_fit^p["b"] + p["aspt"]}) # MC worlds in columns
fitted_boot_ic <- apply(fitted_boot, 1, quantile, 
                 probs = c(0.025, 0.5, 0.975), na.rm = TRUE) # prediction intervals
fitted_boot_mean <- apply(fitted_boot, 1, mean) # meet bottstrapped valur

# intergrates in poc_isere
poc_isere_boot_gnls <- poc_isere %>% mutate(poc_fitted = fitted_boot_mean, upr = fitted_boot_ic[3, ], lwr = fitted_boot_ic[1,])

ggplot(poc_isere_boot_gnls)+
  geom_point(aes(x=mes_for_fit, y = poc_percent, col = "measured", shape = "measured"))+ 
  geom_point(aes(x=mes_for_fit, y = poc_fitted, col = "fitted", shape = "fitted"))+ 
  geom_ribbon(aes(x = mes_for_fit, ymin = lwr, ymax = upr), fill = "gray80", alpha = 0.5)+
  geom_abline(slope = 0, intercept = aspt_value, col = "darkred")+
  annotate(geom = "label", label = formula_pocfitg, x = Inf, y = Inf, hjust = 1.1, vjust = 1.1)+
  scale_color_manual(values = c("darkblue", "lightblue"))+
  labs(x = "MES, mg/L", y = "POC, %", colour = "", shape = "", title = "POC% measured and fitted vs MES measured",subtitle = "Confidence interval in grey")+
  theme_minimal()

ggplot(poc_isere_boot_gnls, aes(x=poc_percent))+
  geom_point(aes(y=poc_fitted), col = "darkblue")+ 
  geom_errorbar(aes(ymin = lwr, ymax = upr), fill = "gray80", alpha = 0.5)+
  geom_abline(slope = 1, intercept = 0, col = "darkred")+
  annotate(geom = "label", label = formula_pocfitg, x = Inf, y = Inf, hjust = 1.1, vjust = 1.1)+
  labs(x = "POC measured", y = "POC fitted", colour = "", shape = "", title = "POC fitted vs measured",subtitle = "Confidence interval in grey")+
  theme_minimal()
```


#### GNLS extension to Isere

```{r pred-isere-gnls, cache.lazy = F}

# prepare df 
with(isere, sum(mes_for_fit == 0 | is.na(mes_for_fit), na.rm = T)) # 144 -> removed from df because model unstable with zero (when 0^(-b))

isere_for_gnls <- isere %>% filter(mes_for_fit != 0 & !is.na(mes_for_fit))
isere_for_gnls$aspt <- aspt_value

nrow_boot <- nrow(coefs_boot) # number of bootstrap for the GNLS coefficients

# predict POC pour mes > 0
isere_for_gnls$poc_fitted <- predict(pocfitg, newdata = isere_for_gnls, na.action = na.pass) 

# get mes_mat from earlier
mes_mat_gnls <- mes_mat_nls

# Prediction matrix, no noise
mu_gnls <- f(mes_mat_gnls, coefs_boot[,"a"], coefs_boot[,"b"], coefs_boot[,"aspt"])

# Prediction matrix, with noise
noise_mat_gnls <- matrix(NA_real_, nrow = nrow_boot, ncol = nrow_isere)
sigma_mat_gnls <- sigma_gnls * abs(mu_gnls)^theta # variance depends on predicted value

noise_mat_gnls <- matrix(rnorm(nrow_boot*nrow_isere, mean = 0, sd = 1), nrow = nrow_boot, ncol = nrow_isere)
noise_mat_gnls <- noise_mat_gnls*sigma_mat_gnls

pred_gnls <- mu_gnls + noise_mat_gnls
pred_gnls <- pmin(pmax(pred_gnls, 0), 100) # clampe pred_nls pour éviter les intervalles de prédiction en dessous de zéro et au dessus de 100 (no case)

# Prediction interval 
pi <- t(apply(pred_gnls, 2, quantile, probs = c(0.025, 0.975), na.rm = T))
colnames(pi) <- c("lower", "upper")

# Mean bootstrap value
boot_pred_gnls <- colMeans(pred_gnls, na.rm = T)

## insert in isere_for_gnls
isere_for_gnls <- isere_for_gnls %>% mutate(poc_boot_pred = boot_pred_gnls,
                          poc_pred_lower = pi[,1],
                          poc_pred_upper = pi[,2])

# variances
isere_for_gnls$poc_var_mean <- apply(mu_nls, 2, var) # variance of fit parameters + MES 
isere_for_gnls$poc_var_tot <- apply(pred_nls, 2, var) # total variance per prediction, for prediction total uncertainty

# plot
ggplot(isere_for_gnls, aes(x = mes_for_fit))+
  geom_line(aes(y = poc_pred_lower, ymax = poc_pred_upper), col = "black")+
  geom_line(aes(y = poc_pred_upper), col = "black")+
  geom_point(aes(y = poc_percent, col = "measured"), alpha = 0.5, size = 0.5)+
  geom_point(aes(y = poc_fitted, col = "fitted with all events"), size = 2)+
  geom_point(aes(y = poc_boot_pred, col ="poc_boot_pred"), alpha = 0.5, size = 1)+
  scale_color_manual(values = c("darkblue","gray50","lightblue"))+
  geom_abline(slope = 0, intercept = aspt_value, col = "darkred")+
  annotate(geom = "label", label = formula_pocfitg, x = Inf, y = Inf, hjust = 1.1, vjust = 1.1)+
  labs(x = "MES, mg/L", y = "POC, %", colour = "", shape = "", title = "POC predicted from MES",subtitle = "Prediction interval in grey")+
  theme_minimal()+
  theme(legend.position = "bottom")

# plot variance
ggplot(isere_for_gnls, aes(x = mes_for_fit))+
  geom_line(aes(y = poc_var_mean, col = "model variance"))+
  geom_line(aes(y = poc_var_tot, col = "total variance (includes noise)"))+
  scale_color_manual(values = c("lightblue", "darkblue"))+
  scale_x_continuous(trans = "log", breaks = c(0.01,0.1,1,10,50))+
  labs(x = "MES, g/L", y = "variance")+
  theme_minimal()
    
```


### Comparison NLS / GNLS 

```{r comparaison-nls-gnls}

par(mfrow = c(1, 2))

# nls : les résidus montrent un pattern en éventail
plot(fitted(pocfit), residuals(pocfit),
     main = "Résidus nls (non pondérés)",
     xlab = "Fitted", ylab = "Résidus")
abline(h = 0, col = "red")

# gnls : les résidus normalisés sont homoscédastiques
plot(fitted(pocfitg), residuals(pocfitg, type = "normalized"),
     main = "Résidus gnls (normalisés)",
     xlab = "Fitted", ylab = "Résidus normalisés")
abline(h = 0, col = "red")

```

# Reference annual and interannual fluxes

## Annual flux based on gnls model + Monte Carlo


```{r annual-flux-reference, cache.lazy=F}
# create matrix of q
q_meas <- matrix(isere_for_gnls$q_m3.s, nrow = nrow_boot, ncol = nrow_isere, byrow = T) # repeats nrow_boot times the vector isere_for_gnls$q_m3.s
q_noise <- matrix(rnorm(nrow_boot*nrow_isere, mean = 0, sd = q_u), nrow = nrow_boot, ncol = nrow_isere) # creates a noise in percent (proportion), between 0 and 10%
q_mat <- q_meas * (1 + q_noise) # final value of q, with noise


# matrix of period (no uncertainty,tge same repeated nrow_boot times)
period_mat <- matrix(isere_for_gnls$period, nrow = nrow_boot, ncol = nrow_isere, byrow = T)

# Instant flux matrix
flux_kg.s_mat <- pred_gnls*mes_mat_gnls*1e-6*q_mat*1e-2*period_mat #pred_gnls * mes_mat : poc in g/L converted to ton/L; q_mat converted from m3/s to L/s. We consider no uncertainty on period. 

# Get index for the columns corresponding to the same year
index_years <- sapply(unique(isere_for_gnls$year), function(y){which(isere_for_gnls$year == y)}) # list of indices corresponding to each year

# Annual flux
annual_flux_ton.y <- sapply(index_years, function(idx){apply(flux_kg.s_mat[,idx], 1, sum, na.rm = T)}) # sum of fluxes per year, for each iteration of the bootstrap. Result is a matrix with nrow_boot rows and 19 columns (1 per year)
annual_flux_pi <- apply(annual_flux_ton.y, 2, quantile, probs = c(0.025, 0.5, 0.975), na.rm = T) # prediction interval for annual fluxes, per year. 3 lignes, 19 columns
annual_flux_mean <- colMeans(annual_flux_ton.y, na.rm = T) # mean annual flux per year. 1 vector
annual_flux_sd <- apply(annual_flux_ton.y, 2, sd, na.rm = T) # standard deviation of annual flux per year. Is just an estimate of goodness of mean, not as good as than the confidence interval. 

# Merge in df
annual_flux_df <- data.frame(year = unique(isere_for_gnls$year), 
                        annual_flux_mean = annual_flux_mean, 
                        annual_flux_variability = annual_flux_sd, 
                        annual_flux_pi_lower = annual_flux_pi[1,], 
                        annual_flux_pi_upper = annual_flux_pi[3,])
# Plot
ggplot(annual_flux_df)+
  geom_col(aes(x=year, y = annual_flux_mean), fill = "lightblue")+
  geom_errorbar(aes(x = year, ymin = annual_flux_pi_lower, ymax = annual_flux_pi_upper), width = 0.2)+
  labs(title = "Mean annual flux with prediction interval", x = "", y = "Mean annual flux, ton")+
  theme_minimal()
```

## Interannual flux

```{r interannual-flux-reference}
interannual_flux_ton.y <- rowMeans(annual_flux_ton.y, na.rm = T) # mean interannual flux per iteration of the bootstrap
interannual_flux_pi <- quantile(interannual_flux_ton.y, probs = c(0.025, 0.5, 0.975), na.rm = T) # prediction interval
interannual_flux_mean <- mean(interannual_flux_ton.y, na.rm = T) # mean interannual flux
interannual_flux_variability <- sd(annual_flux_mean, na.rm = T) # standard deviation of interannual flux per year

interannual_flux_df <- data.frame(year = "interannual", annual_flux_mean = interannual_flux_mean, 
                                  annual_flux_variability = interannual_flux_variability,
                        annual_flux_pi_lower = interannual_flux_pi[1], 
                        annual_flux_pi_upper = interannual_flux_pi[3])

total_flux_df <- rbind(annual_flux_df, interannual_flux_df)
total_flux_df$group <- c(rep("annual", length(unique(isere_for_gnls$year))), "interannual")

ggplot(total_flux_df)+
  geom_col(aes(x=year, y = annual_flux_mean, fill = group))+
    geom_errorbar(aes(x = year, ymin = annual_flux_pi_lower, ymax = annual_flux_pi_upper, col = "prediction interval"), width = 0.3, size = 0.8)+
  geom_errorbar(aes(x = year, ymin = annual_flux_mean - annual_flux_variability, ymax = annual_flux_mean + annual_flux_variability, col = "variability"), width = 0.2, size = 0.8, linetype = 2)+
  scale_fill_manual(values = c("annual" = "lightblue", "interannual" = "indianred"))+
  scale_color_manual(values = c("prediction interval" = "darkblue", "variability" = "darkred"), name = "")+
   labs(x = "Year", y = "Flux (kg/year)", fill = "")+
  theme_minimal()+
  theme(axis.text.x = element_text(angle = 45, hjust = 1), legend.position = "bottom")
```

# Time steps

```{r common-data}
isere_time <- isere %>% filter(mes_for_fit != 0 & !is.na(mes_for_fit))

mes_u <- 0.05
q_u <- 0.05

set.seed(2502)
```


Random CMES over timer period: mean Q, then GNLS. 

## Day 

```{r pred-isere-gnls-day, cache.lazy = F}
# prepare df
isere_group_day <- isere_time %>% mutate("day" = format(DateHeure, "%Y-%m-%d"), year = year(DateHeure), DateHeure = NULL) %>% group_by(day,year) # group isere_time by day
nrow_day <- n_groups(isere_group_day)

# get mean q
q_day <- isere_group_day %>% select(c("day", "q_m3.s")) %>% summarize_all(list("q_mean" = mean, "q_sd" = sd)) %>% ungroup() # mean of Q for each day


# creates matrix for MES
isere_mes_day <- isere_group_day %>% select(c("day", "mes_for_fit")) %>% summarize("list_mes" = list(mes_for_fit)) %>% ungroup() # creates a list of mes for each day
mes_day_random <- replicate(nrow_boot, sapply(isere_mes_day$list_mes, function(x) sample(x,1)))%>% t() # matrix of mes: one random sample per day, replicated 1000 times
mes_day_noise <- matrix(rnorm(nrow_boot*nrow_day, mean = 0, sd = mes_u), nrow = nrow_boot, ncol = nrow_day) 
mes_mat_day <- mes_day_random * (1 + mes_day_noise) # final value of mes, with noise

mes_mean <- colMeans(mes_mat_day)

# Prediction matrix
mu_day <- f(mes_mat_day, coefs_boot[,"a"], coefs_boot[,"b"], coefs_boot[,"aspt"])


# Prediction matrix, with noise
noise_mat_day <- matrix(NA_real_, nrow = nrow_boot, ncol = nrow_isere)
sigma_mat_day <- sigma_gnls * abs(mu_day)^theta

noise_mat_day <- matrix(rnorm(nrow_boot*nrow_day, mean = 0, sd = 1), nrow = nrow_boot, ncol = nrow_day)
noise_mat_day <- noise_mat_day*sigma_mat_day

pred_day <- mu_day + noise_mat_day
pred_day <- pmin(pmax(pred_day, 0), 100) # clampe pred_nls pour éviter les intervalles de prédiction en dessous de zéro


## computes prediction interval 
pi_day <- t(
  apply(pred_day, 2, quantile, probs = c(0.025, 0.975), na.rm = T)
)

colnames(pi_day) <- c("lower", "upper")

boot_pred_day <- colMeans(pred_day, na.rm = T)

## insert in isere_day
isere_day <- q_day %>% mutate(
                          mes_for_fit = mes_mean, # keep name for "fitting model"predict" function
                          poc_boot_pred = boot_pred_day,
                          poc_pred_lower = pi_day[,"lower"],
                          poc_pred_upper = pi_day[,"upper"],
                          aspt = aspt_value)

isere_day$poc_fitted <- predict(pocfitg, isere_day)

# variance 
isere_day$poc_var_mean <- apply(mu_day, 2, var) # variance of fit parameters + MES 
isere_day$poc_var_tot <- apply(pred_day, 2, var) # total variance per prediction, for prediction total uncertainty


# plot

ggplot(isere_day, aes(x = mes_for_fit))+
  geom_line(aes(y = poc_pred_lower, ymax = poc_pred_upper), col = "black")+
  geom_line(aes(y = poc_pred_upper), col = "black")+
  geom_point(aes(y = poc_fitted, col = "fitted with all events"), size = 2)+
  geom_point(aes(y = poc_boot_pred, col ="poc_boot_pred"), alpha = 0.5, size = 0.5)+
  labs(x = "MES, mg.L", y = "POC, %", col = "")+
  scale_color_manual(values = c("darkblue","gray50","lightblue"))+
  geom_abline(slope = 0, intercept = aspt_value, col = "darkred")+
  annotate(geom = "label", label = formula_pocfitg, x = Inf, y = Inf, hjust = 1.1, vjust = 1.1)+
  labs(x = "MES, mg/L", y = "POC,prop", colour = "", shape = "", title = "POC predicted from MES",subtitle = "Prediction interval in grey")+
  theme_minimal()+
  theme(legend.position = "bottom")

# plot, log-transformed x
ggplot(isere_day, aes(x = mes_for_fit))+
  geom_line(aes(y = poc_pred_lower, ymax = poc_pred_upper), col = "black")+
  geom_line(aes(y = poc_pred_upper), col = "black")+
  geom_point(aes(y = poc_fitted, col = "fitted with all events"), size = 2)+
  geom_point(aes(y = poc_boot_pred, col ="poc_boot_pred"), alpha = 0.5, size = 0.5)+
  labs(x = "MES, mg.L", y = "POC, %", col = "")+
  scale_color_manual(values = c("darkblue","gray50","lightblue"))+
  scale_x_continuous(trans = "log", breaks = c(1,10,100,1000))+
  geom_abline(slope = 0, intercept = aspt_value, col = "darkred")+
  annotate(geom = "label", label = formula_pocfitg, x = Inf, y = Inf, hjust = 1.1, vjust = 1.1)+
  labs(x = "MES, mg/L", y = "POC, %", colour = "", shape = "", title = "POC predicted from MES",subtitle = "Prediction interval in grey")+
  theme_minimal()+
  theme(legend.position = "bottom")
```

```{r annual-flux-day, cache.lazy=F}

# creates matrix for Q

q_day_mean <-  matrix(q_day$q_mean, nrow = nrow_boot, ncol = nrow_day, byrow = T)
q_noise <- matrix(rnorm(nrow_boot*nrow_day, mean = 0, sd = q_u), nrow = nrow_boot, ncol = nrow_day) # creates a noise in percent (proportion), between 0 and 10%
q_mat_day <- q_day_mean * (1 + q_noise) # final MC of q, with noise. SD NOT INCLUDED: will not always be available


# compute flux
flux_kg.s_mat_day <- pred_day*mes_mat_day*1e-6*q_mat_day*1e-2*60*60*24 #pred_day * mes_mat : poc in mg/L converted to ton; q_mat converted from m3/s to L/s. Period : nb of seconds in 1 day. 

# Get index for columns by year
index_years <- sapply(unique(isere_day$year), function(y){which(isere_day$year == y)}) # list of indices corresponding to each year

# annual flux
annual_flux_ton.y_day <- sapply(index_years, function(idx){apply(flux_kg.s_mat_day[,idx], 1, sum, na.rm = T)}) # sum of fluxes per year, for each iteration of the bootstrap. Result is a matrix with nrow_boot rows and 19 columns (1 per year)

annual_flux_day_pi <- apply(annual_flux_ton.y_day, 2, quantile, probs = c(0.025, 0.5, 0.975), na.rm = T) # confidence interval for annual fluxes, per year. 3 lignes, 19 columns
annual_flux_day_mean <- colMeans(annual_flux_ton.y_day, na.rm = T) # mean annual flux per year. 1 vector

annual_flux_day_sd <- apply(annual_flux_ton.y_day, 2, sd, na.rm = T) # standard deviation of annual flux per year. Is just an estimate of goodness of mean, not as good as than the confidence interval. 
 

annual_flux_day_df <- data.frame(year = unique(isere_day$year), 
                        annual_flux_mean = annual_flux_day_mean, 
                        annual_flux_variability = annual_flux_day_sd, 
                        annual_flux_pi_lower = annual_flux_day_pi[1,], 
                        annual_flux_pi_upper = annual_flux_day_pi[3,])

ggplot(annual_flux_day_df)+
  geom_col(aes(x=year, y = annual_flux_day_mean), fill = "lightblue")+
  geom_errorbar(aes(x = year, ymin = annual_flux_pi_lower, ymax = annual_flux_pi_upper), width = 0.2)+
  labs(title = "Mean annual flux with prediction interval", subtitle = "Sampling grequency: day", x = "", y = "Mean annual flux, ton")+
  theme_minimal()

interannual_flux_ton.y_day <- rowMeans(annual_flux_ton.y_day, na.rm = T) # mean interannual flux per iteration of the bootstrap
interannual_flux_pi_day <- quantile(interannual_flux_ton.y_day, probs = c(0.025, 0.5, 0.975), na.rm = T) # prediction interval
interannual_flux_mean_day <- mean(interannual_flux_ton.y_day, na.rm = T) # mean interannual flux
interannual_flux_variability_day <- sd(annual_flux_day_mean, na.rm = T) # standard deviation of interannual flux per year

interannual_flux_day_df <- data.frame(year = "interannual", annual_flux_mean = interannual_flux_mean_day, 
                                  annual_flux_variability = interannual_flux_variability_day,
                        annual_flux_pi_lower = interannual_flux_pi_day[1], 
                        annual_flux_pi_upper = interannual_flux_pi_day[3])

total_flux_day_df <- rbind(annual_flux_day_df, interannual_flux_day_df)
total_flux_day_df$group <- c(rep("annual", length(unique(isere_day$year))), "interannual")

ggplot(total_flux_day_df)+
  geom_col(aes(x=year, y = annual_flux_mean, fill = group))+
    geom_errorbar(aes(x = year, ymin = annual_flux_pi_lower, ymax = annual_flux_pi_upper, col = "prediction interval"), width = 0.3, size = 0.8)+
  geom_errorbar(aes(x = year, ymin = annual_flux_mean - annual_flux_variability, ymax = annual_flux_mean + annual_flux_variability, col = "interannual variability"), width = 0.2, size = 0.8, linetype = 2)+
  scale_fill_manual(values = c("annual" = "lightblue", "interannual" = "indianred"))+
  scale_color_manual(values = c("prediction interval" = "darkblue", "interannual variability" = "darkred"), name = "")+
   labs(x = "Year", y = "Flux, from dayly mean values (ton/year)", fill = "")+
  theme_minimal()+
  theme(axis.text.x = element_text(angle = 45, hjust = 1), legend.position = "bottom")
```

## Week

```{r pred-isere-gnls-week, cache.lazy = F}
# prepare df
isere_group_week <- isere_time %>% mutate("week" = week(DateHeure), year = year(DateHeure), DateHeure = NULL) %>% group_by(week,year) # group isere_time by week
nrow_week <- n_groups(isere_group_week)

# get mean q
q_week <- isere_group_week %>% select(c("week", "q_m3.s")) %>% summarize_all(list("q_mean" = mean, "q_sd" = sd)) %>% ungroup() # mean of Q for each week


# creates matrix for MES
isere_mes_week <- isere_group_week %>% select(c("week", "mes_for_fit")) %>% summarize("list_mes" = list(mes_for_fit)) %>% ungroup() # creates a list of mes for each week
mes_week_random <- replicate(nrow_boot, sapply(isere_mes_week$list_mes, function(x) sample(x,1)))%>% t() # matrix of mes: one random sample per week, replicated 1000 times
mes_week_noise <- matrix(rnorm(nrow_boot*nrow_week, mean = 0, sd = mes_u), nrow = nrow_boot, ncol = nrow_week) 
mes_mat_week <- mes_week_random * (1 + mes_week_noise) # final value of mes, with noise

mes_mean <- colMeans(mes_mat_week)

# Prediction matrix
mu_week <- f(mes_mat_week, coefs_boot[,"a"], coefs_boot[,"b"], coefs_boot[,"aspt"])


# Prediction matrix, with noise
noise_mat_week <- matrix(NA_real_, nrow = nrow_boot, ncol = nrow_isere)
sigma_mat_week <- sigma_gnls * abs(mu_week)^theta

noise_mat_week <- matrix(rnorm(nrow_boot*nrow_week, mean = 0, sd = 1), nrow = nrow_boot, ncol = nrow_week)
noise_mat_week <- noise_mat_week*sigma_mat_week

pred_week <- mu_week + noise_mat_week
pred_week <- pmin(pmax(pred_week, 0), 100) # clampe pred_nls pour éviter les intervalles de prédiction en dessous de zéro


## computes prediction interval 
pi_week <- t(
  apply(pred_week, 2, quantile, probs = c(0.025, 0.975), na.rm = T)
)

colnames(pi_week) <- c("lower", "upper")

boot_pred_week <- colMeans(pred_week, na.rm = T)

## insert in isere_week
isere_week <-q_week %>% mutate(
                          mes_for_fit = mes_mean, # keep name for "fitting model"predict" function
                          poc_boot_pred = boot_pred_week,
                          poc_pred_lower = pi_week[,"lower"],
                          poc_pred_upper = pi_week[,"upper"],
                          aspt = aspt_value)

isere_week$poc_fitted <- predict(pocfitg, isere_week)

# variance 
isere_week$poc_var_mean <- apply(mu_week, 2, var) # variance of fit parameters + MES 
isere_week$poc_var_tot <- apply(pred_week, 2, var) # total variance per prediction, for prediction total uncertainty


# plot

ggplot(isere_week, aes(x = mes_for_fit))+
  geom_line(aes(y = poc_pred_lower, ymax = poc_pred_upper), col = "black")+
  geom_line(aes(y = poc_pred_upper), col = "black")+
  geom_point(aes(y = poc_fitted, col = "fitted with all events"), size = 2)+
  geom_point(aes(y = poc_boot_pred, col ="poc_boot_pred"), alpha = 0.5, size = 0.5)+
  labs(x = "MES, mg.L", y = "POC, %", col = "")+
  scale_color_manual(values = c("darkblue","gray50","lightblue"))+
  geom_abline(slope = 0, intercept = aspt_value, col = "darkred")+
  annotate(geom = "label", label = formula_pocfitg, x = Inf, y = Inf, hjust = 1.1, vjust = 1.1)+
  labs(x = "MES, mg/L", y = "POC,prop", colour = "", shape = "", title = "POC predicted from MES",subtitle = "Prediction interval in grey")+
  theme_minimal()+
  theme(legend.position = "bottom")

# plot, log-transformed x
ggplot(isere_week, aes(x = mes_for_fit))+
  geom_line(aes(y = poc_pred_lower, ymax = poc_pred_upper), col = "black")+
  geom_line(aes(y = poc_pred_upper), col = "black")+
  geom_point(aes(y = poc_fitted, col = "fitted with all events"), size = 2)+
  geom_point(aes(y = poc_boot_pred, col ="poc_boot_pred"), alpha = 0.5, size = 0.5)+
  labs(x = "MES, mg.L", y = "POC, %", col = "")+
  scale_color_manual(values = c("darkblue","gray50","lightblue"))+
  scale_x_continuous(trans = "log", breaks = c(1,10,100,1000))+
  geom_abline(slope = 0, intercept = aspt_value, col = "darkred")+
  annotate(geom = "label", label = formula_pocfitg, x = Inf, y = Inf, hjust = 1.1, vjust = 1.1)+
  labs(x = "MES, mg/L", y = "POC, %", colour = "", shape = "", title = "POC predicted from MES",subtitle = "Prediction interval in grey")+
  theme_minimal()+
  theme(legend.position = "bottom")
```

```{r annual-flux-week, cache.lazy=F}

# creates matrix for Q

q_week_mean <-  matrix(q_week$q_mean, nrow = nrow_boot, ncol = nrow_week, byrow = T)
q_noise <- matrix(rnorm(nrow_boot*nrow_week, mean = 0, sd = q_u), nrow = nrow_boot, ncol = nrow_week) # creates a noise in percent (proportion), between 0 and 10%
q_mat_week <- q_week_mean * (1 + q_noise) # final MC of q, with noise. SD NOT INCLUDED: will not always be available


# compute flux
flux_kg.s_mat_week <- pred_week*mes_mat_week*1e-6*q_mat_week*1e-2*60*60*24*7 #pred_week * mes_mat : poc in mg/L converted to ton; q_mat converted from m3/s to L/s. Period : nb of seconds in 1 week. 

# Get index for columns by year
index_years <- sapply(unique(isere_week$year), function(y){which(isere_week$year == y)}) # list of indices corresponding to each year

# annual flux
annual_flux_ton.y_week <- sapply(index_years, function(idx){apply(flux_kg.s_mat_week[,idx], 1, sum, na.rm = T)}) # sum of fluxes per year, for each iteration of the bootstrap. Result is a matrix with nrow_boot rows and 19 columns (1 per year)

annual_flux_week_pi <- apply(annual_flux_ton.y_week, 2, quantile, probs = c(0.025, 0.5, 0.975), na.rm = T) # confidence interval for annual fluxes, per year. 3 lignes, 19 columns
annual_flux_week_mean <- colMeans(annual_flux_ton.y_week, na.rm = T) # mean annual flux per year. 1 vector

annual_flux_week_sd <- apply(annual_flux_ton.y_week, 2, sd, na.rm = T) # standard deviation of annual flux per year. Is just an estimate of goodness of mean, not as good as than the confidence interval. 
 

annual_flux_week_df <- data.frame(year = unique(isere_week$year), 
                        annual_flux_mean = annual_flux_week_mean, 
                        annual_flux_variability = annual_flux_week_sd, 
                        annual_flux_pi_lower = annual_flux_week_pi[1,], 
                        annual_flux_pi_upper = annual_flux_week_pi[3,])

ggplot(annual_flux_week_df)+
  geom_col(aes(x=year, y = annual_flux_week_mean), fill = "lightblue")+
  geom_errorbar(aes(x = year, ymin = annual_flux_pi_lower, ymax = annual_flux_pi_upper), width = 0.2)+
  labs(title = "Mean annual flux with prediction interval", subtitle = "Sampling grequency: week", x = "", y = "Mean annual flux, ton")+
  theme_minimal()

interannual_flux_ton.y_week <- rowMeans(annual_flux_ton.y_week, na.rm = T) # mean interannual flux per iteration of the bootstrap
interannual_flux_pi_week <- quantile(interannual_flux_ton.y_week, probs = c(0.025, 0.5, 0.975), na.rm = T) # prediction interval
interannual_flux_mean_week <- mean(interannual_flux_ton.y_week, na.rm = T) # mean interannual flux
interannual_flux_variability_week <- sd(annual_flux_week_mean, na.rm = T) # standard deviation of interannual flux per year

interannual_flux_week_df <- data.frame(year = "interannual", annual_flux_mean = interannual_flux_mean_week, 
                                  annual_flux_variability = interannual_flux_variability_week,
                        annual_flux_pi_lower = interannual_flux_pi_week[1], 
                        annual_flux_pi_upper = interannual_flux_pi_week[3])

total_flux_week_df <- rbind(annual_flux_week_df, interannual_flux_week_df)
total_flux_week_df$group <- c(rep("annual", length(unique(isere_week$year))), "interannual")

ggplot(total_flux_week_df)+
  geom_col(aes(x=year, y = annual_flux_mean, fill = group))+
    geom_errorbar(aes(x = year, ymin = annual_flux_pi_lower, ymax = annual_flux_pi_upper, col = "prediction interval"), width = 0.3, size = 0.8)+
  geom_errorbar(aes(x = year, ymin = annual_flux_mean - annual_flux_variability, ymax = annual_flux_mean + annual_flux_variability, col = "interannual variability"), width = 0.2, size = 0.8, linetype = 2)+
  scale_fill_manual(values = c("annual" = "lightblue", "interannual" = "indianred"))+
  scale_color_manual(values = c("prediction interval" = "darkblue", "interannual variability" = "darkred"), name = "")+
   labs(x = "Year", y = "Flux, from weekly mean values (ton/year)", fill = "")+
  theme_minimal()+
  theme(axis.text.x = element_text(angle = 45, hjust = 1), legend.position = "bottom")
```


## Month

```{r pred-isere-gnls-month, cache.lazy = F}
# prepare df
isere_group_month <- isere_time %>% mutate("month" = month(DateHeure), year = year(DateHeure), DateHeure = NULL) %>% group_by(month,year) # group isere_time by month
nrow_month <- n_groups(isere_group_month)

# get mean q
q_month <- isere_group_month %>% select(c("month", "q_m3.s")) %>% summarize_all(list("q_mean" = mean, "q_sd" = sd)) %>% ungroup() # mean of Q for each month


# creates matrix for MES
isere_mes_month <- isere_group_month %>% select(c("month", "mes_for_fit")) %>% summarize("list_mes" = list(mes_for_fit)) %>% ungroup() # creates a list of mes for each month
mes_month_random <- replicate(nrow_boot, sapply(isere_mes_month$list_mes, function(x) sample(x,1)))%>% t() # matrix of mes: one random sample per month, replicated 1000 times
mes_month_noise <- matrix(rnorm(nrow_boot*nrow_month, mean = 0, sd = mes_u), nrow = nrow_boot, ncol = nrow_month) 
mes_mat_month <- mes_month_random * (1 + mes_month_noise) # final value of mes, with noise

mes_mean <- colMeans(mes_mat_month)

# Prediction matrix
mu_month <- f(mes_mat_month, coefs_boot[,"a"], coefs_boot[,"b"], coefs_boot[,"aspt"])


# Prediction matrix, with noise
noise_mat_month <- matrix(NA_real_, nrow = nrow_boot, ncol = nrow_isere)
sigma_mat_month <- sigma_gnls * abs(mu_month)^theta

noise_mat_month <- matrix(rnorm(nrow_boot*nrow_month, mean = 0, sd = 1), nrow = nrow_boot, ncol = nrow_month)
noise_mat_month <- noise_mat_month*sigma_mat_month

pred_month <- mu_month + noise_mat_month
pred_month <- pmin(pmax(pred_month, 0), 100) # clampe pred_nls pour éviter les intervalles de prédiction en dessous de zéro


## computes prediction interval 
pi_month <- t(
  apply(pred_month, 2, quantile, probs = c(0.025, 0.975), na.rm = T)
)

colnames(pi_month) <- c("lower", "upper")

boot_pred_month <- colMeans(pred_month, na.rm = T)

## insert in isere_month
isere_month <-q_month %>% mutate(
                          mes_for_fit = mes_mean, # keep name for "fitting model"predict" function
                          poc_boot_pred = boot_pred_month,
                          poc_pred_lower = pi_month[,"lower"],
                          poc_pred_upper = pi_month[,"upper"],
                          aspt = aspt_value)

isere_month$poc_fitted <- predict(pocfitg, isere_month)

# variance 
isere_month$poc_var_mean <- apply(mu_month, 2, var) # variance of fit parameters + MES 
isere_month$poc_var_tot <- apply(pred_month, 2, var) # total variance per prediction, for prediction total uncertainty


# plot

ggplot(isere_month, aes(x = mes_for_fit))+
  geom_line(aes(y = poc_pred_lower, ymax = poc_pred_upper), col = "black")+
  geom_line(aes(y = poc_pred_upper), col = "black")+
  geom_point(aes(y = poc_fitted, col = "fitted with all events"), size = 2)+
  geom_point(aes(y = poc_boot_pred, col ="poc_boot_pred"), alpha = 0.5, size = 0.5)+
  labs(x = "MES, mg.L", y = "POC, %", col = "")+
  scale_color_manual(values = c("darkblue","gray50","lightblue"))+
  geom_abline(slope = 0, intercept = aspt_value, col = "darkred")+
  annotate(geom = "label", label = formula_pocfitg, x = Inf, y = Inf, hjust = 1.1, vjust = 1.1)+
  labs(x = "MES, g/L", y = "POC, %", colour = "", shape = "", title = "POC predicted from MES",subtitle = "Prediction interval in grey")+
  theme_minimal()+
  theme(legend.position = "bottom")

# plot, log-transformed x
ggplot(isere_month, aes(x = mes_for_fit))+
  geom_line(aes(y = poc_pred_lower, ymax = poc_pred_upper), col = "black")+
  geom_line(aes(y = poc_pred_upper), col = "black")+
  geom_point(aes(y = poc_fitted, col = "fitted with all events"), size = 2)+
  geom_point(aes(y = poc_boot_pred, col ="poc_boot_pred"), alpha = 0.5, size = 0.5)+
  labs(x = "MES, mg.L", y = "POC, %", col = "")+
  scale_color_manual(values = c("darkblue","gray50","lightblue"))+
  scale_x_continuous(trans = "log", breaks = c(1,10,100,1000))+
  geom_abline(slope = 0, intercept = aspt_value, col = "darkred")+
  annotate(geom = "label", label = formula_pocfitg, x = Inf, y = Inf, hjust = 1.1, vjust = 1.1)+
  labs(x = "MES, g/L", y = "POC, %", colour = "", shape = "", title = "POC predicted from MES",subtitle = "Prediction interval in grey")+
  theme_minimal()+
  theme(legend.position = "bottom")
```

```{r annual-flux-month, cache.lazy=F}

# creates matrix for Q

q_month_mean <-  matrix(q_month$q_mean, nrow = nrow_boot, ncol = nrow_month, byrow = T)
q_noise <- matrix(rnorm(nrow_boot*nrow_month, mean = 0, sd = q_u), nrow = nrow_boot, ncol = nrow_month) # creates a noise in percent (proportion), between 0 and 10%
q_mat_month <- q_month_mean * (1 + q_noise) # final MC of q, with noise. SD NOT INCLUDED: will not always be available


# compute flux
flux_kg.s_mat_month <- pred_month*mes_mat_month*1e-6*q_mat_month*1e-2*60*60*24*30 #pred_month * mes_mat : poc in mg/L converted to ton; q_mat converted from m3/s to L/s. Period : nb of seconds in 1 month. 

# Get index for columns by year
index_years <- sapply(unique(isere_month$year), function(y){which(isere_month$year == y)}) # list of indices corresponding to each year

# annual flux
annual_flux_ton.y_month <- sapply(index_years, function(idx){apply(flux_kg.s_mat_month[,idx], 1, sum, na.rm = T)}) # sum of fluxes per year, for each iteration of the bootstrap. Result is a matrix with nrow_boot rows and 19 columns (1 per year)

annual_flux_month_pi <- apply(annual_flux_ton.y_month, 2, quantile, probs = c(0.025, 0.5, 0.975), na.rm = T) # confidence interval for annual fluxes, per year. 3 lignes, 19 columns
annual_flux_month_mean <- colMeans(annual_flux_ton.y_month, na.rm = T) # mean annual flux per year. 1 vector

annual_flux_month_sd <- apply(annual_flux_ton.y_month, 2, sd, na.rm = T) # standard deviation of annual flux per year. Is just an estimate of goodness of mean, not as good as than the confidence interval. 
 

annual_flux_month_df <- data.frame(year = unique(isere_month$year), 
                        annual_flux_mean = annual_flux_month_mean, 
                        annual_flux_variability = annual_flux_month_sd, 
                        annual_flux_pi_lower = annual_flux_month_pi[1,], 
                        annual_flux_pi_upper = annual_flux_month_pi[3,])

ggplot(annual_flux_month_df)+
  geom_col(aes(x=year, y = annual_flux_month_mean), fill = "lightblue")+
  geom_errorbar(aes(x = year, ymin = annual_flux_pi_lower, ymax = annual_flux_pi_upper), width = 0.2)+
  labs(title = "Mean annual flux with prediction interval", subtitle = "Sampling grequency: month", x = "", y = "Mean annual flux, ton")+
  theme_minimal()

interannual_flux_ton.y_month <- rowMeans(annual_flux_ton.y_month, na.rm = T) # mean interannual flux per iteration of the bootstrap
interannual_flux_pi_month <- quantile(interannual_flux_ton.y_month, probs = c(0.025, 0.5, 0.975), na.rm = T) # prediction interval
interannual_flux_mean_month <- mean(interannual_flux_ton.y_month, na.rm = T) # mean interannual flux
interannual_flux_variability_month <- sd(annual_flux_month_mean, na.rm = T) # standard deviation of interannual flux per year

interannual_flux_month_df <- data.frame(year = "interannual", annual_flux_mean = interannual_flux_mean_month, 
                                  annual_flux_variability = interannual_flux_variability_month,
                        annual_flux_pi_lower = interannual_flux_pi_month[1], 
                        annual_flux_pi_upper = interannual_flux_pi_month[3])

total_flux_month_df <- rbind(annual_flux_month_df, interannual_flux_month_df)
total_flux_month_df$group <- c(rep("annual", length(unique(isere_month$year))), "interannual")

ggplot(total_flux_month_df)+
  geom_col(aes(x=year, y = annual_flux_mean, fill = group))+
    geom_errorbar(aes(x = year, ymin = annual_flux_pi_lower, ymax = annual_flux_pi_upper, col = "prediction interval"), width = 0.3, size = 0.8)+
  geom_errorbar(aes(x = year, ymin = annual_flux_mean - annual_flux_variability, ymax = annual_flux_mean + annual_flux_variability, col = "interannual variability"), width = 0.2, size = 0.8, linetype = 2)+
  scale_fill_manual(values = c("annual" = "lightblue", "interannual" = "indianred"))+
  scale_color_manual(values = c("prediction interval" = "darkblue", "interannual variability" = "darkred"), name = "")+
   labs(x = "Year", y = "Flux, from monthly mean values (ton/year)", fill = "")+
  theme_minimal()+
  theme(axis.text.x = element_text(angle = 45, hjust = 1), legend.position = "bottom")
```



## Compare fluxes

```{r compare}

compare_timesteps <- rbind(mutate(total_flux_df, "timestep" = "ref"), mutate(total_flux_day_df, "timestep" = "day"), mutate(total_flux_week_df, "timestep" = "week"), mutate(total_flux_month_df, "timestep" = "month")) %>%
  mutate(timestep = factor(timestep, levels = c("ref", "day", "week", "month")))

pd <- position_dodge(width = 0.9)

ggplot(compare_timesteps)+
  geom_col(aes(x=year, y = annual_flux_mean, fill = timestep), position = pd)+
  geom_errorbar(aes(x = year, ymin = annual_flux_pi_lower, ymax = annual_flux_pi_upper, col = timestep, group = timestep), width = 0.3, size = 0.5, position = pd)+
 # geom_errorbar(aes(x = year, ymin = annual_flux_mean - annual_flux_variability, ymax = annual_flux_mean + annual_flux_variability, col = "interannual variability"), width = 0.2, size = 0.8, linetype = 2)+
  scale_fill_manual(values = c("ref" = "#CAD2C5", "day" = "#84A98C", week = "#52796F", month = "#354F52"))+
  scale_color_manual(values = c("ref" = "grey20", "day" = "grey30", week = "grey50", month = "grey60"), name = "")+
   labs(x = "Year", y = "Flux, from dayly mean values (kg/year)", fill = "")+
  theme_minimal()+
  theme(axis.text.x = element_text(angle = 45, hjust = 1), legend.position = "bottom")
```
```{r interannual-error-in-percent}
# relative error by Monte-Carlo world

error_day <- (interannual_flux_ton.y_day - interannual_flux_ton.y)/interannual_flux_ton.y * 100
error_day_pi <- quantile(error_day, probs = c(0.025, 0.5, 0.975), na.rm = T) # confidence interval for annual fluxes, per year. 3 lignes, 19 columns
error_day_mean <- mean(error_day)

error_week <- (interannual_flux_ton.y_week - interannual_flux_ton.y)/interannual_flux_ton.y * 100
error_week_pi <- quantile(error_week, probs = c(0.025, 0.5, 0.975), na.rm = T) # confidence interval for annual fluxes, per year. 3 lignes, 19 columns
error_week_mean <- mean(error_week)

error_month <- (interannual_flux_ton.y_month - interannual_flux_ton.y)/interannual_flux_ton.y * 100
error_month_pi <- quantile(error_month, probs = c(0.025, 0.5, 0.975), na.rm = T) # confidence interval for annual fluxes, per year. 3 lignes, 19 columns
error_month_mean <- mean(error_month)

error <- data.frame(time_step = c("day","week","month"),
                    error = c(error_day_mean, error_week_mean, error_month_mean),
                    pi_upr = c(error_day_pi[3], error_month_pi[3], error_month_pi[3]),
                    pi_lwr = c(error_day_pi[1], error_month_pi[1], error_month_pi[1])) %>% 
                    mutate(time_step = factor(time_step, levels = c("day", "week", "month")))

ggplot(data=error, aes(x = time_step))+
  geom_point(aes(y = error))+
  geom_errorbar(aes(ymin=pi_lwr, ymax=pi_upr))+
  theme_minimal()
```







# Archives
## Timestep méthode 1: moyenne des flux MC

Méthode: moyenner les flux MC par jour avant de calculer le flux annuel. Revient à: Somme par jour puis somme par an. Pb: flux annuels 10^3 plus élevés que flux de ref

```{r group-by-day}
isere_for_gnls$day <- isere_for_gnls$DateHeure %>% format("%Y-%m-%d")
index_day <- sapply(unique(isere_for_gnls$day), function(y){which(isere_for_gnls$day == y)}) # list of indices corresponding to each day

mean_flux_day <- lapply(index_day,
                        function(idx){
                        tryCatch({apply(flux_kg.s_mat[,idx], 1, sum, na.rm = T)},
                        error = function(e) NULL)
                        }) # sum of fluxes per day, for each iteration of the bootstrap. Result is a matrix with nrow_boot rows and many columns (1 per day)

day_year <- names(index_day) %>% as.Date %>% year
index_year <- sapply(unique(day_year), function(y){which(day_year == y)})

annual_flux_day <- sapply(index_year, function(idx){
                                      tryCatch({sum(unlist(mean_flux_day[idx]), na.rm = T)},
                                               error = function(e) NULL)}) # sum of fluxes per year after grouping per day


compare_flux <- total_flux_df %>% cbind("annual_flux_day" = c(annual_flux_day, mean(annual_flux_day)))

ggplot(compare_flux) +
  geom_col(aes(x=year, y = annual_flux_mean, fill = group))+
  geom_point(aes(x=year, y = annual_flux_day), fill = "darkgreen")+
  geom_errorbar(aes(x = year, ymin = annual_flux_ci_lower, ymax = annual_flux_ci_upper, col = "prediction interval"), width = 0.3, size = 0.8)+
  geom_errorbar(aes(x = year, ymin = annual_flux_mean - annual_flux_variability, ymax = annual_flux_mean + annual_flux_variability, col = "interannual variability"), width = 0.2, size = 0.8, linetype = 2)+
  scale_fill_manual(values = c("annual" = "lightblue", "interannual" = "indianred"))+
  scale_color_manual(values = c("prediction interval" = "darkblue", "interannual variability" = "darkred"), name = "")+
   labs(x = "Year", y = "Flux (kg/year)", fill = "")+
  theme_minimal()+
  theme(axis.text.x = element_text(angle = 45, hjust = 1), legend.position = "bottom")
```

## Timestep méthode 2: moyenne de CMES et Q par time step avant d'appliquer GNLS, avec sd de moyennage

### Day 

```{r pred-isere-gnls-day-sd, cache.lazy = F}

isere_day <- isere %>% filter(mes_for_fit != 0 & !is.na(mes_for_fit)) %>% select(c("DateHeure", "mes_for_fit", "q_m3.s")) %>% mutate("day" = format(DateHeure, "%Y-%m-%d"), year = year(DateHeure), DateHeure = NULL) %>% group_by(day,year) %>% summarize_all(list("mean" = mean, "sd" = sd)) %>% ungroup()
names(isere_day) <- c("day","year","mes_for_fit","q_m3.s","mes_for_fit_sd","q_m3.s_sd")
isere_day$aspt <- aspt_value


nrow_isere <- nrow(isere_day)
nrow_boot <- nrow(coefs_boot)

# predict POC pour mes > 0
isere_day$poc_fitted <- predict(pocfitg, newdata = isere_day, na.action = na.pass) 


# Prediction interval

## Uncertainty on MES - AJOUTER INCERTITUDE DUE A LA MOYENNE?
mes_u <- summary(fit_cmes)$coefficients[4]

mes_mat_day <- matrix(NA_real_, nrow = nrow_boot, ncol = nrow_isere)

for(i in 1:nrow_isere){
  mes_mat_day[,i] <- rnorm(nrow_boot, mean = isere_day$mes_for_fit[i], sd = mes_u + isere_day$mes_for_fit_sd[i]) # chaque colonne de la matrice correspond à une observation de MES. Exactly same code as when working on lines.
}


## model function 
f <- function(x, a, b){
  a * x ^ b + aspt_value
}

## paramètres de variance from GNLS
theta <- as.numeric(coef(pocfitg$modelStruct$varStruct, unconstrained = F))
sigma_gnls <- pocfitg$sigma


### Matrice de prédictions, sans bruit


mu_day <- matrix(NA_real_, nrow = nrow_boot, ncol = nrow_isere)
for(i in 1:nrow_boot){
   mu_day[i,] <- with(as.list(coefs_boot[i,]), # listing the coefficients allows to have 2 named numbers to be used in the function
                      f(mes_mat_day[i, ], a, b))
}


isere_day$poc_var_mean <- apply(mu_day, 2, var) # variance of fit parameters + MES 

# adds noise
noise_mat_day <- matrix(NA_real_, nrow = nrow_boot, ncol = nrow_isere)
sigma_mat_day <- sigma_gnls * abs(mu_day)^theta

noise_mat_day <- matrix(rnorm(nrow_boot*nrow_isere, mean = 0, sd = 1), nrow = nrow_boot, ncol = nrow_isere)
noise_mat_day <- noise_mat_day*sigma_mat_day

pred_day <- mu_day + noise_mat_day

pred_day <- pmin(pmax(pred_day, 0), 1) # clampe pred_nls pour éviter les intervalles de prédiction en dessous de zéro

### computes variance, y-wise
isere_day$poc_var_tot <- apply(pred_day, 2, var) # total variance per prediction, for prediction total uncertainty

## computes prediction interval 
pi_day <- t(
  apply(pred_day, 2, quantile, probs = c(0.025, 0.975), na.rm = T)
)

colnames(pi_day) <- c("lower", "upper")

boot_pred_day <- colMeans(pred_day, na.rm = T)

## insert in isere_day

isere_day <- isere_day %>% mutate(poc_boot_pred = boot_pred_day,
                          poc_pred_lower = pi_day[,1],
                          poc_pred_upper = pi_day[,2])

# plot

ggplot(isere_day, aes(x = mes_for_fit))+
  geom_line(aes(y = poc_pred_lower, ymax = poc_pred_upper), col = "black")+
  geom_line(aes(y = poc_pred_upper), col = "black")+
  geom_point(aes(y = poc_fitted, col = "fitted with all events"), size = 2)+
  geom_point(aes(y = poc_boot_pred, col ="poc_boot_pred"), alpha = 0.5, size = 0.5)+
  labs(x = "MES, mg.L", y = "POC, %", col = "")+
  scale_color_manual(values = c("darkblue","gray50","lightblue"))+
  geom_abline(slope = 0, intercept = aspt_value, col = "darkred")+
  annotate(geom = "label", label = formula_pocfitg, x = Inf, y = Inf, hjust = 1.1, vjust = 1.1)+
  labs(x = "MES, mg/L", y = "POC,prop", colour = "", shape = "", title = "POC predicted from MES",subtitle = "Prediction interval in grey")+
  theme_minimal()+
  theme(legend.position = "bottom")

ggplot(isere_day, aes(x = mes_for_fit))+
  geom_line(aes(y = poc_pred_lower, ymax = poc_pred_upper), col = "black")+
  geom_line(aes(y = poc_pred_upper), col = "black")+
  geom_point(aes(y = poc_fitted, col = "fitted with all events"), size = 2)+
  geom_point(aes(y = poc_boot_pred, col ="poc_boot_pred"), alpha = 0.5, size = 0.5)+
  labs(x = "MES, mg.L", y = "POC, %", col = "")+
  scale_color_manual(values = c("darkblue","gray50","lightblue"))+
  scale_x_continuous(trans = "log", breaks = c(1,10,100,1000))+
  geom_abline(slope = 0, intercept = aspt_value, col = "darkred")+
  annotate(geom = "label", label = formula_pocfitg, x = Inf, y = Inf, hjust = 1.1, vjust = 1.1)+
  labs(x = "MES, mg/L", y = "POC,prop", colour = "", shape = "", title = "POC predicted from MES",subtitle = "Prediction interval in grey")+
  theme_minimal()+
  theme(legend.position = "bottom")
```

```{r annual-flux-day-sd, cache.lazy=F}

# create matrix of q
q_day_mean <-  matrix(isere_day$q_m3.s, nrow = nrow_boot, ncol = nrow_isere, byrow = T)
q_sd <- matrix(isere_day$q_m3.s_sd, nrow = nrow_boot, ncol = nrow_isere, byrow = T)

q_day_sd <- matrix(rnorm(nrow_boot*nrow_isere, mean = 0, sd = q_sd))

q_u = 0.1 # Cédric - avis d'expert NOT WORKING; has to be 10% of the Q measured, not ALWAYS 0.1!
q_noise <- matrix(rnorm(nrow_boot*nrow_isere, mean = 0, sd = q_u), nrow = nrow_boot, ncol = nrow_isere) # creates a noise in percent (proportion), between 0 and 10%

q_mat_day <- (q_day_mean + q_sd) * (1 + q_noise) # final MC of q, with sd variability + noise


# compute flux

flux_kg.s_mat_day <- pred_day*mes_mat_day*q_mat_day*1e-2*60*60*24 #pred_day * mes_mat : poc in mg/L; q_mat converted from m3/s to L/s. Period : nb of seconds in 1 day. 

index_years <- sapply(unique(isere_day$year), function(y){which(isere_day$year == y)}) # list of indices corresponding to each year

annual_flux_ton.y_day <- sapply(index_years, function(idx){apply(flux_kg.s_mat_day[,idx], 1, sum, na.rm = T)}) # sum of fluxes per year, for each iteration of the bootstrap. Result is a matrix with nrow_boot rows and 19 columns (1 per year)

annual_flux_day_ci <- apply(annual_flux_ton.y_day, 2, quantile, probs = c(0.025, 0.5, 0.975), na.rm = T) # confidence interval for annual fluxes, per year. 3 lignes, 19 columns
annual_flux_day_mean <- colMeans(annual_flux_ton.y_day, na.rm = T) # mean annual flux per year. 1 vector

annual_flux_day_sd <- apply(annual_flux_ton.y_day, 2, sd, na.rm = T) # standard deviation of annual flux per year. Is just an estimate of goodness of mean, not as good as than the confidence interval. 
 

annual_flux_day_df <- data.frame(year = unique(isere_day$year), 
                        annual_flux_mean = annual_flux_day_mean, 
                        annual_flux_variability = rep(NA, 19), # no physical sense in calculating "annual variability". Would be standard deviation of annual flux. But we prefer to show the prediction interval.
                        annual_flux_ci_lower = annual_flux_day_ci[1,], 
                        annual_flux_ci_upper = annual_flux_day_ci[3,])

ggplot(annual_flux_day_df)+
  geom_col(aes(x=year, y = annual_flux_day_mean), fill = "lightblue")+
  geom_errorbar(aes(x = year, ymin = annual_flux_ci_lower, ymax = annual_flux_ci_upper), width = 0.2)+
  theme_minimal()

interannual_flux_ton.y_day <- rowMeans(annual_flux_ton.y_day, na.rm = T) # mean interannual flux per iteration of the bootstrap
interannual_flux_ci_day <- quantile(interannual_flux_ton.y_day, probs = c(0.025, 0.5, 0.975), na.rm = T) # prediction interval
interannual_flux_mean_day <- mean(interannual_flux_ton.y_day, na.rm = T) # mean interannual flux
interannual_flux_variability_day <- sd(annual_flux_day_mean, na.rm = T) # standard deviation of interannual flux per year

interannual_flux_day_df <- data.frame(year = "interannual", annual_flux_mean = interannual_flux_mean_day, 
                                  annual_flux_variability = interannual_flux_variability_day,
                        annual_flux_ci_lower = interannual_flux_ci_day[1], 
                        annual_flux_ci_upper = interannual_flux_ci_day[3])

total_flux_day_df <- rbind(annual_flux_day_df, interannual_flux_day_df)
total_flux_day_df$group <- c(rep("annual", length(unique(isere_day$year))), "interannual")

ggplot(total_flux_day_df)+
  geom_col(aes(x=year, y = annual_flux_mean, fill = group))+
    geom_errorbar(aes(x = year, ymin = annual_flux_ci_lower, ymax = annual_flux_ci_upper, col = "prediction interval"), width = 0.3, size = 0.8)+
  geom_errorbar(aes(x = year, ymin = annual_flux_mean - annual_flux_variability, ymax = annual_flux_mean + annual_flux_variability, col = "interannual variability"), width = 0.2, size = 0.8, linetype = 2)+
  scale_fill_manual(values = c("annual" = "lightblue", "interannual" = "indianred"))+
  scale_color_manual(values = c("prediction interval" = "darkblue", "interannual variability" = "darkred"), name = "")+
   labs(x = "Year", y = "Flux, from dayly mean values (kg/year)", fill = "")+
  theme_minimal()+
  theme(axis.text.x = element_text(angle = 45, hjust = 1), legend.position = "bottom")
```

### Week

```{r pred-isere-gnls-week-sd, cache.lazy = F}

isere_week <- isere %>% filter(mes_for_fit != 0 & !is.na(mes_for_fit)) %>% select(c("DateHeure", "mes_for_fit", "q_m3.s")) %>% mutate("week" = week(DateHeure), year = year(DateHeure), DateHeure = NULL) %>% group_by(week,year) %>% summarize_all(list("mean" = mean, "sd" = sd)) %>% ungroup()
names(isere_week) <- c("week","year","mes_for_fit","q_m3.s","mes_for_fit_sd","q_m3.s_sd")
isere_week$aspt <- aspt_value


nrow_isere <- nrow(isere_week)
nrow_boot <- nrow(coefs_boot)

# predict POC pour mes > 0
isere_week$poc_fitted <- predict(pocfitg, newdata = isere_week, na.action = na.pass) 


# Prediction interval

## Uncertainty on MES - AJOUTER INCERTITUDE DUE A LA MOYENNE?
mes_u <- summary(fit_cmes)$coefficients[4]

mes_mat_week <- matrix(NA_real_, nrow = nrow_boot, ncol = nrow_isere)

for(i in 1:nrow_isere){
  mes_mat_week[,i] <- rnorm(nrow_boot, mean = isere_week$mes_for_fit[i], sd = mes_u + isere_week$mes_for_fit_sd[i]) # chaque colonne de la matrice correspond à une observation de MES. Exactly same code as when working on lines.
}


## model function 
f <- function(x, a, b){
  a * x ^ b + aspt_value
}

## paramètres de variance from GNLS
theta <- as.numeric(coef(pocfitg$modelStruct$varStruct, unconstrained = F))
sigma_gnls <- pocfitg$sigma


### Matrice de prédictions, sans bruit


mu_week <- matrix(NA_real_, nrow = nrow_boot, ncol = nrow_isere)
for(i in 1:nrow_boot){
   mu_week[i,] <- with(as.list(coefs_boot[i,]), # listing the coefficients allows to have 2 named numbers to be used in the function
                      f(mes_mat_week[i, ], a, b))
}


isere_week$poc_var_mean <- apply(mu_week, 2, var) # variance of fit parameters + MES 

# adds noise
noise_mat_week <- matrix(NA_real_, nrow = nrow_boot, ncol = nrow_isere)
sigma_mat_week <- sigma_gnls * abs(mu_week)^theta

noise_mat_week <- matrix(rnorm(nrow_boot*nrow_isere, mean = 0, sd = 1), nrow = nrow_boot, ncol = nrow_isere)
noise_mat_week <- noise_mat_week*sigma_mat_week

pred_week <- mu_week + noise_mat_week

pred_week <- pmin(pmax(pred_week, 0), 1) # clampe pred_nls pour éviter les intervalles de prédiction en dessous de zéro

### computes variance, y-wise
isere_week$poc_var_tot <- apply(pred_week, 2, var) # total variance per prediction, for prediction total uncertainty

## computes prediction interval 
pi_week <- t(
  apply(pred_week, 2, quantile, probs = c(0.025, 0.975), na.rm = T)
)

colnames(pi_week) <- c("lower", "upper")

boot_pred_week <- colMeans(pred_week, na.rm = T)

## insert in isere_week

isere_week <- isere_week %>% mutate(poc_boot_pred = boot_pred_week,
                          poc_pred_lower = pi_week[,1],
                          poc_pred_upper = pi_week[,2])

# plot

ggplot(isere_week, aes(x = mes_for_fit))+
  geom_line(aes(y = poc_pred_lower, ymax = poc_pred_upper), col = "black")+
  geom_line(aes(y = poc_pred_upper), col = "black")+
  geom_point(aes(y = poc_fitted, col = "fitted with all events"), size = 2)+
  geom_point(aes(y = poc_boot_pred, col ="poc_boot_pred"), alpha = 0.5, size = 0.5)+
  labs(x = "MES, mg.L", y = "POC, %", col = "")+
  scale_color_manual(values = c("darkblue","gray50","lightblue"))+
  geom_abline(slope = 0, intercept = aspt_value, col = "darkred")+
  annotate(geom = "label", label = formula_pocfitg, x = Inf, y = Inf, hjust = 1.1, vjust = 1.1)+
  labs(x = "MES, mg/L", y = "POC,prop", colour = "", shape = "", title = "POC predicted from MES",subtitle = "Prediction interval in grey")+
  theme_minimal()+
  theme(legend.position = "bottom")

ggplot(isere_week, aes(x = mes_for_fit))+
  geom_line(aes(y = poc_pred_lower, ymax = poc_pred_upper), col = "black")+
  geom_line(aes(y = poc_pred_upper), col = "black")+
  geom_point(aes(y = poc_fitted, col = "fitted with all events"), size = 2)+
  geom_point(aes(y = poc_boot_pred, col ="poc_boot_pred"), alpha = 0.5, size = 0.5)+
  labs(x = "MES, mg.L", y = "POC, %", col = "")+
  scale_color_manual(values = c("darkblue","gray50","lightblue"))+
  scale_x_continuous(trans = "log", breaks = c(1,10,100,1000))+
  geom_abline(slope = 0, intercept = aspt_value, col = "darkred")+
  annotate(geom = "label", label = formula_pocfitg, x = Inf, y = Inf, hjust = 1.1, vjust = 1.1)+
  labs(x = "MES, mg/L", y = "POC,prop", colour = "", shape = "", title = "POC predicted from MES",subtitle = "Prediction interval in grey")+
  theme_minimal()+
  theme(legend.position = "bottom")
```
```{r annual-flux-week-sd, cache.lazy=F}

# create matrix of q
q_week_mean <-  matrix(isere_week$q_m3.s, nrow = nrow_boot, ncol = nrow_isere, byrow = T)
q_sd <- matrix(isere_week$q_m3.s_sd, nrow = nrow_boot, ncol = nrow_isere, byrow = T)

q_week_sd <- matrix(rnorm(nrow_boot*nrow_isere, mean = 0, sd = q_sd))

q_u = 0.1 # Cédric - avis d'expert NOT WORKING; has to be 10% of the Q measured, not ALWAYS 0.1!
q_noise <- matrix(rnorm(nrow_boot*nrow_isere, mean = 0, sd = q_u), nrow = nrow_boot, ncol = nrow_isere) # creates a noise in percent (proportion), between 0 and 10%

q_mat_week <- (q_week_mean + q_sd) * (1 + q_noise) # final MC of q, with sd variability + noise


# compute flux

flux_kg.s_mat_week <- pred_week*mes_mat_week*q_mat_week*1e-2*60*60*24*7 #pred_week * mes_mat : poc in mg/L; q_mat converted from m3/s to L/s. Period : nb of seconds in 1 week. 

index_years <- sapply(unique(isere_week$year), function(y){which(isere_week$year == y)}) # list of indices corresponding to each year

annual_flux_ton.y_week <- sapply(index_years, function(idx){apply(flux_kg.s_mat_week[,idx], 1, sum, na.rm = T)}) # sum of fluxes per year, for each iteration of the bootstrap. Result is a matrix with nrow_boot rows and 19 columns (1 per year)

annual_flux_week_ci <- apply(annual_flux_ton.y_week, 2, quantile, probs = c(0.025, 0.5, 0.975), na.rm = T) # confidence interval for annual fluxes, per year. 3 lignes, 19 columns
annual_flux_week_mean <- colMeans(annual_flux_ton.y_week, na.rm = T) # mean annual flux per year. 1 vector

annual_flux_week_sd <- apply(annual_flux_ton.y_week, 2, sd, na.rm = T) # standard deviation of annual flux per year. Is just an estimate of goodness of mean, not as good as than the confidence interval. 
 

annual_flux_week_df <- data.frame(year = unique(isere_week$year), 
                        annual_flux_mean = annual_flux_week_mean, 
                        annual_flux_variability = rep(NA, 19), # no physical sense in calculating "annual variability". Would be standard deviation of annual flux. But we prefer to show the prediction interval.
                        annual_flux_ci_lower = annual_flux_week_ci[1,], 
                        annual_flux_ci_upper = annual_flux_week_ci[3,])

ggplot(annual_flux_week_df)+
  geom_col(aes(x=year, y = annual_flux_week_mean), fill = "lightblue")+
  geom_errorbar(aes(x = year, ymin = annual_flux_ci_lower, ymax = annual_flux_ci_upper), width = 0.2)+
  theme_minimal()

interannual_flux_ton.y_week <- rowMeans(annual_flux_ton.y_week, na.rm = T) # mean interannual flux per iteration of the bootstrap
interannual_flux_ci_week <- quantile(interannual_flux_ton.y_week, probs = c(0.025, 0.5, 0.975), na.rm = T) # prediction interval
interannual_flux_mean_week <- mean(interannual_flux_ton.y_week, na.rm = T) # mean interannual flux
interannual_flux_variability_week <- sd(annual_flux_week_mean, na.rm = T) # standard deviation of interannual flux per year

interannual_flux_week_df <- data.frame(year = "interannual", annual_flux_mean = interannual_flux_mean_week, 
                                  annual_flux_variability = interannual_flux_variability_week,
                        annual_flux_ci_lower = interannual_flux_ci_week[1], 
                        annual_flux_ci_upper = interannual_flux_ci_week[3])

total_flux_week_df <- rbind(annual_flux_week_df, interannual_flux_week_df)
total_flux_week_df$group <- c(rep("annual", length(unique(isere_week$year))), "interannual")

ggplot(total_flux_week_df)+
  geom_col(aes(x=year, y = annual_flux_mean, fill = group))+
    geom_errorbar(aes(x = year, ymin = annual_flux_ci_lower, ymax = annual_flux_ci_upper, col = "prediction interval"), width = 0.3, size = 0.8)+
  geom_errorbar(aes(x = year, ymin = annual_flux_mean - annual_flux_variability, ymax = annual_flux_mean + annual_flux_variability, col = "interannual variability"), width = 0.2, size = 0.8, linetype = 2)+
  scale_fill_manual(values = c("annual" = "lightblue", "interannual" = "indianred"))+
  scale_color_manual(values = c("prediction interval" = "darkblue", "interannual variability" = "darkred"), name = "")+
   labs(x = "Year", y = "Flux, from weekly mean values (kg/year)", fill = "")+
  theme_minimal()+
  theme(axis.text.x = element_text(angle = 45, hjust = 1), legend.position = "bottom")
```


### Month

```{r pred-isere-gnls-month-sd, cache.lazy = F}

isere_month <- isere %>% filter(mes_for_fit != 0 & !is.na(mes_for_fit)) %>% select(c("DateHeure", "mes_for_fit", "q_m3.s")) %>% mutate("month" = month(DateHeure), year = year(DateHeure), DateHeure = NULL) %>% group_by(month,year) %>% summarize_all(list("mean" = mean, "sd" = sd)) %>% ungroup()
names(isere_month) <- c("month","year","mes_for_fit","q_m3.s","mes_for_fit_sd","q_m3.s_sd")
isere_month$aspt <- aspt_value


nrow_isere <- nrow(isere_month)
nrow_boot <- nrow(coefs_boot)

# predict POC pour mes > 0
isere_month$poc_fitted <- predict(pocfitg, newdata = isere_month, na.action = na.pass) 


# Prediction interval

## Uncertainty on MES - AJOUTER INCERTITUDE DUE A LA MOYENNE?
mes_u <- summary(fit_cmes)$coefficients[4]

mes_mat_month <- matrix(NA_real_, nrow = nrow_boot, ncol = nrow_isere)

for(i in 1:nrow_isere){
  mes_mat_month[,i] <- rnorm(nrow_boot, mean = isere_month$mes_for_fit[i], sd = mes_u + isere_month$mes_for_fit_sd[i]) # chaque colonne de la matrice correspond à une observation de MES. Exactly same code as when working on lines.
}


## model function 
f <- function(x, a, b){
  a * x ^ b + aspt_value
}

## paramètres de variance from GNLS
theta <- as.numeric(coef(pocfitg$modelStruct$varStruct, unconstrained = F))
sigma_gnls <- pocfitg$sigma


### Matrice de prédictions, sans bruit


mu_month <- matrix(NA_real_, nrow = nrow_boot, ncol = nrow_isere)
for(i in 1:nrow_boot){
   mu_month[i,] <- with(as.list(coefs_boot[i,]), # listing the coefficients allows to have 2 named numbers to be used in the function
                      f(mes_mat_month[i, ], a, b))
}


isere_month$poc_var_mean <- apply(mu_month, 2, var) # variance of fit parameters + MES 

# adds noise
noise_mat_month <- matrix(NA_real_, nrow = nrow_boot, ncol = nrow_isere)
sigma_mat_month <- sigma_gnls * abs(mu_month)^theta

noise_mat_month <- matrix(rnorm(nrow_boot*nrow_isere, mean = 0, sd = 1), nrow = nrow_boot, ncol = nrow_isere)
noise_mat_month <- noise_mat_month*sigma_mat_month

pred_month <- mu_month + noise_mat_month

pred_month <- pmin(pmax(pred_month, 0), 1) # clampe pred_nls pour éviter les intervalles de prédiction en dessous de zéro

### computes variance, y-wise
isere_month$poc_var_tot <- apply(pred_month, 2, var) # total variance per prediction, for prediction total uncertainty

## computes prediction interval 
pi_month <- t(
  apply(pred_month, 2, quantile, probs = c(0.025, 0.975), na.rm = T)
)

colnames(pi_month) <- c("lower", "upper")

boot_pred_month <- colMeans(pred_month, na.rm = T)

## insert in isere_month

isere_month <- isere_month %>% mutate(poc_boot_pred = boot_pred_month,
                          poc_pred_lower = pi_month[,1],
                          poc_pred_upper = pi_month[,2])

# plot

ggplot(isere_month, aes(x = mes_for_fit))+
  geom_line(aes(y = poc_pred_lower, ymax = poc_pred_upper), col = "black")+
  geom_line(aes(y = poc_pred_upper), col = "black")+
  geom_point(aes(y = poc_fitted, col = "fitted with all events"), size = 2)+
  geom_point(aes(y = poc_boot_pred, col ="poc_boot_pred"), alpha = 0.5, size = 0.5)+
  labs(x = "MES, mg.L", y = "POC, %", col = "")+
  scale_color_manual(values = c("darkblue","gray50","lightblue"))+
  geom_abline(slope = 0, intercept = aspt_value, col = "darkred")+
  annotate(geom = "label", label = formula_pocfitg, x = Inf, y = Inf, hjust = 1.1, vjust = 1.1)+
  labs(x = "MES, mg/L", y = "POC,prop", colour = "", shape = "", title = "POC predicted from MES",subtitle = "Prediction interval in grey")+
  theme_minimal()+
  theme(legend.position = "bottom")

ggplot(isere_month, aes(x = mes_for_fit))+
  geom_line(aes(y = poc_pred_lower, ymax = poc_pred_upper), col = "black")+
  geom_line(aes(y = poc_pred_upper), col = "black")+
  geom_point(aes(y = poc_fitted, col = "fitted with all events"), size = 2)+
  geom_point(aes(y = poc_boot_pred, col ="poc_boot_pred"), alpha = 0.5, size = 0.5)+
  labs(x = "MES, mg.L", y = "POC, %", col = "")+
  scale_color_manual(values = c("darkblue","gray50","lightblue"))+
  scale_x_continuous(trans = "log", breaks = c(1,10,100,1000))+
  geom_abline(slope = 0, intercept = aspt_value, col = "darkred")+
  annotate(geom = "label", label = formula_pocfitg, x = Inf, y = Inf, hjust = 1.1, vjust = 1.1)+
  labs(x = "MES, mg/L", y = "POC,prop", colour = "", shape = "", title = "POC predicted from MES",subtitle = "Prediction interval in grey")+
  theme_minimal()+
  theme(legend.position = "bottom")
```
```{r annual-flux-month-sd, cache.lazy=F}

# create matrix of q
q_month_mean <-  matrix(isere_month$q_m3.s, nrow = nrow_boot, ncol = nrow_isere, byrow = T)
q_sd <- matrix(isere_month$q_m3.s_sd, nrow = nrow_boot, ncol = nrow_isere, byrow = T)

q_month_sd <- matrix(rnorm(nrow_boot*nrow_isere, mean = 0, sd = q_sd))

q_u = 0.1 # Cédric - avis d'expert NOT WORKING; has to be 10% of the Q measured, not ALWAYS 0.1!
q_noise <- matrix(rnorm(nrow_boot*nrow_isere, mean = 0, sd = q_u), nrow = nrow_boot, ncol = nrow_isere) # creates a noise in percent (proportion), between 0 and 10%

q_mat_month <- (q_month_mean + q_sd) * (1 + q_noise) # final MC of q, with sd variability + noise

# compute flux

flux_kg.s_mat_month <- pred_month*mes_mat_month*q_mat_month*1e-2*60*60*24*30 #pred_month * mes_mat : poc in mg/L; q_mat converted from m3/s to L/s. Period : nb of seconds in 1 month. 

index_years <- sapply(unique(isere_month$year), function(y){which(isere_month$year == y)}) # list of indices corresponding to each year

annual_flux_ton.y_month <- sapply(index_years, function(idx){apply(flux_kg.s_mat_month[,idx], 1, sum, na.rm = T)}) # sum of fluxes per year, for each iteration of the bootstrap. Result is a matrix with nrow_boot rows and 19 columns (1 per year)

annual_flux_month_ci <- apply(annual_flux_ton.y_month, 2, quantile, probs = c(0.025, 0.5, 0.975), na.rm = T) # confidence interval for annual fluxes, per year. 3 lignes, 19 columns
annual_flux_month_mean <- colMeans(annual_flux_ton.y_month, na.rm = T) # mean annual flux per year. 1 vector

annual_flux_month_sd <- apply(annual_flux_ton.y_month, 2, sd, na.rm = T) # standard deviation of annual flux per year. Is just an estimate of goodness of mean, not as good as than the confidence interval. 
 

annual_flux_month_df <- data.frame(year = unique(isere_month$year), 
                        annual_flux_mean = annual_flux_month_mean, 
                        annual_flux_variability = rep(NA, 19), # no physical sense in calculating "annual variability". Would be standard deviation of annual flux. But we prefer to show the prediction interval.
                        annual_flux_ci_lower = annual_flux_month_ci[1,], 
                        annual_flux_ci_upper = annual_flux_month_ci[3,])

ggplot(annual_flux_month_df)+
  geom_col(aes(x=year, y = annual_flux_month_mean), fill = "lightblue")+
  geom_errorbar(aes(x = year, ymin = annual_flux_ci_lower, ymax = annual_flux_ci_upper), width = 0.2)+
  theme_minimal()

interannual_flux_ton.y_month <- rowMeans(annual_flux_ton.y_month, na.rm = T) # mean interannual flux per iteration of the bootstrap
interannual_flux_ci_month <- quantile(interannual_flux_ton.y_month, probs = c(0.025, 0.5, 0.975), na.rm = T) # prediction interval
interannual_flux_mean_month <- mean(interannual_flux_ton.y_month, na.rm = T) # mean interannual flux
interannual_flux_variability_month <- sd(annual_flux_month_mean, na.rm = T) # standard deviation of interannual flux per year

interannual_flux_month_df <- data.frame(year = "interannual", annual_flux_mean = interannual_flux_mean_month, 
                                  annual_flux_variability = interannual_flux_variability_month,
                        annual_flux_ci_lower = interannual_flux_ci_month[1], 
                        annual_flux_ci_upper = interannual_flux_ci_month[3])

total_flux_month_df <- rbind(annual_flux_month_df, interannual_flux_month_df)
total_flux_month_df$group <- c(rep("annual", length(unique(isere_month$year))), "interannual")

ggplot(total_flux_month_df)+
  geom_col(aes(x=year, y = annual_flux_mean, fill = group))+
    geom_errorbar(aes(x = year, ymin = annual_flux_ci_lower, ymax = annual_flux_ci_upper, col = "prediction interval"), width = 0.3, size = 0.8)+
  geom_errorbar(aes(x = year, ymin = annual_flux_mean - annual_flux_variability, ymax = annual_flux_mean + annual_flux_variability, col = "interannual variability"), width = 0.2, size = 0.8, linetype = 2)+
  scale_fill_manual(values = c("annual" = "lightblue", "interannual" = "indianred"))+
  scale_color_manual(values = c("prediction interval" = "darkblue", "interannual variability" = "darkred"), name = "")+
   labs(x = "Year", y = "Flux, from monthly mean values (kg/year)", fill = "")+
  theme_minimal()+
  theme(axis.text.x = element_text(angle = 45, hjust = 1), legend.position = "bottom")
```



### Compare fluxes

```{r compare-with-sd}

compare_timesteps <- rbind(mutate(total_flux_df, "timestep" = "ref"), mutate(total_flux_day_df, "timestep" = "day"), mutate(total_flux_week_df, "timestep" = "week"), mutate(total_flux_month_df, "timestep" = "month"))

pd <- position_dodge(width = 0.9)
ggplot(compare_timesteps)+
  geom_col(aes(x=year, y = annual_flux_mean, fill = timestep), position = pd)+
  geom_errorbar(aes(x = year, ymin = annual_flux_ci_lower, ymax = annual_flux_ci_upper, col = timestep, group = timestep), width = 0.3, size = 0.8, position = pd)+
 # geom_errorbar(aes(x = year, ymin = annual_flux_mean - annual_flux_variability, ymax = annual_flux_mean + annual_flux_variability, col = "interannual variability"), width = 0.2, size = 0.8, linetype = 2)+
  scale_fill_manual(values = c("ref" = "lightblue", "day" = "indianred", week = "darkolivegreen2", month = "burlywood2"))+
  scale_color_manual(values = c("ref" = "darkblue", "day" = "darkred", week = "darkolivegreen", month = "burlywood4"), name = "")+
   labs(x = "Year", y = "Flux, from dayly mean values (kg/year)", fill = "")+
  theme_minimal()+
  theme(axis.text.x = element_text(angle = 45, hjust = 1), legend.position = "bottom")
```




