---
title: "Isere Campus"
output: 
  html_document:
    code_folding: hide
    toc: true
    toc_float: true
    number_section: true
date: "2025-06-30"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = F, warning = F, error = F, fig.align = "center", collapse = T,
                      cache = T)
```

```{r libraries}

library(ggplot2)
library(ggpubr)

library(dplyr)
library(readxl)
library(lubridate)

set.seed(1902)
```


# Données

Les données dont on dispose pour la station de mesures d'Isère - campus sont: 

* débits horaires de 2005 à 2025
* CMES de 2006 à 2025
* POC mesuré (et non calculé): 
    - Carbonisère: suivi hebdo de 2006 à 2008 + crue du 19 mai 2006  + chasse du 27/06/2006 + crue du 30/08/2006 + chasse du 5/06/2006
    - crues du 19/08/2022 (lave torrentielle) et chasse du 22/06/2022
    - suivi hebdo Carbonium (pas encore disponible)
* DOC: 
  - Carbonisère: suivi hebdo de 2006 à 2008 + crue du 19 mai 2006  + chasse du 27/06/2006 + crue du 30/08/2006 + chasse du 5/06/2006
  - suivi hebdo Carbonium (pas encore dispo)

## Charger les données

```{r data}

# Crues
carbonisere <- read_xlsx("Bilan carbonisère.xlsx")


crues_2022 <- read_xlsx(path = "Crues_Isère_2022.xlsx", sheet = "test_match") 
crues_2022$mes_mg.L <- NA
crues_2022$debit_m3.s <- NA
crues_2022$doc_mg.L <- NA

doc_isere_2011 <- read_excel("doc_isere_2011-2012.xls")
doc_isere_2011$name <- "DOC 2011"
doc_isere_2011$poc_percent <- NA
doc_isere_2011$mes_mg.L <- doc_isere_2011$mes_g.L * 1e3

poc_isere_2011 <- read_excel("poc_isere_2011-2012.xls")
poc_isere_2011$doc_mg.L <- NA
poc_isere_2011$name <- "POC 2011"
poc_isere_2011$mes_mg.L <- poc_isere_2011$mes_g.L * 1e3

crues <- rbind(select(carbonisere, c("DateHeure","name","debit_m3.s","mes_mg.L","poc_percent", "doc_mg.L")),select(crues_2022, c("DateHeure","name","debit_m3.s", "mes_mg.L","poc_percent", "doc_mg.L"))) %>%
  rbind(select(doc_isere_2011, c("DateHeure","name","debit_m3.s","mes_mg.L","poc_percent", "doc_mg.L"))) %>% rbind(select(poc_isere_2011, c("DateHeure","name","debit_m3.s","mes_mg.L","poc_percent", "doc_mg.L")))

# Chroniques BDOH
cmes <- readxl::read_xlsx(path = "isere.xlsx", sheet = "cmes", col_types = c("date","numeric","text")) %>% subset(Qualite == "v") %>% mutate(Qualite = NULL)
debit <- readxl::read_xlsx(path = "isere.xlsx", sheet = "debit", col_types = c("date","numeric","text")) %>% subset(Qualite == "v") %>% mutate(Qualite = NULL)

#crues <- crues %>% group_by(Crue) %>% mutate(period = as.numeric(-(Date - lead(Date)))) # period in hours

isere <- merge(debit, cmes, by="DateHeure") %>% merge(crues, by = "DateHeure", all = T) 
isere$year <- year(isere$DateHeure)
isere$commondate <- as.Date(paste0("2000-", format(isere$Date,"%j")), "%Y-%j")

isere$period <- as.numeric(-(isere$DateHeure - lead(isere$DateHeure))) # period in s

summary_isere <- merge(
isere %>% subset(!is.na(poc_percent)) %>% group_by(year) %>% summarise(nb_poc = n()),
isere %>% subset(!is.na(cmes_g.L)) %>% group_by(year) %>% summarise(nb_cmes = n()),
by = "year", all = T) %>% 
  merge(isere %>% subset(!is.na(doc_mg.L)) %>% group_by(year) %>% summarise(nb_doc = n()), by = "year", all = T) %>%
  merge(isere %>% subset(!is.na(q_m3.s)) %>% group_by(year) %>% summarise(nb_q = n()), by = "year", all = T) %>%
  merge(isere %>% subset(!is.na(period)) %>% group_by(year) %>% summarise(total_period_j = round(sum(period)/(24*60*60))), by = "year", all = T)
  
summary_isere %>% knitr::kable(caption = "Nombre d'observations de DOC, POC, CMES et débit par an") %>% kableExtra::kable_styling()

poc_isere <- filter(isere, !is.na(poc_percent))
# add mes for POC 2011 to poc_isere (were not measured, but we have cmes)
poc_isere$mes_for_fit <- poc_isere$mes_mg.L
poc_isere$mes_for_fit[which(is.na(poc_isere$mes_for_fit))] <-  poc_isere$cmes_g.L[which(is.na(poc_isere$mes_for_fit))]*1e3
poc_isere <- poc_isere %>% subset(!is.na(mes_for_fit))

poc_isere$poc_prop <- poc_isere$poc_percent / 100 # converts % in proportion 
```

```{r annual-q-mes, fig.dim = c(10, 10)}

ggarrange(
ggplot(isere, aes(x = commondate)) + 
  geom_point(aes(y = q_m3.s), col = "lightblue", size = 0.5) +
  scale_x_date(labels = function(x) format(x, "%d-%b"), date_minor_breaks = "1 month", name = "")+
  facet_grid(rows = vars(year))+
  labs(x = "", y = "Q, m3/s") +
  theme_minimal()+
  theme(legend.position = "bottom"),

ggplot(isere, aes(x = commondate)) + 
  geom_point(aes(y = cmes_g.L), col = "palegreen4", size = 0.5) +
  scale_x_date(labels = function(x) format(x, "%d-%b"), date_minor_breaks = "1 month", name = "")+
  facet_grid(rows = vars(year))+
  labs(x = "", y = "CMES, g/L") +
  theme_minimal()+
  theme(legend.position = "bottom"),

ncol = 2
) %>%
  annotate_figure(top = text_grob("Mesures de débit et CMES", face = "bold", size = 14))

```

```{r annual-doc-poc, fig.dim = c(10, 5)}

ggarrange(

ggplot(subset(isere, !is.na(doc_mg.L)), aes(x = commondate)) + 
  geom_point(aes(y = doc_mg.L), col = "orange") +
  scale_x_date(labels = function(x) format(x, "%d-%b"), date_minor_breaks = "1 month", name = "")+
  facet_grid(rows = vars(year))+
  labs(x = "", y = "DOC, mg/L") +
  theme_minimal()+
  theme(legend.position = "bottom"),

ggplot(subset(isere, !is.na(poc_percent)), aes(x = commondate)) + 
  geom_point(aes(y = poc_percent), col = "darkred") +
  scale_x_date(labels = function(x) format(x, "%d-%b"), date_minor_breaks = "1 month", name = "")+
  facet_grid(rows = vars(year))+
  labs(x = "", y = "POC, %") +
  theme_minimal()+
  theme(legend.position = "bottom"),

ncol = 2
) %>%
  annotate_figure(top = text_grob("Mesures de DOC et POC", face = "bold", size = 14))



```

Les mesures de POC sont réalisées parallèlement à des mesures de MES. La valeur de *MES* mesurée à cette occasion est légèrement différente de la valeur de *CMES* reconstruire à partir des sondes de turbidité. 

```{r compare-cmes-and-mes}
ggplot(isere)+
  geom_point(aes(x=cmes_g.L, y = mes_mg.L, col = name))+
  geom_abline(slope = 1000, intercept = 0)+
  scale_colour_viridis_d()+
  labs(title = "Comparaison entre CMES et MES", x = "CMES, g/L", y = "MES, mg/L")+
  scale_x_continuous(limits = c(0,20))+ 
  theme_minimal()

ggarrange(
  ggplot(isere)+
    geom_point(aes(x = mes_mg.L, y = poc_percent, col = name))+
    scale_color_viridis_d()+
    scale_x_continuous(trans = "log")+scale_y_continuous(trans = "log")+
    labs( x = "MES, mg/L", y = "POC%")+
    theme_minimal(),
  ggplot(isere)+
    geom_point(aes(x = cmes_g.L, y = poc_percent, col = name))+
        scale_color_viridis_d()+
      scale_x_continuous(trans = "log")+scale_y_continuous(trans = "log")+
        labs( x = "CMES, g/L", y = "POC%")+
    theme_minimal(),
  ncol = 2, common.legend = T, legend = "bottom"
) %>%
  annotate_figure(top = text_grob("POC% et valeur associée de MES et CMES", face = "bold", size = 14))


```


## Example of data - Carbonisere

Visualisation des données de la campagne Carbonisère: DOC et POC mesurés sur les années 2006-2007-2009. 

```{r view-fluxes}

ggplot(carbonisere)+
  geom_point(aes(x=as.Date(DateHeure), y = debit_m3.s), col = "cadetblue4")+
  geom_abline(slope = 0, intercept = mean(carbonisere$debit_m3.s, na.rm = T), col = "darkred")+
 annotate(geom = "label", label = round(mean(carbonisere$debit_m3.s, na.rm = T), 2), x= as.Date("2008-01-01"), y = 250)+
   scale_x_date(labels = function(x) format(x, "%d-%b-%y"), date_breaks = "1 year", date_minor_breaks = "1 month",name = "", limits = c(as.Date("2006-01-01"), as.Date("2008-03-31")))+ 
  labs(y = "Débit, m3/s")+
  theme_minimal(base_size = 15)

isere678 <- subset(isere, year == c(2006,2007,2008))

ggplot(isere678)+
  geom_point(aes(x=as.Date(DateHeure), y = q_m3.s), col = "cadetblue4", size = 1)+
  geom_abline(slope = 0, intercept = mean(isere678$q_m3.s, na.rm = T), col = "darkred")+
 annotate(geom = "label", label = round(mean(isere678$q_m3.s, na.rm = T), 2), x= as.Date("2006-01-01"), y = 200)+
   scale_x_date(labels = function(x) format(x, "%d-%b-%y"), date_breaks = "1 year", date_minor_breaks = "1 month",name = "", limits = c(as.Date("2006-01-01"), as.Date("2008-03-31")))+ 
  labs(y = "Débit, m3/s")+
  theme_minimal(base_size = 15)

ggplot(carbonisere)+
  geom_point(aes(x=as.Date(DateHeure), y = doc_mg.L), col = "darkolivegreen4")+
  geom_abline(slope = 0, intercept = mean(carbonisere$doc_mg.L, na.rm = T), col = "darkred")+
 annotate(geom = "label", label = round(mean(carbonisere$doc_mg.L, na.rm = T), 2), x= as.Date("2008-01-01"), y = 3)+
   scale_x_date(labels = function(x) format(x, "%d-%b-%y"), date_breaks = "1 year", date_minor_breaks = "1 month",name = "", limits = c(as.Date("2006-01-01"), as.Date("2008-03-31")))+ 
  labs(y = "Carbone Organique Dissous, mg/L")+
  theme_minimal(base_size = 15)


ggplot(carbonisere)+
  geom_point(aes(x=as.Date(DateHeure), y = poc_percent*mes_mg.L), col = "darkolivegreen4")+
 #  geom_abline(slope = 0, intercept = mean(carbonisere$poc_percent * carbonisere$mes_mg.L, na.rm = T), col = "darkred")+
 # annotate(geom = "label", label = round(mean(carbonisere$poc_percent * carbonisere$mes_mg.L, na.rm = T), 2), x= as.Date("2008-01-01"), y = 3)+
   scale_x_date(labels = function(x) format(x, "%d-%b-%y"), date_breaks = "1 year", date_minor_breaks = "1 month",name = "", limits = c(as.Date("2006-01-01"), as.Date("2008-03-31")))+ 
  labs(y = "Carbone Organique Particulaire, mg/L")+
  theme_minimal(base_size = 15)

```




# Method - which relation MES-POC to choose?

Objectif: construire la relation MES-POC pour pouvoir reconstruire la chronique de POC à partir de la chronique de MES. Cette relation prend la forme de $POC\% = a*MES^b + c$.

## Test : should we fit with distinct events ?

Que se passe-t-il si on n'effectue pas le fit avec tous les évènements mesurés ?

### Fit par série

Quelle est la différente de fit si on effectue le fit MES-POC sur chacun des évènements analysées (crue, chasse, suivi)?

```{r fit-by-event, eval = T}
name_crues <- subset(poc_isere, !is.na(name) & name != "DOC 2011") %>% pull(name) %>% unique()
mes_for_fit <- poc_isere$mes_for_fit

for(i in name_crues){
  df <- poc_isere
  dfi <- subset(df, name == i &!is.na(poc_percent))
  
  dfi$tail <- dfi[order(dfi$mes_mg.L, decreasing = T),] %>% pull(poc_percent) %>% head(dim(dfi)[1]/10) %>% median() # 10% of poc_percent corresponding to the max cmes
  
  a_i <- dfi$poc_percent %>% max()
  b_i <- - dfi$tail[1]/2
    
  fiti <-  tryCatch(
    nls(poc_percent ~ a * mes_for_fit^b + tail, data = dfi, start = list(a = a_i, b = b_i)),
    error = function(e) {lm(poc_percent ~ mes_for_fit, data = dfi)}
  )
  
  if(class(fiti)=="nls"){
    coef1 <- coef(fiti)[1]
    coef2 <- coef(fiti)[2]
    formula_fiti <- paste("NLS : POC =", round(coef1,2), "* MES (mg/L) ^", round(coef2,2), "+", round(dfi$tail[1],2))
  } else {
    coef1 <- coef(fiti)[1]
    coef2 <- coef(fiti)[2]
    formula_fiti <- paste("LM : POC =", format(coef2, scientific = T, digits = 2), "* MES (mg/L) +", round(coef1))
 }

  df$poc_percent_fiti <- predict(fiti, newdata = df)
  
 g <- ggplot(subset(df, name ==i), aes(x = mes_for_fit))+
  geom_point(aes(y = poc_percent, col = "measured", shape = "measured"), size = 2)+
  geom_point(aes(y = poc_percent_fiti, col = "fitted only with this event", shape = "fitted only with this event"), size = 2)+
#  geom_point(aes(y = poc_nls_fitted, col = "fitted with all events", shape = "fitted with all events"), size = 2)+
  labs(title = i, x = "MES, mg.L", y = "POC, %", col = "", shape = "")+
  scale_color_manual(values = c("darkblue","hotpink4","lightblue"))+
  geom_abline(slope = 0, intercept = dfi$tail[1], col = "darkred")+
  annotate(geom = "label", label = formula_fiti, x = Inf, y = Inf, hjust = 1.1, vjust = 1.1)+
  theme_minimal()+
  theme(legend.position = "bottom")
  
 print(g)
}

```

### All but one fit

```{r leave-one-out-event-to-fit-the-last, eval = T}
name_crues <- subset(poc_isere, !is.na(name) & name != "DOC 2011") %>% pull(name) %>% unique()

for(i in name_crues){
  df <- poc_isere
  dfi <- subset(df, name != i &!is.na(poc_percent))
  
  dfi$tail <- dfi[order(dfi$mes_mg.L, decreasing = T),] %>% pull(poc_percent) %>% head(dim(dfi)[1]/10) %>% median() # 10% of poc_percent corresponding to the max cmes
  
  a_i <- dfi$poc_percent %>% max()
  b_i <- - dfi$tail[1]/2
    
  fiti <-  tryCatch(
    nls(poc_percent ~ a * mes_for_fit^b + tail, data = dfi, start = list(a = a_i, b = b_i)),
    error = function(e) {lm(poc_percent ~ mes_mg.L, data = dfi)}
  )
  
  if(class(fiti)=="nls"){
    coef1 <- coef(fiti)[1]
    coef2 <- coef(fiti)[2]
    formula_fiti <- paste("NLS : POC =", round(coef1,2), "* MES (mg/L) ^", round(coef2,2), "+", round(dfi$tail[1],2))
  } else {
    coef1 <- coef(fiti)[1]
    coef2 <- coef(fiti)[2]
    formula_fiti <- paste("LM : POC =", format(coef2, scientific = T, digits = 2), "* MES (mg/L) +", round(coef1))
 }

  df$poc_percent_fiti <- predict(fiti, newdata = df)
  
 g <- ggplot(subset(df, name == i), aes(x = mes_for_fit))+
  geom_point(aes(y = poc_percent, col = "measured"))+
  geom_point(aes(y = poc_percent_fiti, col = "fitted with all events except this one"))+
#  geom_point(aes(y = poc_nls_fitted, col = "fitted with all events"))+
  labs(title = i, x = "MES, mg.L", y = "POC, %", col = "")+
  scale_color_manual(values = c("darkblue","hotpink4","lightblue"))+
  geom_abline(slope = 0, intercept = dfi$tail[1], col = "darkred")+
  annotate(geom = "label", label = formula_fiti, x = Inf, y = Inf, hjust = 1.1, vjust = 1.1)+
  theme_minimal()+
  theme(legend.position = "bottom")
  
 print(g)
}
```




## Powerlaw

### NLS

#### bootstrap with nlsBoot

```{r fit-poc-mes-nls}

# find asymptotic value : arbitrarily decide that it corresponds to the median of the 10% of poc_percent corresponding to the 10% of highest MES values.
aspt_value <- poc_isere[order(poc_isere$cmes_g.L, decreasing = T),] %>% pull(poc_prop) %>% head(dim(poc_isere)[1]/10) %>% median() 
poc_isere$aspt <- aspt_value


#fit nls
pocfit <- nls(
  poc_prop ~ a * mes_for_fit^b + aspt,
  data = poc_isere,
  start = list(a = 1, b = -0.5)
)

sigma_poc <- summary(pocfit)$sigma

# predicted values (from original data)
poc_isere$poc_nls_fitted <- predict(pocfit, poc_isere)
poc_isere$poc_nls_resid <- residuals(pocfit)

formula_pocfit <- paste("NLS:", round(coef(pocfit)[1],3), "x MES ^", round(coef(pocfit)[2],3), "+", round(aspt_value, 3))
```


#### wild bootstrap

```{r nls-wild-bootstrap}

n_boot <- 1000
n_obs <- nrow(poc_isere)

coefs_wboot_nls <- matrix(NA, nrow = n_boot, ncol = 2, dimnames = list(NULL, c("a","b")))


for(i in seq_len(n_boot)){
  
  weights <- sample(c(-1,1), size = length(residuals(pocfit)), replace = T)
  resid_wboot <- residuals(pocfit) * weights
  
  y_wboot <- fitted(pocfit) + resid_wboot
  
  df_wboot <- poc_isere %>% mutate(poc_prop = y_wboot)
  
  tryCatch(
    {pocfit_wb <- nls(
      poc_prop~a*mes_for_fit^b+aspt,
      data = df_wboot,
      start = coef(pocfit))
    coefs_wboot_nls[i,] <- coef(pocfit_wb)}, 
    error = function(e) NULL) 
}

coefs_wboot_nls <- na.omit(coefs_wboot_nls)
length(coefs_wboot_nls)
apply(coefs_wboot_nls, 2, quantile, probs = c(0.025, 0.975)) #ic coef


ggplot(as.data.frame(coefs_wboot_nls))+
  geom_point(aes(x = a, y = b))+
  theme_minimal()+
  theme(legend.position = "none")


fitted_wboot_nls <- apply(coefs_wboot_nls, 1, function(p){p["a"] * mes_for_fit^p["b"] + aspt_value}) # les MC worlds sont en colonne

fitted_wboot_nls_ic <- apply(fitted_wboot_nls, 1, quantile,
                 probs = c(0.025, 0.5, 0.975), na.rm = TRUE)
fitted_wboot_nls_mean <- apply(fitted_wboot_nls, 1, mean)

poc_isere_wboot_nls <- poc_isere %>% mutate(poc_fitted = fitted_wboot_nls_mean, upr = fitted_wboot_nls_ic[3, ], lwr = fitted_wboot_nls_ic[1,])

ggplot(poc_isere_wboot_nls)+
  geom_point(aes(x=mes_for_fit, y = poc_prop, col = "measured", shape = "measured"))+ 
  geom_point(aes(x=mes_for_fit, y = poc_fitted, col = "fitted", shape = "fitted"))+ 
  geom_ribbon(aes(x = mes_for_fit, ymin = lwr, ymax = upr), fill = "gray80", alpha = 0.5)+
  geom_abline(slope = 0, intercept = aspt_value, col = "darkred")+
  annotate(geom = "label", label = formula_pocfit, x = Inf, y = Inf, hjust = 1.1, vjust = 1.1)+
  scale_color_manual(values = c("darkblue", "lightblue"))+
  labs(x = "MES, mg/L", y = "POC, %", colour = "", shape = "", title = "POC% measured and fitted vs MES measured",subtitle = "Confidence interval in grey")+
  theme_minimal()

ggplot(poc_isere_wboot_nls, aes(x=poc_prop))+
  geom_point(aes(y=poc_fitted), col = "darkblue")+ 
  geom_errorbar(aes(ymin = lwr, ymax = upr), fill = "gray80", alpha = 0.5)+
  geom_abline(slope = 1, intercept = 0, col = "darkred")+
  annotate(geom = "label", label = formula_pocfit, x = Inf, y = Inf, hjust = 1.1, vjust = 1.1)+
  labs(x = "POC measured", y = "POC fitted", colour = "", shape = "", title = "POC fitted vs measured",subtitle = "Confidence interval in grey")+
  theme_minimal()
```

#### NLS extention to Isère

```{r pred-isere-nls}
isere$mes_for_fit <- isere$cmes_g.L * 1e3 
with(isere, sum(mes_for_fit == 0 | is.na(mes_for_fit), na.rm = T)) # 144 -> removed from df because model unstable with zero (when 0^(-b))

isere_for_nls <- isere %>% filter(mes_for_fit != 0 & !is.na(mes_for_fit))

isere_for_nls$poc_prop <- isere_for_nls$poc_percent / 100
isere_for_nls$aspt <- aspt_value

nrow_isere <- nrow(isere_for_nls)
nrow_boot <- nrow(coefs_wboot_nls) # number of bootstrap for the NLS coefficients

# predict POC pour mes > 0
isere_for_nls$poc_fitted <- predict(pocfit, newdata = isere_for_nls) 


# Prediction interval

## Uncertainty on MES
poc_isere$cmes_mg.L <- poc_isere$cmes_g.L * 1000
fit_cmes <- lm(mes_mg.L~cmes_mg.L, data = poc_isere)
summary(fit_cmes)

mes_u <- summary(fit_cmes)$coefficients[4]

mes_mat_nls <- matrix(NA_real_, nrow = nrow_boot, ncol = nrow_isere)

for(i in 1:nrow_boot){
  mes_mat_nls[i,] <-rnorm(nrow_isere, mean = isere_for_nls$mes_for_fit, sd = mes_u) # chaque colonne de la matrice correspond à une observation de MES
}


## model function 
f <- function(x, a, b){
  a * x ^ b + aspt_value
}

## paramètres de variance
theta_nls <- as.numeric(coef(pocfit$modelStruct$varStruct, unconstrained = F))
sigma_nls <- summary(pocfit)$sigma


### Matrice de prédictions, sans bruit


mu_nls <- matrix(NA_real_, nrow = nrow_boot, ncol = nrow_isere)
for(i in 1:nrow_boot){
   mu_nls[i,] <- with(as.list(coefs_wboot_nls[i,]), # listing the coefficients allows to have 2 named numbers to be used in the function
                      f(mes_mat_nls[i, ], a, b))
}


isere_for_nls$poc_var_mean <- apply(mu_nls, 2, var) # variance of fit parameters + MES 

# adds noise
# noise_mat <- matrix(NA_real_, nrow = nrow_boot, ncol = nrow_isere)
# sigma_mat <- sigma_hat * abs(mu_nls)^theta

noise_mat_nls <- matrix(rnorm(nrow_boot*nrow_isere, mean = 0, sd = sigma_nls), nrow = nrow_boot, ncol = nrow_isere)

pred_nls <- mu_nls + noise_mat_nls

#pred_nls <- pmin(pmax(pred_nls, 0), 1) # clampe pred_nls pour éviter les intervalles de prédiction en dessous de zéro

### computes variance, y-wise
isere_for_nls$poc_var_tot <- apply(pred_nls, 2, var) # total variance per prediction, for prediction total uncertainty

## computes prediction interval 
pi <- t(
  apply(pred_nls, 2, quantile, probs = c(0.025, 0.975), na.rm = T)
)

colnames(pi) <- c("lower", "upper")

boot_pred_nls <- colMeans(pred_nls, na.rm = T)

## insert in isere_for_nls

isere_for_nls <- isere_for_nls %>% mutate(poc_boot_pred = boot_pred_nls,
                          poc_pred_lower = pi[,1],
                          poc_pred_upper = pi[,2])

# plot

ggplot(isere_for_nls, aes(x = mes_for_fit))+
  geom_line(aes(y = poc_pred_lower, ymax = poc_pred_upper), col = "black")+
  geom_line(aes(y = poc_pred_upper), col = "black")+
  geom_point(aes(y = poc_prop, col = "measured"), alpha = 0.5)+
  geom_point(aes(y = poc_fitted, col = "fitted with all events"), size = 2)+
  geom_point(aes(y = poc_boot_pred, col ="poc_boot_pred"), alpha = 0.5, size = 1)+
  labs(x = "MES, mg.L", y = "POC, %", col = "")+
  scale_color_manual(values = c("darkblue","gray50","lightblue"))+
  geom_abline(slope = 0, intercept = aspt_value, col = "darkred")+
  annotate(geom = "label", label = formula_pocfit, x = Inf, y = Inf, hjust = 1.1, vjust = 1.1)+
  labs(x = "MES, mg/L", y = "POC,prop", colour = "", shape = "", title = "POC predicted from MES",subtitle = "Prediction interval in grey")+
  theme_minimal()+
  theme(legend.position = "bottom")+
  ylim(-0.05,0.1)


ggplot(isere_for_nls, aes(x = mes_for_fit))+
  geom_line(aes(y = poc_pred_lower, ymax = poc_pred_upper), col = "black")+
  geom_line(aes(y = poc_pred_upper), col = "black")+
  geom_point(aes(y = poc_prop, col = "measured"), alpha = 0.5)+
  geom_point(aes(y = poc_fitted, col = "fitted with all events"), size = 2)+
  geom_point(aes(y = poc_boot_pred, col ="poc_boot_pred"), alpha = 0.5, size = 1)+
  labs(x = "MES, mg.L", y = "POC, %", col = "")+
  scale_color_manual(values = c("darkblue","gray50","lightblue"))+
  scale_x_continuous(trans = "log")+
 # scale_y_continuous(trans = "log")+ # useless
  geom_abline(slope = 0, intercept = aspt_value, col = "darkred")+
  annotate(geom = "label", label = formula_pocfit, x = Inf, y = Inf, hjust = 1.1, vjust = 1.1)+
  labs(x = "MES, mg/L", y = "POC,prop", colour = "", shape = "", title = "POC predicted from MES",subtitle = "Prediction interval in grey")+
  theme_minimal()+
  theme(legend.position = "bottom")+
  ylim(-0.05,0.1)
```


### GNLS

```{r fit-poc-mes-gnls}

# find asymptotic value : arbitrarily decide that it corresponds to the median of the 10% of poc_percent corresponding to the 10% of highest MES values.
aspt_value <- poc_isere[order(poc_isere$cmes_g.L, decreasing = T),] %>% pull(poc_prop) %>% head(dim(poc_isere)[1]/10) %>% median() 
poc_isere$aspt <- aspt_value

library(nlme)

# on utilise les valeurs de pocfit comme coefficients initiaux

pocfitg <- gnls(
  poc_prop ~ a*mes_for_fit^b + aspt,
  data = select(poc_isere, c(mes_for_fit, poc_prop, aspt)),
  start = list(a = 0.1, b = 0.5),
  weights = varPower(value = 1, form = ~ fitted(.)),
  control = gnlsControl(nlsTol = 1e-3, tolerance = 1e-4)
)

formula_pocfitg <- paste("GNLS:", round(coef(pocfitg)[1], 3), "x MES ^", round(coef(pocfitg)[2],3), "+", round(aspt_value, 3), sep = "")
```


#### GNLS bootstrap

```{r intervalles-de-confiance-bootstrap}
n_boot <- 1000
n_obs <- nrow(poc_isere)

coefs_boot <- matrix(NA, nrow = n_boot, ncol = 2, dimnames = list(NULL, c("a","b")))
                     

for(i in seq_len(n_boot)){
  
  idx_boot <- sample(n_obs, replace = T)
  df_boot <- poc_isere[idx_boot, c("mes_for_fit","poc_prop","aspt")]
  
  tryCatch(
    {fit_init <- nls(
      poc_prop ~ a * mes_for_fit^b + aspt,
      data = df_boot,
      start = coef(pocfitg))
      # fit init is necessary to find the correct starting values for gnls. Otherwise, too much convergence result in extreme values in a and b

      pocfit_bg <- gnls(
      poc_prop~a*mes_for_fit^b+aspt,
      data = df_boot,
      start = coef(fit_init),
      weights = varPower(form = ~fitted(.)),
      control = gnlsControl(nlsTol = 1e-3, tolerance = 1e-4, maxIter = 200))
      
      coefs_boot[i,] <- coef(pocfit_bg)
      }, 
    error = function(e) NULL) 
}

coefs_boot <- na.omit(coefs_boot)
length(coefs_boot)
apply(coefs_boot, 2, quantile, probs = c(0.025, 0.975)) #ic coef



ggplot(as.data.frame(coefs_boot))+
  geom_point(aes(x = a, y = b))+
  theme_minimal()+
  theme(legend.position = "none")


fitted_boot <- apply(coefs_boot, 1, function(p){p["a"] * mes_for_fit^p["b"] + aspt_value}) # les MC worlds sont en colonne

fitted_boot_ic <- apply(fitted_boot, 1, quantile,
                 probs = c(0.025, 0.5, 0.975), na.rm = TRUE)
fitted_boot_mean <- apply(fitted_boot, 1, mean)

poc_isere_boot <- poc_isere %>% mutate(poc_fitted = fitted_boot_mean, upr = fitted_boot_ic[3, ], lwr = fitted_boot_ic[1,])

ggplot(poc_isere_boot)+
  geom_point(aes(x=mes_for_fit, y = poc_prop, col = "measured", shape = "measured"))+ 
  geom_point(aes(x=mes_for_fit, y = poc_fitted, col = "fitted", shape = "fitted"))+ 
  geom_ribbon(aes(x = mes_for_fit, ymin = lwr, ymax = upr), fill = "gray80", alpha = 0.5)+
  geom_abline(slope = 0, intercept = aspt_value, col = "darkred")+
  annotate(geom = "label", label = formula_pocfitg, x = Inf, y = Inf, hjust = 1.1, vjust = 1.1)+
  scale_color_manual(values = c("darkblue", "lightblue"))+
  labs(x = "MES, mg/L", y = "POC, %", colour = "", shape = "", title = "POC% measured and fitted vs MES measured",subtitle = "Confidence interval in grey")+
  theme_minimal()

ggplot(poc_isere_boot, aes(x=poc_prop))+
  geom_point(aes(y=poc_fitted), col = "darkblue")+ 
  geom_errorbar(aes(ymin = lwr, ymax = upr), fill = "gray80", alpha = 0.5)+
  geom_abline(slope = 1, intercept = 0, col = "darkred")+
  annotate(geom = "label", label = formula_pocfitg, x = Inf, y = Inf, hjust = 1.1, vjust = 1.1)+
  labs(x = "POC measured", y = "POC fitted", colour = "", shape = "", title = "POC fitted vs measured",subtitle = "Confidence interval in grey")+
  theme_minimal()
```



```{r comparaison-nls-gnls}

par(mfrow = c(1, 2))

# nls : les résidus montrent un pattern en éventail
plot(fitted(pocfit), residuals(pocfit),
     main = "Résidus nls (non pondérés)",
     xlab = "Fitted", ylab = "Résidus")
abline(h = 0, col = "red")

# gnls : les résidus normalisés sont homoscédastiques
plot(fitted(pocfitg), residuals(pocfitg, type = "normalized"),
     main = "Résidus gnls (normalisés)",
     xlab = "Fitted", ylab = "Résidus normalisés")
abline(h = 0, col = "red")

```

#### GNLS extension to Isere

```{r pred-isere-gnls, cache.lazy = F}
isere$mes_for_fit <- isere$cmes_g.L * 1e3 
with(isere, sum(mes_for_fit == 0 | is.na(mes_for_fit), na.rm = T)) # 144 -> removed from df because model unstable with zero (when 0^(-b))

isere_for_gnls <- isere %>% filter(mes_for_fit != 0 & !is.na(mes_for_fit))

isere_for_gnls$poc_prop <- isere_for_gnls$poc_percent / 100
isere_for_gnls$aspt <- aspt_value

nrow_isere <- nrow(isere_for_gnls)
nrow_boot <- nrow(coefs_boot)

# predict POC pour mes > 0
isere_for_gnls$poc_fitted <- predict(pocfitg, newdata = isere_for_gnls, na.action = na.pass) 


# Prediction interval

## Uncertainty on MES
poc_isere$cmes_mg.L <- poc_isere$cmes_g.L * 1000
fit_cmes <- lm(mes_mg.L~cmes_mg.L, data = poc_isere)
summary(fit_cmes)

mes_u <- summary(fit_cmes)$coefficients[4]

mes_mat_gnls <- matrix(NA_real_, nrow = nrow_boot, ncol = nrow_isere)

for(i in 1:nrow(isere_for_gnls)){
  mes_mat_gnls[,i] <-rnorm(nrow_boot, mean = isere_for_gnls$mes_for_fit[i], sd = mes_u) # chaque colonne de la matrice correspond à une observation de MES. Exactly same code as when working on lines.
}


## model function 
f <- function(x, a, b){
  a * x ^ b + aspt_value
}

## paramètres de variance
theta <- as.numeric(coef(pocfitg$modelStruct$varStruct, unconstrained = F))
sigma_gnls <- pocfitg$sigma


### Matrice de prédictions, sans bruit


mu_gnls <- matrix(NA_real_, nrow = nrow_boot, ncol = nrow_isere)
for(i in 1:nrow_boot){
   mu_gnls[i,] <- with(as.list(coefs_boot[i,]), # listing the coefficients allows to have 2 named numbers to be used in the function
                      f(mes_mat_gnls[i, ], a, b))
}


isere_for_gnls$poc_var_mean <- apply(mu_nls, 2, var) # variance of fit parameters + MES 

# adds noise
noise_mat_gnls <- matrix(NA_real_, nrow = nrow_boot, ncol = nrow_isere)
sigma_mat_gnls <- sigma_gnls * abs(mu_gnls)^theta

noise_mat_gnls <- matrix(rnorm(nrow_boot*nrow_isere, mean = 0, sd = 1), nrow = nrow_boot, ncol = nrow_isere)
noise_mat_gnls <- noise_mat_gnls*sigma_mat_gnls

pred_gnls <- mu_gnls + noise_mat_gnls

pred_gnls <- pmin(pmax(pred_gnls, 0), 1) # clampe pred_nls pour éviter les intervalles de prédiction en dessous de zéro

### computes variance, y-wise
isere_for_gnls$poc_var_tot <- apply(pred_gnls, 2, var) # total variance per prediction, for prediction total uncertainty

## computes prediction interval 
pi <- t(
  apply(pred_gnls, 2, quantile, probs = c(0.025, 0.975), na.rm = T)
)

colnames(pi) <- c("lower", "upper")

boot_pred_gnls <- colMeans(pred_gnls, na.rm = T)

## insert in isere_for_gnls

isere_for_gnls <- isere_for_gnls %>% mutate(poc_boot_pred = boot_pred_gnls,
                          poc_pred_lower = pi[,1],
                          poc_pred_upper = pi[,2])

# plot

ggplot(isere_for_gnls, aes(x = mes_for_fit))+
  geom_line(aes(y = poc_pred_lower, ymax = poc_pred_upper), col = "black")+
  geom_line(aes(y = poc_pred_upper), col = "black")+
  geom_point(aes(y = poc_prop, col = "measured"), alpha = 0.5)+
  geom_point(aes(y = poc_fitted, col = "fitted with all events"), size = 2)+
  geom_point(aes(y = poc_boot_pred, col ="poc_boot_pred"), alpha = 0.5, size = 0.5)+
  labs(x = "MES, mg.L", y = "POC, %", col = "")+
  scale_color_manual(values = c("darkblue","gray50","lightblue"))+
  geom_abline(slope = 0, intercept = aspt_value, col = "darkred")+
  annotate(geom = "label", label = formula_pocfitg, x = Inf, y = Inf, hjust = 1.1, vjust = 1.1)+
  labs(x = "MES, mg/L", y = "POC,prop", colour = "", shape = "", title = "POC predicted from MES",subtitle = "Prediction interval in grey")+
  theme_minimal()+
  theme(legend.position = "bottom")+
  ylim(-0.05,0.1)

ggplot(isere_for_gnls, aes(x = mes_for_fit))+
  geom_line(aes(y = poc_pred_lower, ymax = poc_pred_upper), col = "black")+
  geom_line(aes(y = poc_pred_upper), col = "black")+
  geom_point(aes(y = poc_prop, col = "measured"), alpha = 0.5)+
  geom_point(aes(y = poc_fitted, col = "fitted with all events"), size = 2)+
  geom_point(aes(y = poc_boot_pred, col ="poc_boot_pred"), alpha = 0.5, size = 0.5)+
  labs(x = "MES, mg.L", y = "POC, %", col = "")+
  scale_color_manual(values = c("darkblue","gray50","lightblue"))+
  scale_x_continuous(trans = "log", breaks = c(1,10,100,1000))+
  geom_abline(slope = 0, intercept = aspt_value, col = "darkred")+
  annotate(geom = "label", label = formula_pocfitg, x = Inf, y = Inf, hjust = 1.1, vjust = 1.1)+
  labs(x = "MES, mg/L", y = "POC,prop", colour = "", shape = "", title = "POC predicted from MES",subtitle = "Prediction interval in grey")+
  theme_minimal()+
  theme(legend.position = "bottom")
```

# Reference annual and interannual fluxes

## Annual flux based on gnls model + Monte Carlo


```{r annual-flux-reference}
# create matrix of q
q_u = 0.1 # Cédric - avis d'expert NOT WORKING; has to be 10% of the Q measured, not ALWAYS 0.1!

q_meas <- matrix(isere_for_gnls$q_m3.s, nrow = nrow_boot, ncol = nrow_isere, byrow = T) # repeats nrow_boot times the vector isere_for_gnls$q_m3.s

q_noise <- matrix(rnorm(nrow_boot*nrow_isere, mean = 0, sd = q_u), nrow = nrow_boot, ncol = nrow_isere) # creates a noise in percent (proportion), between 0 and 10%

q_mat <- q_meas * (1 + q_noise) # final value of q, with noise


# compute flux
period_mat <- matrix(isere_for_gnls$period, nrow = nrow_boot, ncol = nrow_isere, byrow = T)

flux_kg.s_mat <- pred_gnls*mes_mat_gnls*q_mat*1e-2*period_mat #pred_gnls * mes_mat : poc in mg/L; q_mat converted from m3/s to L/s. We consider no uncertainty on period. 

index_years <- sapply(unique(isere_for_gnls$year), function(y){which(isere_for_gnls$year == y)}) # list of indices corresponding to each year

annual_flux_kg.y <- sapply(index_years, function(idx){apply(flux_kg.s_mat[,idx], 1, sum, na.rm = T)}) # sum of fluxes per year, for each iteration of the bootstrap. Result is a matrix with nrow_boot rows and 19 columns (1 per year)

annual_flux_ci <- apply(annual_flux_kg.y, 2, quantile, probs = c(0.025, 0.5, 0.975), na.rm = T) # confidence interval for annual fluxes, per year. 3 lignes, 19 columns
annual_flux_mean <- colMeans(annual_flux_kg.y, na.rm = T) # mean annual flux per year. 1 vector

annual_flux_sd <- apply(annual_flux_kg.y, 2, sd, na.rm = T) # standard deviation of annual flux per year. Is just an estimate of goodness of mean, not as good as than the confidence interval. 
 

annual_flux_df <- data.frame(year = unique(isere_for_gnls$year), 
                        annual_flux_mean = annual_flux_mean, 
                        annual_flux_variability = rep(NA, 19), # no physical sense in calculating "annual variability". Would be standard deviation of annual flux. But we prefer to show the prediction interval.
                        annual_flux_ci_lower = annual_flux_ci[1,], 
                        annual_flux_ci_upper = annual_flux_ci[3,])

ggplot(annual_flux_df)+
  geom_col(aes(x=year, y = annual_flux_mean), fill = "lightblue")+
  geom_errorbar(aes(x = year, ymin = annual_flux_ci_lower, ymax = annual_flux_ci_upper), width = 0.2)+
  theme_minimal()
```

## Interannual flux

```{r interannual-flux-reference}
interannual_flux_kg.y <- rowMeans(annual_flux_kg.y, na.rm = T) # mean interannual flux per iteration of the bootstrap
interannual_flux_ci <- quantile(interannual_flux_kg.y, probs = c(0.025, 0.5, 0.975), na.rm = T) # prediction interval
interannual_flux_mean <- mean(interannual_flux_kg.y, na.rm = T) # mean interannual flux
interannual_flux_variability <- sd(annual_flux_mean, na.rm = T) # standard deviation of interannual flux per year

interannual_flux_df <- data.frame(year = "interannual", annual_flux_mean = interannual_flux_mean, 
                                  annual_flux_variability = interannual_flux_variability,
                        annual_flux_ci_lower = interannual_flux_ci[1], 
                        annual_flux_ci_upper = interannual_flux_ci[3])

total_flux_df <- rbind(annual_flux_df, interannual_flux_df)
total_flux_df$group <- c(rep("annual", length(unique(isere_for_gnls$year))), "interannual")

ggplot(total_flux_df)+
  geom_col(aes(x=year, y = annual_flux_mean, fill = group))+
    geom_errorbar(aes(x = year, ymin = annual_flux_ci_lower, ymax = annual_flux_ci_upper, col = "prediction interval"), width = 0.3, size = 0.8)+
  geom_errorbar(aes(x = year, ymin = annual_flux_mean - annual_flux_variability, ymax = annual_flux_mean + annual_flux_variability, col = "interannual variability"), width = 0.2, size = 0.8, linetype = 2)+
  scale_fill_manual(values = c("annual" = "lightblue", "interannual" = "indianred"))+
  scale_color_manual(values = c("prediction interval" = "darkblue", "interannual variability" = "darkred"), name = "")+
   labs(x = "Year", y = "Flux (kg/year)", fill = "")+
  theme_minimal()+
  theme(axis.text.x = element_text(angle = 45, hjust = 1), legend.position = "bottom")
```
# Time steps

```{r group-by-day}
isere_for_gnls$day <- isere_for_gnls$DateHeure %>% format("%Y-%m-%d")
index_day <- sapply(unique(isere_for_gnls$day), function(y){which(isere_for_gnls$day == y)}) # list of indices corresponding to each day

mean_flux_day <- sapply(index_day, function(idx){apply(flux_kg.s_mat[,idx], 1, sum, na.rm = T)}) # sum of fluxes per day, for each iteration of the bootstrap. Result is a matrix with nrow_boot rows and many columns (1 per day)






q_day <- sapply(index_day, function(idx){mean(q_mat[,idx], na.rm = T)}) # mean discharge per day
poc_day <- sapply(index_day, function(idx){mean(pred_gnls[,idx], na.rm = T)}) # mean POC per day
mes_day <- sapply(index_day, function(idx){mean(mes_mat_gnls[,idx], na.rm = T)}) # mean MES per day

flux_kg.s_day <- poc_day * mes_day * q_day * 1e-2 # flux in kg/s per day, for each iteration of the bootstrap. Result is a vector with length equal to the number of days

annual_flux_day <- sapply(index_day, function(idx){sum(flux_kg.s_mat[,idx], na.rm = T)}) # sum of fluxes per day, for each iteration of the bootstrap. Result is a vector with length equal to the number of days


```


# Estimation of annual POC fluxes, time steps, without uncertainty

```{r time-steps}
isere$day <- isere$DateHeure %>% format("%Y-%m-%d")
isere$week <- week(isere$DateHeure)
isere$month <- month(isere$DateHeure)
```


## Daily means

```{r dayly-flux-poc-fitted, eval = T}
isere_day <- isere %>% group_by(day) %>% summarise(q_m3.s = mean(q_m3.s, na.rm = T), mes_for_fit = mean(mes_for_fit, na.rm = T), mes_for_fit_sd = sd(mes_for_fit, na.rm = T), poc_fitted = mean(poc_fitted, na.rm = T), year = first(year))


isere_day$fpoc_kg.d <- with(isere_day, q_m3.s * 1e3 * (mes_for_fit * poc_fitted * 1e-2) * 1e-6) # discharge converted from m3/s to L/h; fPOC is obtained in mg/L/s

day_fluxes_fitted <- isere_day %>% 
                  group_by(year) %>% 
                    summarise(fpoc_kg.year = sum(fpoc_kg.d * 24*60*60, na.rm = T),
                              mean_annual_q = mean(q_m3.s, na.rm = T),
                              nb_datapoints = sum(!is.na(poc_fitted)))

knitr::kable(day_fluxes_fitted)

n <- 30

ggplot(day_fluxes_fitted, aes(x = year))+
  geom_col(aes(y = fpoc_kg.year/5570), fill = "palegreen4")+
  geom_line(aes(y = mean_annual_q*n))+
  scale_y_continuous(
    name = "Flux de POC, kg/year/km2",
    sec.axis = sec_axis(~./n, name = "Débit moyen annuel, m3/s"))+
  labs(x = "", y = "Flux de POC, kg/year/km2")+
  theme_minimal()
```

A FAIRE : intégrer l'incertitude due au moyennage par jour (sd?)

```{r daily-mean-with-uncertainty}
N_MC <- 1000

q_u <- 0.1 # from Cedric

poc_isere$cmes_mg.L <- poc_isere$cmes_g.L * 1000
fit_cmes <- lm(mes_mg.L~cmes_mg.L, data = poc_isere)
summary(fit_cmes)

mes_u <- summary(fit_cmes)$coefficients[4]
a_u <- summary(pocfit)$coefficients[3]
b_u <- summary(pocfit)$coefficients[4]

coef_poc <- coef(pocfit)
a_mean <- coef_poc[1]
b_mean <- coef_poc[2]

isere$year <- as.factor(isere$year)
list_isere <-  isere %>% group_split(year)
list_isere <- lapply(list_isere, as.data.frame)
list_isere_mc <- list()

list_isere_mc <- vector("list", length(list_isere))

for (j in seq_along(list_isere)) {

  df <- list_isere[[j]]
  n  <- nrow(df)

    # matrice [temps x MC]
  fpoc_mc <- matrix(NA_real_, nrow = n, ncol = N_MC)

  for (i in seq_len(n)) {

    qn   <- rnorm(N_MC, df$q_m3.s[i], q_u)
    mesn <- rnorm(N_MC, df$mes_for_fit[i], mes_u)
    an   <- rnorm(N_MC, a_mean, a_u)
    bn   <- rnorm(N_MC, b_mean, b_u)

    pocn <- an * mesn^bn + tail_value

    fpoc_mc[i, ] <-
      qn * 1e3 *
      (mesn * pocn * 1e-2) *
      1e-6 *
      df$period[i]
  }

  list_isere_mc[[j]] <- fpoc_mc

  # stats instantanées 
  list_isere[[j]]$fpoc_mc_mean <- rowMeans(fpoc_mc)
  list_isere[[j]]$fpoc_mc_sd   <- apply(fpoc_mc, 1, sd)
}
```


## Weekly means

```{r weekly-flux-poc-fitted, eval = T}
isere_week <- isere %>% group_by(week,year) %>% summarise(q_m3.s = mean(q_m3.s, na.rm = T), mes_for_fit = mean(mes_for_fit, na.rm = T), poc_fitted = mean(poc_fitted, na.rm = T))


isere_week$fpoc_kg.d <- with(isere_week, q_m3.s * 1e3 * (mes_for_fit * poc_fitted * 1e-2) * 1e-6) # discharge converted from m3/s to L/h; fPOC is obtained in mg/L/s

week_fluxes_fitted <- isere_week %>% 
                  group_by(year) %>% 
                    summarise(fpoc_kg.year = sum(fpoc_kg.d * 7*24*60*60, na.rm = T),
                              mean_annual_q = mean(q_m3.s, na.rm = T),
                              nb_datapoints = sum(!is.na(poc_fitted)))

knitr::kable(week_fluxes_fitted)

n <- 30

ggplot(week_fluxes_fitted, aes(x = year))+
  geom_col(aes(y = fpoc_kg.year/5570), fill = "palegreen4")+
  geom_line(aes(y = mean_annual_q*n))+
  scale_y_continuous(
    name = "Flux de POC, kg/year/km2",
    sec.axis = sec_axis(~./n, name = "Débit moyen annuel, m3/s"))+
  labs(x = "", y = "Flux de POC, kg/year/km2")+
  theme_minimal()

```

## Monthly means

```{r monthly-flux-poc-fitted, eval = T}
isere_month <- isere %>% group_by(month,year) %>% summarise(q_m3.s = mean(q_m3.s, na.rm = T), mes_for_fit = mean(mes_for_fit, na.rm = T), poc_fitted = mean(poc_fitted, na.rm = T))


isere_month$fpoc_kg.d <- with(isere_month, q_m3.s * 1e3 * (mes_for_fit * poc_fitted * 1e-2) * 1e-6) # discharge converted from m3/s to L/h; fPOC is obtained in mg/L/s

month_fluxes_fitted <- isere_month %>% 
                  group_by(year) %>% 
                    summarise(fpoc_kg.year = sum(fpoc_kg.d * 30*24*60*60, na.rm = T),
                              mean_annual_q = mean(q_m3.s, na.rm = T),
                              nb_datapoints = sum(!is.na(poc_fitted)))

knitr::kable(month_fluxes_fitted)

n <- 30

ggplot(month_fluxes_fitted, aes(x = year))+
  geom_col(aes(y = fpoc_kg.year/5570), fill = "palegreen4")+
  geom_line(aes(y = mean_annual_q*n))+
  scale_y_continuous(
    name = "Flux de POC, kg/year/km2",
    sec.axis = sec_axis(~./n, name = "Débit moyen annuel, m3/s"))+
  labs(x = "", y = "Flux de POC, kg/year/km2")+
  theme_minimal()

```

## Compare time steps

```{r compare-time-steps}

yearly_fluxes <- merge(yearly_fluxes_fitted, day_fluxes_fitted, by = "year", suffixes = c("_hourly", "_daily")) %>%
                  merge(week_fluxes_fitted, by = "year") %>%
                    merge(month_fluxes_fitted, by = "year", suffixes = c("_weekly", "_monthly"))
yearly_fluxes$diff_ref_month <- with(yearly_fluxes, (fpoc_kg.year_monthly - fpoc_kg.year_hourly)/fpoc_kg.year_hourly*100)
yearly_fluxes$diff_ref_week <- with(yearly_fluxes, (fpoc_kg.year_weekly - fpoc_kg.year_hourly)/fpoc_kg.year_hourly*100)
yearly_fluxes$diff_ref_day <- with(yearly_fluxes, (fpoc_kg.year_daily - fpoc_kg.year_hourly)/fpoc_kg.year_hourly*100)

knitr::kable(yearly_fluxes)

yearly_fluxes_long <- rbind(mutate(yearly_fluxes_fitted, freq = "1.hourly"), 
                            mutate(day_fluxes_fitted, freq = "2.daily"),
                            mutate(week_fluxes_fitted, freq = "3.weekly"),
                            mutate(month_fluxes_fitted, freq = "4.monthly"))


ggplot(yearly_fluxes_long, aes(x = year))+
  geom_col(aes(y = fpoc_kg.year/5570, fill = freq), stat = "identity", position = "dodge")+  
  scale_fill_manual(values = c("1.hourly" = "darkblue", "2.daily" = "lightblue", "3.weekly" = "palegreen4", "4.monthly" = "honeydew3"))+
  scale_y_continuous(name = "Flux de POC, kg/year/km2")+
  labs(x = "", y = "Flux de POC, kg/year/km2")+
  theme_minimal()+
  theme(legend.position = "bottom")

ggplot(yearly_fluxes, aes(x = year))+
  geom_line(aes(y = diff_ref_month, col = "4.monthly"), size = 2)+
    geom_line(aes(y = diff_ref_week, col = "3.weekly"), size = 2)+ 
    geom_line(aes(y = diff_ref_day, col = "2.daily"), size = 2)+ 
  scale_color_manual(values = c("1.hourly" = "darkblue", "2.daily" = "lightblue", "3.weekly" = "palegreen4", "4.monthly" = "honeydew3"))+
  scale_y_continuous(name = "Différence avec le flux de référence, %")+
  labs(x = "", y = "Flux de POC, kg/year/km2")+
  scale_x_continuous(breaks = c(unique(yearly_fluxes$year)), minor_breaks = NULL)+
  theme_minimal()+
  theme(legend.position = "bottom")

yearly_fluxes_long %>% group_by(freq) %>% summarise(mean_flux = mean(fpoc_kg.year/5570), sd_flux = sd(fpoc_kg.year/5570), mean_diff_ref = mean((fpoc_kg.year - yearly_fluxes_fitted$fpoc_kg.year)/yearly_fluxes_fitted$fpoc_kg.year*100, na.rm = T)) %>% knitr::kable()


```


```{r exit}
knitr::knit_exit()
```



# Archives

```{r yearly-fluxes, eval = F}
crues$year <- year(crues$Date) %>% as.character()

crues$poc_mg.L <- with(crues, MES_mg.L*COP_percent) # CMES converted from mg/L to kg/L, POC obtained in g is converted to mg
crues$fpoc_kg.h <- with(crues, debit_m3.s * 1e3 * poc_mg.L * 3600 * 1e-6) # discharge converted from m3/s to L/h; fPOC is obtained in mg/L/s and converted to kg/h

yearly_fluxes <- crues %>% 
                  group_by(year) %>% 
                    summarise(fpoc_kg.year = sum(fpoc_kg.h*period, na.rm = T), 
                              percent_poc_included = sum(!is.na(fpoc_kg.h))/n()*100,
                              nb_days_sampled = length(unique(Date)),
                              nb_days_sampled_poc = length(unique(Date[!is.na(fpoc_kg.h)])),
                              sum_discharge.year = sum(debit_m3.s, na.rm = T),  # faut-il inclure les débits correspondants à des heures où le POC n'est pas mesuré?
                              mean_discharge.year = mean(debit_m3.s, na.rm = T), 
                              sd_discharge.year = sd(debit_m3.s, na.rm = T),
                              sum_discharge_poc = sum(debit_m3.s[!is.na(fpoc_kg.h)], na.rm = T),
                              mean_discharge_poc = mean(debit_m3.s[!is.na(fpoc_kg.h)], na.rm = T),
                              average_fpoc = mean(fpoc_kg.h, na.rm = T)) 
# discharge is converted from m3/s to L/h before being summed, as in the formula for fpoc

bv <- 5570
  
# fluxes by adding all hourly fluxes, with uncertainty depending on the nb of observations per year
yearly_fluxes$fpoc_kg.year.km2 <- yearly_fluxes$fpoc_kg.year/bv

# fluxes with ponderation method @Nemery2013 citing Walling and Webb 1985
yearly_fluxes$fpoc_ww_kg.year.km2 <- with(yearly_fluxes, fpoc_kg.year/sum_discharge.year*mean_discharge.year) * 24 * 365 / bv

yearly_fluxes$fpoc_wwpoc_kg.year.km2 <- with(yearly_fluxes, fpoc_kg.year/sum_discharge_poc*mean_discharge_poc) * 24 * 365 / bv

# fluxes only average
yearly_fluxes$fpoc_average_kg.y.km2 <- yearly_fluxes$average_fpoc *24*365 / bv

```

```{r figures-flux, eval = F} 
yearly_fluxes %>% dplyr::mutate_if(is.numeric, funs(as.character(signif(., 3)))) %>% knitr::kable() %>% kableExtra::kable_styling()
```

```{r test-2006, eval = F}
t2006 <- crues %>% subset(year == 2006)
t2006

sum(t2006$fpoc_kg.h)
```


```{r compare-fluxes, eval = F}
yearly_fluxes$label <- paste(round(yearly_fluxes$nb_days_sampled,2), "days q\n", round(yearly_fluxes$nb_days_sampled_poc,2), " days poc")
ggplot(yearly_fluxes, aes(x = year))+
  geom_col(aes(y = fpoc_kg.year.km2, fill = "POC flux as sum"), position = position_nudge(-0.2), width = 0.4)+
  geom_col(aes(y = fpoc_ww_kg.year.km2, fill = "POC flux as weigthed"), position = position_nudge(0.2), width = 0.4)+
  geom_label(aes(x = year, y = fpoc_ww_kg.year.km2, label = label), nudge_y = 500, label.size = 0.1)+
  #scale_x_continuous(breaks = c(unique(yearly_fluxes$year)), minor_breaks = NULL)+
  scale_size_continuous(range = c(0.1,10))+
  scale_fill_manual(values = c("palegreen4", "lightblue"))+
  labs(x = "", fill = "", y = "Flux de POC, kg/year/km2")+
  theme_minimal()+
  theme(legend.position = "bottom")

ggplot(yearly_fluxes, aes(x = year))+
  geom_col(aes(y = fpoc_kg.year.km2, fill = "POC flux as sum"), position = position_nudge(-0.2), width = 0.4)+
  #scale_x_continuous(breaks = c(unique(yearly_fluxes$year)), minor_breaks = NULL)+
  scale_size_continuous(range = c(0.1,10))+
  scale_fill_manual(values = c("palegreen4", "lightblue"))+
  labs(x = "", fill = "", y = "Flux de POC, kg/year/km2")+
  theme_minimal()+
  theme(legend.position = "bottom")
```
```{r yf, eval = F}
yf <- yearly_fluxes %>% subset(nb_days_sampled_poc > 10)

yf %>% dplyr::mutate_if(is.numeric, funs(as.character(signif(., 3)))) %>% knitr::kable() %>% kableExtra::kable_styling()
```

```{r compare-fluxes-nona, eval = F}
yf$label <- paste(round(yf$nb_days_sampled,2), "days q\n", round(yf$nb_days_sampled_poc,2), " days poc")
ggplot(yf, aes(x = year))+
  geom_col(aes(y = fpoc_kg.year.km2, fill = "POC flux as sum"), position = position_nudge(-0.2), width = 0.4)+
  geom_col(aes(y = fpoc_ww_kg.year.km2, fill = "POC flux as weigthed"), position = position_nudge(0.2), width = 0.4)+
  geom_label(aes(x = year, y = fpoc_ww_kg.year.km2, label = label), nudge_y = 15000, size = 3)+
 # scale_x_continuous(breaks = c(unique(yearly_fluxes$year)), minor_breaks = NULL)+
  scale_size_continuous(range = c(0.1,10))+
  scale_fill_manual(values = c("palegreen4", "lightblue"))+
  labs(x = "", fill = "", y = "Flux de POC, kg/year/km2")+
  theme_minimal()+
  theme(legend.position = "bottom", text = element_text(size = 10))
```

```{r interrannual-fluxes, eval = F}

mixedfluxes_mean <- with(yf, ifelse(nb_days_sampled_poc < 200, fpoc_ww_kg.year.km2, fpoc_kg.year.km2)) %>% mean()
mixedfluxes_sd <- with(yf, ifelse(nb_days_sampled_poc < 200, fpoc_ww_kg.year.km2, fpoc_kg.year.km2)) %>% sd()

means <- data.frame(
  "Mean FPOC sum, kg/year/m2" = mean(yf$fpoc_kg.year.km2),
  "Sd FPOC sum" = sd(yf$fpoc_kg.year.km2),
  "Mean FPOC weighted, kg/m2/year" = mean(yf$fpoc_ww_kg.year.km2, na.rm = T),
  "Sd FPOC weighted" = sd(yf$fpoc_ww_kg.year.km2, na.rm = T),
  "Mean FPOC mixed" = mixedfluxes_mean,
  "Sd FPOC mixed" = mixedfluxes_sd
)

knitr::kable(t(means), digits = 3) %>% kableExtra::kable_styling()
```


