---
title: "ardeche"
output:
  html_document:
    toc: true
    toc_float: true
    number_sections: true
    code_folding: hide
date: "2026-07-31"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = F, warning = F, error = F, fig.align = "center", collapse = T,
                      cache = T)
```


```{r libraries}
lapply(c("dplyr"), library, character.only = T)
lapply(c("ggplot2","ggpubr"), library, character.only = T)
lapply(c("lubridate"), library, character.only = T)
lapply(c("knitr","kableExtra"), library, character.only = T)
lapply(c("readxl","writexl"), library, character.only = T)
library(here)

```



# Questions

Why so high flux in 2018?
Why so low fluxes in 2022-2023?

# Get data

```{r bv-km2}
bv <- 2258
unit_flux = "kg"
```


```{r load-data-from-excel, message = F}

cmes <- readxl::read_xlsx(path = "ardeche.xlsx", sheet = "CMES", col_types = c("date","numeric","text")) %>% subset(Qualite == "v") %>% mutate(Qualite = NULL)

poc <- readxl::read_xlsx(path = "ardeche.xlsx", sheet = "POC") %>% subset(Qualite == "v") %>% mutate(Qualite = NULL)

poc$poc_timeinterval <- poc$Debut %--% poc$Fin
poc$poc_g.kg <- as.numeric(poc$poc_g.kg)

debit <- readxl::read_xlsx(path = "ardeche.xlsx", sheet = "Debit", col_types = c("date","numeric","numeric")) %>% 
        setNames(c("DateHeure","q_m3.s", "Qualification")) 

na_interval <- poc$Fin[85] %--% poc$Debut[1]  %>% as.character()

debit_timeinterval <- sapply(debit$DateHeure, FUN = function (x){as.character(poc$poc_timeinterval[x >= poc$Debut & x <= poc$Fin])}, simplify = T)
na_timeinterval <- which(lengths(debit_timeinterval) == 0)
debit_timeinterval[na_timeinterval] <- na_interval

debit$poc_timeinterval <- do.call(c, (debit_timeinterval))

ardeche <- merge(debit, cmes, by = "DateHeure", all = T) %>% filter(!is.na(q_m3.s)) %>% merge(poc, by = "poc_timeinterval", all = T) %>% unique()

ardeche <- ardeche %>% arrange(DateHeure) %>% mutate(
  year = year(DateHeure),
  Date = as.Date(DateHeure),
  commondate = as.Date(update(DateHeure, year = 2000)),
  period = as.numeric(difftime(lead(DateHeure), DateHeure, units = "secs")),
  poc_mg.L = poc_g.kg*cmes_mg.L*1e-6,
  q_L.s = q_m3.s * 1e3,
  mes_mg.L = cmes_mg.L)
```


## Visualisation


```{r plot-by-year-poc, fig.dim = c(15,15)}

title <- expression(atop("Series of Q and MES by year"))
plots <- ggarrange(
ggplot(ardeche, aes(x = commondate))+
  geom_point(aes(y = q_m3.s, col = "Débit, m3/s"), alpha = 0.5)+
  scale_x_date(labels = function(x) format(x, "%d-%b"), date_minor_breaks = "1 month", name = "")+
  scale_color_manual(values = c("lightblue"), name = "")+
  facet_grid(rows = vars(year))+
  labs(y = "Débit, m3/s", col = "")+
  theme_bw(base_size = 15)+
  theme(legend.position = "none"),

ggplot(ardeche, aes(x = commondate))+
  geom_point(aes(y = poc_mg.L, col = "MES, mg.L"), alpha = 0.5)+
  scale_x_date(labels = function(x) format(x, "%d-%b"), date_minor_breaks = "1 month", name = "")+
  scale_color_manual(values = c("palegreen4"), name = "")+
  facet_grid(rows = vars(year))+
  labs(y = "MES, mg/L", col = "")+
  theme_bw(base_size = 15)+
  theme(legend.position = "none"),

ggplot(ardeche, aes(x = commondate))+
  geom_point(aes(y = poc_mg.L, col = "POC, mg/L"), alpha = 0.5)+
  scale_x_date(labels = function(x) format(x, "%d-%b"), date_minor_breaks = "1 month", name = "")+
  scale_color_manual(values = c("darkred"), name = "")+
  facet_grid(rows = vars(year))+
  labs(y = "POC, mg/L", col = "")+
  theme_bw(base_size = 15)+
  theme(legend.position = "none"),

ncol = 3
)

annotate_figure(plots, top = text_grob(title))

```


```{r ardeche-complete-years, fig.dim = c(10,15)}
complete_years <- c(2016:2022)
ardeche_complete <- ardeche %>% subset(year %in% complete_years) %>% filter(!is.na(q_L.s))
```


## Characteristics

```{r summary-data}
summary_ardeche <- merge(
  ardeche %>% subset(!is.na(mes_mg.L)) %>% group_by(year) %>% 
            summarise("Number of MES observations" = n(), 
                      "MES range, mg/L" = paste(round(quantile(mes_mg.L, probs = c(0,0.5,1), na.rm = T),2), collapse = " / ")),
  ardeche %>% subset(!is.na(poc_mg.L)) %>% group_by(year) %>% 
            summarise("Number of POC observations" = n(), 
            "POC, mg/L" = paste(round(quantile(poc_mg.L, probs = c(0,0.5,1), na.rm = T),3), collapse = " / ")), by = "year", all = T) %>%

  merge(ardeche %>% subset(!is.na(q_m3.s)) %>% group_by(year) %>% 
                  summarise("Number of Q observations" = n(), 
                  "Q range, m3/s" = paste(quantile(q_m3.s, probs = c(0,0.5,1), na.rm = T), collapse = " / ")), by = "year", all = T) %>% 
  merge(ardeche %>% group_by(year) %>% summarise("Number of days sampled" = length(unique(Date))), by = "year", all = T) %>%
  merge(ardeche %>% group_by(year) %>% 
                  summarise("Correlation MES/log(Q)" = round(cor(mes_mg.L, log(q_m3.s), use = "pairwise.complete.obs"),2)),
        by = "year", all = T) %>%
  merge(ardeche %>% group_by(year) %>% 
                  summarise("Correlation POC/log(Q)" = round(cor(poc_mg.L, log(q_m3.s), use = "pairwise.complete.obs"),2)),
        by = "year", all = T) %>%
  rbind(c("All years", 
          dim(subset(ardeche, !is.na(mes_mg.L)))[1], 
          paste(round(quantile(ardeche$mes_mg.L, probs = c(0,0.5,1), na.rm = T),2), collapse = " / "), 
          dim(subset(ardeche, !is.na(poc_mg.L)))[1], 
          paste(round(quantile(ardeche$poc_mg.L, probs = c(0,0.5,1), na.rm = T),3), collapse = " / "), 
          dim(subset(ardeche, !is.na(q_m3.s)))[1], 
          paste(quantile(ardeche$q_m3.s, probs = c(0,0.5,1), na.rm = T), collapse = " / "), 
          length(unique(ardeche$Date)),
          round(cor(ardeche$mes_mg.L, log(ardeche$q_m3.s), use = "pairwise.complete.obs" ),2),
          round(cor(ardeche$poc_mg.L, log(ardeche$q_m3.s), use = "pairwise.complete.obs" ),2)
          )) %>%
    rbind(c("Complete years", 
          dim(subset(ardeche_complete, !is.na(mes_mg.L)))[1], 
          paste(round(quantile(ardeche_complete$mes_mg.L, probs = c(0,0.5,1), na.rm = T),2), collapse = " / "), 
          dim(subset(ardeche_complete, !is.na(poc_mg.L)))[1], 
          paste(round(quantile(ardeche_complete$poc_mg.L, probs = c(0,0.5,1), na.rm = T),2), collapse = " / "), 
          dim(subset(ardeche_complete, !is.na(q_m3.s)))[1], 
          paste(round(quantile(ardeche_complete$q_m3.s, probs = c(0,0.5,1), na.rm = T),3), collapse = " / "), 
          length(unique(ardeche_complete$Date)),
          round(cor(ardeche_complete$mes_mg.L, log(ardeche_complete$q_m3.s), use = "pairwise.complete.obs" ),2),
          round(cor(ardeche_complete$poc_mg.L, log(ardeche_complete$q_m3.s), use = "pairwise.complete.obs" ),2)
          )
          ) %>%
  mutate(`POCobs/Qobs` = round(as.numeric(`Number of POC observations`)/as.numeric(`Number of Q observations`),2)) 

knitr::kable(summary_ardeche, digits = 2, caption = "Summary table of ardeche data") %>% kableExtra::kable_styling()

```




 Méthode choisie pour le calcul de flux: ratio. 


# Annual and interannual flux 



Il y a plus de mesures de Q que de mesures de poc. On utilise l'équivalence sum(load)/sum(q) = sum(load obs)/sum(q obs).

```{r uncertainties}
nyears <- length(complete_years)

q_u <- 0.1

```

## total flux

Quelle incertitude attribuer au POC ? On ne sait pas par quel instrument il a été mesuré. Faut-il lui attribuer une incertitude similaire à celle des MES dont il est issu ? 

```{r flux-for-obs}
ardeche_poc <- ardeche %>% filter(!is.na(poc_mg.L) & year %in% complete_years)

nrep <- 1000
nobs <- dim(ardeche_poc)[1]

poc_meas <- matrix(ardeche_poc$poc_mg.L, nrow = nrep, ncol = nobs, byrow = T)
# poc_cv <- 3.3*poc_meas^(-0.6) # from all data available on 29/05/2026
# poc_random <- matrix(rnorm(nrep*nobs, mean = 0, sd = 1), nrow=nrep, ncol = nobs)
# poc_noise <- poc_cv*poc_random
poc_mat <- poc_meas # * (1 + poc_noise/100) # final value of poc, with noise in percent

# Q matrix
q_meas <- matrix(ardeche_poc$q_L.s, nrow = nrep, ncol = nobs, byrow = T) # repeats nrow_boot times the vector q_L.s
q_noise <- matrix(rnorm(nrep*nobs, mean = 0, sd = q_u), nrow = nrep, ncol = nobs) # creates a noise in percent (proportion), between 0 and 10%
q_mat <- q_meas * (1 + q_noise) # final value of q, with noise

# Flux per time step
load_kg.s_mat <- poc_mat*1e-6*q_mat # without period

# Annual flux
index_years <- lapply(complete_years, function(y){which(ardeche_poc$year == y)}) # list of indices corresponding to each year
sum_loadobs <- sapply(index_years, function(idx){apply(load_kg.s_mat[,idx], 1, sum, na.rm = T)}) # 1 col per year

sum_qobs <- sapply(index_years, function(idx){apply(q_mat[,idx], 1, sum, na.rm = T)})

```

```{r sum-q-tot, cache.lazy = F}

nrep <- 1000
nobs <- dim(ardeche_complete)[1]

# Q matrix
qtot_meas <- matrix(ardeche_complete$q_L.s, nrow = nrep, ncol = nobs, byrow = T) # repeats nrow_boot times the vector q_L.s
qtot_noise <- matrix(rnorm(nrep*nobs, mean = 0, sd = q_u), nrow = nrep, ncol = nobs) # creates a noise in percent (proportion), between 0 and 10%
qtot_mat <- qtot_meas * (1 + qtot_noise) # final value of q, with noise


index_years_tot <- lapply(complete_years, function(y){which(ardeche_complete$year == y)}) # list of indices corresponding to each year
sum_qtot <- sapply(index_years_tot, function(idx){apply(qtot_mat[,idx], 1, sum, na.rm = T)})



```

```{r compute-flux}
annual_flux_kg.y <- sum_qtot*sum_loadobs/sum_qobs

u_method <- (53-0.53*(summary_ardeche$`POCobs/Qobs`*100))/100 # déterminé dans ardeche_method
# add uncertainty due to method, based on % POCobs/Qobs and results 
sd_by_year <- rep(u_method[match(complete_years, summary_ardeche$year)], each = nrep)
print(u_method)

flux_noise <- matrix(rnorm(nrep*length(complete_years), mean = 0, sd = sd_by_year), nrow = nrep, ncol = length(complete_years))


# Add uncertainty on years with less frequent sampling
s_u <- 0.25 # from test in isere_method for monthly mean of POC
sampling_noise <- matrix(rnorm(nrep*length(complete_years), mean = 0, sd = s_u), nrow = nrep, ncol = length(complete_years))


# annual flux
annual_flux_kg.y <- annual_flux_kg.y * (1 + flux_noise) * (1 + sampling_noise)


annual_flux_pi <- apply(annual_flux_kg.y, 2, quantile, probs = c(0.025, 0.5, 0.975), na.rm = T) # prediction interval for annual fluxes, per year. 3 lignes, 19 columns
annual_flux_mean <- colMeans(annual_flux_kg.y, na.rm = T) # mean annual flux per year. 1 vector
annual_flux_sd <- apply(annual_flux_kg.y, 2, sd, na.rm = T) # standard deviation of annual flux per year. Is just an estimate of goodness of mean, not as good as than the confidence interval. 

annual_flux_df <- data.frame(year = complete_years, 
                        annual_flux_mean = annual_flux_mean, 
                        annual_flux_variability = annual_flux_sd, 
                        annual_flux_pi_lower = annual_flux_pi[1,], 
                        annual_flux_pi_upper = annual_flux_pi[3,])

# Interannual flux 
interannual_flux_kg.y <- rowMeans(annual_flux_kg.y, na.rm = T) # mean interannual flux per iteration of the bootstrap
interannual_flux_pi <- quantile(interannual_flux_kg.y, probs = c(0.025, 0.5, 0.975), na.rm = T) # prediction interval
interannual_flux_mean <- mean(interannual_flux_kg.y, na.rm = T) # mean interannual flux
interannual_flux_variability <- sd(annual_flux_mean, na.rm = T) # standard deviation of interannual flux per year

interannual_flux_df <- data.frame(year = "interannual", annual_flux_mean = interannual_flux_mean, 
                                  annual_flux_variability = interannual_flux_variability,
                        annual_flux_pi_lower = interannual_flux_pi[1], 
                        annual_flux_pi_upper = interannual_flux_pi[3])

total_flux_df <- rbind(annual_flux_df, interannual_flux_df)
total_flux_df$group <- c(rep("annual", nyears), "interannual")

# Q df ----

annual_q <- sapply(index_years, function(idx){apply(q_mat[,idx], 1, sum, na.rm = T)}) # sum of fluxes per year, for each iteration of the bootstrap. Result is a matrix with nrow_boot rows and 19 columns (1 per year)
annual_q_pi <- apply(annual_q, 2, quantile, probs = c(0.025, 0.5, 0.975), na.rm = T) # prediction interval for annual fluxes, per year. 3 lignes, 19 columns
annual_q_mean <- colMeans(annual_q, na.rm = T) # mean annual flux per year. 1 vector
annual_q_sd <- apply(annual_q, 2, sd, na.rm = T) # standard deviation of annual flux per year. Is just an estimate of goodness of mean, not as good as than the confidence interval. 
interannual_q <- rowMeans(annual_q, na.rm = T) # mean interannual flux per iteration of the bootstrap
interannual_q_pi <- quantile(interannual_q, probs = c(0.025, 0.5, 0.975), na.rm = T) # prediction interval
interannual_q_mean <- mean(interannual_q, na.rm = T) # mean interannual flux
interannual_q_variability <- sd(annual_q_mean, na.rm = T) # standard deviation of interannual flux per year

q_df <- data.frame(year = c(complete_years, "interannual"), 
                        q_mean = c(annual_q_mean, interannual_q_mean),
                        q_variability = c(annual_flux_sd, interannual_q_variability), 
                        q_pi_lower = c(annual_q_pi[1,], interannual_q_pi[1]), 
                        q_pi_upper = c(annual_q_pi[3,], interannual_q_pi[3]),
                   group = c(rep("annual", nyears), "interannual"))

# Plot -----
ggplot()+
  geom_col(data = total_flux_df, aes(x=year, y = annual_flux_mean, fill = group))+
    geom_errorbar(data = total_flux_df, aes(x = year, ymin = annual_flux_pi_lower, ymax = annual_flux_pi_upper, col = "prediction interval"), width = 0.3, size = 0.8)+
  geom_errorbar(data = filter(total_flux_df, year == "interannual"), aes(x = year, ymin = annual_flux_mean - annual_flux_variability, ymax = annual_flux_mean + annual_flux_variability, col = "interannual variability"), width = 0.2, size = 0.8, linetype = 2)+
  scale_fill_manual(values = c("annual" = "lightblue", "interannual" = "indianred"))+
  scale_color_manual(values = c("prediction interval" = "darkblue", "interannual variability" = "darkred"), name = "")+
   labs(x = "Year", y = "Flux (kg/year)", fill = "")+
  theme_minimal(base_size = 15)+
  theme(axis.text.x = element_text(angle = 45, hjust = 1), legend.position = "bottom")

ggplot()+
  geom_col(data = q_df, aes(x=year, y = q_mean, fill = group))+
    geom_errorbar(data = q_df, aes(x = year, ymin = q_pi_lower, ymax = q_pi_upper, col = "prediction interval"), width = 0.3, size = 0.8)+
  geom_errorbar(data = filter(q_df, year == "interannual"), aes(x = year, ymin = q_mean - q_variability, ymax = q_mean + q_variability, col = "interannual variability"), width = 0.2, size = 0.8, linetype = 2)+
  scale_fill_manual(values = c("annual" = "lightblue", "interannual" = "indianred"))+
  scale_color_manual(values = c("prediction interval" = "darkblue", "interannual variability" = "darkred"), name = "")+
   labs(x = "Year", y = "Discharge (L/year)", fill = "")+
  theme_minimal(base_size = 15)+
  theme(axis.text.x = element_text(angle = 45, hjust = 1), legend.position = "bottom")

knitr::kable(total_flux_df, digits = 2, row.names = F) %>% kableExtra::kable_styling()

```

## Specific flux

```{r specific-flux}
total_sflux_df <- cbind(total_flux_df[,"year"], total_flux_df[,2:5] / bv, total_flux_df[,"group"]) %>% setNames(names(total_flux_df))
#total_sflux_df <- rbind(annual_sflux_df, interannual_sflux_df)
total_sflux_df$group <- c(rep("annual", nyears), "interannual")

ggplot()+
  geom_col(data = total_sflux_df, aes(x=year, y = annual_flux_mean, fill = group), width = 0.8)+
    geom_errorbar(data = total_sflux_df, aes(x = year, ymin = annual_flux_pi_lower, ymax = annual_flux_pi_upper, col = "prediction interval"), width = 0.3, size = 0.8)+
  geom_errorbar(data = filter(total_sflux_df, year == "interannual"), aes(x = year, ymin = annual_flux_mean - annual_flux_variability, ymax = annual_flux_mean + annual_flux_variability, col = "interannual variability"), width = 0.2, size = 0.8, linetype = 2)+
  scale_fill_manual(values = c("annual" = "lightblue", "interannual" = "indianred"))+
  scale_color_manual(values = c("prediction interval" = "darkblue", "interannual variability" = "darkred"), name = "")+
   labs(x = "Year", y = "Flux (kg/km2/year)", fill = "")+
  theme_minimal(base_size = 15)+
  theme(axis.text.x = element_text(angle = 45, hjust = 1), legend.position = "bottom")

ggsave(here("figures","sflux_ardeche_poc.svg"))

knitr::kable(total_sflux_df, digits = 2, row.names = F) %>% kableExtra::kable_styling()
```


## Variance decomposition

LOAD = sumQ * sum(load obs) / sum(q obs)

log(load) = log(sumQ) + log(sum load obs) - log(sum q obs)

log(load) = log(q1)+...+log(qtot)

```{r variance}
## Variances par année

list_var <- lapply(1:length(complete_years), function(idx){
  
lnQtot <- as.vector(log(sum_qtot[,idx]))
lnloadobs <- as.vector(log(sum_loadobs[,idx]))
lnQobs <- as.vector(log(sum_qobs[,idx]))

mask <- complete.cases(lnQtot, lnloadobs, lnQobs)  &
        is.finite(lnQtot) & is.finite(lnloadobs) & is.finite(lnQobs)

M <- cbind(Qtot = lnQtot[mask], load = lnloadobs[mask], Qobs = lnQobs[mask])

cov_matrix <- cov(M, use = "pairwise.complete.obs") 

# verif
var_lnF_check <- sum(cov_matrix)
var_lnF_direct <- var(rowSums(M))

if(var_lnF_check != var_lnF_direct){warning("Attention : les variances ne correspondent pas")}

return(cov_matrix)
})

var_flux_by_year <- lapply(list_var, function(i){
  var_flux = sum(i)
  setNames(var_flux, "var_lnF")}) %>% bind_rows(.id = "year")
vars_by_year <- lapply(list_var, diag) %>% bind_rows(.id = "year") # variance des paramètres par année
cov_by_year <- lapply(list_var, function(i){
  vals <- i[upper.tri(i)]
  setNames(as.list(vals), c("cov_loadQtot","cov_QobsQtot","cov_Qobsload"))}) %>% 
  bind_rows(.id = "year") 

annual_variances <- merge(var_flux_by_year, vars_by_year, by = "year") %>% merge(cov_by_year, by = "year")
annual_variances$year <- complete_years


# Variance interannuelle

lnQtot <- as.vector(log(sum_qtot))
lnloadobs <- as.vector(log(sum_loadobs))
lnQobs <- as.vector(log(sum_qobs))

mask <- complete.cases(lnQtot, lnloadobs, lnQobs)  &
        is.finite(lnQtot) & is.finite(lnloadobs) & is.finite(lnQobs)

M <- cbind(Qtot = lnQtot[mask], load = lnloadobs[mask], Qobs = lnQobs[mask])

cov_matrix <- cov(M, use = "pairwise.complete.obs") 

# verif
var_lnF_check <- sum(cov_matrix)
var_lnF <- var(rowSums(M))

if(var_lnF_check != var_lnF){warning("Attention : les variances ne correspondent pas")}


# put results in df
vars_interannual <- c(var_lnF, diag(cov_matrix)) # variance des paramètres par année
cov_interannual <- cov_matrix[upper.tri(cov_matrix)] %>%
  setNames(c("cov_loadQtot","cov_QobsQtot","cov_Qobsload")) 

interannual_variances <- c(year = "Interrannuel", vars_interannual, cov_interannual)

all_variances <- rbind(annual_variances, interannual_variances) %>% mutate(across(where(is.character) & !any_of("year"), as.numeric))



variance_decomposition <- all_variances  %>% 
  mutate(part_Qtot = Qtot/var_lnF, part_load = load/var_lnF, part_Qobs = Qobs/var_lnF, 
         part_covloadQtot = 2*cov_loadQtot/var_lnF, 
         part_covQobsQtot = 2*cov_QobsQtot/var_lnF, 
         part_covQobsload = 2*cov_Qobsload/var_lnF, 
         part_cov = part_covloadQtot + part_covQobsQtot + part_covQobsload,
         check = part_Qtot+part_load+part_Qobs+part_covloadQtot+part_covQobsQtot+part_covQobsload)


vd_long <- variance_decomposition %>%
  select(year, part_Qtot, part_load, part_Qobs, part_cov) %>%
  tidyr::pivot_longer(cols = c(part_Qtot, part_load, part_Qobs, part_cov),
               names_to = "terme", values_to = "part")  %>%
  mutate(terme = recode(terme,
                         part_Qtot = "Variance Q annuel",
                         part_load = "Variance flux instantané",
                         part_Qobs = "Variance Q flux",
                        part_cov = "Covariances"))

ggplot(vd_long, aes(x = year, y = part, fill = terme)) +
  geom_col(position = "stack") +
  geom_hline(yintercept = 0, linetype = "dashed", color = "grey40") +
  scale_fill_manual(values = c("Variance Q annuel" = "lightblue",
                                "Variance flux instantané" = "indianred",
                                "Variance Q flux" = "darkblue",
                               "Covariances" = "darkred")) +
  scale_y_continuous(labels = scales::percent, breaks = c(-0.40,-0.20,0,0.20,0.40,0.60,0.80,1.00,1.2,1.4)) +
  labs(x = "Année", y = "Part de la variance du log-flux",
       fill = "Terme",
       title = "Décomposition de la variance du flux") +
  theme_bw() + theme(legend.position = "bottom", axis.text.x = element_text(angle = 45, vjust = 0.5))

vd_long_abs <- variance_decomposition %>%
  select(year, Qtot, load, Qobs, cov_loadQtot,cov_QobsQtot,cov_Qobsload) %>%
  tidyr::pivot_longer(cols = -year, names_to = "terme", values_to = "valeur")

ggplot(vd_long_abs, aes(x = year, y = valeur, fill = terme)) +
  geom_col(position = "dodge") +
  geom_point(data = variance_decomposition, aes(x = year, y = var_lnF),
             inherit.aes = FALSE, shape = 18, size = 3) +
  scale_fill_manual(values = c("darkblue","lightblue","darkred","indianred","palegreen4","cornsilk3"))+
   theme_bw() + theme(legend.position = "bottom", axis.text.x = element_text(angle = 45, vjust = 0.5))+
  scale_y_continuous(trans = "log", breaks = )+
  labs(y = "Variance (échelle log)", title = "Termes de la décomposition (valeurs absolues)")

```



# Export données

```{r exporter-valeurs-dans-csv-commun}

rmd_id <- "ardeche"

if(unit_flux == "ton"){
rmd_values <- data.frame(
  rmd = rmd_id,
  carbon  = "POC",
  flux_ton = total_flux_df$annual_flux_mean[total_flux_df$year == "interannual"],
    flux_ton_sd = total_flux_df$annual_flux_variability[total_flux_df$year == "interannual"],
    flux_ton_pil = total_flux_df$annual_flux_pi_lower[total_flux_df$year == "interannual"],
    flux_ton_piu = total_flux_df$annual_flux_pi_upper[total_flux_df$year == "interannual"],
    flux_ton_km2 = total_sflux_df$annual_flux_mean[total_flux_df$year == "interannual"],
   flux_ton_km2_sd = total_sflux_df$annual_flux_variability[total_flux_df$year == "interannual"],
   flux_ton_km2_pil = total_sflux_df$annual_flux_pi_lower[total_flux_df$year == "interannual"],
   flux_ton_km2_piu = total_sflux_df$annual_flux_pi_upper[total_flux_df$year == "interannual"],
  nb_years = length(complete_years)
)
} else if(unit_flux == "kg"){
  rmd_values <- data.frame(
  rmd = rmd_id,
  carbon  = "POC",
  flux_ton = total_flux_df$annual_flux_mean[total_flux_df$year == "interannual"]*1e-3,
    flux_ton_sd = total_flux_df$annual_flux_variability[total_flux_df$year == "interannual"]*1e-3,
    flux_ton_pil = total_flux_df$annual_flux_pi_lower[total_flux_df$year == "interannual"]*1e-3,
    flux_ton_piu = total_flux_df$annual_flux_pi_upper[total_flux_df$year == "interannual"]*1e-3,
    flux_ton_km2 = total_sflux_df$annual_flux_mean[total_flux_df$year == "interannual"]*1e-3,
   flux_ton_km2_sd = total_sflux_df$annual_flux_variability[total_flux_df$year == "interannual"]*1e-3,
   flux_ton_km2_pil = total_sflux_df$annual_flux_pi_lower[total_flux_df$year == "interannual"]*1e-3,
   flux_ton_km2_piu = total_sflux_df$annual_flux_pi_upper[total_flux_df$year == "interannual"]*1e-3,
  nb_years = length(complete_years)
  )
}


# Lire le fichier existant ou créer un dataframe vide
if (file.exists(here("resultats.xlsx"))) {
  df_shared <- read_xlsx(here("resultats.xlsx"))
} else {
  df_shared <- data.frame()
}

# Mettre à jour la ligne du Rmd ou l'ajouter si absente
if (rmd_id %in% df_shared$rmd) {
  df_shared[df_shared$rmd == rmd_id, ] <- rmd_values  # mise à jour
} else {
  df_shared <- rbind(df_shared, rmd_values)            # ajout
}



# Réécrire
write_xlsx(df_shared, here("resultats.xlsx"))
```